### 2015-03-11 theory.tex
add a couple of formulas for the theory part

\section{Theoretical Approach}

\begin{align}
 \Gamma_{ICD}  &= \sum\limits_{i,\beta} N_{ICD,i}  \Gamma_{ICD,i,\beta}\\
 \Gamma_{ETMD} &= \sum\limits_{j,\beta} N_{ETMD,j} \Gamma_{ETMD,j,\beta}\\
\end{align}

$N_{ICD} = N_{in} \cdot N_{fin} = N_{Ar} \cdot N_{Xe}
 = \sum\limits_i N_{ICD,i}$
$N_{ETMD} = N_{in} \cdot N_{fin} (N_{fin} - 1) = N_{Ar} \cdot N_{Xe} (N_{Xe} - 1)
 = \sum\limits_j N_{ETMD,j}$

$N_{ICD,i}$ and $N_{ETMD,j}$ depend on the structure

\begin{equation}
 \Gamma_{\beta}(E_{res}) = 2\pi \left|
                           \braket{\Phi_{in}| H_f |\chi_{\beta}}
                           \right|^2
\end{equation}

\begin{equation}
 \Gamma_{ICD,i,\beta} = 2\pi
                        \frac{\sigma^{(X_E)}(\omega_{vp,\beta})}
                        {R_i^6 \, \omega_{vp,\beta}^4 \tau_{in,\beta}}
\end{equation}

\begin{equation}
 \Gamma_{ETMD,j,\beta} = 2\pi \sum\limits_{m,M_{in}',D}
                        \frac{a_m \Theta_m(\alpha_i) \sigma^{(X_E)}(\omega_{vp,\beta})
                              \tilde{D}_{m,j,\beta}(M_{in,D},M_{in,D'})}
                         {R_j^6 \omega_{vp,\beta}}
\end{equation}

\begin{equation}
\end{equation}

\begin{equation}
\end{equation}

\begin{equation}
\end{equation}

\begin{equation}
\end{equation}

\begin{equation}
\end{equation}

\begin{equation}
\end{equation}

### 2015-03-11 arxe-2015-v01.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% This is a (brief) model paper using the achemso class
%% The document class accepts keyval options, which should include
%% the target journal and optionally the manuscript type.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[journal=jpccck,manuscript=article]{achemso}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later. Do NOT use any
%% packages which require e-TeX (for example etoolbox): the e-TeX
%% extensions are not currently available on the ACS conversion
%% servers.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional macros here.  Please use \newcommand* where
%% possible, and avoid layout-changing macros (which are not used
%% when typesetting).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newcommand*\mycommand[1]{\texttt{\emph{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Elke Fasshauer}
\affiliation[UIT]{Tromso, Norway}
\email{elke.fasshauer@uit.no}
\author{Melanie Mucke}
\altaffiliation{Now at: Department of Physics and Astronomy, Uppsala University, Box 516, 75120 Uppsala, Sweden}
\author{Marko F\"orstel}
\altaffiliation{Now at: University of Hawai'i at Manoa, 2545 McCarthy Mall, 96816 HI Honolulu, USA}
\affiliation[IPP]{Max-Planck-Institute for Plasma Physics, Boltzmannstr. 2, 85748 Garching, Germany}
\author{...}
\author{Uwe Hergenhahn}
\affiliation[IPP HGW]{Max-Planck-Institute for Plasma Physics, Wendelsteinstr. 1, 14791 Greifswald, Germany}
\email{uwe.hergenhahn@ipp.mpg.de}
%\phone{+123 (0)123 4445556}
%\fax{+123 (0)123 4445557}
%\alsoaffiliation[Second University]
%{Department of Chemistry, Second University, Nearby Town}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{One more attempt on ArXe}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\abbreviations{IR,NMR,UV}
%\keywords{American Chemical Society, \LaTeX}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The manuscript does not need to include \maketitle, which is
%% executed automatically.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "tocentry" environment can be used to create an entry for the
%% graphical table of contents. It is given here as some journals
%% require that it is printed as part of the abstract page. It will
%% be automatically moved as appropriate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tocentry}

Some journals require a graphical entry for the Table of Contents.
This should be laid out ``print ready'' so that the sizing of the
text is correct.

Inside the \texttt{tocentry} environment, the font used is Helvetica
8\,pt, as required by \emph{Journal of the American Chemical
Society}.

The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
permitted for  \emph{Journal of the American Chemical Society}
graphical table of content entries. The box will not resize if the
content is too big: instead it will overflow the edge of the box.

This box and the associated title will always be printed on a
separate page at the end of the document.

\end{tocentry}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%
Electron spectroscopy can make important contributions to the research on composition and structure of free nanoparticles.\cite{jpcc} Besides by photoionization, free electrons emerging from nanoparticles can also be produced by the relaxation of electronically excited states. One such process, which is of particular importance in weakly bonded systems, is the Interatomic or Intermolecular Coulombic Decay (ICD).\cite{cederbaum} In ICD, an electronic excitation decays by energy transfer to one of its neighbour atoms or molecules, thus releasing a free electron from the latter site. ICD is an important relaxation channel e.g. for inner-valence holes in elements C-Ne, and also for core levels vacancies e.g. in \ce{H2O}, where it competes with Auger decay\cite{slavicek}.

By definition, ICD is particularly sensitive to the chemical environment of the atom or molecule in which the primary excitation has taken place. We suggest that this property of ICD decay spectra can be used to derive information on a nanoparticle or a solvation system, for example. We report here about studies in which we produced heterogeneous clusters of the noble gases Ar and Xe with different sizes, and compositions ranging from a few Xe dopant atoms in an Ar matrix to clusters containing an equal amount of both species. By the use of electron, electron coincidence spectroscopy and of {\it ab initio} calculations on prototypical systems we show how the radiationless decay spectrum of Ar inner valence (3s) ionized states connects to the structure of the clusters.

Intermolecular Coulombic Decay initially was predicted from theoretical considerations of the energy levels in singly vs. doubly ionized, and doubly vs. triply ionized, hydrogen bonded clusters.\cite{cederbaum} First experimental work some years later used Ne clusters,\cite{marburger,jahnkenedimer} but quickly was followed by demonstrations of ICD in a diverse range of other systems. Experimental and theoretical progress has been reviewed.\cite{hergenhahn_review, averbukh_review, jahnke_review} ICD proceeds by an initial ionization producing an ion in an excited state, followed by a transfer of energy to a neighbouring site, and an electron emission process therefrom. In the final state a positive charge remains at the site of ionization, and another was created at another atom or molecule. Soon after, related autoionization processes were discovered that proceed via a charge transfer instead of an energy transfer. 
%These were termed `Electron Transfer Mediated Decay' (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in which the originally excited site is neutralized by the decay, and 'exchange ICD' for charge transfer contributions to the normal ICD amplitude.\cite{santrarev,jahnkesat}
We find that both energy and charge transfer induced autoionization plays a role in Ar-Xe, and will detail the relevant processes below. The notion of ICD requires that the electronic orbitals of the two sites can be distinguished, which typically is the case in weakly bonded systems, held together by hydrogen bonds or van-der-Waals bonds. In the case of strong (covalent or metallic) bonding, there is no distinction between ICD and Auger decay.\cite{hergenhahn_review}

First experiments on ICD in heterogeneous systems were on Ne-Ar clusters.\cite{barthnear} Those were followed by studies of ICD-like inner-shell decays in aqueous solution.\cite{aziz,pokapanich,pokapanich2011} Pioneering work also showed the potential for studies of the interface between a substrate and an adsorbate by ICD.\cite{grieves} More detailed work on Ne-Ar clusters was recently presented by some of the authors.\cite{fasshauer2014} For this system, a detailed analysis of photoelectron spectra with respect to structural features of the mixed clusters is also available.\cite{lundwall} In Ref. \citenum{fasshauer2014} it was shown that an analysis of the ICD spectra allowed to decide between structural alternatives for which the photoelectron data were indiscriminate.

Rare gas clusters are suitable prototype systems for studies of (e.g.) ICD, as they can easily be produced by supersonic expansion. Mixed rare gas clusters easily form by coexpansion of the two gases through a cooled nozzle. The size of the clusters can be changed by varying the expansion parameters, although for heterogeneous clusters some uncertainty remains with respect to the cluster size, as empirical scaling laws \cite{hagena1981} apply to expansion of pure gases only. Early studies of Ar-Xe clusters mostly focussed on the extreme cases of a single Xe atom embedded in an Ar cluster (e.g. Ref. \citenum{lengenprl}). Different sites of the dopant atom (on top of a surface, integrated in an Ar surface, inside the cluster) were distinguished by three separate bands in the fluorescence yield recorded as a function of excitation wavelength.\cite{lengenprl} Increasing the Xe concentration in the expansion lead to changes in the fluorescence excitation spectrum that were interpreted as formation of \ce{Xe2} and larger Xe complexes inside the clusters.\cite{lengen} Experiments on Xe-rich mixed clusters were also conducted, and concluded that increasing the Xe content in a coexpanding ArXe mixture leads to the formation of Xe-core, Ar-shell systems with a sharp interface.\cite{tchaplyguine} This finding was confirmed by electron diffraction experiments.\cite{Danylchenko} Always, the observed Xe content in the clusters is above the Xe content in the expanding gas mixture, as Xe can be condensed much easier than Ar.

Most recently, on the experimental side the investigations

<Lindblad, Fasshauer>

%\begin{figure}
%  As well as the standard float types \texttt{table}\\
%  and \texttt{figure}, the class also recognises\\
%  \texttt{scheme}, \texttt{chart} and \texttt{graph}.
%  \caption{An example figure}
%  \label{fgr:example}
%\end{figure}

%\begin{table}
%  \caption{An example table}
%  \label{tbl:example}
%  \begin{tabular}{ll}
%    \hline
%    Header one  & Header two  \\
%    \hline
%    Entry one   & Entry two   \\
%    Entry three & Entry four  \\
%    Entry five  & Entry five  \\
%    Entry seven & Entry eight \\
%    \hline
%  \end{tabular}
%\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "Acknowledgement" section can be given in all manuscript
%% classes.  This should be given within the "acknowledgement"
%% environment, which will make the correct section or running title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgement}
%
We thank HZB for the allocation of synchrotron radiation beamtime, and the Deutsche Forschungsgemeinschaft for funding via the Forschergruppe 1789.
%
\end{acknowledgement}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The same is true for Supporting Information, which should use the
%% suppinfo environment.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{suppinfo}

This will usually read something like: ``Experimental procedures and
characterization data for all new compounds. The class will
automatically add a sentence pointing to the information on-line:

\end{suppinfo}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The appropriate \bibliography command should be placed here.
%% Notice that the class file automatically sets \bibliographystyle
%% and also names the section correctly.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{arxe}

\end{document}

### 2015-03-12 arxe-2015-v01.tex

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[journal=jpccck,manuscript=article]{achemso}
+\documentclass[journal=jpccck,manuscript=article,layout=twocolumn]{achemso}
 
@@
 \citenum{lengenprl}).
-Different sites of the dopant atom (on top of a surface, integrated in an Ar surface, inside the cluster) were distinguished by three separate bands in the fluorescence yield recorded as a function of excitation wavelength.\cite{lengenprl} Increasing the Xe concentration in the expansion lead to changes in the fluorescence excitation spectrum that were interpreted as formation of \ce{Xe2} and larger Xe complexes inside the clusters.\cite{lengen} Experiments on Xe-rich mixed clusters were also conducted, and concluded that increasing the Xe content in a coexpanding ArXe mixture leads to the formation of Xe-core, Ar-shell systems with a sharp interface.\cite{tchaplyguine} This finding was confirmed by electron diffraction experiments.\cite{Danylchenko} Always, the observed Xe content in the clusters is above the Xe content in the expanding gas mixture, as Xe can be condensed much easier than Ar.
+Different sites of the dopant atom (on top of a surface, integrated in an Ar surface, inside the cluster) were distinguished by three separate bands in the fluorescence yield recorded as a function of excitation wavelength.\cite{lengenprl} Increasing the Xe concentration in the expansion lead to changes in the fluorescence excitation spectrum that were interpreted as formation of \ce{Xe2} and larger Xe complexes inside the clusters.\cite{lengen} Experiments on Xe-rich mixed clusters were also conducted, and concluded that increasing the Xe content in a coexpanding ArXe mixture leads to the formation of Xe-core, Ar-shell systems with a sharp interface between the two species.\cite{tchaplyguine,hoener} This finding was confirmed by electron diffraction experiments.\cite{Danylchenko} Always, the observed Xe content in the clusters is above the Xe content in the expanding gas mixture, as Xe can be condensed much easier than Ar.
 
-Most recently, on the experimental side the investigations
+Most recently, on the experimental side photoelectron spectra of small Ar-Xe clusters were analyzed, adding to the findings in earlier work.\cite{Lindblad} We will discuss this paper in connection with our results below.
+Theoretical work on Ar-Xe was also published, and had a focus on the radiationless decay of Ar inner valence vacancies in these systems.\cite{fasshauer,fasshauer_b} Interestingly, it was found that Ar 3s$^{-1}$ is stable against autoionization in an ArXe dimer, but is destabilized by adding further Xe atoms, or an Ar solvation shell, to the system.
+Again, we will detail these results in conjunction with our current work.
 
-<Lindblad, Fasshauer>
+The plan of our paper is as follows: ...
 

### 2015-03-12 intro.tex
make master file and move introduction to separate file

--- 2015-03-12 arxe-2015-v01.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% This is a (brief) model paper using the achemso class
-%% The document class accepts keyval options, which should include
-%% the target journal and optionally the manuscript type.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[journal=jpccck,manuscript=article,layout=twocolumn]{achemso}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Place any additional packages needed here.  Only include packages
-%% which are essential, to avoid problems later. Do NOT use any
-%% packages which require e-TeX (for example etoolbox): the e-TeX
-%% extensions are not currently available on the ACS conversion
-%% servers.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% If issues arise when submitting your manuscript, you may want to
-%% un-comment the next line.  This provides information on the
-%% version of every file you have used.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%\listfiles
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Place any additional macros here.  Please use \newcommand* where
-%% possible, and avoid layout-changing macros (which are not used
-%% when typesetting).
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newcommand*\mycommand[1]{\texttt{\emph{#1}}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Meta-data block
-%% ---------------
-%% Each author should be given as a separate \author command.
-%%
-%% Corresponding authors should have an e-mail given after the author
-%% name as an \email command. Phone and fax numbers can be given
-%% using \phone and \fax, respectively; this information is optional.
-%%
-%% The affiliation of authors is given after the authors; each
-%% \affiliation command applies to all preceding authors not already
-%% assigned an affiliation.
-%%
-%% The affiliation takes an option argument for the short name.  This
-%% will typically be something like "University of Somewhere".
-%%
-%% The \altaffiliation macro should be used for new address, etc.
-%% On the other hand, \alsoaffiliation is used on a per author basis
-%% when authors are associated with multiple institutions.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author{Elke Fasshauer}
-\affiliation[UIT]{Tromso, Norway}
-\email{elke.fasshauer@uit.no}
-\author{Melanie Mucke}
-\altaffiliation{Now at: Department of Physics and Astronomy, Uppsala University, Box 516, 75120 Uppsala, Sweden}
-\author{Marko F\"orstel}
-\altaffiliation{Now at: University of Hawai'i at Manoa, 2545 McCarthy Mall, 96816 HI Honolulu, USA}
-\affiliation[IPP]{Max-Planck-Institute for Plasma Physics, Boltzmannstr. 2, 85748 Garching, Germany}
-\author{...}
-\author{Uwe Hergenhahn}
-\affiliation[IPP HGW]{Max-Planck-Institute for Plasma Physics, Wendelsteinstr. 1, 14791 Greifswald, Germany}
-\email{uwe.hergenhahn@ipp.mpg.de}
-%\phone{+123 (0)123 4445556}
-%\fax{+123 (0)123 4445557}
-%\alsoaffiliation[Second University]
-%{Department of Chemistry, Second University, Nearby Town}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The document title should be given as usual. Some journals require
-%% a running title from the author: this should be supplied as an
-%% optional argument to \title.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{One more attempt on ArXe}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Some journals require a list of abbreviations or keywords to be
-%% supplied. These should be set up here, and will be printed after
-%% the title and author information, if needed.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\abbreviations{IR,NMR,UV}
-%\keywords{American Chemical Society, \LaTeX}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The manuscript does not need to include \maketitle, which is
-%% executed automatically.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The "tocentry" environment can be used to create an entry for the
-%% graphical table of contents. It is given here as some journals
-%% require that it is printed as part of the abstract page. It will
-%% be automatically moved as appropriate.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{tocentry}
-
-Some journals require a graphical entry for the Table of Contents.
-This should be laid out ``print ready'' so that the sizing of the
-text is correct.
-
-Inside the \texttt{tocentry} environment, the font used is Helvetica
-8\,pt, as required by \emph{Journal of the American Chemical
-Society}.
-
-The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
-permitted for  \emph{Journal of the American Chemical Society}
-graphical table of content entries. The box will not resize if the
-content is too big: instead it will overflow the edge of the box.
-
-This box and the associated title will always be printed on a
-separate page at the end of the document.
-
-\end{tocentry}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The abstract environment will automatically gobble the contents
-%% if an abstract is not used by the target journal.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-\end{abstract}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The "Acknowledgement" section can be given in all manuscript
-%% classes.  This should be given within the "acknowledgement"
-%% environment, which will make the correct section or running title.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{acknowledgement}
-%
-We thank HZB for the allocation of synchrotron radiation beamtime, and the Deutsche Forschungsgemeinschaft for funding via the Forschergruppe 1789.
-%
-\end{acknowledgement}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The same is true for Supporting Information, which should use the
-%% suppinfo environment.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{suppinfo}
-
-This will usually read something like: ``Experimental procedures and
-characterization data for all new compounds. The class will
-automatically add a sentence pointing to the information on-line:
-
-\end{suppinfo}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The appropriate \bibliography command should be placed here.
-%% Notice that the class file automatically sets \bibliographystyle
-%% and also names the section correctly.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliography{arxe}
-
-\end{document}

### 2015-03-13 theory.tex
add some theory from my thesis

@@
 \section{Theoretical Approach}
+Experimental coincidence spectra are given by the kinetic energies $E_{sec}$
+of the secondary electron
+and the intensities of the peaks. The latter is proportional to the
+probability of the decay as well as the theoretically determinable
+decay width $\Gamma=\frac{\hbar}{\tau}$,
+which is inverse proportional to the lifetime $\tau$. The manifold of these
+energies and decay widths will therefore compose the electron-electron
+coincidence spectrum.
+In case of noble gas clusters
+with given structures three aspects have to be taken into account:
+different decay mechanisms, the possibility to decay with multiple
+interaction partners and different decay channels within each decay mechanism.
+At the current stage of development we need to neglect the nuclear dynamics which
+additionally might play an important role.
+
+Decomposing every system into pairs and triples of atoms is a very useful
+first order approximation to both the investigation of energies and
+decay widths of a larger system. Pairs and triples are combinations of
+two and three atoms, respectively.
+These atoms do not necessarily need to form bonds between each other or
+even be close, but they are characterized according to fixed internal
+coordinates. Each pair and triple can be described by its properties
+which are in first order of approximation independent of further, eventually
+present, atoms. In the following, this approach is going to be called
+model of pairs and triples.
+
+In case of the electronic decay processes one is interested in the
+energies of the initial $E_{in}$ and the final states $E_{fin}$ of
+the corresponding processes in order to determine, whether a channel $\beta$
+is open, i.e., in accordance with energy conservation, or not. When the channel
+is open, the excess energy is carried away by the emitted electron $E_{sec}$
+in form of its kinetic energy. These energies can in the model
+of pairs and triples be approximated to be
+
+\begin{align}
+ E_{in}^\beta  &= SIP(X_{in}^\beta) \label{equation:E_in}\\
+ E_{fin}^\beta &= SIP(X_{fin1}^\beta) + SIP(X_{fin2}^\beta) + \frac 1d
+           \label{equation:E_fin}\\
+ E_{sec}^\beta &= E_{in}^\beta - E_{fin}^\beta \label{equation:E_sec}
+\end{align}
+where $X_{in}$ denotes the initially ionized atom and
+$X_{fin1}$ and $X_{fin2}$ describe the two ionized
+atoms in the final state. $\beta$ denotes the decay channel characterized
+by the quantum numbers of the ionized atoms in the pairs
+and triples and $d$ denotes the interatomic distance between the atoms
+$X_{fin1}$ and $X_{fin2}$. The initially ionized atom $X_{in}$ can
+coincide with one or both of
+the final state atoms
+$X_{fin1}$ and $X_{fin2}$. As explained in
+chapter \ref{chapter:autoionization}, the distribution
+of the vacancies over the different
+atoms determines the kind of electronic decay process at hand. Hence, in an
+Auger process all three atoms would coincide, for an ICD $X_{in}$
+would coincide with one of $X_{fin1}$ and $X_{fin2}$ and for an {ETMD}3
+all ionized states are located on different atoms.
+
+In all autoionization processes considered, a second electron
+is emitted with the kinetic energy $E_{sec}$. If $E_{sec}<0$, then
+the final state energy is higher than the initial state energy and the        
+process is energetically not accessible. Hence, the corresponding channel     
+is closed.
+
+This ad hoc approach easily allows to correct for energetic shifts of         
+ionization potentials as observed in larger clusters.
 

### 2015-03-13 intro.tex

@@
 %
-Electron spectroscopy can make important contributions to the research on composition and structure of free nanoparticles.\cite{jpcc} Besides by photoionization, free electrons emerging from nanoparticles can also be produced by the relaxation of electronically excited states.
-One such process, which is of particular importance in weakly bonded systems, is the Interatomic or Intermolecular Coulombic Decay (ICD).\cite{cederbaum} In ICD, an electronic excitation decays by energy transfer to one of its neighbour atoms or molecules, thus releasing a free electron from the latter site.
-ICD is an important relaxation channel e.g.
-for inner-valence holes in elements C-Ne, and also for core levels vacancies e.g.
-in \ce{H2O}, where it competes with Auger decay\cite{slavicek}.
+Electron spectroscopy can make important contributions to the 
+research on composition and structure of free nanoparticles.\cite{
+jpcc} Besides by photoionization, free electrons emerging from 
+nanoparticles can also be produced by the relaxation of 
+electronically excited states. One such process, which is of 
+particular importance in weakly bonded systems, is the 
+Interatomic or Intermolecular Coulombic Decay (ICD).\cite{
+cederbaum} In ICD, an electronic excitation decays by energy 
+transfer to one of its neighbour atoms or molecules, thus 
+releasing a free electron from the latter site. ICD is an 
+important relaxation channel e.g. for inner-valence holes in 
+elements C-Ne, and also for core levels vacancies e.g. in \ce{H2O}
+, where it competes with Auger decay\cite{slavicek}.
 
-By definition, ICD is particularly sensitive to the chemical environment of the atom or molecule in which the primary excitation has taken place.
-We suggest that this property of ICD decay spectra can be used to derive information on a nanoparticle or a solvation system, for example.
-We report here about studies in which we produced heterogeneous clusters of the noble gases Ar and Xe with different sizes, and compositions ranging from a few Xe dopant atoms in an Ar matrix to clusters containing an equal amount of both species.
-By the use of electron, electron coincidence spectroscopy and of {\it ab initio} calculations on prototypical systems we show how the radiationless decay spectrum of Ar inner valence (3s) ionized states connects to the structure of the clusters.
+By definition, ICD is particularly sensitive to the chemical 
+environment of the atom or molecule in which the primary 
+excitation has taken place. We suggest that this property of ICD 
+decay spectra can be used to derive information on a nanoparticle 
+or a solvation system, for example. We report here about studies 
+in which we produced heterogeneous clusters of the noble gases Ar 
+and Xe with different sizes, and compositions ranging from a few 
+Xe dopant atoms in an Ar matrix to clusters containing an equal 
+amount of both species. By the use of electron, electron 
+coincidence spectroscopy and of {\it ab initio} calculations on 
+prototypical systems we show how the radiationless decay spectrum 
+of Ar inner valence (3s) ionized states connects to the structure 
+of the clusters.
 
-Intermolecular Coulombic Decay initially was predicted from theoretical considerations of the energy levels in singly vs.
-doubly ionized, and doubly vs.
-triply ionized, hydrogen bonded clusters.\cite{cederbaum} First experimental work some years later used Ne clusters,\cite{marburger,jahnkenedimer} but quickly was followed by demonstrations of ICD in a diverse range of other systems.
-Experimental and theoretical progress has been reviewed.\cite{hergenhahn_review, averbukh_review, jahnke_review} ICD proceeds by an initial ionization producing an ion in an excited state, followed by a transfer of energy to a neighbouring site, and an electron emission process therefrom.
-In the final state a positive charge remains at the site of ionization, and another was created at another atom or molecule.
-Soon after, related autoionization processes were discovered that proceed via a charge transfer instead of an energy transfer.
-%These were termed `Electron Transfer Mediated Decay' (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in which the originally excited site is neutralized by the decay, and 'exchange ICD' for charge transfer contributions to the normal ICD amplitude.\cite{santrarev,jahnkesat}
-We find that both energy and charge transfer induced autoionization plays a role in Ar-Xe, and will detail the relevant processes below.
-The notion of ICD requires that the electronic orbitals of the two sites can be distinguished, which typically is the case in weakly bonded systems, held together by hydrogen bonds or van-der-Waals bonds.
-In the case of strong (covalent or metallic) bonding, there is no distinction between ICD and Auger decay.\cite{hergenhahn_review}
+Intermolecular Coulombic Decay initially was predicted from 
+theoretical considerations of the energy levels in singly vs. 
+doubly ionized, and doubly vs. triply ionized, hydrogen bonded 
+clusters.\cite{cederbaum} First experimental work some years 
+later used Ne clusters,\cite{marburger,jahnkenedimer} but quickly 
+was followed by demonstrations of ICD in a diverse range of other 
+systems. Experimental and theoretical progress has been reviewed.
+\cite{hergenhahn_review, averbukh_review, jahnke_review} ICD 
+proceeds by an initial ionization producing an ion in an excited 
+state, followed by a transfer of energy to a neighbouring site, 
+and an electron emission process therefrom. In the final state a 
+positive charge remains at the site of ionization, and another 
+was created at another atom or molecule. Soon after, related 
+autoionization processes were discovered that proceed via a 
+charge transfer instead of an energy transfer. 
+%These were termed `Electron Transfer Mediated Decay' 
+% (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
+% which the originally excited site is neutralized by the decay, 
+% and 'exchange ICD' for charge transfer contributions to the 
+% normal ICD amplitude.\cite{santrarev,jahnkesat}
+We find that both energy and charge transfer induced 
+autoionization plays a role in Ar-Xe, and will detail the 
+relevant processes below. The notion of ICD requires that the 
+electronic orbitals of the two sites can be distinguished, which 
+typically is the case in weakly bonded systems, held together by 
+hydrogen bonds or van-der-Waals bonds. In the case of strong (
+covalent or metallic) bonding, there is no distinction between 
+ICD and Auger decay.\cite{hergenhahn_review}
 
-First experiments on ICD in heterogeneous systems were on Ne-Ar clusters.\cite{barthnear} Those were followed by studies of ICD-like inner-shell decays in aqueous solution.\cite{aziz,pokapanich,pokapanich2011} Pioneering work also showed the potential for studies of the interface between a substrate and an adsorbate by ICD.\cite{grieves} More detailed work on Ne-Ar clusters was recently presented by some of the authors.\cite{fasshauer2014} For this system, a detailed analysis of photoelectron spectra with respect to structural features of the mixed clusters is also available.\cite{lundwall} In Ref.
-\citenum{fasshauer2014} it was shown that an analysis of the ICD spectra allowed to decide between structural alternatives for which the photoelectron data were indiscriminate.
+First experiments on ICD in heterogeneous systems were on Ne-Ar 
+clusters.\cite{barthnear} Those were followed by studies of ICD-
+like inner-shell decays in aqueous solution.\cite{
+aziz,pokapanich,pokapanich2011} Pioneering work also showed the 
+potential for studies of the interface between a substrate and an 
+adsorbate by ICD.\cite{grieves} More detailed work on Ne-Ar 
+clusters was recently presented by some of the authors.\cite{
+fasshauer2014} For this system, a detailed analysis of 
+photoelectron spectra with respect to structural features of the 
+mixed clusters is also available.\cite{lundwall} In Ref. \citenum{
+fasshauer2014} it was shown that an analysis of the ICD spectra 
+allowed to decide between structural alternatives for which the 
+photoelectron data were indiscriminate.
 
-Rare gas clusters are suitable prototype systems for studies of (e.g.) ICD, as they can easily be produced by supersonic expansion.
-Mixed rare gas clusters easily form by coexpansion of the two gases through a cooled nozzle.
-The size of the clusters can be changed by varying the expansion parameters, although for heterogeneous clusters some uncertainty remains with respect to the cluster size, as empirical scaling laws \cite{hagena1981} apply to expansion of pure gases only.
-Early studies of Ar-Xe clusters mostly focussed on the extreme cases of a single Xe atom embedded in an Ar cluster (e.g.
-Ref.
-\citenum{lengenprl}).
-Different sites of the dopant atom (on top of a surface, integrated in an Ar surface, inside the cluster) were distinguished by three separate bands in the fluorescence yield recorded as a function of excitation wavelength.\cite{lengenprl} Increasing the Xe concentration in the expansion lead to changes in the fluorescence excitation spectrum that were interpreted as formation of \ce{Xe2} and larger Xe complexes inside the clusters.\cite{lengen} Experiments on Xe-rich mixed clusters were also conducted, and concluded that increasing the Xe content in a coexpanding ArXe mixture leads to the formation of Xe-core, Ar-shell systems with a sharp interface between the two species.\cite{tchaplyguine,hoener} This finding was confirmed by electron diffraction experiments.\cite{Danylchenko} Always, the observed Xe content in the clusters is above the Xe content in the expanding gas mixture, as Xe can be condensed much easier than Ar.
+Rare gas clusters are suitable prototype systems for studies of (
+e.g.) ICD, as they can easily be produced by supersonic 
+expansion. Mixed rare gas clusters easily form by coexpansion of 
+the two gases through a cooled nozzle. The size of the clusters 
+can be changed by varying the expansion parameters, although for 
+heterogeneous clusters some uncertainty remains with respect to 
+the cluster size, as empirical scaling laws \cite{hagena1981} 
+apply to expansion of pure gases only. Early studies of Ar-Xe 
+clusters mostly focussed on the extreme cases of a single Xe atom 
+embedded in an Ar cluster (e.g. Ref. \citenum{lengenprl}). 
+Different sites of the dopant atom (on top of a surface, 
+integrated in an Ar surface, inside the cluster) were 
+distinguished by three separate bands in the fluorescence yield 
+recorded as a function of excitation wavelength.\cite{lengenprl} 
+Increasing the Xe concentration in the expansion lead to changes 
+in the fluorescence excitation spectrum that were interpreted as 
+formation of \ce{Xe2} and larger Xe complexes inside the clusters.
+\cite{lengen} Experiments on Xe-rich mixed clusters were also 
+conducted, and concluded that increasing the Xe content in a 
+coexpanding ArXe mixture leads to the formation of Xe-core, Ar-
+shell systems with a sharp interface between the two species.\cite
+{tchaplyguine,hoener} This finding was confirmed by electron 
+diffraction experiments.\cite{Danylchenko} Always, the observed 
+Xe content in the clusters is above the Xe content in the 
+expanding gas mixture, as Xe can be condensed much easier than Ar.
 
-Most recently, on the experimental side photoelectron spectra of small Ar-Xe clusters were analyzed, adding to the findings in earlier work.\cite{Lindblad} We will discuss this paper in connection with our results below.
-Theoretical work on Ar-Xe was also published, and had a focus on the radiationless decay of Ar inner valence vacancies in these systems.\cite{fasshauer,fasshauer_b} Interestingly, it was found that Ar 3s$^{-1}$ is stable against autoionization in an ArXe dimer, but is destabilized by adding further Xe atoms, or an Ar solvation shell, to the system.
-Again, we will detail these results in conjunction with our current work.
+Most recently, on the experimental side photoelectron spectra of 
+small Ar-Xe clusters were analyzed, adding to the findings in 
+earlier work.\cite{Lindblad} We will discuss this paper in 
+connection with our results below. Theoretical work on Ar-Xe was 
+also published, and had a focus on the radiationless decay of Ar 
+inner valence vacancies in these systems.\cite{fasshauer,fasshauer
+_b} Interestingly, it was found that Ar 3s$^{-1}$ is stable 
+against autoionization in an ArXe dimer, but is destabilized by 
+adding further Xe atoms, or an Ar solvation shell, to the system. 
+Again, we will detail these results in conjunction with our 
+current work.
 

### 2015-03-13 theory.tex
add more theory text

@@
 
-In case of the electronic decay processes one is interested in the
-energies of the initial $E_{in}$ and the final states $E_{fin}$ of
-the corresponding processes in order to determine, whether a channel $\beta$
-is open, i.e., in accordance with energy conservation, or not. When the channel
+In order to determine, whether a channel $\beta$ for a given geometry and decay
+mechanism is open ,i.e., in accordance with energy conservation,
+the energies of the initial $E_{in}$ and the final states $E_{fin}$ of
+the corresponding processes are necessary.
+When the channel
 is open, the excess energy is carried away by the emitted electron $E_{sec}$
@@
 \begin{align}
- E_{in}^\beta  &= SIP(X_{in}^\beta) \label{equation:E_in}\\
- E_{fin}^\beta &= SIP(X_{fin1}^\beta) + SIP(X_{fin2}^\beta) + \frac 1d
+ E_{in}        &= SIP(X_{in}) \label{equation:E_in}\\
+ E_{fin}^\beta &= SIP(X_{D}^\beta) + SIP(X_{E}^\beta) + \frac 1d
            \label{equation:E_fin}\\
@@
 where $X_{in}$ denotes the initially ionized atom and
-$X_{fin1}$ and $X_{fin2}$ describe the two ionized
-atoms in the final state. $\beta$ denotes the decay channel characterized
+$X_{D}$ and $X_{E}$ describe the electron donating atom and electron
+emitting atom, respectively.
+$\beta$ denotes the decay channel characterized
 by the quantum numbers of the ionized atoms in the pairs
 and triples and $d$ denotes the interatomic distance between the atoms
-$X_{fin1}$ and $X_{fin2}$. The initially ionized atom $X_{in}$ can
+$X_{D}$ and $X_{E}$. The initially ionized atom $X_{in}$ can
 coincide with one or both of
 the final state atoms
-$X_{fin1}$ and $X_{fin2}$. As explained in
-chapter \ref{chapter:autoionization}, the distribution
-of the vacancies over the different
+$X_{D}$ and $X_{E}$.
+The distribution of the vacancies over the different
 atoms determines the kind of electronic decay process at hand. Hence, in an
 Auger process all three atoms would coincide, for an ICD $X_{in}$
-would coincide with one of $X_{fin1}$ and $X_{fin2}$ and for an {ETMD}3
+would coincide with one of $X_{D}$ and $X_{E}$ and for an {ETMD}3
 all ionized states are located on different atoms.
@@
 This ad hoc approach easily allows to correct for energetic shifts of         
-ionization potentials as observed in larger clusters.
+ionization potentials as observed in larger clusters by adding experimentally
+or theoretically determined energy shifts $\Delta E(X_{A}^{\beta})$
+for a given role in the decay
+$A=in,D,E$ and a channel $\beta$ which yields
+the working expression for the kinetic energy of the secondary electron
+
+\begin{equation}
+ E_{sec}^\beta = SIP(X_{in}) + \Delta E (X_{in})
+               - SIP(X_{D}^\beta) - \Delta E (X_{D}^\beta)
+               - SIP(X_{E}^\beta) - \Delta E (X_{E}^\beta)
+               - \frac 1d .
+\end{equation}
+
+The total decay width $\Gamma$ is given by the sum over the decay widths
+of all decay mechanisms. In case of the ArXe clusters we only consider
+ICD and ETMD:
+
+\begin{equation}
+ \Gamma = \Gamma_{ICD} + \Gamma_{ETMD} .
+\end{equation}
+
+These are given by the sum over the decay widths of all pairs $i$ for the
+ICD and all triples $j$ for the ETMD3, respectively and all channels $\beta$.
 
 \begin{align}
- \Gamma_{ICD}  &= \sum\limits_{i,\beta} N_{ICD,i}  \Gamma_{ICD,i,\beta}\\
- \Gamma_{ETMD} &= \sum\limits_{j,\beta} N_{ETMD,j} \Gamma_{ETMD,j,\beta}\\
+ \Gamma_{ICD}  &= \sum\limits_{i,\beta} N_{ICD,i}  \, \Gamma_{ICD,i,\beta}\\
+ \Gamma_{ETMD} &= \sum\limits_{j,\beta} N_{ETMD,j} \, \Gamma_{ETMD,j,\beta}\\
 \end{align}
+Here, $N_{ICD,i}$ and $N_{ETMD,j}$ denote the number of geometrically
+equal pairs and triples in a given cluster structure. The total number of pairs
+reads
+$N_{ICD} = N_{in} \cdot N_{D/E} = N_{Ar} \cdot N_{Xe}
+ = \sum\limits_i N_{ICD,i}$ and the number of triples as
+$N_{ETMD} = N_{in} \cdot N_{D/E} (N_{D/E} - 1) = N_{Ar} \cdot N_{Xe} (N_{Xe} - 1)
+ = \sum\limits_j N_{ETMD,j}$.
+The number of geometrically equal pairs $N_{ICD,i}$ and $N_{ETMD,j}$
+strongly depend on the structure of the cluster. From these relationships
+it can be seen that a higher xenon content in the cluster statistically
+favours the ETMD3 over the ICD.
 
-$N_{ICD} = N_{in} \cdot N_{fin} = N_{Ar} \cdot N_{Xe}
- = \sum\limits_i N_{ICD,i}$
-$N_{ETMD} = N_{in} \cdot N_{fin} (N_{fin} - 1) = N_{Ar} \cdot N_{Xe} (N_{Xe} - 1)
- = \sum\limits_j N_{ETMD,j}$
-
-$N_{ICD,i}$ and $N_{ETMD,j}$ depend on the structure
+In previous work \cite{Fasshauer13,Fasshauer_PhD} we have shown that
+the decay width for a single pair or triple for a distinct channel $\beta$
+following Wentzel \cite{Wentzel27} Feshbach\cite{Feshbach58,Feshbach62}
+and Fano \cite{Fano61}
 
@@
 \end{equation}
+
+can be approximated by its asymptotic behaviour
 
@@
  \Gamma_{ETMD,j,\beta} = 2\pi \sum\limits_{m,M_{in}',D}
-                        \frac{a_m \Theta_m(\alpha_i) \sigma^{(X_E)}(\omega_{vp,\beta})
+                        \frac{a_m \Theta_m(\alpha_j) \sigma^{(X_E)}(\omega_{vp,\beta})
                               \tilde{D}_{m,j,\beta}(M_{in,D},M_{in,D'})}
@@
 
-\begin{equation}
-\end{equation}
-
-\begin{equation}
-\end{equation}
-
-\begin{equation}
-\end{equation}
-
-\begin{equation}
-\end{equation}
-
-\begin{equation}
-\end{equation}
-
-\begin{equation}
-\end{equation}
+depending on constants ($a_m=4,2$) as well as experimental properties
+of atoms like ionization cross sections
+$\sigma^{(X_E)}(\omega_{vp,\beta})$, radiative lifetimes of the initially
+ionized state $\tau_{in,\beta}$ and the excess energy transferred to the
+emitting atom (the energy of the virtual photon) $\omega_{vp,\beta}$
+and calculated dipole transition moments $\tilde{D}_{m,j,\beta}$, only.
+Here, $\Theta_m(\alpha_j)$ is a function depending on the angle $\alpha_j$
+of the triple (compare Ref. \cite{Fasshauer13}).

### 2015-03-13 theo_results.tex
add table with theoretical Gammas for all cluster structures and their properties

\section{Theoretical Results}

\begin{table}
\centering
\caption{.}
\begin{tabular}{lrrrccc}
\toprule
name                 & Xe atoms & Ar atoms & Xe \% &   ICD                &  ETMD                & $\Gamma_{ICD,ETMD}$\\
\midrule
ArXe\_2\_1atom       &      1   &     12   &  7.7  &      0.0             &  0.0                 &     0.0            \\
ArXe\_3\_1atom       &      1   &     54   &  1.8  &      0.0             &  0.0                 &     0.0            \\ 
ArXe\_3\_2atom       &      2   &     53   &  3.6  & 3.346$\cdot 10^{-6}$ & 1.666$\cdot 10^{-5}$ & 2.006$\cdot 10^{-5}$ \\
ArXe\_8\_1layer      &   1415   &    642   & 68.8  & 7.039$\cdot 10^{-4}$ & 2.573$\cdot 10^{-4}$ & 9.612$\cdot 10^{-4}$ \\
XeAr\_2\_surface     &      1   &     13   &  7.1  & 7.922$\cdot 10^{-5}$ & 0.0                  & 7.922$\cdot 10^{-5}$ \\
XeAr\_2\_edge        &      1   &     13   &  7.1  & 1.320$\cdot 10^{-6}$ & 0.0                  & 1.320$\cdot 10^{-6}$ \\
XeAr\_2\_vertex      &      1   &     13   &  7.1  & 5.013$\cdot 10^{-6}$ & 0.0                  & 5.013$\cdot 10^{-6}$ \\
XeAr\_2\_2top        &      2   &     13   & 13.3  & 1.011$\cdot 10^{-5}$ & 1.513$\cdot 10^{-5}$ & 2.523$\cdot 10^{-5}$ \\
XeAr\_3\_surface     &      1   &     55   &  1.8  & 6.371$\cdot 10^{-6}$ & 0.0                  & 6.371$\cdot 10^{-6}$ \\
XeAr\_3\_edge        &      1   &     55   &  1.8  & 4.791$\cdot 10^{-6}$ & 0.0                  & 4.791$\cdot 10^{-6}$ \\
XeAr\_3\_vertex      &      1   &     55   &  1.8  & 2.701$\cdot 10^{-6}$ & 0.0                  & 2.701$\cdot 10^{-6}$ \\
XeAr\_3\_edge\_in    &      1   &     54   &  1.8  & 7.708$\cdot 10^{-6}$ & 0.0                  & 7.708$\cdot 10^{-6}$ \\
XeAr\_3\_vertex\_in  &      1   &     54   &  1.8  & 5.258$\cdot 10^{-6}$ & 0.0                  & 5.258$\cdot 10^{-6}$ \\
XeAr\_3\_2in         &      2   &     53   &  3.6  & 1.166$\cdot 10^{-5}$ & 5.453$\cdot 10^{-6}$ & 1.711$\cdot 10^{-5}$ \\
XeAr\_3\_6in         &      6   &     49   & 10.9  & 3.746$\cdot 10^{-5}$ & 4.050$\cdot 10^{-5}$ & 7.796$\cdot 10^{-5}$ \\
XeAr\_3\_6\_scat     &      6   &     49   & 10.9  & 2.923$\cdot 10^{-5}$ & 6.737$\cdot 10^{-5}$ & 9.660$\cdot 10^{-5}$ \\
\bottomrule
\end{tabular}
\label{table:theo_gammas}
\end{table}

### 2015-03-13 exp_results.tex

\section{Experimental Results}
\begin{table}
\caption{
Expansion parameters used in this work for cluster production. All clusters were produced with a $d = 80~\mu$m conical nozzle of 15$^\circ$ half opening angle. For the mixed clusters, $\langle N_{Ar} \rangle$ and $\langle N_{Xe} \rangle$ refer to hypothetical cluster sizes yielded with an expansion of the respective pure gas at the conditions given. These values are calculated as in ref.\ \protect\citenum{hagena1981}. Due to the small amount of Xe admixture, we basically have a Xe seeded expansion of Ar gas. We therefore expect actual cluster sizes in-between the two limiting values given. Inaccuracies in the calculation of $\langle N\rangle$ due to fluctuations of the input parameters are less than 6\,\%. This figure does not include systematic errors of the empirical model used.
\label{tab:cluster} }

\begin{ruledtabular}
\begin{tabular}{l c c c r r}
%
  label  &  Xe$_{in}$ [\%]  &  $T$ [K]  &  $p$ [bar] & $\langle N_{Ar} \rangle$ & $\langle N_{Xe} \rangle$ \\
%
\hline
% Ar, from Marko 
Ar (1)  & --- &  96.5  & 0.35  &  42  &  --- \\
% Ar, from Marko 
Ar (2)  & --- &  96.5  & 0.67  & 190  &  --- \\
% 1103 676, 679
 (a) & 1.2 &  174   & 0.32  &   4  &   62 \\
% 1103 670
 (b) & 1.2 &  174   & 0.49  &  10  &  168 \\
% 1103 671
 (c) & 1.2 &  174   & 0.68  &  21  &  362 \\
% 1103 663
 (d) & 3.0 &  172   & 0.28  &   3  &   48 \\
% 1103 640
 (e) & 5.0 &  171   & 0.51  &  12  &  202 \\
% 0506 382, Keller offset berücksichtigt
Xe (1)  & 100 & 183.5  & 0.68  & ---  &  517 \\     
\hline
% 1103 653
1103, only coinc  & 3.0 &  172   & 0.51  &  11  &  196 \\
% 1103 658
  & 3.0 &  172   & 0.68  &  22  &  385 \\
% 1103 630
  & 5.0 &  167   & 0.37  &   6  &  108 \\
% 1103 629
  & 5.0 &  167   & 0.68  &  26  &  451 \\
\hline
% 1004 842
1004  & 3.0 &  165   & 2.8   & 1220 & 20900\\
% 1004 858
  & 5.0 &  149   & 2.5   & 1620 & 27700\\
%
\end{tabular}
\end{ruledtabular}
\end{table}

\begin{table}
\caption{Properties of the outer valence spectra of mixed ArXe clusters. Spectra of pure Ar and Xe clusters are included for reference. All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV). Binding energies $E_b$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit. The experimental Xe content of the clusters always is higher than in the original gas mixture (see Tab.\ \protect\ref{tab:cluster}). It was determined from the areas of the respective photolines, corrected by the respective atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}. Uncertainty are estimated as 3\,\% for the Xe content and 0.05~eV for the binding energies. Labels given in the first column refer to the expansion parameters in Tab.\ \protect\ref{tab:cluster}. $E_b$ and $w$ are in eV, $A$ is in \%. The binding energies can be compared to atomic values of 15.82~eV, 13.43~eV and 12.13~eV for Ar 3p and Xe 5p.
\label{tab:valence} }
\begin{ruledtabular}
\begin{tabular}{ l c c c c c c}
%
  label & $E_b$(Ar 3p) & $w$(Ar 3p) & $E_b$(Xe 5p$_{1/2}$) &  $E_b$(Xe 5p$_{3/2}$) & $w$(Xe 5p$_{3/2}$)  &  $A$(Xe) \\
%
\hline
% Ar, from Marko
 Ar (1) &  15.3  &  1.1 & & & &  \\
% Ar, from Marko 
 Ar (2) &  15.1  &  1.3 & & & &  \\
%
%  columns in the following: energies c.g. 51-plt-oval, widths Marko Diss., Xe content Marko Diss
% 1103 676, 679
 (a) & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
% 1103 670
 (b) & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
% 1103 671
 (c) & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
% 1103 663
 (d) & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
% 1103 640
 (e) & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
% 0506 
Xe (1) & & & 12.76 & 11.19 & 1.18 & 100\\
%
\end{tabular}
\end{ruledtabular}
\end{table}

### 2015-03-17 theo_results.tex
add latest cluster structures

@@
 ArXe\_8\_1layer      &   1415   &    642   & 68.8  & 7.039$\cdot 10^{-4}$ & 2.573$\cdot 10^{-4}$ & 9.612$\cdot 10^{-4}$ \\
+\midrule
 XeAr\_2\_surface     &      1   &     13   &  7.1  & 7.922$\cdot 10^{-5}$ & 0.0                  & 7.922$\cdot 10^{-5}$ \\
@@
 XeAr\_2\_2top        &      2   &     13   & 13.3  & 1.011$\cdot 10^{-5}$ & 1.513$\cdot 10^{-5}$ & 2.523$\cdot 10^{-5}$ \\
+XeAr\_2\_2midtop     &      2   &     13   & 13.3  & 1.588$\cdot 10^{-5}$ & 7.686$\cdot 10^{-7}$ & 1.665$\cdot 10^{-5}$ \\
+XeAr\_2\_2endtop     &      2   &     13   & 13.3  & 1.587$\cdot 10^{-5}$ & 1.772$\cdot 10^{-7}$ & 1.605$\cdot 10^{-5}$ \\
 XeAr\_3\_surface     &      1   &     55   &  1.8  & 6.371$\cdot 10^{-6}$ & 0.0                  & 6.371$\cdot 10^{-6}$ \\

### 2015-03-18 pics/replace.py
vereinheitliche Bereich der Spektren

@@ -16,7 +16,7 @@ count = 0
 rootdir = os.getcwd()
 #outfile = open('','w')
 
-for filename in glob.glob("*8*.tex"):
+for filename in glob.glob("xe_3_in.tex"):
    print filename
    infile = open(filename, 'r')
    outfile = open('tmpfile', 'w')

### 2015-03-18 theo_results.tex
add caption to figures

@@
 \end{table}
+
+\begin{figure}[h]
+ \centering
+ \includegraphics[scale=0.7]{pics/surf.pdf}\\
+ \includegraphics[scale=0.7]{pics/R_comp.pdf}
+ \caption{Panel 1: Simulated electron-electron coincidence spectra
+          for argon clusters
+          consisting of 13 and 55 atoms with on additional xenon atom residing
+          on top of one of the argon surfaces.\\
+          Panel 2: Distribution of Ar-Xe distances $d$ in the studied ArXe
+          clusters. The ICD channels open at \unit[7.58]{\AA} and
+          \unit[36.00]{\AA}, respectively. Hence only pairs at longer interatomic
+          distances than the gray line contribute to the coincidence spectra.
+          The distance distribution of the larger cluster contains larger
+          distances which correspond to peaks at higher kinetic energies of
+          the ICD electron in the coincidence spectra (Panel 1).}
+ \label{figure:surf}
+\end{figure}
+
+\begin{figure}[h]
+ \centering
+ \includegraphics[scale=0.7]{pics/2tops.pdf}
+ \caption{Simulated coincidence spectra of argon clusters consisting of 13
+          argon atoms with 2 additional xenon atoms on top of two different
+          argon surfaces. The ICD and ETMD spectra are shown for all three
+          different relative positionings of the two xenon atoms. In case of
+          the two xenon atoms being close to each other, an ETMD process is
+          clearly visible. In the other two cases the spectra are dominated by
+          the corresponding ICD spectrum.}
+ \label{figure:2tops}
+\end{figure}
+
+\begin{figure}[h]
+ \centering
+ \includegraphics[scale=0.7]{pics/ar_3_6in.pdf}
+ \caption{Simulated ICD and ETMD electron spectra for clusters consisting of
+          55 atoms out of which 6 are xenon atoms. These are either clustered
+          (group) on one side of the cluster of evenly distributed
+          inside the cluster (scattered). In both cases the ETMD peaks are
+          clearly visible in the spectra.}
+ \label{figure:ar_3_6in}
+\end{figure}
+
+\begin{figure}[h]
+ \centering
+ \includegraphics[scale=0.7]{pics/xe_3_in.pdf}
+ \caption{Simulated ICD and ETMD electron spectra for argon clusters with
+          one or two atoms in the core of the cluster. In case of the xenon
+          atom inhabiting the central position of the cluster for a 13 atoms
+          cluster (not shown here) and a 55 atoms cluster all channels are closed
+          for all pairs, which leads to no signal. For those clusters with two
+          xenon atoms in the core the first ICD channel is open for some pairs
+          and additionally ETMD is possible for multiple triples. Due to a
+          different distance distribution compared to the clusters with an argon
+          core the ICD peak is shifted to higher kinetic energies.}
+ \label{figure:xe_3_in}
+\end{figure}
+
+\begin{figure}[h]
+ \centering
+ \includegraphics[scale=0.7]{pics/xe_8_1lay.pdf}
+ \caption{Simulated ICD and ETMD electron spectra for a large cluster consisting
+          of a xenon core of 1415 atoms surrounded by two complete layers of
+          argon atoms. The ICD and ETMD peak overlap such, that the peak structure
+          might not be visible.}
+ \label{figure:xe_8_lay1}
+\end{figure}

### 2015-03-18 theory.tex
add channel pic

@@
 
+\begin{figure}[h]
+ \centering
+ \includegraphics[scale=0.7]{pics/channel_open_ICD.pdf}
+ \caption{Initial and final state energies for ArXe pairs at different
+          distances using the experimental ionization potentials as given
+          in Table \ref{}. For distances larger than the channel opening
+          distance the ICD channel is open.}
+ \label{figure:channel_open_ICD}
+\end{figure}
+
 In all autoionization processes considered, a second electron
@@
 process is energetically not accessible. Hence, the corresponding channel     
-is closed.
+is closed as shown in Figure \ref{figure:channel_open_ICD}.
 

### 2015-03-18 exp_results.tex
ruledtabular raus
1004 values added, changed

@@
 \caption{
-Expansion parameters used in this work for cluster production.
-All clusters were produced with a $d = 80~\mu$m conical nozzle of 15$^\circ$ half opening angle.
+Expansion parameters used for cluster production in this work.
+All experiments were done with a $d = 80~\mu$m conical nozzle of 15$^\circ$ half opening angle.
 For the mixed clusters, $\langle N_{Ar} \rangle$ and $\langle N_{Xe} \rangle$ refer to hypothetical cluster sizes yielded with an expansion of the respective pure gas at the conditions given.
@@
 
-\begin{ruledtabular}
 \begin{tabular}{l c c c r r}
 %
+\toprule
   label  &  Xe$_{in}$ [\%]  &  $T$ [K]  &  $p$ [bar] & $\langle N_{Ar} \rangle$ & $\langle N_{Xe} \rangle$ \\
 %
-\hline
+\midrule
 % Ar, from Marko 
@@
  (e) & 5.0 &  171   & 0.51  &  12  &  202 \\
-% 0506 382, Keller offset berücksichtigt
+% 0506 382, Keller offset ber?cksichtigt
 Xe (1)  & 100 & 183.5  & 0.68  & ---  &  517 \\     
-\hline
+\midrule
 % 1103 653
@@
   & 5.0 &  167   & 0.68  &  26  &  451 \\
-\hline
-% 1004 842
-1004  & 3.0 &  165   & 2.8   & 1220 & 20900\\
+\midrule
 % 1004 858
-  & 5.0 &  149   & 2.5   & 1620 & 27700\\
+858  & 5.0 &  149   & 2.50  & 1620 & 27700\\
+% 1004 867
+867  & 2.5 &  154   & 2.12  &  920 & 15760\\
+% 1004 868
+868  & 2.5 &  158   & 1.50  &  355 &  6090\\
+% 1004 886
+886  & 2.5 &  161   & 2.41  &  980 & 16770\\
 %
+\bottomrule
 \end{tabular}
-\end{ruledtabular}
 \end{table}
@@
 \label{tab:valence} }
-\begin{ruledtabular}
 \begin{tabular}{ l c c c c c c}
 %
+\toprule
   label & $E_b$(Ar 3p) & $w$(Ar 3p) & $E_b$(Xe 5p$_{1/2}$) &  $E_b$(Xe 5p$_{3/2}$) & $w$(Xe 5p$_{3/2}$)  &  $A$(Xe) \\
 %
-\hline
+\midrule
 % Ar, from Marko
@@
 %
+\midrule
+%
+%  1004  886  (UHe, c.g. + roi values)
+ 556 & 15.12 & 1.3 & 12.44 & 10.70 & 1.24 & 19\\
+\bottomrule
 \end{tabular}
-\end{ruledtabular}
 \end{table}

### 2015-03-18 exp_results.tex
more work on the cluster tables

@@
 Expansion parameters used for cluster production in this work.
-All experiments were done with a $d = 80~\mu$m conical nozzle of 15$^\circ$ half opening angle.
+Experiments were done with $d = 80~\mu$m (first two sections) and $d = 100~\mu$m (bottom section) conical nozzles of 15$^\circ$ half opening angle.
 For the mixed clusters, $\langle N_{Ar} \rangle$ and $\langle N_{Xe} \rangle$ refer to hypothetical cluster sizes yielded with an expansion of the respective pure gas at the conditions given.
@@
 \midrule
-% 1004 858
-858  & 5.0 &  149   & 2.50  & 1620 & 27700\\
 % 1004 867
-867  & 2.5 &  154   & 2.12  &  920 & 15760\\
+1004, 867  & 2.5 &  154   & 2.12  &  920 & 15760\\
 % 1004 868
@@
 886  & 2.5 &  161   & 2.41  &  980 & 16770\\
+% 1004 858
+858  & 5.0 &  149   & 2.50  & 1620 & 27700\\
 %
@@
 It was determined from the areas of the respective photolines, corrected by the respective atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}.
-Uncertainty are estimated as 3\,\% for the Xe content and 0.05~eV for the binding energies.
+Uncertainties are estimated as 3\,\% for the Xe content and 0.05~eV for the binding energies.
 Labels given in the first column refer to the expansion parameters in Tab.\ \protect\ref{tab:cluster}.
@@
 %  1004  886  (UHe, c.g. + roi values)
- 556 & 15.12 & 1.3 & 12.44 & 10.70 & 1.24 & 19\\
+ 886 & 15.12 & 1.3 & 12.44 & 10.70 & 1.24 & 19\\
 \bottomrule

### 2015-03-18 structures.tex
width of figures

\section{Cluster Structures}

\begin{figure}[h]
 \centering
 \includegraphics[width=8.5cm]{pics/cluster_2_overview.pdf}
 \caption{Cluster structures with 13 argon atoms and two additional xenon
          atoms on different surfaces of the argon icosahedron:
          \textbf{a)} closest possible \textbf{b)} middle \textbf{c)}
          furthest away.}
 \label{figure:cluster_2_overview}
\end{figure}

\begin{figure}[h]
 \centering
 \includegraphics[width=8.5cm]{pics/cluster_3_overview.pdf}
 \caption{Cluster structures based on 55 atoms icosahedral cluster structure.
          \textbf{a)} 1 xenon atom on the surface of a 55 atoms icosahedral
          argon cluster. \textbf{b)} six xenon atoms inside a 55 atoms cluster
          grouped on one side. \textbf{c)} six xenon atoms distributed
          in a 55 atoms cluster. }
 \label{figure:cluster_3_overview}
\end{figure}

### 2015-03-19 structures.tex
add description of cluster structures

@@
 \section{Cluster Structures}
+
+From the experimental results we can obtain two hints for the cluster
+structure: the minimum size and the xenon content. We will in the following
+use these to construct possible cluster structures for which we will later
+simulate the ICD and ETMD spectra. At this step we put in whatever structure
+we might think of and hope to be able to exclude some of them by comparison of
+the ICD and ETMD spectra to the experimental electron-electron coincidence
+spectra.
+
+The expected mean argon cluster sizes can be
+estimated were estiamted and collected in Table \ref{table:}.
+In case of the smaller clusters measured
+these expectation values range from \unit[3 -- 21]{Ar atoms} for
+expansion of pure argon. The cluster sizes of a mixed gas are unknown but
+for xenon as the second component the cluster sizes can be expected to
+be larger than those of pure argon due to the higher polarizability
+and hence xyz of xenon. All clusters contributing to the coincidence spectrum
+do contain at least one xenon atom, otherwise there would be no signal at all.
+In an expansion a large variance of clusters and with different structures
+is produced. However, for small clusters consisting of less than
+approximately \unit[1000]{atoms} so-called \emph{islands of stability} were
+found for clusters with icosahedral shape. This means, that the probability
+to find and measure such a cluster is higher than a different structure.
+We therefore start from an icosahedral structures and substitute atoms
+in the clusters by
+argon / xenon atoms or add these to a given structure close to the wanted
+position. Afterwards the cluster structures were optimized using the
+UFF force field \cite{} implemented in
+Avogadro \cite{} for a structure optimization.
 
@@
 \end{figure}
+
+As discussed  in section \ref{}, the small clusters are very likely
+to deviate from a core-shell structure with a xenon core surrounded
+by argon shells as observed for large clusters. We therefore start from
+argon clusters of 13 or 55 atoms and modify them in one of the following
+ways:
+
+\begin{itemize}
+ \item add one xenon atom on top of a surface / edge / vertex of
+       the argon core as for example shown in
+       Figure \ref{figure:cluster_3_overview} Panel a)
+       for one additional xenon atom
+       on top of surface of a \unit[55]{atoms} argon core
+ \item substitute one argon atom in a surface / edge / vertex position if
+       possible
+ \item substitute one or two argon atoms in the core of the argon cluster
+       by xenon atom(s) for the simulation of the core-shell structure
+ \item add two xenon atoms on top of surfaces of a 13 atoms argon core
+       in different relative positions (see Figure \ref{cluster_2_overview})
+       in order to achieve a xenon content in the cluster close to the
+       measured one shown in Table \ref{}
+ \item substitute six argon atoms of a 55 atoms argon cluster by xenon
+       atoms either grouping them or scattering them througout the cluster
+       (see Figure \ref{cluster_3_overview} Panels b) and c)) in order to
+       achieve a xenon content in the cluster close to the experimental one
+\end{itemize}
+
+Furthermore we constructed a core-shell structure with a core of
+1415 xenon atoms and one additional complete layer of argon atoms for
+comparison with the largest measured ArXe clusters.

### 2015-03-25 intro.tex
take care of utf8 and no linebreak within one specific citation key

@@
 also published, and had a focus on the radiationless decay of Ar 
-inner valence vacancies in these systems.\cite{fasshauer,fasshauer
-_b} Interestingly, it was found that Ar 3s$^{-1}$ is stable 
+inner valence vacancies in these systems.\cite{fasshauer,Fasshauer13}
+Interestingly, it was found that Ar 3s$^{-1}$ is stable 
 against autoionization in an ArXe dimer, but is destabilized by 

### 2015-04-07 pics/front1.tex
front pictures

\begin{tikzpicture}[scale=1.0,>=stealth]
    %\Large
    %\draw [help lines] (0,0) grid (16,15);
% links
    \draw [->,decorate,decoration=snake,diplom2,ultra thick] (0.5,9.2) --
              (2,8.5) node [midway,anchor=south]{$h\nu$};
    \node at (3,8) {\includegraphics[scale=0.10]{nearest_one.png}};
    \draw[->,very thick,diplom3] (4,8.5) -- (5,9.5)
         node [above]{$\color{diplom3}{e^-}$};

    \node at (3,6) {\textbf{Ionization}};

%Mitte
    \draw[->,ultra thick] (4.5,8) -- (6.5,8);
    \node at (8,8) {\includegraphics[scale=0.10]{nearest_two.png}};
    \draw[->,ultra thick,diplom3] (9.5,8) -- (11.5,8)
         node [midway,anchor=south]{$\color{diplom3}{e^-}$};

    \node at (8,6) {\textbf{ICD}};

%unten
% links
    \draw [->,decorate,decoration=snake,diplom2,ultra thick] (0.5,5.2) --
              (2,4.5) node [midway,anchor=south]{$h\nu$};
    \node at (3,4) {\includegraphics[scale=0.110]{next_nearest_one.png}};
    \draw[->,very thick,diplom3] (4,4.5) -- (5,5.5)
         node [above]{$\color{diplom3}{e^-}$};

%Mitte
    \draw[->,ultra thick] (4.5,4) -- (6.5,4);
    \node at (8,4) {\includegraphics[scale=0.11]{next_nearest_two.png}};
    \draw[->,ultra thick,diplom3] (9.5,4) -- (11.5,6.0)
         node [midway,anchor=south,distance=1.5cm]{$\color{diplom3}{e^-}$};

%Rechts
    \node at (14,6) {\includegraphics[scale=0.5,angle=270]{surf3.pdf}};

\end{tikzpicture}

### 2015-04-12 theory.tex
width of figures
work through theory section

@@
 decay width $\Gamma=\frac{\hbar}{\tau}$,
-which is inverse proportional to the lifetime $\tau$. The manifold of these
-energies and decay widths will therefore compose the electron-electron
+which is inverse proportional to the lifetime $\tau$. The manifold of the
+secondary energies and decay widths will therefore compose the electron-electron
 coincidence spectrum.
@@
 
-Decomposing every system into pairs and triples of atoms is a very useful
-first order approximation to both the investigation of energies and
-decay widths of a larger system. Pairs and triples are combinations of
-two and three atoms, respectively.
+This means we are dealing with a sum over three different indices for the
+evaluation of the decay width. For a given structure it is most convenient to
+start with a decomposition of the total system into interaction partners of
+the different decay mechanisms, i.e. pairs (combination of two atoms regardless
+the internuclear distance) for the ICD and triples (combinations of three atoms)
+for the ETMD.
 These atoms do not necessarily need to form bonds between each other or
 even be close, but they are characterized according to fixed internal
-coordinates. Each pair and triple can be described by its properties
+coordinates. Each pair and triple can be described by its properties, like
+energy of the secondary electron and decay width,
 which are in first order of approximation independent of further, eventually
@@
 model of pairs and triples.
+
+%Decomposing every system into pairs and triples of atoms is a very useful
+%first order approximation to both the investigation of energies and
+%decay widths of a larger system. Pairs and triples are combinations of
+%two and three atoms, respectively.
 
@@
 Auger process all three atoms would coincide, for an ICD $X_{in}$
-would coincide with one of $X_{D}$ and $X_{E}$ and for an {ETMD}3
+would coincide with $X_{D}$ and for an {ETMD}3
 all ionized states are located on different atoms.
@@
  \centering
- \includegraphics[scale=0.7]{pics/channel_open_ICD.pdf}
+ \includegraphics[width=8.5cm]{pics/channel_open_ICD.pdf}
  \caption{Initial and final state energies for ArXe pairs at different
@@
 process is energetically not accessible. Hence, the corresponding channel     
-is closed as shown in Figure \ref{figure:channel_open_ICD}.
+is closed as shown in Figure \ref{figure:channel_open_ICD}. Related to
+the opening of each channel is an internuclear distance which we in the
+following call \emph{channel opening distance}.
 
@@
 the decay width for a single pair or triple for a distinct channel $\beta$
-following Wentzel \cite{Wentzel27} Feshbach\cite{Feshbach58,Feshbach62}
+following Wentzel \cite{Wentzel27}, Feshbach\cite{Feshbach58,Feshbach62}
 and Fano \cite{Fano61}
@@
 of the triple (compare Ref. \cite{Fasshauer13}).
+
+In this work we evaluate the secondary energies and decay widths with
+the program HARDRoC \cite{} using the
+experimental ionization energies of Table \ref{}
+and data from the literature given in Tables \ref{} and \ref{}.
+These are the same as the ones used in Reference \cite{Fasshauer13}.

### 2015-05-03 theory.tex
correct ETMD formula and add citations

@@
 
-In previous work \cite{Fasshauer13,Fasshauer_PhD} we have shown that
+In previous work \cite{Fasshauer13,Fasshauer_thesis} we have shown that
 the decay width for a single pair or triple for a distinct channel $\beta$
@@
 \begin{equation}
- \Gamma_{ETMD,j,\beta} = 2\pi \sum\limits_{m,M_{in}',D}
-                        \frac{a_m \Theta_m(\alpha_j) \sigma^{(X_E)}(\omega_{vp,\beta})
+ \Gamma_{ETMD,j,\beta} = \frac{c}{2\pi} \sum\limits_{m,k,M_{in}',D}
+                        \frac{a_{m,k} \Theta_{m,k}(\alpha_j) \sigma^{(X_E)}(\omega_{vp,\beta})
                               \tilde{D}_{m,j,\beta}(M_{in,D},M_{in,D'})}
@@
 
-depending on constants ($a_m=4,2$) as well as experimental properties
+depending on constants ($a_{m,k}=4,2$)
+as well as experimental properties
 of atoms like ionization cross sections
@@
 and calculated dipole transition moments $\tilde{D}_{m,j,\beta}$, only.
-Here, $\Theta_m(\alpha_j)$ is a function depending on the angle $\alpha_j$
-of the triple (compare Ref. \cite{Fasshauer13}).
+Here, $\Theta_{m,k}(\alpha_j)$ is a function depending on the angle $\alpha_j$
+of the triple, the direction of the dipole
+transition moment $m$ and an additional counter $k$
+(compare Ref. \cite{Fasshauer13}).
 
 In this work we evaluate the secondary energies and decay widths with
-the program HARDRoC \cite{} using the
+the program HARDRoC \cite{HARDRoC,fasshauer2014} using the
 experimental ionization energies of Table \ref{}

### 2015-05-03 theo_results.tex
add caption of theo overview table
width of figures
correct labels and refs

@@
 
-\begin{table}
+The geometrical properties as well as the total ICD and ETMD decay widths
+of the investigated structures are shown in Table \ref{table:theo_gammas}.
+It is important to remember that the first ICD channel opens at a
+channel opening distance of \unit[7.58]{\AA}. Therefore, small
+clusters in which none of the possible Ar-Xe pairs in larger than
+these \unit[7.58]{\AA}, no ICD can take place. Also, two xenon atoms are
+required for an ETMD3 and hence the ETMD3 has to be excluded from
+the possible decay mechanism in clusters with only one xenon atom.
+Because secondary electrons are observed in the experimental spectra
+we exclude all structures without any signal from our further
+discussions.
+
+\begin{table}[h]
 \centering
-\caption{.}
+\caption{Properties of simulated clusters.}
 \begin{tabular}{lrrrccc}
@@
 
-\begin{figure}[h]
+In the investigated structures several different aspects have to be
+taken into account which we will discuss separately if possible
+on selected structures.
+
+Firstly, we consider two different argon core sizes one consisting
+of 13 and one consisting of 55 atoms with one xenon atom on one of
+the surfaces (see Figure \ref{figure:cluster_3_overview} Panel a)
+for the 55 atom core). The simulated secondary electron spectra are
+shown in Figure \ref{figure:surf} Panel 1.
+
+\begin{figure}[ht]
  \centering
- \includegraphics[scale=0.7]{pics/surf.pdf}\\
- \includegraphics[scale=0.7]{pics/R_comp.pdf}
+ \includegraphics[width=8.5cm]{pics/surf.pdf}\\
+ \includegraphics[width=8.5cm]{pics/R_comp.pdf}
  \caption{Panel 1: Simulated electron-electron coincidence spectra
@@
 
+Because the structures have only one xenon atom ETMD3 is not possible and
+ICD only is to be expected. Both spectra show several smaller peaks which
+are convoluted into one single peak with a maximum at
+approximately \unit[0.2]{eV}. In comparison to the 13 argon atoms core
+spectrum the 55 argon atoms core spectrum shows
+signals at higher energies of the secondary electron. These features
+can be explained by analysis of the Ar-Xe distances in the clusters shown
+in Figure \ref{figure:surf} Panel 2. Every different atom pair distance
+yields in a different energy of the secondary electron and only pairs
+with a distance of larger than the channel opening distance
+(dashed, gray line) will contribute
+to the spectrum. The larger the interatomic distance is, the higher is the
+kinetic energy of the secondary electron for a given channel.
+Since the 55 argon atom core cluster is larger and therefore
+has Ar-Xe pairs with larger distances its spectrum has signals at higher
+energies as well.
+This effect holds for all clusters.
+
+For clusters with more than one xenon atom the ETMD3 channel is possible
+as well. Depending on the positions of the relative positions of the xenon
+atoms in or on the cluster the spectra are expected to be different.
+As an example we therefore discuss the secondary electron spectra of the
+clusters with an 13 argon atoms core and two xenon atoms on different
+surfaces illustrated in Figure \ref{figure:cluster_2_overview} shown in Figure
+\ref{figure:2tops}. In these the xenon content is \unit[13.3]{\%} and therefore
+close to the experimental ones of \unit[10-12]{\%} for the low xenon pressure.
+
 \begin{figure}[h]
  \centering
- \includegraphics[scale=0.7]{pics/2tops.pdf}
+ \includegraphics[width=8.5cm]{pics/2tops.pdf}
  \caption{Simulated coincidence spectra of argon clusters consisting of 13
@@
 
+In all three cases both ICD and ETMD3 are energetically allowed and the ICD
+spectra are either identical or at least very similar consisting of one
+convoluted peak at approximately \unit[0.2]{eV}. However, the ETMD3 spectra
+are very sensitive to the relative positioning of the two xenon atoms.
+Two aspects have to be taken into account: an energy shift of the peak due
+to different charge distances in the final state (i.e. the interatomic Xe-Xe
+distance) and the different decay widths decreasing with $\frac{1}{R^6}$
+between the electron transfer unit and the finally ionized xenon atom.
+The larger the distance between the xenon atoms is, the lower are the energies
+of the secondary electrons and the higher are the decay widths. Therefore a
+significant contribution from the ETMD3 compared to the ICD is only
+to be seen in case of the two xenon atoms residing on two adjacent
+surfaces. The threefold peak structure of the ETMD3 peak does in contrast to
+the ICD spectrum not stem from different triple structures but from the
+four different decay channels for one triple structure.
+
+For the 55 atoms clusters the xenon content of \unit[10--12]{\%}
+corresponds to six xenon atoms out of the 55 total atoms. These can have
+different relative positions in the cluster. They could either be grouped
+together in one part of the cluster or be evenly distributed in the cluster
+as shown in Figure \ref{figure:cluster_3_overview} Panels b) and c). Their
+ICD and ETMD3 spectra are shown in Figure \ref{figure:ar_3_6in}.
+
 \begin{figure}[h]
  \centering
- \includegraphics[scale=0.7]{pics/ar_3_6in.pdf}
+ \includegraphics[width=8.5cm]{pics/ar_3_6in.pdf}
  \caption{Simulated ICD and ETMD electron spectra for clusters consisting of
@@
 
+For both cases the overall ICD spectra are very similar with concoluted
+peaks at approximately \unit[0.3]{eV}. For the grouped xenon atoms ICD
+signals at slightly higher energies are to be observed from ArXe pairs of
+larger distances du to the different cluster structure. However, the
+significant difference is to be observed in the ETMD3 spectra. The
+interatomic xenon distance in the grouped xenon is shorther than in the
+cluster with evenly distributed xenon atoms. Hence, the threefold
+peak structure for the cluster with the grouped xenon atoms is seen at
+lower ETMD3 electron energies than for the cluster with evenly
+distributed xenon atoms. Additionally, the probabilty for an electron
+transfer from a xenon to an argon atom decreases exponentially with the
+interatomic distance. Therefore, only those xenon atoms which have argon
+atoms as their direct neighbours have a significant contribution to the
+total decay width and the total ETMD3 decay width for the structure with
+the grouped xenon atoms is lower than the total ETMD3 decay width of
+the structure with evenly distributed xenon atoms.
+
+For comparison with the previous assumptions of a xenon core surrounded
+by argon atoms we investigated 13 and 55 atoms clusters with one or two
+xenon atoms in the core. Some of the corresponding
+spectra are shown in Figure \ref{figure:xe_3_in}.
+
 \begin{figure}[h]
  \centering
- \includegraphics[scale=0.7]{pics/xe_3_in.pdf}
+ \includegraphics[width=8.5cm]{pics/xe_3_in.pdf}
  \caption{Simulated ICD and ETMD electron spectra for argon clusters with
@@
 
+For the clusters with only one xenon atom in the core and the ionization
+energies used for the simulation of the secondary electron energies
+all ICD channels are closed. Since the cluster contains only one xenon atom,
+an ETMD3 is not possible. Hence there is no signal to be expected at all.
+For a core consisting of two xenon atoms both an ICD and an ETMD3 spectrum
+can be seen. Compared to the argon core cluster structures the ICD peak is
+shifted to higher ICD electron energies not being in agreement with
+the experimental spectrum. Additionally, the ICD and ETMD3 spectra overlap.
+In case of the ETMD3 only three of the four different decay channels are
+anergetically allowed.
+
+Originally, very large argon-xenon clusters were measured experimentally,
+which we approximate by a cluster consisting of 1415 xenon atoms surrounded
+by two complete layers of argon atoms. The spectra are shown in Figure
+\ref{figure:xe_8_lay1}.
+
 \begin{figure}[h]
  \centering
- \includegraphics[scale=0.7]{pics/xe_8_1lay.pdf}
+ \includegraphics[width=8.5cm]{pics/xe_8_1lay.pdf}
  \caption{Simulated ICD and ETMD electron spectra for a large cluster consisting
@@
 \end{figure}
+
+Compared to the small clusters with a xenon core in Figure \ref{figure:xe_3_in}
+the ICD peak is broadened and shifted to higher ICD electron energies which could be
+expected due to the larger interatomic Ar-Xe distances in the large cluster and
+the better stabilization of charges (the final state), which was taken care of
+in the input of the simulation.
+The ETMD3 peak is as well shifted to slightly higher energies allowing for the
+fourth decay channel to open.

### 2015-05-03 structures.tex
improve structures part

@@
 
-The expected mean argon cluster sizes can be
-estimated were estiamted and collected in Table \ref{table:}.
+The expected mean argon cluster sizes
+were estimated and collected in Table \ref{table:cluster}.
 In case of the smaller clusters measured
@@
 be larger than those of pure argon due to the higher polarizability
-and hence xyz of xenon. All clusters contributing to the coincidence spectrum
+and hence larger cohesive energy of xenon. All clusters
+contributing to the coincidence spectrum
 do contain at least one xenon atom, otherwise there would be no signal at all.
@@
 to find and measure such a cluster is higher than a different structure.
-We therefore start from an icosahedral structures and substitute atoms
+We therefore started from icosahedral structures and substituted atoms
 in the clusters by
-argon / xenon atoms or add these to a given structure close to the wanted
+argon / xenon atoms or added these to a given structure close to the wanted
 position. Afterwards the cluster structures were optimized using the
@@
 
-As discussed  in section \ref{}, the small clusters are very likely
+As discussed in the introduction, the small clusters are very likely
 to deviate from a core-shell structure with a xenon core surrounded
@@
  \item add two xenon atoms on top of surfaces of a 13 atoms argon core
-       in different relative positions (see Figure \ref{cluster_2_overview})
+       in different relative positions (see Figure
+       \ref{figure:cluster_2_overview})
        in order to achieve a xenon content in the cluster close to the
-       measured one shown in Table \ref{}
+       measured one shown in Table \ref{table:cluster}
  \item substitute six argon atoms of a 55 atoms argon cluster by xenon
        atoms either grouping them or scattering them througout the cluster
-       (see Figure \ref{cluster_3_overview} Panels b) and c)) in order to
+       (see Figure \ref{figure:cluster_3_overview} Panels b) and c)) in order to
        achieve a xenon content in the cluster close to the experimental one

### 2015-05-06 structures.tex
add more history of structure determination

@@
 spectra.
+
+In the previous studies \cite{Fasshauer13} the ArXe clusters were assumed
+to be large and have more than 1500 atoms. The model structures assumed
+an fcc structure and not an icosahedral structure as would be more
+probable for small clusters.
+Additionally,
+the expectation value for the number of xenon atoms relies on a pure
+xenon gas. Since the xenon content in the mixed gas is much lower, also
+the number of xenon atoms can be expected to be by far less. We therefore
+start from the estimated number of atoms in the cluster after expansion
+of pure argon gas.
+We therefore rethink the possible cluster structures.
+%Furthermore, the theoretical prediction did not match the experimental results.
+%Since the spectra are strongly depending on the cluster structure as shown in
+%\cite{fasshauer2014}, the underlying structure seems not to fit and hence
+%we rethink the possible cluster structures.
 
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
  \centering

### 2015-05-06 theo_discussion.tex
add more history of structure determination

\section{Discussion}

We have discussed the experimental spectra in iSection \ref{} and
the expected features of spectra for different cluster types in
Section \ref{}. In this section we combine the experimental and theoretical
results in order to determine the structure of the noble gas clusters.

### 2015-05-11 experimental.tex
started on experimental section

--- 2015-03-18 exp_results.tex
@@
-\section{Experimental Results}
+\section{Experimental}
+%
 \begin{table}
 \caption{
-Expansion parameters used for cluster production in this work.
+Expansion parameters used for cluster production.
+Here, Xe$_{in}$ is the fraction (particle number) of Xe in the expanding gas before the expansion, $T$ the nozzle temperature, and $p$ the stagnation pressure.
 Experiments were done with $d = 80~\mu$m (first two sections) and $d = 100~\mu$m (bottom section) conical nozzles of 15$^\circ$ half opening angle.
@@
 These values are calculated as in ref.\ \protect\citenum{hagena1981}.
-Due to the small amount of Xe admixture, we basically have a Xe seeded expansion of Ar gas.
+Due to the much lower freezing point of Ar, we basically have an Ar seeded expansion of Xe gas.
 We therefore expect actual cluster sizes in-between the two limiting values given.
@@
 This figure does not include systematic errors of the empirical model used.
-\label{tab:cluster} }
+}
+\label{tab:cluster}
 
@@
 \end{table}
+%
+%
+The apparatus used for the experiments consists of a cooled, supersonic molecular jet apparatus and a magnetic bottle spectrometer, which detects photoelectrons and secondary electrons produced after ionization with synchrotron radiation.
+A detailed description can be found in Ref.
+\citenum{arion}, and here we focus on those details specific for the current experiment.
+Commercial Ar and Xe gas was used.
+Separate containers for the two gases were filled up to pressures suitable for producing a certain mixing ratio.
+The gases were then allowed to mix before the expansion.
+Expansion parameters and mean cluster sizes according to an empirical model are given in Tab.\ \ref{tab:cluster}.
+We note that currently no such empirical model for heterogeneous expansions exists.
+We therefore can only give the mean size for a pure jet of one or the other gas at the given conditions.
 
-\begin{table}
-\caption{Properties of the outer valence spectra of mixed ArXe clusters.
-Spectra of pure Ar and Xe clusters are included for reference.
-All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV).
-Binding energies $E_b$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit.
-The experimental Xe content of the clusters always is higher than in the original gas mixture (see Tab.\ \protect\ref{tab:cluster}).
-It was determined from the areas of the respective photolines, corrected by the respective atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}.
-Uncertainties are estimated as 3\,\% for the Xe content and 0.05~eV for the binding energies.
-Labels given in the first column refer to the expansion parameters in Tab.\ \protect\ref{tab:cluster}.
-$E_b$ and $w$ are in eV, $A$ is in \%.
-The binding energies can be compared to atomic values of 15.82~eV, 13.43~eV and 12.13~eV for Ar 3p and Xe 5p.
-\label{tab:valence} }
-\begin{tabular}{ l c c c c c c}
-%
-\toprule
-  label & $E_b$(Ar 3p) & $w$(Ar 3p) & $E_b$(Xe 5p$_{1/2}$) &  $E_b$(Xe 5p$_{3/2}$) & $w$(Xe 5p$_{3/2}$)  &  $A$(Xe) \\
-%
-\midrule
-% Ar, from Marko
- Ar (1) &  15.3  &  1.1 & & & &  \\
-% Ar, from Marko 
- Ar (2) &  15.1  &  1.3 & & & &  \\
-%
-%  columns in the following: energies c.g. 51-plt-oval, widths Marko Diss., Xe content Marko Diss
-% 1103 676, 679
- (a) & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
-% 1103 670
- (b) & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
-% 1103 671
- (c) & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
-% 1103 663
- (d) & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
-% 1103 640
- (e) & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
-% 0506 
-Xe (1) & & & 12.76 & 11.19 & 1.18 & 100\\
-%
-\midrule
-%
-%  1004  886  (UHe, c.g. + roi values)
- 886 & 15.12 & 1.3 & 12.44 & 10.70 & 1.24 & 19\\
-\bottomrule
-\end{tabular}
-\end{table}
+The expansion chamber for the supersonic is separated from the interaction chamber by a non-magnetic, conical skimmer with a diameter 1~mm opening (Beam Dynamics).
+At few cm distance behind the skimmer, the cluster jet was crossed by synchrotron radiation from the BESSY electron storage ring at Helmholtz-Zentrum Berlin.
+Electrons were detected by a short 'magnetic bottle´ time-of-flight spectrometer, that has been described earlier.\cite{mucke_review} Experiments were carried out at the TGM-4 (last section in Tab.\ \ref{tab:cluster}) and the UE112-PGM-1 (first two sections) beamlines with linearly, horizontally polarized radiation.

### 2015-07-02 theo_discussion.tex
add beginning of theoretical discussion -> lacks information from experiment

@@
 
-We have discussed the experimental spectra in iSection \ref{} and
+We have discussed the experimental spectra in Section \ref{} and
 the expected features of spectra for different cluster types in
@@
 results in order to determine the structure of the noble gas clusters.
+
+The simulated secondary electron spectra for the xenon core structures
+(see Figure \ref{figure:xe_3_in})
+show an ICD peak at higher energies than those structures with added xenon
+atoms on the surface. This does not fit to the experimentally determined
+spectra and hence we consider an argon core to be more probable for the
+small measured clusters.
+
+The experimental spectra in Figure \ref{}
+show a broadening of the secondary electron peak with increasing
+pressure (?) and hence cluster size just as can be expected from
+the theoretically simulated spectra in Figure \ref{figure:surf}.
+
+From the theoretical simulations of larger small clusters
+having the same xenon content as experimentally observed a clearly
+visible ETMD peak is to be expected as shown in Figure \ref{figure:ar_3_6in}.
+However, the experimental spectra do not show a signal in the energy
+region of \unit[1.5--6.5]{eV}. From this we conclude that the clusters
+measured were smaller than 55 atoms containing only very few xenon atoms.
+Additionally, if the cluster contains more than one xenon atom, they are
+not expected to be close because of an otherwise visible ETMD peak
+(compare Figure \ref{figure:2tops}).
+
+The large clusters with a large xenon content can be expected to have
+a xenon core being surrounded by argon layers and hence, both ICD and
+ETMD should be visible in the spectrum. Unfortunately, the ICD and ETMD
+peaks overlap such that the two processes can not be distiguished.

### 2015-07-02 exp_results.tex
correct labels and refs

@@
 \section{Experimental Results}
-\begin{table}
-\caption{
-Expansion parameters used for cluster production in this work.
-Experiments were done with $d = 80~\mu$m (first two sections) and $d = 100~\mu$m (bottom section) conical nozzles of 15$^\circ$ half opening angle.
-For the mixed clusters, $\langle N_{Ar} \rangle$ and $\langle N_{Xe} \rangle$ refer to hypothetical cluster sizes yielded with an expansion of the respective pure gas at the conditions given.
-These values are calculated as in ref.\ \protect\citenum{hagena1981}.
-Due to the small amount of Xe admixture, we basically have a Xe seeded expansion of Ar gas.
-We therefore expect actual cluster sizes in-between the two limiting values given.
-Inaccuracies in the calculation of $\langle N\rangle$ due to fluctuations of the input parameters are less than 6\,\%.
-This figure does not include systematic errors of the empirical model used.
-\label{tab:cluster} }
-
-\begin{tabular}{l c c c r r}
-%
-\toprule
-  label  &  Xe$_{in}$ [\%]  &  $T$ [K]  &  $p$ [bar] & $\langle N_{Ar} \rangle$ & $\langle N_{Xe} \rangle$ \\
-%
-\midrule
-% Ar, from Marko 
-Ar (1)  & --- &  96.5  & 0.35  &  42  &  --- \\
-% Ar, from Marko 
-Ar (2)  & --- &  96.5  & 0.67  & 190  &  --- \\
-% 1103 676, 679
- (a) & 1.2 &  174   & 0.32  &   4  &   62 \\
-% 1103 670
- (b) & 1.2 &  174   & 0.49  &  10  &  168 \\
-% 1103 671
- (c) & 1.2 &  174   & 0.68  &  21  &  362 \\
-% 1103 663
- (d) & 3.0 &  172   & 0.28  &   3  &   48 \\
-% 1103 640
- (e) & 5.0 &  171   & 0.51  &  12  &  202 \\
-% 0506 382, Keller offset ber?cksichtigt
-Xe (1)  & 100 & 183.5  & 0.68  & ---  &  517 \\     
-\midrule
-% 1103 653
-1103, only coinc  & 3.0 &  172   & 0.51  &  11  &  196 \\
-% 1103 658
-  & 3.0 &  172   & 0.68  &  22  &  385 \\
-% 1103 630
-  & 5.0 &  167   & 0.37  &   6  &  108 \\
-% 1103 629
-  & 5.0 &  167   & 0.68  &  26  &  451 \\
-\midrule
-% 1004 867
-1004, 867  & 2.5 &  154   & 2.12  &  920 & 15760\\
-% 1004 868
-868  & 2.5 &  158   & 1.50  &  355 &  6090\\
-% 1004 886
-886  & 2.5 &  161   & 2.41  &  980 & 16770\\
-% 1004 858
-858  & 5.0 &  149   & 2.50  & 1620 & 27700\\
-%
-\bottomrule
-\end{tabular}
-\end{table}
 
@@
 %  1004  886  (UHe, c.g. + roi values)
- 886 & 15.12 & 1.3 & 12.44 & 10.70 & 1.24 & 19\\
+ 886 & 15.15 & 1.3 & 12.59 & 11.01 & 1.24 & 19\\
 \bottomrule

### 2015-07-02 experimental.tex

@@
 %
-The apparatus used for the experiments consists of a cooled, supersonic molecular jet apparatus and a magnetic bottle spectrometer, which detects photoelectrons and secondary electrons produced after ionization with synchrotron radiation.
-A detailed description can be found in Ref.
+The apparatus used for the experiments consists of a supersonic molecular jet with a cooled nozzle, and a magnetic bottle spectrometer, which detects photoelectrons and secondary electrons produced after ionization with synchrotron radiation.\cite{arion} A detailed description can be found in Ref.
 \citenum{arion}, and here we focus on those details specific for the current experiment.
@@
 Expansion parameters and mean cluster sizes according to an empirical model are given in Tab.\ \ref{tab:cluster}.
-We note that currently no such empirical model for heterogeneous expansions exists.
+We note that currently no such  model for heterogeneous expansions exists.
 We therefore can only give the mean size for a pure jet of one or the other gas at the given conditions.
@@
 At few cm distance behind the skimmer, the cluster jet was crossed by synchrotron radiation from the BESSY electron storage ring at Helmholtz-Zentrum Berlin.
-Electrons were detected by a short 'magnetic bottle´ time-of-flight spectrometer, that has been described earlier.\cite{mucke_review} Experiments were carried out at the TGM-4 (last section in Tab.\ \ref{tab:cluster}) and the UE112-PGM-1 (first two sections) beamlines with linearly, horizontally polarized radiation.
+Electrons were detected by a short `magnetic bottle' time-of-flight spectrometer, that has been described earlier.\cite{mucke_review} Data were recorded in two different beamtimes at the UE112-PGM-1 (small and medium sized clusters, first two sections in Tab.\ \ref{tab:cluster}) and at the TGM-4 beamline (large clusters, last section in Tab.\ \ref{tab:cluster}).
+Linearly, horizontally polarized radiation was used.

### 2015-07-02 intro.tex

@@
 research on composition and structure of free nanoparticles.\cite{
-jpcc} Besides by photoionization, free electrons emerging from 
+jpcc} Besides photoionization, free electrons emerging from 
 nanoparticles can also be produced by the relaxation of 
@@
 elements C-Ne, and also for core levels vacancies e.g. in \ce{H2O}
-, where it competes with Auger decay\cite{slavicek}.
+, where it competes with Auger decay.\cite{slavicek}
 
@@
 state, followed by a transfer of energy to a neighbouring site, 
-and an electron emission process therefrom. In the final state a 
-positive charge remains at the site of ionization, and another 
-was created at another atom or molecule. Soon after, related 
+and an electron emission process therefrom. The final state contains 
+two positive charges; one at the original site of ionization, and a second
+one at another atom or molecule.
+
+Soon after, related 
 autoionization processes were discovered that proceed via a 
@@
 typically is the case in weakly bonded systems, held together by 
-hydrogen bonds or van-der-Waals bonds. In the case of strong (
-covalent or metallic) bonding, there is no distinction between 
-ICD and Auger decay.\cite{hergenhahn_review}
+hydrogen bonds or van-der-Waals bonds. In the case of strong
+(covalent or metallic) bonding, it is inpossible to make a
+distinction between ICD and Auger decay.\cite{hergenhahn_review}
 
 First experiments on ICD in heterogeneous systems were on Ne-Ar 
-clusters.\cite{barthnear} Those were followed by studies of ICD-
-like inner-shell decays in aqueous solution.\cite{
-aziz,pokapanich,pokapanich2011} Pioneering work also showed the 
+clusters.\cite{barthnear} Those were followed by studies of 
+ICD-like inner-shell decays in aqueous solution.\cite{aziz,pokapanich,pokapanich2011}
+Pioneering work also showed the 
 potential for studies of the interface between a substrate and an 
@@
 clusters was recently presented by some of the authors.\cite{
-fasshauer2014} For this system, a detailed analysis of 
+fasshauer2014} For that system, a detailed analysis of 
 photoelectron spectra with respect to structural features of the 
@@
 
-Rare gas clusters are suitable prototype systems for studies of (
-e.g.) ICD, as they can easily be produced by supersonic 
+Rare gas clusters are suitable prototype systems for studies of
+(e.g.) ICD, as they can readily be produced by supersonic 
 expansion. Mixed rare gas clusters easily form by coexpansion of 
@@
 conducted, and concluded that increasing the Xe content in a 
-coexpanding ArXe mixture leads to the formation of Xe-core, Ar-
-shell systems with a sharp interface between the two species.\cite
+coexpanding ArXe mixture leads to the formation of Xe-core, 
+Ar-shell systems with a sharp interface between the two species.\cite
 {tchaplyguine,hoener} This finding was confirmed by electron 
@@
 expanding gas mixture, as Xe can be condensed much easier than Ar.
+A complementary study used photoelectron-photoion coincidence of
+large Ar-Xe clusters, and found that after inner shell (Xe 4d, Ar 2p)
+photoionization significant charge transfer between both species
+occurs before the mass spectroscopic final state is reached.\cite{berrah}
 

### 2015-07-02 theory.tex
correct refs

@@
 \section{Theoretical Approach}
+%
 Experimental coincidence spectra are given by the kinetic energies $E_{sec}$
@@
 \begin{equation}
- \Gamma_{ICD,i,\beta} = 2\pi
+ \Gamma_{ICD,i,\beta} = (2J_{in}+1) \frac{3c^4}{8\pi}
+                        \sum\limits_{M_{in}'}
+                        \left| \left(
+                        \begin{array}{ccc}
+                        J_A'  & 1        & J_A\\
+                        -M_A' & M_A'-M_A & M_A
+                        \end{array}\right) \right|^2
                         \frac{\sigma^{(X_E)}(\omega_{vp,\beta})}

### 2015-09-30 exp_results.tex
experimental outer valence spectra added, order of sections changed

@@
 \end{table}
+
+\begin{figure}[ht]
+ \centering
+ \includegraphics[width=8.5cm]{pics/figure_oval_1.pdf}
+ \caption{
+ Outer valence spectra of mixed Ar-Xe clusters, in comparison to the pure species.
+Panel a) shows the outer valence region of homogeneous Ar and Xe clusters, respectively (see text for details).
+The two lower panels show the spectra of the mixed species of different size.
+Sharp lines marked `m' result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states.
+Labels in panels b) and c) give the Xe content in the expanding gas mixture, which is lower then the Xe content observed in the heterogeneous clusters.
+Parts of the spectrum resulting from the Xe inventory of the clusters are shown in blue colour.
+The photon energy used was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
+}
+ \label{figure:oval1}
+\end{figure}
+
+\begin{figure}[ht]
+ \centering
+ \includegraphics[width=8.5cm]{pics/figure_oval_2.pdf}
+ \caption{
+Outer valence spectra of mixed Ar-Xe clusters from gas mixtures with different Xe concentration. See Fig.\ \ref{figure:oval1} and text for details.
+}
+ \label{figure:oval2}
+\end{figure}

### 2015-10-13 exp_results.tex

@@
  \caption{
- Outer valence spectra of mixed Ar-Xe clusters, in comparison to the pure species.
+Outer valence photoelectron spectra of mixed Ar-Xe clusters, in comparison to the pure species.
 Panel a) shows the outer valence region of homogeneous Ar and Xe clusters, respectively (see text for details).
@@
  \caption{
-Outer valence spectra of mixed Ar-Xe clusters from gas mixtures with different Xe concentration. See Fig.\ \ref{figure:oval1} and text for details.
+Outer valence photoelectron spectra of mixed Ar-Xe clusters from gas mixtures with different Xe concentration. See Fig.\ \ref{figure:oval1} and text for details.
 }
@@
 \end{figure}
+
+\begin{figure}[ht]
+ \centering
+ \includegraphics[width=8.5cm]{pics/figure_map.pdf}
+ \caption{
+Photon excited electron-electron coincidence spectra of mixed Ar-Xe clusters in the inner valence region.
+Panel b): Color-coded map of coincident electron pairs, with high energy electron $e_1$ and low energy electron $e_2$.
+The kinetic energy of the high energy electron is drawn as binding energy, using the photon energy of $h\nu = 32$~eV.
+Panel c): Energy spectrum of primary electrons $e_1$, irrespective of the energy of the secondary electron (summation of the coincidence map along horizontal lines).
+The peak at a binding energy of 28.7~eV pertains to the Ar 3s photoelectron line.
+Panel a): Energy spectrum of all secondary (ICD or ETMS) electrons $e_2$ pertaining to the binding energy region marked by two black bars.
+Intensity is expressed as coincident events/pixel of 20~meV$^2$.
+See text for details.
+}
+ \label{figure:map}
+\end{figure}

### 2015-10-29 exp_results.tex
experimental figures added

@@
 Labels in panels b) and c) give the Xe content in the expanding gas mixture, which is lower then the Xe content observed in the heterogeneous clusters.
-Parts of the spectrum resulting from the Xe inventory of the clusters are shown in blue colour.
 The photon energy used was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
@@
  \caption{
-Photon excited electron-electron coincidence spectra of mixed Ar-Xe clusters in the inner valence region.
-Panel b): Color-coded map of coincident electron pairs, with high energy electron $e_1$ and low energy electron $e_2$.
-The kinetic energy of the high energy electron is drawn as binding energy, using the photon energy of $h\nu = 32$~eV.
+Photon excited electron-electron coincidence spectrum of mixed Ar-Xe clusters in the inner valence region.
+Panel b): Color-coded map of coincident electron pairs, with the electron of higher kinetic named $e_1$.
+The energy of $e_1$ is given as binding energy, using the photon energy of $h\nu = 32$~eV.
 Panel c): Energy spectrum of primary electrons $e_1$, irrespective of the energy of the secondary electron (summation of the coincidence map along horizontal lines).
 The peak at a binding energy of 28.7~eV pertains to the Ar 3s photoelectron line.
-Panel a): Energy spectrum of all secondary (ICD or ETMS) electrons $e_2$ pertaining to the binding energy region marked by two black bars.
-Intensity is expressed as coincident events/pixel of 20~meV$^2$.
+Panel a): Energy spectrum of all secondary (ICD or ETMD) electrons $e_2$ pertaining to the Ar 3s binding energy region marked by two black bars.
 See text for details.
+Intensity is expressed as coincident events/pixel of 20~meV$^2$ (b) or as coincident events per interval of 20~meV (a,c).
+The color scale of panel b) is linear.
 }
@@
 \end{figure}
+
+\begin{figure}[ht]
+ \centering
+ \includegraphics[width=8.5cm]{pics/figure_ival.pdf}
+ \caption{
+Photon excited electron spectra and electron-electron coincidence spectra of mixed Ar-Xe clusters in the inner valence region.
+Spectra show the Ar 3s photoline from clusters (`cl') and uncondensed Ar monomers (`m'), atop of a background resulting from inelastic intracluster scattering of outer valence photoelectrons.\protect\cite{hergenhahn2002} Black symbols: sum of non-coincident and coincident (1st hit) events, red symbols: coincident events only.
+Solid, colored lines show the results of various least-squares fits, see text for details.
+}
+ \label{figure:ival}
+\end{figure}
+
+\begin{figure}[ht]
+ \centering
+ \includegraphics[width=8.5cm]{pics/figure_eff.pdf}
+ \caption{
+Efficiency of the decay of Ar 3s ionized states in ArXe clusters by emission of a secondary electron via ICD or ETMD.
+Values are arranged by Xe content of the initial gas mixture ('+' symbols: 1.2\,\%, asterisk: 3\,\%, triangle: 5\,\%).
+Symbol sizes indicate the photon energy (large symbols: 32 eV, small: 34 eV), and color indicates the cluster size (black symbols: S, red: M, blue: L).
+See text for details.
+}
+ \label{figure:eff}
+\end{figure}

### 2015-10-30 experimental.tex
Text überarbeitet

@@
 Expansion parameters used for cluster production.
-Here, Xe$_{in}$ is the fraction (particle number) of Xe in the expanding gas before the expansion, $T$ the nozzle temperature, and $p$ the stagnation pressure.
+Here, Xe$_{in}$ is the molar fraction of Xe in the gas mixture before the expansion, $T$ is the nozzle temperature, and $p$ the stagnation pressure.
 Experiments were done with $d = 80~\mu$m (first two sections) and $d = 100~\mu$m (bottom section) conical nozzles of 15$^\circ$ half opening angle.
-For the mixed clusters, $\langle N_{Ar} \rangle$ and $\langle N_{Xe} \rangle$ refer to hypothetical cluster sizes yielded with an expansion of the respective pure gas at the conditions given.
+For the mixed clusters, $\langle N_{Ar} \rangle$ and $\langle N_{Xe} \rangle$ refer to cluster sizes arrived at by an expansion of the respective pure gases at the given conditions.
 These values are calculated as in ref.\ \protect\citenum{hagena1981}.
@@
 
-\begin{tabular}{l c c c r r}
+\begin{tabular}{l c c c c r r}
 %
 \toprule
-  label  &  Xe$_{in}$ [\%]  &  $T$ [K]  &  $p$ [bar] & $\langle N_{Ar} \rangle$ & $\langle N_{Xe} \rangle$ \\
+  & size label  &  Xe$_{in}$ (\%)  &  $T$ (K)  &  $p$ (bar) & $\langle N_{Ar} \rangle$ & $\langle N_{Xe} \rangle$ \\
 %
@@
 % Ar, from Marko 
-Ar (1)  & --- &  96.5  & 0.35  &  42  &  --- \\
+Ar &  & --- &  96.5  & 0.35  &  42  &  --- \\
 % Ar, from Marko 
-Ar (2)  & --- &  96.5  & 0.67  & 190  &  --- \\
+Ar &  & --- &  96.5  & 0.67  & 190  &  --- \\
 % 1103 676, 679
- (a) & 1.2 &  174   & 0.32  &   4  &   62 \\
+ArXe & S & 1.2 &  174   & 0.32  &   4  &   62 \\
 % 1103 670
- (b) & 1.2 &  174   & 0.49  &  10  &  168 \\
+ArXe & M & 1.2 &  174   & 0.49  &  10  &  168 \\
 % 1103 671
- (c) & 1.2 &  174   & 0.68  &  21  &  362 \\
+ArXe & L & 1.2 &  174   & 0.68  &  21  &  362 \\
 % 1103 663
- (d) & 3.0 &  172   & 0.28  &   3  &   48 \\
+ArXe & S & 3.0 &  172   & 0.28  &   3  &   48 \\
 % 1103 640
- (e) & 5.0 &  171   & 0.51  &  12  &  202 \\
+ArXe & M & 5.0 &  171   & 0.51  &  12  &  202 \\
 % 0506 382, Keller offset ber?cksichtigt
-Xe (1)  & 100 & 183.5  & 0.68  & ---  &  517 \\     
+Xe &  & 100 & 183.5  & 0.68  & ---  &  517 \\     
 \midrule
 % 1103 653
-1103, only coinc  & 3.0 &  172   & 0.51  &  11  &  196 \\
+ArXe & M & 3.0 &  172   & 0.51  &  11  &  196 \\
 % 1103 658
-  & 3.0 &  172   & 0.68  &  22  &  385 \\
+ArXe & L & 3.0 &  172   & 0.68  &  22  &  385 \\
 % 1103 630
-  & 5.0 &  167   & 0.37  &   6  &  108 \\
+ArXe & S  & 5.0 &  167   & 0.37  &   6  &  108 \\
 % 1103 629
-  & 5.0 &  167   & 0.68  &  26  &  451 \\
+ArXe & L  & 5.0 &  167   & 0.68  &  26  &  451 \\
 \midrule
 % 1004 867
-1004, 867  & 2.5 &  154   & 2.12  &  920 & 15760\\
+1004, 867 &  & 2.5 &  154   & 2.12  &  920 & 15760\\
 % 1004 868
-868  & 2.5 &  158   & 1.50  &  355 &  6090\\
+868 & & 2.5 &  158   & 1.50  &  355 &  6090\\
 % 1004 886
-886  & 2.5 &  161   & 2.41  &  980 & 16770\\
+886 & XL & 2.5 &  161   & 2.41  &  980 & 16770\\
 % 1004 858
-858  & 5.0 &  149   & 2.50  & 1620 & 27700\\
+858 &  & 5.0 &  149   & 2.50  & 1620 & 27700\\
 %
@@
 %
-The apparatus used for the experiments consists of a supersonic molecular jet with a cooled nozzle, and a magnetic bottle spectrometer, which detects photoelectrons and secondary electrons produced after ionization with synchrotron radiation.\cite{arion} A detailed description can be found in Ref.
-\citenum{arion}, and here we focus on those details specific for the current experiment.
-Commercial Ar and Xe gas was used.
-Separate containers for the two gases were filled up to pressures suitable for producing a certain mixing ratio.
-The gases were then allowed to mix before the expansion.
-Expansion parameters and mean cluster sizes according to an empirical model are given in Tab.\ \ref{tab:cluster}.
-We note that currently no such  model for heterogeneous expansions exists.
+The apparatus used for the experiments consists of a supersonic molecular jet with a cooled nozzle, and a magnetic bottle spectrometer, which detects photoelectrons and secondary electrons produced after ionization with synchrotron radiation.\cite{arion}
+% Leave this citation in place to avoid Latex error
+A detailed description can be found in Ref. \citenum{arion}, and here we focus on details specific for the current experiment. Commercial Ar and Xe gas was used. 
+Separate containers for the two gases were filled up to pressures suitable for producing a certain mixing ratio. The gases were then allowed to mix before the expansion. 
+Expansion parameters and mean cluster sizes, according to an empirical model, are given in Tab.\ \ref{tab:cluster}. 
+We note that currently no empirical model for cluster sizes in a heterogeneous gas expansion exists. 
 We therefore can only give the mean size for a pure jet of one or the other gas at the given conditions.
 
-The expansion chamber for the supersonic is separated from the interaction chamber by a non-magnetic, conical skimmer with a diameter 1~mm opening (Beam Dynamics).
+The expansion chamber for the supersonic jet is separated from the interaction chamber by a non-magnetic, conical skimmer with a diameter 1~mm opening (Beam Dynamics). 
 At few cm distance behind the skimmer, the cluster jet was crossed by synchrotron radiation from the BESSY electron storage ring at Helmholtz-Zentrum Berlin. 
-Electrons were detected by a short `magnetic bottle' time-of-flight spectrometer, that has been described earlier.\cite{mucke_review} Data were recorded in two different beamtimes at the UE112-PGM-1 (small and medium sized clusters, first two sections in Tab.\ \ref{tab:cluster}) and at the TGM-4 beamline (large clusters, last section in Tab.\ \ref{tab:cluster}).
+Electrons were detected by a short `magnetic bottle' time-of-flight spectrometer, that has been described earlier.\cite{mucke_review} 
+Data were recorded in two different beamtimes at the UE112-PGM-1 (small and medium sized clusters, first two sections in Tab.\ \ref{tab:cluster}) and at the TGM-4 beamline (large clusters, last section in Tab.\ \ref{tab:cluster}).
 Linearly, horizontally polarized radiation was used. 
+The storage ring was operated in single bunch conditions.

### 2015-10-30 structures.tex
Text überarbeitet

--- 2015-05-03 structures.tex
@@
 From the experimental results we can obtain two hints for the cluster
-structure: the minimum size and the xenon content. We will in the following
+structure: the minimum size and the xenon content. In the following we will 
 use these to construct possible cluster structures for which we will later
-simulate the ICD and ETMD spectra. At this step we put in whatever structure
-we might think of and hope to be able to exclude some of them by comparison of
-the ICD and ETMD spectra to the experimental electron-electron coincidence
-spectra.
+simulate the ICD and ETMD spectra. At this point we put in a variety of structures,
+in the hope to exclude some of them by comparison of
+the ICD and ETMD spectra to the experimental ones.
 
-The expected mean argon cluster sizes
-were estimated and collected in Table \ref{table:cluster}.
-In case of the smaller clusters measured
-these expectation values range from \unit[3 -- 21]{Ar atoms} for
-expansion of pure argon. The cluster sizes of a mixed gas are unknown but
-for xenon as the second component the cluster sizes can be expected to
-be larger than those of pure argon due to the higher polarizability
+In our previous study\cite{Fasshauer13} the ArXe clusters were assumed
+to be large, having more than 1500 atoms. The model structures assumed
+an fcc structure and not an icosahedral structure, which is energetically
+favoured for small clusters.
+Most estimated cluster sizes given in Table \ref{tab:cluster} are much smaller.
+We use the estimated number of atoms for a pure Ar expansion as the lower limit for the actual cluster size, start our search for model structures from there.
+%
+%Additionally,
+%the expectation value for the number of xenon atoms relies on a pure
+%xenon gas. Since the xenon content in the mixed gas is much lower, also
+%the number of xenon atoms can be expected to be by far less. We therefore
+%start from the estimated number of atoms in the cluster after expansion
+%of pure argon gas.
+%We therefore rethink the possible cluster structures.
+%Furthermore, the theoretical prediction did not match the experimental results.
+%Since the spectra are strongly depending on the cluster structure as shown in
+%\cite{fasshauer2014}, the underlying structure seems not to fit and hence
+%we rethink the possible cluster structures.
+%
+For the smaller clusters measured,
+these expectation values range from \unit[3--21]{Ar atoms}. 
+The cluster sizes for expansion of a mixed gas are unknown, but
+for xenon as the second component a larger size is expected compared to a
+pure argon expansion, due to the higher polarizability
 and hence larger cohesive energy of xenon. All clusters
 contributing to the coincidence spectrum
-do contain at least one xenon atom, otherwise there would be no signal at all.
-In an expansion a large variance of clusters and with different structures
-is produced. However, for small clusters consisting of less than
-approximately \unit[1000]{atoms} so-called \emph{islands of stability} were
-found for clusters with icosahedral shape. This means, that the probability
-to find and measure such a cluster is higher than a different structure.
-We therefore started from icosahedral structures and substituted atoms
-in the clusters by
-argon / xenon atoms or added these to a given structure close to the wanted
-position. Afterwards the cluster structures were optimized using the
-UFF force field \cite{} implemented in
-Avogadro \cite{} for a structure optimization.
+contain at least one xenon atom, as otherwise decay by ICD or ETMD is energetically not allowed.
 
-\begin{figure}[h]
+In a gas expansion a range of clusters sizes with different structures is produced. 
+However, for small rare gas clusters consisting of less than approximately \unit[1000]{atoms} so-called \emph{islands of stability} were found.\cite{haberland}  
+In mass spectra, clusters with mass numbers corresponding to icosahedral shapes had a (slightly) enhanced abundance over other sizes. 
+We therefore started from icosahedral structures and produced mixed cluster structures by substitution of individual atoms with one or the other kind (Ar or Xe), or added individual atoms to a given structure close to the desired position.
+After that, the cluster structures were optimized using the UFF force field method \cite{} implemented in the 
+Avogadro programme \cite{}.
+%
+\begin{figure}[ht]
  \centering
  \includegraphics[width=8.5cm]{pics/cluster_2_overview.pdf}
- \caption{Cluster structures with 13 argon atoms and two additional xenon
-          atoms on different surfaces of the argon icosahedron:
-          \textbf{a)} closest possible \textbf{b)} middle \textbf{c)}
-          furthest away.}
+ \caption{Cluster structures composed of 13 argon atoms and two additional xenon
+          atoms on different surfaces of the argon icosahedron, varying in Xe-Xe distance:
+          (a) closest possible, (b) middle, (c) furthest away.}
  \label{figure:cluster_2_overview}
 \end{figure}
-
+%
 \begin{figure}[h]
@@
  \includegraphics[width=8.5cm]{pics/cluster_3_overview.pdf}
- \caption{Cluster structures based on 55 atoms icosahedral cluster structure.
-          \textbf{a)} 1 xenon atom on the surface of a 55 atoms icosahedral
-          argon cluster. \textbf{b)} six xenon atoms inside a 55 atoms cluster
-          grouped on one side. \textbf{c)} six xenon atoms distributed
-          in a 55 atoms cluster. }
+ \caption{Cluster structures derived from a 55 atom icosahedral structure:
+          (a) one xenon atom on the surface, (b) six xenon atoms inside a 55 atoms cluster,
+          grouped on one side, (c) six xenon atoms distributed randomly
+          in a 55 atoms cluster.}
  \label{figure:cluster_3_overview}
@@
 
-As discussed in the introduction, the small clusters are very likely
-to deviate from a core-shell structure with a xenon core surrounded
-by argon shells as observed for large clusters. We therefore start from
-argon clusters of 13 or 55 atoms and modify them in one of the following
+As discussed in the introduction, the small clusters will likely
+deviate from a core-shell structure with a xenon core surrounded
+by argon shells, as observed for large clusters.\cite{tchaplyguinearxe,Vach_1999} We therefore start from
+argon clusters of 13 or 55 atoms, and modify them in one of the following
 ways:
-
+%
 \begin{itemize}
  \item add one xenon atom on top of a surface / edge / vertex of
-       the argon core as for example shown in
-       Figure \ref{figure:cluster_3_overview} Panel a)
+       the argon core, as for example shown in
+       Figure \ref{figure:cluster_3_overview} a)
        for one additional xenon atom
-       on top of surface of a \unit[55]{atoms} argon core
- \item substitute one argon atom in a surface / edge / vertex position if
-       possible
+       on top of surface of a \unit[55]{atoms} argon core,
+ \item substitute one argon atom in a surface / edge / vertex position,
  \item substitute one or two argon atoms in the core of the argon cluster
-       by xenon atom(s) for the simulation of the core-shell structure
+       by xenon atom(s) for the simulation of the core-shell structures,
  \item add two xenon atoms on top of surfaces of a 13 atoms argon core
        in different relative positions (see Figure
-       \ref{figure:cluster_2_overview})
+       \ref{figure:cluster_2_overview}),
        in order to achieve a xenon content in the cluster close to the
-       measured one shown in Table \ref{table:cluster}
+       measured one (see below),
  \item substitute six argon atoms of a 55 atoms argon cluster by xenon
-       atoms either grouping them or scattering them througout the cluster
-       (see Figure \ref{figure:cluster_3_overview} Panels b) and c)) in order to
-       achieve a xenon content in the cluster close to the experimental one
+       atoms either grouping them or distributing them througout the cluster
+       (see Figure \ref{figure:cluster_3_overview} b) and c)) in order to
+       achieve a xenon content in the cluster close to the measured one.
 \end{itemize}
-
-Furthermore we constructed a core-shell structure with a core of
-1415 xenon atoms and one additional complete layer of argon atoms for
-comparison with the largest measured ArXe clusters.
+%
+Furthermore, for comparison with the largest measured ArXe clusters, we constructed a core-shell structure with a core of 1415 xenon atoms and one additional complete layer of argon atoms.

### 2015-10-30 theo_results.tex
add more history of structure determination
Text überarbeitet

@@
 \section{Theoretical Results}
-
-The geometrical properties as well as the total ICD and ETMD decay widths
-of the investigated structures are shown in Table \ref{table:theo_gammas}.
-It is important to remember that the first ICD channel opens at a
-channel opening distance of \unit[7.58]{\AA}. Therefore, small
-clusters in which none of the possible Ar-Xe pairs in larger than
-these \unit[7.58]{\AA}, no ICD can take place. Also, two xenon atoms are
-required for an ETMD3 and hence the ETMD3 has to be excluded from
-the possible decay mechanism in clusters with only one xenon atom.
-Because secondary electrons are observed in the experimental spectra
-we exclude all structures without any signal from our further
-discussions.
-
+%
+%
 \begin{table}[h]
 \centering
-\caption{Properties of simulated clusters.}
+\caption{Properties of simulated clusters.
+{\it Q: Einheit von $\Gamma$? 
+Ich schlage vor, alle Zerfallsbreiten mit einem festen Exponenten von z.B. 10${-6}$ aufzuschreiben, und diesen wegzulassen. 
+Es w\"urde dadurch sehr viel \"ubersichtlicher, und man sieht gleich welche Zerf\"alle \"uberhaupt wichtig sind.}
+}
 \begin{tabular}{lrrrccc}
 \toprule
-name                 & Xe atoms & Ar atoms & Xe \% &   ICD                &  ETMD                & $\Gamma_{ICD,ETMD}$\\
+name                 & Xe atoms & Ar atoms & Xe \% &   ICD                &  ETMD                & $\Gamma_{\rm ICD,ETMD}$\\
 \midrule
@@
 \end{table}
+%
+The geometrical properties as well as the total ICD and ETMD decay widths
+of the investigated structures are shown in Table \ref{table:theo_gammas}.
+It is important to remember that the first ICD channel opens at a
+channel opening distance of \unit[7.58]{\AA}. Therefore, in small
+clusters, in which none of the possible Ar-Xe pair distances is larger than
+these \unit[7.58]{\AA}, no ICD can take place. Also, by definition two xenon atoms are
+required for ETMD(3), hence it cannot occur in clusters with only one xenon atom.
+%Because secondary electrons are observed in the experimental spectra
+%we exclude all structures without any signal from our further
+%discussions.
+%
+%In the investigated structures several different aspects have to be
+%taken into account which we will discuss separately if possible
+%on selected structures.
 
-In the investigated structures several different aspects have to be
-taken into account which we will discuss separately if possible
-on selected structures.
+We will now discuss features of several structures, using selected examples.
 
@@
  \includegraphics[width=8.5cm]{pics/surf.pdf}\\
- \includegraphics[width=8.5cm]{pics/R_comp.pdf}
+ \includegraphics[width=8.2cm]{pics/R_comp.pdf}
  \caption{Panel 1: Simulated electron-electron coincidence spectra
@@
 
-Because the structures have only one xenon atom ETMD3 is not possible and
+Because the structures have only one xenon atom ETMD(3) is not possible and
 ICD only is to be expected. Both spectra show several smaller peaks which
@@
 
-For clusters with more than one xenon atom the ETMD3 channel is possible
+For clusters with more than one xenon atom the ETMD(3) channel is possible
 as well. Depending on the positions of the relative positions of the xenon
@@
 
-In all three cases both ICD and ETMD3 are energetically allowed and the ICD
+In all three cases both ICD and ETMD(3) are energetically allowed and the ICD
 spectra are either identical or at least very similar consisting of one
-convoluted peak at approximately \unit[0.2]{eV}. However, the ETMD3 spectra
+convoluted peak at approximately \unit[0.2]{eV}. However, the ETMD(3) spectra
 are very sensitive to the relative positioning of the two xenon atoms.
@@
 of the secondary electrons and the higher are the decay widths. Therefore a
-significant contribution from the ETMD3 compared to the ICD is only
+significant contribution from the ETMD(3) compared to the ICD is only
 to be seen in case of the two xenon atoms residing on two adjacent
-surfaces. The threefold peak structure of the ETMD3 peak does in contrast to
+surfaces. The threefold peak structure of the ETMD(3) peak does in contrast to
 the ICD spectrum not stem from different triple structures but from the
@@
 as shown in Figure \ref{figure:cluster_3_overview} Panels b) and c). Their
-ICD and ETMD3 spectra are shown in Figure \ref{figure:ar_3_6in}.
+ICD and ETMD(3) spectra are shown in Figure \ref{figure:ar_3_6in}.
 
@@
 larger distances du to the different cluster structure. However, the
-significant difference is to be observed in the ETMD3 spectra. The
+significant difference is to be observed in the ETMD(3) spectra. The
 interatomic xenon distance in the grouped xenon is shorther than in the
@@
 peak structure for the cluster with the grouped xenon atoms is seen at
-lower ETMD3 electron energies than for the cluster with evenly
+lower ETMD(3) electron energies than for the cluster with evenly
 distributed xenon atoms. Additionally, the probabilty for an electron
@@
 atoms as their direct neighbours have a significant contribution to the
-total decay width and the total ETMD3 decay width for the structure with
-the grouped xenon atoms is lower than the total ETMD3 decay width of
+total decay width and the total ETMD(3) decay width for the structure with
+the grouped xenon atoms is lower than the total ETMD(3) decay width of
 the structure with evenly distributed xenon atoms.
@@
 all ICD channels are closed. Since the cluster contains only one xenon atom,
-an ETMD3 is not possible. Hence there is no signal to be expected at all.
-For a core consisting of two xenon atoms both an ICD and an ETMD3 spectrum
+an ETMD(3) is not possible. Hence there is no signal to be expected at all.
+For a core consisting of two xenon atoms both an ICD and an ETMD(3) spectrum
 can be seen. Compared to the argon core cluster structures the ICD peak is
 shifted to higher ICD electron energies not being in agreement with
-the experimental spectrum. Additionally, the ICD and ETMD3 spectra overlap.
-In case of the ETMD3 only three of the four different decay channels are
+the experimental spectrum. Additionally, the ICD and ETMD(3) spectra overlap.
+In case of the ETMD(3) only three of the four different decay channels are
 anergetically allowed.
@@
 in the input of the simulation.
-The ETMD3 peak is as well shifted to slightly higher energies allowing for the
+The ETMD(3) peak is as well shifted to slightly higher energies allowing for the
 fourth decay channel to open.

### 2015-10-30 theory.tex
Text überarbeitet

@@
 %
-Experimental coincidence spectra are given by the kinetic energies $E_{sec}$
-of the secondary electron
-and the intensities of the peaks. The latter is proportional to the
-probability of the decay as well as the theoretically determinable
-decay width $\Gamma=\frac{\hbar}{\tau}$,
-which is inverse proportional to the lifetime $\tau$. The manifold of the
-secondary energies and decay widths will therefore compose the electron-electron
-coincidence spectrum.
-In case of noble gas clusters
-with given structures three aspects have to be taken into account:
-different decay mechanisms, the possibility to decay with multiple
-interaction partners and different decay channels within each decay mechanism.
-At the current stage of development we need to neglect the nuclear dynamics which
+We are interested in describing the electron emission spectra of excited states in clusters, that where measured by the electron-electron coincidence method in our experiments. 
+In our theoretical description, these will be composed of multiple transitions, each characterized by a kinetic energy $E_{\rm sec}$ of the secondary electrons, and the intensity of the peak.
+The latter is proportional to the probability of the decay, represented here by the decay width $\Gamma_\beta = \hbar/\tau_\beta$, where $\tau_\beta$ is the lifetime due to the respective transition.
+The total decay width $\Gamma$ is the sum of all partial $\Gamma_\beta$.
+In case of noble gas clusters with a given geometrical structure, three aspects have to be taken into account:
+different decay mechanisms, the contribution of different cluster sites to the respective decay, and the existence of different decay channels within each decay mechanism.
+At the current stage of development we have to neglect the nuclear dynamics, which
 additionally might play an important role.
 
-This means we are dealing with a sum over three different indices for the
-evaluation of the decay width. For a given structure it is most convenient to
-start with a decomposition of the total system into interaction partners of
+This means, for the evaluation of the decay width we are dealing with a sum over three different indices: 
+For a given structure it is most convenient to
+start with a decomposition of the system into interaction partners of
 the different decay mechanisms, i.e. pairs (combination of two atoms regardless
-the internuclear distance) for the ICD and triples (combinations of three atoms)
+of their internuclear distance) for the ICD and triples (combinations of three atoms)
 for the ETMD.
+{\em Q: Doubles for ETMD(2) and triples for ETMD(3) ?! Do we make this distinction here?}
 These atoms do not necessarily need to form bonds between each other or
 even be close, but they are characterized according to fixed internal
-coordinates. Each pair and triple can be described by its properties, like
-energy of the secondary electron and decay width,
-which are in first order of approximation independent of further, eventually
-present, atoms. In the following, this approach is going to be called
-model of pairs and triples.
+coordinates. 
+Each pair and each triple leads to a decay spectrum that can be described by the energy of the secondary electron and the decay width, and which is in first order of approximation independent of other atoms present in the cluster.
+In the following, this approach will be called model of pairs and triples.
 
@@
 In order to determine, whether a channel $\beta$ for a given geometry and decay
-mechanism is open ,i.e., in accordance with energy conservation,
-the energies of the initial $E_{in}$ and the final states $E_{fin}$ of
+mechanism is open, i.e., whether it is in accordance with energy conservation,
+knowledge of the energies of the initial and the final states, $E_{\rm in}$ and $E_{\rm fin}$, of
 the corresponding processes are necessary.
-When the channel
-is open, the excess energy is carried away by the emitted electron $E_{sec}$
-in form of its kinetic energy. These energies can in the model
-of pairs and triples be approximated to be
+If the channel
+is open, the excess energy is carried away by the emitted electron
+in form of its kinetic energy $E_{\rm sec}$. These energies in the model
+of pairs and triples can be approximated by
 
 \begin{align}
- E_{in}        &= SIP(X_{in}) \label{equation:E_in}\\
- E_{fin}^\beta &= SIP(X_{D}^\beta) + SIP(X_{E}^\beta) + \frac 1d
+ E_{\rm in}        &= SIP(X_{\rm in}) \label{equation:E_in}\\
+ E_{\rm fin}^\beta &= SIP(X_{D}^\beta) + SIP(X_{E}^\beta) + \frac 1d
            \label{equation:E_fin}\\
- E_{sec}^\beta &= E_{in}^\beta - E_{fin}^\beta \label{equation:E_sec}
+ E_{\rm sec}^\beta &= E_{\rm in}^\beta - E_{\rm fin}^\beta \label{equation:E_sec}
 \end{align}
-where $X_{in}$ denotes the initially ionized atom and
+where $X_{\rm in}$ denotes the initially ionized atom and
 $X_{D}$ and $X_{E}$ describe the electron donating atom and electron
 emitting atom, respectively.
-$\beta$ denotes the decay channel characterized
-by the quantum numbers of the ionized atoms in the pairs
-and triples and $d$ denotes the interatomic distance between the atoms
-$X_{D}$ and $X_{E}$. The initially ionized atom $X_{in}$ can
+$\beta$ denotes the decay channel characterized by the quantum numbers of the ionized atoms in the pairs and triples, $SIP(X^\beta)$ the single ionization potential of vacancy $\beta$ in atom $X$ and $d$ the interatomic distance between the atoms $X_{D}$ and $X_{E}$.
+Atomic units are used.
+The initially ionized atom $X_{\rm in}$ can
 coincide with one or both of
@@
 atoms determines the kind of electronic decay process at hand. Hence, in an
-Auger process all three atoms would coincide, for an ICD $X_{in}$
-would coincide with $X_{D}$ and for an {ETMD}3
+Auger process all three atoms coincide, for an ICD process $X_{\rm in}$
+coincides with $X_{D}$ and for an {ETMD}3 process
 all ionized states are located on different atoms.
@@
  \includegraphics[width=8.5cm]{pics/channel_open_ICD.pdf}
- \caption{Initial and final state energies for ArXe pairs at different
-          distances using the experimental ionization potentials as given
+ \caption{Initial (black trace) and final state energies (blue traces) 
+          for ICD in ArXe pairs as a function of 
+          internuclear distance, using the experimental ionization potentials given
           in Table \ref{}. For distances larger than the channel opening
@@
 
-In all autoionization processes considered, a second electron
-is emitted with the kinetic energy $E_{sec}$. If $E_{sec}<0$, then
+The electron emitted by autoionization has the kinetic energy $E_{\rm sec}$. 
+If the calculated value of $E_{\rm sec}$ is negative,
 the final state energy is higher than the initial state energy and the        
 process is energetically not accessible. Hence, the corresponding channel     
-is closed as shown in Figure \ref{figure:channel_open_ICD}. Related to
-the opening of each channel is an internuclear distance which we in the
-following call \emph{channel opening distance}.
+is closed, as shown in Figure \ref{figure:channel_open_ICD}. Related to
+the opening of each channel is an internuclear distance which we will call 
+\emph{channel opening distance} in the following.
 
-This ad hoc approach easily allows to correct for energetic shifts of         
-ionization potentials as observed in larger clusters by adding experimentally
-or theoretically determined energy shifts $\Delta E(X_{A}^{\beta})$
-for a given role in the decay
-$A=in,D,E$ and a channel $\beta$ which yields
-the working expression for the kinetic energy of the secondary electron
+This {\latin ad hoc} approach allows to easily correct for energetic shifts of ionization potentials as observed in larger clusters by adding experimentally or theoretically determined energy shifts $\Delta E(X_{A}^{\beta})$ for a given vacancy $A={\rm in},D,E$ and channel $\beta$.
+This yields the working expression for the kinetic energy of the secondary electron:
 
 \begin{equation}
- E_{sec}^\beta = SIP(X_{in}) + \Delta E (X_{in})
+ E_{\rm sec}^\beta = SIP(X_{\rm in}) + \Delta E (X_{\rm in})
                - SIP(X_{D}^\beta) - \Delta E (X_{D}^\beta)
@@
 \begin{equation}
- \Gamma = \Gamma_{ICD} + \Gamma_{ETMD} .
+ \Gamma = \Gamma_{\rm ICD} + \Gamma_{\rm ETMD} .
 \end{equation}
@@
 These are given by the sum over the decay widths of all pairs $i$ for the
-ICD and all triples $j$ for the ETMD3, respectively and all channels $\beta$.
-
+ICD and all triples $j$ for the ETMD(3), respectively, and over all channels $\beta$:
+%
 \begin{align}
- \Gamma_{ICD}  &= \sum\limits_{i,\beta} N_{ICD,i}  \, \Gamma_{ICD,i,\beta}\\
- \Gamma_{ETMD} &= \sum\limits_{j,\beta} N_{ETMD,j} \, \Gamma_{ETMD,j,\beta}\\
+ \Gamma_{\rm ICD}  &= \sum\limits_{i,\beta} N_{{\rm ICD},i}  \, \Gamma_{{\rm ICD},i,\beta},\\
+ \Gamma_{\rm ETMD} &= \sum\limits_{j,\beta} N_{{\rm ETMD},j} \, \Gamma_{{\rm ETMD},j,\beta}.
 \end{align}
-Here, $N_{ICD,i}$ and $N_{ETMD,j}$ denote the number of geometrically
+Here, $N_{{\rm ICD},i}$ and $N_{{\rm ETMD},j}$ denote the number of geometrically
 equal pairs and triples in a given cluster structure. The total number of pairs
 reads
-$N_{ICD} = N_{in} \cdot N_{D/E} = N_{Ar} \cdot N_{Xe}
- = \sum\limits_i N_{ICD,i}$ and the number of triples as
-$N_{ETMD} = N_{in} \cdot N_{D/E} (N_{D/E} - 1) = N_{Ar} \cdot N_{Xe} (N_{Xe} - 1)
- = \sum\limits_j N_{ETMD,j}$.
-The number of geometrically equal pairs $N_{ICD,i}$ and $N_{ETMD,j}$
+$N_{{\rm ICD}} = N_{\rm in} \cdot N_{D/E} = N_{\rm Ar} \cdot N_{\rm Xe}
+ = \sum\limits_i N_{{\rm ICD},i}$ and the number of triples is
+$N_{{\rm ETMD}} = N_{\rm in} \cdot N_{D/E} (N_{D/E} - 1) = N_{\rm Ar} \cdot N_{\rm Xe} (N_{\rm Xe} - 1)
+ = \sum\limits_j N_{{\rm ETMD},j}$.
+The numbers of geometrically equivalent pairs $N_{{\rm ICD},i}$ and triples $N_{{\rm ETMD},j}$
 strongly depend on the structure of the cluster. From these relationships
 it can be seen that a higher xenon content in the cluster statistically
-favours the ETMD3 over the ICD.
+favours the ETMD(3) over the ICD.
 
@@
 following Wentzel \cite{Wentzel27}, Feshbach\cite{Feshbach58,Feshbach62}
-and Fano \cite{Fano61}
-
+and Fano,\cite{Fano61}
+%
 \begin{equation}
- \Gamma_{\beta}(E_{res}) = 2\pi \left|
-                           \braket{\Phi_{in}| H_f |\chi_{\beta}}
-                           \right|^2
+ \Gamma_{\beta}(E_{\rm res}) = 2\pi \left|
+                           \braket{\Phi_{\rm in}| H_f |\chi_{\beta}}
+                           \right|^2,
 \end{equation}
-
+%
 can be approximated by its asymptotic behaviour
-
+%
 \begin{equation}
- \Gamma_{ICD,i,\beta} = (2J_{in}+1) \frac{3c^4}{8\pi}
+ \Gamma_{{\rm ICD},i,\beta} = (2J_{\rm in}+1)\, \frac{3c^4}{8\pi}\,
                         \sum\limits_{M_{in}'}
@@
 \end{equation}
-
+%
+and
+%
 \begin{equation}
- \Gamma_{ETMD,j,\beta} = \frac{c}{2\pi} \sum\limits_{m,k,M_{in}',D}
+ \Gamma_{{\rm ETMD},j,\beta} = \frac{c}{2\pi} \sum\limits_{m,k,M_{in}',D}
                         \frac{a_{m,k} \Theta_{m,k}(\alpha_j) \sigma^{(X_E)}(\omega_{vp,\beta})
@@
 \end{equation}
-
+%
 depending on constants ($a_{m,k}=4,2$)
 as well as experimental properties
-of atoms like ionization cross sections
+of atoms, like the ionization cross sections
 $\sigma^{(X_E)}(\omega_{vp,\beta})$, radiative lifetimes of the initially
@@
 of the triple, the direction of the dipole
-transition moment $m$ and an additional counter $k$
+transition moment $m$ and an additional index $k$
 (compare Ref. \cite{Fasshauer13}).
@@
 and data from the literature given in Tables \ref{} and \ref{}.
-These are the same as the ones used in Reference \cite{Fasshauer13}.
+This choice is identical to the one made in Reference \cite{Fasshauer13}.

### 2015-11-02 exp_results.tex

@@
  \centering
+ \includegraphics[width=8.5cm]{pics/figure_icd_12.pdf}
+ \caption{
+Energy spectrum of all coincident secondary (ICD or ETMD) electrons $e_2$ pertaining to primary electrons $e_1$ in the Ar 3s binding energy region.
+Spectra were recorded with a photon energy of $h\nu = 32$~eV.
+Black symbols with error bars show the data points for the smallest clusters measured (`S'), two larger clusters sizes are shown by the red and blue traces.
+For comparison, all spectra are shown area-normalized.
+}
+ \label{figure:icd_12}
+\end{figure}
+
+\begin{figure}[ht]
+ \centering
+ \includegraphics[width=8.5cm]{pics/figure_icd_l.pdf}
+ \caption{
+Energy spectrum of all coincident secondary (ICD or ETMD) electrons $e_2$ for clusters of the same size, but from gas mixtures with different Xe concentration.
+See Figure \protect\ref{figure:icd_12} for details.
+}
+ \label{figure:icd_l}
+\end{figure}
+
+\begin{figure}[ht]
+ \centering
  \includegraphics[width=8.5cm]{pics/figure_ival.pdf}

### 2015-11-02 theo_results.tex

@@
 It is important to remember that the first ICD channel opens at a
-channel opening distance of \unit[7.58]{\AA}. Therefore, in small
-clusters, in which none of the possible Ar-Xe pair distances is larger than
-these \unit[7.58]{\AA}, no ICD can take place. Also, by definition two xenon atoms are
+channel opening distance of \unit[7.58]{\AA}. In small
+clusters, are Ar-Xe pair distances are below that value, therefore 
+no ICD can take place. Also, by definition two Xe atoms are
 required for ETMD(3), hence it cannot occur in clusters with only one xenon atom.
@@
 
-Firstly, we consider two different argon core sizes one consisting
-of 13 and one consisting of 55 atoms with one xenon atom on one of
-the surfaces (see Figure \ref{figure:cluster_3_overview} Panel a)
-for the 55 atom core). The simulated secondary electron spectra are
-shown in Figure \ref{figure:surf} Panel 1.
+Firstly, we consider cluster having an argon core of 13 and 55 atoms with a single xenon
+atom on one of the surfaces (see Figure \ref{figure:cluster_3_overview}a
+for the 55 atom core).
+Secondary electron spectra simulated for these systems are shown in Figure \ref{figure:surf}, top panel.
+%two different argon core sizes one consisting
+%of 13 and one consisting of 55 atoms with one xenon atom on one of
+%the surfaces (see Figure \ref{figure:cluster_3_overview} Panel a)
+%for the 55 atom core). The simulated secondary electron spectra are
+%shown in Figure \ref{figure:surf} Panel 1.
 
@@
  \includegraphics[width=8.2cm]{pics/R_comp.pdf}
- \caption{Panel 1: Simulated electron-electron coincidence spectra
-          for argon clusters
-          consisting of 13 and 55 atoms with on additional xenon atom residing
-          on top of one of the argon surfaces.\\
-          Panel 2: Distribution of Ar-Xe distances $d$ in the studied ArXe
-          clusters. The ICD channels open at \unit[7.58]{\AA} and
-          \unit[36.00]{\AA}, respectively. Hence only pairs at longer interatomic
-          distances than the gray line contribute to the coincidence spectra.
-          The distance distribution of the larger cluster contains larger
-          distances which correspond to peaks at higher kinetic energies of
-          the ICD electron in the coincidence spectra (Panel 1).}
+ \caption{
+ {\it Q: Generell f\"ande ich es gut wenn man die panels immer mit a), b), \dots kennzeichnen k\"onnte.}
+ %
+ Top panel: Simulated electron emission spectra of an Ar 3s vacancy in 
+          argon clusters
+          consisting of 13 and 55 atoms, with an additional xenon atom residing
+          on top of one of the argon surfaces.
+          Bottom panel: Distribution of Ar-Xe distances $d$ in the studied ArXe
+          clusters. The ICD channels to final states involving Xe 5p$_{3/2}^{-1}$ and 
+          5p$_{1/2}^{-1}$ vacancies open at \unit[7.58]{\AA} and
+          \unit[36.00]{\AA}, resp.; the former distance is marked by a vertical dotted line. 
+          Only pairs at longer interatomic
+          distances contribute to the electron emission spectra.
+          Larger Ar-Xe distances, as found in the larger cluster,
+          correspond to features at higher kinetic energies of
+          the ICD electron (top panel).}
  \label{figure:surf}
@@
 
-Because the structures have only one xenon atom ETMD(3) is not possible and
-ICD only is to be expected. Both spectra show several smaller peaks which
-are convoluted into one single peak with a maximum at
-approximately \unit[0.2]{eV}. In comparison to the 13 argon atoms core
-spectrum the 55 argon atoms core spectrum shows
+Because the structures have only one xenon atom, ETMD(3) is not possible
+and only ICD is expected. 
+{\it Q: What about ETMD(2)? Probably it is not important anywhere in the paper?!
+Maybe we should make a general statement about this somewhere early in the discussion.}
+%Both spectra show several smaller peaks which
+%are convoluted into one single peak with a maximum at
+%approximately \unit[0.2]{eV}. 
+%In comparison to the 13 argon atoms core
+%spectrum t
+The spectrum pertaining to the clusters with larger (55 atom) Ar core shows
 signals at higher energies of the secondary electron. These features
-can be explained by analysis of the Ar-Xe distances in the clusters shown
-in Figure \ref{figure:surf} Panel 2. Every different atom pair distance
-yields in a different energy of the secondary electron and only pairs
-with a distance of larger than the channel opening distance
-(dashed, gray line) will contribute
-to the spectrum. The larger the interatomic distance is, the higher is the
+can be explained by looking at the Ar-Xe distances in the clusters, shown
+in the bottom panel of Figure \ref{figure:surf}. 
+%Every different atom pair distance
+%yields in a different energy of the secondary electron and only pairs
+%with a distance of larger than the channel opening distance
+%(dashed, gray line) will contribute
+%to the spectrum. 
+In our model, there is a one-to-one correspondence between interatomic distance $d$ and kinetic energy of the ICD electron.
+The larger the interatomic distance, the higher is the
 kinetic energy of the secondary electron for a given channel.
-Since the 55 argon atom core cluster is larger and therefore
-has Ar-Xe pairs with larger distances its spectrum has signals at higher
-energies as well.
-This effect holds for all clusters.
+%Since the 55 argon atom core cluster is larger and therefore
+%has Ar-Xe pairs with larger distances its spectrum has signals at higher
+%energies as well.
+%This effect holds for all clusters.
+This explains why the ICD spectrum for larger clusters extends to higher energies, and holds for all cluster structures.
 
-For clusters with more than one xenon atom the ETMD(3) channel is possible
-as well. Depending on the positions of the relative positions of the xenon
-atoms in or on the cluster the spectra are expected to be different.
-As an example we therefore discuss the secondary electron spectra of the
-clusters with an 13 argon atoms core and two xenon atoms on different
-surfaces illustrated in Figure \ref{figure:cluster_2_overview} shown in Figure
-\ref{figure:2tops}. In these the xenon content is \unit[13.3]{\%} and therefore
-close to the experimental ones of \unit[10-12]{\%} for the low xenon pressure.
+For clusters with more than one xenon atom, also ETMD(3) is possible.
+Depending on the positions of the xenon
+atoms in or on the cluster, the spectra are expected to be different.
+As an example, we discuss the secondary electron spectra of 
+clusters with a core of 13 argon atoms and two xenon atoms on different
+surfaces. The cluster structures were illustrated in Figure \ref{figure:cluster_2_overview}, 
+simulated spectra are shown in Figure
+\ref{figure:2tops}. Their xenon content is \unit[13.3]{\%} and thus
+close to the experimental one of \unit[10-12]{\%} for the lowes xenon admixture.
 
@@
 
-In all three cases both ICD and ETMD(3) are energetically allowed and the ICD
-spectra are either identical or at least very similar consisting of one
-convoluted peak at approximately \unit[0.2]{eV}. However, the ETMD(3) spectra
-are very sensitive to the relative positioning of the two xenon atoms.
+In all three cases, both ICD and ETMD(3) are energetically allowed. The ICD
+spectra do not change qualitatively by adding the second xenon.
+%either identical or at least very similar to the ones for
+%cluster with a single  consisting of one
+%convoluted peak at approximately \unit[0.2]{eV}. 
+However, the ETMD(3) spectra
+are very sensitive to the relative position of the two xenon atoms.
 Two aspects have to be taken into account: an energy shift of the peak due
 to different charge distances in the final state (i.e. the interatomic Xe-Xe
-distance) and the different decay widths decreasing with $\frac{1}{R^6}$
-between the electron transfer unit and the finally ionized xenon atom.
-The larger the distance between the xenon atoms is, the lower are the energies
-of the secondary electrons and the higher are the decay widths. Therefore a
+distance) and the decrease of the decay width with $R^{-6}$
+between the electron transfer unit and the xenon atom ionized in the final state.
+The larger the distance between the xenon atoms, the lower are the energies
+of the secondary electrons and the smaller are the decay widths. 
+{\it Q: war: `the higher are the decay widths', falschrum, oder?}
+Therefore a
 significant contribution from the ETMD(3) compared to the ICD is only
-to be seen in case of the two xenon atoms residing on two adjacent
-surfaces. The threefold peak structure of the ETMD(3) peak does in contrast to
+seen if the two xenon atoms reside on two adjacent
+surfaces. 
+{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
+The threefold peak structure of the ETMD(3) peak does in contrast to
 the ICD spectrum not stem from different triple structures but from the
@@
 
-For the 55 atoms clusters the xenon content of \unit[10--12]{\%}
-corresponds to six xenon atoms out of the 55 total atoms. These can have
-different relative positions in the cluster. They could either be grouped
-together in one part of the cluster or be evenly distributed in the cluster
-as shown in Figure \ref{figure:cluster_3_overview} Panels b) and c). Their
-ICD and ETMD(3) spectra are shown in Figure \ref{figure:ar_3_6in}.
+For the 55 atom clusters, a xenon content of \unit[10--12]{\%}
+corresponds to six xenon atoms out of a total of 55 atoms. These can have
+different relative positions in the cluster. They can either form a connected 
+group in one part of the cluster or can be evenly distributed in the cluster,
+as shown in Figures \ref{figure:cluster_3_overview}b and \ref{figure:cluster_3_overview}c. The
+ICD and ETMD(3) spectra for these structures are shown in Figure \ref{figure:ar_3_6in}.
 

### 2015-11-04 theo_results.tex
various stylistic changes

@@
 \centering
-\caption{Properties of simulated clusters.
+\caption{Calculated properties of some model clusters. ICD, ETMD, and $\Gamma_{\rm ICD, ETMD}$ are the respective partial and total decay widths in 
 {\it Q: Einheit von $\Gamma$? 
-Ich schlage vor, alle Zerfallsbreiten mit einem festen Exponenten von z.B. 10${-6}$ aufzuschreiben, und diesen wegzulassen. 
-Es w\"urde dadurch sehr viel \"ubersichtlicher, und man sieht gleich welche Zerf\"alle \"uberhaupt wichtig sind.}
+Ich schlage vor, alle Zerfallsbreiten mit einem festen Exponenten von z.B. 10$^{-6}$ aufzuschreiben, und diesen wegzulassen. 
+Die Tabelle w\"urde dadurch \"ubersichtlicher, und man sieht gleich welche Zerf\"alle \"uberhaupt wichtig sind.
+Ich schlage weiterhin vor, statt $\Gamma_{\rm ICD, ETMD}$ das ratio $\Gamma_{\rm ETMD}/\rm total$ zu zeigen (ist glaube ich n\"utzlicher f\"ur die Diskussion).}
 }
@@
 
-For clusters with more than one xenon atom, also ETMD(3) is possible.
-Depending on the positions of the xenon
-atoms in or on the cluster, the spectra are expected to be different.
-As an example, we discuss the secondary electron spectra of 
-clusters with a core of 13 argon atoms and two xenon atoms on different
-surfaces. The cluster structures were illustrated in Figure \ref{figure:cluster_2_overview}, 
-simulated spectra are shown in Figure
-\ref{figure:2tops}. Their xenon content is \unit[13.3]{\%} and thus
-close to the experimental one of \unit[10-12]{\%} for the lowes xenon admixture.
-
-\begin{figure}[h]
+\begin{figure}[ht]
  \centering
  \includegraphics[width=8.5cm]{pics/2tops.pdf}
- \caption{Simulated coincidence spectra of argon clusters consisting of 13
+ \caption{Simulated electron emission spectra of an Ar 3s vacancy in 
+          argon clusters consisting of 13
           argon atoms with 2 additional xenon atoms on top of two different
-          argon surfaces. The ICD and ETMD spectra are shown for all three
-          different relative positionings of the two xenon atoms. In case of
-          the two xenon atoms being close to each other, an ETMD process is
+          argon surfaces. ICD and ETMD spectra are shown for three
+          different relative positions of the two xenon atoms. If 
+          the xenon atoms are close to each other, an ETMD process is
           clearly visible. In the other two cases the spectra are dominated by
-          the corresponding ICD spectrum.}
+          the ICD spectrum.
+          {\it Q: Warum ist in diesen (und vielen anderen) Bildern jedes Label doppelt?}}
  \label{figure:2tops}
 \end{figure}
-
+%
+For clusters with more than one xenon atom, also ETMD(3) is possible.
+Depending on the positions of the xenon atoms relative to each other and to the Ar core, the spectra are expected to be different.
+As an example, we discuss clusters with a core of 13 argon atoms and two xenon atoms on different surfaces. 
+Their xenon content is \unit[13.3]{\%} and thus close to the experimental one of \unit[10-12]{\%} for the lowes xenon admixture.
+The cluster structures were illustrated in Figure \ref{figure:cluster_2_overview}, simulated spectra are shown in Figure \ref{figure:2tops}.
 In all three cases, both ICD and ETMD(3) are energetically allowed. The ICD
@@
 
+\begin{figure}[ht]
+ \centering
+ \includegraphics[width=8.5cm]{pics/ar_3_6in.pdf}
+ \caption{Same as Figure \protect\ref{figure:2tops}, for clusters consisting of
+          55 atoms, 6 out of which are xenon atoms. These are either grouped
+          on one side of the cluster (label `group') or evenly distributed
+          in the cluster interior (label `scattered').}
+ \label{figure:ar_3_6in}
+\end{figure}
+%
 For the 55 atom clusters, a xenon content of \unit[10--12]{\%}
-corresponds to six xenon atoms out of a total of 55 atoms. These can have
-different relative positions in the cluster. They can either form a connected 
-group in one part of the cluster or can be evenly distributed in the cluster,
+corresponds to six xenon atoms out of a total of 55 atoms. These can form a connected 
+group in one part of the cluster or can be evenly distributed,
 as shown in Figures \ref{figure:cluster_3_overview}b and \ref{figure:cluster_3_overview}c. The
@@
 
-\begin{figure}[h]
- \centering
- \includegraphics[width=8.5cm]{pics/ar_3_6in.pdf}
- \caption{Simulated ICD and ETMD electron spectra for clusters consisting of
-          55 atoms out of which 6 are xenon atoms. These are either clustered
-          (group) on one side of the cluster of evenly distributed
-          inside the cluster (scattered). In both cases the ETMD peaks are
-          clearly visible in the spectra.}
- \label{figure:ar_3_6in}
-\end{figure}
-
-For both cases the overall ICD spectra are very similar with concoluted
-peaks at approximately \unit[0.3]{eV}. For the grouped xenon atoms ICD
-signals at slightly higher energies are to be observed from ArXe pairs of
-larger distances du to the different cluster structure. However, the
-significant difference is to be observed in the ETMD(3) spectra. The
-interatomic xenon distance in the grouped xenon is shorther than in the
-cluster with evenly distributed xenon atoms. Hence, the threefold
-peak structure for the cluster with the grouped xenon atoms is seen at
-lower ETMD(3) electron energies than for the cluster with evenly
-distributed xenon atoms. Additionally, the probabilty for an electron
+For both cases the overall ICD spectra are very similar, and show a maximum at a kinetic energy of approximately \unit[0.3]{eV}. 
+In case that the xenon atoms are grouped, the ICD spectrum extends to slightly higher energies, corresponding to ArXe pairs at slightly larger spatial distance.
+A more significant difference is observed in the ETMD(3) spectra. 
+The interatomic xenon distance is shorter in clusters, in which the xenon atoms form a connected group.
+Hence, the triple structure of the ETMD(3) spectrum is seen at lower kinetic energies. 
+Additionally, the probability for an electron
 transfer from a xenon to an argon atom decreases exponentially with the
@@
 atoms as their direct neighbours have a significant contribution to the
-total decay width and the total ETMD(3) decay width for the structure with
-the grouped xenon atoms is lower than the total ETMD(3) decay width of
-the structure with evenly distributed xenon atoms.
+total decay width, and the total ETMD(3) decay width is lower for the structure with
+grouped xenon atoms than for
+the structure with evenly distributed xenon atoms (see Table \ref{table:theo_gammas}).
 
+\begin{figure}[ht]
+ \centering
+ \includegraphics[width=8.5cm]{pics/xe_3_in.pdf}
+ \caption{Same as Figure \protect\ref{figure:2tops}, for argon clusters with
+          one or two xenon atoms in the core of the cluster (55 atoms total). 
+          All ICD and ETMD channels are closed, if the cluster contains only 
+          a single xenon atom. For clusters with two xenon atoms
+          in the core, the first ICD channel is open for some pairs,
+          and additionally ETMD is possible for multiple triples. Due to a
+          different distance distribution compared to the clusters with an argon
+          core (Figure \protect\ref{figure:2tops}), 
+          the ICD peak is shifted to higher kinetic energies.}
+ \label{figure:xe_3_in}
+\end{figure}
+%
 For comparison with the previous assumptions of a xenon core surrounded
-by argon atoms we investigated 13 and 55 atoms clusters with one or two
+by argon atoms we investigated clusters of 13 and 55 atoms with one or two
 xenon atoms in the core. Some of the corresponding
@@
 
-\begin{figure}[h]
- \centering
- \includegraphics[width=8.5cm]{pics/xe_3_in.pdf}
- \caption{Simulated ICD and ETMD electron spectra for argon clusters with
-          one or two atoms in the core of the cluster. In case of the xenon
-          atom inhabiting the central position of the cluster for a 13 atoms
-          cluster (not shown here) and a 55 atoms cluster all channels are closed
-          for all pairs, which leads to no signal. For those clusters with two
-          xenon atoms in the core the first ICD channel is open for some pairs
-          and additionally ETMD is possible for multiple triples. Due to a
-          different distance distribution compared to the clusters with an argon
-          core the ICD peak is shifted to higher kinetic energies.}
- \label{figure:xe_3_in}
-\end{figure}
+%For the clusters with only one xenon atom in the core and the ionization
+%energies used for the simulation of the secondary electron energies
+%all ICD channels are closed. Since the cluster contains only one xenon atom,
+%an ETMD(3) is not possible. Hence there is no signal to be expected at all.
+For a core consisting of two xenon atoms both an ICD and an ETMD(3) spectrum
+can be seen. Compared to the cluster structures involving an argon core, the ICD peak is
+shifted to higher ICD electron energies. 
+Additionally, the ICD and ETMD(3) spectra overlap.
+For ETMD(3), only three of the four different decay channels are
+energetically allowed.
 
-For the clusters with only one xenon atom in the core and the ionization
-energies used for the simulation of the secondary electron energies
-all ICD channels are closed. Since the cluster contains only one xenon atom,
-an ETMD(3) is not possible. Hence there is no signal to be expected at all.
-For a core consisting of two xenon atoms both an ICD and an ETMD(3) spectrum
-can be seen. Compared to the argon core cluster structures the ICD peak is
-shifted to higher ICD electron energies not being in agreement with
-the experimental spectrum. Additionally, the ICD and ETMD(3) spectra overlap.
-In case of the ETMD(3) only three of the four different decay channels are
-anergetically allowed.
-
-Originally, very large argon-xenon clusters were measured experimentally,
-which we approximate by a cluster consisting of 1415 xenon atoms surrounded
-by two complete layers of argon atoms. The spectra are shown in Figure
-\ref{figure:xe_8_lay1}.
-
-\begin{figure}[h]
+\begin{figure}[ht]
  \centering
  \includegraphics[width=8.5cm]{pics/xe_8_1lay.pdf}
- \caption{Simulated ICD and ETMD electron spectra for a large cluster consisting
-          of a xenon core of 1415 atoms surrounded by two complete layers of
-          argon atoms. The ICD and ETMD peak overlap such, that the peak structure
+ \caption{Same as Figure \protect\ref{figure:2tops}, for a large cluster consisting
+          of a xenon core of 1415 atoms surrounded by one complete layer of
+          argon atoms. {\it Q: War: `two complete layers' - bitte \"uberpr\"ufen.} The ICD and ETMD peak overlap such, that the peak structure
           might not be visible.}
@@
 \end{figure}
+%
+In the first experiments very large argon-xenon clusters were measured,\cite{Mucke_phd}
+which we approximate by a cluster consisting of 1415 xenon atoms surrounded
+by one layer of argon atoms. The spectra are shown in Figure
+\ref{figure:xe_8_lay1}.
 
 Compared to the small clusters with a xenon core in Figure \ref{figure:xe_3_in}
-the ICD peak is broadened and shifted to higher ICD electron energies which could be
+the ICD peak is broadened and shifted to higher ICD electron energies which is
 expected due to the larger interatomic Ar-Xe distances in the large cluster and
-the better stabilization of charges (the final state), which was taken care of
-in the input of the simulation.
-The ETMD(3) peak is as well shifted to slightly higher energies allowing for the
-fourth decay channel to open.
+the better stabilization of charges (the final state), which has been taken into account
+in the simulation.
+The ETMD(3) peak is shifted to slightly higher energies as well, which allows opening of the
+fourth decay channel.

### 2015-11-09 intro.tex
remove typo and add ETMD-description again

@@
 charge transfer instead of an energy transfer. 
-%These were termed `Electron Transfer Mediated Decay' 
-% (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
-% which the originally excited site is neutralized by the decay, 
-% and 'exchange ICD' for charge transfer contributions to the 
-% normal ICD amplitude.\cite{santrarev,jahnkesat}
+These were termed `Electron Transfer Mediated Decay' 
+ (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
+ which the originally excited site is neutralized by the decay, 
+ and 'exchange ICD' for charge transfer contributions to the 
+ normal ICD amplitude.\cite{santrarev,jahnkesat}
 We find that both energy and charge transfer induced 
@@
 hydrogen bonds or van-der-Waals bonds. In the case of strong
-(covalent or metallic) bonding, it is inpossible to make a
+(covalent or metallic) bonding, it is impossible to make a
 distinction between ICD and Auger decay.\cite{hergenhahn_review}

### 2015-11-09 theory.tex
exclude ETMD2 from possible decay mechanisms

@@
 start with a decomposition of the system into interaction partners of
-the different decay mechanisms, i.e. pairs (combination of two atoms regardless
+the different, relevant decay mechanisms, i.e. pairs (combination of two atoms regardless
 of their internuclear distance) for the ICD and triples (combinations of three atoms)
-for the ETMD.
-{\em Q: Doubles for ETMD(2) and triples for ETMD(3) ?! Do we make this distinction here?}
+for the ETMD3.
 These atoms do not necessarily need to form bonds between each other or
@@
 Auger process all three atoms coincide, for an ICD process $X_{\rm in}$
-coincides with $X_{D}$ and for an {ETMD}3 process
+coincides with $X_{D}$, for an ETMD2 process $X_D$ and $X_E$ coincide
+and for an {ETMD}3 process
 all ionized states are located on different atoms.
@@
 of all decay mechanisms. In case of the ArXe clusters we only consider
-ICD and ETMD:
+ICD and ETMD3, because the ETMD2 pathway is energetically not accessible:
 

### 2015-11-09 experimental.tex
table of outer valence results improved

@@
 Expansion parameters used for cluster production.
-Here, Xe$_{in}$ is the molar fraction of Xe in the gas mixture before the expansion, $T$ is the nozzle temperature, and $p$ the stagnation pressure.
+Here, Xe$_{\rm in}$ is the molar fraction of Xe in the gas mixture before the expansion, $T$ is the nozzle temperature, and $p$ the stagnation pressure.
 Experiments were done with $d = 80~\mu$m (first two sections) and $d = 100~\mu$m (bottom section) conical nozzles of 15$^\circ$ half opening angle.
-For the mixed clusters, $\langle N_{Ar} \rangle$ and $\langle N_{Xe} \rangle$ refer to cluster sizes arrived at by an expansion of the respective pure gases at the given conditions.
+For the mixed clusters, $\langle N_{\rm Ar} \rangle$ and $\langle N_{\rm Xe} \rangle$ refer to cluster sizes arrived at by an expansion of the respective pure gases at the given conditions.
 These values are calculated as in ref.\ \protect\citenum{hagena1981}.
@@
 \toprule
-  & size label  &  Xe$_{in}$ (\%)  &  $T$ (K)  &  $p$ (bar) & $\langle N_{Ar} \rangle$ & $\langle N_{Xe} \rangle$ \\
+  \multicolumn{2}{r}{size label}  &  Xe$_{\rm in}$ (\%)  &  $T$ (K)  &  $p$ (bar) & $\langle N_{\rm Ar} \rangle$ & $\langle N_{\rm Xe} \rangle$ \\
 %
@@
 % Ar, from Marko 
-Ar &  & --- &  96.5  & 0.35  &  42  &  --- \\
+Ar & (1) & --- &  96.5  & 0.35  &  42  &  --- \\
 % Ar, from Marko 
-Ar &  & --- &  96.5  & 0.67  & 190  &  --- \\
+Ar & (2) & --- &  96.5  & 0.67  & 190  &  --- \\
 % 1103 676, 679
@@
 \midrule
-% 1004 867
-1004, 867 &  & 2.5 &  154   & 2.12  &  920 & 15760\\
+% 1004 867 (32 eV)
+ArXe & XL & 2.5 &  154   & 2.12  &  920 & 15760\\
 % 1004 868
-868 & & 2.5 &  158   & 1.50  &  355 &  6090\\
-% 1004 886
-886 & XL & 2.5 &  161   & 2.41  &  980 & 16770\\
+%868 & & 2.5 &  158   & 1.50  &  355 &  6090\\
+% 1004 886 (17 eV)
+%886 &  & 2.5 &  161   & 2.41  &  980 & 16770\\
 % 1004 858
-858 &  & 5.0 &  149   & 2.50  & 1620 & 27700\\
+%858 &  & 5.0 &  149   & 2.50  & 1620 & 27700\\
 %

### 2015-11-09 theo_results.tex
change theoretical results table -> 10-4eV and ICD percentage

@@
 \centering
-\caption{Calculated properties of some model clusters. ICD, ETMD, and $\Gamma_{\rm ICD, ETMD}$ are the respective partial and total decay widths in 
-{\it Q: Einheit von $\Gamma$? 
-Ich schlage vor, alle Zerfallsbreiten mit einem festen Exponenten von z.B. 10$^{-6}$ aufzuschreiben, und diesen wegzulassen. 
-Die Tabelle w\"urde dadurch \"ubersichtlicher, und man sieht gleich welche Zerf\"alle \"uberhaupt wichtig sind.
-Ich schlage weiterhin vor, statt $\Gamma_{\rm ICD, ETMD}$ das ratio $\Gamma_{\rm ETMD}/\rm total$ zu zeigen (ist glaube ich n\"utzlicher f\"ur die Diskussion).}
+\caption{Calculated properties of some model clusters. ICD, ETMD, and
+are the respective partial decay widths
+in \unit[$10^{-4}$]{eV} and \% ICD gives the ICD percentage of the
+total decay width.
 }
-\begin{tabular}{lrrrccc}
+\begin{tabular}{lrrrccr}
 \toprule
-name                 & Xe atoms & Ar atoms & Xe \% &   ICD                &  ETMD                & $\Gamma_{\rm ICD,ETMD}$\\
+name                 & Xe atoms & Ar atoms & Xe \% & ICD   &  ETMD & \% ICD\\ %$\Gamma_{\rm ICD,ETMD}$\\
 \midrule
-ArXe\_2\_1atom       &      1   &     12   &  7.7  &      0.0             &  0.0                 &     0.0            \\
-ArXe\_3\_1atom       &      1   &     54   &  1.8  &      0.0             &  0.0                 &     0.0            \\ 
-ArXe\_3\_2atom       &      2   &     53   &  3.6  & 3.346$\cdot 10^{-6}$ & 1.666$\cdot 10^{-5}$ & 2.006$\cdot 10^{-5}$ \\
-ArXe\_8\_1layer      &   1415   &    642   & 68.8  & 7.039$\cdot 10^{-4}$ & 2.573$\cdot 10^{-4}$ & 9.612$\cdot 10^{-4}$ \\
+ArXe\_2\_1atom       &      1   &     12   &  7.7  & 0.000 & 0.000 &  --\\ %    0.0            \\
+ArXe\_3\_1atom       &      1   &     54   &  1.8  & 0.000 & 0.000 &  --\\ %    0.0            \\ 
+ArXe\_3\_2atom       &      2   &     53   &  3.6  & 0.033 & 0.167 &  16.7\\ %2.006$\cdot 10^{-5}$ \\
+ArXe\_8\_1layer      &   1415   &    642   & 68.8  & 7.039 & 2.573 &  73.2\\ %9.612$\cdot 10^{-4}$ \\
 \midrule
-XeAr\_2\_surface     &      1   &     13   &  7.1  & 7.922$\cdot 10^{-5}$ & 0.0                  & 7.922$\cdot 10^{-5}$ \\
-XeAr\_2\_edge        &      1   &     13   &  7.1  & 1.320$\cdot 10^{-6}$ & 0.0                  & 1.320$\cdot 10^{-6}$ \\
-XeAr\_2\_vertex      &      1   &     13   &  7.1  & 5.013$\cdot 10^{-6}$ & 0.0                  & 5.013$\cdot 10^{-6}$ \\
-XeAr\_2\_2top        &      2   &     13   & 13.3  & 1.011$\cdot 10^{-5}$ & 1.513$\cdot 10^{-5}$ & 2.523$\cdot 10^{-5}$ \\
-XeAr\_2\_2midtop     &      2   &     13   & 13.3  & 1.588$\cdot 10^{-5}$ & 7.686$\cdot 10^{-7}$ & 1.665$\cdot 10^{-5}$ \\
-XeAr\_2\_2endtop     &      2   &     13   & 13.3  & 1.587$\cdot 10^{-5}$ & 1.772$\cdot 10^{-7}$ & 1.605$\cdot 10^{-5}$ \\
-XeAr\_3\_surface     &      1   &     55   &  1.8  & 6.371$\cdot 10^{-6}$ & 0.0                  & 6.371$\cdot 10^{-6}$ \\
-XeAr\_3\_edge        &      1   &     55   &  1.8  & 4.791$\cdot 10^{-6}$ & 0.0                  & 4.791$\cdot 10^{-6}$ \\
-XeAr\_3\_vertex      &      1   &     55   &  1.8  & 2.701$\cdot 10^{-6}$ & 0.0                  & 2.701$\cdot 10^{-6}$ \\
-XeAr\_3\_edge\_in    &      1   &     54   &  1.8  & 7.708$\cdot 10^{-6}$ & 0.0                  & 7.708$\cdot 10^{-6}$ \\
-XeAr\_3\_vertex\_in  &      1   &     54   &  1.8  & 5.258$\cdot 10^{-6}$ & 0.0                  & 5.258$\cdot 10^{-6}$ \\
-XeAr\_3\_2in         &      2   &     53   &  3.6  & 1.166$\cdot 10^{-5}$ & 5.453$\cdot 10^{-6}$ & 1.711$\cdot 10^{-5}$ \\
-XeAr\_3\_6in         &      6   &     49   & 10.9  & 3.746$\cdot 10^{-5}$ & 4.050$\cdot 10^{-5}$ & 7.796$\cdot 10^{-5}$ \\
-XeAr\_3\_6\_scat     &      6   &     49   & 10.9  & 2.923$\cdot 10^{-5}$ & 6.737$\cdot 10^{-5}$ & 9.660$\cdot 10^{-5}$ \\
+XeAr\_2\_surface     &      1   &     13   &  7.1  & 0.792 & 0.000 & 100.0\\ %7.922$\cdot 10^{-5}$ \\
+XeAr\_2\_edge        &      1   &     13   &  7.1  & 0.013 & 0.000 & 100.0\\ %1.320$\cdot 10^{-6}$ \\
+XeAr\_2\_vertex      &      1   &     13   &  7.1  & 0.050 & 0.000 & 100.0\\ %5.013$\cdot 10^{-6}$ \\
+XeAr\_2\_2top        &      2   &     13   & 13.3  & 0.101 & 0.151 &  40.1\\ %2.523$\cdot 10^{-5}$ \\
+XeAr\_2\_2midtop     &      2   &     13   & 13.3  & 0.159 & 0.008 &  95.4\\ %1.665$\cdot 10^{-5}$ \\
+XeAr\_2\_2endtop     &      2   &     13   & 13.3  & 0.159 & 0.002 &  98.9\\ %1.605$\cdot 10^{-5}$ \\
+XeAr\_3\_surface     &      1   &     55   &  1.8  & 0.064 & 0.000 & 100.0\\ %6.371$\cdot 10^{-6}$ \\
+XeAr\_3\_edge        &      1   &     55   &  1.8  & 0.048 & 0.000 & 100.0\\ %4.791$\cdot 10^{-6}$ \\
+XeAr\_3\_vertex      &      1   &     55   &  1.8  & 0.027 & 0.000 & 100.0\\ %2.701$\cdot 10^{-6}$ \\
+XeAr\_3\_edge\_in    &      1   &     54   &  1.8  & 0.077 & 0.000 & 100.0\\ %7.708$\cdot 10^{-6}$ \\
+XeAr\_3\_vertex\_in  &      1   &     54   &  1.8  & 0.053 & 0.000 & 100.0\\ %5.258$\cdot 10^{-6}$ \\
+XeAr\_3\_2in         &      2   &     53   &  3.6  & 0.117 & 0.055 &  68.1\\ %1.711$\cdot 10^{-5}$ \\
+XeAr\_3\_6in         &      6   &     49   & 10.9  & 0.375 & 0.405 &  48.1\\ %7.796$\cdot 10^{-5}$ \\
+XeAr\_3\_6\_scat     &      6   &     49   & 10.9  & 0.292 & 0.674 &  30.3\\ %9.660$\cdot 10^{-5}$ \\
 \bottomrule

### 2015-11-09 exp_results.tex

@@
 All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV).
-Binding energies $E_b$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit.
-The experimental Xe content of the clusters always is higher than in the original gas mixture (see Tab.\ \protect\ref{tab:cluster}).
-It was determined from the areas of the respective photolines, corrected by the respective atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}.
+Binding energies $\EB$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit.
+The experimental Xe content of the clusters (Xe$_{\rm cl}$) always is higher than in the original gas mixture (Xe$_{\rm in}$).
+Xe$_{\rm cl}$ was determined from the areas of the respective photolines, corrected by the respective atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}.
 Uncertainties are estimated as 3\,\% for the Xe content and 0.05~eV for the binding energies.
-Labels given in the first column refer to the expansion parameters in Tab.\ \protect\ref{tab:cluster}.
-$E_b$ and $w$ are in eV, $A$ is in \%.
-The binding energies can be compared to atomic values of 15.82~eV, 13.43~eV and 12.13~eV for Ar 3p and Xe 5p.
+$\EB$ and $w$ are in eV.
+The theoretical Ar 3p binding energy, averaged over fine structure, amounts to 15.27 eV.
 \label{tab:valence} }
-\begin{tabular}{ l c c c c c c}
+\begin{tabular}{ l c c c c c c c c}
 %
 \toprule
-  label & $E_b$(Ar 3p) & $w$(Ar 3p) & $E_b$(Xe 5p$_{1/2}$) &  $E_b$(Xe 5p$_{3/2}$) & $w$(Xe 5p$_{3/2}$)  &  $A$(Xe) \\
+ \multicolumn{2}{r}{size} &  Xe$_{in}$& $\EB$ & $w$& \multicolumn{2}{c}{$\EB$}  & $w$ &  Xe$_{cl}$ \\
 %
+ \multicolumn{2}{r}{(label)}&  (\%) & (Ar 3p) & (Ar 3p) & (Xe 5p$_{1/2}$) &  (Xe 5p$_{3/2}$) & (Xe 5p$_{3/2}$)  &  (\%) \\
 \midrule
 % Ar, from Marko
- Ar (1) &  15.3  &  1.1 & & & &  \\
+ Ar & (1) &&  15.3  &  1.1 & & & &  \\
 % Ar, from Marko 
- Ar (2) &  15.1  &  1.3 & & & &  \\
+ Ar & (2) &&  15.1  &  1.3 & & & &  \\
 %
@@
 % 1103 676, 679
- (a) & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
+ ArXe & S &1.2 & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
 % 1103 670
- (b) & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
+ ArXe & M &1.2 & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
 % 1103 671
- (c) & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
+ ArXe & L &1.2 & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
 % 1103 663
- (d) & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
+ ArXe & S &3.0 & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
 % 1103 640
- (e) & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
+ ArXe & M &5.0 & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
 % 0506 
-Xe (1) & & & 12.76 & 11.19 & 1.18 & 100\\
+ Xe &  & & & & 12.76 & 11.19 & 1.18 & 100\\
 %
@@
 %  1004  886  (UHe, c.g. + roi values)
- 886 & 15.15 & 1.3 & 12.59 & 11.01 & 1.24 & 19\\
+ ArXe & XL &2.5 & 15.15 & 1.3 & 12.59 & 11.01 & 1.24 & 19\\
+%
+\midrule
+%
+ Ar, Xe & th.\cite{Fasshauer13} && 14.76|15.53 && 12.53 & 10.83 &&\\
+%
+ \multicolumn{2}{r}{atomic\cite{velchev,sansonetti}} && 15.82 && 13.43 & 12.13 &&\\
+%
 \bottomrule

### 2015-11-09 theo_results.tex
rm mistakes and use some old formulations containing much more detailed information

@@
 channel opening distance of \unit[7.58]{\AA}. In small
-clusters, are Ar-Xe pair distances are below that value, therefore 
+clusters, Ar-Xe pair distances are below that value, therefore 
 no ICD can take place. Also, by definition two Xe atoms are
@@
 We will now discuss features of several structures, using selected examples.
-
 Firstly, we consider cluster having an argon core of 13 and 55 atoms with a single xenon
@@
 and only ICD is expected. 
-{\it Q: What about ETMD(2)? Probably it is not important anywhere in the paper?!
-Maybe we should make a general statement about this somewhere early in the discussion.}
 %Both spectra show several smaller peaks which
@@
 in the bottom panel of Figure \ref{figure:surf}. 
-%Every different atom pair distance
-%yields in a different energy of the secondary electron and only pairs
-%with a distance of larger than the channel opening distance
-%(dashed, gray line) will contribute
-%to the spectrum. 
-In our model, there is a one-to-one correspondence between interatomic distance $d$ and kinetic energy of the ICD electron.
+Every different atom pair distance
+yields in a different energy of the secondary electron and only pairs
+with a distance of larger than the channel opening distance
+(dashed, gray line) will contribute
+to the spectrum. 
+%In our model, there is a one-to-one correspondence between interatomic distance $d$ and kinetic energy of the ICD electron.
 The larger the interatomic distance, the higher is the
 kinetic energy of the secondary electron for a given channel.
-%Since the 55 argon atom core cluster is larger and therefore
-%has Ar-Xe pairs with larger distances its spectrum has signals at higher
+Since the 55 argon atom core cluster is larger and therefore
+has Ar-Xe pairs with larger distances its spectrum is extended to
+higher energies.
 %energies as well.
-%This effect holds for all clusters.
-This explains why the ICD spectrum for larger clusters extends to higher energies, and holds for all cluster structures.
+This effect holds for all clusters.
+%This explains why the ICD spectrum for larger clusters extends to higher energies, and holds for all cluster structures.
 
@@
 between the electron transfer unit and the xenon atom ionized in the final state.
-The larger the distance between the xenon atoms, the lower are the energies
+The larger the distance between the xenon atoms, the higher are the energies
 of the secondary electrons and the smaller are the decay widths. 
-{\it Q: war: `the higher are the decay widths', falschrum, oder?}
-Therefore a
+Therefore, a
 significant contribution from the ETMD(3) compared to the ICD is only

### 2015-11-09 theo_results.tex
tweek theoretical pictures to show up in the text

@@
 %
-\begin{table}[h]
+\begin{table*}[h]
 \centering
@@
 \label{table:theo_gammas}
-\end{table}
+\end{table*}
 %
@@
 %
-%In the investigated structures several different aspects have to be
-%taken into account which we will discuss separately if possible
-%on selected structures.
-
-We will now discuss features of several structures, using selected examples.
-Firstly, we consider cluster having an argon core of 13 and 55 atoms with a single xenon
-atom on one of the surfaces (see Figure \ref{figure:cluster_3_overview}a
-for the 55 atom core).
-Secondary electron spectra simulated for these systems are shown in Figure \ref{figure:surf}, top panel.
-%two different argon core sizes one consisting
-%of 13 and one consisting of 55 atoms with one xenon atom on one of
-%the surfaces (see Figure \ref{figure:cluster_3_overview} Panel a)
-%for the 55 atom core). The simulated secondary electron spectra are
-%shown in Figure \ref{figure:surf} Panel 1.
-
-\begin{figure}[ht]
+\begin{figure}[H]
  \centering
- \includegraphics[width=8.5cm]{pics/surf.pdf}\\
- \includegraphics[width=8.2cm]{pics/R_comp.pdf}
+ \includegraphics[width=8.0cm]{pics/surf.pdf}\\
+ \includegraphics[width=8.0cm]{pics/R_comp.pdf}
  \caption{
@@
 \end{figure}
+
+%In the investigated structures several different aspects have to be
+%taken into account which we will discuss separately if possible
+%on selected structures.
+
+We will now discuss features of several structures, using selected examples.
+Firstly, we consider cluster having an argon core of 13 and 55 atoms with a single xenon
+atom on one of the surfaces (see Figure \ref{figure:cluster_3_overview}a
+for the 55 atom core).
+Secondary electron spectra simulated for these systems are shown in Figure \ref{figure:surf}, top panel.
+%two different argon core sizes one consisting
+%of 13 and one consisting of 55 atoms with one xenon atom on one of
+%the surfaces (see Figure \ref{figure:cluster_3_overview} Panel a)
+%for the 55 atom core). The simulated secondary electron spectra are
+%shown in Figure \ref{figure:surf} Panel 1.
 

### 2015-11-11 exp_results.tex
started discussion of valence spectra, minor edits in introduction, theory results

@@
-\section{Experimental Results}
+\section{Experimental Results
+\label{sec:exp_results}}
 
@@
 Binding energies $\EB$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit.
-The experimental Xe content of the clusters (Xe$_{\rm cl}$) always is higher than in the original gas mixture (Xe$_{\rm in}$).
-Xe$_{\rm cl}$ was determined from the areas of the respective photolines, corrected by the respective atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}.
+The Xe content of the clusters (Xe$_{\rm cl}$) always is higher than in the original gas mixture (Xe$_{\rm in}$).
+Xe$_{\rm cl}$ was determined from the areas of the respective photolines, corrected by their atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}.
+$\EB$ and $w$ are in eV.
 Uncertainties are estimated as 3\,\% for the Xe content and 0.05~eV for the binding energies.
-$\EB$ and $w$ are in eV.
-The theoretical Ar 3p binding energy, averaged over fine structure, amounts to 15.27 eV.
+For reference, the row labelled `(th.)' gives the binding energies used in the simulations of this paper (same as in Ref.
+\citenum{Fasshauer13}), and the last row their atomic counterparts.
 \label{tab:valence} }
@@
 \toprule
- \multicolumn{2}{r}{size} &  Xe$_{in}$& $\EB$ & $w$& \multicolumn{2}{c}{$\EB$}  & $w$ &  Xe$_{cl}$ \\
+ \multicolumn{2}{r}{size} &  Xe$_{in}$& $\EB$ & $w$& \multicolumn{2}{c}{$\EB$}  & $w$ &  Xe$_{\rm cl}$ \\
 %
@@
 %
- Ar, Xe & th.\cite{Fasshauer13} && 14.76|15.53 && 12.53 & 10.83 &&\\
+ Ar, Xe & (th.) && 14.76|15.53 && 12.53 & 10.83 &&\\
 %
- \multicolumn{2}{r}{atomic\cite{velchev,sansonetti}} && 15.82 && 13.43 & 12.13 &&\\
+ \multicolumn{2}{l}{(atomic)\cite{velchev,sansonetti}} && 15.76|15.94 && 13.43 & 12.13 &&\\
 %
@@
 Panel a) shows the outer valence region of homogeneous Ar and Xe clusters, respectively (see text for details).
-The two lower panels show the spectra of the mixed species of different size.
+The two lower panels show spectra of the mixed species with different mean size.
 Sharp lines marked `m' result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states.
@@
 \end{figure}
+
+Figure \ref{figure:oval1} shows the outer valence spectra of small and large ArXe clusters, compared to clusters of the pure gases.
+Differences are seen in particular for the Ar component.
+In pure Ar clusters, outer valence photoionization leads to a broad band, caused both by spin-orbit coupling and crystal field splitting.
+The relative importance of these two mechanisms remains under debate.\cite{hergenhahnprb,rolles} At the particular photon energy selected here, atop of this band a sharp feature is also visible (in Figure \ref{figure:oval1} at a kinetic energy of about 1.8 eV).
+For larger clusters, this shows a dispersion characteristic for photoionization of crystalline bulk matter.\cite{foerstel_arg1_2010,foerstel_arg2_2011}
 

### 2015-11-11 experimental.tex
tweek theoretical pictures to show up in the text
started discussion of valence spectra, minor edits in introduction, theory results

@@
 Separate containers for the two gases were filled up to pressures suitable for producing a certain mixing ratio. The gases were then allowed to mix before the expansion. 
-Expansion parameters and mean cluster sizes, according to an empirical model, are given in Tab.\ \ref{tab:cluster}. 
-We note that currently no empirical model for cluster sizes in a heterogeneous gas expansion exists. 
-We therefore can only give the mean size for a pure jet of one or the other gas at the given conditions.
+Expansion parameters and mean cluster sizes are given in Table \ref{tab:cluster}. 
+Currently, no model to predict cluster sizes in a heterogeneous gas expansion exists. 
+We therefore can only give the mean size for a pure jet of one or the other gas at the given conditions, which we have derived according to an empirical scaling law.\cite{hagena1981} 
+We note that recent analyses of photoionization spectra suggests that  mean sizes arrived at by scaling laws are smaller than the actual size, at least for rare gas clusters.\cite{bergersen,hergenhahnprb,foerstel_arg2_2011}
 
@@
 Electrons were detected by a short `magnetic bottle' time-of-flight spectrometer, that has been described earlier.\cite{mucke_review} 
-Data were recorded in two different beamtimes at the UE112-PGM-1 (small and medium sized clusters, first two sections in Tab.\ \ref{tab:cluster}) and at the TGM-4 beamline (large clusters, last section in Tab.\ \ref{tab:cluster}).
+Data were recorded in two different beamtimes at the UE112-PGM-1 (small and medium sized clusters, first two sections in Table \ref{tab:cluster}) and at the TGM-4 beamline (large clusters, last section in Table \ref{tab:cluster}).
 Linearly, horizontally polarized radiation was used. 

### 2015-11-11 theo_results.tex
started discussion of valence spectra, minor edits in introduction, theory results

--- 2015-11-09 theo_results.tex
@@
 \centering
-\caption{Calculated properties of some model clusters. ICD, ETMD, and
-are the respective partial decay widths
-in \unit[$10^{-4}$]{eV} and \% ICD gives the ICD percentage of the
-total decay width.
+\caption{Calculated properties of some model clusters. ICD, ETMD, and $\Gamma_{\rm ICD, ETMD}$ are the respective partial and total decay widths in 
+{\it Q: Einheit von $\Gamma$? 
+Ich schlage vor, alle Zerfallsbreiten mit einem festen Exponenten von z.B. 10$^{-6}$ aufzuschreiben, und diesen wegzulassen. 
+Die Tabelle w\"urde dadurch \"ubersichtlicher, und man sieht gleich welche Zerf\"alle \"uberhaupt wichtig sind.
+Ich schlage weiterhin vor, statt $\Gamma_{\rm ICD, ETMD}$ das ratio $\Gamma_{\rm ETMD}/\rm total$ zu zeigen (ist glaube ich n\"utzlicher f\"ur die Diskussion).}
 }
-\begin{tabular}{lrrrccr}
+\begin{tabular}{lrrrccc}
 \toprule
-name                 & Xe atoms & Ar atoms & Xe \% & ICD   &  ETMD & \% ICD\\ %$\Gamma_{\rm ICD,ETMD}$\\
+name                 & Xe atoms & Ar atoms & Xe \% &   ICD                &  ETMD                & $\Gamma_{\rm ICD,ETMD}$\\
 \midrule
-ArXe\_2\_1atom       &      1   &     12   &  7.7  & 0.000 & 0.000 &  --\\ %    0.0            \\
-ArXe\_3\_1atom       &      1   &     54   &  1.8  & 0.000 & 0.000 &  --\\ %    0.0            \\ 
-ArXe\_3\_2atom       &      2   &     53   &  3.6  & 0.033 & 0.167 &  16.7\\ %2.006$\cdot 10^{-5}$ \\
-ArXe\_8\_1layer      &   1415   &    642   & 68.8  & 7.039 & 2.573 &  73.2\\ %9.612$\cdot 10^{-4}$ \\
+ArXe\_2\_1atom       &      1   &     12   &  7.7  &      0.0             &  0.0                 &     0.0            \\
+ArXe\_3\_1atom       &      1   &     54   &  1.8  &      0.0             &  0.0                 &     0.0            \\ 
+ArXe\_3\_2atom       &      2   &     53   &  3.6  & 3.346$\cdot 10^{-6}$ & 1.666$\cdot 10^{-5}$ & 2.006$\cdot 10^{-5}$ \\
+ArXe\_8\_1layer      &   1415   &    642   & 68.8  & 7.039$\cdot 10^{-4}$ & 2.573$\cdot 10^{-4}$ & 9.612$\cdot 10^{-4}$ \\
 \midrule
-XeAr\_2\_surface     &      1   &     13   &  7.1  & 0.792 & 0.000 & 100.0\\ %7.922$\cdot 10^{-5}$ \\
-XeAr\_2\_edge        &      1   &     13   &  7.1  & 0.013 & 0.000 & 100.0\\ %1.320$\cdot 10^{-6}$ \\
-XeAr\_2\_vertex      &      1   &     13   &  7.1  & 0.050 & 0.000 & 100.0\\ %5.013$\cdot 10^{-6}$ \\
-XeAr\_2\_2top        &      2   &     13   & 13.3  & 0.101 & 0.151 &  40.1\\ %2.523$\cdot 10^{-5}$ \\
-XeAr\_2\_2midtop     &      2   &     13   & 13.3  & 0.159 & 0.008 &  95.4\\ %1.665$\cdot 10^{-5}$ \\
-XeAr\_2\_2endtop     &      2   &     13   & 13.3  & 0.159 & 0.002 &  98.9\\ %1.605$\cdot 10^{-5}$ \\
-XeAr\_3\_surface     &      1   &     55   &  1.8  & 0.064 & 0.000 & 100.0\\ %6.371$\cdot 10^{-6}$ \\
-XeAr\_3\_edge        &      1   &     55   &  1.8  & 0.048 & 0.000 & 100.0\\ %4.791$\cdot 10^{-6}$ \\
-XeAr\_3\_vertex      &      1   &     55   &  1.8  & 0.027 & 0.000 & 100.0\\ %2.701$\cdot 10^{-6}$ \\
-XeAr\_3\_edge\_in    &      1   &     54   &  1.8  & 0.077 & 0.000 & 100.0\\ %7.708$\cdot 10^{-6}$ \\
-XeAr\_3\_vertex\_in  &      1   &     54   &  1.8  & 0.053 & 0.000 & 100.0\\ %5.258$\cdot 10^{-6}$ \\
-XeAr\_3\_2in         &      2   &     53   &  3.6  & 0.117 & 0.055 &  68.1\\ %1.711$\cdot 10^{-5}$ \\
-XeAr\_3\_6in         &      6   &     49   & 10.9  & 0.375 & 0.405 &  48.1\\ %7.796$\cdot 10^{-5}$ \\
-XeAr\_3\_6\_scat     &      6   &     49   & 10.9  & 0.292 & 0.674 &  30.3\\ %9.660$\cdot 10^{-5}$ \\
+XeAr\_2\_surface     &      1   &     13   &  7.1  & 7.922$\cdot 10^{-5}$ & 0.0                  & 7.922$\cdot 10^{-5}$ \\
+XeAr\_2\_edge        &      1   &     13   &  7.1  & 1.320$\cdot 10^{-6}$ & 0.0                  & 1.320$\cdot 10^{-6}$ \\
+XeAr\_2\_vertex      &      1   &     13   &  7.1  & 5.013$\cdot 10^{-6}$ & 0.0                  & 5.013$\cdot 10^{-6}$ \\
+XeAr\_2\_2top        &      2   &     13   & 13.3  & 1.011$\cdot 10^{-5}$ & 1.513$\cdot 10^{-5}$ & 2.523$\cdot 10^{-5}$ \\
+XeAr\_2\_2midtop     &      2   &     13   & 13.3  & 1.588$\cdot 10^{-5}$ & 7.686$\cdot 10^{-7}$ & 1.665$\cdot 10^{-5}$ \\
+XeAr\_2\_2endtop     &      2   &     13   & 13.3  & 1.587$\cdot 10^{-5}$ & 1.772$\cdot 10^{-7}$ & 1.605$\cdot 10^{-5}$ \\
+XeAr\_3\_surface     &      1   &     55   &  1.8  & 6.371$\cdot 10^{-6}$ & 0.0                  & 6.371$\cdot 10^{-6}$ \\
+XeAr\_3\_edge        &      1   &     55   &  1.8  & 4.791$\cdot 10^{-6}$ & 0.0                  & 4.791$\cdot 10^{-6}$ \\
+XeAr\_3\_vertex      &      1   &     55   &  1.8  & 2.701$\cdot 10^{-6}$ & 0.0                  & 2.701$\cdot 10^{-6}$ \\
+XeAr\_3\_edge\_in    &      1   &     54   &  1.8  & 7.708$\cdot 10^{-6}$ & 0.0                  & 7.708$\cdot 10^{-6}$ \\
+XeAr\_3\_vertex\_in  &      1   &     54   &  1.8  & 5.258$\cdot 10^{-6}$ & 0.0                  & 5.258$\cdot 10^{-6}$ \\
+XeAr\_3\_2in         &      2   &     53   &  3.6  & 1.166$\cdot 10^{-5}$ & 5.453$\cdot 10^{-6}$ & 1.711$\cdot 10^{-5}$ \\
+XeAr\_3\_6in         &      6   &     49   & 10.9  & 3.746$\cdot 10^{-5}$ & 4.050$\cdot 10^{-5}$ & 7.796$\cdot 10^{-5}$ \\
+XeAr\_3\_6\_scat     &      6   &     49   & 10.9  & 2.923$\cdot 10^{-5}$ & 6.737$\cdot 10^{-5}$ & 9.660$\cdot 10^{-5}$ \\
 \bottomrule
@@
 are very sensitive to the relative position of the two xenon atoms.
-Two aspects have to be taken into account: an energy shift of the peak due
+Two aspects have to be taken into account: an energy shift of the peaks due
 to different charge distances in the final state (i.e. the interatomic Xe-Xe
-distance) and the decrease of the decay width with $R^{-6}$
+distance) and the decrease of the decay width with $R^{-6}$, $R$ being the distance
 between the electron transfer unit and the xenon atom ionized in the final state.
@@
 {\it Q: war: `the higher are the decay widths', falschrum, oder?}
-Therefore a
-significant contribution from the ETMD(3) compared to the ICD is only
+Therefore, a
+significant contribution from ETMD(3) compared to ICD is only
 seen if the two xenon atoms reside on two adjacent
 surfaces. 
-{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
-The threefold peak structure of the ETMD(3) peak does in contrast to
-the ICD spectrum not stem from different triple structures but from the
-four different decay channels for one triple structure.
+%{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
+The three energetically separated peaks in the ETMD(3) spectrum pertain to different combinations of the Xe 5p$_j^{-1}$ vacancy states, which have a substantial fine-structure splitting (see \ref{sec:exp_results}).
+%
+%The threefold peak structure of the ETMD(3) peak does in contrast to
+%the ICD spectrum not stem from different triple structures but from the
+%four different decay channels for one triple structure.
 
@@
 in the simulation.
-The ETMD(3) peak is shifted to slightly higher energies as well, which allows opening of the
-fourth decay channel.
+The ETMD(3) peak is shifted to slightly higher energies as well. This allows opening of the
+fourth decay channel, pertaining to Xe 5p$_{1/2}^{-1}$ Ar 3p$_{1/2}^{-1}$ final states.

### 2015-11-12 theo_results.tex

--- 2015-11-09 theo_results.tex
@@
 Therefore, a
-significant contribution from the ETMD(3) compared to the ICD is only
+significant contribution from ETMD(3) compared to ICD is only
 seen if the two xenon atoms reside on two adjacent
 surfaces. 
-{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
-The threefold peak structure of the ETMD(3) peak does in contrast to
-the ICD spectrum not stem from different triple structures but from the
-four different decay channels for one triple structure.
+%{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
+The three energetically separated peaks in the ETMD(3) spectrum pertain to different combinations of the Xe 5p$_j^{-1}$ vacancy states, which have a substantial fine-structure splitting (see \ref{sec:exp_results}).
+%
+%The threefold peak structure of the ETMD(3) peak does in contrast to
+%the ICD spectrum not stem from different triple structures but from the
+%four different decay channels for one triple structure.
 

### 2015-11-12 exp_results.tex
minor text edits

@@
 Uncertainties are estimated as 3\,\% for the Xe content and 0.05~eV for the binding energies. 
-For reference, the row labelled `(th.)' gives the binding energies used in the simulations of this paper (same as in Ref.
-\citenum{Fasshauer13}), and the last row their atomic counterparts.
+For reference, the row labelled `(th.)' gives the binding energies used in the simulations of this paper (same as in Ref. \citenum{Fasshauer13}), and the last row their atomic counterparts. 
+Values for Ar 3p in these two rows refer to the fine structure states.
 \label{tab:valence} }
@@
 Sharp lines marked `m' result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states. 
-Labels in panels b) and c) give the Xe content in the expanding gas mixture, which is lower then the Xe content observed in the heterogeneous clusters.
-The photon energy used was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
+Labels in panels b) and c) give the Xe content in the expanding gas mixture (Xe$_{\rm in}$), which is lower then the Xe content observed in the heterogeneous clusters (Xe$_{\rm cl}$). 
+The photon energy was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
 }
@@
  \caption{
-Outer valence photoelectron spectra of mixed Ar-Xe clusters from gas mixtures with different Xe concentration. See Fig.\ \ref{figure:oval1} and text for details.
+Outer valence photoelectron spectra of mixed Ar-Xe clusters from gas mixtures with different Xe concentration. 
+See Fig.\ \ref{figure:oval1} and text for details.
 }
@@
 In pure Ar clusters, outer valence photoionization leads to a broad band, caused both by spin-orbit coupling and crystal field splitting. 
-The relative importance of these two mechanisms remains under debate.\cite{hergenhahnprb,rolles} At the particular photon energy selected here, atop of this band a sharp feature is also visible (in Figure \ref{figure:oval1} at a kinetic energy of about 1.8 eV).
-For larger clusters, this shows a dispersion characteristic for photoionization of crystalline bulk matter.\cite{foerstel_arg1_2010,foerstel_arg2_2011}
+The relative importance of these two mechanisms remains under debate.\cite{hergenhahnprb,rolles} 
+For larger clusters (e.g.
+$\langle N\rangle = 190$, black trace), the maximum at low binding energies becomes more pronounced, and is identified with emission from the cluster interior.\cite{hergenhahnprb,rolles}
+At the particular photon energy selected here, atop of this band a sharp feature is also visible (in Figure \ref{figure:oval1} at a kinetic energy of about 1.8 eV). 
+For larger clusters (above $\langle N\rangle \approx 100$), it shows a dispersion characteristic for photoemission of crystalline bulk matter.\cite{foerstel_arg1_2010,foerstel_arg2_2011} 
+Ar 3p spectra from the mixed clusters show neither of these traits.
+For smaller clusters (panel c), their shape is rather reminiscent of
 

### 2015-11-12 theo_results.tex
minor text edits

@@
 \centering
-\caption{Calculated properties of some model clusters. ICD, ETMD, and
+\caption{Calculated properties of some model clusters. Columns `ICD' and `ETMD'
 are the respective partial decay widths
-in \unit[$10^{-4}$]{eV} and \% ICD gives the ICD percentage of the
+in \unit[$10^{-4}$]{eV}, and `\% ICD' gives the percentage of ICD in the
 total decay width.
@@
 \toprule
-name                 & Xe atoms & Ar atoms & Xe \% & ICD   &  ETMD & \% ICD\\ %$\Gamma_{\rm ICD,ETMD}$\\
+name                 & Xe atoms & Ar atoms & Xe$_{\rm cl}$ \% & ICD   &  ETMD & \% ICD\\ %$\Gamma_{\rm ICD,ETMD}$\\
 \midrule
@@
           Larger Ar-Xe distances, as found in the larger cluster,
-          correspond to features at higher kinetic energies of
+          correspond to features at higher kinetic energy of
           the ICD electron (top panel).}

### 2015-12-22 exp_results.tex
discussion of valence spectra

@@
 Binding energies $\EB$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit. 
-The Xe content of the clusters (Xe$_{\rm cl}$) always is higher than in the original gas mixture (Xe$_{\rm in}$). 
-Xe$_{\rm cl}$ was determined from the areas of the respective photolines, corrected by their atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}. 
-$\EB$ and $w$ are in eV. 
-Uncertainties are estimated as 3\,\% for the Xe content and 0.05~eV for the binding energies. 
+The average Xe content of the cluster ensemble, Xe$_{\rm cl}$, was determined from the areas of the respective photolines, corrected by their atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}.
+Uncertainties are estimated as $\pm$3\,\% for the Xe content and 0.05~eV for the binding energies. 
 For reference, the row labelled `(th.)' gives the binding energies used in the simulations of this paper (same as in Ref. \citenum{Fasshauer13}), and the last row their atomic counterparts. 
@@
 \toprule
- \multicolumn{2}{r}{size} &  Xe$_{in}$& $\EB$ & $w$& \multicolumn{2}{c}{$\EB$}  & $w$ &  Xe$_{\rm cl}$ \\
+ \multicolumn{2}{r}{size} &  Xe$_{in}$& $\EB$ (eV)& $w$ (eV)& \multicolumn{2}{c}{$\EB$ (eV)}  & $w$ (eV) &  Xe$_{\rm cl}$ \\
 %
- \multicolumn{2}{r}{(label)}&  (\%) & (Ar 3p) & (Ar 3p) & (Xe 5p$_{1/2}$) &  (Xe 5p$_{3/2}$) & (Xe 5p$_{3/2}$)  &  (\%) \\
+ \multicolumn{2}{r}{(label)}&  (\%) & Ar 3p & Ar 3p & Xe 5p$_{1/2}$ &  Xe 5p$_{3/2}$ & Xe 5p$_{3/2}$  &  (\%) \\
 \midrule
@@
 %
- Ar, Xe & (th.) && 14.76|15.53 && 12.53 & 10.83 &&\\
+ Ar, Xe & (th.) && 14.76|15.54 && 12.53 & 10.83 &&\\
 %
@@
 
+\subsection{Outer valence spectra}
+%
 \begin{figure}[ht]
@@
 Outer valence photoelectron spectra of mixed Ar-Xe clusters, in comparison to the pure species. 
-Panel a) shows the outer valence region of homogeneous Ar and Xe clusters, respectively (see text for details). 
+(a) shows the outer valence region of homogeneous Ar and Xe clusters, respectively (see text for details). 
 The two lower panels show spectra of the mixed species with different mean size. 
 Sharp lines marked `m' result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states. 
-Labels in panels b) and c) give the Xe content in the expanding gas mixture (Xe$_{\rm in}$), which is lower then the Xe content observed in the heterogeneous clusters (Xe$_{\rm cl}$). 
+Labels in (b) and (c) give the Xe content in the expanding gas mixture (Xe$_{\rm in}$), which is lower then the Xe content observed in the heterogeneous clusters (Xe$_{\rm cl}$). 
 The photon energy was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
@@
 Outer valence photoelectron spectra of mixed Ar-Xe clusters from gas mixtures with different Xe concentration. 
+For better visibility, a scaling factor is applied to the Xe part of the spectrum in (a).
 See Fig.\ \ref{figure:oval1} and text for details.
@@
 Figure \ref{figure:oval1} shows the outer valence spectra of small and large ArXe clusters, compared to clusters of the pure gases. 
+Qualitatively similar spectra have been published without detailed discussion in Ref.\ \citenum{lindblad}.
 Differences are seen in particular for the Ar component. 
 In pure Ar clusters, outer valence photoionization leads to a broad band, caused both by spin-orbit coupling and crystal field splitting. 
-The relative importance of these two mechanisms remains under debate.\cite{hergenhahnprb,rolles} 
+The relative importance of these two mechanisms remains under debate.\cite{hergenhahnprb,rolles,foerstel_arg1_2010} 
 For larger clusters (e.g.
@@
 For larger clusters (above $\langle N\rangle \approx 100$), it shows a dispersion characteristic for photoemission of crystalline bulk matter.\cite{foerstel_arg1_2010,foerstel_arg2_2011}
-Ar 3p spectra from the mixed clusters show neither of these traits.
-For smaller clusters (panel c), their shape is rather reminiscent of
 
+Ar 3p spectra of the mixed clusters show neither of these traits.
+Rather, the Ar band is symmetric, less wide than in the pure clusters and at a higher binding energy. 
+For further interpretation of the shape we refer to photoemission spectra of condensed Ar monolayers, measured in several settings.\cite{jacobi,jacobi2}
+Spectra were reported for physisorption of Ar on two different metal single crystal substrates, and for Ar atop of a Xe spacer layer adsorbed on the metal.
+While the binding energy is substrate dependent, the spectral shape is very similar in all cases. 
+Most spectra were recorded for emission along the surface normal, and show a double peak split by about 0.5 eV, leading to a structure with $w$ about 1 eV.
+Although this value is larger than the gas phase fine structure split of 0.18 eV, the pertaining states have been assigned to Ar 3p$_{1/2}$ and 3p$_{3/2}$.
+A crystal field splitting of the 3p$_{3/2}$ state is assumed to be also present, but with a smaller value of 0.1-0.2 eV, approx.\cite{jacobi2} 
+The spectrum changes drastically when going to an angle of 40$^\circ$ with respect to the surface normal (Fig. 2 in Ref.\ \citenum{jacobi2}).
+The higher binding energy peak significantly loses in intensity, and the spectrum is now dominated by a single peak comprising both crystal field split substates of Ar 3p$_{3/2}$, with a $w$ of only 0.4 eV.
+As our clusters are probed under all angles at the same time, grazing emission will be the rule, and thus we consider the comparison to a thin Ar layer to be satisfactory. 
+The larger value of the widths measured in our experiments is believed to result from the implicit averaging over several emission directions.
+
+Emission from the Xe 5p state shows a much larger fine structure splitting, which dominates the spectrum even in clusters (where other broadening mechanisms are also present). 
+For the mixed clusters, the Xe band broadens and shifts towards lower binding energy for larger size clusters. 
+For pure Xe clusters, an asymmetry observed in the Xe 5p$_{3/2}$ part has no counterpart in the respective spectra from the mixed clusters.
+This might be caused by the difference in photon energy, as can be seen from a comparison to literature spectra (ArXe at $h\nu = 90$ eV in Ref.\ \citenum{lindblad}, Xe at $h\nu = 20$ eV in Ref.\ \citenum{rolles}).
+For the largest clusters, the nominal size yielded from the jet parameters applied to a pure Xe expansion would correspond to clusters in which bulk atoms far outweigh those on the surface.
+At least for the 5p$_{1/2}$, this would be a seen as a clear asymmetry towards the low binding energy side, which is not observed in our spectra.
+
+In Figure \ref{figure:oval2}, we compare the outer valence spectra of clusters with similar expansion conditions, but different composition of the gas mixture.
+A Xe-rich mixture obviously leads to clusters with more intense Xe photolines, but besides that the main change consists in a narrowing of the Ar band, which remains at about the same binding energy though.
+A comparison with the Ar monomer features (clipped in the Figure) also shows an increased degree of condensation for the Ar gas in the expansion.
+Finally, comparing Figure \ref{figure:oval2} to \ref{figure:oval1} reveals that much larger changes in the valence emission spectra occur for changes in the expansion conditions than for changes of the gax mixture.
+This finding is supported by the spectra shown in Ref.\ \citenum{lindblad}.
+%
+%
+\subsection{Inner valence and electron-electron coincidence spectra}
+%
 \begin{figure}[ht]
@@
 Photon excited electron-electron coincidence spectrum of mixed Ar-Xe clusters in the inner valence region. 
-Panel b): Color-coded map of coincident electron pairs, with the electron of higher kinetic named $e_1$.
+(b): Color-coded map of coincident electron pairs, with the electron of higher kinetic named $e_1$. 
 The energy of $e_1$ is given as binding energy, using the photon energy of $h\nu = 32$~eV. 
-Panel c): Energy spectrum of primary electrons $e_1$, irrespective of the energy of the secondary electron (summation of the coincidence map along horizontal lines).
-The peak at a binding energy of 28.7~eV pertains to the Ar 3s photoelectron line.
-Panel a): Energy spectrum of all secondary (ICD or ETMD) electrons $e_2$ pertaining to the Ar 3s binding energy region marked by two black bars.
+(c): Energy spectrum of primary electrons $e_1$, irrespective of the energy of the secondary electron (summation of the coincidence map along horizontal lines). 
+(a): Energy spectrum of all secondary (ICD or ETMD) electrons $e_2$ pertaining to the Ar 3s binding energy region marked by two black bars. 
 See text for details. 
 Intensity is expressed as coincident events/pixel of 20~meV$^2$ (b) or as coincident events per interval of 20~meV (a,c). 
-The color scale of panel b) is linear.
+In total, approx. 4$\times 10^5$ events are shown. 
+The color scale of (b) is linear.
+ \label{figure:map}
  }
- \label{figure:map}
 \end{figure}
+%
+In our system, only inner valence and core ionized states have sufficient energy to decay via ICD. 
+Here, we focus on the Ar inner valence (3s) vacancy states. 
+Figure\ \ref{figure:map}b shows a typical electron-electron coincidence spectrum pertaining to primary ionization of energy levels in the inner valence region of binding energies.
+More conventional, one-dimensional electron spectra pertaining to the photoelectrons and the ICD/ETMD electrons are obtained by summing up along one of the energy axis of the two-dimensional map, and are shown in (c) and (a).
+The peak in Figure \ref{figure:map}c at a binding energy of 28.7~eV pertains to the Ar 3s photoelectron line.
+No atomic counterpart of this line is visible in this Figure, as only the cluster photoelectrons lead to electron-electron coincidences (see below).
+The Figure shows that a significant amount of slow electrons $e_2$ are recorded in coincidence with the primary 3s electrons ($e_1$), which have a kinetic energy of approx. 3.3 eV. 
+Some background of electron pairs at other energies is also visible.
+This results from inelastic scattering of outer valence photoelectrons, and (in particular for the feature which has both electrons with kinetic energy less than 0.2 eV, upper left corner of \ref{figure:map}b) due to inelastic scattering at parts of the analyzer.
+We subtract this background by fitting a second order polynomial to the background, marked by the two pairs of red horizontal bars, and subtract it from ICD/ETMD signal between the pair of black bars.
+A different polynomial is used for each 0.5 eV wide interval of $e_2$ energies.
+The summation of all background signals is shown as a wavy, solid line in Figure \ref{figure:map}c, and the signal of secondary electron, background subtracted, is shown as the lower trace of data points in Figure \ref{figure:map}a.
+These data were recorded under all expansion conditions listed in Table\ \ref{tab:cluster}.
 

### 2015-12-22 experimental.tex
discussion of valence spectra

--- 2015-11-09 experimental.tex
@@
 %
-\begin{table}
+\begin{table*}
 \caption{
@@
 Experiments were done with $d = 80~\mu$m (first two sections) and $d = 100~\mu$m (bottom section) conical nozzles of 15$^\circ$ half opening angle. 
-For the mixed clusters, $\langle N_{\rm Ar} \rangle$ and $\langle N_{\rm Xe} \rangle$ refer to cluster sizes arrived at by an expansion of the respective pure gases at the given conditions.
-These values are calculated as in ref.\ \protect\citenum{hagena1981}.
 Due to the much lower freezing point of Ar, we basically have an Ar seeded expansion of Xe gas. 
-We therefore expect actual cluster sizes in-between the two limiting values given.
-Inaccuracies in the calculation of $\langle N\rangle$ due to fluctuations of the input parameters are less than 6\,\%.
-This figure does not include systematic errors of the empirical model used.
+$\langle N_{\rm Ar} \rangle$ and $\langle N_{\rm Xe} \rangle$ refer to cluster sizes for a pure Ar, or pure Xe expansion, resp., at the given conditions, calculated from a scaling law.\protect\cite{hagena1981}
+We expect actual cluster sizes in-between these two limiting values. 
+Inaccuracies in the calculation of $\langle N\rangle$ due to fluctuations of the input parameters are less than 6\,\%. This figure does not include systematic errors of the empirical model.
 }
@@
 % Ar, from Marko 
-Ar & (1) & --- &  96.5  & 0.35  &  42  &  --- \\
+Ar & (1) & --- &  96.5  & 0.35  & 44  &  --- \\
 % Ar, from Marko 
-Ar & (2) & --- &  96.5  & 0.67  & 190  &  --- \\
+Ar & (2) & --- &  96.5  & 0.67  & 200  &  --- \\
 % 1103 676, 679
-ArXe & S & 1.2 &  174   & 0.32  &   4  &   62 \\
+ArXe & S & 1.2 &  174   & 0.32  & 4  &   74 \\
 % 1103 670
-ArXe & M & 1.2 &  174   & 0.49  &  10  &  168 \\
+ArXe & M & 1.2 &  174   & 0.49  & 11  &  199 \\
 % 1103 671
-ArXe & L & 1.2 &  174   & 0.68  &  21  &  362 \\
+ArXe & L & 1.2 &  174   & 0.68  & 23  &  431 \\
 % 1103 663
-ArXe & S & 3.0 &  172   & 0.28  &   3  &   48 \\
+ArXe & S & 3.0 &  172   & 0.28  & 3  &   57 \\
 % 1103 640
-ArXe & M & 5.0 &  171   & 0.51  &  12  &  202 \\
+ArXe & M & 5.0 &  171   & 0.51  & 13  &  240 \\
 % 0506 382, Keller offset ber?cksichtigt
-Xe &  & 100 & 183.5  & 0.68  & ---  &  517 \\     
+Xe &  & 100 & 183.5  & 0.68  & ---  &  615 \\     
 \midrule
 % 1103 653
-ArXe & M & 3.0 &  172   & 0.51  &  11  &  196 \\
+ArXe & M & 3.0 &  172   & 0.51  & 12  &  233 \\
 % 1103 658
-ArXe & L & 3.0 &  172   & 0.68  &  22  &  385 \\
+ArXe & L & 3.0 &  172   & 0.68  & 24  &  458 \\
 % 1103 630
-ArXe & S  & 5.0 &  167   & 0.37  &   6  &  108 \\
+ArXe & S  & 5.0 &  167  & 0.37  & 7  &  129 \\
 % 1103 629
-ArXe & L  & 5.0 &  167   & 0.68  &  26  &  451 \\
+ArXe & L  & 5.0 &  167  & 0.68  & 28  &  537 \\
 \midrule
 % 1004 867 (32 eV)
-ArXe & XL & 2.5 &  154   & 2.12  &  920 & 15760\\
+ArXe & XL & 2.5 &  154  & 2.12  & 995 & 18800\\
 % 1004 868
@@
 \end{tabular}
-\end{table}
+\end{table*}
 %
@@
 % Leave this citation in place to avoid Latex error
-A detailed description can be found in Ref. \citenum{arion}, and here we focus on details specific for the current experiment. Commercial Ar and Xe gas was used. 
+A comprehensive description can be found in Ref. \citenum{arion}, and here we focus on details specific for the current experiment. Commercial Ar and Xe gas was used. 
 Separate containers for the two gases were filled up to pressures suitable for producing a certain mixing ratio. The gases were then allowed to mix before the expansion. 
-Expansion parameters and mean cluster sizes, according to an empirical model, are given in Tab.\ \ref{tab:cluster}. 
-We note that currently no empirical model for cluster sizes in a heterogeneous gas expansion exists. 
-We therefore can only give the mean size for a pure jet of one or the other gas at the given conditions.
+Expansion parameters are given in Table \ref{tab:cluster}.
+
+The prediction of the sizes of clusters from a supersonic expansion mainly rests on empirical scaling laws,\cite{hagena1981} which have been the subject of some discussion.
+Recent analyses of photoionization spectra suggests that mean sizes arrived at by scaling laws are smaller than the actual size, at least for rare gas clusters in the range $\langle N\rangle < 1000$.\cite{bergersen,hergenhahnprb,foerstel_arg2_2011}
+Moreover, such scaling laws originally were derived only for pure gas expansions.
+A recent investigation of cluster sizes in a mixed Ar-Kr expansion yielded a revised scaling law, which essentially amounts to the use of a weighted average over the atom-specific parameters of the two gases.\cite{danylchenko2015}
+Although the analogy to our case is not complete, as phase segregation occurs in Ar-Kr ot a much lesser extent, we therefore expect actual cluster sizes between the values calculated for Ar and Xe.
 
@@
 Electrons were detected by a short `magnetic bottle' time-of-flight spectrometer, that has been described earlier.\cite{mucke_review}
-Data were recorded in two different beamtimes at the UE112-PGM-1 (small and medium sized clusters, first two sections in Tab.\ \ref{tab:cluster}) and at the TGM-4 beamline (large clusters, last section in Tab.\ \ref{tab:cluster}).
+Due to its large collection angle, this instrument is particularly suited for experiments that employ electron-electron coincidence detection.
+Data were recorded in two different beamtimes at the UE112-PGM-1 (small and medium sized clusters, first two sections in Table \ref{tab:cluster}) and at the TGM-4 beamline (large clusters, last section in Table \ref{tab:cluster}).
 Linearly, horizontally polarized radiation was used. 
 The storage ring was operated in single bunch conditions.
+Spectra of pure Ar clusters that are shown for comparison are from Ref.
+\citenum{foerstel_arg2_2011}, and a spectrum of pure Xe clusters was recorded with the set-up described in Ref.
+\citenum{hergenhahnprb}.

### 2015-12-22 intro.tex
discussion of valence spectra

@@
  which the originally excited site is neutralized by the decay, 
- and 'exchange ICD' for charge transfer contributions to the 
+ and `exchange ICD' for charge transfer contributions to the 
  normal ICD amplitude.\cite{santrarev,jahnkesat}
@@
 
-First experiments on ICD in heterogeneous systems were on Ne-Ar 
+Rare gas clusters are suitable prototype systems for studies of
+ICD, as they can readily be produced by supersonic 
+expansion through a cooled nozzle. 
+The size of the clusters can be changed by varying the expansion parameters.
+The formation of heterogeneous rare gas clusters by coexpansion of a gas mixture cannot {\it a priori} be taken for granted, but was experimentally shown for most combinations of two rare gases, when suitable mixing ratios and expansion parameters are used (see references throughout this article).
+
+First experiments on ICD in heterogeneous systems used Ne-Ar 
 clusters.\cite{barthnear} Those were followed by studies of 
@@
 clusters was recently presented by some of the authors.\cite{
-fasshauer2014} For that system, a detailed analysis of 
+fasshauer2014} For this system, a detailed account of the
 photoelectron spectra with respect to structural features of the 
@@
 fasshauer2014} it was shown that an analysis of the ICD spectra 
-allowed to decide between structural alternatives for which the 
+allowed to decide between structural alternatives, for which the 
 photoelectron data were indiscriminate.
 
-Rare gas clusters are suitable prototype systems for studies of
-(e.g.) ICD, as they can readily be produced by supersonic 
-expansion. Mixed rare gas clusters easily form by coexpansion of 
-the two gases through a cooled nozzle. The size of the clusters 
-can be changed by varying the expansion parameters, although for 
-heterogeneous clusters some uncertainty remains with respect to 
-the cluster size, as empirical scaling laws \cite{hagena1981} 
-apply to expansion of pure gases only. Early studies of Ar-Xe 
-clusters mostly focussed on the extreme cases of a single Xe atom 
-embedded in an Ar cluster (e.g. Ref. \citenum{lengenprl}). 
-Different sites of the dopant atom (on top of a surface, 
-integrated in an Ar surface, inside the cluster) were 
-distinguished by three separate bands in the fluorescence yield 
-recorded as a function of excitation wavelength.\cite{lengenprl} 
-Increasing the Xe concentration in the expansion lead to changes 
-in the fluorescence excitation spectrum that were interpreted as 
-formation of \ce{Xe2} and larger Xe complexes inside the clusters.
-\cite{lengen} Experiments on Xe-rich mixed clusters were also 
-conducted, and concluded that increasing the Xe content in a 
-coexpanding ArXe mixture leads to the formation of Xe-core, 
-Ar-shell systems with a sharp interface between the two species.\cite
-{tchaplyguine,hoener} This finding was confirmed by electron 
-diffraction experiments.\cite{Danylchenko} Always, the observed 
-Xe content in the clusters is above the Xe content in the 
-expanding gas mixture, as Xe can be condensed much easier than Ar.
-A complementary study used photoelectron-photoion coincidence of
-large Ar-Xe clusters, and found that after inner shell (Xe 4d, Ar 2p)
-photoionization significant charge transfer between both species
-occurs before the mass spectroscopic final state is reached.\cite{berrah}
+Several experimental techniques have been used for the study of mixed Ar-Xe clusters, most notably fluorescence spectroscopy, electron diffraction and photoelectron spectroscopy. 
+Early work focussed on the fluorescence of a single Xe atom 
+embedded in an Ar cluster.\cite{lengenprl}
+%Different sites of the dopant atom (on top of a surface, 
+%integrated in an Ar surface, inside the cluster) were 
+%distinguished by three separate bands in the fluorescence yield 
+%recorded as a function of excitation wavelength.\cite{goldberg} 
+Increasing the Xe concentration in the expansion lead to the formation of \ce{Xe2} and larger Xe complexes inside the clusters.\cite{lengen} 
+With increasing Xe content, the formation of Xe-core, Ar-shell systems with a sharp interface between the two species was shown in photoionization experiments.\cite{tchaplyguine,hoener}
+This finding was confirmed by electron diffraction.\cite{Danylchenko,PhysRevA.76.043202} 
+Always, the observed Xe content in the clusters is higher than the Xe content in the expanding gas mixture, as Xe can be condensed much easier than Ar.\cite{hoener,PhysRevA.76.043202}
+%A complementary study used photoelectron-photoion coincidence of
+%large Ar-Xe clusters, and found that after inner shell (Xe 4d, Ar 2p)
+%photoionization significant charge transfer between both species
+%occurs before the mass spectroscopic final state is reached.\cite{berrah}
+%
+More recently, photoelectron spectra of 
+small Ar-Xe clusters were analyzed, adding to the findings in 
+earlier work.\cite{lindblad} We will discuss this paper in 
+connection with our results below. 
+For completeness, we mention that Ar-Xe complexes can also be produced by passing clusters from a neat Ar expansion through a zone filled with Xe gas (`pick-up').\cite{pietrowski}
+Clusters produced such can structurally be quite different from those produced by coexpansion.\cite{lindbladpccp}
 
-Most recently, on the experimental side photoelectron spectra of 
-small Ar-Xe clusters were analyzed, adding to the findings in 
-earlier work.\cite{Lindblad} We will discuss this paper in 
-connection with our results below. Theoretical work on Ar-Xe was 
-also published, and had a focus on the radiationless decay of Ar 
-inner valence vacancies in these systems.\cite{fasshauer,Fasshauer13}
+A number of theoretical works on Ar-Xe clusters aimed at the prediction of minimum energy structures. 
+Most recently, these converged to structures which have the Xe atoms mainly in the interior.\cite{marques} 
+Xe was also found to diffuse into the interior of Ar clusters in molecular dynamics simulations after pick-up.\cite{Vach_1999} 
+The electronic energy levels of very small Ar-Xe clusters were calculated in Ref.s\ \citenum{fasshauer,Fasshauer13}.
 Interestingly, it was found that Ar 3s$^{-1}$ is stable 

### 2015-12-22 theo_results.tex
discussion of valence spectra

@@
 %
-\begin{table*}[h]
+\begin{table*}[th]
 \centering
@@
 We will now discuss features of several structures, using selected examples.
-Firstly, we consider cluster having an argon core of 13 and 55 atoms with a single xenon
+First we consider cluster having an argon core of 13 and 55 atoms with a single xenon
 atom on one of the surfaces (see Figure \ref{figure:cluster_3_overview}a

### 2015-12-29 suppl.tex
coincidence map now in supplement

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% This is a (brief) model paper using the achemso class
%% The document class accepts keyval options, which should include
%% the target journal and optionally the manuscript type.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[journal=jpccck,manuscript=suppinfo]{achemso}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later. Do NOT use any
%% packages which require e-TeX (for example etoolbox): the e-TeX
%% extensions are not currently available on the ACS conversion
%% servers.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional macros here.  Please use \newcommand* where
%% possible, and avoid layout-changing macros (which are not used
%% when typesetting).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand*\mycommand[1]{\texttt{\emph{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Elke Fasshauer}
\affiliation[UIT]{Centre for Theoretical and Computational Chemistry,
Department of Chemistry, University of Troms\o
-- The Arctic University of Norway, N-9037 Troms\o, Norway}
\email{elke.fasshauer@uit.no}
\author{Melanie Mucke}
\altaffiliation{Now at: Department of Physics and Astronomy, Uppsala University, Box 516, 75120 Uppsala, Sweden}
\author{Marko F\"orstel}
\altaffiliation{Now at: University of Hawai'i at Manoa, 2545 McCarthy Mall, 96816 HI Honolulu, USA}
\affiliation[IPP]{Max-Planck-Institute for Plasma Physics, Boltzmannstr. 2, 85748 Garching, Germany}
\author{...}
\author{Uwe Hergenhahn}
\affiliation[IPP HGW]{Max-Planck-Institute for Plasma Physics, Wendelsteinstr. 1, 14791 Greifswald, Germany}
\affiliation[IOM]{}
\email{uwe.hergenhahn@ipp.mpg.de}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[ArXe]
  {One more attempt on ArXe}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Electron-electron coincidence spectra}
%
%
In this work, we use electron-electron coincidence spectroscopy to isolate electrons from autoionization decays of Ar 3s$^{-1}$ vacancies from the remainder of the electron spectrum, mostly photoelectrons from outer valence levels and secondary electrons from intracluster inelastic collisions.
By recording two electrons ejected in the same process, on an event-by-event basis, we are able to identify those secondary electrons which are ejected after Ar 3s photoionization.
Here, we show a more detailed representation of the electron-electron coincidence data, from which figures in the main paper showing the ICD/ETMD spectra, and the pertaining Ar 3s photoelectron spectra, were derived.

A necessary condition for the ejection of two electrons by a single photon, irrespective of the mechanism by which this is accomplished, is a sufficient photon energy. 
In case of a sequential process, such as photoionization followed by ICD/ETMD, moreover the ionic state which is produced in the primary step must be located above the ionization threshold for the doubly ionized systems.
For Ar 3s autoionization, these conditions are discussed in detail in the main paper.
For a general double ionization process, the required energy can be estimated as the sum of the single ionization energies of the final state holes (main paper, Table 3) plus the geometry-dependent Coulomb repulsion (main paper, Figure 1).
Roughly, 27 eV are needed to produce an Ar 3p$^{-1}$ Xe 5p$_{3/2}^{-1}$ state, and about 2-4 eV less for $\rm (Xe\ 5p^{-1})_2$ states.
For photon energies exceeding this limit, the excess energy can be distributed to any, or both, of the released electrons.
For photoionization followed by autoionization the energy imparted to the first electron is determined by the binding energy of the primary vacancy, however.
This can be used to identify the pertaining second-step spectrum.

Figure\ \ref{figure:map}b shows a typical electron-electron coincidence spectrum recorded with a photon energy of 32 eV, a few eV above the inner valence ionization thresholds.

The Figure shows that a significant amount of slow electrons $e_2$ are recorded in coincidence with the primary 3s electrons ($e_1$), which have a kinetic energy of approx. 3.3 eV. 
Some background of electron pairs at other energies is also visible.
It results from inelastic scattering of outer valence photoelectrons, and (in particular for the feature which has both electrons with kinetic energy less than 0.2 eV, upper left corner of Figure \ref{figure:map}b) due to inelastic scattering at parts of the analyzer.

More conventional, one-dimensional electron spectra pertaining to the photoelectrons and the ICD/ETMD electrons are obtained by summing up along one of the energy axis of the two-dimensional map, and are shown in (c) and (a). 
The peak in Figure \ref{figure:map}c at a binding energy of 28.7~eV pertains to the Ar 3s photoelectron line.
No atomic counterpart of this line is visible in this Figure, as only the cluster photoelectrons lead to electron-electron coincidences.
The trace shown in Figure \ref{figure:map}a is interpreted as the spectral shape of ICD/ETMD decays.

We have subtracted the background from random coincidences or coincidences due to electron scattering from the signals shown in Figures \ref{figure:map}a,c.
In order to do so, the regions between the two pairs of red horizontal bars in Figure \ref{figure:map}b were identified as background.
The coincidence map was then subdivided into intervals of 0.5 eV width in the $e_2$ energy coordinate.
For each interval, a second order polynomial was fitted to the background signal, and subsequently subtracted from the ICD/ETMD signal marked by the black bars.
The summation of all background signals is shown as a wavy, solid red line in Figure \ref{figure:map}c, and the signal of secondary electrons, background subtracted, is shown as the lower trace of data points in Figure \ref{figure:map}a.
Background subtracted ICD/ETMD signals are shown throughout the main paper.

These data were recorded under all expansion conditions listed in Table 1.
%
\begin{figure}[ht]
 \centering
 \includegraphics[width=12cm]{pics/figure_map.pdf}
 \caption{
Photon excited electron-electron coincidence spectrum of mixed Ar-Xe clusters in the inner valence region. 
(b): Color-coded map of coincident electron pairs, with the electron of higher kinetic named $e_1$. 
The energy of $e_1$ is given as binding energy, using the photon energy of $h\nu = 32$~eV. 
(c): Energy spectrum of primary electrons $e_1$, irrespective of the energy of the secondary electron (summation of the coincidence map along horizontal lines). 
(a): Energy spectrum of all secondary (ICD or ETMD) electrons $e_2$ pertaining to the Ar 3s binding energy region marked by two black bars. 
See text for details. 
Intensity is expressed as coincident events/pixel of 20~meV$^2$ (b) or as coincident events per interval of 20~meV (a,c). 
In total, approx. 4$\times 10^5$ events are shown. 
The color scale of (b) is linear.
 \label{figure:map}
 }
\end{figure}
%
Similar figures were recorded for all combinations of expansion parameters listed in Table 1 of the main paper.
A more detailed description of methods for analysing these data sets has been given.\cite{Foerstel_phd}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The appropriate \bibliography command should be placed here.
%% Notice that the class file automatically sets \bibliographystyle
%% and also names the section correctly.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raggedright
\bibliography{arxe}

\end{document}

### 2016-01-10 exp_results.tex
description of experimental results, more figures for supporting information

@@
 \label{sec:exp_results}}
-
+%
+%
 \begin{table}
@@
 \toprule
- \multicolumn{2}{r}{size} &  Xe$_{in}$& $\EB$ (eV)& $w$ (eV)& \multicolumn{2}{c}{$\EB$ (eV)}  & $w$ (eV) &  Xe$_{\rm cl}$ \\
+ \multicolumn{2}{r}{size} &  Xe$_{\rm in}$& $\EB$ (eV)& $w$ (eV)& \multicolumn{2}{c}{$\EB$ (eV)}  & $w$ (eV) &  Xe$_{\rm cl}$ \\
 %
@@
 Rather, the Ar band is symmetric, less wide than in the pure clusters and at a higher binding energy. 
-For further interpretation of the shape we refer to photoemission spectra of condensed Ar monolayers, measured in several settings.\cite{jacobi,jacobi2}
+We characterize the spectral shape by giving a single value for the Ar 3p binding energy, and the FWHM of the feature.
+Values for different expansion parameters, and for both Ar and Xe valence lines, are collected in Table\ \ref{tab:valence}.
+
+We find experimentally that clusters we have produced have a Xe content Xe$_{\rm cl}$ between 10 and 50\,\%.
+A slight decrease of the binding energy with cluster size is seen for all outer valence lines, and is attributed to a larger final state polarization energy in larger clusters.
+
+For further interpretation of its shape we refer to photoemission spectra of condensed Ar monolayers, measured in several settings.\cite{jacobi,jacobi2}
 Spectra were reported for physisorption of Ar on two different metal single crystal substrates, and for Ar atop of a Xe spacer layer adsorbed on the metal.
-While the binding energy is substrate dependent, the spectral shape is very similar in all cases. 
+While the binding energy depends on the substrate, the spectral shape is very similar in all cases. 
 Most spectra were recorded for emission along the surface normal, and show a double peak split by about 0.5 eV, leading to a structure with $w$ about 1 eV.
-Although this value is larger than the gas phase fine structure split of 0.18 eV, the pertaining states have been assigned to Ar 3p$_{1/2}$ and 3p$_{3/2}$.
-A crystal field splitting of the 3p$_{3/2}$ state is assumed to be also present, but with a smaller value of 0.1-0.2 eV, approx.\cite{jacobi2} 
-The spectrum changes drastically when going to an angle of 40$^\circ$ with respect to the surface normal (Fig. 2 in Ref.\ \citenum{jacobi2}).
-The higher binding energy peak significantly loses in intensity, and the spectrum is now dominated by a single peak comprising both crystal field split substates of Ar 3p$_{3/2}$, with a $w$ of only 0.4 eV.
-As our clusters are probed under all angles at the same time, grazing emission will be the rule, and thus we consider the comparison to a thin Ar layer to be satisfactory. 
-The larger value of the widths measured in our experiments is believed to result from the implicit averaging over several emission directions.
+Although the splitting is larger than the gas phase fine structure split of 0.18 eV, the pertaining states have been assigned to Ar 3p$_{1/2}$ and 3p$_{3/2}$.
+A crystal field splitting of the 3p$_{3/2}$ state has been assumed to be also present, but with a smaller value of 0.1-0.2 eV, approx.\cite{jacobi2} 
+The spectrum clearly changes when going to an emission angle of 40$^\circ$ with respect to the surface normal (Fig.\ 2 in Ref.\ \citenum{jacobi2}).
+The higher binding energy peak significantly loses in intensity, and the spectrum is now dominated by a single peak comprising both crystal field split substates of Ar 3p$_{3/2}$, with a FWHM ($w$) of only 0.4 eV.
+As our measured spectrum is comprised of contributions recorded under all emission angles with respect to the cluster surface, grazing emission will be the rule.
+We therefore believe that the arguments given above make it plausible that only a single peak is observed in all our spectra.
 
@@
 In Figure \ref{figure:oval2}, we compare the outer valence spectra of clusters with similar expansion conditions, but different composition of the gas mixture.
-A Xe-rich mixture obviously leads to clusters with more intense Xe photolines, but besides that the main change consists in a narrowing of the Ar band, which remains at about the same binding energy though.
+A Xe-rich mixture obviously leads to clusters with more intense Xe photolines, but besides that the main change consists in a narrowing of the Ar band.
 A comparison with the Ar monomer features (clipped in the Figure) also shows an increased degree of condensation for the Ar gas in the expansion.
+
+For the smallest clusters we have produced, a plausible model is provided by calculated minimum energy structures of Ar$_N$Xe$_{38-N}$ (Fig.\ 7 in Ref.\ \citenum{marques}).
+We there see that for a Xe content of less than 60\,\%, core-shell systems are {\it not} formed, and although the Xe atoms tend to connect, the degree of Ar-Xe mixing is large.
+While for low Xe content (approx. 10\,\%), some Ar atoms have only Ar nearest neighbours, for larger Xe content all Ar atoms seem to see both Ar and Xe nearest neighbours.
+We believe this leads to the Ar 3p narrowing pointed out above.
+Possibly, some clusters of our ensemble already are in the core-shell regime, which would lead to an even lower 3p width.
+For the largest clusters we have produced (Figure \ref{figure:oval1}b), the low binding energy of the Xe lines and the broadening of the Ar feature without appearance of the `bulk Ar'-maximum, supports formation of a Xe core covered by at least two layers of Ar.
+If the scaling law size for a pure Ar expansion is taken as the lower limit for the cluster size, from the observed Xe content we arrive at clusters composed of a Xe core with four layers, covered by three layers of Ar (see Supporting Information).
+
 Finally, comparing Figure \ref{figure:oval2} to \ref{figure:oval1} reveals that much larger changes in the valence emission spectra occur for changes in the expansion conditions than for changes of the gax mixture.
@@
 %
-\subsection{Inner valence and electron-electron coincidence spectra}
+\subsection{Inner valence spectra}
+%
+We now focus on the Ar inner valence (3s) vacancy states. 
 %
@@
  \centering
- \includegraphics[width=8.5cm]{pics/figure_map.pdf}
+ \includegraphics[width=8.8cm]{pics/figure_ival.pdf}
  \caption{
-Photon excited electron-electron coincidence spectrum of mixed Ar-Xe clusters in the inner valence region. 
-(b): Color-coded map of coincident electron pairs, with the electron of higher kinetic named $e_1$. 
-The energy of $e_1$ is given as binding energy, using the photon energy of $h\nu = 32$~eV. 
-(c): Energy spectrum of primary electrons $e_1$, irrespective of the energy of the secondary electron (summation of the coincidence map along horizontal lines). 
-(a): Energy spectrum of all secondary (ICD or ETMD) electrons $e_2$ pertaining to the Ar 3s binding energy region marked by two black bars. 
-See text for details. 
-Intensity is expressed as coincident events/pixel of 20~meV$^2$ (b) or as coincident events per interval of 20~meV (a,c). 
-In total, approx. 4$\times 10^5$ events are shown. 
-The color scale of (b) is linear.
- \label{figure:map}
+Photon excited electron spectra of mixed Ar-Xe clusters in the inner valence region.
+Symbols show the Ar 3s photoline from clusters (`cl') and uncondensed Ar monomers (`m'), atop of a background resulting from inelastic intracluster scattering of outer valence photoelectrons (`excitonic satellites'\protect\cite{hergenhahn2002}).
+Colored symbols result from accumulating photoelectrons only from those events, which resulted in the subsequent emission of a second electron.
+Solid lines represent various least-squares fits to the data, see text for details.
+A photon energy of $h\nu = 32$ eV was used.
+ \label{figure:ival}
  }
 \end{figure}
+
+Figure\ \ref{figure:ival} shows the Ar part of the inner valence spectrum for representative ArXe clusters. 
+The total photoelectron signal looks similar to literature spectra for pure Ar clusters.\cite{feifel,zhang} 
+A low energy tail seen for the Ar 3s monomer line results from the transmission properties of the electron spectrometer, together with the strongly positive angular distribution parameter of this line.\cite{kruit}
+The Ar 3s cluster line shows no splitting into bulk and surface components, different to the literature on pure clusters but in agreement with our discussion of the outer valence spectra.
+
+If we produce a spectrum only from those electrons recorded as part of a two-electron coincidence (colored symbols in Figure \ref{figure:ival}), the apparent intensity drops.
+This can partly be attributed to the finite detection efficiency of the spectrometer. 
+Moreover, the monomer part of the Ar 3s signal completely disappears, as 3s photoionization of an uncondensed Ar atom in the gas jet cannot lead to emission of a second electron. 
+Further features of these diagrams and the least squares fits shown in the Figure are discussed below.
 %
-In our system, only inner valence and core ionized states have sufficient energy to decay via ICD. 
-Here, we focus on the Ar inner valence (3s) vacancy states. 
-Figure\ \ref{figure:map}b shows a typical electron-electron coincidence spectrum pertaining to primary ionization of energy levels in the inner valence region of binding energies.
-More conventional, one-dimensional electron spectra pertaining to the photoelectrons and the ICD/ETMD electrons are obtained by summing up along one of the energy axis of the two-dimensional map, and are shown in (c) and (a).
-The peak in Figure \ref{figure:map}c at a binding energy of 28.7~eV pertains to the Ar 3s photoelectron line.
-No atomic counterpart of this line is visible in this Figure, as only the cluster photoelectrons lead to electron-electron coincidences (see below).
-The Figure shows that a significant amount of slow electrons $e_2$ are recorded in coincidence with the primary 3s electrons ($e_1$), which have a kinetic energy of approx. 3.3 eV. 
-Some background of electron pairs at other energies is also visible.
-This results from inelastic scattering of outer valence photoelectrons, and (in particular for the feature which has both electrons with kinetic energy less than 0.2 eV, upper left corner of \ref{figure:map}b) due to inelastic scattering at parts of the analyzer.
-We subtract this background by fitting a second order polynomial to the background, marked by the two pairs of red horizontal bars, and subtract it from ICD/ETMD signal between the pair of black bars.
-A different polynomial is used for each 0.5 eV wide interval of $e_2$ energies.
-The summation of all background signals is shown as a wavy, solid line in Figure \ref{figure:map}c, and the signal of secondary electron, background subtracted, is shown as the lower trace of data points in Figure \ref{figure:map}a.
-These data were recorded under all expansion conditions listed in Table\ \ref{tab:cluster}.
-
+%
+\subsection{ICD/ETMD spectra}
+%
 \begin{figure}[ht]
@@
 Black symbols with error bars show the data points for the smallest clusters measured (`S'), two larger clusters sizes are shown by the red and blue traces. 
+Error bars for the latter are smaller than the ones shown and have been omitted.
 For comparison, all spectra are shown area-normalized. 
@@
 \end{figure}
-
+%
+%
 \begin{figure}[ht]
@@
 \end{figure}
+%
+In Figure \ref{figure:icd_12}, we show the spectra of ICD/ETMD electrons pertaining to emission of an Ar 3s cluster photoelectron. 
+These, and the following figure, constitute the central experimental result of the article.
+Due to their low kinetic energy, without use of a coincidence method they could hardly be separated from the background of inelastically scattered photoelectrons.\cite{mucke}
+Further details on the data acquisition and analysis methodology are given in the Supporting Information.
+We note here that spectra recorded at $h\nu = 34$ eV as a cross-check, quantitatively agree to those shown in the Figure.
 
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{pics/figure_ival.pdf}
- \caption{
-Photon excited electron spectra and electron-electron coincidence spectra of mixed Ar-Xe clusters in the inner valence region.
-Spectra show the Ar 3s photoline from clusters (`cl') and uncondensed Ar monomers (`m'), atop of a background resulting from inelastic intracluster scattering of outer valence photoelectrons.\protect\cite{hergenhahn2002} Black symbols: sum of non-coincident and coincident (1st hit) events, red symbols: coincident events only.
-Solid, colored lines show the results of various least-squares fits, see text for details.
-}
- \label{figure:ival}
-\end{figure}
+Clearly, spectra for the three different cluster sizes shown in Figure \ref{figure:icd_12} show significant differences: Spectra for the larger cluster, in comparison acquire more intensity in the 1-1.5 eV region and have less intensity for energies below 0.5 eV.
+In contrast to that, the ICD/ETMD spectrum hardly varies when the composition of the expanding gas mixture is changed (Figure \ref{figure:icd_l}).
+The full set of ICD/ETMD spectra is shown as Supporting Information.
 
@@
 Efficiency of the decay of Ar 3s ionized states in ArXe clusters by emission of a secondary electron via ICD or ETMD.
-Values are arranged by Xe content of the initial gas mixture ('+' symbols: 1.2\,\%, asterisk: 3\,\%, triangle: 5\,\%).
+Values are arranged by Xe content of the initial gas mixture (`+' symbols: 1.2\,\%, asterisk: 3\,\%, triangle: 5\,\%).
 Symbol sizes indicate the photon energy (large symbols: 32 eV, small: 34 eV), and color indicates the cluster size (black symbols: S, red: M, blue: L).
@@
 \end{figure}
+%
+We now discuss which fraction of Ar 3s vacancy states relax via ICD or ETMD.
+A method to derive this figure has been established, which we apply here.\cite{foerstel_2013}
+Briefly, we correct the intensity of the Ar 3s photoline in the coincident spectra by the detector efficiency, and divide it by the 3s intensity in the undiscriminated spectrum.
+The result gives the branching ratio of decay via ICD/ETMD vs. all channels, including those not involving electron emission.
+To arrive at quantitative results, we have performed least squares fits of the non-coincident and coincident $e_1$ spectra.
+The fits assumed one or two Gaussian peaks, resp., atop of a background modelled by two more Gaussian curves with a very large widths.
+The peak pertaining to the Ar 3s cluster photoline, with the background added, is shown by the blue and red solid line in Figure \ref{figure:ival}.
+Moreover, the line labelled `c.fit/det.' shows the fit to the coincident events corrected by the detection efficiency. 
+This virtually agrees with the fit to the total spectrum in Figure \ref{figure:ival}a, but not in \ref{figure:ival}b, which corresponds to ICD/ETMD efficiencies of one and significantly smaller than one.
+Figure \ref{figure:eff} shows the results of this analysis.
+The error in the quantity shown is mainly determined by uncertainties in the peak/background separation.
+(Our choice for the background shape is shown in Figure \ref{figure:ival}.)
+For the gas mixture with a Xe$_{\rm in}$ of 1.2\,\%, we therefore show results from fits using two different models appearing both justifiable.
+Statistical errors are much smaller.
+
+Within the accuracy of our experiment we found an Ar 3s autoionization efficiency which is smaller than unity for all spectra with Xe$_{\rm in}$ of 1.2\,\%, and decreases with cluster size. 
+For larger Xe$_{\rm in}$, the values are compatible with one.

### 2016-01-10 suppl.tex
description of experimental results, more figures for supporting information

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newcommand*\mycommand[1]{\texttt{\emph{#1}}}
+%\newcommand*\mycommand[1]{\texttt{\emph{#1}}}
 
@@
 
-Figure\ \ref{figure:map}b shows a typical electron-electron coincidence spectrum recorded with a photon energy of 32 eV, a few eV above the inner valence ionization thresholds.
-
-The Figure shows that a significant amount of slow electrons $e_2$ are recorded in coincidence with the primary 3s electrons ($e_1$), which have a kinetic energy of approx. 3.3 eV. 
-Some background of electron pairs at other energies is also visible.
-It results from inelastic scattering of outer valence photoelectrons, and (in particular for the feature which has both electrons with kinetic energy less than 0.2 eV, upper left corner of Figure \ref{figure:map}b) due to inelastic scattering at parts of the analyzer.
-
-More conventional, one-dimensional electron spectra pertaining to the photoelectrons and the ICD/ETMD electrons are obtained by summing up along one of the energy axis of the two-dimensional map, and are shown in (c) and (a).
-The peak in Figure \ref{figure:map}c at a binding energy of 28.7~eV pertains to the Ar 3s photoelectron line.
-No atomic counterpart of this line is visible in this Figure, as only the cluster photoelectrons lead to electron-electron coincidences.
-The trace shown in Figure \ref{figure:map}a is interpreted as the spectral shape of ICD/ETMD decays.
-
-We have subtracted the background from random coincidences or coincidences due to electron scattering from the signals shown in Figures \ref{figure:map}a,c.
-In order to do so, the regions between the two pairs of red horizontal bars in Figure \ref{figure:map}b were identified as background.
-The coincidence map was then subdivided into intervals of 0.5 eV width in the $e_2$ energy coordinate.
-For each interval, a second order polynomial was fitted to the background signal, and subsequently subtracted from the ICD/ETMD signal marked by the black bars.
-The summation of all background signals is shown as a wavy, solid red line in Figure \ref{figure:map}c, and the signal of secondary electrons, background subtracted, is shown as the lower trace of data points in Figure \ref{figure:map}a.
-Background subtracted ICD/ETMD signals are shown throughout the main paper.
-
-These data were recorded under all expansion conditions listed in Table 1.
-%
-\begin{figure}[ht]
+\begin{figure}
  \centering
@@
 %
-Similar figures were recorded for all combinations of expansion parameters listed in Table 1 of the main paper.
+Figure\ \ref{figure:map}b shows a typical electron-electron coincidence spectrum recorded with a photon energy of 32 eV, a few eV above the inner valence ionization thresholds.
+
+The Figure shows that a significant amount of slow electrons $e_2$ are recorded in coincidence with the primary 3s electrons ($e_1$), which have a kinetic energy of approx. 3.3 eV. 
+Some background of electron pairs at other energies is also visible.
+It results from inelastic scattering of outer valence photoelectrons, and (in particular for the feature which has both electrons with kinetic energy less than 0.2 eV, upper left corner of Figure \ref{figure:map}b) due to inelastic scattering at parts of the analyzer.
+
+More conventional, one-dimensional electron spectra pertaining to the photoelectrons and the ICD/ETMD electrons are obtained by summing up along one of the energy axis of the two-dimensional map, and are shown in (c) and (a).
+The peak in Figure \ref{figure:map}c at a binding energy of 28.7~eV pertains to the Ar 3s photoelectron line.
+No atomic counterpart of this line is visible in this Figure, as only the cluster photoelectrons lead to electron-electron coincidences.
+The trace shown in Figure \ref{figure:map}a is interpreted as the spectral shape of ICD/ETMD decays.
+
+We have subtracted the background from random coincidences and coincidences due to electron scattering (electron impact ionization) from the signals shown in Figures \ref{figure:map}a,c.
+In order to do so, the regions between the two pairs of red horizontal bars in Figure \ref{figure:map}b were identified as background.
+The coincidence map was then subdivided into intervals of 0.5 eV width in the $e_2$ energy coordinate.
+For each interval, a second order polynomial was fitted to the background signal, and subsequently subtracted from the ICD/ETMD signal marked by the black bars.
+The summation of all background signals is shown as a wavy, solid red line in Figure \ref{figure:map}c, and the signal of secondary electrons, background subtracted, is shown as the lower trace of data points in Figure \ref{figure:map}a.
+Background subtracted ICD/ETMD signals are shown throughout the main paper.
+
+These data were recorded under all expansion conditions listed in Table 1.
+
+Similar figures were recorded for all combinations of expansion parameters listed in Table~1 of the main paper.
 A more detailed description of methods for analysing these data sets has been given.\cite{Foerstel_phd}
+%
+%
+\section{ICD/ETMD spectra}
+%
+\begin{figure}
+ \centering
+ \includegraphics[width=8.2cm]{pics/630_631_cs.pdf}
+ \includegraphics[width=8.2cm]{pics/673_674_cs.pdf}
+ \caption{
+Energy spectrum of all coincident secondary (ICD or ETMD) electrons $e_2$ pertaining to primary electrons $e_1$ in the Ar 3s binding energy region. 
+Spectra were recorded with photon energies of $h\nu = 32$~eV (symbols) and $h\nu = 34$~eV (trace). 
+Spectra were normalized to equal area. 
+ \label{figure:hnucomp}
+ }
+\end{figure}
+%
+The background subtracted signal of secondary electrons $e_2$ being recorded in coincidence with a primary Ar 3s photoelectron $e_1$ is interpreted as the energy spectrum of ICD/ETMD of the cluster ensemble under study.
+Some representative examples for such spectra are shown in the main article.
+Here, we present a full account of these spectra.
+For better comparison, similar to the article they have been arranged into groups of spectra from either clusters of equal size, or of equal composition of the gas mixture (resulting in a similar ratio of condensed Ar to Xe, at least when averaged over the cluster ensemble).
+Thus, identical spectra appear more than once in the presentation.
+
+As expected, the shape of the coincident $e_2$ spectra does not depend on the excitation energy (examples: Figure \ref{figure:hnucomp}).
+
+\begin{figure}
+ \centering
+ \includegraphics[width=8.2cm]{pics/661_653_cs.pdf}
+ \includegraphics[width=8.2cm]{pics/867_658_cs.pdf}
+ \includegraphics[width=8.2cm]{pics/630_998_cs.pdf}
+ \caption{
+Energy spectrum of all coincident secondary (ICD or ETMD) electrons $e_2$ pertaining to primary electrons $e_1$ in the Ar 3s binding energy region. 
+Comparison of the spectra from cluster ensembles of different mean size.
+Spectra were recorded at $h\nu = 32$~eV and were normalized to equal area. 
+ \label{figure:sizcomp}
+ }
+\end{figure}
+%
+%
+\begin{figure}
+ \centering
+ \includegraphics[width=8.2cm]{pics/677_661_cs.pdf}
+ \includegraphics[width=8.2cm]{pics/668_653_cs.pdf}
+ \caption{
+Comparison of the spectra from cluster ensembles of different gas composition, see Figure \protect\ref{figure:sizcomp} for details.
+ \label{figure:compcomp}
+ }
+\end{figure}
+%
+%
+As discussed in the main paper, the differences between clusters of different size (Figure \ref{figure:sizcomp}) are more substantial than those between clusters of different gas composition (Figure \ref{figure:compcomp}).
 

### 2016-01-14 exp_results.tex
small edits, started discussion section

@@
 
-Clearly, spectra for the three different cluster sizes shown in Figure \ref{figure:icd_12} show significant differences: Spectra for the larger cluster, in comparison acquire more intensity in the 1-1.5 eV region and have less intensity for energies below 0.5 eV.
+Clearly, spectra for the three different cluster sizes in Figure \ref{figure:icd_12} are significantly different: Spectra for the larger cluster acquire more intensity in the 1-1.5 eV region and have less intensity for energies below 0.5 eV.
 In contrast to that, the ICD/ETMD spectrum hardly varies when the composition of the expanding gas mixture is changed (Figure \ref{figure:icd_l}).
@@
 %
-We now discuss which fraction of Ar 3s vacancy states relax via ICD or ETMD.
-A method to derive this figure has been established, which we apply here.\cite{foerstel_2013}
+We now discuss which fraction of Ar 3s vacancy states relaxes via ICD or ETMD.
+A method to derive this information has been established by some of us.\cite{foerstel_2013}
 Briefly, we correct the intensity of the Ar 3s photoline in the coincident spectra by the detector efficiency, and divide it by the 3s intensity in the undiscriminated spectrum.
-The result gives the branching ratio of decay via ICD/ETMD vs. all channels, including those not involving electron emission.
+The result gives the branching ratio of decay via ICD/ETMD vs. the sum of all channels, including those not involving electron emission.
 To arrive at quantitative results, we have performed least squares fits of the non-coincident and coincident $e_1$ spectra.
@@
 The peak pertaining to the Ar 3s cluster photoline, with the background added, is shown by the blue and red solid line in Figure \ref{figure:ival}.
-Moreover, the line labelled `c.fit/det.' shows the fit to the coincident events corrected by the detection efficiency. 
-This virtually agrees with the fit to the total spectrum in Figure \ref{figure:ival}a, but not in \ref{figure:ival}b, which corresponds to ICD/ETMD efficiencies of one and significantly smaller than one.
+Moreover, the line labelled `c.fit/det.' shows the fit to the coincident events, corrected by the detection efficiency. 
+This virtually agrees with the fit to the total spectrum in Figure \ref{figure:ival}a, but not in \ref{figure:ival}b.
+The corresponding figure for the ICD/ETMD efficiency is at one for \ref{figure:ival}a, and significantly smaller than one for \ref{figure:ival}b.
 Figure \ref{figure:eff} shows the results of this analysis.
@@
 (Our choice for the background shape is shown in Figure \ref{figure:ival}.)
-For the gas mixture with a Xe$_{\rm in}$ of 1.2\,\%, we therefore show results from fits using two different models appearing both justifiable.
+For the gas mixture with a Xe$_{\rm in}$ of 1.2\,\%, we therefore show results from fits using two different models.
 Statistical errors are much smaller.

### 2016-01-14 theo_discussion.tex
small edits, started discussion section

--- 2015-05-06 theo_discussion.tex
@@
-\section{Discussion}
-
-We have discussed the experimental spectra in iSection \ref{} and
-the expected features of spectra for different cluster types in
-Section \ref{}. In this section we combine the experimental and theoretical
-results in order to determine the structure of the noble gas clusters.
+\section{Discussion
+\label{sec:discussion}}
+%
+%We have discussed the experimental spectra in Section \ref{sec:exp_results} and
+%the expected features of spectra for different cluster types in
+%Section \ref{sec:th_results}. In this section we combine the experimental and theoretical
+%results in order to determine the structure of the noble gas clusters.
+%
+%The simulated secondary electron spectra for the xenon core structures
+%(see Figure \ref{figure:xe_3_in})
+%show an ICD peak at higher energies than those structures with added xenon
+%atoms on the surface. This does not fit to the experimentally determined
+%spectra and hence we consider an argon core to be more probable for the
+%small measured clusters.
+%
+%The experimental spectra in Figure \ref{}
+%show a broadening of the secondary electron peak with increasing
+%pressure (?) and hence cluster size just as can be expected from
+%the theoretically simulated spectra in Figure \ref{figure:surf}.
+%
+%From the theoretical simulations of larger small clusters
+%having the same xenon content as experimentally observed a clearly
+%visible ETMD peak is to be expected as shown in Figure \ref{figure:ar_3_6in}.
+%However, the experimental spectra do not show a signal in the energy
+%region of \unit[1.5--6.5]{eV}. From this we conclude that the clusters
+%measured were smaller than 55 atoms containing only very few xenon atoms.
+%Additionally, if the cluster contains more than one xenon atom, they are
+%not expected to be close because of an otherwise visible ETMD peak
+%(compare Figure \ref{figure:2tops}).
+%
+%The large clusters with a large xenon content can be expected to have
+%a xenon core being surrounded by argon layers and hence, both ICD and
+%ETMD should be visible in the spectrum. Unfortunately, the ICD and ETMD
+%peaks overlap such that the two processes can not be distiguished.
+%
+We now would like to interpret our experimental findings in view of the simulated results described in Section \ref{sec:th_results}.
+Figure \ref{figure:eff} shows that for Ar 3s$^{-1}$ states, autoionization by either ICD or ETMD is the only mode of relaxation except for the clusters with the smallest Xe content.

### 2016-01-18 experimental.tex
description of experimental results, more figures for supporting information

@@
 
-The prediction of the sizes of clusters from a supersonic expansion mainly rests on empirical scaling laws,\cite{hagena1981} which have been the subject of some discussion.
+Prediction of the sizes of clusters from a supersonic expansion mainly rests on empirical scaling laws,\cite{hagena1981} which have been the subject of some discussion.
 Recent analyses of photoionization spectra suggests that mean sizes arrived at by scaling laws are smaller than the actual size, at least for rare gas clusters in the range $\langle N\rangle < 1000$.\cite{bergersen,hergenhahnprb,foerstel_arg2_2011}
@@
 A recent investigation of cluster sizes in a mixed Ar-Kr expansion yielded a revised scaling law, which essentially amounts to the use of a weighted average over the atom-specific parameters of the two gases.\cite{danylchenko2015}
-Although the analogy to our case is not complete, as phase segregation occurs in Ar-Kr ot a much lesser extent, we therefore expect actual cluster sizes between the values calculated for Ar and Xe.
+Although the analogy to our case is not complete, as phase segregation occurs in Ar-Kr to a much lesser extent,\cite{Vach_1999,lundwall_arkr} we therefore expect actual cluster sizes between the values calculated for Ar and Xe.
 
@@
 The storage ring was operated in single bunch conditions.
-Spectra of pure Ar clusters that are shown for comparison are from Ref.
-\citenum{foerstel_arg2_2011}, and a spectrum of pure Xe clusters was recorded with the set-up described in Ref.
-\citenum{hergenhahnprb}.
+Spectra of pure Ar clusters shown for comparison are from Ref. \citenum{foerstel_arg2_2011}, and a spectrum of pure Xe clusters was recorded with the set-up described in Ref. \citenum{hergenhahnprb}.
+
+Entrance aperture and drift tube of the magnetical bottle spectrometer can be independently biased to influence the electron flight times. 
+For the data shown here, slightly positive bias voltages were used (+1.8 V to +2.2 V) in order to have all electrons arriving at the detector within one BESSY single bunch period (800 ns). 
+The detection efficiency was determined as 0.6, with the method outlined in Ref. \citenum{mucke_review}.

### 2016-01-18 structures.tex

@@
 Most estimated cluster sizes given in Table \ref{tab:cluster} are much smaller.
-We use the estimated number of atoms for a pure Ar expansion as the lower limit for the actual cluster size, start our search for model structures from there.
+We use the estimated number of atoms for a pure Ar expansion as the lower limit for the actual cluster size and start our search for model structures from there.
 %

### 2016-01-18 theo_results.tex

@@
-\section{Theoretical Results}
+\section{Theoretical Results
+\label{sec:th_results}}
 %
@@
           argon clusters consisting of 13
-          argon atoms with 2 additional xenon atoms on top of two different
+          argon atoms with two additional xenon atoms on top of two different
           argon surfaces. ICD and ETMD spectra are shown for three
@@
           the ICD spectrum.
-          {\it Q: Warum ist in diesen (und vielen anderen) Bildern jedes Label doppelt?}}
+          {\it Q: Ich sehe die traces für die 'furthest' Konfiguration nicht(?!) Q: Warum ist in diesen (und vielen anderen) Bildern jedes Label doppelt?}}
  \label{figure:2tops}

### 2016-01-18 theory.tex

@@
 transition moment $m$ and an additional index $k$
-(compare Ref. \cite{Fasshauer13}).
+(compare Ref. \citenum{Fasshauer13}).
 
@@
 the program HARDRoC \cite{HARDRoC,fasshauer2014} using the
-experimental ionization energies of Table \ref{}
+experimental ionization energies of Table \ref{tab:valence}
 and data from the literature given in Tables \ref{} and \ref{}.
-This choice is identical to the one made in Reference \cite{Fasshauer13}.
+This choice is identical to the one made in Reference \citenum{Fasshauer13}.

### 2016-01-18 exp_results.tex
figures for 3s binding energy added

@@
 The Ar 3s cluster line shows no splitting into bulk and surface components, different to the literature on pure clusters but in agreement with our discussion of the outer valence spectra. 
+The binding energy of the cluster line has values between 28.85 and 28.70 eV for all cluster ensembles with size label S-L, and 28.67 eV for the largest clusters measured. 
+A small, but systematic decrease of the binding energy is observed when the cluster size is increased. 
+The value assumed in the simulations is 28.60 eV.\cite{Fasshauer13}
 

### 2016-01-18 theory.tex
figures for 3s binding energy added

@@
 %
-depending on constants ($a_{m,k}=4,2$)
+depending on constants ($a_{m,k}=4,2$) {\it Q: ??? Hei\ss t das, $a_{m.k}$ kann die Werte 2 und 4 annehmen?}
 as well as experimental properties

### 2016-01-19 exp_results.tex
allow for compilation

--- 2016-01-14 exp_results.tex
@@
 Uncertainties are estimated as $\pm$3\,\% for the Xe content and 0.05~eV for the binding energies. 
-For reference, the row labelled `(th.)' gives the binding energies used in the simulations of this paper (same as in Ref. \citenum{Fasshauer13}), and the last row their atomic counterparts. 
+For reference, the row labelled `(th.)' gives the binding energies used in the simulations of this paper (same as in Ref. \cite{Fasshauer13}), and the last row their atomic counterparts. 
 Values for Ar 3p in these two rows refer to the fine structure states.
@@
 Figure \ref{figure:oval1} shows the outer valence spectra of small and large ArXe clusters, compared to clusters of the pure gases. 
-Qualitatively similar spectra have been published without detailed discussion in Ref.\ \citenum{lindblad}.
+Qualitatively similar spectra have been published without detailed discussion in Ref.\ \cite{lindblad}.
 Differences are seen in particular for the Ar component. 
@@
 A crystal field splitting of the 3p$_{3/2}$ state has been assumed to be also present, but with a smaller value of 0.1-0.2 eV, approx.\cite{jacobi2} 
-The spectrum clearly changes when going to an emission angle of 40$^\circ$ with respect to the surface normal (Fig.\ 2 in Ref.\ \citenum{jacobi2}).
+The spectrum clearly changes when going to an emission angle of 40$^\circ$ with respect to the surface normal (Fig.\ 2 in Ref.\ \cite{jacobi2}).
 The higher binding energy peak significantly loses in intensity, and the spectrum is now dominated by a single peak comprising both crystal field split substates of Ar 3p$_{3/2}$, with a FWHM ($w$) of only 0.4 eV.
@@
 For pure Xe clusters, an asymmetry observed in the Xe 5p$_{3/2}$ part has no counterpart in the respective spectra from the mixed clusters.
-This might be caused by the difference in photon energy, as can be seen from a comparison to literature spectra (ArXe at $h\nu = 90$ eV in Ref.\ \citenum{lindblad}, Xe at $h\nu = 20$ eV in Ref.\ \citenum{rolles}).
+This might be caused by the difference in photon energy, as can be seen from a comparison to literature spectra (ArXe at $h\nu = 90$ eV in Ref.\ \cite{lindblad}, Xe at $h\nu = 20$ eV in Ref.\ \cite{rolles}).
 For the largest clusters, the nominal size yielded from the jet parameters applied to a pure Xe expansion would correspond to clusters in which bulk atoms far outweigh those on the surface.
@@
 
-For the smallest clusters we have produced, a plausible model is provided by calculated minimum energy structures of Ar$_N$Xe$_{38-N}$ (Fig.\ 7 in Ref.\ \citenum{marques}).
+For the smallest clusters we have produced, a plausible model is provided by calculated minimum energy structures of Ar$_N$Xe$_{38-N}$ (Fig.\ 7 in Ref.\ \cite{marques}).
 We there see that for a Xe content of less than 60\,\%, core-shell systems are {\it not} formed, and although the Xe atoms tend to connect, the degree of Ar-Xe mixing is large.
@@
 Finally, comparing Figure \ref{figure:oval2} to \ref{figure:oval1} reveals that much larger changes in the valence emission spectra occur for changes in the expansion conditions than for changes of the gax mixture.
-This finding is supported by the spectra shown in Ref.\ \citenum{lindblad}.
+This finding is supported by the spectra shown in Ref.\ \cite{lindblad}.
 %

### 2016-01-19 experimental.tex
allow for compilation

@@
 % Leave this citation in place to avoid Latex error
-A comprehensive description can be found in Ref. \citenum{arion}, and here we focus on details specific for the current experiment. Commercial Ar and Xe gas was used. 
+A comprehensive description can be found in Ref. \cite{arion}, and here we focus on details specific for the current experiment. Commercial Ar and Xe gas was used. 
 Separate containers for the two gases were filled up to pressures suitable for producing a certain mixing ratio. The gases were then allowed to mix before the expansion. 
@@
 The storage ring was operated in single bunch conditions.
-Spectra of pure Ar clusters shown for comparison are from Ref. \citenum{foerstel_arg2_2011}, and a spectrum of pure Xe clusters was recorded with the set-up described in Ref. \citenum{hergenhahnprb}.
+Spectra of pure Ar clusters shown for comparison are from Ref. \cite{foerstel_arg2_2011}, and a spectrum of pure Xe clusters was recorded with the set-up described in Ref. \cite{hergenhahnprb}.
 
@@
 For the data shown here, slightly positive bias voltages were used (+1.8 V to +2.2 V) in order to have all electrons arriving at the detector within one BESSY single bunch period (800 ns). 
-The detection efficiency was determined as 0.6, with the method outlined in Ref. \citenum{mucke_review}.
+The detection efficiency was determined as 0.6, with the method outlined in Ref. \cite{mucke_review}.

### 2016-01-19 intro.tex
allow for compilation

@@
 photoelectron spectra with respect to structural features of the 
-mixed clusters is also available.\cite{lundwall} In Ref. \citenum{
+mixed clusters is also available.\cite{lundwall} In Ref. \cite{
 fasshauer2014} it was shown that an analysis of the ICD spectra 
@@
 With increasing Xe content, the formation of Xe-core, Ar-shell systems with a sharp interface between the two species was shown in photoionization experiments.\cite{tchaplyguine,hoener}
-This finding was confirmed by electron diffraction.\cite{Danylchenko,PhysRevA.76.043202} 
-Always, the observed Xe content in the clusters is higher than the Xe content in the expanding gas mixture, as Xe can be condensed much easier than Ar.\cite{hoener,PhysRevA.76.043202}
+This finding was confirmed by electron diffraction.\cite{Danylchenko,Danylchenko07} 
+Always, the observed Xe content in the clusters is higher than the Xe content in the expanding gas mixture, as Xe can be condensed much easier than Ar.\cite{hoener,Danylchenko07}
 %A complementary study used photoelectron-photoion coincidence of
@@
 Xe was also found to diffuse into the interior of Ar clusters in molecular dynamics simulations after pick-up.\cite{Vach_1999} 
-The electronic energy levels of very small Ar-Xe clusters were calculated in Ref.s\ \citenum{fasshauer,Fasshauer13}.
+The electronic energy levels of very small Ar-Xe clusters were calculated in Ref.s\ \cite{fasshauer,Fasshauer13}.
 Interestingly, it was found that Ar 3s$^{-1}$ is stable 

### 2016-01-19 pics/replace.py
add Ar_x Xe_y pics

@@ -16,7 +16,7 @@ count = 0
 rootdir = os.getcwd()
 #outfile = open('','w')
 
-for filename in glob.glob("xe_3_in.tex"):
+for filename in glob.glob("Ar3Xe35.tex"):
    print filename
    infile = open(filename, 'r')
    outfile = open('tmpfile', 'w')
@@ -24,7 +24,7 @@ for filename in glob.glob("xe_3_in.tex"):
 #   outfile.write(' 300 10000 0\n')
 
 #   replacements = {'includegraphics[scale=0.5]':'input', '/compl':'/schale', '/incompl':'/in-shell', '_':'-core', '.ps':'', 'caps':'cap'}
-   replacements = {'arxe':'../data/arxe'}
+   replacements = {'13':'3','25':'35'}
 
    for line in infile:
       if 'FloatBarrier' not in line:

### 2016-01-19 replace.py
add new cluster strutures and ICD efficiencies for them

@@ -1,0 +1,39 @@
+#! /opt/local/bin/python
+
+# IMPORT
+import os
+import sys
+import shutil
+import string
+import glob
+import math
+
+ls = os.listdir('.')
+ls.sort()
+
+count = 0
+
+rootdir = os.getcwd()
+#outfile = open('','w')
+
+for filename in glob.glob("*.tex"):
+#for filename in glob.glob("schale08.tex"):
+   print filename
+   infile = open(filename, 'r')
+   outfile = open('tmpfile', 'w')
+
+   
+#   replacements = {'includegraphics[scale=0.5]':'input', '/compl':'/schale', '/incompl':'/in-shell', '_':'-core', '.ps':'', 'caps':'cap'}
+   replacements = {'citenum':'cite'}
+
+   for line in infile:
+      if 'FloatBarrier' not in line:
+          for src, target in replacements.iteritems():
+              line = line.replace(src, target)
+          outfile.write(line)
+
+   infile.close()
+   outfile.close()
+
+   shutil.copyfile('tmpfile',filename)
+   os.remove('tmpfile')

### 2016-01-20 exp_results.tex
values for atomic binding energies used in the simulations updated

--- 2016-01-18 exp_results.tex
@@
 Uncertainties are estimated as $\pm$3\,\% for the Xe content and 0.05~eV for the binding energies. 
-For reference, the row labelled `(th.)' gives the binding energies used in the simulations of this paper (same as in Ref. \citenum{Fasshauer13}), and the last row their atomic counterparts. 
-Values for Ar 3p in these two rows refer to the fine structure states.
+For reference, the row labelled `(th.)' gives the binding energies used in the simulations of this paper, and the last row their atomic counterparts. 
+Values for Ar 3p in the last row refer to the fine structure states.
 \label{tab:valence} }
@@
 \midrule
-%
- Ar, Xe & (th.) && 14.76|15.54 && 12.53 & 10.83 &&\\
+% Date: Wed, 20 Jan 2016 11:27:39, From: Elke Faﬂhauer <elke.fasshauer@uit.no>
+ Ar, Xe & (th.) && 15.3 && 13.0 & 11.5 &&\\
 %
@@
 A small, but systematic decrease of the binding energy is observed when the cluster size is increased. 
-The value assumed in the simulations is 28.60 eV.\cite{Fasshauer13}
+The value assumed in the simulations is 28.7 eV.
 

### 2016-01-25 exp_results.tex

--- 2016-01-19 exp_results.tex
@@
 Uncertainties are estimated as $\pm$3\,\% for the Xe content and 0.05~eV for the binding energies. 
-For reference, the row labelled `(th.)' gives the binding energies used in the simulations of this paper (same as in Ref. \cite{Fasshauer13}), and the last row their atomic counterparts. 
-Values for Ar 3p in these two rows refer to the fine structure states.
+For reference, the row labelled `(th.)' gives the binding energies used in the simulations of this paper, and the last row their atomic counterparts. 
+Values for Ar 3p in the last row refer to the fine structure states.
 \label{tab:valence} }

### 2016-01-25 theory.tex
allow for compilation
Kommentar hinzugefügt -> bitte einmal lesen

--- 2015-11-09 theory.tex
@@
 %
-depending on constants ($a_{m,k}=4,2$)
+depending on constants ($a_{m,k}=4,2$) {\it Q: ??? Hei\ss t das, $a_{m.k}$ kann die Werte 2 und 4 annehmen? \color{red}{Ja, genau das heißt es. Zum Vergleich
+kannst du dir Formel 19 in \cite{Fasshauer13} ansehen.}}
 as well as experimental properties
@@
 the program HARDRoC \cite{HARDRoC,fasshauer2014} using the
-experimental ionization energies of Table \ref{}
-and data from the literature given in Tables \ref{} and \ref{}.
+experimental ionization energies of Table \ref{tab:valence}
+and data from the literature given in Tables II and III.
 This choice is identical to the one made in Reference \cite{Fasshauer13}.

### 2016-01-27 structures.tex
change characterization in table 2

@@
           atoms on different surfaces of the argon icosahedron, varying in Xe-Xe distance:
-          (a) closest possible, (b) middle, (c) furthest away.}
+          (a) closest possible, (b) middle, (c) furthest away. They refer to
+          numbers 8--10 in Table \ref{table:theo_gammas}.}
  \label{figure:cluster_2_overview}
@@
           grouped on one side, (c) six xenon atoms distributed randomly
-          in a 55 atoms cluster.}
+          in a 55 atoms cluster. They refer to numbers 11, 17 and 18
+          in Table \ref{table:theo_gammas}.}
  \label{figure:cluster_3_overview}

### 2016-01-27 theo_results.tex
change characterization in table 2

@@
 %
-\begin{table*}[th]
+\begin{table}[h]
+\small
 \centering
-\caption{Calculated properties of some model clusters. Columns `ICD' and `ETMD'
+\caption{Structural and calculated properties of some model clusters.
+The cluster structures are characterized by the number of
+Ar and Xe atoms in the cluster. The first group has a xenon core
+surrounded by argon atoms while the second group except for
+number 18 has a xenon core. The last group of structures was taken
+from Reference \cite{} and contains various structures.
+The structures are then categorized (str. cl.) into core-layer (cl)
+structures, structures, where single atoms in the outermost layer
+are replaced by the different atom type (in) and mixed structures, that
+do not show a clear layer structure. In case one atom is placed on top
+of a cluster or replaces a different atom in the outermost layer, its
+position is given as surface/edge/vertex. In case two atoms are placed
+on top of a cluster, their relative position is declared.
+The columns `ICD' and `ETMD'
 are the respective partial decay widths
@@
 }
-\begin{tabular}{lrrrccr}
+\begin{tabular}{rrrrcccccr}
 \toprule
-name                 & Xe atoms & Ar atoms & Xe$_{\rm cl}$ \% & ICD   &  ETMD & \% ICD\\ %$\Gamma_{\rm ICD,ETMD}$\\
+\# & \# Xe & \# Ar & Xe$_{\rm cl}$\% & str. cl. & pos. & rel. pos. & ICD   &  ETMD & \% ICD\\ %$\Gamma_{\rm ICD,ETMD}$\\
 \midrule
-ArXe\_2\_1atom       &      1   &     12   &  7.7  & 0.000 & 0.000 &  --\\ %    0.0            \\
-ArXe\_3\_1atom       &      1   &     54   &  1.8  & 0.000 & 0.000 &  --\\ %    0.0            \\ 
-ArXe\_3\_2atom       &      2   &     53   &  3.6  & 0.033 & 0.167 &  16.7\\ %2.006$\cdot 10^{-5}$ \\
-ArXe\_8\_1layer      &   1415   &    642   & 68.8  & 7.039 & 2.573 &  73.2\\ %9.612$\cdot 10^{-4}$ \\
+ 1 &     1 &    12 &  7.7  & cl    &         &          & 0.000 & 0.000 &  --\\ %    0.0            \\     ArXe\_2\_1atom      
+ 2 &     1 &    54 &  1.8  & cl    &         &          & 0.000 & 0.000 &  --\\ %    0.0            \\     ArXe\_3\_1atom      
+ 3 &     2 &    53 &  3.6  & cl    &         &          & 0.033 & 0.167 &  16.7\\ %2.006$\cdot 10^{-5}$ \\ ArXe\_3\_2atom      
+ 4 &  1415 &   642 & 68.8  & cl    &         &          & 7.039 & 2.573 &  73.2\\ %9.612$\cdot 10^{-4}$ \\ ArXe\_8\_1layer     
                                                                                              \midrule
-XeAr\_2\_surface     &      1   &     13   &  7.1  & 0.792 & 0.000 & 100.0\\ %7.922$\cdot 10^{-5}$ \\
-XeAr\_2\_edge        &      1   &     13   &  7.1  & 0.013 & 0.000 & 100.0\\ %1.320$\cdot 10^{-6}$ \\
-XeAr\_2\_vertex      &      1   &     13   &  7.1  & 0.050 & 0.000 & 100.0\\ %5.013$\cdot 10^{-6}$ \\
-XeAr\_2\_2top        &      2   &     13   & 13.3  & 0.101 & 0.151 &  40.1\\ %2.523$\cdot 10^{-5}$ \\
-XeAr\_2\_2midtop     &      2   &     13   & 13.3  & 0.159 & 0.008 &  95.4\\ %1.665$\cdot 10^{-5}$ \\
-XeAr\_2\_2endtop     &      2   &     13   & 13.3  & 0.159 & 0.002 &  98.9\\ %1.605$\cdot 10^{-5}$ \\
-XeAr\_3\_surface     &      1   &     55   &  1.8  & 0.064 & 0.000 & 100.0\\ %6.371$\cdot 10^{-6}$ \\
-XeAr\_3\_edge        &      1   &     55   &  1.8  & 0.048 & 0.000 & 100.0\\ %4.791$\cdot 10^{-6}$ \\
-XeAr\_3\_vertex      &      1   &     55   &  1.8  & 0.027 & 0.000 & 100.0\\ %2.701$\cdot 10^{-6}$ \\
-XeAr\_3\_edge\_in    &      1   &     54   &  1.8  & 0.077 & 0.000 & 100.0\\ %7.708$\cdot 10^{-6}$ \\
-XeAr\_3\_vertex\_in  &      1   &     54   &  1.8  & 0.053 & 0.000 & 100.0\\ %5.258$\cdot 10^{-6}$ \\
-XeAr\_3\_2in         &      2   &     53   &  3.6  & 0.117 & 0.055 &  68.1\\ %1.711$\cdot 10^{-5}$ \\
-XeAr\_3\_6in         &      6   &     49   & 10.9  & 0.375 & 0.405 &  48.1\\ %7.796$\cdot 10^{-5}$ \\
-XeAr\_3\_6\_scat     &      6   &     49   & 10.9  & 0.292 & 0.674 &  30.3\\ %9.660$\cdot 10^{-5}$ \\
+ 5 &     1 &    13 &  7.1  & cl    & surface &          & 0.792 & 0.000 & 100.0\\ %7.922$\cdot 10^{-5}$ \\ XeAr\_2\_surface    
+ 6 &     1 &    13 &  7.1  & cl    & edge    &          & 0.013 & 0.000 & 100.0\\ %1.320$\cdot 10^{-6}$ \\ XeAr\_2\_edge       
+ 7 &     1 &    13 &  7.1  & cl    & vertex  &          & 0.050 & 0.000 & 100.0\\ %5.013$\cdot 10^{-6}$ \\ XeAr\_2\_vertex     
+ 8 &     2 &    13 & 13.3  & cl    &         & closest  & 0.101 & 0.151 &  40.1\\ %2.523$\cdot 10^{-5}$ \\ XeAr\_2\_2top       
+ 9 &     2 &    13 & 13.3  & cl    &         & middle   & 0.159 & 0.008 &  95.4\\ %1.665$\cdot 10^{-5}$ \\ XeAr\_2\_2midtop    
+10 &     2 &    13 & 13.3  & cl    &         & furthest & 0.159 & 0.002 &  98.9\\ %1.605$\cdot 10^{-5}$ \\ XeAr\_2\_2endtop    
+11 &     1 &    55 &  1.8  & cl    & surface &          & 0.064 & 0.000 & 100.0\\ %6.371$\cdot 10^{-6}$ \\ XeAr\_3\_surface    
+12 &     1 &    55 &  1.8  & cl    & edge    &          & 0.048 & 0.000 & 100.0\\ %4.791$\cdot 10^{-6}$ \\ XeAr\_3\_edge       
+13 &     1 &    55 &  1.8  & cl    & vertex  &          & 0.027 & 0.000 & 100.0\\ %2.701$\cdot 10^{-6}$ \\ XeAr\_3\_vertex     
+14 &     1 &    54 &  1.8  & in    & edge    &          & 0.077 & 0.000 & 100.0\\ %7.708$\cdot 10^{-6}$ \\ XeAr\_3\_edge\_in   
+15 &     1 &    54 &  1.8  & in    & vertex  &          & 0.053 & 0.000 & 100.0\\ %5.258$\cdot 10^{-6}$ \\ XeAr\_3\_vertex\_in 
+16 &     2 &    53 &  3.6  & in    &         &          & 0.117 & 0.055 &  68.1\\ %1.711$\cdot 10^{-5}$ \\ XeAr\_3\_2in        
+17 &     6 &    49 & 10.9  & in    &         &          & 0.375 & 0.405 &  48.1\\ %7.796$\cdot 10^{-5}$ \\ XeAr\_3\_6in        
+18 &     6 &    49 & 10.9  & mixed &         &          & 0.292 & 0.674 &  30.3\\ %9.660$\cdot 10^{-5}$ \\ XeAr\_3\_6\_scat    
+                                                                                                 \midrule
+19 &     2 &    36 &  5.3  & cl    &         &          & 0.117 & 0.151 &  43.6\\                        % Ar$_{36}$Xe$_{2}$   
+20 &     4 &    34 & 10.5  & mixed &         &          & 0.248 & 0.587 &  29.7\\                        % Ar$_{34}$Xe$_{4}$   
+21 &     5 &    33 & 13.2  & mixed &         &          & 0.335 & 0.844 &  28.4\\                        % Ar$_{33}$Xe$_{5}$   
+22 &    13 &    25 & 34.2  & mixed &         &          & 0.828 & 5.414 &  13.3\\                        % Ar$_{25}$Xe$_{13}$  
+23 &    24 &    14 & 63.2  & mixed &         &          & 1.488 &16.718 &   8.2\\                        % Ar$_{14}$Xe$_{24}$  
+24 &    25 &    13 & 65.8  & in    &         &          & 1.432 & 4.995 &  22.3\\                        % Ar$_{13}$Xe$_{25}$  
+25 &    35 &     3 & 92.1  & in    &         &          & 2.017 & 7.051 &  22.2\\                        % Ar$_{3}$Xe$_{35}$   
 \bottomrule
@@
 \label{table:theo_gammas}
-\end{table*}
+\end{table}
 %
@@
           clearly visible. In the other two cases the spectra are dominated by
-          the ICD spectrum.
-          {\it Q: Ich sehe die traces für die 'furthest' Konfiguration nicht(?!) Q: Warum ist in diesen (und vielen anderen) Bildern jedes Label doppelt?}}
+          the ICD spectrum.}
  \label{figure:2tops}
@@
           of a xenon core of 1415 atoms surrounded by one complete layer of
-          argon atoms. {\it Q: War: `two complete layers' - bitte \"uberpr\"ufen.} The ICD and ETMD peak overlap such, that the peak structure
-          might not be visible.}
+          argon atoms. The ICD and ETMD peak overlap such, that the peak
+          structure might not be visible.}
  \label{figure:xe_8_lay1}

### 2016-01-27 exp_results.tex
add comments

@@
 \midrule
-% Date: Wed, 20 Jan 2016 11:27:39, From: Elke Faﬂhauer <elke.fasshauer@uit.no>
+% Date: Wed, 20 Jan 2016 11:27:39, From: Elke Fa?hauer <elke.fasshauer@uit.no>
  Ar, Xe & (th.) && 15.3 && 13.0 & 11.5 &&\\
@@
 The photon energy was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
+{\color{red}{Die Stabilisierung der Xe-bulk Atome ist in den gemischten Cluster
+ höher als in den gemischten Clustern. Das ist ungewöhnlich. Habt ihr hier
+ verschiedene CLustergrößen?}}
 }
@@
 $\langle N\rangle = 190$, black trace), the maximum at low binding energies becomes more pronounced, and is identified with emission from the cluster interior.\cite{hergenhahnprb,rolles}
-At the particular photon energy selected here, atop of this band a sharp feature is also visible (in Figure \ref{figure:oval1} at a kinetic energy of about 1.8 eV). 
-For larger clusters (above $\langle N\rangle \approx 100$), it shows a dispersion characteristic for photoemission of crystalline bulk matter.\cite{foerstel_arg1_2010,foerstel_arg2_2011}
+At the particular photon energy selected here, atop of this band a sharp
+feature is also visible (in Figure \ref{figure:oval1} at a kinetic energy of
+about 1.8 eV). {\color{red}{Das Maximum ist bei etwa 1.8. Meinst du nicht oberhalb
+von 1.8?}}
+For larger clusters (above $\langle N\rangle \approx 100$),
+it shows a dispersion {\color{red}{Was genau meinst du mit dispersion?}}
+characteristic for photoemission of crystalline bulk matter.\cite{foerstel_arg1_2010,foerstel_arg2_2011}
 
 Ar 3p spectra of the mixed clusters show neither of these traits.
-Rather, the Ar band is symmetric, less wide than in the pure clusters and at a higher binding energy. 
+Rather, the Ar band is symmetric,
+less wide than in the pure clusters and at a higher binding energy.
+{\color{red}{Wenn du dich auf panel b beziehst, dann kann das zwar sein, man sieht
+es aber aus der Abbildung nicht. Kannst du das noch genauer belegen?}}
 We characterize the spectral shape by giving a single value for the Ar 3p binding energy, and the FWHM of the feature.
@@
 At least for the 5p$_{1/2}$, this would be a seen as a clear asymmetry towards the low binding energy side, which is not observed in our spectra.
+{\color{red}{Hier wäre es wichtig zu bemerken, dass es sich um die Bindungsenergie
+ des Elektrons und nicht der Atome im Cluster handelt. Das hat mich an mehreren
+ Stellen irritiert.}}
 
@@
 Possibly, some clusters of our ensemble already are in the core-shell regime, which would lead to an even lower 3p width.
+{\color{red}{Falsch. Für core-shell Strukturen müsste der Peak wieder breiter sein,
+ da es dann wieder Argon Atome ohne Xenonnachbarn gibt (zumindest bei mehr als
+ einer Argonschicht).}}
 For the largest clusters we have produced (Figure \ref{figure:oval1}b), the low binding energy of the Xe lines and the broadening of the Ar feature without appearance of the `bulk Ar'-maximum, supports formation of a Xe core covered by at least two layers of Ar.
 If the scaling law size for a pure Ar expansion is taken as the lower limit for the cluster size, from the observed Xe content we arrive at clusters composed of a Xe core with four layers, covered by three layers of Ar (see Supporting Information).
+{\color{red}{Dann sollten wir zumindest diesen Fall auch berechnen. Meinst du
+$c=4$ oder 4 Schichten um ein Atom? -> Fehlt auch noch in supporting information}}
 
-Finally, comparing Figure \ref{figure:oval2} to \ref{figure:oval1} reveals that much larger changes in the valence emission spectra occur for changes in the expansion conditions than for changes of the gax mixture.
+Finally, comparing Figure \ref{figure:oval2} to Figure \ref{figure:oval1} reveals
+that much larger changes in the valence emission spectra occur for changes in
+the expansion conditions than for changes of the gas mixture.
 This finding is supported by the spectra shown in Ref.\ \cite{lindblad}.
@@
 To arrive at quantitative results, we have performed least squares fits of the non-coincident and coincident $e_1$ spectra.
-The fits assumed one or two Gaussian peaks, resp., atop of a background modelled by two more Gaussian curves with a very large widths.
+The fits assumed one or two Gaussian peaks, resp., atop of a background modelled by two more Gaussian curves with very large widths.
 The peak pertaining to the Ar 3s cluster photoline, with the background added, is shown by the blue and red solid line in Figure \ref{figure:ival}.

### 2016-05-16 theo_results.tex
small reformulations

@@
 kinetic energy of the secondary electron for a given channel.
-Since the 55 argon atom core cluster is larger and therefore
-has Ar-Xe pairs with larger distances its spectrum is extended to
+Since the cluster with an Ar core of 55 atoms is larger, and therefore
+contains Ar-Xe pairs with larger distances, its spectrum extends to
 higher energies.
 %energies as well.
-This effect holds for all clusters.
+This relation between ICD energy and cluster size holds true for all cluster structures.
 %This explains why the ICD spectrum for larger clusters extends to higher energies, and holds for all cluster structures.

### 2016-05-16 exp_results.tex
small reformulations

--- 2016-01-25 exp_results.tex
@@
 At the particular photon energy selected here, atop of this band a sharp feature is also visible (in Figure \ref{figure:oval1} at a kinetic energy of about 1.8 eV).
-For larger clusters (above $\langle N\rangle \approx 100$), it shows a dispersion characteristic for photoemission of crystalline bulk matter.\cite{foerstel_arg1_2010,foerstel_arg2_2011}
+For larger clusters (above $\langle N\rangle \approx 100$), over a range of photon energies of about 3 eV, its appararent binding energy changes in a way which is reminiscent to photoemission of crystalline bulk matter (`dispersion').\cite{foerstel_arg1_2010,foerstel_arg2_2011}
 
-Ar 3p spectra of the mixed clusters show neither of these traits.
+Ar 3p spectra of the smaller mixed clusters (Figure \ref{figure:oval1}c, Figure \ref{figure:oval2}) show neither of these traits.
 Rather, the Ar band is symmetric, less wide than in the pure clusters and at a higher binding energy.
+Even for very large clusters (Figure \ref{figure:oval1}b) the asymmetry of the 3p band and the `dispersing feature' do not appear.
 We characterize the spectral shape by giving a single value for the Ar 3p binding energy, and the FWHM of the feature.
@@
 For the largest clusters, the nominal size yielded from the jet parameters applied to a pure Xe expansion would correspond to clusters in which bulk atoms far outweigh those on the surface.
-At least for the 5p$_{1/2}$, this would be a seen as a clear asymmetry towards the low binding energy side, which is not observed in our spectra.
+At least for the 5p$_{1/2}$ photoelectron line, this would be seen as a clear asymmetry towards the low binding energy side, which is not observed in our spectra.
 
@@
 We believe this leads to the Ar 3p narrowing pointed out above.
-Possibly, some clusters of our ensemble already are in the core-shell regime, which would lead to an even lower 3p width.
+For Figure \ref{figure:oval2}, possibly, some clusters of our ensemble already are in the core-shell regime, which would lead to an even lower 3p width.
 For the largest clusters we have produced (Figure \ref{figure:oval1}b), the low binding energy of the Xe lines and the broadening of the Ar feature without appearance of the `bulk Ar'-maximum, supports formation of a Xe core covered by at least two layers of Ar.
@@
 
-Finally, comparing Figure \ref{figure:oval2} to \ref{figure:oval1} reveals that much larger changes in the valence emission spectra occur for changes in the expansion conditions than for changes of the gax mixture.
+Finally, comparing Figure \ref{figure:oval2} to Figure \ref{figure:oval1} reveals
+that much larger changes in the valence emission spectra occur for changes in
+the expansion conditions than for changes of the gas mixture.
 This finding is supported by the spectra shown in Ref.\ \cite{lindblad}.

### 2016-05-16 suppl.tex
small reformulations

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Composition of core-shell clusters}
+%
+\begin{figure}
+ \centering
+ \includegraphics[width=8.2cm]{pics/figure_layers.pdf}
+ \caption{
+ Argon content of ideal icosaedric Xe-core, Ar-shell systems. 
+ The relative number of surface atoms decreases with increasing cluster size.
+ The hatched area corresponds to the Ar content of the largest clusters produced in our experiments (label `XL').
+ \label{figure:layers}
+ }
+\end{figure}
+%
+For icosaedric clusters, the number of atoms in every shell is given.\cite{Mackay}
+For a core-shell system in this ideal geometry, the relative content of both species can therefore readily be calculated.
+In Figure \ref{figure:layers} we draw the Ar content of Xe-core, Ar-shell systems with one, two and three full Ar outer layers. 
+A comparison of these graphs with Tables 1 and 3 of the main article shows that the largest clusters produced in our experiments (`XL'), for which a core-shell structure is probable, may have between 923 and 1415 atoms in total, corresponding to three and four Xe shells around a central Xe atom, followed by three Ar outer layers.
+The Xe content for these systems is 0.16 and 0.22, resp.
+%
+%
 \section{Electron-electron coincidence spectra}

### 2016-05-16 intro.tex
Querverweise zwischen Text, Tab. 2, Bildern

@@
 Xe was also found to diffuse into the interior of Ar clusters in molecular dynamics simulations after pick-up.\cite{Vach_1999} 
-The electronic energy levels of very small Ar-Xe clusters were calculated in Ref.s\ \cite{fasshauer,Fasshauer13}.
+The electronic energy levels of very small Ar-Xe clusters were calculated in Ref.s~ \citenum{fasshauer,Fasshauer13}.
 Interestingly, it was found that Ar 3s$^{-1}$ is stable 

### 2016-05-16 structures.tex
Querverweise zwischen Text, Tab. 2, Bildern

@@
 structure: the minimum size and the xenon content. In the following we will 
-use these to construct possible cluster structures for which we will later
+use these to construct representative cluster structures, for which we will 
 simulate the ICD and ETMD spectra. At this point we put in a variety of structures,
@@
 Avogadro programme \cite{}.
+All cluster structures are listed in Table \ref{table:theo_gammas}.
 %
@@
           (a) closest possible, (b) middle, (c) furthest away. They refer to
-          numbers 8--10 in Table \ref{table:theo_gammas}.}
+          numbers 9--11 in Table \ref{table:theo_gammas}.}
  \label{figure:cluster_2_overview}
@@
           grouped on one side, (c) six xenon atoms distributed randomly
-          in a 55 atoms cluster. They refer to numbers 11, 17 and 18
+          in a 55 atoms cluster. They refer to numbers 12, 18 and 19
           in Table \ref{table:theo_gammas}.}
@@
        for one additional xenon atom
-       on top of surface of a \unit[55]{atoms} argon core,
- \item substitute one argon atom in a surface / edge / vertex position,
+       on top of surface of a \unit[55]{atoms} argon core
+       (Table \ref{table:theo_gammas}, \#6--8, \#12--14),
+ \item substitute one argon atom in a surface / edge / vertex position
+       (Table \ref{table:theo_gammas}, \#15--16),
  \item substitute one or two argon atoms in the core of the argon cluster
-       by xenon atom(s) for the simulation of the core-shell structures,
+       by xenon atom(s) for the simulation of the core-shell structures
+       (Table \ref{table:theo_gammas}, \#1--3),
  \item add two xenon atoms on top of surfaces of a 13 atoms argon core
@@
        in order to achieve a xenon content in the cluster close to the
-       measured one (see below),
+       measured one (see below)
+       (Table \ref{table:theo_gammas}, \#9--11),
  \item substitute six argon atoms of a 55 atoms argon cluster by xenon
@@
        (see Figure \ref{figure:cluster_3_overview} b) and c)) in order to
-       achieve a xenon content in the cluster close to the measured one.
+       achieve a xenon content in the cluster close to the measured one
+       (Table \ref{table:theo_gammas}, \#18--19).
 \end{itemize}
 %
-Furthermore, for comparison with the largest measured ArXe clusters, we constructed a core-shell structure with a core of 1415 xenon atoms and one additional complete layer of argon atoms.
+Furthermore, for comparison with the largest measured ArXe clusters, we constructed also larger core-shell structures (Table \ref{table:theo_gammas}, \#4--5).

### 2016-05-16 theo_results.tex
Querverweise zwischen Text, Tab. 2, Bildern

--- 2016-01-18 theo_results.tex
@@
 %
-\begin{table*}[th]
+\begin{table}[h]
+\small
 \centering
-\caption{Calculated properties of some model clusters. Columns `ICD' and `ETMD'
-are the respective partial decay widths
-in \unit[$10^{-4}$]{eV}, and `\% ICD' gives the percentage of ICD in the
-total decay width.
+\caption{Structural and calculated properties of some model clusters.
+The cluster structures are characterized by the number of Ar and Xe atoms, and are arranged in three groups according to gross structural properties. 
+The first group contains Xe core-Ar shell systems of various size and relative Xe content.
+In the second group, model structures for small clusters are displayed, in which 1-2 Xe atoms are added at systematically varied locations to an icosahedric Ar clusters consisting of one or two full shells, or in which 1-6 Ar atoms of such cluster were replaced by Xe atoms, while keeping the geometry of the original Xe lattice.
+The last group contains data for calculated minimal energy structures of mixed ArXe clusters.
+\protect\cite{marques}
+The columns `ICD' and `ETMD' are the respective partial decay widths in \unit[$10^{-4}$]{eV}, and `\% ICD' gives the percentage of ICD in the total decay width.
+See text for details.
+\label{table:theo_gammas}
 }
-\begin{tabular}{lrrrccr}
+\begin{tabular}{rrrrcccccrrr}
 \toprule
-name                 & Xe atoms & Ar atoms & Xe$_{\rm cl}$ \% & ICD   &  ETMD & \% ICD\\ %$\Gamma_{\rm ICD,ETMD}$\\
+\# & \# Xe & \# Ar & Xe$_{\rm cl}$\% & str. cl. & pos. & rel. pos. & ICD   &  ETMD & \% ICD & Fig.\\ %$\Gamma_{\rm ICD,ETMD}$\\
 \midrule
-ArXe\_2\_1atom       &      1   &     12   &  7.7  & 0.000 & 0.000 &  --\\ %    0.0            \\
-ArXe\_3\_1atom       &      1   &     54   &  1.8  & 0.000 & 0.000 &  --\\ %    0.0            \\ 
-ArXe\_3\_2atom       &      2   &     53   &  3.6  & 0.033 & 0.167 &  16.7\\ %2.006$\cdot 10^{-5}$ \\
-ArXe\_8\_1layer      &   1415   &    642   & 68.8  & 7.039 & 2.573 &  73.2\\ %9.612$\cdot 10^{-4}$ \\
+ 1 &     1 &    12 &  7.7  & cl    &         &          & 0.000 & 0.000 &  -- &\\ %    0.0            \\     ArXe\_2\_1atom      
+ 2 &     1 &    54 &  1.8  & cl    &         &          & 0.000 & 0.000 &  -- & \ref{figure:xe_3_in}\\ %    0.0            \\     ArXe\_3\_1atom      
+ 3 &     2 &    53 &  3.6  & cl    &         &          & 0.033 & 0.167 &  16.7& \ref{figure:xe_3_in}\\ %2.006$\cdot 10^{-5}$ \\ ArXe\_3\_2atom      
+ 4 &  1415 &   642 & 68.8  & cl    &         &          & 7.039 & 2.573 &  73.2& suppl.\\ %9.612$\cdot 10^{-4}$ \\ ArXe\_8\_1layer     
+ 5 &   561 &  3310 & 14.5  & cl    &         &          &       &       &  85  & \ref{figure:xe_6_lay5}\\ % c6l5
+
 \midrule
-XeAr\_2\_surface     &      1   &     13   &  7.1  & 0.792 & 0.000 & 100.0\\ %7.922$\cdot 10^{-5}$ \\
-XeAr\_2\_edge        &      1   &     13   &  7.1  & 0.013 & 0.000 & 100.0\\ %1.320$\cdot 10^{-6}$ \\
-XeAr\_2\_vertex      &      1   &     13   &  7.1  & 0.050 & 0.000 & 100.0\\ %5.013$\cdot 10^{-6}$ \\
-XeAr\_2\_2top        &      2   &     13   & 13.3  & 0.101 & 0.151 &  40.1\\ %2.523$\cdot 10^{-5}$ \\
-XeAr\_2\_2midtop     &      2   &     13   & 13.3  & 0.159 & 0.008 &  95.4\\ %1.665$\cdot 10^{-5}$ \\
-XeAr\_2\_2endtop     &      2   &     13   & 13.3  & 0.159 & 0.002 &  98.9\\ %1.605$\cdot 10^{-5}$ \\
-XeAr\_3\_surface     &      1   &     55   &  1.8  & 0.064 & 0.000 & 100.0\\ %6.371$\cdot 10^{-6}$ \\
-XeAr\_3\_edge        &      1   &     55   &  1.8  & 0.048 & 0.000 & 100.0\\ %4.791$\cdot 10^{-6}$ \\
-XeAr\_3\_vertex      &      1   &     55   &  1.8  & 0.027 & 0.000 & 100.0\\ %2.701$\cdot 10^{-6}$ \\
-XeAr\_3\_edge\_in    &      1   &     54   &  1.8  & 0.077 & 0.000 & 100.0\\ %7.708$\cdot 10^{-6}$ \\
-XeAr\_3\_vertex\_in  &      1   &     54   &  1.8  & 0.053 & 0.000 & 100.0\\ %5.258$\cdot 10^{-6}$ \\
-XeAr\_3\_2in         &      2   &     53   &  3.6  & 0.117 & 0.055 &  68.1\\ %1.711$\cdot 10^{-5}$ \\
-XeAr\_3\_6in         &      6   &     49   & 10.9  & 0.375 & 0.405 &  48.1\\ %7.796$\cdot 10^{-5}$ \\
-XeAr\_3\_6\_scat     &      6   &     49   & 10.9  & 0.292 & 0.674 &  30.3\\ %9.660$\cdot 10^{-5}$ \\
+ 6 &     1 &    13 &  7.1  & cl    & surface &          & 0.792 & 0.000 & 100.0& \ref{figure:surf}\\ %7.922$\cdot 10^{-5}$ \\ XeAr\_2\_surface    
+ 7 &     1 &    13 &  7.1  & cl    & edge    &          & 0.013 & 0.000 & 100.0&\\ %1.320$\cdot 10^{-6}$ \\ XeAr\_2\_edge       
+ 8 &     1 &    13 &  7.1  & cl    & vertex  &          & 0.050 & 0.000 & 100.0&\\ %5.013$\cdot 10^{-6}$ \\ XeAr\_2\_vertex     
+ 9 &     2 &    13 & 13.3  & cl    &         & closest  & 0.101 & 0.151 &  40.1& \ref{figure:2tops}\\ %2.523$\cdot 10^{-5}$ \\ XeAr\_2\_2top       
+10 &     2 &    13 & 13.3  & cl    &         & middle   & 0.159 & 0.008 &  95.4& \ref{figure:2tops}\\ %1.665$\cdot 10^{-5}$ \\ XeAr\_2\_2midtop    
+11 &     2 &    13 & 13.3  & cl    &         & furthest & 0.159 & 0.002 &  98.9& \ref{figure:2tops}\\ %1.605$\cdot 10^{-5}$ \\ XeAr\_2\_2endtop    
+12 &     1 &    55 &  1.8  & cl    & surface &          & 0.064 & 0.000 & 100.0& \ref{figure:surf}\\ %6.371$\cdot 10^{-6}$ \\ XeAr\_3\_surface    
+13 &     1 &    55 &  1.8  & cl    & edge    &          & 0.048 & 0.000 & 100.0&\\ %4.791$\cdot 10^{-6}$ \\ XeAr\_3\_edge       
+14 &     1 &    55 &  1.8  & cl    & vertex  &          & 0.027 & 0.000 & 100.0&\\ %2.701$\cdot 10^{-6}$ \\ XeAr\_3\_vertex     
+15 &     1 &    54 &  1.8  & in    & edge    &          & 0.077 & 0.000 & 100.0&\\ %7.708$\cdot 10^{-6}$ \\ XeAr\_3\_edge\_in   
+16 &     1 &    54 &  1.8  & in    & vertex  &          & 0.053 & 0.000 & 100.0&\\ %5.258$\cdot 10^{-6}$ \\ XeAr\_3\_vertex\_in 
+17 &     2 &    53 &  3.6  & in    &         &          & 0.117 & 0.055 &  68.1&\\ %1.711$\cdot 10^{-5}$ \\ XeAr\_3\_2in        
+18 &     6 &    49 & 10.9  & in    &         &          & 0.375 & 0.405 &  48.1& \ref{figure:ar_3_6in}\\ %7.796$\cdot 10^{-5}$ \\ XeAr\_3\_6in        
+19 &     6 &    49 & 10.9  & mixed &         &          & 0.292 & 0.674 &  30.3& \ref{figure:ar_3_6in}\\ %9.660$\cdot 10^{-5}$ \\ XeAr\_3\_6\_scat    
+                                                                                                 \midrule
+20 &     2 &    36 &  5.3  & cl    &         &          & 0.117 & 0.151 &  43.6& suppl.\\                        % Ar$_{36}$Xe$_{2}$   
+21 &     4 &    34 & 10.5  & mixed &         &          & 0.248 & 0.587 &  29.7& suppl.\\                        % Ar$_{34}$Xe$_{4}$   
+22 &     5 &    33 & 13.2  & mixed &         &          & 0.335 & 0.844 &  28.4& suppl.\\                        % Ar$_{33}$Xe$_{5}$   
+23 &    13 &    25 & 34.2  & mixed &         &          & 0.828 & 5.414 &  13.3& suppl.\\                        % Ar$_{25}$Xe$_{13}$  
+24 &    24 &    14 & 63.2  & mixed &         &          & 1.488 &16.718 &   8.2& suppl.\\                        % Ar$_{14}$Xe$_{24}$  
+25 &    25 &    13 & 65.8  & in    &         &          & 1.432 & 4.995 &  22.3& suppl.\\                        % Ar$_{13}$Xe$_{25}$  
+26 &    35 &     3 & 92.1  & in    &         &          & 2.017 & 7.051 &  22.2& suppl.\\                        % Ar$_{3}$Xe$_{35}$   
 \bottomrule
 \end{tabular}
-\label{table:theo_gammas}
-\end{table*}
+\end{table}
 %
@@
  \centering
- \includegraphics[width=8.5cm]{pics/xe_8_1lay.pdf}
+ \includegraphics[width=8.5cm]{pics/xe_6_5lay.pdf}
  \caption{Same as Figure \protect\ref{figure:2tops}, for a large cluster consisting
-          of a xenon core of 1415 atoms surrounded by one complete layer of
-          argon atoms. {\it Q: War: `two complete layers' - bitte \"uberpr\"ufen.} The ICD and ETMD peak overlap such, that the peak structure
-          might not be visible.}
- \label{figure:xe_8_lay1}
+          of a xenon core of 561 atoms surrounded by five complete layers of
+          argon atoms (Xe content: 14.5\,\%). The ICD and ETMD peak overlap such, that the peak
+          structure might not be visible.}
+ \label{figure:xe_6_lay5}
 \end{figure}
@@
 In the first experiments very large argon-xenon clusters were measured,\cite{Mucke_phd}
-which we approximate by a cluster consisting of 1415 xenon atoms surrounded
-by one layer of argon atoms. The spectra are shown in Figure
-\ref{figure:xe_8_lay1}.
+which we approximate by a cluster consisting of 561 xenon atoms surrounded
+by five layers of argon atoms. The spectra are shown in Figure
+\ref{figure:xe_6_lay5}.
 

### 2016-05-16 theo_discussion.tex
Querverweise zwischen Text, Tab. 2, Bildern
some discussion added (though not all of it)

@@
 %
-We now would like to interpret our experimental findings in view of the simulated results described in Section \ref{sec:th_results}.
-Figure \ref{figure:eff} shows that for Ar 3s$^{-1}$ states, autoionization by either ICD or ETMD is the only mode of relaxation except for the clusters with the smallest Xe content.
+We now would like to interpret our experimental findings in view of the simulated results described in Section `Theoretical Results'.
+Figure \ref{figure:eff} shows that for Ar 3s$^{-1}$ states autoionization by either ICD or ETMD is the only mode of relaxation, except for the clusters with the smallest Xe content.
+We consider this a remarkable result, because the ICD decay path in this system is only possible with a Xe atom in the second coordination shell (or further shells).
+ETMD may take place between Ar and two Xe neighbours, but this channel has often been found less probable than ICD.\cite{zobeley}
+Nevertheless, even in this situation radiative decay channels appear to be less probable.
+
+% lowest kinetic energy is the first point of energy raster for t-E code of 52-proc-spec
+Structurally, all experimental ICD/ETMD spectra have a maximum at or near the lowest kinetic energy that could be measured (50~meV), and decrease in intensity to less than half for kinetic energies below one eV.
+Qualitatively, this shape fits to the ICD contributions to the autoionization spectra discussed in the `Theory' section, but not the ones from ETMD.
+These calculated spectra have a typical three-fold structure with peaks between 3.5-5~eV, 1.5-2.5~eV and around 0 eV kinetic energy.
+The former two features seem not to be present in the experimental spectra. 
+Due to restrictions in the detector electronics, electron pairs with very similar kinetic energy cannot be detected. 
+The highest kinetic energy for an autoionization electron that can be detected in coincidence with a photoelectron of $\sim3.5$~eV ($h\nu = 32$~eV) is around 2.5~eV.
+Very weak intensity is observed at this energy, and also at higher $e_2$ energy that can be probed at $h\nu = 34$~eV (Supporting Information).
+
+As a cross-check for our theoretical methods we have calculated the radiationless decay spectrum of Ar 3s$^{-1}$ in ArKr, and arrived at qualitative agreement with the experimental data.\cite{arkr}
+
+We are therefore lead to the conclusion that the autoionization spectra we incur are dominated by ICD to non-nearest neighbour atoms, while the intensity of the ETMD channel is low. 
+We would like to recall the factors that lead to a propensity for decay via ICD, which have been discussed in the `Theoretical Results'-section.
+For ETMD to occur with a measurable rate, two Xe atoms have to be present in the vincinity of the decaying Ar atom (Figure \ref{figure:2tops}).
+Should that be the case for a large part of the Ar atoms in some structure, ETMD can even dominate over ICD (Figure \ref{figure:ar_3_6in} and Supporting Information).
+Model structures shown in Figures \ref{figure:2tops} and \ref{figure:ar_3_6in} have a Xe content similar to the lowest one probed in our experiment ($\sim$11\,\%).
+For a higher Xe content, ETMD will always dominate the spectra if the two species are given the chance to mix, as e.g.
+in the calculated minimum energy structures of $N=38$ ArXe clusters (Supporting Info.).
+For core-shell systems however, the percentage of decay via ETMD stays below 25\,\% even a Xe content above 50\,\% (Table \ref{table:theo_gammas}).
+
+In summary, the two structural motifes that can best be reconciled with our experimental data are
+\begin{enumerate}
+	\item small clusters containing only few Xe atoms that are spread out to distant positions on the cluster surface, and
+	\item systems with a compact Xe core and Ar outer layers.
+\end{enumerate}
+As even in these two cases intensities would not vanish completely, we have to leave it open though whether other mechanisms are present, which further suppress ETMD vs. ICD.

### 2016-05-16 theo_results.tex
some discussion added (though not all of it)

@@
 In the second group, model structures for small clusters are displayed, in which 1-2 Xe atoms are added at systematically varied locations to an icosahedric Ar clusters consisting of one or two full shells, or in which 1-6 Ar atoms of such cluster were replaced by Xe atoms, while keeping the geometry of the original Xe lattice.
-The last group contains data for calculated minimal energy structures of mixed ArXe clusters.
-\protect\cite{marques}
+The last group contains data for calculated minimal energy structures of mixed ArXe clusters.\protect\cite{marques}
 The columns `ICD' and `ETMD' are the respective partial decay widths in \unit[$10^{-4}$]{eV}, and `\% ICD' gives the percentage of ICD in the total decay width.

### 2016-05-17 abstract.tex
abstract and title added

\begin{abstract}
We report about autoionization channels of Ar inner valence ionized states in mixed ArXe clusters produced by coexpansion of the two gases.
Clusters with a range of sizes were probed, and the Xe content was varied between 10 and 53\,\%. 
Our experimental data obtained by electron, electron coincidence spectroscopy are compared to {\it ab initio} calculations for representative cluster structures.
The combined experimental and theoretical data show that the autoionization of Ar 3s$^{-1}$ in ArXe is dominated by Interatomic Coulombic Decay (ICD) to Xe atoms in the second coordination shell of the originally excited atom.
Electron Transfer Mediated Decay (ETMD) is energetically allowed as well for most cluster structures, but has less intensity in the experimental spectra.
We show experimentally that the relaxation of Ar inner valence states by ICD and ETMD together has an efficiency of unity, within the experimental accuracy, for all clusters expect those with the lowest Xe content.
Decay rates calculated for ETMD favour cluster structures with either a clear seggregation between Ar and Xe fractions, e.g. Xe core, Ar shell systems, or with few Xe atoms singled out in surface sites.
They differ significantly from calculated minimum energy structures for ArXe systems, which might show that the latter structures are not realized in supersonic expansion.
\end{abstract}

### 2016-05-23 summary.tex
summary added - version for sending to co-authors

\section{Summary}
%
In summary, we have presented comprehensive experimental and theoretical data for the autoionization of inner valence ionized states in ArXe clusters.
Both ICD and ETMD are allowed for most cases we considered.
Because of energetical reasons ICD requires a separation of the final state vacancies by about 8~\AA or more, which is at least two times the typical Ar-Xe distance.
We found that autoionization has 0.8 to 1.0 efficiency within the experimental accuracy, that is it dominates over other modes of relaxation.
By comparing our measured spectra to calculations, we identified `long range' ICD as the most important decay mode.

### 2016-05-23 abstract.tex

@@
 \begin{abstract}
-We report about autoionization channels of Ar inner valence ionized states in mixed ArXe clusters produced by coexpansion of the two gases.
-Clusters with a range of sizes were probed, and the Xe content was varied between 10 and 53\,\%. 
+We report about autoionization channels of Ar inner valence ionized states in mixed ArXe clusters. 
+The mixed clusters were produced by supersonic coexpansion of the two gases.
+Clusters with a range of sizes and compositions were probed. 
+The Xe content in the clusters was varied between 10 and 53\,\%. 
 Our experimental data obtained by electron, electron coincidence spectroscopy are compared to {\it ab initio} calculations for representative cluster structures.

### 2016-05-23 exp_results.tex

@@
 Values for Ar 3p in the last row refer to the fine structure states.
-\label{tab:valence} }
+\label{tab:valence}}
 \begin{tabular}{ l c c c c c c c c}
@@
 the expansion conditions than for changes of the gas mixture.
-This finding is supported by the spectra shown in Ref.\ \cite{lindblad}.
+This finding is supported by the spectra shown in Ref.\ \citenum{lindblad}.
 %
@@
 
-If we produce a spectrum only from those electrons recorded as part of a two-electron coincidence (colored symbols in Figure \ref{figure:ival}), the apparent intensity drops.
+If we produce a spectrum only from those electrons recorded as part of a two-electron coincidence (electron pair with kinetic energies ($e_1,e_2$)) the apparent intensity drops (colored symbols in Figure \ref{figure:ival}).
 This can partly be attributed to the finite detection efficiency of the spectrometer. 
@@
 In Figure \ref{figure:icd_12}, we show the spectra of ICD/ETMD electrons pertaining to emission of an Ar 3s cluster photoelectron. 
+Due to their low kinetic energy, without use of a coincidence method they could hardly be separated from the background of inelastically scattered photoelectrons.\cite{mucke}
 These, and the following figure, constitute the central experimental result of the article.
-Due to their low kinetic energy, without use of a coincidence method they could hardly be separated from the background of inelastically scattered photoelectrons.\cite{mucke}
-Further details on the data acquisition and analysis methodology are given in the Supporting Information.
-We note here that spectra recorded at $h\nu = 34$ eV as a cross-check, quantitatively agree to those shown in the Figure.
+Spectra recorded at $h\nu = 34$ eV as a cross-check quantitatively agree to those shown in the Figure.
+This underpins our assignment of this intensity to an autoionization process.
+Further details on the data acquisition and analysis methodology, as well as the 34~eV spectra, are given in the Supporting Information.
 
-Clearly, spectra for the three different cluster sizes in Figure \ref{figure:icd_12} are significantly different: Spectra for the larger cluster acquire more intensity in the 1-1.5 eV region and have less intensity for energies below 0.5 eV.
+Spectra for the three different cluster sizes in Figure \ref{figure:icd_12} are significantly different: Spectra for the larger cluster acquire more intensity in the 1-1.5 eV region and have less intensity for energies below 0.5 eV.
 In contrast to that, the ICD/ETMD spectrum hardly varies when the composition of the expanding gas mixture is changed (Figure \ref{figure:icd_l}).

### 2016-05-23 experimental.tex

--- 2016-01-18 experimental.tex
@@
 Experiments were done with $d = 80~\mu$m (first two sections) and $d = 100~\mu$m (bottom section) conical nozzles of 15$^\circ$ half opening angle. 
-Due to the much lower freezing point of Ar, we basically have an Ar seeded expansion of Xe gas. 
+We basically have an Ar seeded expansion of Xe gas, as the freezing point of Ar is much lower. 
 $\langle N_{\rm Ar} \rangle$ and $\langle N_{\rm Xe} \rangle$ refer to cluster sizes for a pure Ar, or pure Xe expansion, resp., at the given conditions, calculated from a scaling law.\protect\cite{hagena1981}
@@
 Prediction of the sizes of clusters from a supersonic expansion mainly rests on empirical scaling laws,\cite{hagena1981} which have been the subject of some discussion.
-Recent analyses of photoionization spectra suggests that mean sizes arrived at by scaling laws are smaller than the actual size, at least for rare gas clusters in the range $\langle N\rangle < 1000$.\cite{bergersen,hergenhahnprb,foerstel_arg2_2011}
 Moreover, such scaling laws originally were derived only for pure gas expansions.
 A recent investigation of cluster sizes in a mixed Ar-Kr expansion yielded a revised scaling law, which essentially amounts to the use of a weighted average over the atom-specific parameters of the two gases.\cite{danylchenko2015}
-Although the analogy to our case is not complete, as phase segregation occurs in Ar-Kr to a much lesser extent,\cite{Vach_1999,lundwall_arkr} we therefore expect actual cluster sizes between the values calculated for Ar and Xe.
+Although the analogy to our case is not complete, as phase segregation occurs in Ar-Kr to a much lesser extent,\cite{Vach_1999,lundwall_arkr} we therefore expect scaling law cluster sizes between the values calculated for Ar and Xe.
+Recent analyses of photoionization spectra suggests that mean sizes arrived at by scaling laws are smaller than the actual size, at least for rare gas clusters in the range $\langle N\rangle < 1000$.\cite{bergersen,hergenhahnprb,foerstel_arg2_2011}
+We expansion conditions labelled `S'-`L', we therefore expect that the scaling law estimates are a lower boundary for the actual cluster size.
 
@@
 The storage ring was operated in single bunch conditions.
-Spectra of pure Ar clusters shown for comparison are from Ref. \citenum{foerstel_arg2_2011}, and a spectrum of pure Xe clusters was recorded with the set-up described in Ref. \citenum{hergenhahnprb}.
+Spectra of pure Ar clusters shown for comparison are from Ref.\ \citenum{foerstel_arg2_2011}, and a spectrum of pure Xe clusters was recorded with the set-up described in Ref.\ \citenum{hergenhahnprb}.
 
@@
 For the data shown here, slightly positive bias voltages were used (+1.8 V to +2.2 V) in order to have all electrons arriving at the detector within one BESSY single bunch period (800 ns). 
-The detection efficiency was determined as 0.6, with the method outlined in Ref. \citenum{mucke_review}.
+The detection efficiency was determined as 0.6, with the method outlined in Ref.\ \citenum{mucke_review}.
+
+The high detection efficiency of the instrument is a pre-requisite for measuring two-electron emission processes, such as photoelectron emission followed by ICD or ETMD, by using electron-electron coincidence detection.
+This allows to filter the full electron spectrum for contributions arising after emission of an Ar 3s photoelectron.
+ICD/ETMD spectra presented here are based on this method, which has been explained earlier.\cite{mucke_review,Foerstel_phd}
+Technical details and full electron-electron coincidence spectra are given in the Supporting Information.

### 2016-05-23 intro.tex

@@
 
-The plan of our paper is as follows: ...
+The plan of our paper is as follows: We firstly delineate our experimental and theoretical methods. 
+Calculations were done for a number of model structures which were systematically varied, and are described in the following section.
+After that, we describe and discuss our theoretical results for the autoionization spectra of the model clusters.
+Experimental results are then shown and possible conclusions from comparing them to the calculations are given.
+Details on the experimental technique, and calculated spectra for a wider range of structures are given as Supporting Information.
 

### 2016-05-23 theo_discussion.tex

@@
 Figure \ref{figure:eff} shows that for Ar 3s$^{-1}$ states autoionization by either ICD or ETMD is the only mode of relaxation, except for the clusters with the smallest Xe content.
-We consider this a remarkable result, because the ICD decay path in this system is only possible with a Xe atom in the second coordination shell (or further shells).
-ETMD may take place between Ar and two Xe neighbours, but this channel has often been found less probable than ICD.\cite{zobeley}
-Nevertheless, even in this situation radiative decay channels appear to be less probable.
+We consider this a remarkable result, because ICD in this system is only possible with a Xe atom in the second coordination shell of the decaying Ar vacancy (or shells even further apart), which reduces its decay rate.
+Also decay rates for ETMD were found to be small in early studies of this effect.\cite{zobeley}
+Nevertheless, even in this situation the non-local autoionization channels foreclose radiative decay.
 
@@
 Structurally, all experimental ICD/ETMD spectra have a maximum at or near the lowest kinetic energy that could be measured (50~meV), and decrease in intensity to less than half for kinetic energies below one eV.
-Qualitatively, this shape fits to the ICD contributions to the autoionization spectra discussed in the `Theory' section, but not the ones from ETMD.
-These calculated spectra have a typical three-fold structure with peaks between 3.5-5~eV, 1.5-2.5~eV and around 0 eV kinetic energy.
+Qualitatively, this shape fits to the ICD contributions in the autoionization spectra discussed in the `Theory' section, but not to the ones from ETMD. 
+The calculated ETMD spectra have a typical three-fold structure with peaks between 3.5-5~eV, 1.5-2.5~eV and around 0 eV kinetic energy. 
 The former two features seem not to be present in the experimental spectra. 
@@
 The highest kinetic energy for an autoionization electron that can be detected in coincidence with a photoelectron of $\sim3.5$~eV ($h\nu = 32$~eV) is around 2.5~eV.
-Very weak intensity is observed at this energy, and also at higher $e_2$ energy that can be probed at $h\nu = 34$~eV (Supporting Information).
+Very weak intensity is observed at this energy, and also at higher $e_2$ energies that can be probed at $h\nu = 34$~eV (Supporting Information).
 
@@
 We are therefore lead to the conclusion that the autoionization spectra we incur are dominated by ICD to non-nearest neighbour atoms, while the intensity of the ETMD channel is low. 
-We would like to recall the factors that lead to a propensity for decay via ICD, which have been discussed in the `Theoretical Results'-section.
+We would like to recall the factors that lead to a propensity for decay via one or the other mechanism, which have been discussed in the `Theoretical Results'-section.
 For ETMD to occur with a measurable rate, two Xe atoms have to be present in the vincinity of the decaying Ar atom (Figure \ref{figure:2tops}).
@@
 For a higher Xe content, ETMD will always dominate the spectra if the two species are given the chance to mix, as e.g.
-in the calculated minimum energy structures of $N=38$ ArXe clusters (Supporting Info.).
-For core-shell systems however, the percentage of decay via ETMD stays below 25\,\% even a Xe content above 50\,\% (Table \ref{table:theo_gammas}).
+in the calculated minimum energy structures of $N=38$ ArXe clusters (Supporting Info).
+On the other hand, in core-shell systems decay via ETMD is probable only for Ar atoms in the interface layer, as this mechanism requires some wavefunction overlap between Ar and one of the Xe atoms involved.
+For the core-shell systems we have investigated, the likelihood of decay via ETMD stays below 25\,\% even for a Xe content above 50\,\% (Table \ref{table:theo_gammas}).
 
@@
 \end{enumerate}
-As even in these two cases intensities would not vanish completely, we have to leave it open though whether other mechanisms are present, which further suppress ETMD vs. ICD.
+These structures are compatible with the findings of Lindblad {\it et al.}\ from core level photoelectron spectroscopy, who proposed the former structure for the smallest clusters in their study, and the latter for larger ones.\cite{lindblad}
+As even in these two cases intensity for decay via ETMD would not vanish completely, we have to leave it open though whether other mechanisms are present, which further suppress ETMD vs. ICD.

### 2016-05-23 theo_results.tex

@@
 fourth decay channel, pertaining to Xe 5p$_{1/2}^{-1}$ Ar 3p$_{1/2}^{-1}$ final states.
+
+We also note that the percentage of decay via ICD is practically independent of the Xe content. 
+This can be expected, as ETMD takes place via an exchange transition matrix element, which requires some wavefunction overlap.
+ETMD therefore mainly takes place in the Ar atoms at the interface layer to the

### 2016-05-23 theory.tex

@@
           internuclear distance, using the experimental ionization potentials given
-          in Table \ref{}. For distances larger than the channel opening
+          in Table \ref{tab:valence}. For distances larger than the channel opening
           distance the ICD channel is open.}

### 2016-05-24 abstract.tex
work through abstract and intro

@@
 The Xe content in the clusters was varied between 10 and 53\,\%. 
-Our experimental data obtained by electron, electron coincidence spectroscopy are compared to {\it ab initio} calculations for representative cluster structures.
-The combined experimental and theoretical data show that the autoionization of Ar 3s$^{-1}$ in ArXe is dominated by Interatomic Coulombic Decay (ICD) to Xe atoms in the second coordination shell of the originally excited atom.
-Electron Transfer Mediated Decay (ETMD) is energetically allowed as well for most cluster structures, but has less intensity in the experimental spectra.
+Our experimental data obtained by electron, electron coincidence spectroscopy are compared to theoretical simulations for representative cluster structures.
+The combined experimental and theoretical data show that the autoionization of Ar 3s$^{-1}$ in ArXe is dominated by Interatomic Coulombic Decay (ICD) to Xe atoms in the second and higher coordination shells of the originally excited atom.
+Electron Transfer Mediated Decay (ETMD3) is energetically allowed as well for
+most cluster structures. It is even dominant for some of the cluster
+structures, but has less intensity in the experimental spectra. We therefore
+conclude that 
+cluster structures with either a clear seggregation between Ar and Xe fractions, e.g. Xe core, Ar shell systems, or with few Xe atoms singled out in surface sites
+are favoured.
+These structures differ significantly from the majority of calculated minimum
+energy structures for ArXe systems of 38 atoms, which might show that the latter structures are not realized in supersonic expansion.
+
 We show experimentally that the relaxation of Ar inner valence states by ICD and ETMD together has an efficiency of unity, within the experimental accuracy, for all clusters expect those with the lowest Xe content.
-Decay rates calculated for ETMD favour cluster structures with either a clear seggregation between Ar and Xe fractions, e.g.
-Xe core, Ar shell systems, or with few Xe atoms singled out in surface sites.
-They differ significantly from calculated minimum energy structures for ArXe systems, which might show that the latter structures are not realized in supersonic expansion.
 \end{abstract}

### 2016-05-24 intro.tex
work through abstract and intro

@@
 research on composition and structure of free nanoparticles.\cite{
-jpcc} Besides photoionization, free electrons emerging from 
+jpcc, Fasshauer14_1} Besides photoionization, free electrons emerging from 
 nanoparticles can also be produced by the relaxation of 
@@
 amount of both species. By the use of electron, electron 
-coincidence spectroscopy and of {\it ab initio} calculations on 
+coincidence spectroscopy and of theoretical simulations on 
 prototypical systems we show how the radiationless decay spectrum 
@@
 Xe was also found to diffuse into the interior of Ar clusters in molecular dynamics simulations after pick-up.\cite{Vach_1999} 
-The electronic energy levels of very small Ar-Xe clusters were calculated in Ref.s~ \citenum{fasshauer,Fasshauer13}.
+The electronic energy levels of very small Ar-Xe clusters were calculated in Ref.~ \citenum{Fasshauer10} and the seondary electron spectra were simulated for
+model structures of one argon atom placed on a xenon surface \cite{Fasshauer13}.
 Interestingly, it was found that Ar 3s$^{-1}$ is stable 
 against autoionization in an ArXe dimer, but is destabilized by 
-adding further Xe atoms, or an Ar solvation shell, to the system. 
+adding further Xe atoms, or an Ar solvation shell, to the system, thereby allowing
+for combinations of argon and xenon atoms with larger interatomic distances. 
 Again, we will detail these results in conjunction with our 

### 2016-05-24 theory.tex
improve theory part
the beginning is very close to my original text
please leave this way of introducing the theory. Like this it is not connected
to valueing the different approaches and their importance.
Also the different parameters of the later calculation are introduced one by one and not all at the same time.

@@
 %
-We are interested in describing the electron emission spectra of excited states in clusters, that where measured by the electron-electron coincidence method in our experiments. 
-In our theoretical description, these will be composed of multiple transitions, each characterized by a kinetic energy $E_{\rm sec}$ of the secondary electrons, and the intensity of the peak.
-The latter is proportional to the probability of the decay, represented here by the decay width $\Gamma_\beta = \hbar/\tau_\beta$, where $\tau_\beta$ is the lifetime due to the respective transition.
-The total decay width $\Gamma$ is the sum of all partial $\Gamma_\beta$.
-In case of noble gas clusters with a given geometrical structure, three aspects have to be taken into account:
-different decay mechanisms, the contribution of different cluster sites to the respective decay, and the existence of different decay channels within each decay mechanism.
-At the current stage of development we have to neglect the nuclear dynamics, which
+Experimental coincidence spectra are given by the multitude of
+kinetic energies $E_{\rm sec}$ of the secondary electron
+and the intensities of the peaks. The latter is proportional to the
+probability of the decay as well as the theoretically determinable
+decay width $\Gamma=\frac{\hbar}{\tau}$,
+which is inverse proportional to the lifetime $\tau$ of the decay process.
+The manifold of the
+secondary energies and decay widths will therefore compose the electron-electron
+coincidence spectrum.
+In case of noble gas clusters
+with given geometrical structures three aspects have to be taken into account:
+different decay mechanisms, the possibility to decay with multiple
+interaction partners and different decay channels $\beta$ within
+each decay mechanism.
+At the current stage of development we need to neglect the nuclear dynamics which
 additionally might play an important role.
+
+%We are interested in describing the electron emission spectra of excited states in clusters, that where measured by the electron-electron coincidence method in our experiments. 
+%In our theoretical description, these will be composed of multiple transitions, each characterized by a kinetic energy $E_{\rm sec}$ of the secondary electrons, and the intensity of the peak.
+%The latter is proportional to the probability of the decay, represented here by the decay width $\Gamma_\beta = \hbar/\tau_\beta$, where $\tau_\beta$ is the lifetime due to the respective transition.
+%The total decay width $\Gamma$ is the sum of all partial $\Gamma_\beta$.
+%In case of noble gas clusters with a given geometrical structure, three aspects have to be taken into account:
+%different decay mechanisms, the contribution of different cluster sites to the respective decay, and the existence of different decay channels within each decay mechanism.
+%At the current stage of development we have to neglect the nuclear dynamics, which
 
@@
 coordinates. 
-Each pair and each triple leads to a decay spectrum that can be described by the energy of the secondary electron and the decay width, and which is in first order of approximation independent of other atoms present in the cluster.
+Each pair and each triple leads to a decay spectrum that can be described by the energy of the secondary electron and the decay width, which is in first order of approximation independent of other atoms present in the cluster.
 In the following, this approach will be called model of pairs and triples.
@@
 
-This {\latin ad hoc} approach allows to easily correct for energetic shifts of ionization potentials as observed in larger clusters by adding experimentally or theoretically determined energy shifts $\Delta E(X_{A}^{\beta})$ for a given vacancy $A={\rm in},D,E$ and channel $\beta$.
+This {\latin ad hoc} approach allows to easily correct for energetic shifts of ionization potentials as observed in larger clusters by adding experimentally or theoretically determined energy shifts $\Delta E(X_{I}^{\beta})$ for a given vacancy $I={\rm in},D,E$ and channel $\beta$.
 This yields the working expression for the kinetic energy of the secondary electron:
@@
                         \frac{\sigma^{(X_E)}(\omega_{vp,\beta})}
-                        {R_i^6 \, \omega_{vp,\beta}^4 \tau_{in,\beta}}
+                        {R_i^6 \, \omega_{vp,\beta}^4 \tau_{in,\beta}},
 \end{equation}
 %
+where $J_A$, $J_A'$ and $M_A$, $M_A'$ denote the total angular momentum of the
+initially ionized atom (which is the same as the electron doner atom) in the
+initial and final state, respectively,
 and
 %
-\begin{equation}
- \Gamma_{{\rm ETMD},j,\beta} = \frac{c}{2\pi} \sum\limits_{m,k,M_{in}',D}
-                        \frac{a_{m,k} \Theta_{m,k}(\alpha_j) \sigma^{(X_E)}(\omega_{vp,\beta})
-                              \tilde{D}_{m,j,\beta}(M_{in,D},M_{in,D'})}
-                         {R_j^6 \omega_{vp,\beta}}
-\end{equation}
+\begin{align}
+ \Gamma_{{\rm ETMD},j,\beta} =& \frac{c}{\pi} \sum\limits_{m,M_{in,D'}}
+                        \frac{\Theta_{m,k}(\alpha_j) \sigma^{(X_E)}(\omega_{vp,\beta})
+                              \left| <\tilde{D}_{m,j,\beta}(M_{in,D'})>\right|^2}
+                         {R_j^6 \omega_{vp,\beta}}\\
+               =& \frac{c}{\pi R_j^6}
+               \sum\limits_{M_{in,D'}}
+               \left( \left| <\tilde{D}_{x,j,\beta} (M_{in,D'}) > \right|^2
+                 (2+ \sin^2\alpha_j)
+               + \left| <\tilde{D}_{z,j,\beta} (M_{in,D'}) > \right|^2
+                 (1+\cos^2\alpha_j) \right) \nonumber \\
+           & \times\, \frac{c\sigma^{(X_E)}(\omega_{vp,\beta})}{\omega_{vp,\beta}}
+\end{align}
 %
-depending on constants ($a_{m,k}=4,2$) {\it Q: ??? Hei\ss t das, $a_{m.k}$ kann die Werte 2 und 4 annehmen? \color{red}{Ja, genau das heißt es. Zum Vergleich
-kannst du dir Formel 19 in \cite{Fasshauer13} ansehen.}}
-as well as experimental properties
+depending on 
+experimental properties
 of atoms, like the ionization cross sections
@@
 and calculated dipole transition moments $\tilde{D}_{m,j,\beta}$, only.
-Here, $\Theta_{m,k}(\alpha_j)$ is a function depending on the angle $\alpha_j$
-of the triple, the direction of the dipole
-transition moment $m$ and an additional index $k$
+Here, $\Theta_{m}(\alpha_j)$ is a function depending on the angle $\alpha_j$
+of the triple and the direction of the dipole
+transition moment $m$
 (compare Ref. \cite{Fasshauer13}).

### 2016-05-24 structures.tex
improve structures section

@@
 use these to construct representative cluster structures, for which we will 
-simulate the ICD and ETMD spectra. At this point we put in a variety of structures,
-in the hope to exclude some of them by comparison of
+simulate the ICD and ETMD spectra. At this point we put in a variety of
+structures, in order to learn about general structure-spectrum relations
+and therefore being able to
+exclude some of them by comparison of
 the ICD and ETMD spectra to the experimental ones.
@@
 We therefore started from icosahedral structures and produced mixed cluster structures by substitution of individual atoms with one or the other kind (Ar or Xe), or added individual atoms to a given structure close to the desired position.
-After that, the cluster structures were optimized using the UFF force field method \cite{} implemented in the 
-Avogadro programme \cite{}.
+After that, the cluster structures were optimized using the unified force
+field implemented in the 
+Avogadro programme (version 1.1.0) \cite{Avogadro,Hanwell12}.
 All cluster structures are listed in Table \ref{table:theo_gammas}.

### 2016-05-24 theo_results.tex
complete and correct theo_results

--- 2016-05-16 theo_results.tex
@@
 It is important to remember that the first ICD channel opens at a
-channel opening distance of \unit[7.58]{\AA}. In small
-clusters, Ar-Xe pair distances are below that value, therefore 
-no ICD can take place. Also, by definition two Xe atoms are
+channel opening distance of \unit[7.58]{\AA}. In the smallest
+clusters with only one argon layer around each
+xenon atom, the Ar-Xe pair distances are below that value, therefore 
+no ICD can take place. Also, by definition, two Xe atoms are
 required for ETMD(3), hence it cannot occur in clusters with only one xenon atom.
@@
 
-Because the structures have only one xenon atom, ETMD(3) is not possible
-and only ICD is expected. 
+Because the structures have only one xenon atom, an ETMD(3) is not possible
+and only ICD is to be expected. 
 %Both spectra show several smaller peaks which
@@
 %{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
-The three energetically separated peaks in the ETMD(3) spectrum pertain to different combinations of the Xe 5p$_j^{-1}$ vacancy states, which have a substantial fine-structure splitting (see \ref{sec:exp_results}).
+The three energetically separated peaks in the ETMD(3) spectrum pertain to different combinations of the Xe 5p$_j^{-1}$ vacancy states, which have a substantial fine-structure splitting (see Section \ref{sec:exp_results}).
 %
@@
 For both cases the overall ICD spectra are very similar, and show a maximum at a kinetic energy of approximately \unit[0.3]{eV}. 
-In case that the xenon atoms are grouped, the ICD spectrum extends to slightly higher energies, corresponding to ArXe pairs at slightly larger spatial distance.
+In case of grouped xenon atoms, the ICD spectrum extends to slightly higher energies, corresponding to ArXe pairs at slightly larger spatial distances.
 A more significant difference is observed in the ETMD(3) spectra. 
@@
 transfer from a xenon to an argon atom decreases exponentially with the
-interatomic distance. Therefore, only those xenon atoms which have argon
-atoms as their direct neighbours have a significant contribution to the
+interatomic distance. Therefore, only those xenon atoms which have direct
+argon atom neighbours have a significant contribution to the
 total decay width, and the total ETMD(3) decay width is lower for the structure with
@@
  \centering
- \includegraphics[width=8.5cm]{pics/xe_6_5lay.pdf}
- \caption{Same as Figure \protect\ref{figure:2tops}, for a large cluster consisting
+ \includegraphics[width=\columnwidth]{pics/c6l5.pdf}
+ \caption{Same as Figure \protect\ref{figure:2tops},
+          for a large cluster consisting
           of a xenon core of 561 atoms surrounded by five complete layers of
-          argon atoms (Xe content: 14.5\,\%). The ICD and ETMD peak overlap such, that the peak
+          argon atoms (Xe content: 14.5\,\%) for both an icosahedral and
+          cuboctahedral basic structure.
+          The ICD and ETMD peak overlap such, that the peak
           structure might not be visible.}
@@
 %
-In the first experiments very large argon-xenon clusters were measured,\cite{Mucke_phd}
-which we approximate by a cluster consisting of 561 xenon atoms surrounded
-by five layers of argon atoms. The spectra are shown in Figure
-\ref{figure:xe_6_lay5}.
+In the first experiments very large argon-xenon clusters of 
+$\approx 4380$ atoms with a xenon content of \unit[19]{\%}
+were measured,\cite{Mucke_phd}
+which we in one example approximate by a cluster consisting of 561 xenon
+atoms surrounded
+by five layers of argon atoms (3871 atoms in total). In order to take the
+better stabilization of charges in larger clusters into account, the
+ionization energies of the XL clusters (see Table \ref{tab:valence})
+were used.
+The spectra are shown in 
+Figure \ref{figure:xe_6_lay5}.
 
@@
 expected due to the larger interatomic Ar-Xe distances in the large cluster and
-the better stabilization of charges (the final state), which has been taken into account
-in the simulation.
+the better stabilization of charges, which is relevant mostly for the final state, but also the initial state.
 The ETMD(3) peak is shifted to slightly higher energies as well. This allows opening of the
 fourth decay channel, pertaining to Xe 5p$_{1/2}^{-1}$ Ar 3p$_{1/2}^{-1}$ final states.
+
+We also note that the percentage of decay via ICD is practically
+independent of the Xe content for large clusters with a core-shell structure.
+This can be expected, as both decay processes are most pronounced for the
+atoms in the interface region of the xenon core and the argon shell.
+The ETMD3, depending on the electron transfer from one xenon atom to the
+initially ionized argon atom and hence the corresponding orbital overlap,
+is a pure interface effect involving the argon atoms with direct xenon
+neighbours and the two xenon layers closest to the argon shell.
+The ICD has a stronger long range character, due to which the description
+of decays with partners of at least twice the smallest channel opening
+distance is necessary for clusters. However, the bigger the clusters are,
+the more homogeneous does the interface region become for clusters of
+different sizes. This is manifests itself in the distribution of relevant
+Ar-Xe pair distances (compare Fig. \ref{figure:surf} lower panel).
+As a consequence, the ICD spectra of two large clusters of different size
+do hardly differ.

### 2016-05-25 supp_theo_specs.tex
add ArxXey pictures to suppl

\section{Additional Theoretical ICD/ETMD3 Spectra}

\subsection{Clusters with $N=38$ Atoms of Different Composition}

\begin{figure}
 \centering
 \includegraphics[width=0.5\columnwidth]{pics/Ar36Xe2.pdf}
 \caption{}
 \label{}
\end{figure}

\begin{figure}
 \centering
 \includegraphics[width=0.5\columnwidth]{pics/Ar34Xe4.pdf}
 \caption{}
 \label{}
\end{figure}

\begin{figure}
 \centering
 \includegraphics[width=0.5\columnwidth]{pics/Ar33Xe5.pdf}
 \caption{}
 \label{}
\end{figure}

\begin{figure}
 \centering
 \includegraphics[width=0.5\columnwidth]{pics/Ar25Xe13.pdf}
 \caption{}
 \label{}
\end{figure}

\begin{figure}
 \centering
 \includegraphics[width=0.5\columnwidth]{pics/Ar14Xe24.pdf}
 \caption{}
 \label{figure:}
\end{figure}

\begin{figure}
 \centering
 \includegraphics[width=0.5\columnwidth]{pics/Ar13Xe25.pdf}
 \caption{}
 \label{figure:Ar13Xe25}
\end{figure}

\begin{figure}
 \centering
 \includegraphics[width=0.5\columnwidth]{pics/Ar3Xe35.pdf}
 \caption{}
 \label{figure:Ar3Xe35}
\end{figure}

%\begin{figure}
% \centering
% \includegraphics[width=0.5\columnwidth]{pics/ArXe.pdf}
% \caption{}
% \label{}
%\end{figure}
%
%\begin{figure}
% \centering
% \includegraphics[width=0.5\columnwidth]{pics/ArXe.pdf}
% \caption{}
% \label{}
%\end{figure}

### 2016-05-25 intro.tex

@@
 Xe was also found to diffuse into the interior of Ar clusters in molecular dynamics simulations after pick-up.\cite{Vach_1999} 
-The electronic energy levels of very small Ar-Xe clusters were calculated in Ref.~ \citenum{Fasshauer10} and the seondary electron spectra were simulated for
+The electronic energy levels of very small Ar-Xe clusters were calculated in Ref.~ \citenum{fasshauer} and the seondary electron spectra were simulated for
 model structures of one argon atom placed on a xenon surface \cite{Fasshauer13}.

### 2016-05-25 summary.tex

@@
 %
-In summary, we have presented comprehensive experimental and theoretical data for the autoionization of inner valence ionized states in ArXe clusters.
+We have presented comprehensive experimental and theoretical data for the
+autoionization of inner valence ionized states in ArXe clusters.
 Both ICD and ETMD are allowed for most cases we considered.
-Because of energetical reasons ICD requires a separation of the final state vacancies by about 8~\AA or more, which is at least two times the typical Ar-Xe distance.
-We found that autoionization has 0.8 to 1.0 efficiency within the experimental accuracy, that is it dominates over other modes of relaxation.
-By comparing our measured spectra to calculations, we identified `long range' ICD as the most important decay mode.
+Because of energetical reasons ICD requires a separation of the final state
+vacancies of \unit[7.58]{\AA} or more, which is about two times the typical
+Ar-Xe distance.
+We found that autoionization has an efficiency of 0.8 to 1.0 within the
+experimental accuracy, that is it dominates over other modes of relaxation.
+By comparing our measured spectra to calculations, we identified `long range'
+ICD as the most important decay mode.

### 2016-05-26 supp_theo_specs.tex
text for Ar_xXe_y in supplementary material

@@
 \subsection{Clusters with $N=38$ Atoms of Different Composition}
+Recently, structures for ArXe clusters of in total 38 atoms were optimized
+using an evolutionary algorithm based on two-body potentials determined
+by xyz. \cite{}
+In this section, the simulated ICD and ETMD3 spectra for selected cluster
+structures shown in Figure xyz of Ref. \citenum{} are shown in Figures
+\ref{} -- \ref{} and discussed.
 
@@
  \includegraphics[width=0.5\columnwidth]{pics/Ar14Xe24.pdf}
- \caption{}
- \label{figure:}
+ \includegraphics[width=0.5\columnwidth]{pics/Ar13Xe25.pdf}
+ \includegraphics[width=0.5\columnwidth]{pics/Ar3Xe35.pdf}
+ \caption{Ar$_x$Xe$_y$ clusters with a xenon content of more than \unit[50]{\%}.
+          The ETMD3 is the dominant processi for these cluster structures.
+          They are shown for completeness but can, due to the high xenon content,
+          not be related to the experimental secondary electron measurements.}
+ \label{figure:ArXe_gt50}
 \end{figure}
 
-\begin{figure}
- \centering
- \includegraphics[width=0.5\columnwidth]{pics/Ar13Xe25.pdf}
- \caption{}
- \label{figure:Ar13Xe25}
-\end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[width=0.5\columnwidth]{pics/Ar3Xe35.pdf}
- \caption{}
- \label{figure:Ar3Xe35}
-\end{figure}
+For all these cluster structures the ETMD3 is the more probable decay process and
+except for the Ar$_{36}$Xe$_2$ case with \unit[43.6]{\%} ICD, the ETMD3 is clearly
+the dominant process (compare Table xyz of the main text).
+This can be explained by a combination of high xenon content and the
+scattered distribution of the xenon atoms within the cluster structures.
+Since the decay width of the ETMD3 is mostly caused by the decay
+with direct neighbours and for these $\Gamma_{ETMD3} \propto N_{Ar} N_{Xe}^2$
+both the maximization of direct xenon neighbours of an argon atom and the
+maximization of the number of argon atoms being surrounded by xenon atoms
+leads to a strong increase of the ETMD3 decay width. This situation is realized
+in cluster structures without a seggregation of the two different elements like
+in the structures of Ref. \cite{}. At the same time, all ICD channels are closed
+for direct xenon neighbours. Therefore, a higher number of direct xenon neighbours
+for all argon atoms reduces the number of possible decay partners for a given
+cluster composition and therefore the ICD decay width.
 

### 2016-05-26 supp_theo_specs.tex
wording

@@
 except for the Ar$_{36}$Xe$_2$ case with \unit[43.6]{\%} ICD, the ETMD3 is clearly
-the dominant process (compare Table xyz of the main text).
+the dominant process (compare Table xyz of the main article).
 This can be explained by a combination of high xenon content and the

### 2016-05-27 supp_theo_specs.tex
low xenon content clusters

@@
 using an evolutionary algorithm based on two-body potentials determined
-by xyz. \cite{}
+by xyz. \cite{marques}
 In this section, the simulated ICD and ETMD3 spectra for selected cluster
-structures shown in Figure xyz of Ref. \citenum{} are shown in Figures
-\ref{} -- \ref{} and discussed.
+structures shown in Figure 7 of Ref. \citenum{marques} are shown in Figures
+\ref{figure:ArXe_lt15} -- \ref{figure:ArXe_gt50} and discussed.
 
@@
  \centering
- \includegraphics[width=0.5\columnwidth]{pics/Ar36Xe2.pdf}
- \caption{}
- \label{}
-\end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[width=0.5\columnwidth]{pics/Ar34Xe4.pdf}
- \caption{}
- \label{}
-\end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[width=0.5\columnwidth]{pics/Ar33Xe5.pdf}
- \caption{}
- \label{}
+ \includegraphics[width=0.32\columnwidth]{pics/Ar36Xe2.pdf}
+ \includegraphics[width=0.32\columnwidth]{pics/Ar34Xe4.pdf}
+ \includegraphics[width=0.32\columnwidth]{pics/Ar33Xe5.pdf}
+ \caption{Ar$_N$Xe$_{38-N}$ clusters with a xenon content of
+          \unit[5]{\%} to \unit[13]{\%}.
+          According to our simulations the ETMD3 is the most prominent decay
+          process for these cluster structures.
+          In case of the Ar$_{36}$Xe$_2$ cluster only Xe-Xe distance is
+          realized and therefore, the ETMD3 spectrum is very similar
+          to one of a trimer
+          showing two peaks originating
+          from three different decay channels. In the other two cases the ETMD3
+          spectrum is slightly more complex, but in all three cases, the ETMD3
+          is manifested by peaks between \unit[0.5]{eV} and \unit[4.0]{eV} being
+          in contrast to the experimental observations.}
+ \label{figure:ArXe_lt15}
 \end{figure}
@@
  \includegraphics[width=0.5\columnwidth]{pics/Ar3Xe35.pdf}
- \caption{Ar$_x$Xe$_y$ clusters with a xenon content of more than \unit[50]{\%}.
-          The ETMD3 is the dominant processi for these cluster structures.
+ \caption{Ar$_N$Xe$_{38-N}$ clusters with a xenon content of more
+          than \unit[50]{\%}.
+          Our simulations show that ETMD3 is the dominant process
+          for these cluster structures.
           They are shown for completeness but can, due to the high xenon content,

### 2016-05-27 theo_results.tex
correct Uwes statements about the theoretical structures

@@
 \caption{Structural and calculated properties of some model clusters.
-The cluster structures are characterized by the number of Ar and Xe atoms, and are arranged in three groups according to gross structural properties. 
-The first group contains Xe core-Ar shell systems of various size and relative Xe content.
-In the second group, model structures for small clusters are displayed, in which 1-2 Xe atoms are added at systematically varied locations to an icosahedric Ar clusters consisting of one or two full shells, or in which 1-6 Ar atoms of such cluster were replaced by Xe atoms, while keeping the geometry of the original Xe lattice.
-The last group contains data for calculated minimal energy structures of mixed ArXe clusters.\protect\cite{marques}
-The columns `ICD' and `ETMD' are the respective partial decay widths in \unit[$10^{-4}$]{eV}, and `\% ICD' gives the percentage of ICD in the total decay width.
+The cluster structures are characterized by the number of Ar and Xe atoms,
+and are arranged in three groups according to gross structural properties. 
+The first group contains Xe core-Ar shell systems of various
+size and relative Xe content.
+In the second group, model structures for small clusters are displayed,
+in which 1-2 Xe atoms are added at systematically varied locations
+to an icosahedric Ar clusters consisting of one or two full shells,
+or in which 1-6 Ar atoms of such cluster were replaced by Xe atoms.
+Afterwards the cluster structures were optimized using force fields to
+give local minimum structures.
+The last group contains data for calculated minimal energy structures
+of mixed ArXe clusters.\protect\cite{marques}
+The cluster structures are classified into core-shell structures (cs),
+structures with seggregated xenon atoms (in) and completely mixed
+structures.
+The columns `ICD' and `ETMD' are the respective partial decay widths
+in \unit[$10^{-4}$]{eV}, and `\% ICD' gives the percentage of ICD in
+the total decay width.
 See text for details.
@@
 \midrule
- 1 &     1 &    12 &  7.7  & cl    &         &          & 0.000 & 0.000 &  -- &\\ %    0.0            \\     ArXe\_2\_1atom      
- 2 &     1 &    54 &  1.8  & cl    &         &          & 0.000 & 0.000 &  -- & \ref{figure:xe_3_in}\\ %    0.0            \\     ArXe\_3\_1atom      
- 3 &     2 &    53 &  3.6  & cl    &         &          & 0.033 & 0.167 &  16.7& \ref{figure:xe_3_in}\\ %2.006$\cdot 10^{-5}$ \\ ArXe\_3\_2atom      
- 4 &  1415 &   642 & 68.8  & cl    &         &          & 7.039 & 2.573 &  73.2& suppl.\\ %9.612$\cdot 10^{-4}$ \\ ArXe\_8\_1layer     
- 5 &   561 &  3310 & 14.5  & cl    &         &          &       &       &  85  & \ref{figure:xe_6_lay5}\\ % c6l5
+ 1 &     1 &    12 &  7.7  & cs    &         &          & 0.000 & 0.000 &  -- &\\ %    0.0            \\     ArXe\_2\_1atom      
+ 2 &     1 &    54 &  1.8  & cs    &         &          & 0.000 & 0.000 &  -- & \ref{figure:xe_3_in}\\ %    0.0            \\     ArXe\_3\_1atom      
+ 3 &     2 &    53 &  3.6  & cs    &         &          & 0.033 & 0.167 &  16.7& \ref{figure:xe_3_in}\\ %2.006$\cdot 10^{-5}$ \\ ArXe\_3\_2atom      
+ 4 &  1415 &   642 & 68.8  & cs    &         &          & 7.039 & 2.573 &  73.2& suppl.\\ %9.612$\cdot 10^{-4}$ \\ ArXe\_8\_1layer     
+ 5 &   561 &  3310 & 14.5  & cs    &         &          &       &       &  85  & \ref{figure:xe_6_lay5}\\ % c6l5
 
 \midrule
- 6 &     1 &    13 &  7.1  & cl    & surface &          & 0.792 & 0.000 & 100.0& \ref{figure:surf}\\ %7.922$\cdot 10^{-5}$ \\ XeAr\_2\_surface    
- 7 &     1 &    13 &  7.1  & cl    & edge    &          & 0.013 & 0.000 & 100.0&\\ %1.320$\cdot 10^{-6}$ \\ XeAr\_2\_edge       
- 8 &     1 &    13 &  7.1  & cl    & vertex  &          & 0.050 & 0.000 & 100.0&\\ %5.013$\cdot 10^{-6}$ \\ XeAr\_2\_vertex     
- 9 &     2 &    13 & 13.3  & cl    &         & closest  & 0.101 & 0.151 &  40.1& \ref{figure:2tops}\\ %2.523$\cdot 10^{-5}$ \\ XeAr\_2\_2top       
-10 &     2 &    13 & 13.3  & cl    &         & middle   & 0.159 & 0.008 &  95.4& \ref{figure:2tops}\\ %1.665$\cdot 10^{-5}$ \\ XeAr\_2\_2midtop    
-11 &     2 &    13 & 13.3  & cl    &         & furthest & 0.159 & 0.002 &  98.9& \ref{figure:2tops}\\ %1.605$\cdot 10^{-5}$ \\ XeAr\_2\_2endtop    
-12 &     1 &    55 &  1.8  & cl    & surface &          & 0.064 & 0.000 & 100.0& \ref{figure:surf}\\ %6.371$\cdot 10^{-6}$ \\ XeAr\_3\_surface    
-13 &     1 &    55 &  1.8  & cl    & edge    &          & 0.048 & 0.000 & 100.0&\\ %4.791$\cdot 10^{-6}$ \\ XeAr\_3\_edge       
-14 &     1 &    55 &  1.8  & cl    & vertex  &          & 0.027 & 0.000 & 100.0&\\ %2.701$\cdot 10^{-6}$ \\ XeAr\_3\_vertex     
+ 6 &     1 &    13 &  7.1  & cs    & surface &          & 0.792 & 0.000 & 100.0& \ref{figure:surf}\\ %7.922$\cdot 10^{-5}$ \\ XeAr\_2\_surface    
+ 7 &     1 &    13 &  7.1  & cs    & edge    &          & 0.013 & 0.000 & 100.0&\\ %1.320$\cdot 10^{-6}$ \\ XeAr\_2\_edge       
+ 8 &     1 &    13 &  7.1  & cs    & vertex  &          & 0.050 & 0.000 & 100.0&\\ %5.013$\cdot 10^{-6}$ \\ XeAr\_2\_vertex     
+ 9 &     2 &    13 & 13.3  & cs    &         & closest  & 0.101 & 0.151 &  40.1& \ref{figure:2tops}\\ %2.523$\cdot 10^{-5}$ \\ XeAr\_2\_2top       
+10 &     2 &    13 & 13.3  & cs    &         & middle   & 0.159 & 0.008 &  95.4& \ref{figure:2tops}\\ %1.665$\cdot 10^{-5}$ \\ XeAr\_2\_2midtop    
+11 &     2 &    13 & 13.3  & cs    &         & furthest & 0.159 & 0.002 &  98.9& \ref{figure:2tops}\\ %1.605$\cdot 10^{-5}$ \\ XeAr\_2\_2endtop    
+12 &     1 &    55 &  1.8  & cs    & surface &          & 0.064 & 0.000 & 100.0& \ref{figure:surf}\\ %6.371$\cdot 10^{-6}$ \\ XeAr\_3\_surface    
+13 &     1 &    55 &  1.8  & cs    & edge    &          & 0.048 & 0.000 & 100.0&\\ %4.791$\cdot 10^{-6}$ \\ XeAr\_3\_edge       
+14 &     1 &    55 &  1.8  & cs    & vertex  &          & 0.027 & 0.000 & 100.0&\\ %2.701$\cdot 10^{-6}$ \\ XeAr\_3\_vertex     
 15 &     1 &    54 &  1.8  & in    & edge    &          & 0.077 & 0.000 & 100.0&\\ %7.708$\cdot 10^{-6}$ \\ XeAr\_3\_edge\_in   
@@
                                                                                                  \midrule
-20 &     2 &    36 &  5.3  & cl    &         &          & 0.117 & 0.151 &  43.6& suppl.\\                        % Ar$_{36}$Xe$_{2}$   
+20 &     2 &    36 &  5.3  & cs    &         &          & 0.117 & 0.151 &  43.6& suppl.\\                        % Ar$_{36}$Xe$_{2}$   
 21 &     4 &    34 & 10.5  & mixed &         &          & 0.248 & 0.587 &  29.7& suppl.\\                        % Ar$_{34}$Xe$_{4}$   

### 2016-06-05 abstract.tex
small textual edits throughout the ms. Abstract rewritten.

@@
 We report about autoionization channels of Ar inner valence ionized states in mixed ArXe clusters. 
-The mixed clusters were produced by supersonic coexpansion of the two gases.
+Our experimental data obtained by electron-electron coincidence spectroscopy are compared to theoretical simulations for representative cluster structures.
+The combined experimental and theoretical data show that the autoionization of Ar 3s$^{-1}$ in ArXe is dominated by Interatomic Coulombic Decay (ICD) to Xe atoms in the second and higher coordination shells of the originally excited atom.
 Clusters with a range of sizes and compositions were probed. 
-The Xe content in the clusters was varied between 10 and 53\,\%. 
-Our experimental data obtained by electron, electron coincidence spectroscopy are compared to theoretical simulations for representative cluster structures.
-The combined experimental and theoretical data show that the autoionization of Ar 3s$^{-1}$ in ArXe is dominated by Interatomic Coulombic Decay (ICD) to Xe atoms in the second and higher coordination shells of the originally excited atom.
-Electron Transfer Mediated Decay (ETMD3) is energetically allowed as well for
-most cluster structures. It is even dominant for some of the cluster
-structures, but has less intensity in the experimental spectra. We therefore
-conclude that 
-cluster structures with either a clear seggregation between Ar and Xe fractions, e.g. Xe core, Ar shell systems, or with few Xe atoms singled out in surface sites
-are favoured.
-These structures differ significantly from the majority of calculated minimum
-energy structures for ArXe systems of 38 atoms, which might show that the latter structures are not realized in supersonic expansion.
-
+The Xe content in the clusters was varied between 10\,\% and 53\,\%. 
+Besides ICD, also Electron Transfer Mediated Decay (ETMD(3)) was found important in many of the calculated spectra, but is seen with less intensity in the experimental spectra. 
+From the calculations, we identify structural motifes which minimize the ETMD vs.
+the ICD rate and suggest that these are preferentially realized in our experiment, in which clusters are formed by supersonic expansion of an Ar-Xe mixture.
+Suggested cluster structures either feature a clear seggregation between Ar and Xe fractions, e.g. Xe core, Ar shell systems, or contain a few Xe atoms singled out in surface sites on an Ar cluster.
+These structures differ significantly from the majority of calculated minimum energy structures for ArXe systems of 38 atoms, which might show that the latter, annealed structures are not realized in our experiment.
 We show experimentally that the relaxation of Ar inner valence states by ICD and ETMD together has an efficiency of unity, within the experimental accuracy, for all clusters expect those with the lowest Xe content.

### 2016-06-05 supp_theo_specs.tex
supplementary N=38
small textual edits throughout the ms. Abstract rewritten.

@@
 Recently, structures for ArXe clusters of in total 38 atoms were optimized
-using an evolutionary algorithm based on two-body potentials determined
-by xyz. \cite{marques}
+using an evolutionary algorithm based on two-body potentials of the Lennard-Jones (LJ) type, or using two other models aimed at improving over the simple LJ potential.\cite{marques}
 In this section, the simulated ICD and ETMD3 spectra for selected cluster
@@
  \centering
- \includegraphics[width=0.32\columnwidth]{pics/Ar36Xe2.pdf}
- \includegraphics[width=0.32\columnwidth]{pics/Ar34Xe4.pdf}
- \includegraphics[width=0.32\columnwidth]{pics/Ar33Xe5.pdf}
+% \includegraphics[width=0.32\columnwidth]{pics/Ar36Xe2.pdf}
+% \includegraphics[width=0.32\columnwidth]{pics/Ar34Xe4.pdf}
+% \includegraphics[width=0.32\columnwidth]{pics/Ar33Xe5.pdf}
+ \includegraphics[width=8.2cm]{pics/Ar36Xe2.pdf}
+ \includegraphics[width=8.2cm]{pics/Ar34Xe4.pdf}
+ \includegraphics[width=8.2cm]{pics/Ar33Xe5.pdf}
  \caption{Ar$_N$Xe$_{38-N}$ clusters with a xenon content of
           \unit[5]{\%} to \unit[13]{\%}.
-          According to our simulations the ETMD3 is the most prominent decay
+          According to our simulations ETMD3 is the most prominent decay
           process for these cluster structures.
-          In case of the Ar$_{36}$Xe$_2$ cluster only Xe-Xe distance is
-          realized and therefore, the ETMD3 spectrum is very similar
-          to one of a trimer
-          showing two peaks originating
+          In case of the Ar$_{36}$Xe$_2$ cluster only a single pair of Xe
+          atoms, with one single Xe-Xe distance occurs in the cluster,
+          and therefore, the ETMD3 spectrum is very similar
+          to the one of a trimer, showing two peaks originating
           from three different decay channels. In the other two cases the ETMD3
           spectrum is slightly more complex, but in all three cases, the ETMD3
-          is manifested by peaks between \unit[0.5]{eV} and \unit[4.0]{eV} being
-          in contrast to the experimental observations.}
+          is manifested by peaks between \unit[0.5]{eV} and \unit[4.0]{eV}, which 
+          is in contrast to the experimental observations.}
  \label{figure:ArXe_lt15}
@@
  \centering
- \includegraphics[width=0.5\columnwidth]{pics/Ar25Xe13.pdf}
- \caption{}
+% \includegraphics[width=0.32\columnwidth]{pics/Ar25Xe13.pdf}
+ \includegraphics[width=8.2cm]{pics/Ar25Xe13.pdf}
+ \caption{
+          Same as Fig. \ref{figure:ArXe_lt15}, but for the 
+          optimized structure of an Ar$_25$Xe$_{13}$ cluster 
+          with a xenon content of \unit[34]{\%}.}
  \label{}
@@
  \centering
- \includegraphics[width=0.5\columnwidth]{pics/Ar14Xe24.pdf}
- \includegraphics[width=0.5\columnwidth]{pics/Ar13Xe25.pdf}
- \includegraphics[width=0.5\columnwidth]{pics/Ar3Xe35.pdf}
+% \includegraphics[width=0.32\columnwidth]{pics/Ar14Xe24.pdf}
+% \includegraphics[width=0.32\columnwidth]{pics/Ar13Xe25.pdf}
+% \includegraphics[width=0.32\columnwidth]{pics/Ar3Xe35.pdf}
+ \includegraphics[width=8.2cm]{pics/Ar14Xe24.pdf}
+ \includegraphics[width=8.2cm]{pics/Ar13Xe25.pdf}
+ \includegraphics[width=8.2cm]{pics/Ar3Xe35.pdf}
  \caption{Ar$_N$Xe$_{38-N}$ clusters with a xenon content of more
@@
           for these cluster structures.
-          They are shown for completeness but can, due to the high xenon content,
-          not be related to the experimental secondary electron measurements.}
+          They are shown for completeness here, but due to their high xenon
+          content cannot be compared to the experimental 
+          secondary electron measurements in this work.}
  \label{figure:ArXe_gt50}
@@
 
-For all these cluster structures the ETMD3 is the more probable decay process and
+For all of these cluster structures, ETMD3 is the more probable decay process and
 except for the Ar$_{36}$Xe$_2$ case with \unit[43.6]{\%} ICD, the ETMD3 is clearly
-the dominant process (compare Table xyz of the main article).
+the dominant process (compare Table 2 of the main article).
 This can be explained by a combination of high xenon content and the

### 2016-06-05 suppl.tex
add ArxXey pictures to suppl
allow units in supplementary material
clearpage between exp and theo results
small textual edits throughout the ms. Abstract rewritten.

@@
 \usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
+\usepackage{units}
 
@@
 -- The Arctic University of Norway, N-9037 Troms\o, Norway}
-\email{elke.fasshauer@uit.no}
+\author{Marko F\"orstel}
+\altaffiliation{Now at: University of Hawai'i at Manoa, 2545 McCarthy Mall, 96816 HI Honolulu, USA}
 \author{Melanie Mucke}
 \altaffiliation{Now at: Department of Physics and Astronomy, Uppsala University, Box 516, 75120 Uppsala, Sweden}
-\author{Marko F\"orstel}
-\altaffiliation{Now at: University of Hawai'i at Manoa, 2545 McCarthy Mall, 96816 HI Honolulu, USA}
+\author{Tiberiu Arion}
+\altaffiliation{Now at: Center for Free-Electron Laser Science/DESY, Notkestr. 85, 22607 Hamburg, Germany}
+\author{Toralf Lischke}
 \affiliation[IPP]{Max-Planck-Institute for Plasma Physics, Boltzmannstr. 2, 85748 Garching, Germany}
-\author{...}
 \author{Uwe Hergenhahn}
-\affiliation[IPP HGW]{Max-Planck-Institute for Plasma Physics, Wendelsteinstr. 1, 14791 Greifswald, Germany}
-\affiliation[IOM]{}
-\email{uwe.hergenhahn@ipp.mpg.de}
+\affiliation[IOM]{Leibniz Institute of Surface Modification, Permoserstr. 15, 04318 Leipzig, Germany}
+\alsoaffiliation[IPP HGW]{Max-Planck-Institute for Plasma Physics, Wendelsteinstr. 1, 14791 Greifswald, Germany}
 
@@
 \title[ArXe]
-  {One more attempt on ArXe}
+  {Long-range Interatomic Coulombic Decay in ArXe clusters: Experiment and Theory}
 
@@
  \caption{
- Argon content of ideal icosaedric Xe-core, Ar-shell systems. 
+ Argon content of ideal icosahedric Xe-core, Ar-shell systems. 
  The relative number of surface atoms decreases with increasing cluster size.
@@
 %
-For icosaedric clusters, the number of atoms in every shell is given.\cite{Mackay}
+For icosahedric clusters, the number of atoms in every shell is given.\cite{Mackay}
 For a core-shell system in this ideal geometry, the relative content of both species can therefore readily be calculated.
@@
 
-A necessary condition for the ejection of two electrons by a single photon, irrespective of the mechanism by which this is accomplished, is a sufficient photon energy. 
+A necessary condition for the ejection of two electrons by a single photon, irrespective of the mechanism by which this is accomplished, is a sufficiently high photon energy. 
 In case of a sequential process, such as photoionization followed by ICD/ETMD, moreover the ionic state which is produced in the primary step must be located above the ionization threshold for the doubly ionized systems.
@@
  \caption{
-Photon excited electron-electron coincidence spectrum of mixed Ar-Xe clusters in the inner valence region. 
+Photon excited electron-electron coincidence spectrum of mixed Ar-Xe clusters (3\,\% Xe in the initial gas mixture) in the region of Ar inner valence electrons. 
 (b): Color-coded map of coincident electron pairs, with the electron of higher kinetic named $e_1$. 
@@
 
-We have subtracted the background from random coincidences and coincidences due to electron scattering (electron impact ionization) from the signals shown in Figures \ref{figure:map}a,c.
-In order to do so, the regions between the two pairs of red horizontal bars in Figure \ref{figure:map}b were identified as background.
+We have subtracted the background from random coincidences and coincidences due to inelastic electron scattering (electron impact ionization) from the signals shown in Figures \ref{figure:map}a,c.
+In order to do so, the regions marked by the two pairs of red, horizontal bars in Figure \ref{figure:map}b were identified as background.
 The coincidence map was then subdivided into intervals of 0.5 eV width in the $e_2$ energy coordinate.
-For each interval, a second order polynomial was fitted to the background signal, and subsequently subtracted from the ICD/ETMD signal marked by the black bars.
+For each interval, a second order polynomial was fitted to the background signal, and subsequently subtracted from the ICD/ETMD signal marked by the black, horizontal bars.
 The summation of all background signals is shown as a wavy, solid red line in Figure \ref{figure:map}c, and the signal of secondary electrons, background subtracted, is shown as the lower trace of data points in Figure \ref{figure:map}a.
@@
 These data were recorded under all expansion conditions listed in Table 1.
-
-Similar figures were recorded for all combinations of expansion parameters listed in Table~1 of the main paper.
-A more detailed description of methods for analysing these data sets has been given.\cite{Foerstel_phd}
+A more detailed description of methods for analysing the data sets has been given.\cite{Foerstel_phd}
 %
 %
-\section{ICD/ETMD spectra}
+\section{Experimental ICD/ETMD spectra}
 %
@@
  \centering
- \includegraphics[width=8.2cm]{pics/630_631_cs.pdf}
- \includegraphics[width=8.2cm]{pics/673_674_cs.pdf}
+ \includegraphics[width=13.12cm]{pics/630_631_cs.pdf}
+ \includegraphics[width=13.12cm]{pics/673_674_cs.pdf}
  \caption{
-Energy spectrum of all coincident secondary (ICD or ETMD) electrons $e_2$ pertaining to primary electrons $e_1$ in the Ar 3s binding energy region. 
-Spectra were recorded with photon energies of $h\nu = 32$~eV (symbols) and $h\nu = 34$~eV (trace). 
-Spectra were normalized to equal area. 
+Photon excited secondary electron spectra of mixed Ar-Xe clusters.
+Spectra pertain to ICD and ETMD electrons with kinetic energy $e_2$ that are emitted after photoionization of an Ar 3s electron.
+Excitation energies of $h\nu = 32$~eV (symbols) and $h\nu = 34$~eV (traces) are compared.
+For comparison, spectra in each panel were normalized to equal area. 
+(a) small clusters, 5\,\% Xe in the initial gas mixture.
+(b) large clusters, 1.2\,\% Xe in the initial gas mixture.
  \label{figure:hnucomp}
@@
 %
-The background subtracted signal of secondary electrons $e_2$ being recorded in coincidence with a primary Ar 3s photoelectron $e_1$ is interpreted as the energy spectrum of ICD/ETMD of the cluster ensemble under study.
+The background subtracted signal of secondary electrons (of kinetic energy $e_2$) recorded in coincidence with a primary Ar 3s photoelectron (of kinetic energy $e_1$) is interpreted as the energy spectrum of ICD/ETMD of the cluster ensemble under study.
 Some representative examples for such spectra are shown in the main article.
@@
 As expected, the shape of the coincident $e_2$ spectra does not depend on the excitation energy (examples: Figure \ref{figure:hnucomp}).
+For an excitation photon energy of $h\nu = 34$~eV, $e_2$ energies up to at least four eV can be observed in coincidence with an Ar 3s primary photoelectron.
+No secondary electrons with energies exceeding two eV are observed however.
 
@@
  \caption{
-Energy spectrum of all coincident secondary (ICD or ETMD) electrons $e_2$ pertaining to primary electrons $e_1$ in the Ar 3s binding energy region. 
+Same as Figure \protect\ref{figure:hnucomp}.
 Comparison of the spectra from cluster ensembles of different mean size.
 Spectra were recorded at $h\nu = 32$~eV and were normalized to equal area. 
+(a) small to large clusters, 3\,\% Xe in the initial gas mixture.
+(b) very large and large clusters, 2.5\,\% Xe or 3\,\% Xe in the initial gas mixture, resp.
+(c) small to large clusters, 5\,\% Xe in the initial gas mixture.
  \label{figure:sizcomp}
@@
 Comparison of the spectra from cluster ensembles of different gas composition, see Figure \protect\ref{figure:sizcomp} for details.
+(a) small cluster, 1.2-5\,\% Xe in the initial gas mixture.
+(b) medium-sized clusters, 1.2-5\,\% Xe in the initial gas mixture.
  \label{figure:compcomp}
@@
 As discussed in the main paper, the differences between clusters of different size (Figure \ref{figure:sizcomp}) are more substantial than those between clusters of different gas composition (Figure \ref{figure:compcomp}).
+
+\clearpage
+\input{supp_theo_specs}
 

### 2016-06-05 theo_results.tex
small textual edits throughout the ms. Abstract rewritten.

@@
 or in which 1-6 Ar atoms of such cluster were replaced by Xe atoms.
-Afterwards the cluster structures were optimized using force fields to
+Mixed cluster structures were optimized using force fields to
 give local minimum structures.
@@
  3 &     2 &    53 &  3.6  & cs    &         &          & 0.033 & 0.167 &  16.7& \ref{figure:xe_3_in}\\ %2.006$\cdot 10^{-5}$ \\ ArXe\_3\_2atom      
- 4 &  1415 &   642 & 68.8  & cs    &         &          & 7.039 & 2.573 &  73.2& suppl.\\ %9.612$\cdot 10^{-4}$ \\ ArXe\_8\_1layer     
+ 4 &  1415 &   642 & 68.8  & cs    &         &          & 7.039 & 2.573 &  73.2& supp.\\ %9.612$\cdot 10^{-4}$ \\ ArXe\_8\_1layer     
  5 &   561 &  3310 & 14.5  & cs    &         &          &       &       &  85  & \ref{figure:xe_6_lay5}\\ % c6l5
@@
                                                                                                  \midrule
-20 &     2 &    36 &  5.3  & cs    &         &          & 0.117 & 0.151 &  43.6& suppl.\\                        % Ar$_{36}$Xe$_{2}$   
-21 &     4 &    34 & 10.5  & mixed &         &          & 0.248 & 0.587 &  29.7& suppl.\\                        % Ar$_{34}$Xe$_{4}$   
-22 &     5 &    33 & 13.2  & mixed &         &          & 0.335 & 0.844 &  28.4& suppl.\\                        % Ar$_{33}$Xe$_{5}$   
-23 &    13 &    25 & 34.2  & mixed &         &          & 0.828 & 5.414 &  13.3& suppl.\\                        % Ar$_{25}$Xe$_{13}$  
-24 &    24 &    14 & 63.2  & mixed &         &          & 1.488 &16.718 &   8.2& suppl.\\                        % Ar$_{14}$Xe$_{24}$  
-25 &    25 &    13 & 65.8  & in    &         &          & 1.432 & 4.995 &  22.3& suppl.\\                        % Ar$_{13}$Xe$_{25}$  
-26 &    35 &     3 & 92.1  & in    &         &          & 2.017 & 7.051 &  22.2& suppl.\\                        % Ar$_{3}$Xe$_{35}$   
+20 &     2 &    36 &  5.3  & cs    &         &          & 0.117 & 0.151 &  43.6& supp.\\                        % Ar$_{36}$Xe$_{2}$   
+21 &     4 &    34 & 10.5  & mixed &         &          & 0.248 & 0.587 &  29.7& supp.\\                        % Ar$_{34}$Xe$_{4}$   
+22 &     5 &    33 & 13.2  & mixed &         &          & 0.335 & 0.844 &  28.4& supp.\\                        % Ar$_{33}$Xe$_{5}$   
+23 &    13 &    25 & 34.2  & mixed &         &          & 0.828 & 5.414 &  13.3& supp.\\                        % Ar$_{25}$Xe$_{13}$  
+24 &    24 &    14 & 63.2  & mixed &         &          & 1.488 &16.718 &   8.2& supp.\\                        % Ar$_{14}$Xe$_{24}$  
+25 &    25 &    13 & 65.8  & in    &         &          & 1.432 & 4.995 &  22.3& supp.\\                        % Ar$_{13}$Xe$_{25}$  
+26 &    35 &     3 & 92.1  & in    &         &          & 2.017 & 7.051 &  22.2& supp.\\                        % Ar$_{3}$Xe$_{35}$   
 \bottomrule
@@
 We will now discuss features of several structures, using selected examples.
-First we consider cluster having an argon core of 13 and 55 atoms with a single xenon
+First we consider clusters having an argon core of 13 and 55 atoms with a single xenon
 atom on one of the surfaces (see Figure \ref{figure:cluster_3_overview}a
-for the 55 atom core).
+for the 55 atoms core).
 Secondary electron spectra simulated for these systems are shown in Figure \ref{figure:surf}, top panel.
@@
 %spectrum t
-The spectrum pertaining to the clusters with larger (55 atom) Ar core shows
+The spectrum pertaining to the clusters with larger (55 atoms) Ar core shows
 signals at higher energies of the secondary electron. These features
@@
 %{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
-The three energetically separated peaks in the ETMD(3) spectrum pertain to different combinations of the Xe 5p$_j^{-1}$ vacancy states, which have a substantial fine-structure splitting (see Section \ref{sec:exp_results}).
+The three energetically separated peaks in the ETMD(3) spectrum pertain to different combinations of the Xe 5p$_j^{-1}$ vacancy states, which have a substantial fine-structure splitting (see Section `Experimental Results').
+%\ref{sec:exp_results}).
 %
@@
 %
-For the 55 atom clusters, a xenon content of \unit[10--12]{\%}
+For the 55 atoms clusters, a xenon content of \unit[10--12]{\%}
 corresponds to six xenon atoms out of a total of 55 atoms. These can form a connected 
@@
  \centering
- \includegraphics[width=\columnwidth]{pics/c6l5.pdf}
+ \includegraphics[width=8.5cm]{pics/c6l5.pdf}
  \caption{Same as Figure \protect\ref{figure:2tops},

### 2016-06-05 theory.tex
small textual edits throughout the ms. Abstract rewritten.

@@
 decay width $\Gamma=\frac{\hbar}{\tau}$,
-which is inverse proportional to the lifetime $\tau$ of the decay process.
+which is inversely proportional to the lifetime $\tau$ of the decay process.
 The manifold of the
@@
 knowledge of the energies of the initial and the final states, $E_{\rm in}$ and $E_{\rm fin}$, of
-the corresponding processes are necessary.
+the corresponding processes is necessary.
 If the channel

### 2016-06-05 supp_theo_specs.tex
Schreibweise ETMD

@@
-\section{Additional Theoretical ICD/ETMD3 Spectra}
+\section{Additional Theoretical ICD/ETMD(3) Spectra}
 
@@
 using an evolutionary algorithm based on two-body potentials of the Lennard-Jones (LJ) type, or using two other models aimed at improving over the simple LJ potential.\cite{marques}
-In this section, the simulated ICD and ETMD3 spectra for selected cluster
+In this section, the simulated ICD and ETMD(3) spectra for selected cluster
 structures shown in Figure 7 of Ref. \citenum{marques} are shown in Figures
@@
           \unit[5]{\%} to \unit[13]{\%}.
-          According to our simulations ETMD3 is the most prominent decay
+          According to our simulations ETMD(3) is the most prominent decay
           process for these cluster structures.
@@
           atoms, with one single Xe-Xe distance occurs in the cluster,
-          and therefore, the ETMD3 spectrum is very similar
+          and therefore, the ETMD(3) spectrum is very similar
           to the one of a trimer, showing two peaks originating
-          from three different decay channels. In the other two cases the ETMD3
-          spectrum is slightly more complex, but in all three cases, the ETMD3
+          from three different decay channels. In the other two cases the ETMD(3)
+          spectrum is slightly more complex, but in all three cases, the ETMD(3)
           is manifested by peaks between \unit[0.5]{eV} and \unit[4.0]{eV}, which 
@@
           than \unit[50]{\%}.
-          Our simulations show that ETMD3 is the dominant process
+          Our simulations show that ETMD(3) is the dominant process
           for these cluster structures.
@@
 
-For all of these cluster structures, ETMD3 is the more probable decay process and
-except for the Ar$_{36}$Xe$_2$ case with \unit[43.6]{\%} ICD, the ETMD3 is clearly
+For all of these cluster structures, ETMD(3) is the more probable decay process and
+except for the Ar$_{36}$Xe$_2$ case with \unit[43.6]{\%} ICD, the ETMD(3) is clearly
 the dominant process (compare Table 2 of the main article).
@@
 scattered distribution of the xenon atoms within the cluster structures.
-Since the decay width of the ETMD3 is mostly caused by the decay
-with direct neighbours and for these $\Gamma_{ETMD3} \propto N_{Ar} N_{Xe}^2$
+Since the decay width of the ETMD(3) is mostly caused by the decay
+with direct neighbours and for these $\Gamma_{ETMD(3)} \propto N_{Ar} N_{Xe}^2$
 both the maximization of direct xenon neighbours of an argon atom and the
 maximization of the number of argon atoms being surrounded by xenon atoms
-leads to a strong increase of the ETMD3 decay width. This situation is realized
+leads to a strong increase of the ETMD(3) decay width. This situation is realized
 in cluster structures without a seggregation of the two different elements like
-in the structures of Ref. \cite{}. At the same time, all ICD channels are closed
+in the structures of Ref. \cite{marques}. At the same time, all ICD channels are closed
 for direct xenon neighbours. Therefore, a higher number of direct xenon neighbours

### 2016-06-05 theo_results.tex
Schreibweise ETMD

@@
 atoms in the interface region of the xenon core and the argon shell.
-The ETMD3, depending on the electron transfer from one xenon atom to the
+The ETMD(3), depending on the electron transfer from one xenon atom to the
 initially ionized argon atom and hence the corresponding orbital overlap,

### 2016-06-05 exp_results.tex
try to change format of label

@@
-\section{Experimental Results
-\label{sec:exp_results}}
+\section{Experimental Results}
+\label{sec:exp_results}
 %
@@
 A crystal field splitting of the 3p$_{3/2}$ state has been assumed to be also present, but with a smaller value of 0.1-0.2 eV, approx.\cite{jacobi2} 
-The spectrum clearly changes when going to an emission angle of 40$^\circ$ with respect to the surface normal (Fig.\ 2 in Ref.\ \cite{jacobi2}).
+The spectrum clearly changes when going to an emission angle of 40$^\circ$ with respect to the surface normal (Fig.\ 2 in Ref.\ \citenum{jacobi2}).
 The higher binding energy peak significantly loses in intensity, and the spectrum is now dominated by a single peak comprising both crystal field split substates of Ar 3p$_{3/2}$, with a FWHM ($w$) of only 0.4 eV.
@@
 
-Finally, comparing Figure \ref{figure:oval2} to Figure \ref{figure:oval1} reveals
-that much larger changes in the valence emission spectra occur for changes in
-the expansion conditions than for changes of the gas mixture.
+Finally, comparing Figure \ref{figure:oval2} to Figure \ref{figure:oval1} reveals that much larger changes in the valence emission spectra occur by changes in
+the expansion conditions than by changes of the gas mixture.
 This finding is supported by the spectra shown in Ref.\ \citenum{lindblad}.
@@
 These, and the following figure, constitute the central experimental result of the article.
-Spectra recorded at $h\nu = 34$ eV as a cross-check quantitatively agree to those shown in the Figure.
+Spectra recorded at $h\nu = 34$ eV as a cross-check quantitatively agree to those shown here.
 This underpins our assignment of this intensity to an autoionization process.
@@
 Within the accuracy of our experiment we found an Ar 3s autoionization efficiency which is smaller than unity for all spectra with Xe$_{\rm in}$ of 1.2\,\%, and decreases with cluster size. 
-For larger Xe$_{\rm in}$, the values are compatible with one.
+For larger Xe$_{\rm in}$, the values are compatible with unity.

### 2016-06-05 experimental.tex

@@
 \caption{
-Expansion parameters used for cluster production. 
+The expansion parameters used for cluster production. 
 Here, Xe$_{\rm in}$ is the molar fraction of Xe in the gas mixture before the expansion, $T$ is the nozzle temperature, and $p$ the stagnation pressure. 
-Experiments were done with $d = 80~\mu$m (first two sections) and $d = 100~\mu$m (bottom section) conical nozzles of 15$^\circ$ half opening angle. 
+Experiments were performed with $d = 80~\mu$m (first two sections) and $d = 100~\mu$m (bottom section) conical nozzles of 15$^\circ$ half opening angle. 
 We basically have an Ar seeded expansion of Xe gas, as the freezing point of Ar is much lower. 
@@
 % 1103 676, 679
-ArXe & S & 1.2 &  174   & 0.32  & 4  &   74 \\
+ArXe & `S' & 1.2 &  174   & 0.32  & 4  &   74 \\
 % 1103 670
-ArXe & M & 1.2 &  174   & 0.49  & 11  &  199 \\
+ArXe & `M' & 1.2 &  174   & 0.49  & 11  &  199 \\
 % 1103 671
-ArXe & L & 1.2 &  174   & 0.68  & 23  &  431 \\
+ArXe & `L' & 1.2 &  174   & 0.68  & 23  &  431 \\
 % 1103 663
-ArXe & S & 3.0 &  172   & 0.28  & 3  &   57 \\
+ArXe & `S' & 3.0 &  172   & 0.28  & 3  &   57 \\
 % 1103 640
-ArXe & M & 5.0 &  171   & 0.51  & 13  &  240 \\
+ArXe & `M' & 5.0 &  171   & 0.51  & 13  &  240 \\
 % 0506 382, Keller offset ber?cksichtigt
@@
 % 1103 653
-ArXe & M & 3.0 &  172   & 0.51  & 12  &  233 \\
+ArXe & `M' & 3.0 &  172   & 0.51  & 12  &  233 \\
 % 1103 658
-ArXe & L & 3.0 &  172   & 0.68  & 24  &  458 \\
+ArXe & `L' & 3.0 &  172   & 0.68  & 24  &  458 \\
 % 1103 630
-ArXe & S  & 5.0 &  167  & 0.37  & 7  &  129 \\
+ArXe & `S'  & 5.0 &  167  & 0.37  & 7  &  129 \\
 % 1103 629
-ArXe & L  & 5.0 &  167  & 0.68  & 28  &  537 \\
+ArXe & `L'  & 5.0 &  167  & 0.68  & 28  &  537 \\
 \midrule
 % 1004 867 (32 eV)
-ArXe & XL & 2.5 &  154  & 2.12  & 995 & 18800\\
+ArXe & `XL' & 2.5 &  154  & 2.12  & 995 & 18800\\
 % 1004 868
@@
 Expansion parameters are given in Table \ref{tab:cluster}. 
+Similar expansion conditions are further referred by labels `S'-`XL', as given shown in the Table.grep
 
@@
 A recent investigation of cluster sizes in a mixed Ar-Kr expansion yielded a revised scaling law, which essentially amounts to the use of a weighted average over the atom-specific parameters of the two gases.\cite{danylchenko2015}
-Although the analogy to our case is not complete, as phase segregation occurs in Ar-Kr to a much lesser extent,\cite{Vach_1999,lundwall_arkr} we therefore expect scaling law cluster sizes between the values calculated for Ar and Xe.
-Recent analyses of photoionization spectra suggests that mean sizes arrived at by scaling laws are smaller than the actual size, at least for rare gas clusters in the range $\langle N\rangle < 1000$.\cite{bergersen,hergenhahnprb,foerstel_arg2_2011}
-We expansion conditions labelled `S'-`L', we therefore expect that the scaling law estimates are a lower boundary for the actual cluster size.
+Although the analogy to our case is not complete, as phase segregation occurs in Ar-Kr to a much lesser extent,\cite{Vach_1999,lundwall_arkr} we expect scaling law cluster sizes between the values calculated for Ar and Xe.
+Recent analyses of photoionization spectra suggest that mean sizes arrived at by scaling laws are smaller than the actual size, at least for rare gas clusters in the range $\langle N\rangle < 1000$.\cite{bergersen,hergenhahnprb,foerstel_arg2_2011}
+For the expansion conditions labelled `S'-`L', we therefore expect that the scaling law estimates are a lower boundary for the actual cluster size.
 
-The expansion chamber for the supersonic jet is separated from the interaction chamber by a non-magnetic, conical skimmer with a diameter 1~mm opening (Beam Dynamics). 
+The expansion chamber for the supersonic jet is separated from the interaction chamber by a non-magnetic, conical skimmer with an opening of 1~mm in diameter (Beam Dynamics). 
 At few cm distance behind the skimmer, the cluster jet was crossed by synchrotron radiation from the BESSY electron storage ring at Helmholtz-Zentrum Berlin. 
@@
 
-Entrance aperture and drift tube of the magnetical bottle spectrometer can be independently biased to influence the electron flight times. 
+The entrance aperture and drift tube of the magnetical bottle spectrometer can be independently biased to influence the electron flight times. 
 For the data shown here, slightly positive bias voltages were used (+1.8 V to +2.2 V) in order to have all electrons arriving at the detector within one BESSY single bunch period (800 ns). 
 The detection efficiency was determined as 0.6, with the method outlined in Ref.\ \citenum{mucke_review}.
+Data were converted from flight times to kinetic energy by measuring calibration data for atomic photolines of known binding energy.
+The systematical uncertainty of this procedure may lead to a common shift of all experimental kinetic energy data shown in this article of up to 30~meV.
 

### 2016-06-05 intro.tex

--- 2016-05-23 intro.tex
@@
 cederbaum} In ICD, an electronic excitation decays by energy 
-transfer to one of its neighbour atoms or molecules, thus 
+transfer to one of its neighboring atoms or molecules, thus 
 releasing a free electron from the latter site. ICD is an 
@@
 Xe dopant atoms in an Ar matrix to clusters containing an equal 
-amount of both species. By the use of electron, electron 
-coincidence spectroscopy and of {\it ab initio} calculations on 
+amount of both species. By the use of electron-electron 
+coincidence spectroscopy and of theoretical simulations on 
 prototypical systems we show how the radiationless decay spectrum 
@@
 Intermolecular Coulombic Decay initially was predicted from 
-theoretical considerations of the energy levels in singly vs. 
-doubly ionized, and doubly vs. triply ionized, hydrogen bonded 
+theoretical considerations of the energy levels in singly vs.\  
+doubly ionized, and doubly vs.\ triply ionized, hydrogen bonded 
 clusters.\cite{cederbaum} First experimental work some years 
@@
 We find that both energy and charge transfer induced 
-autoionization plays a role in Ar-Xe, and will detail the 
+autoionization play a role in Ar-Xe, and will detail the 
 relevant processes below. The notion of ICD requires that the 
@@
 photoelectron spectra with respect to structural features of the 
-mixed clusters is also available.\cite{lundwall} In Ref. \cite{
+mixed clusters is also available.\cite{lundwall} In Ref.\ \citenum{
 fasshauer2014} it was shown that an analysis of the ICD spectra 
@@
 Xe was also found to diffuse into the interior of Ar clusters in molecular dynamics simulations after pick-up.\cite{Vach_1999} 
-The electronic energy levels of very small Ar-Xe clusters were calculated in Ref.s~ \citenum{fasshauer,Fasshauer13}.
+The electronic energy levels of very small Ar-Xe clusters were calculated in Ref.~ \citenum{fasshauer} and the secondary electron spectra were simulated for
+model structures of one argon atom placed on a xenon surface \cite{Fasshauer13}.
 Interestingly, it was found that Ar 3s$^{-1}$ is stable 
 against autoionization in an ArXe dimer, but is destabilized by 
-adding further Xe atoms, or an Ar solvation shell, to the system. 
+adding further Xe atoms, or an Ar solvation shell, to the system, thereby allowing
+for combinations of argon and xenon atoms with larger interatomic distances. 
 Again, we will detail these results in conjunction with our 

### 2016-06-05 theo_discussion.tex

@@
 
-As a cross-check for our theoretical methods we have calculated the radiationless decay spectrum of Ar 3s$^{-1}$ in ArKr, and arrived at qualitative agreement with the experimental data.\cite{arkr}
+As a cross-check for our theoretical methods we have calculated the radiationless decay spectrum of Ar 3s$^{-1}$ in ArKr, which may arise {\it only} from ETMD(3),\cite{foerstel} and arrived at qualitative agreement with the experimental data.\cite{arkr}
+
+The size-dependent trend within the experimental data is in qualitative agreement to the change in the calculated spectral shape for ICD in systems of increased size (compare Figure~\ref{figure:2tops} to \ref{figure:xe_3_in} and \ref{figure:xe_6_lay5}.)
 
@@
 As even in these two cases intensity for decay via ETMD would not vanish completely, we have to leave it open though whether other mechanisms are present, which further suppress ETMD vs. ICD.
+
+While in early work on ICD it has almost been a paradigm that the decay involves two {\it neighbouring} atoms or molecules,\cite{hergenhahn_review} more recently significant intensity for non-nearest neighbour ICD has been found also in other systems.
+One example is Ne-Ar after Ne 2s ionization, where decay to Ar in the second coordination shell is clearly visible despite the fact that in this system decay involving nearest neighbours is energetically allowed.\cite{fasshauer2014}
+A further theoretical delineation of the respective factors has recently been presented by onw of us.\cite{fasshauernjp}

### 2016-06-05 theory.tex

@@
 of their internuclear distance) for the ICD and triples (combinations of three atoms)
-for the ETMD3.
+for the ETMD(3).
 These atoms do not necessarily need to form bonds between each other or
@@
 Auger process all three atoms coincide, for an ICD process $X_{\rm in}$
-coincides with $X_{D}$, for an ETMD2 process $X_D$ and $X_E$ coincide
-and for an {ETMD}3 process
+coincides with $X_{D}$, for an ETMD(2) process $X_D$ and $X_E$ coincide
+and for an ETMD(3) process
 all ionized states are located on different atoms.
@@
 of all decay mechanisms. In case of the ArXe clusters we only consider
-ICD and ETMD3, because the ETMD2 pathway is energetically not accessible:
+ICD and ETMD(3), because the ETMD(2) pathway is energetically not accessible:
 

### 2016-06-07 supp_theo_specs.tex
work on supporting information

@@
 Recently, structures for ArXe clusters of in total 38 atoms were optimized
-using an evolutionary algorithm based on two-body potentials of the Lennard-Jones (LJ) type, or using two other models aimed at improving over the simple LJ potential.\cite{marques}
+using an evolutionary algorithm based on two-body potentials of the
+Lennard-Jones (LJ) or the improved Lennard-Jones type \cite{marques,Pirani08},
+which have been fitted to experimental parameters.
 In this section, the simulated ICD and ETMD(3) spectra for selected cluster

### 2016-06-07 abstract.tex
Überarbeiten

@@
 \begin{abstract}
-We report about autoionization channels of Ar inner valence ionized states in mixed ArXe clusters. 
-Our experimental data obtained by electron-electron coincidence spectroscopy are compared to theoretical simulations for representative cluster structures.
+We report about autoionization channels of Ar inner valence ionized states in mixed ArXe clusters and compare
+our experimental data obtained by electron-electron coincidence spectroscopy
+to our theoretical simulations for representative cluster structures.
 The combined experimental and theoretical data show that the autoionization of Ar 3s$^{-1}$ in ArXe is dominated by Interatomic Coulombic Decay (ICD) to Xe atoms in the second and higher coordination shells of the originally excited atom.
-Clusters with a range of sizes and compositions were probed. 
+Clusters with a range of sizes, compositions and structures were probed. 
 The Xe content in the clusters was varied between 10\,\% and 53\,\%. 

### 2016-06-07 intro.tex
Überarbeiten

@@
  (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
- which the originally excited site is neutralized by the decay, 
- and `exchange ICD' for charge transfer contributions to the 
- normal ICD amplitude.\cite{santrarev,jahnkesat}
+ which the originally excited site is neutralized by the decay.
+% and `exchange ICD' for charge transfer contributions to the 
+% normal ICD amplitude.\cite{santrarev,jahnkesat}
 We find that both energy and charge transfer induced 

### 2016-06-07 structures.tex
Überarbeiten

@@
 field implemented in the 
-Avogadro programme (version 1.1.0) \cite{Avogadro,Hanwell12}.
+Avogadro programme (version 1.1.0) \cite{Avogadro,Hanwell12} to give local
+minimum structures.
 All cluster structures are listed in Table \ref{table:theo_gammas}.
@@
 \end{itemize}
+
+These structures were then optimized using force field methods.
 %

### 2016-06-07 theo_discussion.tex
Überarbeiten

@@
 One example is Ne-Ar after Ne 2s ionization, where decay to Ar in the second coordination shell is clearly visible despite the fact that in this system decay involving nearest neighbours is energetically allowed.\cite{fasshauer2014}
-A further theoretical delineation of the respective factors has recently been presented by onw of us.\cite{fasshauernjp}
+A further theoretical delineation of the respective factors has recently been presented by one of us.\cite{fasshauernjp}

### 2016-06-07 theo_results.tex
Überarbeiten

@@
 or in which 1-6 Ar atoms of such cluster were replaced by Xe atoms.
-Mixed cluster structures were optimized using force fields to
-give local minimum structures.
 The last group contains data for calculated minimal energy structures
@@
  \caption{
- {\it Q: Generell f\"ande ich es gut wenn man die panels immer mit a), b), \dots kennzeichnen k\"onnte.}
  %
@@
 signals at higher energies of the secondary electron. These features
-can be explained by looking at the Ar-Xe distances in the clusters, shown
+can be explained by investigating the Ar-Xe distance distributions
+in the clusters, shown
 in the bottom panel of Figure \ref{figure:surf}. 
@@
 %{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
-The three energetically separated peaks in the ETMD(3) spectrum pertain to different combinations of the Xe 5p$_j^{-1}$ vacancy states, which have a substantial fine-structure splitting (see Section `Experimental Results').
+The three energetically separated peaks in the ETMD(3) spectrum pertain to different combinations of the Xe 5p$_j^{-1}$ vacancy states, which have a substantial fine-structure splitting (see Table \ref{tab:valence}).
 %\ref{sec:exp_results}).
@@
 the more homogeneous does the interface region become for clusters of
-different sizes. This is manifests itself in the distribution of relevant
+different sizes. This manifests itself in the distribution of relevant
 Ar-Xe pair distances (compare Fig. \ref{figure:surf} lower panel).

### 2016-06-08 intro.tex
excitation - additional sentences
add exchange ICD agin

@@
  which the originally excited site is neutralized by the decay.
-% and `exchange ICD' for charge transfer contributions to the 
-% normal ICD amplitude.\cite{santrarev,jahnkesat}
+ and `exchange ICD' for charge transfer contributions to the 
+ normal ICD amplitude.\cite{santrarev,jahnkesat}
 We find that both energy and charge transfer induced 

### 2016-06-09 intro.tex
take care of C-Ne

@@
 decay spectra can be used to derive information on a nanoparticle 
-or a solvation system, for example. We report here about studies 
+or a solvation system, for example. 
+Here, the term excitation is used in a broader sense---in the
+systems we consider in this work, ICD occurs from an excited, singly 
+charged Ar state created by photoionization.
+In other systems, ICD was also observed from neutral excited
+states and states with more than one vacancy.
+
+We report here about studies 
 in which we produced heterogeneous clusters of the noble gases Ar 
@@
  (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
- which the originally excited site is neutralized by the decay.
+ which the originally excited site is neutralized by the decay 
 and `exchange ICD' for charge transfer contributions to the 

### 2016-06-14 summary.tex
add more details to summary

@@
 By comparing our measured spectra to calculations, we identified `long range'
-ICD as the most important decay mode.
+ICD as the most important decay mode and were able to determine the most
+probable structural motifes to be a xenon core surrounded by several argon layers
+for large clusters and argon clusters with with very few xenon atoms spread out
+over the surface.

### 2016-06-26 intro.tex
Änderungen von Melanie

@@
 electronically excited states. One such process, which is of 
-particular importance in weakly bonded systems, is the 
+particular relevance in weakly bonded systems, is the 
 Interatomic or Intermolecular Coulombic Decay (ICD).\cite{
@@
 important relaxation channel e.g. for inner-valence holes in 
-elements C-Ne, and also for core levels vacancies e.g. in \ce{H2O}
+atoms, and also for core level vacancies e.g. in \ce{H2O}
 , where it competes with Auger decay.\cite{slavicek}
@@
 decay spectra can be used to derive information on a nanoparticle 
-or a solvation system, for example. 
-Here, the term excitation is used in a broader sense---in the
+or a solvation system. 
+The term excitation is used here in a broader sense---in the
 systems we consider in this work, ICD occurs from an excited, singly 
@@
 photoelectron spectra with respect to structural features of the 
-mixed clusters is also available.\cite{lundwall} In Ref.\ \citenum{
+mixed clusters is also available.\cite{lundwall} In ref \citenum{
 fasshauer2014} it was shown that an analysis of the ICD spectra 
@@
 Xe was also found to diffuse into the interior of Ar clusters in molecular dynamics simulations after pick-up.\cite{Vach_1999} 
-The electronic energy levels of very small Ar-Xe clusters were calculated in Ref.~ \citenum{fasshauer} and the secondary electron spectra were simulated for
+The electronic energy levels of very small Ar-Xe clusters were calculated in ref \citenum{fasshauer} and the secondary electron spectra were simulated for
 model structures of one argon atom placed on a xenon surface \cite{Fasshauer13}.

### 2016-06-26 supp_theo_specs.tex
Änderungen von Melanie

--- 2016-06-05 supp_theo_specs.tex
@@
 Recently, structures for ArXe clusters of in total 38 atoms were optimized
-using an evolutionary algorithm based on two-body potentials of the Lennard-Jones (LJ) type, or using two other models aimed at improving over the simple LJ potential.\cite{marques}
+using an evolutionary algorithm based on two-body potentials of the
+Lennard-Jones (LJ) or the improved Lennard-Jones type,\cite{marques,Pirani08}
+which have been fitted to experimental parameters.
 In this section, the simulated ICD and ETMD(3) spectra for selected cluster
-structures shown in Figure 7 of Ref. \citenum{marques} are shown in Figures
+structures shown in Figure 7 of ref \citenum{marques} are shown in Figures
 \ref{figure:ArXe_lt15} -- \ref{figure:ArXe_gt50} and discussed.
@@
 % \includegraphics[width=0.32\columnwidth]{pics/Ar33Xe5.pdf}
- \includegraphics[width=8.2cm]{pics/Ar36Xe2.pdf}
- \includegraphics[width=8.2cm]{pics/Ar34Xe4.pdf}
- \includegraphics[width=8.2cm]{pics/Ar33Xe5.pdf}
+ \includegraphics[width=8.0cm]{pics/Ar36Xe2.pdf}
+ \includegraphics[width=8.0cm]{pics/Ar34Xe4.pdf}
+ \includegraphics[width=8.0cm]{pics/Ar33Xe5.pdf}
  \caption{Ar$_N$Xe$_{38-N}$ clusters with a xenon content of
@@
 % \includegraphics[width=0.32\columnwidth]{pics/Ar25Xe13.pdf}
- \includegraphics[width=8.2cm]{pics/Ar25Xe13.pdf}
+ \includegraphics[width=8.0cm]{pics/Ar25Xe13.pdf}
  \caption{
-          Same as Fig. \ref{figure:ArXe_lt15}, but for the 
-          optimized structure of an Ar$_25$Xe$_{13}$ cluster 
+          Same as Figure \ref{figure:ArXe_lt15}, but for the 
+          optimized structure of an Ar$_{25}$Xe$_{13}$ cluster 
           with a xenon content of \unit[34]{\%}.}
@@
 % \includegraphics[width=0.32\columnwidth]{pics/Ar3Xe35.pdf}
- \includegraphics[width=8.2cm]{pics/Ar14Xe24.pdf}
- \includegraphics[width=8.2cm]{pics/Ar13Xe25.pdf}
- \includegraphics[width=8.2cm]{pics/Ar3Xe35.pdf}
+ \includegraphics[width=8.0cm]{pics/Ar14Xe24.pdf}
+ \includegraphics[width=8.0cm]{pics/Ar13Xe25.pdf}
+ \includegraphics[width=8.0cm]{pics/Ar3Xe35.pdf}
  \caption{Ar$_N$Xe$_{38-N}$ clusters with a xenon content of more
@@
 leads to a strong increase of the ETMD(3) decay width. This situation is realized
-in cluster structures without a seggregation of the two different elements like
-in the structures of Ref. \cite{marques}. At the same time, all ICD channels are closed
+in cluster structures without a segregation of the two different elements like
+in the structures of ref \citenum{marques}. At the same time, all ICD channels are closed
 for direct xenon neighbours. Therefore, a higher number of direct xenon neighbours

### 2016-06-26 theory.tex
Änderungen von Melanie

@@
 start with a decomposition of the system into interaction partners of
-the different, relevant decay mechanisms, i.e. pairs (combination of two atoms regardless
+the different relevant decay mechanisms, i.e. pairs (combination of two atoms regardless
 of their internuclear distance) for the ICD and triples (combinations of three atoms)
@@
           internuclear distance, using the experimental ionization potentials given
-          in Table \ref{tab:valence}. For distances larger than the channel opening
+          below in Table \ref{tab:valence}. For distances larger than the channel opening
           distance the ICD channel is open.}
@@
 it can be seen that a higher xenon content in the cluster statistically
-favours the ETMD(3) over the ICD.
+favours ETMD(3) over ICD.
 
@@
 where $J_A$, $J_A'$ and $M_A$, $M_A'$ denote the total angular momentum of the
-initially ionized atom (which is the same as the electron doner atom) in the
+initially ionized atom (which is the same as the electron donor atom) in the
 initial and final state, respectively,
@@
 transition moment $m$
-(compare Ref. \cite{Fasshauer13}).
+(compare ref \citenum{Fasshauer13}).
 
 In this work we evaluate the secondary energies and decay widths with
-the program HARDRoC \cite{HARDRoC,fasshauer2014} using the
+the programme HARDRoC\cite{HARDRoC,fasshauer2014} using the
 experimental ionization energies of Table \ref{tab:valence}
 and data from the literature given in Tables II and III.
-This choice is identical to the one made in Reference \cite{Fasshauer13}.
+This choice is identical to the one made in ref \citenum{Fasshauer13}.

### 2016-06-27 abstract.tex

@@
 Besides ICD, also Electron Transfer Mediated Decay (ETMD(3)) was found important in many of the calculated spectra, but is seen with less intensity in the experimental spectra. 
-From the calculations, we identify structural motifes which minimize the ETMD vs.
+From the calculations, we identify structural motifs which minimize the ETMD vs.
 the ICD rate and suggest that these are preferentially realized in our experiment, in which clusters are formed by supersonic expansion of an Ar-Xe mixture.
-Suggested cluster structures either feature a clear seggregation between Ar and Xe fractions, e.g. Xe core, Ar shell systems, or contain a few Xe atoms singled out in surface sites on an Ar cluster.
+Suggested cluster structures either feature a clear segregation between Ar and Xe fractions, e.g. Xe core, Ar shell systems, or contain a few Xe atoms singled out in surface sites on an Ar cluster.
 These structures differ significantly from the majority of calculated minimum energy structures for ArXe systems of 38 atoms, which might show that the latter, annealed structures are not realized in our experiment.
-We show experimentally that the relaxation of Ar inner valence states by ICD and ETMD together has an efficiency of unity, within the experimental accuracy, for all clusters expect those with the lowest Xe content.
+We show experimentally that the relaxation of Ar inner valence states by ICD and ETMD together has an efficiency of unity, within the experimental accuracy, for all clusters except those with the lowest Xe content.
 \end{abstract}

### 2016-06-27 exp_results.tex
remove comment, please still comment!!!!

@@
 Uncertainties are estimated as $\pm$3\,\% for the Xe content and 0.05~eV for the binding energies. 
-For reference, the row labelled `(th.)' gives the binding energies used in the simulations of this paper, and the last row their atomic counterparts. 
+The row labelled `(th.)' gives the binding energies used in the simulations of this paper, and the last row their atomic counterparts. 
 Values for Ar 3p in the last row refer to the fine structure states.
@@
 The two lower panels show spectra of the mixed species with different mean size. 
-Sharp lines marked `m' result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states. 
-Labels in (b) and (c) give the Xe content in the expanding gas mixture (Xe$_{\rm in}$), which is lower then the Xe content observed in the heterogeneous clusters (Xe$_{\rm cl}$). 
+Sharp lines marked `m' (for `monomer') result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states. 
+Labels in (b) and (c) give the Xe content in the expanding gas mixture (Xe$_{\rm in}$), which is lower than the Xe content observed in the heterogeneous clusters (Xe$_{\rm cl}$). 
 The photon energy was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
-{\color{red}{Die Stabilisierung der Xe-bulk Atome ist in den gemischten Cluster
- höher als in den gemischten Clustern. Das ist ungewöhnlich. Habt ihr hier
- verschiedene CLustergrößen?}}
+%{\color{red}{Die Stabilisierung der Xe-bulk Atome ist in den gemischten Cluster
+% höher als in den gemischten Clustern. Das ist ungewöhnlich. Habt ihr hier
+% verschiedene CLustergrößen?}}
 }
@@
 Outer valence photoelectron spectra of mixed Ar-Xe clusters from gas mixtures with different Xe concentration. 
-For better visibility, a scaling factor is applied to the Xe part of the spectrum in (a).
-See Fig.\ \ref{figure:oval1} and text for details.
+For better visibility, a scaling factor is applied to the Xe part of the spectrum in panel (a).
+See Figure \ref{figure:oval1} and text for details.
 }
@@
 Figure \ref{figure:oval1} shows the outer valence spectra of small and large ArXe clusters, compared to clusters of the pure gases. 
-Qualitatively similar spectra have been published without detailed discussion in Ref.\ \cite{lindblad}.
+Qualitatively similar spectra have been published without detailed discussion in ref \citenum{lindblad}.
 Differences are seen in particular for the Ar component. 
@@
 
-We find experimentally that clusters we have produced have a Xe content Xe$_{\rm cl}$ between 10 and 50\,\%.
+We find experimentally that clusters we have produced have a Xe content Xe$_{\rm cl}$ between 10\,\% and 50\,\%.
 A slight decrease of the binding energy with cluster size is seen for all outer valence lines, and is attributed to a larger final state polarization energy in larger clusters.
 
-For further interpretation of its shape we refer to photoemission spectra of condensed Ar monolayers, measured in several settings.\cite{jacobi,jacobi2}
+For further interpretation of the shape of the Ar peaks we refer to photoemission spectra of condensed Ar monolayers, measured in several settings.\cite{jacobi,jacobi2}
 Spectra were reported for physisorption of Ar on two different metal single crystal substrates, and for Ar atop of a Xe spacer layer adsorbed on the metal.
@@
 A crystal field splitting of the 3p$_{3/2}$ state has been assumed to be also present, but with a smaller value of 0.1-0.2 eV, approx.\cite{jacobi2} 
-The spectrum clearly changes when going to an emission angle of 40$^\circ$ with respect to the surface normal (Fig.\ 2 in Ref.\ \citenum{jacobi2}).
+The spectrum clearly changes when going to an emission angle of 40$^\circ$ with respect to the surface normal (Figure 2 in ref \citenum{jacobi2}).
 The higher binding energy peak significantly loses in intensity, and the spectrum is now dominated by a single peak comprising both crystal field split substates of Ar 3p$_{3/2}$, with a FWHM ($w$) of only 0.4 eV.
@@
 
-Emission from the Xe 5p state shows a much larger fine structure splitting, which dominates the spectrum even in clusters (where other broadening mechanisms are also present). 
-For the mixed clusters, the Xe band broadens and shifts towards lower binding energy for larger size clusters. 
-For pure Xe clusters, an asymmetry observed in the Xe 5p$_{3/2}$ part has no counterpart in the respective spectra from the mixed clusters.
-This might be caused by the difference in photon energy, as can be seen from a comparison to literature spectra (ArXe at $h\nu = 90$ eV in Ref.\ \cite{lindblad}, Xe at $h\nu = 20$ eV in Ref.\ \cite{rolles}).
-For the largest clusters, the nominal size yielded from the jet parameters applied to a pure Xe expansion would correspond to clusters in which bulk atoms far outweigh those on the surface.
-At least for the 5p$_{1/2}$ photoelectron line, this would be seen as a clear asymmetry towards the low binding energy side, which is not observed in our spectra.
+Emission from the Xe 5p state shows a much larger fine structure splitting then from the Ar 3p state; it dominates the spectrum even in clusters (where other broadening mechanisms are also present).
+The shift of the cluster bands with respect to the monomer lines in the largest mixed clusters we have probed (Figure \ref{figure:oval1}b) are similar to the ones in the pure Xe spectrum, the scaling law size of which is at somewhat more than five filled shells.
+This indicates an approximate upper limit for the size of the Xe core in our mixed clusters, as their binding energy shift might be somewhat higher than the one in pure clusters, due to polarization of covering Ar layers.
+Xe cluster features in the spectra of mixed clusters appear less asymmetric than the pure Xe spectrum, and also less asymmetric as some the ArXe spectra shown in ref \citenum{lindblad}.
+This might be caused by the difference in photon energy ($h\nu = 90$ eV in ref \citenum{lindblad} and for the pure Xe spectrum, $h\nu = 32$ eV for the mixed ArXe spectra in this work).
+% For the mixed clusters, the Xe band broadens and shifts towards lower binding energy for larger size clusters.
+%For pure Xe clusters, an asymmetry observed in the Xe 5p$_{3/2}$ part has no counterpart in the respective spectra from the mixed clusters.
+%This might be caused by the difference in photon energy, as can be seen from a comparison to literature spectra (ArXe at $h\nu = 90$ eV in ref \citenum{lindblad}, Xe at $h\nu = 20$ eV in ref \citenum{rolles}).
+%For the largest clusters, the nominal size yielded from the jet parameters applied to a pure Xe expansion would correspond to clusters in which bulk atoms far outweigh those on the surface.
+%At least for the 5p$_{1/2}$ photoelectron line, this would be seen as a clear asymmetry towards the low binding energy side, which is not observed in our spectra.
 
@@
 
-For the smallest clusters we have produced, a plausible model is provided by calculated minimum energy structures of Ar$_N$Xe$_{38-N}$ (Fig.\ 7 in Ref.\ \cite{marques}).
+For the smallest clusters we have produced, a possible model is provided by calculated minimum energy structures of Ar$_N$Xe$_{38-N}$ (Figure 7 in ref \citenum{marques}).
 We there see that for a Xe content of less than 60\,\%, core-shell systems are {\it not} formed, and although the Xe atoms tend to connect, the degree of Ar-Xe mixing is large.
@@
 For Figure \ref{figure:oval2}, possibly, some clusters of our ensemble already are in the core-shell regime, which would lead to an even lower 3p width.
+
 For the largest clusters we have produced (Figure \ref{figure:oval1}b), the low binding energy of the Xe lines and the broadening of the Ar feature without appearance of the `bulk Ar'-maximum, supports formation of a Xe core covered by at least two layers of Ar.
@@
 
-Finally, comparing Figure \ref{figure:oval2} to Figure \ref{figure:oval1} reveals that much larger changes in the valence emission spectra occur by changes in
-the expansion conditions than by changes of the gas mixture.
-This finding is supported by the spectra shown in Ref.\ \citenum{lindblad}.
+Finally, comparing Figure \ref{figure:oval2} to Figure \ref{figure:oval1} reveals that much larger changes in the valence emission spectra occur by changes in size than by changes of the (relative) Xe content.
+This finding is supported by the spectra shown in ref \citenum{lindblad}.
 %
@@
 Photon excited electron spectra of mixed Ar-Xe clusters in the inner valence region.
-Symbols show the Ar 3s photoline from clusters (`cl') and uncondensed Ar monomers (`m'), atop of a background resulting from inelastic intracluster scattering of outer valence photoelectrons (`excitonic satellites'\protect\cite{hergenhahn2002}).
-Colored symbols result from accumulating photoelectrons only from those events, which resulted in the subsequent emission of a second electron.
-Solid lines represent various least-squares fits to the data, see text for details.
-A photon energy of $h\nu = 32$ eV was used.
+Symbols show the Ar 3s photoline from clusters (`cl') and uncondensed Ar monomers (`m'), atop of a background resulting from inelastic intracluster scattering of outer valence photoelectrons (`excitonic satellites').\protect\cite{hergenhahn2002}
+The photon energy was $h\nu = 32$ eV.
+Panel (a) shows all electrons accumulated.
+For the same conditions, in panel (b) we only show electrons that were detected in coincidence with a secondary electron of lower kinetic energy.
+The black solid trace in (a), and red solid trace in (b) result from a least squares fit to the cluster part of the spectrum. 
+The red solid trace in (a) is the fit shown in (b), divided by the detection efficiency of the spectrometer of 0.6.
+Panels (c) and (d) show the same type of data for smaller clusters with a lower Xe content.
+See text for details.
 \label{figure:ival}
@@
 The total photoelectron signal looks similar to literature spectra for pure Ar clusters.\cite{feifel,zhang} 
-A low energy tail seen for the Ar 3s monomer line results from the transmission properties of the electron spectrometer, together with the strongly positive angular distribution parameter of this line.\cite{kruit}
+A low energy tail seen for the Ar 3s monomer line results from the transmission properties of the electron spectrometer, together with the strongly positive angular distribution parameter of this line.\cite{zhang,kruit}
 The Ar 3s cluster line shows no splitting into bulk and surface components, different to the literature on pure clusters but in agreement with our discussion of the outer valence spectra. 
@@
 
-If we produce a spectrum only from those electrons recorded as part of a two-electron coincidence (electron pair with kinetic energies ($e_1,e_2$)) the apparent intensity drops (colored symbols in Figure \ref{figure:ival}).
+If we produce a spectrum only from those electrons recorded as part of a two-electron coincidence (electron pair with kinetic energies ($e_1,e_2$)) the apparent intensity drops (compare panel b to a, and d to c in Figure \ref{figure:ival}).
 This can partly be attributed to the finite detection efficiency of the spectrometer. 
@@
  \caption{
-Energy spectrum of all coincident secondary (ICD or ETMD) electrons $e_2$ pertaining to primary electrons $e_1$ in the Ar 3s binding energy region. 
+Energy spectrum of all coincident secondary (ICD or ETMD) electrons of kinetic energy $e_2$ pertaining to primary electrons of kinetic energy $e_1$ in the Ar 3s binding energy region. 
 Spectra were recorded with a photon energy of $h\nu = 32$~eV. 
-Black symbols with error bars show the data points for the smallest clusters measured (`S'), two larger clusters sizes are shown by the red and blue traces. 
+Black error bars show the data points for the smallest clusters measured (`S'), two larger clusters sizes are shown by the red and blue traces. 
 Error bars for the latter are smaller than the ones shown and have been omitted.
-For comparison, all spectra are shown area-normalized. 
+For better comparison, all spectra are shown area-normalized. 
 }
@@
  \caption{
-Energy spectrum of all coincident secondary (ICD or ETMD) electrons $e_2$ for clusters of the same size, but from gas mixtures with different Xe concentration.
+Energy spectrum of all coincident secondary (ICD or ETMD) electrons, kinetic energy $e_2$, for clusters of the same size, but from gas mixtures with different Xe concentration.
 See Figure \protect\ref{figure:icd_12} for details.
@@
 Due to their low kinetic energy, without use of a coincidence method they could hardly be separated from the background of inelastically scattered photoelectrons.\cite{mucke}
-These, and the following figure, constitute the central experimental result of the article.
+This and the following Figure constitute the central experimental result of the article.
 Spectra recorded at $h\nu = 34$ eV as a cross-check quantitatively agree to those shown here.
@@
 
-Spectra for the three different cluster sizes in Figure \ref{figure:icd_12} are significantly different: Spectra for the larger cluster acquire more intensity in the 1-1.5 eV region and have less intensity for energies below 0.5 eV.
-In contrast to that, the ICD/ETMD spectrum hardly varies when the composition of the expanding gas mixture is changed (Figure \ref{figure:icd_l}).
+Spectra for the three different cluster sizes in Figure \ref{figure:icd_12} are significantly different: Spectra for the larger clusters acquire more intensity in the 1-1.5 eV region and have less intensity for energies below 0.5 eV.
+In contrast to that, the ICD/ETMD spectrum hardly varies when the composition of the expanding gas mixture, and with that the relative Xe content of the clusters, is changed (Figure \ref{figure:icd_l}).
 The full set of ICD/ETMD spectra is shown as Supporting Information.
@@
 A method to derive this information has been established by some of us.\cite{foerstel_2013}
-Briefly, we correct the intensity of the Ar 3s photoline in the coincident spectra by the detector efficiency, and divide it by the 3s intensity in the undiscriminated spectrum.
+Briefly, we correct the intensity of the Ar 3s photoline in the coincident spectra by the detector efficiency, and divide it by the total (coincident and non-coincident) Ar 3s intensity.
 The result gives the branching ratio of decay via ICD/ETMD vs. the sum of all channels, including those not involving electron emission.
+(If all Ar 3s vacancies decay by emission of another electron, the coincident and non-coincident count rate differ only by the probability for the spectrometer to actually detect the secondary electron.
+This figure has been determined as 0.6 for this data set, in the same way as discussed earlier.\cite{mucke_review})
 To arrive at quantitative results, we have performed least squares fits of the non-coincident and coincident $e_1$ spectra.
 The fits assumed one or two Gaussian peaks, resp., atop of a background modelled by two more Gaussian curves with very large widths.
-The peak pertaining to the Ar 3s cluster photoline, with the background added, is shown by the blue and red solid line in Figure \ref{figure:ival}.
-Moreover, the line labelled `c.fit/det.' shows the fit to the coincident events, corrected by the detection efficiency. 
-This virtually agrees with the fit to the total spectrum in Figure \ref{figure:ival}a, but not in \ref{figure:ival}b.
-The corresponding figure for the ICD/ETMD efficiency is at one for \ref{figure:ival}a, and significantly smaller than one for \ref{figure:ival}b.
-Figure \ref{figure:eff} shows the results of this analysis.
-The error in the quantity shown is mainly determined by uncertainties in the peak/background separation.
-(Our choice for the background shape is shown in Figure \ref{figure:ival}.)
-For the gas mixture with a Xe$_{\rm in}$ of 1.2\,\%, we therefore show results from fits using two different models.
-Statistical errors are much smaller.
+The peak pertaining to the Ar 3s cluster photoline, with the background added, is shown by the black solid trace in Figure \ref{figure:ival}a and red solid trace in Figure \ref{figure:ival}b.
+Moreover, the line labelled `c.fit/det.' shows the fit to the coincident events, corrected by the detection efficiency, and plotted atop of the non-coincident intensity. 
+This virtually agrees with the fit to the total spectrum in Figure \ref{figure:ival}a, but not in \ref{figure:ival}c. 
+The corresponding figure for the ICD/ETMD efficiency comes out as one for \ref{figure:ival}a, and significantly smaller than one for \ref{figure:ival}c.
+Figure \ref{figure:eff} shows all results of this analysis.
+The error in the autoionization efficiency shown is mainly determined by uncertainties in the peak/background separation.
+%(Our choice for the background shape is shown in Figure \ref{figure:ival}.)
+For the gas mixture with a Xe$_{\rm in}$ of 1.2\,\%, we therefore show results from fits using two different choices of the background shape in Figure \ref{figure:eff}.
+Statistical errors are much smaller than the differences between the pairs of values arrived at such.
 
-Within the accuracy of our experiment we found an Ar 3s autoionization efficiency which is smaller than unity for all spectra with Xe$_{\rm in}$ of 1.2\,\%, and decreases with cluster size. 
-For larger Xe$_{\rm in}$, the values are compatible with unity.
+We found an Ar 3s autoionization efficiency which, for clusters with the lowest Xe content (Xe$_{\rm cl}$ approx.
+10-12\,\%), is smaller than unity, and further decreases with decreasing cluster size.
+For larger Xe$_{\rm cl}$, the values are compatible with unity, within the accuracy of our experiment.

### 2016-06-27 structures.tex

@@
 However, for small rare gas clusters consisting of less than approximately \unit[1000]{atoms} so-called \emph{islands of stability} were found.\cite{haberland}  
-In mass spectra, clusters with mass numbers corresponding to icosahedral shapes had a (slightly) enhanced abundance over other sizes. 
-We therefore started from icosahedral structures and produced mixed cluster structures by substitution of individual atoms with one or the other kind (Ar or Xe), or added individual atoms to a given structure close to the desired position.
+In mass spectra, clusters with mass numbers corresponding to icosahedral shapes had an abundance that was (slightly) enhanced over other sizes. 
+We therefore started from icosahedral structures and constructed mixed cluster structures by substitution of individual atoms with one or the other kind (Ar or Xe), or added individual atoms close to the desired position within a given structure.
 After that, the cluster structures were optimized using the unified force
@@
  \item add one xenon atom on top of a surface / edge / vertex of
-       the argon core, as for example shown in
-       Figure \ref{figure:cluster_3_overview} a)
-       for one additional xenon atom
-       on top of surface of a \unit[55]{atoms} argon core
+       the argon core, with an example shown in
+       Figure \ref{figure:cluster_3_overview}a
+       (one additional xenon atom
+       on top of a surface of a \unit[55]{atom} argon core)
        (Table \ref{table:theo_gammas}, \#6--8, \#12--14),
@@
        atoms either grouping them or distributing them througout the cluster
-       (see Figure \ref{figure:cluster_3_overview} b) and c)) in order to
+       (see Figure \ref{figure:cluster_3_overview}b and c) in order to
        achieve a xenon content in the cluster close to the measured one

### 2016-06-27 theo_results.tex
have table where it is supposed to be

@@
 %
-\begin{table}[h]
+\begin{table}[H]
 \small
@@
 The cluster structures are classified into core-shell structures (cs),
-structures with seggregated xenon atoms (in) and completely mixed
+structures with segregated xenon atoms (in) and completely mixed
 structures.
@@
           Larger Ar-Xe distances, as found in the larger cluster,
-          correspond to features at higher kinetic energy of
+          correspond to features at a higher kinetic energy of
           the ICD electron (top panel).}
@@
 We will now discuss features of several structures, using selected examples.
-First we consider clusters having an argon core of 13 and 55 atoms with a single xenon
+First we consider clusters having an argon core of 13 and 55 atoms plus a single xenon
 atom on one of the surfaces (see Figure \ref{figure:cluster_3_overview}a
-for the 55 atoms core).
+for the structure of clusters with the 55 atoms core).
 Secondary electron spectra simulated for these systems are shown in Figure \ref{figure:surf}, top panel.
@@
 
-Because the structures have only one xenon atom, an ETMD(3) is not possible
-and only ICD is to be expected. 
+Because the structures contain only one xenon atom, ETMD(3) is not possible, only ICD is expected. 
 %Both spectra show several smaller peaks which
@@
 in the bottom panel of Figure \ref{figure:surf}. 
-Every different atom pair distance
-yields in a different energy of the secondary electron and only pairs
+Every different value of the atom pair distance
+results in a different energy of the secondary electron and only pairs
 with a distance of larger than the channel opening distance
-(dashed, gray line) will contribute
+(dashed gray line) will contribute
 to the spectrum. 
-%In our model, there is a one-to-one correspondence between interatomic distance $d$ and kinetic energy of the ICD electron.
+In our model, there is a one-to-one correspondence between interatomic distance $d$ and kinetic energy of the ICD electron.
 The larger the interatomic distance, the higher is the
 kinetic energy of the secondary electron for a given channel.
-Since the cluster with an Ar core of 55 atoms is larger, and therefore
-contains Ar-Xe pairs with larger distances, its spectrum extends to
-higher energies.
+%Since the cluster with an Ar core of 55 atoms is larger, and therefore
+%contains Ar-Xe pairs with larger distances, its spectrum 
+Therefore, the spectrum of the cluster with a 55 atoms core extends to higher energies.
 %energies as well.
@@
 As an example, we discuss clusters with a core of 13 argon atoms and two xenon atoms on different surfaces. 
-Their xenon content is \unit[13.3]{\%} and thus close to the experimental one of \unit[10-12]{\%} for the lowes xenon admixture.
+Their xenon content is \unit[13.3]{\%} and thus close to the experimental one of \unit[10-12]{\%} for the lowest xenon admixture.
 The cluster structures were illustrated in Figure \ref{figure:cluster_2_overview}, simulated spectra are shown in Figure \ref{figure:2tops}.
@@
 We also note that the percentage of decay via ICD is practically
-independent of the Xe content for large clusters with a core-shell structure.
+independent of the Xe content for large clusters with a Xe core, Ar shell structure.
 This can be expected, as both decay processes are most pronounced for the
@@
 The ETMD(3), depending on the electron transfer from one xenon atom to the
-initially ionized argon atom and hence the corresponding orbital overlap,
-is a pure interface effect involving the argon atoms with direct xenon
-neighbours and the two xenon layers closest to the argon shell.
+initially ionized argon atom, and hence on the corresponding orbital overlap,
+is purely an interface effect that involves the argon atoms with direct xenon
+neighbours, and the two xenon layers closest to the argon shell.
 The ICD has a stronger long range character, due to which the description
@@
 different sizes. This manifests itself in the distribution of relevant
-Ar-Xe pair distances (compare Fig. \ref{figure:surf} lower panel).
+Ar-Xe pair distances (compare Figure \ref{figure:surf}, lower panel).
 As a consequence, the ICD spectra of two large clusters of different size
-do hardly differ.
+hardly differ.
+
+\clearpage

### 2016-06-27 theory.tex
add changes from Melanie

@@
  \centering
- \includegraphics[width=8.5cm]{pics/channel_open_ICD.pdf}
- \caption{Initial (black trace) and final state energies (blue traces) 
+ \includegraphics[width=\columnwidth]{pics/channel_open_ICD.pdf}
+ \caption{Illustration of channel opening: Initial (Ar3s$^{-1}$)
+          and final state (Ar3p$^{-1}$Xe5p$_{3/2}^{-1}$ and
+          Ar3p$^{-1}$Xe5p$_{1/2}^{-1}$) energies
           for ICD in ArXe pairs as a function of 
-          internuclear distance, using the experimental ionization potentials given
-          below in Table \ref{tab:valence}. For distances larger than the channel opening
-          distance the ICD channel is open.}
+          internuclear distance, using eq. (\ref{equation:E_fin})
+          and the experimental ionization
+          potentials given
+          in Table \ref{tab:valence}. When the final state energy is lower
+          than the initial state energy than the corresponding channel
+          is open. The distance at which the energies cross is called the
+          channel opening distance. If the curves do not cross, the
+          corresponding channel is closed.}
  \label{figure:channel_open_ICD}
@@
 process is energetically not accessible. Hence, the corresponding channel     
-is closed, as shown in Figure \ref{figure:channel_open_ICD}. Related to
+is closed, as shown in Figure \ref{figure:channel_open_ICD} in the
+Ar3p$^{-1}$Xe5p$_{1/2}^{-1}$ curve in the displayed distance range. Related to
 the opening of each channel is an internuclear distance which we will call 

### 2016-06-27 theory.tex
improvements in wording

@@
           in Table \ref{tab:valence}. When the final state energy is lower
-          than the initial state energy than the corresponding channel
-          is open. The distance at which the energies cross is called the
-          channel opening distance. If the curves do not cross, the
+          than the initial state energy the corresponding channel
+          is open. We call the distance at which the energies are equal
+          the `channel opening distance'. If the curves do not cross, the
           corresponding channel is closed.}
@@
 process is energetically not accessible. Hence, the corresponding channel     
-is closed, as shown in Figure \ref{figure:channel_open_ICD} in the
-Ar3p$^{-1}$Xe5p$_{1/2}^{-1}$ curve in the displayed distance range. Related to
+is closed, as shown in Figure \ref{figure:channel_open_ICD} for the
+Ar3p$^{-1}$Xe5p$_{1/2}^{-1}$ final state. Related to
 the opening of each channel is an internuclear distance which we will call 

### 2016-07-04 letters/cover.tex
add the folder which was submitted
unfortunately, the journal requires it like this

\documentclass[DIN,10pt,pagenumber=false,parskip=half,fromalign=left,fromphone=false,fromemail=true,fromurl=false,fromlogo=true,fromrule=false]{scrlttr2}
\usepackage[utf8]{inputenc}
\usepackage{ngerman}
\usepackage{units}
\usepackage{tabularx}
\usepackage[right]{eurosym}
\usepackage{graphicx}
\usepackage[top=2cm,bottom=0cm,left=2cm,right=2cm]{geometry}
%\RequirePackage{graphicx}

\setkomavar{fromname}{Dr. Elke Faßhauer}
\setkomavar{fromaddress}{CTCC\\ University of Tromsø{}
                         --- The Arctic University of Norway
                         \\ 9037 Tromsø \\ Norway}
%\setkomavar{fromphone}{06221/545220}
\setkomavar{fromemail}{elke.fasshauer@uit.no}
\setkomavar{subject}{Manuscript Submission for Journal of Physical Chemistry C}
\setkomavar{signature}{Elke Faßhauer}
\setkomavar{fromlogo}{\includegraphics[width=3cm]{uit.pdf}}

\begin{document}

\begin{letter}{Journal of Physical Chemistry\\Editorial Board}
\textheight200mm
\opening{Dear Editor,}

I hereby submit our manuscript entitled
\emph{Long-range Interatomic Coulombic Decay in ArXe clusters: Experiment and
Theory} written by M. Förstel, M. Mucke, T. Arion, T. Lischke, M. Pernpointner,
Uwe Hergenhahn and E. Fasshauer for consideration of publication in
the Journal of Physical Chemistry C on behalf of all authors.

In this joint theoretical and experimental work we study two competitive
electronic decay processes in clusters for which we have chosen ArXe clusters
as a model system. We find that the Electron Transfer Mediated Decay (ETMD(3)),
which is a pure interface effect,
is dominated by the long-range Interatomic Coulombic Decay (ICD)
decay mechanism. Due to these results we
are able to draw the conclusion, that the cluster structure provides a clear
interface between argon and xenon atoms instead of mixed cluster structures.

\closing{Yours sincerely,}
\end{letter}

\end{document}

### 2016-07-04 onefolder/experimental.tex
add the folder which was submitted
unfortunately, the journal requires it like this

--- 2016-06-05 experimental.tex
@@
 We basically have an Ar seeded expansion of Xe gas, as the freezing point of Ar is much lower. 
-$\langle N_{\rm Ar} \rangle$ and $\langle N_{\rm Xe} \rangle$ refer to cluster sizes for a pure Ar, or pure Xe expansion, resp., at the given conditions, calculated from a scaling law.\protect\cite{hagena1981}
+$\langle N_{\rm Ar} \rangle$ and $\langle N_{\rm Xe} \rangle$ refer to cluster sizes for a pure Ar, or pure Xe expansion, respectively, at the given conditions, calculated from a scaling law.\protect\cite{hagena1981}
 We expect actual cluster sizes in-between these two limiting values. 
@@
 Ar & (2) & --- &  96.5  & 0.67  & 200  &  --- \\
+\midrule
 % 1103 676, 679
@@
 ArXe & `L' & 1.2 &  174   & 0.68  & 23  &  431 \\
+\midrule
 % 1103 663
 ArXe & `S' & 3.0 &  172   & 0.28  & 3  &   57 \\
-% 1103 640
-ArXe & `M' & 5.0 &  171   & 0.51  & 13  &  240 \\
-% 0506 382, Keller offset ber?cksichtigt
-Xe &  & 100 & 183.5  & 0.68  & ---  &  615 \\     
-\midrule
 % 1103 653
@@
 ArXe & `L' & 3.0 &  172   & 0.68  & 24  &  458 \\
+\midrule
 % 1103 630
 ArXe & `S'  & 5.0 &  167  & 0.37  & 7  &  129 \\
+% 1103 640
+ArXe & `M' & 5.0 &  171   & 0.51  & 13  &  240 \\
 % 1103 629
@@
 ArXe & `XL' & 2.5 &  154  & 2.12  & 995 & 18800\\
+\midrule
+% 0506 382, Keller offset ber?cksichtigt
+Xe &  & 100 & 183.5  & 0.68  & ---  &  615 \\     
 % 1004 868
@@
 % Leave this citation in place to avoid Latex error
-A comprehensive description can be found in Ref. \citenum{arion}, and here we focus on details specific for the current experiment. Commercial Ar and Xe gas was used. 
-Separate containers for the two gases were filled up to pressures suitable for producing a certain mixing ratio. The gases were then allowed to mix before the expansion. 
+A comprehensive description can be found in ref \citenum{arion}, and here we focus on details specific for the current experiment. 
+Commercialy obtained Ar and Xe gas was filled into 
+separate cylinders up to pressures suitable for producing a certain mixing ratio. The gases were then allowed to mix before the expansion. 
 Expansion parameters are given in Table \ref{tab:cluster}. 
-Similar expansion conditions are further referred by labels `S'-`XL', as given shown in the Table.grep
+Similar expansion conditions are further referred by the labels `S'-`XL', as given in the Table.
 
@@
 The storage ring was operated in single bunch conditions.
-Spectra of pure Ar clusters shown for comparison are from Ref.\ \citenum{foerstel_arg2_2011}, and a spectrum of pure Xe clusters was recorded with the set-up described in Ref.\ \citenum{hergenhahnprb}.
+Spectra of pure Ar clusters shown for comparison are from ref \citenum{foerstel_arg2_2011}, and a spectrum of pure Xe clusters was recorded with the set-up described in ref \citenum{hergenhahnprb}.
 
@@
 For the data shown here, slightly positive bias voltages were used (+1.8 V to +2.2 V) in order to have all electrons arriving at the detector within one BESSY single bunch period (800 ns). 
-The detection efficiency was determined as 0.6, with the method outlined in Ref.\ \citenum{mucke_review}.
+The detection efficiency was determined as 0.6, with the method outlined in ref \citenum{mucke_review}.
 Data were converted from flight times to kinetic energy by measuring calibration data for atomic photolines of known binding energy.

### 2016-07-04 onefolder/intro.tex
add the folder which was submitted
unfortunately, the journal requires it like this

--- 2016-06-26 intro.tex
@@
 adsorbate by ICD.\cite{grieves} More detailed work on Ne-Ar 
-clusters was recently presented by some of the authors.\cite{
-fasshauer2014} For this system, a detailed account of the
-photoelectron spectra with respect to structural features of the 
-mixed clusters is also available.\cite{lundwall} In ref \citenum{
-fasshauer2014} it was shown that an analysis of the ICD spectra 
+clusters was recently presented by some of the authors \cite{fasshauer2014}
+showing that an analysis of the ICD spectra
 allowed to decide between structural alternatives, for which the
 photoelectron data were indiscriminate.
+For this system, a detailed account of the
+photoelectron spectra with respect to structural features of the 
+mixed clusters is also available.\cite{lundwall}
 

### 2016-07-04 onefolder/master.tex
add the folder which was submitted
unfortunately, the journal requires it like this

	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% This is a (brief) model paper using the achemso class
%% The document class accepts keyval options, which should include
%% the target journal and optionally the manuscript type.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\documentclass[journal=jpccck,manuscript=article,layout=twocolumn]{achemso}
\documentclass[journal=jpccck,manuscript=article]{achemso}

% UHe stuff
\def\EB{E_{\rm b}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later. Do NOT use any
%% packages which require e-TeX (for example etoolbox): the e-TeX
%% extensions are not currently available on the ACS conversion
%% servers.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{braket}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{dsfont}
\usepackage{booktabs}
\usepackage{units}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{tikz,pgfplots}
\usepackage{float} %force figure position

\usetikzlibrary{patterns,shadows,trees,calc}
\usepgfplotslibrary{units}

\pgfplotsset{compat=1.10}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional macros here. Please use \newcommand* where
%% possible, and avoid layout-changing macros (which are not used
%% when typesetting).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newcommand*\mycommand[1]{\texttt{\emph{#1}}}
% Define some colours
\definecolor{diplom1}{rgb}{0.0 0.4 1.0}
\definecolor{diplom2}{rgb}{0.0 0.0 0.6}
\definecolor{diplom3}{RGB}{153,0,0} %unirot

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Marko F\"orstel}
\altaffiliation{Now at: Institut für Optik und Atomare Physik, Technische Universit\"at Berlin, Hardenbergstr. 36, 10623 Berlin, Germany}
\author{Melanie Mucke}
\altaffiliation{Now at: Department of Physics and Astronomy, Uppsala University, Box 516, 75120 Uppsala, Sweden}
\author{Tiberiu Arion}
\altaffiliation{Now at: Center for Free-Electron Laser Science/DESY, Notkestr. 85, D-22607 Hamburg, Germany}
\author{Toralf Lischke}
\affiliation[IPP]{Max-Planck-Institute for Plasma Physics, Boltzmannstr. 2, D-85748 Garching, Germany}
\author{Markus Pernpointner}
\affiliation[University of Heidelberg]{Theoretical Chemistry, University of Heidelberg,
              Im Neuenheimer Feld 229, D-69120 Heidelberg, Germany}
\author{Uwe Hergenhahn}
\affiliation[IOM]{Leibniz Institute of Surface Modification, Permoserstr. 15, D-04318 Leipzig, Germany}
\alsoaffiliation[IPP HGW]{Max-Planck-Institute for Plasma Physics, Wendelsteinstr. 1, D-14791 Greifswald, Germany}
\email{uwe.hergenhahn@iom-leipzig.de}
\author{Elke Fasshauer}
\affiliation[UIT]{Centre for Theoretical and Computational Chemistry,
Department of Chemistry, University of Troms\o
-- The Arctic University of Norway, N-9037 Troms\o, Norway}
\email{elke.fasshauer@uit.no}
%\phone{+123 (0)123 4445556}
%\fax{+123 (0)123 4445557}
%\alsoaffiliation[Second University]
%{Department of Chemistry, Second University, Nearby Town}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Long-range Interatomic Coulombic Decay in ArXe clusters: Experiment and Theory}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\abbreviations{IR,NMR,UV}
%\keywords{American Chemical Society, \LaTeX}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The manuscript does not need to include \maketitle, which is
%% executed automatically.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "tocentry" environment can be used to create an entry for the
%% graphical table of contents. It is given here as some journals
%% require that it is printed as part of the abstract page. It will
%% be automatically moved as appropriate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tocentry}

\begin{center}
 \includegraphics[height=3.5cm]{front1.pdf}
\end{center}

%Some journals require a graphical entry for the Table of Contents.
%This should be laid out ``print ready'' so that the sizing of the
%text is correct.
%
%Inside the \texttt{tocentry} environment, the font used is Helvetica
%8\,pt, as required by \emph{Journal of the American Chemical
%Society}.
%
%The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
%permitted for  \emph{Journal of the American Chemical Society}
%graphical table of content entries. The box will not resize if the
%content is too big: instead it will overflow the edge of the box.
%
%This box and the associated title will always be printed on a
%separate page at the end of the document.

\end{tocentry}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{abstract}

\begin{abstract}
We report about autoionization channels of Ar inner valence ionized states in mixed ArXe clusters and compare
our experimental data obtained by electron-electron coincidence spectroscopy
to our theoretical simulations for representative cluster structures.
The combined experimental and theoretical data show that the autoionization of Ar 3s$^{-1}$ in ArXe is dominated by Interatomic Coulombic Decay (ICD) to Xe atoms in the second and higher coordination shells of the originally excited atom.
Clusters with a range of sizes, compositions and structures were probed. 
The Xe content in the clusters was varied between 10\,\% and 53\,\%. 
Besides ICD, also Electron Transfer Mediated Decay (ETMD(3)) was found important in many of the calculated spectra, but is seen with less intensity in the experimental spectra. 
From the calculations, we identify structural motifs which minimize the ETMD vs. the ICD rate and suggest that these are preferentially realized in our experiment, in which clusters are formed by supersonic expansion of an Ar-Xe mixture.
Suggested cluster structures either feature a clear segregation between Ar and Xe fractions, e.g. Xe core, Ar shell systems, or contain a few Xe atoms singled out in surface sites on an Ar cluster.
These structures differ significantly from the majority of calculated minimum energy structures for ArXe systems of 38 atoms, which might show that the latter, annealed structures are not realized in our experiment.
We show experimentally that the relaxation of Ar inner valence states by ICD and ETMD together has an efficiency of unity, within the experimental accuracy, for all clusters except those with the lowest Xe content.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{intro}
\section{Introduction}
%
Electron spectroscopy can make important contributions to the 
research on composition and structure of free nanoparticles.\cite{
jpcc} Besides photoionization, free electrons emerging from 
nanoparticles can also be produced by the relaxation of 
electronically excited states. One such process, which is of 
particular relevance in weakly bonded systems, is the 
Interatomic or Intermolecular Coulombic Decay (ICD).\cite{
cederbaum} In ICD, an electronic excitation decays by energy 
transfer to one of its neighboring atoms or molecules, thus 
releasing a free electron from the latter site. ICD is an 
important relaxation channel e.g. for inner-valence holes in 
atoms, and also for core level vacancies e.g. in \ce{H2O}
, where it competes with Auger decay.\cite{slavicek}

By definition, ICD is particularly sensitive to the chemical 
environment of the atom or molecule in which the primary 
excitation has taken place. We suggest that this property of ICD 
decay spectra can be used to derive information on a nanoparticle 
or a solvation system. 
The term excitation is used here in a broader sense---in the
systems we consider in this work, ICD occurs from an excited, singly 
charged Ar state created by photoionization.
In other systems, ICD was also observed from neutral excited
states and states with more than one vacancy.

We report here about studies 
in which we produced heterogeneous clusters of the noble gases Ar 
and Xe with different sizes, and compositions ranging from a few 
Xe dopant atoms in an Ar matrix to clusters containing an equal 
amount of both species. By the use of electron-electron 
coincidence spectroscopy and of theoretical simulations on 
prototypical systems we show how the radiationless decay spectrum 
of Ar inner valence (3s) ionized states connects to the structure 
of the clusters.

Intermolecular Coulombic Decay initially was predicted from 
theoretical considerations of the energy levels in singly vs.\  
doubly ionized, and doubly vs.\ triply ionized, hydrogen bonded 
clusters.\cite{cederbaum} First experimental work some years 
later used Ne clusters,\cite{marburger,jahnkenedimer} but quickly 
was followed by demonstrations of ICD in a diverse range of other 
systems. Experimental and theoretical progress has been reviewed.
\cite{hergenhahn_review, averbukh_review, jahnke_review} ICD 
proceeds by an initial ionization producing an ion in an excited 
state, followed by a transfer of energy to a neighbouring site, 
and an electron emission process therefrom. The final state contains 
two positive charges; one at the original site of ionization, and a second
one at another atom or molecule.

Soon after, related 
autoionization processes were discovered that proceed via a 
charge transfer instead of an energy transfer. 
These were termed `Electron Transfer Mediated Decay' 
 (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
 which the originally excited site is neutralized by the decay 
and `exchange ICD' for charge transfer contributions to the 
normal ICD amplitude.\cite{santrarev,jahnkesat}
We find that both energy and charge transfer induced 
autoionization play a role in Ar-Xe, and will detail the 
relevant processes below. The notion of ICD requires that the 
electronic orbitals of the two sites can be distinguished, which 
typically is the case in weakly bonded systems, held together by 
hydrogen bonds or van-der-Waals bonds. In the case of strong
(covalent or metallic) bonding, it is impossible to make a
distinction between ICD and Auger decay.\cite{hergenhahn_review}

Rare gas clusters are suitable prototype systems for studies of
ICD, as they can readily be produced by supersonic 
expansion through a cooled nozzle. 
The size of the clusters can be changed by varying the expansion parameters.
The formation of heterogeneous rare gas clusters by coexpansion of a gas mixture cannot {\it a priori} be taken for granted, but was experimentally shown for most combinations of two rare gases, when suitable mixing ratios and expansion parameters are used (see references throughout this article).

First experiments on ICD in heterogeneous systems used Ne-Ar 
clusters.\cite{barthnear} Those were followed by studies of 
ICD-like inner-shell decays in aqueous solution.\cite{aziz,pokapanich,pokapanich2011}
Pioneering work also showed the 
potential for studies of the interface between a substrate and an 
adsorbate by ICD.\cite{grieves} More detailed work on Ne-Ar 
clusters was recently presented by some of the authors \cite{fasshauer2014}
showing that an analysis of the ICD spectra
allowed to decide between structural alternatives, for which the
photoelectron data were indiscriminate.
For this system, a detailed account of the
photoelectron spectra with respect to structural features of the 
mixed clusters is also available.\cite{lundwall}

Several experimental techniques have been used for the study of mixed Ar-Xe clusters, most notably fluorescence spectroscopy, electron diffraction and photoelectron spectroscopy. 
Early work focussed on the fluorescence of a single Xe atom 
embedded in an Ar cluster.\cite{lengenprl}
%Different sites of the dopant atom (on top of a surface, 
%integrated in an Ar surface, inside the cluster) were 
%distinguished by three separate bands in the fluorescence yield 
%recorded as a function of excitation wavelength.\cite{goldberg} 
Increasing the Xe concentration in the expansion lead to the formation of \ce{Xe2} and larger Xe complexes inside the clusters.\cite{lengen} 
With increasing Xe content, the formation of Xe-core, Ar-shell systems with a sharp interface between the two species was shown in photoionization experiments.\cite{tchaplyguine,hoener}
This finding was confirmed by electron diffraction.\cite{Danylchenko,Danylchenko07} 
Always, the observed Xe content in the clusters is higher than the Xe content in the expanding gas mixture, as Xe can be condensed much easier than Ar.\cite{hoener,Danylchenko07}
%A complementary study used photoelectron-photoion coincidence of
%large Ar-Xe clusters, and found that after inner shell (Xe 4d, Ar 2p)
%photoionization significant charge transfer between both species
%occurs before the mass spectroscopic final state is reached.\cite{berrah}
%
More recently, photoelectron spectra of 
small Ar-Xe clusters were analyzed, adding to the findings in 
earlier work.\cite{lindblad} We will discuss this paper in 
connection with our results below. 
For completeness, we mention that Ar-Xe complexes can also be produced by passing clusters from a neat Ar expansion through a zone filled with Xe gas (`pick-up').\cite{pietrowski}
Clusters produced such can structurally be quite different from those produced by coexpansion.\cite{lindbladpccp}

A number of theoretical works on Ar-Xe clusters aimed at the prediction of minimum energy structures. 
Most recently, these converged to structures which have the Xe atoms mainly in the interior.\cite{marques} 
Xe was also found to diffuse into the interior of Ar clusters in molecular dynamics simulations after pick-up.\cite{Vach_1999} 
The electronic energy levels of very small Ar-Xe clusters were calculated in ref \citenum{fasshauer} and the secondary electron spectra were simulated for
model structures of one argon atom placed on a xenon surface \cite{Fasshauer13}.
Interestingly, it was found that Ar 3s$^{-1}$ is stable 
against autoionization in an ArXe dimer, but is destabilized by 
adding further Xe atoms, or an Ar solvation shell, to the system, thereby allowing
for combinations of argon and xenon atoms with larger interatomic distances. 
Again, we will detail these results in conjunction with our 
current work.

The plan of our paper is as follows: We firstly delineate our experimental and theoretical methods. 
Calculations were done for a number of model structures which were systematically varied, and are described in the following section.
After that, we describe and discuss our theoretical results for the autoionization spectra of the model clusters.
Experimental results are then shown and possible conclusions from comparing them to the calculations are given.
Details on the experimental technique, and calculated spectra for a wider range of structures are given as Supporting Information.

%\input{experimental}

\section{Experimental}
%
\begin{table*}
\caption{
The expansion parameters used for cluster production. 
Here, Xe$_{\rm in}$ is the molar fraction of Xe in the gas mixture before the expansion, $T$ is the nozzle temperature, and $p$ the stagnation pressure. 
Experiments were performed with $d = 80~\mu$m (first two sections) and $d = 100~\mu$m (bottom section) conical nozzles of 15$^\circ$ half opening angle. 
We basically have an Ar seeded expansion of Xe gas, as the freezing point of Ar is much lower. 
$\langle N_{\rm Ar} \rangle$ and $\langle N_{\rm Xe} \rangle$ refer to cluster sizes for a pure Ar, or pure Xe expansion, respectively, at the given conditions, calculated from a scaling law.\protect\cite{hagena1981}
We expect actual cluster sizes in-between these two limiting values. 
Inaccuracies in the calculation of $\langle N\rangle$ due to fluctuations of the input parameters are less than 6\,\%. This figure does not include systematic errors of the empirical model.
}
\label{tab:cluster}

\begin{tabular}{l c c c c r r}
%
\toprule
  \multicolumn{2}{r}{size label}  &  Xe$_{\rm in}$ (\%)  &  $T$ (K)  &  $p$ (bar) & $\langle N_{\rm Ar} \rangle$ & $\langle N_{\rm Xe} \rangle$ \\
%
\midrule
% Ar, from Marko 
Ar & (1) & --- &  96.5  & 0.35  & 44  &  --- \\
% Ar, from Marko 
Ar & (2) & --- &  96.5  & 0.67  & 200  &  --- \\
\midrule
% 1103 676, 679
ArXe & `S' & 1.2 &  174   & 0.32  & 4  &   74 \\
% 1103 670
ArXe & `M' & 1.2 &  174   & 0.49  & 11  &  199 \\
% 1103 671
ArXe & `L' & 1.2 &  174   & 0.68  & 23  &  431 \\
\midrule
% 1103 663
ArXe & `S' & 3.0 &  172   & 0.28  & 3  &   57 \\
% 1103 653
ArXe & `M' & 3.0 &  172   & 0.51  & 12  &  233 \\
% 1103 658
ArXe & `L' & 3.0 &  172   & 0.68  & 24  &  458 \\
\midrule
% 1103 630
ArXe & `S'  & 5.0 &  167  & 0.37  & 7  &  129 \\
% 1103 640
ArXe & `M' & 5.0 &  171   & 0.51  & 13  &  240 \\
% 1103 629
ArXe & `L'  & 5.0 &  167  & 0.68  & 28  &  537 \\
\midrule
% 1004 867 (32 eV)
ArXe & `XL' & 2.5 &  154  & 2.12  & 995 & 18800\\
\midrule
% 0506 382, Keller offset ber?cksichtigt
Xe &  & 100 & 183.5  & 0.68  & ---  &  615 \\     
% 1004 868
%868 & & 2.5 &  158   & 1.50  &  355 &  6090\\
% 1004 886 (17 eV)
%886 &  & 2.5 &  161   & 2.41  &  980 & 16770\\
% 1004 858
%858 &  & 5.0 &  149   & 2.50  & 1620 & 27700\\
%
\bottomrule
\end{tabular}
\end{table*}
%
%
The apparatus used for the experiments consists of a supersonic molecular jet with a cooled nozzle, and a magnetic bottle spectrometer, which detects photoelectrons and secondary electrons produced after ionization with synchrotron radiation.\cite{arion} 
% Leave this citation in place to avoid Latex error
A comprehensive description can be found in ref \citenum{arion}, and here we focus on details specific for the current experiment. 
Commercialy obtained Ar and Xe gas was filled into 
separate cylinders up to pressures suitable for producing a certain mixing ratio. The gases were then allowed to mix before the expansion. 
Expansion parameters are given in Table \ref{tab:cluster}. 
Similar expansion conditions are further referred by the labels `S'-`XL', as given in the Table.

Prediction of the sizes of clusters from a supersonic expansion mainly rests on empirical scaling laws,\cite{hagena1981} which have been the subject of some discussion.
Moreover, such scaling laws originally were derived only for pure gas expansions.
A recent investigation of cluster sizes in a mixed Ar-Kr expansion yielded a revised scaling law, which essentially amounts to the use of a weighted average over the atom-specific parameters of the two gases.\cite{danylchenko2015} 
Although the analogy to our case is not complete, as phase segregation occurs in Ar-Kr to a much lesser extent,\cite{Vach_1999,lundwall_arkr} we expect scaling law cluster sizes between the values calculated for Ar and Xe.
Recent analyses of photoionization spectra suggest that mean sizes arrived at by scaling laws are smaller than the actual size, at least for rare gas clusters in the range $\langle N\rangle < 1000$.\cite{bergersen,hergenhahnprb,foerstel_arg2_2011}
For the expansion conditions labelled `S'-`L', we therefore expect that the scaling law estimates are a lower boundary for the actual cluster size.

The expansion chamber for the supersonic jet is separated from the interaction chamber by a non-magnetic, conical skimmer with an opening of 1~mm in diameter (Beam Dynamics). 
At few cm distance behind the skimmer, the cluster jet was crossed by synchrotron radiation from the BESSY electron storage ring at Helmholtz-Zentrum Berlin. 
Electrons were detected by a short `magnetic bottle' time-of-flight spectrometer, that has been described earlier.\cite{mucke_review}
Due to its large collection angle, this instrument is particularly suited for experiments that employ electron-electron coincidence detection.
Data were recorded in two different beamtimes at the UE112-PGM-1 (small and medium sized clusters, first two sections in Table \ref{tab:cluster}) and at the TGM-4 beamline (large clusters, last section in Table \ref{tab:cluster}). 
Linearly, horizontally polarized radiation was used. 
The storage ring was operated in single bunch conditions.
Spectra of pure Ar clusters shown for comparison are from ref \citenum{foerstel_arg2_2011}, and a spectrum of pure Xe clusters was recorded with the set-up described in ref \citenum{hergenhahnprb}.

The entrance aperture and drift tube of the magnetical bottle spectrometer can be independently biased to influence the electron flight times. 
For the data shown here, slightly positive bias voltages were used (+1.8 V to +2.2 V) in order to have all electrons arriving at the detector within one BESSY single bunch period (800 ns). 
The detection efficiency was determined as 0.6, with the method outlined in ref \citenum{mucke_review}.
Data were converted from flight times to kinetic energy by measuring calibration data for atomic photolines of known binding energy.
The systematical uncertainty of this procedure may lead to a common shift of all experimental kinetic energy data shown in this article of up to 30~meV.

The high detection efficiency of the instrument is a pre-requisite for measuring two-electron emission processes, such as photoelectron emission followed by ICD or ETMD, by using electron-electron coincidence detection. 
This allows to filter the full electron spectrum for contributions arising after emission of an Ar 3s photoelectron.
ICD/ETMD spectra presented here are based on this method, which has been explained earlier.\cite{mucke_review,Foerstel_phd}
Technical details and full electron-electron coincidence spectra are given in the Supporting Information.

%\input{theory}
\section{Theoretical Approach}
%
Experimental coincidence spectra are given by the multitude of
kinetic energies $E_{\rm sec}$ of the secondary electron
and the intensities of the peaks. The latter is proportional to the
probability of the decay as well as the theoretically determinable
decay width $\Gamma=\frac{\hbar}{\tau}$,
which is inversely proportional to the lifetime $\tau$ of the decay process.
The manifold of the
secondary energies and decay widths will therefore compose the electron-electron
coincidence spectrum.
In case of noble gas clusters
with given geometrical structures three aspects have to be taken into account:
different decay mechanisms, the possibility to decay with multiple
interaction partners and different decay channels $\beta$ within
each decay mechanism.
At the current stage of development we need to neglect the nuclear dynamics which
additionally might play an important role.

%We are interested in describing the electron emission spectra of excited states in clusters, that where measured by the electron-electron coincidence method in our experiments. 
%In our theoretical description, these will be composed of multiple transitions, each characterized by a kinetic energy $E_{\rm sec}$ of the secondary electrons, and the intensity of the peak.
%The latter is proportional to the probability of the decay, represented here by the decay width $\Gamma_\beta = \hbar/\tau_\beta$, where $\tau_\beta$ is the lifetime due to the respective transition.
%The total decay width $\Gamma$ is the sum of all partial $\Gamma_\beta$.
%In case of noble gas clusters with a given geometrical structure, three aspects have to be taken into account:
%different decay mechanisms, the contribution of different cluster sites to the respective decay, and the existence of different decay channels within each decay mechanism.
%At the current stage of development we have to neglect the nuclear dynamics, which

This means, for the evaluation of the decay width we are dealing with a sum over three different indices: 
For a given structure it is most convenient to
start with a decomposition of the system into interaction partners of
the different relevant decay mechanisms, i.e. pairs (combination of two atoms regardless
of their internuclear distance) for the ICD and triples (combinations of three atoms)
for the ETMD(3).
These atoms do not necessarily need to form bonds between each other or
even be close, but they are characterized according to fixed internal
coordinates. 
Each pair and each triple leads to a decay spectrum that can be described by the energy of the secondary electron and the decay width, which is in first order of approximation independent of other atoms present in the cluster.
In the following, this approach will be called model of pairs and triples.

%Decomposing every system into pairs and triples of atoms is a very useful
%first order approximation to both the investigation of energies and
%decay widths of a larger system. Pairs and triples are combinations of
%two and three atoms, respectively.

In order to determine, whether a channel $\beta$ for a given geometry and decay
mechanism is open, i.e., whether it is in accordance with energy conservation,
knowledge of the energies of the initial and the final states, $E_{\rm in}$ and $E_{\rm fin}$, of
the corresponding processes is necessary.
If the channel
is open, the excess energy is carried away by the emitted electron
in form of its kinetic energy $E_{\rm sec}$. These energies in the model
of pairs and triples can be approximated by

\begin{align}
 E_{\rm in}        &= SIP(X_{\rm in}) \label{equation:E_in}\\
 E_{\rm fin}^\beta &= SIP(X_{D}^\beta) + SIP(X_{E}^\beta) + \frac 1d
           \label{equation:E_fin}\\
 E_{\rm sec}^\beta &= E_{\rm in}^\beta - E_{\rm fin}^\beta \label{equation:E_sec}
\end{align}
where $X_{\rm in}$ denotes the initially ionized atom and
$X_{D}$ and $X_{E}$ describe the electron donating atom and electron
emitting atom, respectively.
$\beta$ denotes the decay channel characterized by the quantum numbers of the ionized atoms in the pairs and triples, $SIP(X^\beta)$ the single ionization potential of vacancy $\beta$ in atom $X$ and $d$ the interatomic distance between the atoms $X_{D}$ and $X_{E}$. 
Atomic units are used.
The initially ionized atom $X_{\rm in}$ can
coincide with one or both of
the final state atoms
$X_{D}$ and $X_{E}$.
The distribution of the vacancies over the different
atoms determines the kind of electronic decay process at hand. Hence, in an
Auger process all three atoms coincide, for an ICD process $X_{\rm in}$
coincides with $X_{D}$, for an ETMD(2) process $X_D$ and $X_E$ coincide
and for an ETMD(3) process
all ionized states are located on different atoms.

\begin{figure}[h]
 \centering
 \includegraphics[width=\columnwidth]{channel_open_ICD.pdf}
 \caption{Illustration of channel opening: Initial (Ar3s$^{-1}$)
          and final state (Ar3p$^{-1}$Xe5p$_{3/2}^{-1}$ and
          Ar3p$^{-1}$Xe5p$_{1/2}^{-1}$) energies
          for ICD in ArXe pairs as a function of 
          internuclear distance, using eq. (\ref{equation:E_fin})
          and the experimental ionization
          potentials given
          in Table \ref{tab:valence}. When the final state energy is lower
          than the initial state energy the corresponding channel
          is open. We call the distance at which the energies are equal
          the `channel opening distance'. If the curves do not cross, the
          corresponding channel is closed.}
 \label{figure:channel_open_ICD}
\end{figure}

The electron emitted by autoionization has the kinetic energy $E_{\rm sec}$. 
If the calculated value of $E_{\rm sec}$ is negative,
the final state energy is higher than the initial state energy and the        
process is energetically not accessible. Hence, the corresponding channel     
is closed, as shown in Figure \ref{figure:channel_open_ICD} for the
Ar3p$^{-1}$Xe5p$_{1/2}^{-1}$ final state. Related to
the opening of each channel is an internuclear distance which we will call 
\emph{channel opening distance} in the following.

This {\latin ad hoc} approach allows to easily correct for energetic shifts of ionization potentials as observed in larger clusters by adding experimentally or theoretically determined energy shifts $\Delta E(X_{I}^{\beta})$ for a given vacancy $I={\rm in},D,E$ and channel $\beta$. This yields the working expression for the kinetic energy of the secondary electron:

\begin{equation}
 E_{\rm sec}^\beta = SIP(X_{\rm in}) + \Delta E (X_{\rm in})
               - SIP(X_{D}^\beta) - \Delta E (X_{D}^\beta)
               - SIP(X_{E}^\beta) - \Delta E (X_{E}^\beta)
               - \frac 1d .
\end{equation}

The total decay width $\Gamma$ is given by the sum over the decay widths
of all decay mechanisms. In case of the ArXe clusters we only consider
ICD and ETMD(3), because the ETMD(2) pathway is energetically not accessible:

\begin{equation}
 \Gamma = \Gamma_{\rm ICD} + \Gamma_{\rm ETMD} .
\end{equation}

These are given by the sum over the decay widths of all pairs $i$ for the
ICD and all triples $j$ for the ETMD(3), respectively, and over all channels $\beta$:
%
\begin{align}
 \Gamma_{\rm ICD}  &= \sum\limits_{i,\beta} N_{{\rm ICD},i}  \, \Gamma_{{\rm ICD},i,\beta},\\
 \Gamma_{\rm ETMD} &= \sum\limits_{j,\beta} N_{{\rm ETMD},j} \, \Gamma_{{\rm ETMD},j,\beta}.
\end{align}
Here, $N_{{\rm ICD},i}$ and $N_{{\rm ETMD},j}$ denote the number of geometrically
equal pairs and triples in a given cluster structure. The total number of pairs
reads
$N_{{\rm ICD}} = N_{\rm in} \cdot N_{D/E} = N_{\rm Ar} \cdot N_{\rm Xe}
 = \sum\limits_i N_{{\rm ICD},i}$ and the number of triples is
$N_{{\rm ETMD}} = N_{\rm in} \cdot N_{D/E} (N_{D/E} - 1) = N_{\rm Ar} \cdot N_{\rm Xe} (N_{\rm Xe} - 1)
 = \sum\limits_j N_{{\rm ETMD},j}$.
The numbers of geometrically equivalent pairs $N_{{\rm ICD},i}$ and triples $N_{{\rm ETMD},j}$
strongly depend on the structure of the cluster. From these relationships
it can be seen that a higher xenon content in the cluster statistically
favours ETMD(3) over ICD.

In previous work \cite{Fasshauer13,Fasshauer_thesis} we have shown that
the decay width for a single pair or triple for a distinct channel $\beta$
following Wentzel \cite{Wentzel27}, Feshbach\cite{Feshbach58,Feshbach62}
and Fano,\cite{Fano61}
%
\begin{equation}
 \Gamma_{\beta}(E_{\rm res}) = 2\pi \left|
                           \braket{\Phi_{\rm in}| H_f |\chi_{\beta}}
                           \right|^2,
\end{equation}
%
can be approximated by its asymptotic behaviour
%
\begin{equation}
 \Gamma_{{\rm ICD},i,\beta} = (2J_{\rm in}+1)\, \frac{3c^4}{8\pi}\,
                        \sum\limits_{M_{in}'}
                        \left| \left(
                        \begin{array}{ccc}
                        J_A'  & 1        & J_A\\
                        -M_A' & M_A'-M_A & M_A
                        \end{array}\right) \right|^2
                        \frac{\sigma^{(X_E)}(\omega_{vp,\beta})}
                        {R_i^6 \, \omega_{vp,\beta}^4 \tau_{in,\beta}},
\end{equation}
%
where $J_A$, $J_A'$ and $M_A$, $M_A'$ denote the total angular momentum of the
initially ionized atom (which is the same as the electron donor atom) in the
initial and final state, respectively,
and
%
\begin{align}
 \Gamma_{{\rm ETMD},j,\beta} =& \frac{c}{\pi} \sum\limits_{m,M_{in,D'}}
                        \frac{\Theta_{m,k}(\alpha_j) \sigma^{(X_E)}(\omega_{vp,\beta})
                              \left| <\tilde{D}_{m,j,\beta}(M_{in,D'})>\right|^2}
                         {R_j^6 \omega_{vp,\beta}}\\
               =& \frac{c}{\pi R_j^6}
               \sum\limits_{M_{in,D'}}
               \left( \left| <\tilde{D}_{x,j,\beta} (M_{in,D'}) > \right|^2
                 (2+ \sin^2\alpha_j)
               + \left| <\tilde{D}_{z,j,\beta} (M_{in,D'}) > \right|^2
                 (1+\cos^2\alpha_j) \right) \nonumber \\
           & \times\, \frac{c\sigma^{(X_E)}(\omega_{vp,\beta})}{\omega_{vp,\beta}}
\end{align}
%
depending on 
experimental properties
of atoms, like the ionization cross sections
$\sigma^{(X_E)}(\omega_{vp,\beta})$, radiative lifetimes of the initially
ionized state $\tau_{in,\beta}$ and the excess energy transferred to the
emitting atom (the energy of the virtual photon) $\omega_{vp,\beta}$
and calculated dipole transition moments $\tilde{D}_{m,j,\beta}$, only.
Here, $\Theta_{m}(\alpha_j)$ is a function depending on the angle $\alpha_j$
of the triple and the direction of the dipole
transition moment $m$
(compare ref \citenum{Fasshauer13}).

In this work we evaluate the secondary energies and decay widths with
the programme HARDRoC\cite{HARDRoC,fasshauer2014} using the
experimental ionization energies of Table \ref{tab:valence}
and data from the literature given in Tables II and III.
This choice is identical to the one made in ref \citenum{Fasshauer13}.

%\input{structures}
\section{Cluster Structures}

From the experimental results we can obtain two hints for the cluster
structure: the minimum size and the xenon content. In the following we will 
use these to construct representative cluster structures, for which we will 
simulate the ICD and ETMD spectra. At this point we put in a variety of
structures, in order to learn about general structure-spectrum relations
and therefore being able to
exclude some of them by comparison of
the ICD and ETMD spectra to the experimental ones.

In our previous study\cite{Fasshauer13} the ArXe clusters were assumed
to be large, having more than 1500 atoms. The model structures assumed
an fcc structure and not an icosahedral structure, which is energetically
favoured for small clusters.
Most estimated cluster sizes given in Table \ref{tab:cluster} are much smaller.
We use the estimated number of atoms for a pure Ar expansion as the lower limit for the actual cluster size and start our search for model structures from there.
%
%Additionally,
%the expectation value for the number of xenon atoms relies on a pure
%xenon gas. Since the xenon content in the mixed gas is much lower, also
%the number of xenon atoms can be expected to be by far less. We therefore
%start from the estimated number of atoms in the cluster after expansion
%of pure argon gas.
%We therefore rethink the possible cluster structures.
%Furthermore, the theoretical prediction did not match the experimental results.
%Since the spectra are strongly depending on the cluster structure as shown in
%\cite{fasshauer2014}, the underlying structure seems not to fit and hence
%we rethink the possible cluster structures.
%
For the smaller clusters measured,
these expectation values range from \unit[3--21]{Ar atoms}. 
The cluster sizes for expansion of a mixed gas are unknown, but
for xenon as the second component a larger size is expected compared to a
pure argon expansion, due to the higher polarizability
and hence larger cohesive energy of xenon. All clusters
contributing to the coincidence spectrum
contain at least one xenon atom, as otherwise decay by ICD or ETMD is energetically not allowed.

In a gas expansion a range of clusters sizes with different structures is produced. 
However, for small rare gas clusters consisting of less than approximately \unit[1000]{atoms} so-called \emph{islands of stability} were found.\cite{haberland}  
In mass spectra, clusters with mass numbers corresponding to icosahedral shapes had an abundance that was (slightly) enhanced over other sizes. 
We therefore started from icosahedral structures and constructed mixed cluster structures by substitution of individual atoms with one or the other kind (Ar or Xe), or added individual atoms close to the desired position within a given structure. 
After that, the cluster structures were optimized using the unified force
field implemented in the 
Avogadro programme (version 1.1.0) \cite{Avogadro,Hanwell12} to give local
minimum structures.
All cluster structures are listed in Table \ref{table:theo_gammas}.
%
\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{cluster_2_overview.pdf}
 \caption{Cluster structures composed of 13 argon atoms and two additional xenon
          atoms on different surfaces of the argon icosahedron, varying in Xe-Xe distance:
          (a) closest possible, (b) middle, (c) furthest away. They refer to
          numbers 9--11 in Table \ref{table:theo_gammas}.}
 \label{figure:cluster_2_overview}
\end{figure}
%
\begin{figure}[h]
 \centering
 \includegraphics[width=8.5cm]{cluster_3_overview.pdf}
 \caption{Cluster structures derived from a 55 atom icosahedral structure:
          (a) one xenon atom on the surface, (b) six xenon atoms inside a 55 atoms cluster,
          grouped on one side, (c) six xenon atoms distributed randomly
          in a 55 atoms cluster. They refer to numbers 12, 18 and 19
          in Table \ref{table:theo_gammas}.}
 \label{figure:cluster_3_overview}
\end{figure}

As discussed in the introduction, the small clusters will likely
deviate from a core-shell structure with a xenon core surrounded
by argon shells, as observed for large clusters.\cite{tchaplyguinearxe,Vach_1999} We therefore start from
argon clusters of 13 or 55 atoms, and modify them in one of the following
ways:
%
\begin{itemize}
 \item add one xenon atom on top of a surface / edge / vertex of
       the argon core, with an example shown in
       Figure \ref{figure:cluster_3_overview}a
       (one additional xenon atom
       on top of a surface of a \unit[55]{atom} argon core)
       (Table \ref{table:theo_gammas}, \#6--8, \#12--14),
 \item substitute one argon atom in a surface / edge / vertex position
       (Table \ref{table:theo_gammas}, \#15--16),
 \item substitute one or two argon atoms in the core of the argon cluster
       by xenon atom(s) for the simulation of the core-shell structures
       (Table \ref{table:theo_gammas}, \#1--3),
 \item add two xenon atoms on top of surfaces of a 13 atoms argon core
       in different relative positions (see Figure
       \ref{figure:cluster_2_overview}),
       in order to achieve a xenon content in the cluster close to the
       measured one (see below)
       (Table \ref{table:theo_gammas}, \#9--11),
 \item substitute six argon atoms of a 55 atoms argon cluster by xenon
       atoms either grouping them or distributing them througout the cluster
       (see Figure \ref{figure:cluster_3_overview}b and c) in order to
       achieve a xenon content in the cluster close to the measured one
       (Table \ref{table:theo_gammas}, \#18--19).
\end{itemize}

These structures were then optimized using force field methods.
%
Furthermore, for comparison with the largest measured ArXe clusters, we constructed also larger core-shell structures (Table \ref{table:theo_gammas}, \#4--5).

%\input{theo_results}
\section{Theoretical Results
\label{sec:th_results}}
%
%
\begin{table}[H]
\small
\centering
\caption{Structural and calculated properties of some model clusters.
The cluster structures are characterized by the number of Ar and Xe atoms,
and are arranged in three groups according to gross structural properties. 
The first group contains Xe core-Ar shell systems of various
size and relative Xe content.
In the second group, model structures for small clusters are displayed,
in which 1-2 Xe atoms are added at systematically varied locations
to an icosahedric Ar clusters consisting of one or two full shells,
or in which 1-6 Ar atoms of such cluster were replaced by Xe atoms.
The last group contains data for calculated minimal energy structures
of mixed ArXe clusters.\protect\cite{marques}
The cluster structures are classified into core-shell structures (cs),
structures with segregated xenon atoms (in) and completely mixed
structures.
The columns `ICD' and `ETMD' are the respective partial decay widths
in \unit[$10^{-4}$]{eV}, and `\% ICD' gives the percentage of ICD in
the total decay width.
See text for details.
\label{table:theo_gammas}
}
\begin{tabular}{rrrrcccccrrr}
\toprule
\# & \# Xe & \# Ar & Xe$_{\rm cl}$\% & str. cl. & pos. & rel. pos. & ICD   &  ETMD & \% ICD & Fig.\\ %$\Gamma_{\rm ICD,ETMD}$\\
\midrule
 1 &     1 &    12 &  7.7  & cs    &         &          & 0.000 & 0.000 &  -- &\\ %    0.0            \\     ArXe\_2\_1atom      
 2 &     1 &    54 &  1.8  & cs    &         &          & 0.000 & 0.000 &  -- & \ref{figure:xe_3_in}\\ %    0.0            \\     ArXe\_3\_1atom      
 3 &     2 &    53 &  3.6  & cs    &         &          & 0.033 & 0.167 &  16.7& \ref{figure:xe_3_in}\\ %2.006$\cdot 10^{-5}$ \\ ArXe\_3\_2atom      
 4 &  1415 &   642 & 68.8  & cs    &         &          & 7.039 & 2.573 &  73.2& supp.\\ %9.612$\cdot 10^{-4}$ \\ ArXe\_8\_1layer     
 5 &   561 &  3310 & 14.5  & cs    &         &          &       &       &  85  & \ref{figure:xe_6_lay5}\\ % c6l5

\midrule
 6 &     1 &    13 &  7.1  & cs    & surface &          & 0.792 & 0.000 & 100.0& \ref{figure:surf}\\ %7.922$\cdot 10^{-5}$ \\ XeAr\_2\_surface    
 7 &     1 &    13 &  7.1  & cs    & edge    &          & 0.013 & 0.000 & 100.0&\\ %1.320$\cdot 10^{-6}$ \\ XeAr\_2\_edge       
 8 &     1 &    13 &  7.1  & cs    & vertex  &          & 0.050 & 0.000 & 100.0&\\ %5.013$\cdot 10^{-6}$ \\ XeAr\_2\_vertex     
 9 &     2 &    13 & 13.3  & cs    &         & closest  & 0.101 & 0.151 &  40.1& \ref{figure:2tops}\\ %2.523$\cdot 10^{-5}$ \\ XeAr\_2\_2top       
10 &     2 &    13 & 13.3  & cs    &         & middle   & 0.159 & 0.008 &  95.4& \ref{figure:2tops}\\ %1.665$\cdot 10^{-5}$ \\ XeAr\_2\_2midtop    
11 &     2 &    13 & 13.3  & cs    &         & furthest & 0.159 & 0.002 &  98.9& \ref{figure:2tops}\\ %1.605$\cdot 10^{-5}$ \\ XeAr\_2\_2endtop    
12 &     1 &    55 &  1.8  & cs    & surface &          & 0.064 & 0.000 & 100.0& \ref{figure:surf}\\ %6.371$\cdot 10^{-6}$ \\ XeAr\_3\_surface    
13 &     1 &    55 &  1.8  & cs    & edge    &          & 0.048 & 0.000 & 100.0&\\ %4.791$\cdot 10^{-6}$ \\ XeAr\_3\_edge       
14 &     1 &    55 &  1.8  & cs    & vertex  &          & 0.027 & 0.000 & 100.0&\\ %2.701$\cdot 10^{-6}$ \\ XeAr\_3\_vertex     
15 &     1 &    54 &  1.8  & in    & edge    &          & 0.077 & 0.000 & 100.0&\\ %7.708$\cdot 10^{-6}$ \\ XeAr\_3\_edge\_in   
16 &     1 &    54 &  1.8  & in    & vertex  &          & 0.053 & 0.000 & 100.0&\\ %5.258$\cdot 10^{-6}$ \\ XeAr\_3\_vertex\_in 
17 &     2 &    53 &  3.6  & in    &         &          & 0.117 & 0.055 &  68.1&\\ %1.711$\cdot 10^{-5}$ \\ XeAr\_3\_2in        
18 &     6 &    49 & 10.9  & in    &         &          & 0.375 & 0.405 &  48.1& \ref{figure:ar_3_6in}\\ %7.796$\cdot 10^{-5}$ \\ XeAr\_3\_6in        
19 &     6 &    49 & 10.9  & mixed &         &          & 0.292 & 0.674 &  30.3& \ref{figure:ar_3_6in}\\ %9.660$\cdot 10^{-5}$ \\ XeAr\_3\_6\_scat    
                                                                                                 \midrule
20 &     2 &    36 &  5.3  & cs    &         &          & 0.117 & 0.151 &  43.6& supp.\\                        % Ar$_{36}$Xe$_{2}$   
21 &     4 &    34 & 10.5  & mixed &         &          & 0.248 & 0.587 &  29.7& supp.\\                        % Ar$_{34}$Xe$_{4}$   
22 &     5 &    33 & 13.2  & mixed &         &          & 0.335 & 0.844 &  28.4& supp.\\                        % Ar$_{33}$Xe$_{5}$   
23 &    13 &    25 & 34.2  & mixed &         &          & 0.828 & 5.414 &  13.3& supp.\\                        % Ar$_{25}$Xe$_{13}$  
24 &    24 &    14 & 63.2  & mixed &         &          & 1.488 &16.718 &   8.2& supp.\\                        % Ar$_{14}$Xe$_{24}$  
25 &    25 &    13 & 65.8  & in    &         &          & 1.432 & 4.995 &  22.3& supp.\\                        % Ar$_{13}$Xe$_{25}$  
26 &    35 &     3 & 92.1  & in    &         &          & 2.017 & 7.051 &  22.2& supp.\\                        % Ar$_{3}$Xe$_{35}$   
\bottomrule
\end{tabular}
\end{table}
%
The geometrical properties as well as the total ICD and ETMD decay widths
of the investigated structures are shown in Table \ref{table:theo_gammas}.
It is important to remember that the first ICD channel opens at a
channel opening distance of \unit[7.58]{\AA}. In the smallest
clusters with only one argon layer around each
xenon atom, the Ar-Xe pair distances are below that value, therefore 
no ICD can take place. Also, by definition, two Xe atoms are
required for ETMD(3), hence it cannot occur in clusters with only one xenon atom.
%Because secondary electrons are observed in the experimental spectra
%we exclude all structures without any signal from our further
%discussions.
%
\begin{figure}[H]
 \centering
 \includegraphics[width=8.0cm]{surf.pdf}\\
 \includegraphics[width=8.0cm]{R_comp.pdf}
 \caption{
 %
 Top panel: Simulated electron emission spectra of an Ar 3s vacancy in 
          argon clusters
          consisting of 13 and 55 atoms, with an additional xenon atom residing
          on top of one of the argon surfaces.
          Bottom panel: Distribution of Ar-Xe distances $d$ in the studied ArXe
          clusters. The ICD channels to final states involving Xe 5p$_{3/2}^{-1}$ and 
          5p$_{1/2}^{-1}$ vacancies open at \unit[7.58]{\AA} and
          \unit[36.00]{\AA}, resp.; the former distance is marked by a vertical dotted line. 
          Only pairs at longer interatomic
          distances contribute to the electron emission spectra.
          Larger Ar-Xe distances, as found in the larger cluster,
          correspond to features at a higher kinetic energy of
          the ICD electron (top panel).}
 \label{figure:surf}
\end{figure}

%In the investigated structures several different aspects have to be
%taken into account which we will discuss separately if possible
%on selected structures.

We will now discuss features of several structures, using selected examples.
First we consider clusters having an argon core of 13 and 55 atoms plus a single xenon
atom on one of the surfaces (see Figure \ref{figure:cluster_3_overview}a
for the structure of clusters with the 55 atoms core).
Secondary electron spectra simulated for these systems are shown in Figure \ref{figure:surf}, top panel.
%two different argon core sizes one consisting
%of 13 and one consisting of 55 atoms with one xenon atom on one of
%the surfaces (see Figure \ref{figure:cluster_3_overview} Panel a)
%for the 55 atom core). The simulated secondary electron spectra are
%shown in Figure \ref{figure:surf} Panel 1.

Because the structures contain only one xenon atom, ETMD(3) is not possible, only ICD is expected. 
%Both spectra show several smaller peaks which
%are convoluted into one single peak with a maximum at
%approximately \unit[0.2]{eV}. 
%In comparison to the 13 argon atoms core
%spectrum t
The spectrum pertaining to the clusters with larger (55 atoms) Ar core shows
signals at higher energies of the secondary electron. These features
can be explained by investigating the Ar-Xe distance distributions
in the clusters, shown
in the bottom panel of Figure \ref{figure:surf}. 
Every different value of the atom pair distance
results in a different energy of the secondary electron and only pairs
with a distance of larger than the channel opening distance
(dashed gray line) will contribute
to the spectrum. 
In our model, there is a one-to-one correspondence between interatomic distance $d$ and kinetic energy of the ICD electron.
The larger the interatomic distance, the higher is the
kinetic energy of the secondary electron for a given channel.
%Since the cluster with an Ar core of 55 atoms is larger, and therefore
%contains Ar-Xe pairs with larger distances, its spectrum 
Therefore, the spectrum of the cluster with a 55 atoms core extends to higher energies.
%energies as well.
This relation between ICD energy and cluster size holds true for all cluster structures.
%This explains why the ICD spectrum for larger clusters extends to higher energies, and holds for all cluster structures.

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{2tops.pdf}
 \caption{Simulated electron emission spectra of an Ar 3s vacancy in 
          argon clusters consisting of 13
          argon atoms with two additional xenon atoms on top of two different
          argon surfaces. ICD and ETMD spectra are shown for three
          different relative positions of the two xenon atoms. If 
          the xenon atoms are close to each other, an ETMD process is
          clearly visible. In the other two cases the spectra are dominated by
          the ICD spectrum.}
 \label{figure:2tops}
\end{figure}
%
For clusters with more than one xenon atom, also ETMD(3) is possible.
Depending on the positions of the xenon atoms relative to each other and to the Ar core, the spectra are expected to be different.
As an example, we discuss clusters with a core of 13 argon atoms and two xenon atoms on different surfaces. 
Their xenon content is \unit[13.3]{\%} and thus close to the experimental one of \unit[10-12]{\%} for the lowest xenon admixture.
The cluster structures were illustrated in Figure \ref{figure:cluster_2_overview}, simulated spectra are shown in Figure \ref{figure:2tops}.
In all three cases, both ICD and ETMD(3) are energetically allowed. The ICD
spectra do not change qualitatively by adding the second xenon.
%either identical or at least very similar to the ones for
%cluster with a single  consisting of one
%convoluted peak at approximately \unit[0.2]{eV}. 
However, the ETMD(3) spectra
are very sensitive to the relative position of the two xenon atoms.
Two aspects have to be taken into account: an energy shift of the peaks due
to different charge distances in the final state (i.e. the interatomic Xe-Xe
distance) and the decrease of the decay width with $R^{-6}$, $R$ being the distance
between the electron transfer unit and the xenon atom ionized in the final state.
The larger the distance between the xenon atoms, the higher are the energies
of the secondary electrons and the smaller are the decay widths. 
Therefore, a
significant contribution from ETMD(3) compared to ICD is only
seen if the two xenon atoms reside on two adjacent
surfaces. 
%{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
The three energetically separated peaks in the ETMD(3) spectrum pertain to different combinations of the Xe 5p$_j^{-1}$ vacancy states, which have a substantial fine-structure splitting (see Table \ref{tab:valence}). 
%\ref{sec:exp_results}).
%
%The threefold peak structure of the ETMD(3) peak does in contrast to
%the ICD spectrum not stem from different triple structures but from the
%four different decay channels for one triple structure.

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{ar_3_6in.pdf}
 \caption{Same as Figure \protect\ref{figure:2tops}, for clusters consisting of
          55 atoms, 6 out of which are xenon atoms. These are either grouped
          on one side of the cluster (label `group') or evenly distributed
          in the cluster interior (label `scattered').}
 \label{figure:ar_3_6in}
\end{figure}
%
For the 55 atoms clusters, a xenon content of \unit[10--12]{\%}
corresponds to six xenon atoms out of a total of 55 atoms. These can form a connected 
group in one part of the cluster or can be evenly distributed,
as shown in Figures \ref{figure:cluster_3_overview}b and \ref{figure:cluster_3_overview}c. The
ICD and ETMD(3) spectra for these structures are shown in Figure \ref{figure:ar_3_6in}.

For both cases the overall ICD spectra are very similar, and show a maximum at a kinetic energy of approximately \unit[0.3]{eV}. 
In case of grouped xenon atoms, the ICD spectrum extends to slightly higher energies, corresponding to ArXe pairs at slightly larger spatial distances.
A more significant difference is observed in the ETMD(3) spectra. 
The interatomic xenon distance is shorter in clusters, in which the xenon atoms form a connected group.
Hence, the triple structure of the ETMD(3) spectrum is seen at lower kinetic energies. 
Additionally, the probability for an electron
transfer from a xenon to an argon atom decreases exponentially with the
interatomic distance. Therefore, only those xenon atoms which have direct
argon atom neighbours have a significant contribution to the
total decay width, and the total ETMD(3) decay width is lower for the structure with
grouped xenon atoms than for
the structure with evenly distributed xenon atoms (see Table \ref{table:theo_gammas}).

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{xe_3_in.pdf}
 \caption{Same as Figure \protect\ref{figure:2tops}, for argon clusters with
          one or two xenon atoms in the core of the cluster (55 atoms total). 
          All ICD and ETMD channels are closed, if the cluster contains only 
          a single xenon atom. For clusters with two xenon atoms
          in the core, the first ICD channel is open for some pairs,
          and additionally ETMD is possible for multiple triples. Due to a
          different distance distribution compared to the clusters with an argon
          core (Figure \protect\ref{figure:2tops}), 
          the ICD peak is shifted to higher kinetic energies.}
 \label{figure:xe_3_in}
\end{figure}
%
For comparison with the previous assumptions of a xenon core surrounded
by argon atoms we investigated clusters of 13 and 55 atoms with one or two
xenon atoms in the core. Some of the corresponding
spectra are shown in Figure \ref{figure:xe_3_in}.

%For the clusters with only one xenon atom in the core and the ionization
%energies used for the simulation of the secondary electron energies
%all ICD channels are closed. Since the cluster contains only one xenon atom,
%an ETMD(3) is not possible. Hence there is no signal to be expected at all.
For a core consisting of two xenon atoms both an ICD and an ETMD(3) spectrum
can be seen. Compared to the cluster structures involving an argon core, the ICD peak is
shifted to higher ICD electron energies. 
Additionally, the ICD and ETMD(3) spectra overlap.
For ETMD(3), only three of the four different decay channels are
energetically allowed.

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{c6l5.pdf}
 \caption{Same as Figure \protect\ref{figure:2tops},
          for a large cluster consisting
          of a xenon core of 561 atoms surrounded by five complete layers of
          argon atoms (Xe content: 14.5\,\%) for both an icosahedral and
          cuboctahedral basic structure.
          The ICD and ETMD peak overlap such that the ETMD peak
          is unlikely to be visible.}
 \label{figure:xe_6_lay5}
\end{figure}
%
In the first experiments very large argon-xenon clusters of 
$\approx 4380$ atoms with a xenon content of \unit[19]{\%}
were measured,\cite{Mucke_phd}
which we in one example approximate by a cluster consisting of 561 xenon
atoms surrounded
by five layers of argon atoms (3871 atoms in total). In order to take the
better stabilization of charges in larger clusters into account, the
ionization energies of the XL clusters (see Table \ref{tab:valence})
were used.
The spectra are shown in 
Figure \ref{figure:xe_6_lay5}.

Compared to the small clusters with a xenon core in Figure \ref{figure:xe_3_in}
the ICD peak is broadened and shifted to higher ICD electron energies which is
expected due to the larger interatomic Ar-Xe distances in the large cluster and
the better stabilization of charges, which is relevant mostly for the final state, but also the initial state.
The ETMD(3) peak is shifted to slightly higher energies as well. This allows opening of the
fourth decay channel, pertaining to Xe 5p$_{1/2}^{-1}$ Ar 3p$_{1/2}^{-1}$ final states.

We also note that the percentage of decay via ICD is practically
independent of the Xe content for large clusters with a Xe core, Ar shell structure.
This can be expected, as both decay processes are most pronounced for the
atoms in the interface region of the xenon core and the argon shell.
The ETMD(3), depending on the electron transfer from one xenon atom to the
initially ionized argon atom, and hence on the corresponding orbital overlap,
is purely an interface effect that involves the argon atoms with direct xenon
neighbours, and the two xenon layers closest to the argon shell.
The ICD has a stronger long range character, due to which the description
of decays with partners of at least twice the smallest channel opening
distance is necessary for clusters. However, the bigger the clusters are,
the more homogeneous does the interface region become for clusters of
different sizes. This manifests itself in the distribution of relevant
Ar-Xe pair distances (compare Figure \ref{figure:surf}, lower panel).
As a consequence, the ICD spectra of two large clusters of different size
hardly differ.

\clearpage

%\input{exp_results}
\section{Experimental Results}
\label{sec:exp_results}
%
%
\begin{table}
\caption{Properties of the outer valence spectra of mixed ArXe clusters. 
Spectra of pure Ar and Xe clusters are included for reference. 
All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV). 
Binding energies $\EB$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit. 
The average Xe content of the cluster ensemble, Xe$_{\rm cl}$, was determined from the areas of the respective photolines, corrected by their atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}.
Uncertainties are estimated as $\pm$3\,\% for the Xe content and 0.05~eV for the binding energies. 
The row labelled `(th.)' gives the binding energies used in the simulations of this paper, and the last row their atomic counterparts. 
Values for Ar 3p in the last row refer to the fine structure states.
\label{tab:valence}}
\begin{tabular}{ l c c c c c c c c}
%
\toprule
 \multicolumn{2}{r}{size} &  Xe$_{\rm in}$& $\EB$ (eV)& $w$ (eV)& \multicolumn{2}{c}{$\EB$ (eV)}  & $w$ (eV) &  Xe$_{\rm cl}$ \\
%
 \multicolumn{2}{r}{(label)}&  (\%) & Ar 3p & Ar 3p & Xe 5p$_{1/2}$ &  Xe 5p$_{3/2}$ & Xe 5p$_{3/2}$  &  (\%) \\
\midrule
% Ar, from Marko
 Ar & (1) &&  15.3  &  1.1 & & & &  \\
% Ar, from Marko 
 Ar & (2) &&  15.1  &  1.3 & & & &  \\
%
%  columns in the following: energies c.g. 51-plt-oval, widths Marko Diss., Xe content Marko Diss
% 1103 676, 679
 ArXe & S &1.2 & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
% 1103 670
 ArXe & M &1.2 & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
% 1103 671
 ArXe & L &1.2 & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
% 1103 663
 ArXe & S &3.0 & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
% 1103 640
 ArXe & M &5.0 & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
% 0506 
 Xe &  & & & & 12.76 & 11.19 & 1.18 & 100\\
%
\midrule
%
%  1004  886  (UHe, c.g. + roi values)
 ArXe & XL &2.5 & 15.15 & 1.3 & 12.59 & 11.01 & 1.24 & 19\\
%
\midrule
% Date: Wed, 20 Jan 2016 11:27:39, From: Elke Fa?hauer <elke.fasshauer@uit.no>
 Ar, Xe & (th.) && 15.3 && 13.0 & 11.5 &&\\
%
 \multicolumn{2}{l}{(atomic)\cite{velchev,sansonetti}} && 15.76|15.94 && 13.43 & 12.13 &&\\
%
\bottomrule
\end{tabular}
\end{table}

\subsection{Outer valence spectra}
%
\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{figure_oval_1.pdf}
 \caption{
Outer valence photoelectron spectra of mixed Ar-Xe clusters, in comparison to the pure species. 
(a) shows the outer valence region of homogeneous Ar and Xe clusters, respectively (see text for details). 
The two lower panels show spectra of the mixed species with different mean size. 
Sharp lines marked `m' (for `monomer') result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states. 
Labels in (b) and (c) give the Xe content in the expanding gas mixture (Xe$_{\rm in}$), which is lower than the Xe content observed in the heterogeneous clusters (Xe$_{\rm cl}$). 
The photon energy was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
%{\color{red}{Die Stabilisierung der Xe-bulk Atome ist in den gemischten Cluster
% höher als in den gemischten Clustern. Das ist ungewöhnlich. Habt ihr hier
% verschiedene CLustergrößen?}}
}
 \label{figure:oval1}
\end{figure}

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{figure_oval_2.pdf}
 \caption{
Outer valence photoelectron spectra of mixed Ar-Xe clusters from gas mixtures with different Xe concentration. 
For better visibility, a scaling factor is applied to the Xe part of the spectrum in panel (a).
See Figure \ref{figure:oval1} and text for details.
}
 \label{figure:oval2}
\end{figure}

Figure \ref{figure:oval1} shows the outer valence spectra of small and large ArXe clusters, compared to clusters of the pure gases. 
Qualitatively similar spectra have been published without detailed discussion in ref \citenum{lindblad}.
Differences are seen in particular for the Ar component. 
In pure Ar clusters, outer valence photoionization leads to a broad band, caused both by spin-orbit coupling and crystal field splitting. 
The relative importance of these two mechanisms remains under debate.\cite{hergenhahnprb,rolles,foerstel_arg1_2010} 
For larger clusters (e.g. $\langle N\rangle = 190$, black trace), the maximum at low binding energies becomes more pronounced, and is identified with emission from the cluster interior.\cite{hergenhahnprb,rolles}
At the particular photon energy selected here, atop of this band a sharp feature is also visible (in Figure \ref{figure:oval1} at a kinetic energy of about 1.8 eV).
For larger clusters (above $\langle N\rangle \approx 100$), over a range of photon energies of about 3 eV, its appararent binding energy changes in a way which is reminiscent to photoemission of crystalline bulk matter (`dispersion').\cite{foerstel_arg1_2010,foerstel_arg2_2011}

Ar 3p spectra of the smaller mixed clusters (Figure \ref{figure:oval1}c, Figure \ref{figure:oval2}) show neither of these traits.
Rather, the Ar band is symmetric, less wide than in the pure clusters and at a higher binding energy.
Even for very large clusters (Figure \ref{figure:oval1}b) the asymmetry of the 3p band and the `dispersing feature' do not appear.
We characterize the spectral shape by giving a single value for the Ar 3p binding energy, and the FWHM of the feature.
Values for different expansion parameters, and for both Ar and Xe valence lines, are collected in Table\ \ref{tab:valence}.

We find experimentally that clusters we have produced have a Xe content Xe$_{\rm cl}$ between 10\,\% and 50\,\%.
A slight decrease of the binding energy with cluster size is seen for all outer valence lines, and is attributed to a larger final state polarization energy in larger clusters.

For further interpretation of the shape of the Ar peaks we refer to photoemission spectra of condensed Ar monolayers, measured in several settings.\cite{jacobi,jacobi2}
Spectra were reported for physisorption of Ar on two different metal single crystal substrates, and for Ar atop of a Xe spacer layer adsorbed on the metal.
While the binding energy depends on the substrate, the spectral shape is very similar in all cases. 
Most spectra were recorded for emission along the surface normal, and show a double peak split by about 0.5 eV, leading to a structure with $w$ about 1 eV.
Although the splitting is larger than the gas phase fine structure split of 0.18 eV, the pertaining states have been assigned to Ar 3p$_{1/2}$ and 3p$_{3/2}$.
A crystal field splitting of the 3p$_{3/2}$ state has been assumed to be also present, but with a smaller value of 0.1-0.2 eV, approx.\cite{jacobi2} 
The spectrum clearly changes when going to an emission angle of 40$^\circ$ with respect to the surface normal (Figure 2 in ref \citenum{jacobi2}).
The higher binding energy peak significantly loses in intensity, and the spectrum is now dominated by a single peak comprising both crystal field split substates of Ar 3p$_{3/2}$, with a FWHM ($w$) of only 0.4 eV.
As our measured spectrum is comprised of contributions recorded under all emission angles with respect to the cluster surface, grazing emission will be the rule.
We therefore believe that the arguments given above make it plausible that only a single peak is observed in all our spectra.

Emission from the Xe 5p state shows a much larger fine structure splitting then from the Ar 3p state; it dominates the spectrum even in clusters (where other broadening mechanisms are also present).
The shift of the cluster bands with respect to the monomer lines in the largest mixed clusters we have probed (Figure \ref{figure:oval1}b) are similar to the ones in the pure Xe spectrum, the scaling law size of which is at somewhat more than five filled shells.
This indicates an approximate upper limit for the size of the Xe core in our mixed clusters, as their binding energy shift might be somewhat higher than the one in pure clusters, due to polarization of covering Ar layers.
Xe cluster features in the spectra of mixed clusters appear less asymmetric than the pure Xe spectrum, and also less asymmetric as some the ArXe spectra shown in ref \citenum{lindblad}.
This might be caused by the difference in photon energy ($h\nu = 90$ eV in ref \citenum{lindblad} and for the pure Xe spectrum, $h\nu = 32$ eV for the mixed ArXe spectra in this work).
% For the mixed clusters, the Xe band broadens and shifts towards lower binding energy for larger size clusters.
%For pure Xe clusters, an asymmetry observed in the Xe 5p$_{3/2}$ part has no counterpart in the respective spectra from the mixed clusters.
%This might be caused by the difference in photon energy, as can be seen from a comparison to literature spectra (ArXe at $h\nu = 90$ eV in ref \citenum{lindblad}, Xe at $h\nu = 20$ eV in ref \citenum{rolles}).
%For the largest clusters, the nominal size yielded from the jet parameters applied to a pure Xe expansion would correspond to clusters in which bulk atoms far outweigh those on the surface.
%At least for the 5p$_{1/2}$ photoelectron line, this would be seen as a clear asymmetry towards the low binding energy side, which is not observed in our spectra.

In Figure \ref{figure:oval2}, we compare the outer valence spectra of clusters with similar expansion conditions, but different composition of the gas mixture.
A Xe-rich mixture obviously leads to clusters with more intense Xe photolines, but besides that the main change consists in a narrowing of the Ar band.
A comparison with the Ar monomer features (clipped in the Figure) also shows an increased degree of condensation for the Ar gas in the expansion.

For the smallest clusters we have produced, a possible model is provided by calculated minimum energy structures of Ar$_N$Xe$_{38-N}$ (Figure 7 in ref \citenum{marques}).
We there see that for a Xe content of less than 60\,\%, core-shell systems are {\it not} formed, and although the Xe atoms tend to connect, the degree of Ar-Xe mixing is large.
While for low Xe content (approx. 10\,\%), some Ar atoms have only Ar nearest neighbours, for larger Xe content all Ar atoms seem to see both Ar and Xe nearest neighbours.
We believe this leads to the Ar 3p narrowing pointed out above.
For Figure \ref{figure:oval2}, possibly, some clusters of our ensemble already are in the core-shell regime, which would lead to an even lower 3p width.

For the largest clusters we have produced (Figure \ref{figure:oval1}b), the low binding energy of the Xe lines and the broadening of the Ar feature without appearance of the `bulk Ar'-maximum, supports formation of a Xe core covered by at least two layers of Ar.
If the scaling law size for a pure Ar expansion is taken as the lower limit for the cluster size, from the observed Xe content we arrive at clusters composed of a Xe core with four layers, covered by three layers of Ar (see Supporting Information).

Finally, comparing Figure \ref{figure:oval2} to Figure \ref{figure:oval1} reveals that much larger changes in the valence emission spectra occur by changes in size than by changes of the (relative) Xe content.
This finding is supported by the spectra shown in ref \citenum{lindblad}.
%
%
\subsection{Inner valence spectra}
%
We now focus on the Ar inner valence (3s) vacancy states. 
%
\begin{figure}[ht]
 \centering
 \includegraphics[width=8.8cm]{figure_ival.pdf}
 \caption{
Photon excited electron spectra of mixed Ar-Xe clusters in the inner valence region.
Symbols show the Ar 3s photoline from clusters (`cl') and uncondensed Ar monomers (`m'), atop of a background resulting from inelastic intracluster scattering of outer valence photoelectrons (`excitonic satellites').\protect\cite{hergenhahn2002}
The photon energy was $h\nu = 32$ eV.
Panel (a) shows all electrons accumulated.
For the same conditions, in panel (b) we only show electrons that were detected in coincidence with a secondary electron of lower kinetic energy.
The black solid trace in (a), and red solid trace in (b) result from a least squares fit to the cluster part of the spectrum. 
The red solid trace in (a) is the fit shown in (b), divided by the detection efficiency of the spectrometer of 0.6.
Panels (c) and (d) show the same type of data for smaller clusters with a lower Xe content.
See text for details.
\label{figure:ival}
}
\end{figure}

Figure\ \ref{figure:ival} shows the Ar part of the inner valence spectrum for representative ArXe clusters. 
The total photoelectron signal looks similar to literature spectra for pure Ar clusters.\cite{feifel,zhang} 
A low energy tail seen for the Ar 3s monomer line results from the transmission properties of the electron spectrometer, together with the strongly positive angular distribution parameter of this line.\cite{zhang,kruit}
The Ar 3s cluster line shows no splitting into bulk and surface components, different to the literature on pure clusters but in agreement with our discussion of the outer valence spectra. 
The binding energy of the cluster line has values between 28.85 and 28.70 eV for all cluster ensembles with size label S-L, and 28.67 eV for the largest clusters measured. 
A small, but systematic decrease of the binding energy is observed when the cluster size is increased. 
The value assumed in the simulations is 28.7 eV.

If we produce a spectrum only from those electrons recorded as part of a two-electron coincidence (electron pair with kinetic energies ($e_1,e_2$)) the apparent intensity drops (compare panel b to a, and d to c in Figure \ref{figure:ival}).
This can partly be attributed to the finite detection efficiency of the spectrometer. 
Moreover, the monomer part of the Ar 3s signal completely disappears, as 3s photoionization of an uncondensed Ar atom in the gas jet cannot lead to emission of a second electron. 
Further features of these diagrams and the least squares fits shown in the Figure are discussed below.
%
%
\subsection{ICD/ETMD spectra}
%
\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{figure_icd_12.pdf}
 \caption{
Energy spectrum of all coincident secondary (ICD or ETMD) electrons of kinetic energy $e_2$ pertaining to primary electrons of kinetic energy $e_1$ in the Ar 3s binding energy region. 
Spectra were recorded with a photon energy of $h\nu = 32$~eV. 
Black error bars show the data points for the smallest clusters measured (`S'), two larger clusters sizes are shown by the red and blue traces. 
Error bars for the latter are smaller than the ones shown and have been omitted.
For better comparison, all spectra are shown area-normalized. 
}
 \label{figure:icd_12}
\end{figure}
%
%
\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{figure_icd_l.pdf}
 \caption{
Energy spectrum of all coincident secondary (ICD or ETMD) electrons, kinetic energy $e_2$, for clusters of the same size, but from gas mixtures with different Xe concentration. See Figure \protect\ref{figure:icd_12} for details.
}
 \label{figure:icd_l}
\end{figure}
%
In Figure \ref{figure:icd_12}, we show the spectra of ICD/ETMD electrons pertaining to emission of an Ar 3s cluster photoelectron. 
Due to their low kinetic energy, without use of a coincidence method they could hardly be separated from the background of inelastically scattered photoelectrons.\cite{mucke}
This and the following Figure constitute the central experimental result of the article.
Spectra recorded at $h\nu = 34$ eV as a cross-check quantitatively agree to those shown here.
This underpins our assignment of this intensity to an autoionization process.
Further details on the data acquisition and analysis methodology, as well as the 34~eV spectra, are given in the Supporting Information.

Spectra for the three different cluster sizes in Figure \ref{figure:icd_12} are significantly different: Spectra for the larger clusters acquire more intensity in the 1-1.5 eV region and have less intensity for energies below 0.5 eV.
In contrast to that, the ICD/ETMD spectrum hardly varies when the composition of the expanding gas mixture, and with that the relative Xe content of the clusters, is changed (Figure \ref{figure:icd_l}).
The full set of ICD/ETMD spectra is shown as Supporting Information.

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{figure_eff.pdf}
 \caption{
Efficiency of the decay of Ar 3s ionized states in ArXe clusters by emission of a secondary electron via ICD or ETMD. Values are arranged by Xe content of the initial gas mixture (`+' symbols: 1.2\,\%, asterisk: 3\,\%, triangle: 5\,\%). Symbol sizes indicate the photon energy (large symbols: 32 eV, small: 34 eV), and color indicates the cluster size (black symbols: S, red: M, blue: L). See text for details.
}
 \label{figure:eff}
\end{figure}
%
We now discuss which fraction of Ar 3s vacancy states relaxes via ICD or ETMD.
A method to derive this information has been established by some of us.\cite{foerstel_2013}
Briefly, we correct the intensity of the Ar 3s photoline in the coincident spectra by the detector efficiency, and divide it by the total (coincident and non-coincident) Ar 3s intensity.
The result gives the branching ratio of decay via ICD/ETMD vs. the sum of all channels, including those not involving electron emission.
(If all Ar 3s vacancies decay by emission of another electron, the coincident and non-coincident count rate differ only by the probability for the spectrometer to actually detect the secondary electron.
This figure has been determined as 0.6 for this data set, in the same way as discussed earlier.\cite{mucke_review})
To arrive at quantitative results, we have performed least squares fits of the non-coincident and coincident $e_1$ spectra.
The fits assumed one or two Gaussian peaks, resp., atop of a background modelled by two more Gaussian curves with very large widths.
The peak pertaining to the Ar 3s cluster photoline, with the background added, is shown by the black solid trace in Figure \ref{figure:ival}a and red solid trace in Figure \ref{figure:ival}b.
Moreover, the line labelled `c.fit/det.' shows the fit to the coincident events, corrected by the detection efficiency, and plotted atop of the non-coincident intensity. 
This virtually agrees with the fit to the total spectrum in Figure \ref{figure:ival}a, but not in \ref{figure:ival}c. 
The corresponding figure for the ICD/ETMD efficiency comes out as one for \ref{figure:ival}a, and significantly smaller than one for \ref{figure:ival}c.
Figure \ref{figure:eff} shows all results of this analysis.
The error in the autoionization efficiency shown is mainly determined by uncertainties in the peak/background separation.
%(Our choice for the background shape is shown in Figure \ref{figure:ival}.)
For the gas mixture with a Xe$_{\rm in}$ of 1.2\,\%, we therefore show results from fits using two different choices of the background shape in Figure \ref{figure:eff}.
Statistical errors are much smaller than the differences between the pairs of values arrived at such.

We found an Ar 3s autoionization efficiency which, for clusters with the lowest Xe content (Xe$_{\rm cl}$ approx. 10-12\,\%), is smaller than unity, and further decreases with decreasing cluster size. 
For larger Xe$_{\rm cl}$, the values are compatible with unity, within the accuracy of our experiment.

%\input{theo_discussion}
\section{Discussion
\label{sec:discussion}}
%
%We have discussed the experimental spectra in Section \ref{sec:exp_results} and
%the expected features of spectra for different cluster types in
%Section \ref{sec:th_results}. In this section we combine the experimental and theoretical
%results in order to determine the structure of the noble gas clusters.
%
%The simulated secondary electron spectra for the xenon core structures
%(see Figure \ref{figure:xe_3_in})
%show an ICD peak at higher energies than those structures with added xenon
%atoms on the surface. This does not fit to the experimentally determined
%spectra and hence we consider an argon core to be more probable for the
%small measured clusters.
%
%The experimental spectra in Figure \ref{}
%show a broadening of the secondary electron peak with increasing
%pressure (?) and hence cluster size just as can be expected from
%the theoretically simulated spectra in Figure \ref{figure:surf}.
%
%From the theoretical simulations of larger small clusters
%having the same xenon content as experimentally observed a clearly
%visible ETMD peak is to be expected as shown in Figure \ref{figure:ar_3_6in}.
%However, the experimental spectra do not show a signal in the energy
%region of \unit[1.5--6.5]{eV}. From this we conclude that the clusters
%measured were smaller than 55 atoms containing only very few xenon atoms.
%Additionally, if the cluster contains more than one xenon atom, they are
%not expected to be close because of an otherwise visible ETMD peak
%(compare Figure \ref{figure:2tops}).
%
%The large clusters with a large xenon content can be expected to have
%a xenon core being surrounded by argon layers and hence, both ICD and
%ETMD should be visible in the spectrum. Unfortunately, the ICD and ETMD
%peaks overlap such that the two processes can not be distiguished.
%
We now would like to interpret our experimental findings in view of the simulated results described in Section `Theoretical Results'.
Figure \ref{figure:eff} shows that for Ar 3s$^{-1}$ states autoionization by either ICD or ETMD is the only mode of relaxation, except for the clusters with the smallest Xe content.
We consider this a remarkable result, because ICD of these states is only possible with a Xe atom in the second coordination shell of the decaying Ar vacancy (or shells even further apart), which significantly slows down the ICD process.
Also decay rates for ETMD were found to be small in early studies of this effect.\cite{zobeley}
Nevertheless, even in this situation the non-local autoionization channels foreclose radiative decay.

% lowest kinetic energy is the first point of energy raster for t-E code of 52-proc-spec
Structurally, all experimental ICD/ETMD spectra have a maximum at or near the lowest kinetic energy that could be measured (50~meV), and decrease in intensity to less than half for kinetic energies already below one eV. 
Qualitatively, this shape fits to the ICD contributions in the autoionization spectra discussed in the `Theory' section, but not to the ones from ETMD. 
The calculated ETMD spectra have a typical three-fold structure with peaks between 3.5-5~eV, 1.5-2.5~eV and around 0 eV kinetic energy. 
The former two features seem not to be present in the experimental spectra. 
Due to restrictions in the detector electronics, electron pairs with very similar kinetic energy cannot be detected. 
The highest kinetic energy for an autoionization electron that can be detected in coincidence with a photoelectron of $\sim3.5$~eV ($h\nu = 32$~eV) is around 2.5~eV.
Very weak intensity is observed at this energy, and also at higher $e_2$ energies that can be probed at $h\nu = 34$~eV (Supporting Information).

As a cross-check for our theoretical methods we have calculated the radiationless decay spectrum of Ar 3s$^{-1}$ in ArKr, which may arise {\it only} from ETMD(3),\cite{foerstel} and arrived at qualitative agreement with the experimental data.\cite{arkr}

The size-dependent trend within the experimental data is in qualitative agreement to the change in the calculated spectral shape for ICD in systems of increased size (compare Figure~\ref{figure:2tops} to \ref{figure:xe_3_in} and \ref{figure:xe_6_lay5}.)

We are therefore lead to the conclusion that the autoionization spectra we incur are dominated by ICD to non-nearest neighbour atoms, while the intensity of the ETMD channel is low. 
We would like to recall the factors that lead to a propensity for decay via one or the other mechanism, which have been discussed in the `Theoretical Results'-section.
For ETMD to occur with a measurable rate, two Xe atoms have to be present in the vincinity of the decaying Ar atom (Figure \ref{figure:2tops}).
Should that be the case for a large part of the Ar atoms in some cluster structure, ETMD can even dominate over ICD (Figure \ref{figure:ar_3_6in} and Supporting Information).
Model structures shown in Figures \ref{figure:2tops} and \ref{figure:ar_3_6in} have a Xe content similar to the lowest one probed in our experiment ($\sim$11\,\%).
For a higher Xe content, ETMD will always dominate the spectra if the two species are given the chance to mix, as e.g. in the calculated minimum energy structures of $N=38$ ArXe clusters (Supporting Info).
On the other hand, in core-shell systems decay via ETMD is probable only for Ar atoms in the interface layer, as this mechanism requires some wavefunction overlap between Ar and one of the Xe atoms involved.
For the core-shell systems we have investigated, the likelihood of decay via ETMD stays below 25\,\% even for a Xe content above 50\,\% (Table \ref{table:theo_gammas}).

In summary, the two structural motifs that can best be reconciled with our experimental data are
\begin{enumerate}
	\item small clusters containing only few Xe atoms that are spread out to distant positions on the cluster surface, and
	\item systems with a compact Xe core and Ar outer layers.
\end{enumerate}
These structures are compatible with the findings of Lindblad {\it et al.}\ from core level photoelectron spectroscopy, who proposed the former structure for the smallest clusters in their study, and the latter for larger ones.\cite{lindblad}
As even in these two cases intensity for decay via ETMD would not vanish completely, we have to leave it open though whether other mechanisms are present, which further suppress ETMD vs. ICD.

While in early work on ICD it has almost been a paradigm that the decay involves two {\it neighbouring} atoms or molecules,\cite{hergenhahn_review} more recently significant intensity for non-nearest neighbour ICD has been found also in other systems.
One example is Ne-Ar after Ne 2s ionization, where decay to Ar in the second coordination shell is clearly visible despite the fact that in this system decay involving nearest neighbours is energetically allowed.\cite{fasshauer2014}
A further theoretical delineation of the respective factors has recently been presented by one of us.\cite{fasshauernjp}

%\input{summary}
\section{Summary}
%
We have presented comprehensive experimental and theoretical data for the
autoionization of inner valence ionized states in ArXe clusters.
Both ICD and ETMD are allowed for most cases we considered.
Because of energetical reasons ICD requires a separation of the final state
vacancies of \unit[7.58]{\AA} or more, which is about two times the typical
Ar-Xe distance.
We found that autoionization has an efficiency of 0.8 to 1.0 within the
experimental accuracy, that is it dominates over other modes of relaxation.
By comparing our measured spectra to calculations, we identified `long range'
ICD as the most important decay mode and were able to determine the most
probable structural motifs to be a xenon core surrounded by several argon layers
for large clusters and argon clusters with with very few xenon atoms spread out
over the surface.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "Acknowledgement" section can be given in all manuscript
%% classes.  This should be given within the "acknowledgement"
%% environment, which will make the correct section or running title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{acknowledgements}
\begin{acknowledgement}
%
We thank HZB for the allocation of synchrotron radiation beamtime, and the
Deutsche Forschungsgemeinschaft for funding via the Forschergruppe 1789.
E. F. gratefully acknowledges the Research
Council of Norway through a Centre of Excellence Grant (Grant No.\ 179568/V30)
for funding.
%
\end{acknowledgement}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The same is true for Supporting Information, which should use the
%% suppinfo environment.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{suppinfo}

%This will usually read something like: ``Experimental procedures and
%characterization data for all new compounds. The class will
%automatically add a sentence pointing to the information on-line:

%\end{suppinfo}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The appropriate \bibliography command should be placed here.
%% Notice that the class file automatically sets \bibliographystyle
%% and also names the section correctly.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{arxe}

\end{document}

### 2016-07-04 onefolder/theo_results.tex
add the folder which was submitted
unfortunately, the journal requires it like this

--- 2016-07-04 onefolder/master.tex
@@
-	
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% This is a (brief) model paper using the achemso class
-%% The document class accepts keyval options, which should include
-%% the target journal and optionally the manuscript type.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\documentclass[journal=jpccck,manuscript=article,layout=twocolumn]{achemso}
-\documentclass[journal=jpccck,manuscript=article]{achemso}
-
-% UHe stuff
-\def\EB{E_{\rm b}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Place any additional packages needed here.  Only include packages
-%% which are essential, to avoid problems later. Do NOT use any
-%% packages which require e-TeX (for example etoolbox): the e-TeX
-%% extensions are not currently available on the ACS conversion
-%% servers.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage[english]{babel}
-\usepackage{braket}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath,amsfonts,amssymb}
-\usepackage{dsfont}
-\usepackage{booktabs}
-\usepackage{units}
-\usepackage{xcolor}
-\usepackage{multirow}
-\usepackage{tikz,pgfplots}
-\usepackage{float} %force figure position
-
-\usetikzlibrary{patterns,shadows,trees,calc}
-\usepgfplotslibrary{units}
-
-\pgfplotsset{compat=1.10}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% If issues arise when submitting your manuscript, you may want to
-%% un-comment the next line.  This provides information on the
-%% version of every file you have used.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%\listfiles
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Place any additional macros here. Please use \newcommand* where
-%% possible, and avoid layout-changing macros (which are not used
-%% when typesetting).
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newcommand*\mycommand[1]{\texttt{\emph{#1}}}
-% Define some colours
-\definecolor{diplom1}{rgb}{0.0 0.4 1.0}
-\definecolor{diplom2}{rgb}{0.0 0.0 0.6}
-\definecolor{diplom3}{RGB}{153,0,0} %unirot
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Meta-data block
-%% ---------------
-%% Each author should be given as a separate \author command.
-%%
-%% Corresponding authors should have an e-mail given after the author
-%% name as an \email command. Phone and fax numbers can be given
-%% using \phone and \fax, respectively; this information is optional.
-%%
-%% The affiliation of authors is given after the authors; each
-%% \affiliation command applies to all preceding authors not already
-%% assigned an affiliation.
-%%
-%% The affiliation takes an option argument for the short name.  This
-%% will typically be something like "University of Somewhere".
-%%
-%% The \altaffiliation macro should be used for new address, etc.
-%% On the other hand, \alsoaffiliation is used on a per author basis
-%% when authors are associated with multiple institutions.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author{Marko F\"orstel}
-\altaffiliation{Now at: Institut für Optik und Atomare Physik, Technische Universit\"at Berlin, Hardenbergstr. 36, 10623 Berlin, Germany}
-\author{Melanie Mucke}
-\altaffiliation{Now at: Department of Physics and Astronomy, Uppsala University, Box 516, 75120 Uppsala, Sweden}
-\author{Tiberiu Arion}
-\altaffiliation{Now at: Center for Free-Electron Laser Science/DESY, Notkestr. 85, D-22607 Hamburg, Germany}
-\author{Toralf Lischke}
-\affiliation[IPP]{Max-Planck-Institute for Plasma Physics, Boltzmannstr. 2, D-85748 Garching, Germany}
-\author{Markus Pernpointner}
-\affiliation[University of Heidelberg]{Theoretical Chemistry, University of Heidelberg,
-              Im Neuenheimer Feld 229, D-69120 Heidelberg, Germany}
-\author{Uwe Hergenhahn}
-\affiliation[IOM]{Leibniz Institute of Surface Modification, Permoserstr. 15, D-04318 Leipzig, Germany}
-\alsoaffiliation[IPP HGW]{Max-Planck-Institute for Plasma Physics, Wendelsteinstr. 1, D-14791 Greifswald, Germany}
-\email{uwe.hergenhahn@iom-leipzig.de}
-\author{Elke Fasshauer}
-\affiliation[UIT]{Centre for Theoretical and Computational Chemistry,
-Department of Chemistry, University of Troms\o
--- The Arctic University of Norway, N-9037 Troms\o, Norway}
-\email{elke.fasshauer@uit.no}
-%\phone{+123 (0)123 4445556}
-%\fax{+123 (0)123 4445557}
-%\alsoaffiliation[Second University]
-%{Department of Chemistry, Second University, Nearby Town}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The document title should be given as usual. Some journals require
-%% a running title from the author: this should be supplied as an
-%% optional argument to \title.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Long-range Interatomic Coulombic Decay in ArXe clusters: Experiment and Theory}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Some journals require a list of abbreviations or keywords to be
-%% supplied. These should be set up here, and will be printed after
-%% the title and author information, if needed.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\abbreviations{IR,NMR,UV}
-%\keywords{American Chemical Society, \LaTeX}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The manuscript does not need to include \maketitle, which is
-%% executed automatically.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The "tocentry" environment can be used to create an entry for the
-%% graphical table of contents. It is given here as some journals
-%% require that it is printed as part of the abstract page. It will
-%% be automatically moved as appropriate.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{tocentry}
-
-\begin{center}
- \includegraphics[height=3.5cm]{front1.pdf}
-\end{center}
-
-%Some journals require a graphical entry for the Table of Contents.
-%This should be laid out ``print ready'' so that the sizing of the
-%text is correct.
-%
-%Inside the \texttt{tocentry} environment, the font used is Helvetica
-%8\,pt, as required by \emph{Journal of the American Chemical
-%Society}.
-%
-%The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
-%permitted for  \emph{Journal of the American Chemical Society}
-%graphical table of content entries. The box will not resize if the
-%content is too big: instead it will overflow the edge of the box.
-%
-%This box and the associated title will always be printed on a
-%separate page at the end of the document.
-
-\end{tocentry}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The abstract environment will automatically gobble the contents
-%% if an abstract is not used by the target journal.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{abstract}
-
-\begin{abstract}
-We report about autoionization channels of Ar inner valence ionized states in mixed ArXe clusters and compare
-our experimental data obtained by electron-electron coincidence spectroscopy
-to our theoretical simulations for representative cluster structures.
-The combined experimental and theoretical data show that the autoionization of Ar 3s$^{-1}$ in ArXe is dominated by Interatomic Coulombic Decay (ICD) to Xe atoms in the second and higher coordination shells of the originally excited atom.
-Clusters with a range of sizes, compositions and structures were probed. 
-The Xe content in the clusters was varied between 10\,\% and 53\,\%. 
-Besides ICD, also Electron Transfer Mediated Decay (ETMD(3)) was found important in many of the calculated spectra, but is seen with less intensity in the experimental spectra. 
-From the calculations, we identify structural motifs which minimize the ETMD vs.
-the ICD rate and suggest that these are preferentially realized in our experiment, in which clusters are formed by supersonic expansion of an Ar-Xe mixture.
-Suggested cluster structures either feature a clear segregation between Ar and Xe fractions, e.g. Xe core, Ar shell systems, or contain a few Xe atoms singled out in surface sites on an Ar cluster.
-These structures differ significantly from the majority of calculated minimum energy structures for ArXe systems of 38 atoms, which might show that the latter, annealed structures are not realized in our experiment.
-We show experimentally that the relaxation of Ar inner valence states by ICD and ETMD together has an efficiency of unity, within the experimental accuracy, for all clusters except those with the lowest Xe content.
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Start the main part of the manuscript here.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{intro}
-\section{Introduction}
-%
-Electron spectroscopy can make important contributions to the 
-research on composition and structure of free nanoparticles.\cite{
-jpcc} Besides photoionization, free electrons emerging from 
-nanoparticles can also be produced by the relaxation of 
-electronically excited states. One such process, which is of 
-particular relevance in weakly bonded systems, is the 
-Interatomic or Intermolecular Coulombic Decay (ICD).\cite{
-cederbaum} In ICD, an electronic excitation decays by energy 
-transfer to one of its neighboring atoms or molecules, thus 
-releasing a free electron from the latter site. ICD is an 
-important relaxation channel e.g. for inner-valence holes in 
-atoms, and also for core level vacancies e.g. in \ce{H2O}
-, where it competes with Auger decay.\cite{slavicek}
-
-By definition, ICD is particularly sensitive to the chemical 
-environment of the atom or molecule in which the primary 
-excitation has taken place. We suggest that this property of ICD 
-decay spectra can be used to derive information on a nanoparticle 
-or a solvation system. 
-The term excitation is used here in a broader sense---in the
-systems we consider in this work, ICD occurs from an excited, singly 
-charged Ar state created by photoionization.
-In other systems, ICD was also observed from neutral excited
-states and states with more than one vacancy.
-
-We report here about studies 
-in which we produced heterogeneous clusters of the noble gases Ar 
-and Xe with different sizes, and compositions ranging from a few 
-Xe dopant atoms in an Ar matrix to clusters containing an equal 
-amount of both species. By the use of electron-electron 
-coincidence spectroscopy and of theoretical simulations on 
-prototypical systems we show how the radiationless decay spectrum 
-of Ar inner valence (3s) ionized states connects to the structure 
-of the clusters.
-
-Intermolecular Coulombic Decay initially was predicted from 
-theoretical considerations of the energy levels in singly vs.\  
-doubly ionized, and doubly vs.\ triply ionized, hydrogen bonded 
-clusters.\cite{cederbaum} First experimental work some years 
-later used Ne clusters,\cite{marburger,jahnkenedimer} but quickly 
-was followed by demonstrations of ICD in a diverse range of other 
-systems. Experimental and theoretical progress has been reviewed.
-\cite{hergenhahn_review, averbukh_review, jahnke_review} ICD 
-proceeds by an initial ionization producing an ion in an excited 
-state, followed by a transfer of energy to a neighbouring site, 
-and an electron emission process therefrom. The final state contains 
-two positive charges; one at the original site of ionization, and a second
-one at another atom or molecule.
-
-Soon after, related 
-autoionization processes were discovered that proceed via a 
-charge transfer instead of an energy transfer. 
-These were termed `Electron Transfer Mediated Decay' 
- (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
- which the originally excited site is neutralized by the decay 
-and `exchange ICD' for charge transfer contributions to the 
-normal ICD amplitude.\cite{santrarev,jahnkesat}
-We find that both energy and charge transfer induced 
-autoionization play a role in Ar-Xe, and will detail the 
-relevant processes below. The notion of ICD requires that the 
-electronic orbitals of the two sites can be distinguished, which 
-typically is the case in weakly bonded systems, held together by 
-hydrogen bonds or van-der-Waals bonds. In the case of strong
-(covalent or metallic) bonding, it is impossible to make a
-distinction between ICD and Auger decay.\cite{hergenhahn_review}
-
-Rare gas clusters are suitable prototype systems for studies of
-ICD, as they can readily be produced by supersonic 
-expansion through a cooled nozzle. 
-The size of the clusters can be changed by varying the expansion parameters.
-The formation of heterogeneous rare gas clusters by coexpansion of a gas mixture cannot {\it a priori} be taken for granted, but was experimentally shown for most combinations of two rare gases, when suitable mixing ratios and expansion parameters are used (see references throughout this article).
-
-First experiments on ICD in heterogeneous systems used Ne-Ar 
-clusters.\cite{barthnear} Those were followed by studies of 
-ICD-like inner-shell decays in aqueous solution.\cite{aziz,pokapanich,pokapanich2011}
-Pioneering work also showed the 
-potential for studies of the interface between a substrate and an 
-adsorbate by ICD.\cite{grieves} More detailed work on Ne-Ar 
-clusters was recently presented by some of the authors \cite{fasshauer2014}
-showing that an analysis of the ICD spectra
-allowed to decide between structural alternatives, for which the
-photoelectron data were indiscriminate.
-For this system, a detailed account of the
-photoelectron spectra with respect to structural features of the 
-mixed clusters is also available.\cite{lundwall}
-
-Several experimental techniques have been used for the study of mixed Ar-Xe clusters, most notably fluorescence spectroscopy, electron diffraction and photoelectron spectroscopy. 
-Early work focussed on the fluorescence of a single Xe atom 
-embedded in an Ar cluster.\cite{lengenprl}
-%Different sites of the dopant atom (on top of a surface, 
-%integrated in an Ar surface, inside the cluster) were 
-%distinguished by three separate bands in the fluorescence yield 
-%recorded as a function of excitation wavelength.\cite{goldberg} 
-Increasing the Xe concentration in the expansion lead to the formation of \ce{Xe2} and larger Xe complexes inside the clusters.\cite{lengen} 
-With increasing Xe content, the formation of Xe-core, Ar-shell systems with a sharp interface between the two species was shown in photoionization experiments.\cite{tchaplyguine,hoener}
-This finding was confirmed by electron diffraction.\cite{Danylchenko,Danylchenko07} 
-Always, the observed Xe content in the clusters is higher than the Xe content in the expanding gas mixture, as Xe can be condensed much easier than Ar.\cite{hoener,Danylchenko07}
-%A complementary study used photoelectron-photoion coincidence of
-%large Ar-Xe clusters, and found that after inner shell (Xe 4d, Ar 2p)
-%photoionization significant charge transfer between both species
-%occurs before the mass spectroscopic final state is reached.\cite{berrah}
-%
-More recently, photoelectron spectra of 
-small Ar-Xe clusters were analyzed, adding to the findings in 
-earlier work.\cite{lindblad} We will discuss this paper in 
-connection with our results below. 
-For completeness, we mention that Ar-Xe complexes can also be produced by passing clusters from a neat Ar expansion through a zone filled with Xe gas (`pick-up').\cite{pietrowski}
-Clusters produced such can structurally be quite different from those produced by coexpansion.\cite{lindbladpccp}
-
-A number of theoretical works on Ar-Xe clusters aimed at the prediction of minimum energy structures. 
-Most recently, these converged to structures which have the Xe atoms mainly in the interior.\cite{marques} 
-Xe was also found to diffuse into the interior of Ar clusters in molecular dynamics simulations after pick-up.\cite{Vach_1999} 
-The electronic energy levels of very small Ar-Xe clusters were calculated in ref \citenum{fasshauer} and the secondary electron spectra were simulated for
-model structures of one argon atom placed on a xenon surface \cite{Fasshauer13}.
-Interestingly, it was found that Ar 3s$^{-1}$ is stable 
-against autoionization in an ArXe dimer, but is destabilized by 
-adding further Xe atoms, or an Ar solvation shell, to the system, thereby allowing
-for combinations of argon and xenon atoms with larger interatomic distances. 
-Again, we will detail these results in conjunction with our 
-current work.
-
-The plan of our paper is as follows: We firstly delineate our experimental and theoretical methods. 
-Calculations were done for a number of model structures which were systematically varied, and are described in the following section.
-After that, we describe and discuss our theoretical results for the autoionization spectra of the model clusters.
-Experimental results are then shown and possible conclusions from comparing them to the calculations are given.
-Details on the experimental technique, and calculated spectra for a wider range of structures are given as Supporting Information.
-
-%\input{experimental}
-
-\section{Experimental}
-%
-\begin{table*}
-\caption{
-The expansion parameters used for cluster production. 
-Here, Xe$_{\rm in}$ is the molar fraction of Xe in the gas mixture before the expansion, $T$ is the nozzle temperature, and $p$ the stagnation pressure. 
-Experiments were performed with $d = 80~\mu$m (first two sections) and $d = 100~\mu$m (bottom section) conical nozzles of 15$^\circ$ half opening angle. 
-We basically have an Ar seeded expansion of Xe gas, as the freezing point of Ar is much lower. 
-$\langle N_{\rm Ar} \rangle$ and $\langle N_{\rm Xe} \rangle$ refer to cluster sizes for a pure Ar, or pure Xe expansion, respectively, at the given conditions, calculated from a scaling law.\protect\cite{hagena1981}
-We expect actual cluster sizes in-between these two limiting values. 
-Inaccuracies in the calculation of $\langle N\rangle$ due to fluctuations of the input parameters are less than 6\,\%. This figure does not include systematic errors of the empirical model.
-}
-\label{tab:cluster}
-
-\begin{tabular}{l c c c c r r}
-%
-\toprule
-  \multicolumn{2}{r}{size label}  &  Xe$_{\rm in}$ (\%)  &  $T$ (K)  &  $p$ (bar) & $\langle N_{\rm Ar} \rangle$ & $\langle N_{\rm Xe} \rangle$ \\
-%
-\midrule
-% Ar, from Marko 
-Ar & (1) & --- &  96.5  & 0.35  & 44  &  --- \\
-% Ar, from Marko 
-Ar & (2) & --- &  96.5  & 0.67  & 200  &  --- \\
-\midrule
-% 1103 676, 679
-ArXe & `S' & 1.2 &  174   & 0.32  & 4  &   74 \\
-% 1103 670
-ArXe & `M' & 1.2 &  174   & 0.49  & 11  &  199 \\
-% 1103 671
-ArXe & `L' & 1.2 &  174   & 0.68  & 23  &  431 \\
-\midrule
-% 1103 663
-ArXe & `S' & 3.0 &  172   & 0.28  & 3  &   57 \\
-% 1103 653
-ArXe & `M' & 3.0 &  172   & 0.51  & 12  &  233 \\
-% 1103 658
-ArXe & `L' & 3.0 &  172   & 0.68  & 24  &  458 \\
-\midrule
-% 1103 630
-ArXe & `S'  & 5.0 &  167  & 0.37  & 7  &  129 \\
-% 1103 640
-ArXe & `M' & 5.0 &  171   & 0.51  & 13  &  240 \\
-% 1103 629
-ArXe & `L'  & 5.0 &  167  & 0.68  & 28  &  537 \\
-\midrule
-% 1004 867 (32 eV)
-ArXe & `XL' & 2.5 &  154  & 2.12  & 995 & 18800\\
-\midrule
-% 0506 382, Keller offset ber?cksichtigt
-Xe &  & 100 & 183.5  & 0.68  & ---  &  615 \\     
-% 1004 868
-%868 & & 2.5 &  158   & 1.50  &  355 &  6090\\
-% 1004 886 (17 eV)
-%886 &  & 2.5 &  161   & 2.41  &  980 & 16770\\
-% 1004 858
-%858 &  & 5.0 &  149   & 2.50  & 1620 & 27700\\
-%
-\bottomrule
-\end{tabular}
-\end{table*}
-%
-%
-The apparatus used for the experiments consists of a supersonic molecular jet with a cooled nozzle, and a magnetic bottle spectrometer, which detects photoelectrons and secondary electrons produced after ionization with synchrotron radiation.\cite{arion}
-% Leave this citation in place to avoid Latex error
-A comprehensive description can be found in ref \citenum{arion}, and here we focus on details specific for the current experiment. 
-Commercialy obtained Ar and Xe gas was filled into 
-separate cylinders up to pressures suitable for producing a certain mixing ratio. The gases were then allowed to mix before the expansion. 
-Expansion parameters are given in Table \ref{tab:cluster}. 
-Similar expansion conditions are further referred by the labels `S'-`XL', as given in the Table.
-
-Prediction of the sizes of clusters from a supersonic expansion mainly rests on empirical scaling laws,\cite{hagena1981} which have been the subject of some discussion.
-Moreover, such scaling laws originally were derived only for pure gas expansions.
-A recent investigation of cluster sizes in a mixed Ar-Kr expansion yielded a revised scaling law, which essentially amounts to the use of a weighted average over the atom-specific parameters of the two gases.\cite{danylchenko2015}
-Although the analogy to our case is not complete, as phase segregation occurs in Ar-Kr to a much lesser extent,\cite{Vach_1999,lundwall_arkr} we expect scaling law cluster sizes between the values calculated for Ar and Xe.
-Recent analyses of photoionization spectra suggest that mean sizes arrived at by scaling laws are smaller than the actual size, at least for rare gas clusters in the range $\langle N\rangle < 1000$.\cite{bergersen,hergenhahnprb,foerstel_arg2_2011}
-For the expansion conditions labelled `S'-`L', we therefore expect that the scaling law estimates are a lower boundary for the actual cluster size.
-
-The expansion chamber for the supersonic jet is separated from the interaction chamber by a non-magnetic, conical skimmer with an opening of 1~mm in diameter (Beam Dynamics). 
-At few cm distance behind the skimmer, the cluster jet was crossed by synchrotron radiation from the BESSY electron storage ring at Helmholtz-Zentrum Berlin. 
-Electrons were detected by a short `magnetic bottle' time-of-flight spectrometer, that has been described earlier.\cite{mucke_review}
-Due to its large collection angle, this instrument is particularly suited for experiments that employ electron-electron coincidence detection.
-Data were recorded in two different beamtimes at the UE112-PGM-1 (small and medium sized clusters, first two sections in Table \ref{tab:cluster}) and at the TGM-4 beamline (large clusters, last section in Table \ref{tab:cluster}).
-Linearly, horizontally polarized radiation was used. 
-The storage ring was operated in single bunch conditions.
-Spectra of pure Ar clusters shown for comparison are from ref \citenum{foerstel_arg2_2011}, and a spectrum of pure Xe clusters was recorded with the set-up described in ref \citenum{hergenhahnprb}.
-
-The entrance aperture and drift tube of the magnetical bottle spectrometer can be independently biased to influence the electron flight times. 
-For the data shown here, slightly positive bias voltages were used (+1.8 V to +2.2 V) in order to have all electrons arriving at the detector within one BESSY single bunch period (800 ns). 
-The detection efficiency was determined as 0.6, with the method outlined in ref \citenum{mucke_review}.
-Data were converted from flight times to kinetic energy by measuring calibration data for atomic photolines of known binding energy.
-The systematical uncertainty of this procedure may lead to a common shift of all experimental kinetic energy data shown in this article of up to 30~meV.
-
-The high detection efficiency of the instrument is a pre-requisite for measuring two-electron emission processes, such as photoelectron emission followed by ICD or ETMD, by using electron-electron coincidence detection.
-This allows to filter the full electron spectrum for contributions arising after emission of an Ar 3s photoelectron.
-ICD/ETMD spectra presented here are based on this method, which has been explained earlier.\cite{mucke_review,Foerstel_phd}
-Technical details and full electron-electron coincidence spectra are given in the Supporting Information.
-
-%\input{theory}
-\section{Theoretical Approach}
-%
-Experimental coincidence spectra are given by the multitude of
-kinetic energies $E_{\rm sec}$ of the secondary electron
-and the intensities of the peaks. The latter is proportional to the
-probability of the decay as well as the theoretically determinable
-decay width $\Gamma=\frac{\hbar}{\tau}$,
-which is inversely proportional to the lifetime $\tau$ of the decay process.
-The manifold of the
-secondary energies and decay widths will therefore compose the electron-electron
-coincidence spectrum.
-In case of noble gas clusters
-with given geometrical structures three aspects have to be taken into account:
-different decay mechanisms, the possibility to decay with multiple
-interaction partners and different decay channels $\beta$ within
-each decay mechanism.
-At the current stage of development we need to neglect the nuclear dynamics which
-additionally might play an important role.
-
-%We are interested in describing the electron emission spectra of excited states in clusters, that where measured by the electron-electron coincidence method in our experiments. 
-%In our theoretical description, these will be composed of multiple transitions, each characterized by a kinetic energy $E_{\rm sec}$ of the secondary electrons, and the intensity of the peak.
-%The latter is proportional to the probability of the decay, represented here by the decay width $\Gamma_\beta = \hbar/\tau_\beta$, where $\tau_\beta$ is the lifetime due to the respective transition.
-%The total decay width $\Gamma$ is the sum of all partial $\Gamma_\beta$.
-%In case of noble gas clusters with a given geometrical structure, three aspects have to be taken into account:
-%different decay mechanisms, the contribution of different cluster sites to the respective decay, and the existence of different decay channels within each decay mechanism.
-%At the current stage of development we have to neglect the nuclear dynamics, which
-
-This means, for the evaluation of the decay width we are dealing with a sum over three different indices: 
-For a given structure it is most convenient to
-start with a decomposition of the system into interaction partners of
-the different relevant decay mechanisms, i.e. pairs (combination of two atoms regardless
-of their internuclear distance) for the ICD and triples (combinations of three atoms)
-for the ETMD(3).
-These atoms do not necessarily need to form bonds between each other or
-even be close, but they are characterized according to fixed internal
-coordinates. 
-Each pair and each triple leads to a decay spectrum that can be described by the energy of the secondary electron and the decay width, which is in first order of approximation independent of other atoms present in the cluster.
-In the following, this approach will be called model of pairs and triples.
-
-%Decomposing every system into pairs and triples of atoms is a very useful
-%first order approximation to both the investigation of energies and
-%decay widths of a larger system. Pairs and triples are combinations of
-%two and three atoms, respectively.
-
-In order to determine, whether a channel $\beta$ for a given geometry and decay
-mechanism is open, i.e., whether it is in accordance with energy conservation,
-knowledge of the energies of the initial and the final states, $E_{\rm in}$ and $E_{\rm fin}$, of
-the corresponding processes is necessary.
-If the channel
-is open, the excess energy is carried away by the emitted electron
-in form of its kinetic energy $E_{\rm sec}$. These energies in the model
-of pairs and triples can be approximated by
-
-\begin{align}
- E_{\rm in}        &= SIP(X_{\rm in}) \label{equation:E_in}\\
- E_{\rm fin}^\beta &= SIP(X_{D}^\beta) + SIP(X_{E}^\beta) + \frac 1d
-           \label{equation:E_fin}\\
- E_{\rm sec}^\beta &= E_{\rm in}^\beta - E_{\rm fin}^\beta \label{equation:E_sec}
-\end{align}
-where $X_{\rm in}$ denotes the initially ionized atom and
-$X_{D}$ and $X_{E}$ describe the electron donating atom and electron
-emitting atom, respectively.
-$\beta$ denotes the decay channel characterized by the quantum numbers of the ionized atoms in the pairs and triples, $SIP(X^\beta)$ the single ionization potential of vacancy $\beta$ in atom $X$ and $d$ the interatomic distance between the atoms $X_{D}$ and $X_{E}$.
-Atomic units are used.
-The initially ionized atom $X_{\rm in}$ can
-coincide with one or both of
-the final state atoms
-$X_{D}$ and $X_{E}$.
-The distribution of the vacancies over the different
-atoms determines the kind of electronic decay process at hand. Hence, in an
-Auger process all three atoms coincide, for an ICD process $X_{\rm in}$
-coincides with $X_{D}$, for an ETMD(2) process $X_D$ and $X_E$ coincide
-and for an ETMD(3) process
-all ionized states are located on different atoms.
-
-\begin{figure}[h]
- \centering
- \includegraphics[width=\columnwidth]{channel_open_ICD.pdf}
- \caption{Illustration of channel opening: Initial (Ar3s$^{-1}$)
-          and final state (Ar3p$^{-1}$Xe5p$_{3/2}^{-1}$ and
-          Ar3p$^{-1}$Xe5p$_{1/2}^{-1}$) energies
-          for ICD in ArXe pairs as a function of 
-          internuclear distance, using eq. (\ref{equation:E_fin})
-          and the experimental ionization
-          potentials given
-          in Table \ref{tab:valence}. When the final state energy is lower
-          than the initial state energy the corresponding channel
-          is open. We call the distance at which the energies are equal
-          the `channel opening distance'. If the curves do not cross, the
-          corresponding channel is closed.}
- \label{figure:channel_open_ICD}
-\end{figure}
-
-The electron emitted by autoionization has the kinetic energy $E_{\rm sec}$. 
-If the calculated value of $E_{\rm sec}$ is negative,
-the final state energy is higher than the initial state energy and the        
-process is energetically not accessible. Hence, the corresponding channel     
-is closed, as shown in Figure \ref{figure:channel_open_ICD} for the
-Ar3p$^{-1}$Xe5p$_{1/2}^{-1}$ final state. Related to
-the opening of each channel is an internuclear distance which we will call 
-\emph{channel opening distance} in the following.
-
-This {\latin ad hoc} approach allows to easily correct for energetic shifts of ionization potentials as observed in larger clusters by adding experimentally or theoretically determined energy shifts $\Delta E(X_{I}^{\beta})$ for a given vacancy $I={\rm in},D,E$ and channel $\beta$.
-This yields the working expression for the kinetic energy of the secondary electron:
-
-\begin{equation}
- E_{\rm sec}^\beta = SIP(X_{\rm in}) + \Delta E (X_{\rm in})
-               - SIP(X_{D}^\beta) - \Delta E (X_{D}^\beta)
-               - SIP(X_{E}^\beta) - \Delta E (X_{E}^\beta)
-               - \frac 1d .
-\end{equation}
-
-The total decay width $\Gamma$ is given by the sum over the decay widths
-of all decay mechanisms. In case of the ArXe clusters we only consider
-ICD and ETMD(3), because the ETMD(2) pathway is energetically not accessible:
-
-\begin{equation}
- \Gamma = \Gamma_{\rm ICD} + \Gamma_{\rm ETMD} .
-\end{equation}
-
-These are given by the sum over the decay widths of all pairs $i$ for the
-ICD and all triples $j$ for the ETMD(3), respectively, and over all channels $\beta$:
-%
-\begin{align}
- \Gamma_{\rm ICD}  &= \sum\limits_{i,\beta} N_{{\rm ICD},i}  \, \Gamma_{{\rm ICD},i,\beta},\\
- \Gamma_{\rm ETMD} &= \sum\limits_{j,\beta} N_{{\rm ETMD},j} \, \Gamma_{{\rm ETMD},j,\beta}.
-\end{align}
-Here, $N_{{\rm ICD},i}$ and $N_{{\rm ETMD},j}$ denote the number of geometrically
-equal pairs and triples in a given cluster structure. The total number of pairs
-reads
-$N_{{\rm ICD}} = N_{\rm in} \cdot N_{D/E} = N_{\rm Ar} \cdot N_{\rm Xe}
- = \sum\limits_i N_{{\rm ICD},i}$ and the number of triples is
-$N_{{\rm ETMD}} = N_{\rm in} \cdot N_{D/E} (N_{D/E} - 1) = N_{\rm Ar} \cdot N_{\rm Xe} (N_{\rm Xe} - 1)
- = \sum\limits_j N_{{\rm ETMD},j}$.
-The numbers of geometrically equivalent pairs $N_{{\rm ICD},i}$ and triples $N_{{\rm ETMD},j}$
-strongly depend on the structure of the cluster. From these relationships
-it can be seen that a higher xenon content in the cluster statistically
-favours ETMD(3) over ICD.
-
-In previous work \cite{Fasshauer13,Fasshauer_thesis} we have shown that
-the decay width for a single pair or triple for a distinct channel $\beta$
-following Wentzel \cite{Wentzel27}, Feshbach\cite{Feshbach58,Feshbach62}
-and Fano,\cite{Fano61}
-%
-\begin{equation}
- \Gamma_{\beta}(E_{\rm res}) = 2\pi \left|
-                           \braket{\Phi_{\rm in}| H_f |\chi_{\beta}}
-                           \right|^2,
-\end{equation}
-%
-can be approximated by its asymptotic behaviour
-%
-\begin{equation}
- \Gamma_{{\rm ICD},i,\beta} = (2J_{\rm in}+1)\, \frac{3c^4}{8\pi}\,
-                        \sum\limits_{M_{in}'}
-                        \left| \left(
-                        \begin{array}{ccc}
-                        J_A'  & 1        & J_A\\
-                        -M_A' & M_A'-M_A & M_A
-                        \end{array}\right) \right|^2
-                        \frac{\sigma^{(X_E)}(\omega_{vp,\beta})}
-                        {R_i^6 \, \omega_{vp,\beta}^4 \tau_{in,\beta}},
-\end{equation}
-%
-where $J_A$, $J_A'$ and $M_A$, $M_A'$ denote the total angular momentum of the
-initially ionized atom (which is the same as the electron donor atom) in the
-initial and final state, respectively,
-and
-%
-\begin{align}
- \Gamma_{{\rm ETMD},j,\beta} =& \frac{c}{\pi} \sum\limits_{m,M_{in,D'}}
-                        \frac{\Theta_{m,k}(\alpha_j) \sigma^{(X_E)}(\omega_{vp,\beta})
-                              \left| <\tilde{D}_{m,j,\beta}(M_{in,D'})>\right|^2}
-                         {R_j^6 \omega_{vp,\beta}}\\
-               =& \frac{c}{\pi R_j^6}
-               \sum\limits_{M_{in,D'}}
-               \left( \left| <\tilde{D}_{x,j,\beta} (M_{in,D'}) > \right|^2
-                 (2+ \sin^2\alpha_j)
-               + \left| <\tilde{D}_{z,j,\beta} (M_{in,D'}) > \right|^2
-                 (1+\cos^2\alpha_j) \right) \nonumber \\
-           & \times\, \frac{c\sigma^{(X_E)}(\omega_{vp,\beta})}{\omega_{vp,\beta}}
-\end{align}
-%
-depending on 
-experimental properties
-of atoms, like the ionization cross sections
-$\sigma^{(X_E)}(\omega_{vp,\beta})$, radiative lifetimes of the initially
-ionized state $\tau_{in,\beta}$ and the excess energy transferred to the
-emitting atom (the energy of the virtual photon) $\omega_{vp,\beta}$
-and calculated dipole transition moments $\tilde{D}_{m,j,\beta}$, only.
-Here, $\Theta_{m}(\alpha_j)$ is a function depending on the angle $\alpha_j$
-of the triple and the direction of the dipole
-transition moment $m$
-(compare ref \citenum{Fasshauer13}).
-
-In this work we evaluate the secondary energies and decay widths with
-the programme HARDRoC\cite{HARDRoC,fasshauer2014} using the
-experimental ionization energies of Table \ref{tab:valence}
-and data from the literature given in Tables II and III.
-This choice is identical to the one made in ref \citenum{Fasshauer13}.
-
-%\input{structures}
-\section{Cluster Structures}
-
-From the experimental results we can obtain two hints for the cluster
-structure: the minimum size and the xenon content. In the following we will 
-use these to construct representative cluster structures, for which we will 
-simulate the ICD and ETMD spectra. At this point we put in a variety of
-structures, in order to learn about general structure-spectrum relations
-and therefore being able to
-exclude some of them by comparison of
-the ICD and ETMD spectra to the experimental ones.
-
-In our previous study\cite{Fasshauer13} the ArXe clusters were assumed
-to be large, having more than 1500 atoms. The model structures assumed
-an fcc structure and not an icosahedral structure, which is energetically
-favoured for small clusters.
-Most estimated cluster sizes given in Table \ref{tab:cluster} are much smaller.
-We use the estimated number of atoms for a pure Ar expansion as the lower limit for the actual cluster size and start our search for model structures from there.
-%
-%Additionally,
-%the expectation value for the number of xenon atoms relies on a pure
-%xenon gas. Since the xenon content in the mixed gas is much lower, also
-%the number of xenon atoms can be expected to be by far less. We therefore
-%start from the estimated number of atoms in the cluster after expansion
-%of pure argon gas.
-%We therefore rethink the possible cluster structures.
-%Furthermore, the theoretical prediction did not match the experimental results.
-%Since the spectra are strongly depending on the cluster structure as shown in
-%\cite{fasshauer2014}, the underlying structure seems not to fit and hence
-%we rethink the possible cluster structures.
-%
-For the smaller clusters measured,
-these expectation values range from \unit[3--21]{Ar atoms}. 
-The cluster sizes for expansion of a mixed gas are unknown, but
-for xenon as the second component a larger size is expected compared to a
-pure argon expansion, due to the higher polarizability
-and hence larger cohesive energy of xenon. All clusters
-contributing to the coincidence spectrum
-contain at least one xenon atom, as otherwise decay by ICD or ETMD is energetically not allowed.
-
-In a gas expansion a range of clusters sizes with different structures is produced. 
-However, for small rare gas clusters consisting of less than approximately \unit[1000]{atoms} so-called \emph{islands of stability} were found.\cite{haberland}  
-In mass spectra, clusters with mass numbers corresponding to icosahedral shapes had an abundance that was (slightly) enhanced over other sizes. 
-We therefore started from icosahedral structures and constructed mixed cluster structures by substitution of individual atoms with one or the other kind (Ar or Xe), or added individual atoms close to the desired position within a given structure.
-After that, the cluster structures were optimized using the unified force
-field implemented in the 
-Avogadro programme (version 1.1.0) \cite{Avogadro,Hanwell12} to give local
-minimum structures.
-All cluster structures are listed in Table \ref{table:theo_gammas}.
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{cluster_2_overview.pdf}
- \caption{Cluster structures composed of 13 argon atoms and two additional xenon
-          atoms on different surfaces of the argon icosahedron, varying in Xe-Xe distance:
-          (a) closest possible, (b) middle, (c) furthest away. They refer to
-          numbers 9--11 in Table \ref{table:theo_gammas}.}
- \label{figure:cluster_2_overview}
-\end{figure}
-%
-\begin{figure}[h]
- \centering
- \includegraphics[width=8.5cm]{cluster_3_overview.pdf}
- \caption{Cluster structures derived from a 55 atom icosahedral structure:
-          (a) one xenon atom on the surface, (b) six xenon atoms inside a 55 atoms cluster,
-          grouped on one side, (c) six xenon atoms distributed randomly
-          in a 55 atoms cluster. They refer to numbers 12, 18 and 19
-          in Table \ref{table:theo_gammas}.}
- \label{figure:cluster_3_overview}
-\end{figure}
-
-As discussed in the introduction, the small clusters will likely
-deviate from a core-shell structure with a xenon core surrounded
-by argon shells, as observed for large clusters.\cite{tchaplyguinearxe,Vach_1999} We therefore start from
-argon clusters of 13 or 55 atoms, and modify them in one of the following
-ways:
-%
-\begin{itemize}
- \item add one xenon atom on top of a surface / edge / vertex of
-       the argon core, with an example shown in
-       Figure \ref{figure:cluster_3_overview}a
-       (one additional xenon atom
-       on top of a surface of a \unit[55]{atom} argon core)
-       (Table \ref{table:theo_gammas}, \#6--8, \#12--14),
- \item substitute one argon atom in a surface / edge / vertex position
-       (Table \ref{table:theo_gammas}, \#15--16),
- \item substitute one or two argon atoms in the core of the argon cluster
-       by xenon atom(s) for the simulation of the core-shell structures
-       (Table \ref{table:theo_gammas}, \#1--3),
- \item add two xenon atoms on top of surfaces of a 13 atoms argon core
-       in different relative positions (see Figure
-       \ref{figure:cluster_2_overview}),
-       in order to achieve a xenon content in the cluster close to the
-       measured one (see below)
-       (Table \ref{table:theo_gammas}, \#9--11),
- \item substitute six argon atoms of a 55 atoms argon cluster by xenon
-       atoms either grouping them or distributing them througout the cluster
-       (see Figure \ref{figure:cluster_3_overview}b and c) in order to
-       achieve a xenon content in the cluster close to the measured one
-       (Table \ref{table:theo_gammas}, \#18--19).
-\end{itemize}
-
-These structures were then optimized using force field methods.
-%
-Furthermore, for comparison with the largest measured ArXe clusters, we constructed also larger core-shell structures (Table \ref{table:theo_gammas}, \#4--5).
-
-%\input{theo_results}
 \section{Theoretical Results
@@
 \clearpage
-
-%\input{exp_results}
-\section{Experimental Results}
-\label{sec:exp_results}
-%
-%
-\begin{table}
-\caption{Properties of the outer valence spectra of mixed ArXe clusters. 
-Spectra of pure Ar and Xe clusters are included for reference. 
-All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV). 
-Binding energies $\EB$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit. 
-The average Xe content of the cluster ensemble, Xe$_{\rm cl}$, was determined from the areas of the respective photolines, corrected by their atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}.
-Uncertainties are estimated as $\pm$3\,\% for the Xe content and 0.05~eV for the binding energies. 
-The row labelled `(th.)' gives the binding energies used in the simulations of this paper, and the last row their atomic counterparts. 
-Values for Ar 3p in the last row refer to the fine structure states.
-\label{tab:valence}}
-\begin{tabular}{ l c c c c c c c c}
-%
-\toprule
- \multicolumn{2}{r}{size} &  Xe$_{\rm in}$& $\EB$ (eV)& $w$ (eV)& \multicolumn{2}{c}{$\EB$ (eV)}  & $w$ (eV) &  Xe$_{\rm cl}$ \\
-%
- \multicolumn{2}{r}{(label)}&  (\%) & Ar 3p & Ar 3p & Xe 5p$_{1/2}$ &  Xe 5p$_{3/2}$ & Xe 5p$_{3/2}$  &  (\%) \\
-\midrule
-% Ar, from Marko
- Ar & (1) &&  15.3  &  1.1 & & & &  \\
-% Ar, from Marko 
- Ar & (2) &&  15.1  &  1.3 & & & &  \\
-%
-%  columns in the following: energies c.g. 51-plt-oval, widths Marko Diss., Xe content Marko Diss
-% 1103 676, 679
- ArXe & S &1.2 & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
-% 1103 670
- ArXe & M &1.2 & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
-% 1103 671
- ArXe & L &1.2 & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
-% 1103 663
- ArXe & S &3.0 & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
-% 1103 640
- ArXe & M &5.0 & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
-% 0506 
- Xe &  & & & & 12.76 & 11.19 & 1.18 & 100\\
-%
-\midrule
-%
-%  1004  886  (UHe, c.g. + roi values)
- ArXe & XL &2.5 & 15.15 & 1.3 & 12.59 & 11.01 & 1.24 & 19\\
-%
-\midrule
-% Date: Wed, 20 Jan 2016 11:27:39, From: Elke Fa?hauer <elke.fasshauer@uit.no>
- Ar, Xe & (th.) && 15.3 && 13.0 & 11.5 &&\\
-%
- \multicolumn{2}{l}{(atomic)\cite{velchev,sansonetti}} && 15.76|15.94 && 13.43 & 12.13 &&\\
-%
-\bottomrule
-\end{tabular}
-\end{table}
-
-\subsection{Outer valence spectra}
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_oval_1.pdf}
- \caption{
-Outer valence photoelectron spectra of mixed Ar-Xe clusters, in comparison to the pure species. 
-(a) shows the outer valence region of homogeneous Ar and Xe clusters, respectively (see text for details). 
-The two lower panels show spectra of the mixed species with different mean size. 
-Sharp lines marked `m' (for `monomer') result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states. 
-Labels in (b) and (c) give the Xe content in the expanding gas mixture (Xe$_{\rm in}$), which is lower than the Xe content observed in the heterogeneous clusters (Xe$_{\rm cl}$). 
-The photon energy was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
-%{\color{red}{Die Stabilisierung der Xe-bulk Atome ist in den gemischten Cluster
-% höher als in den gemischten Clustern. Das ist ungewöhnlich. Habt ihr hier
-% verschiedene CLustergrößen?}}
-}
- \label{figure:oval1}
-\end{figure}
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_oval_2.pdf}
- \caption{
-Outer valence photoelectron spectra of mixed Ar-Xe clusters from gas mixtures with different Xe concentration. 
-For better visibility, a scaling factor is applied to the Xe part of the spectrum in panel (a).
-See Figure \ref{figure:oval1} and text for details.
-}
- \label{figure:oval2}
-\end{figure}
-
-Figure \ref{figure:oval1} shows the outer valence spectra of small and large ArXe clusters, compared to clusters of the pure gases. 
-Qualitatively similar spectra have been published without detailed discussion in ref \citenum{lindblad}.
-Differences are seen in particular for the Ar component. 
-In pure Ar clusters, outer valence photoionization leads to a broad band, caused both by spin-orbit coupling and crystal field splitting. 
-The relative importance of these two mechanisms remains under debate.\cite{hergenhahnprb,rolles,foerstel_arg1_2010} 
-For larger clusters (e.g.
-$\langle N\rangle = 190$, black trace), the maximum at low binding energies becomes more pronounced, and is identified with emission from the cluster interior.\cite{hergenhahnprb,rolles}
-At the particular photon energy selected here, atop of this band a sharp feature is also visible (in Figure \ref{figure:oval1} at a kinetic energy of about 1.8 eV).
-For larger clusters (above $\langle N\rangle \approx 100$), over a range of photon energies of about 3 eV, its appararent binding energy changes in a way which is reminiscent to photoemission of crystalline bulk matter (`dispersion').\cite{foerstel_arg1_2010,foerstel_arg2_2011}
-
-Ar 3p spectra of the smaller mixed clusters (Figure \ref{figure:oval1}c, Figure \ref{figure:oval2}) show neither of these traits.
-Rather, the Ar band is symmetric, less wide than in the pure clusters and at a higher binding energy.
-Even for very large clusters (Figure \ref{figure:oval1}b) the asymmetry of the 3p band and the `dispersing feature' do not appear.
-We characterize the spectral shape by giving a single value for the Ar 3p binding energy, and the FWHM of the feature.
-Values for different expansion parameters, and for both Ar and Xe valence lines, are collected in Table\ \ref{tab:valence}.
-
-We find experimentally that clusters we have produced have a Xe content Xe$_{\rm cl}$ between 10\,\% and 50\,\%.
-A slight decrease of the binding energy with cluster size is seen for all outer valence lines, and is attributed to a larger final state polarization energy in larger clusters.
-
-For further interpretation of the shape of the Ar peaks we refer to photoemission spectra of condensed Ar monolayers, measured in several settings.\cite{jacobi,jacobi2}
-Spectra were reported for physisorption of Ar on two different metal single crystal substrates, and for Ar atop of a Xe spacer layer adsorbed on the metal.
-While the binding energy depends on the substrate, the spectral shape is very similar in all cases. 
-Most spectra were recorded for emission along the surface normal, and show a double peak split by about 0.5 eV, leading to a structure with $w$ about 1 eV.
-Although the splitting is larger than the gas phase fine structure split of 0.18 eV, the pertaining states have been assigned to Ar 3p$_{1/2}$ and 3p$_{3/2}$.
-A crystal field splitting of the 3p$_{3/2}$ state has been assumed to be also present, but with a smaller value of 0.1-0.2 eV, approx.\cite{jacobi2} 
-The spectrum clearly changes when going to an emission angle of 40$^\circ$ with respect to the surface normal (Figure 2 in ref \citenum{jacobi2}).
-The higher binding energy peak significantly loses in intensity, and the spectrum is now dominated by a single peak comprising both crystal field split substates of Ar 3p$_{3/2}$, with a FWHM ($w$) of only 0.4 eV.
-As our measured spectrum is comprised of contributions recorded under all emission angles with respect to the cluster surface, grazing emission will be the rule.
-We therefore believe that the arguments given above make it plausible that only a single peak is observed in all our spectra.
-
-Emission from the Xe 5p state shows a much larger fine structure splitting then from the Ar 3p state; it dominates the spectrum even in clusters (where other broadening mechanisms are also present).
-The shift of the cluster bands with respect to the monomer lines in the largest mixed clusters we have probed (Figure \ref{figure:oval1}b) are similar to the ones in the pure Xe spectrum, the scaling law size of which is at somewhat more than five filled shells.
-This indicates an approximate upper limit for the size of the Xe core in our mixed clusters, as their binding energy shift might be somewhat higher than the one in pure clusters, due to polarization of covering Ar layers.
-Xe cluster features in the spectra of mixed clusters appear less asymmetric than the pure Xe spectrum, and also less asymmetric as some the ArXe spectra shown in ref \citenum{lindblad}.
-This might be caused by the difference in photon energy ($h\nu = 90$ eV in ref \citenum{lindblad} and for the pure Xe spectrum, $h\nu = 32$ eV for the mixed ArXe spectra in this work).
-% For the mixed clusters, the Xe band broadens and shifts towards lower binding energy for larger size clusters.
-%For pure Xe clusters, an asymmetry observed in the Xe 5p$_{3/2}$ part has no counterpart in the respective spectra from the mixed clusters.
-%This might be caused by the difference in photon energy, as can be seen from a comparison to literature spectra (ArXe at $h\nu = 90$ eV in ref \citenum{lindblad}, Xe at $h\nu = 20$ eV in ref \citenum{rolles}).
-%For the largest clusters, the nominal size yielded from the jet parameters applied to a pure Xe expansion would correspond to clusters in which bulk atoms far outweigh those on the surface.
-%At least for the 5p$_{1/2}$ photoelectron line, this would be seen as a clear asymmetry towards the low binding energy side, which is not observed in our spectra.
-
-In Figure \ref{figure:oval2}, we compare the outer valence spectra of clusters with similar expansion conditions, but different composition of the gas mixture.
-A Xe-rich mixture obviously leads to clusters with more intense Xe photolines, but besides that the main change consists in a narrowing of the Ar band.
-A comparison with the Ar monomer features (clipped in the Figure) also shows an increased degree of condensation for the Ar gas in the expansion.
-
-For the smallest clusters we have produced, a possible model is provided by calculated minimum energy structures of Ar$_N$Xe$_{38-N}$ (Figure 7 in ref \citenum{marques}).
-We there see that for a Xe content of less than 60\,\%, core-shell systems are {\it not} formed, and although the Xe atoms tend to connect, the degree of Ar-Xe mixing is large.
-While for low Xe content (approx. 10\,\%), some Ar atoms have only Ar nearest neighbours, for larger Xe content all Ar atoms seem to see both Ar and Xe nearest neighbours.
-We believe this leads to the Ar 3p narrowing pointed out above.
-For Figure \ref{figure:oval2}, possibly, some clusters of our ensemble already are in the core-shell regime, which would lead to an even lower 3p width.
-
-For the largest clusters we have produced (Figure \ref{figure:oval1}b), the low binding energy of the Xe lines and the broadening of the Ar feature without appearance of the `bulk Ar'-maximum, supports formation of a Xe core covered by at least two layers of Ar.
-If the scaling law size for a pure Ar expansion is taken as the lower limit for the cluster size, from the observed Xe content we arrive at clusters composed of a Xe core with four layers, covered by three layers of Ar (see Supporting Information).
-
-Finally, comparing Figure \ref{figure:oval2} to Figure \ref{figure:oval1} reveals that much larger changes in the valence emission spectra occur by changes in size than by changes of the (relative) Xe content.
-This finding is supported by the spectra shown in ref \citenum{lindblad}.
-%
-%
-\subsection{Inner valence spectra}
-%
-We now focus on the Ar inner valence (3s) vacancy states. 
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.8cm]{figure_ival.pdf}
- \caption{
-Photon excited electron spectra of mixed Ar-Xe clusters in the inner valence region.
-Symbols show the Ar 3s photoline from clusters (`cl') and uncondensed Ar monomers (`m'), atop of a background resulting from inelastic intracluster scattering of outer valence photoelectrons (`excitonic satellites').\protect\cite{hergenhahn2002}
-The photon energy was $h\nu = 32$ eV.
-Panel (a) shows all electrons accumulated.
-For the same conditions, in panel (b) we only show electrons that were detected in coincidence with a secondary electron of lower kinetic energy.
-The black solid trace in (a), and red solid trace in (b) result from a least squares fit to the cluster part of the spectrum. 
-The red solid trace in (a) is the fit shown in (b), divided by the detection efficiency of the spectrometer of 0.6.
-Panels (c) and (d) show the same type of data for smaller clusters with a lower Xe content.
-See text for details.
-\label{figure:ival}
-}
-\end{figure}
-
-Figure\ \ref{figure:ival} shows the Ar part of the inner valence spectrum for representative ArXe clusters. 
-The total photoelectron signal looks similar to literature spectra for pure Ar clusters.\cite{feifel,zhang} 
-A low energy tail seen for the Ar 3s monomer line results from the transmission properties of the electron spectrometer, together with the strongly positive angular distribution parameter of this line.\cite{zhang,kruit}
-The Ar 3s cluster line shows no splitting into bulk and surface components, different to the literature on pure clusters but in agreement with our discussion of the outer valence spectra. 
-The binding energy of the cluster line has values between 28.85 and 28.70 eV for all cluster ensembles with size label S-L, and 28.67 eV for the largest clusters measured. 
-A small, but systematic decrease of the binding energy is observed when the cluster size is increased. 
-The value assumed in the simulations is 28.7 eV.
-
-If we produce a spectrum only from those electrons recorded as part of a two-electron coincidence (electron pair with kinetic energies ($e_1,e_2$)) the apparent intensity drops (compare panel b to a, and d to c in Figure \ref{figure:ival}).
-This can partly be attributed to the finite detection efficiency of the spectrometer. 
-Moreover, the monomer part of the Ar 3s signal completely disappears, as 3s photoionization of an uncondensed Ar atom in the gas jet cannot lead to emission of a second electron. 
-Further features of these diagrams and the least squares fits shown in the Figure are discussed below.
-%
-%
-\subsection{ICD/ETMD spectra}
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_icd_12.pdf}
- \caption{
-Energy spectrum of all coincident secondary (ICD or ETMD) electrons of kinetic energy $e_2$ pertaining to primary electrons of kinetic energy $e_1$ in the Ar 3s binding energy region. 
-Spectra were recorded with a photon energy of $h\nu = 32$~eV. 
-Black error bars show the data points for the smallest clusters measured (`S'), two larger clusters sizes are shown by the red and blue traces. 
-Error bars for the latter are smaller than the ones shown and have been omitted.
-For better comparison, all spectra are shown area-normalized. 
-}
- \label{figure:icd_12}
-\end{figure}
-%
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_icd_l.pdf}
- \caption{
-Energy spectrum of all coincident secondary (ICD or ETMD) electrons, kinetic energy $e_2$, for clusters of the same size, but from gas mixtures with different Xe concentration.
-See Figure \protect\ref{figure:icd_12} for details.
-}
- \label{figure:icd_l}
-\end{figure}
-%
-In Figure \ref{figure:icd_12}, we show the spectra of ICD/ETMD electrons pertaining to emission of an Ar 3s cluster photoelectron. 
-Due to their low kinetic energy, without use of a coincidence method they could hardly be separated from the background of inelastically scattered photoelectrons.\cite{mucke}
-This and the following Figure constitute the central experimental result of the article.
-Spectra recorded at $h\nu = 34$ eV as a cross-check quantitatively agree to those shown here.
-This underpins our assignment of this intensity to an autoionization process.
-Further details on the data acquisition and analysis methodology, as well as the 34~eV spectra, are given in the Supporting Information.
-
-Spectra for the three different cluster sizes in Figure \ref{figure:icd_12} are significantly different: Spectra for the larger clusters acquire more intensity in the 1-1.5 eV region and have less intensity for energies below 0.5 eV.
-In contrast to that, the ICD/ETMD spectrum hardly varies when the composition of the expanding gas mixture, and with that the relative Xe content of the clusters, is changed (Figure \ref{figure:icd_l}).
-The full set of ICD/ETMD spectra is shown as Supporting Information.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_eff.pdf}
- \caption{
-Efficiency of the decay of Ar 3s ionized states in ArXe clusters by emission of a secondary electron via ICD or ETMD.
-Values are arranged by Xe content of the initial gas mixture (`+' symbols: 1.2\,\%, asterisk: 3\,\%, triangle: 5\,\%).
-Symbol sizes indicate the photon energy (large symbols: 32 eV, small: 34 eV), and color indicates the cluster size (black symbols: S, red: M, blue: L).
-See text for details.
-}
- \label{figure:eff}
-\end{figure}
-%
-We now discuss which fraction of Ar 3s vacancy states relaxes via ICD or ETMD.
-A method to derive this information has been established by some of us.\cite{foerstel_2013}
-Briefly, we correct the intensity of the Ar 3s photoline in the coincident spectra by the detector efficiency, and divide it by the total (coincident and non-coincident) Ar 3s intensity.
-The result gives the branching ratio of decay via ICD/ETMD vs. the sum of all channels, including those not involving electron emission.
-(If all Ar 3s vacancies decay by emission of another electron, the coincident and non-coincident count rate differ only by the probability for the spectrometer to actually detect the secondary electron.
-This figure has been determined as 0.6 for this data set, in the same way as discussed earlier.\cite{mucke_review})
-To arrive at quantitative results, we have performed least squares fits of the non-coincident and coincident $e_1$ spectra.
-The fits assumed one or two Gaussian peaks, resp., atop of a background modelled by two more Gaussian curves with very large widths.
-The peak pertaining to the Ar 3s cluster photoline, with the background added, is shown by the black solid trace in Figure \ref{figure:ival}a and red solid trace in Figure \ref{figure:ival}b.
-Moreover, the line labelled `c.fit/det.' shows the fit to the coincident events, corrected by the detection efficiency, and plotted atop of the non-coincident intensity. 
-This virtually agrees with the fit to the total spectrum in Figure \ref{figure:ival}a, but not in \ref{figure:ival}c. 
-The corresponding figure for the ICD/ETMD efficiency comes out as one for \ref{figure:ival}a, and significantly smaller than one for \ref{figure:ival}c.
-Figure \ref{figure:eff} shows all results of this analysis.
-The error in the autoionization efficiency shown is mainly determined by uncertainties in the peak/background separation.
-%(Our choice for the background shape is shown in Figure \ref{figure:ival}.)
-For the gas mixture with a Xe$_{\rm in}$ of 1.2\,\%, we therefore show results from fits using two different choices of the background shape in Figure \ref{figure:eff}.
-Statistical errors are much smaller than the differences between the pairs of values arrived at such.
-
-We found an Ar 3s autoionization efficiency which, for clusters with the lowest Xe content (Xe$_{\rm cl}$ approx.
-10-12\,\%), is smaller than unity, and further decreases with decreasing cluster size.
-For larger Xe$_{\rm cl}$, the values are compatible with unity, within the accuracy of our experiment.
-
-%\input{theo_discussion}
-\section{Discussion
-\label{sec:discussion}}
-%
-%We have discussed the experimental spectra in Section \ref{sec:exp_results} and
-%the expected features of spectra for different cluster types in
-%Section \ref{sec:th_results}. In this section we combine the experimental and theoretical
-%results in order to determine the structure of the noble gas clusters.
-%
-%The simulated secondary electron spectra for the xenon core structures
-%(see Figure \ref{figure:xe_3_in})
-%show an ICD peak at higher energies than those structures with added xenon
-%atoms on the surface. This does not fit to the experimentally determined
-%spectra and hence we consider an argon core to be more probable for the
-%small measured clusters.
-%
-%The experimental spectra in Figure \ref{}
-%show a broadening of the secondary electron peak with increasing
-%pressure (?) and hence cluster size just as can be expected from
-%the theoretically simulated spectra in Figure \ref{figure:surf}.
-%
-%From the theoretical simulations of larger small clusters
-%having the same xenon content as experimentally observed a clearly
-%visible ETMD peak is to be expected as shown in Figure \ref{figure:ar_3_6in}.
-%However, the experimental spectra do not show a signal in the energy
-%region of \unit[1.5--6.5]{eV}. From this we conclude that the clusters
-%measured were smaller than 55 atoms containing only very few xenon atoms.
-%Additionally, if the cluster contains more than one xenon atom, they are
-%not expected to be close because of an otherwise visible ETMD peak
-%(compare Figure \ref{figure:2tops}).
-%
-%The large clusters with a large xenon content can be expected to have
-%a xenon core being surrounded by argon layers and hence, both ICD and
-%ETMD should be visible in the spectrum. Unfortunately, the ICD and ETMD
-%peaks overlap such that the two processes can not be distiguished.
-%
-We now would like to interpret our experimental findings in view of the simulated results described in Section `Theoretical Results'.
-Figure \ref{figure:eff} shows that for Ar 3s$^{-1}$ states autoionization by either ICD or ETMD is the only mode of relaxation, except for the clusters with the smallest Xe content.
-We consider this a remarkable result, because ICD of these states is only possible with a Xe atom in the second coordination shell of the decaying Ar vacancy (or shells even further apart), which significantly slows down the ICD process.
-Also decay rates for ETMD were found to be small in early studies of this effect.\cite{zobeley}
-Nevertheless, even in this situation the non-local autoionization channels foreclose radiative decay.
-
-% lowest kinetic energy is the first point of energy raster for t-E code of 52-proc-spec
-Structurally, all experimental ICD/ETMD spectra have a maximum at or near the lowest kinetic energy that could be measured (50~meV), and decrease in intensity to less than half for kinetic energies already below one eV.
-Qualitatively, this shape fits to the ICD contributions in the autoionization spectra discussed in the `Theory' section, but not to the ones from ETMD. 
-The calculated ETMD spectra have a typical three-fold structure with peaks between 3.5-5~eV, 1.5-2.5~eV and around 0 eV kinetic energy. 
-The former two features seem not to be present in the experimental spectra. 
-Due to restrictions in the detector electronics, electron pairs with very similar kinetic energy cannot be detected. 
-The highest kinetic energy for an autoionization electron that can be detected in coincidence with a photoelectron of $\sim3.5$~eV ($h\nu = 32$~eV) is around 2.5~eV.
-Very weak intensity is observed at this energy, and also at higher $e_2$ energies that can be probed at $h\nu = 34$~eV (Supporting Information).
-
-As a cross-check for our theoretical methods we have calculated the radiationless decay spectrum of Ar 3s$^{-1}$ in ArKr, which may arise {\it only} from ETMD(3),\cite{foerstel} and arrived at qualitative agreement with the experimental data.\cite{arkr}
-
-The size-dependent trend within the experimental data is in qualitative agreement to the change in the calculated spectral shape for ICD in systems of increased size (compare Figure~\ref{figure:2tops} to \ref{figure:xe_3_in} and \ref{figure:xe_6_lay5}.)
-
-We are therefore lead to the conclusion that the autoionization spectra we incur are dominated by ICD to non-nearest neighbour atoms, while the intensity of the ETMD channel is low. 
-We would like to recall the factors that lead to a propensity for decay via one or the other mechanism, which have been discussed in the `Theoretical Results'-section.
-For ETMD to occur with a measurable rate, two Xe atoms have to be present in the vincinity of the decaying Ar atom (Figure \ref{figure:2tops}).
-Should that be the case for a large part of the Ar atoms in some cluster structure, ETMD can even dominate over ICD (Figure \ref{figure:ar_3_6in} and Supporting Information).
-Model structures shown in Figures \ref{figure:2tops} and \ref{figure:ar_3_6in} have a Xe content similar to the lowest one probed in our experiment ($\sim$11\,\%).
-For a higher Xe content, ETMD will always dominate the spectra if the two species are given the chance to mix, as e.g.
-in the calculated minimum energy structures of $N=38$ ArXe clusters (Supporting Info).
-On the other hand, in core-shell systems decay via ETMD is probable only for Ar atoms in the interface layer, as this mechanism requires some wavefunction overlap between Ar and one of the Xe atoms involved.
-For the core-shell systems we have investigated, the likelihood of decay via ETMD stays below 25\,\% even for a Xe content above 50\,\% (Table \ref{table:theo_gammas}).
-
-In summary, the two structural motifs that can best be reconciled with our experimental data are
-\begin{enumerate}
-	\item small clusters containing only few Xe atoms that are spread out to distant positions on the cluster surface, and
-	\item systems with a compact Xe core and Ar outer layers.
-\end{enumerate}
-These structures are compatible with the findings of Lindblad {\it et al.}\ from core level photoelectron spectroscopy, who proposed the former structure for the smallest clusters in their study, and the latter for larger ones.\cite{lindblad}
-As even in these two cases intensity for decay via ETMD would not vanish completely, we have to leave it open though whether other mechanisms are present, which further suppress ETMD vs. ICD.
-
-While in early work on ICD it has almost been a paradigm that the decay involves two {\it neighbouring} atoms or molecules,\cite{hergenhahn_review} more recently significant intensity for non-nearest neighbour ICD has been found also in other systems.
-One example is Ne-Ar after Ne 2s ionization, where decay to Ar in the second coordination shell is clearly visible despite the fact that in this system decay involving nearest neighbours is energetically allowed.\cite{fasshauer2014}
-A further theoretical delineation of the respective factors has recently been presented by one of us.\cite{fasshauernjp}
-
-%\input{summary}
-\section{Summary}
-%
-We have presented comprehensive experimental and theoretical data for the
-autoionization of inner valence ionized states in ArXe clusters.
-Both ICD and ETMD are allowed for most cases we considered.
-Because of energetical reasons ICD requires a separation of the final state
-vacancies of \unit[7.58]{\AA} or more, which is about two times the typical
-Ar-Xe distance.
-We found that autoionization has an efficiency of 0.8 to 1.0 within the
-experimental accuracy, that is it dominates over other modes of relaxation.
-By comparing our measured spectra to calculations, we identified `long range'
-ICD as the most important decay mode and were able to determine the most
-probable structural motifs to be a xenon core surrounded by several argon layers
-for large clusters and argon clusters with with very few xenon atoms spread out
-over the surface.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The "Acknowledgement" section can be given in all manuscript
-%% classes.  This should be given within the "acknowledgement"
-%% environment, which will make the correct section or running title.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{acknowledgements}
-\begin{acknowledgement}
-%
-We thank HZB for the allocation of synchrotron radiation beamtime, and the
-Deutsche Forschungsgemeinschaft for funding via the Forschergruppe 1789.
-E. F. gratefully acknowledges the Research
-Council of Norway through a Centre of Excellence Grant (Grant No.\ 179568/V30)
-for funding.
-%
-\end{acknowledgement}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The same is true for Supporting Information, which should use the
-%% suppinfo environment.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{suppinfo}
-
-%This will usually read something like: ``Experimental procedures and
-%characterization data for all new compounds. The class will
-%automatically add a sentence pointing to the information on-line:
-
-%\end{suppinfo}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The appropriate \bibliography command should be placed here.
-%% Notice that the class file automatically sets \bibliographystyle
-%% and also names the section correctly.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliography{arxe}
-
-\end{document}

### 2016-07-04 onefolder/theory.tex
add the folder which was submitted
unfortunately, the journal requires it like this

--- 2016-07-04 onefolder/master.tex
@@
-	
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% This is a (brief) model paper using the achemso class
-%% The document class accepts keyval options, which should include
-%% the target journal and optionally the manuscript type.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\documentclass[journal=jpccck,manuscript=article,layout=twocolumn]{achemso}
-\documentclass[journal=jpccck,manuscript=article]{achemso}
-
-% UHe stuff
-\def\EB{E_{\rm b}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Place any additional packages needed here.  Only include packages
-%% which are essential, to avoid problems later. Do NOT use any
-%% packages which require e-TeX (for example etoolbox): the e-TeX
-%% extensions are not currently available on the ACS conversion
-%% servers.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage[english]{babel}
-\usepackage{braket}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath,amsfonts,amssymb}
-\usepackage{dsfont}
-\usepackage{booktabs}
-\usepackage{units}
-\usepackage{xcolor}
-\usepackage{multirow}
-\usepackage{tikz,pgfplots}
-\usepackage{float} %force figure position
-
-\usetikzlibrary{patterns,shadows,trees,calc}
-\usepgfplotslibrary{units}
-
-\pgfplotsset{compat=1.10}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% If issues arise when submitting your manuscript, you may want to
-%% un-comment the next line.  This provides information on the
-%% version of every file you have used.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%\listfiles
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Place any additional macros here. Please use \newcommand* where
-%% possible, and avoid layout-changing macros (which are not used
-%% when typesetting).
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newcommand*\mycommand[1]{\texttt{\emph{#1}}}
-% Define some colours
-\definecolor{diplom1}{rgb}{0.0 0.4 1.0}
-\definecolor{diplom2}{rgb}{0.0 0.0 0.6}
-\definecolor{diplom3}{RGB}{153,0,0} %unirot
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Meta-data block
-%% ---------------
-%% Each author should be given as a separate \author command.
-%%
-%% Corresponding authors should have an e-mail given after the author
-%% name as an \email command. Phone and fax numbers can be given
-%% using \phone and \fax, respectively; this information is optional.
-%%
-%% The affiliation of authors is given after the authors; each
-%% \affiliation command applies to all preceding authors not already
-%% assigned an affiliation.
-%%
-%% The affiliation takes an option argument for the short name.  This
-%% will typically be something like "University of Somewhere".
-%%
-%% The \altaffiliation macro should be used for new address, etc.
-%% On the other hand, \alsoaffiliation is used on a per author basis
-%% when authors are associated with multiple institutions.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author{Marko F\"orstel}
-\altaffiliation{Now at: Institut für Optik und Atomare Physik, Technische Universit\"at Berlin, Hardenbergstr. 36, 10623 Berlin, Germany}
-\author{Melanie Mucke}
-\altaffiliation{Now at: Department of Physics and Astronomy, Uppsala University, Box 516, 75120 Uppsala, Sweden}
-\author{Tiberiu Arion}
-\altaffiliation{Now at: Center for Free-Electron Laser Science/DESY, Notkestr. 85, D-22607 Hamburg, Germany}
-\author{Toralf Lischke}
-\affiliation[IPP]{Max-Planck-Institute for Plasma Physics, Boltzmannstr. 2, D-85748 Garching, Germany}
-\author{Markus Pernpointner}
-\affiliation[University of Heidelberg]{Theoretical Chemistry, University of Heidelberg,
-              Im Neuenheimer Feld 229, D-69120 Heidelberg, Germany}
-\author{Uwe Hergenhahn}
-\affiliation[IOM]{Leibniz Institute of Surface Modification, Permoserstr. 15, D-04318 Leipzig, Germany}
-\alsoaffiliation[IPP HGW]{Max-Planck-Institute for Plasma Physics, Wendelsteinstr. 1, D-14791 Greifswald, Germany}
-\email{uwe.hergenhahn@iom-leipzig.de}
-\author{Elke Fasshauer}
-\affiliation[UIT]{Centre for Theoretical and Computational Chemistry,
-Department of Chemistry, University of Troms\o
--- The Arctic University of Norway, N-9037 Troms\o, Norway}
-\email{elke.fasshauer@uit.no}
-%\phone{+123 (0)123 4445556}
-%\fax{+123 (0)123 4445557}
-%\alsoaffiliation[Second University]
-%{Department of Chemistry, Second University, Nearby Town}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The document title should be given as usual. Some journals require
-%% a running title from the author: this should be supplied as an
-%% optional argument to \title.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Long-range Interatomic Coulombic Decay in ArXe clusters: Experiment and Theory}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Some journals require a list of abbreviations or keywords to be
-%% supplied. These should be set up here, and will be printed after
-%% the title and author information, if needed.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\abbreviations{IR,NMR,UV}
-%\keywords{American Chemical Society, \LaTeX}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The manuscript does not need to include \maketitle, which is
-%% executed automatically.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The "tocentry" environment can be used to create an entry for the
-%% graphical table of contents. It is given here as some journals
-%% require that it is printed as part of the abstract page. It will
-%% be automatically moved as appropriate.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{tocentry}
-
-\begin{center}
- \includegraphics[height=3.5cm]{front1.pdf}
-\end{center}
-
-%Some journals require a graphical entry for the Table of Contents.
-%This should be laid out ``print ready'' so that the sizing of the
-%text is correct.
-%
-%Inside the \texttt{tocentry} environment, the font used is Helvetica
-%8\,pt, as required by \emph{Journal of the American Chemical
-%Society}.
-%
-%The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
-%permitted for  \emph{Journal of the American Chemical Society}
-%graphical table of content entries. The box will not resize if the
-%content is too big: instead it will overflow the edge of the box.
-%
-%This box and the associated title will always be printed on a
-%separate page at the end of the document.
-
-\end{tocentry}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The abstract environment will automatically gobble the contents
-%% if an abstract is not used by the target journal.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{abstract}
-
-\begin{abstract}
-We report about autoionization channels of Ar inner valence ionized states in mixed ArXe clusters and compare
-our experimental data obtained by electron-electron coincidence spectroscopy
-to our theoretical simulations for representative cluster structures.
-The combined experimental and theoretical data show that the autoionization of Ar 3s$^{-1}$ in ArXe is dominated by Interatomic Coulombic Decay (ICD) to Xe atoms in the second and higher coordination shells of the originally excited atom.
-Clusters with a range of sizes, compositions and structures were probed. 
-The Xe content in the clusters was varied between 10\,\% and 53\,\%. 
-Besides ICD, also Electron Transfer Mediated Decay (ETMD(3)) was found important in many of the calculated spectra, but is seen with less intensity in the experimental spectra. 
-From the calculations, we identify structural motifs which minimize the ETMD vs.
-the ICD rate and suggest that these are preferentially realized in our experiment, in which clusters are formed by supersonic expansion of an Ar-Xe mixture.
-Suggested cluster structures either feature a clear segregation between Ar and Xe fractions, e.g. Xe core, Ar shell systems, or contain a few Xe atoms singled out in surface sites on an Ar cluster.
-These structures differ significantly from the majority of calculated minimum energy structures for ArXe systems of 38 atoms, which might show that the latter, annealed structures are not realized in our experiment.
-We show experimentally that the relaxation of Ar inner valence states by ICD and ETMD together has an efficiency of unity, within the experimental accuracy, for all clusters except those with the lowest Xe content.
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Start the main part of the manuscript here.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{intro}
-\section{Introduction}
-%
-Electron spectroscopy can make important contributions to the 
-research on composition and structure of free nanoparticles.\cite{
-jpcc} Besides photoionization, free electrons emerging from 
-nanoparticles can also be produced by the relaxation of 
-electronically excited states. One such process, which is of 
-particular relevance in weakly bonded systems, is the 
-Interatomic or Intermolecular Coulombic Decay (ICD).\cite{
-cederbaum} In ICD, an electronic excitation decays by energy 
-transfer to one of its neighboring atoms or molecules, thus 
-releasing a free electron from the latter site. ICD is an 
-important relaxation channel e.g. for inner-valence holes in 
-atoms, and also for core level vacancies e.g. in \ce{H2O}
-, where it competes with Auger decay.\cite{slavicek}
-
-By definition, ICD is particularly sensitive to the chemical 
-environment of the atom or molecule in which the primary 
-excitation has taken place. We suggest that this property of ICD 
-decay spectra can be used to derive information on a nanoparticle 
-or a solvation system. 
-The term excitation is used here in a broader sense---in the
-systems we consider in this work, ICD occurs from an excited, singly 
-charged Ar state created by photoionization.
-In other systems, ICD was also observed from neutral excited
-states and states with more than one vacancy.
-
-We report here about studies 
-in which we produced heterogeneous clusters of the noble gases Ar 
-and Xe with different sizes, and compositions ranging from a few 
-Xe dopant atoms in an Ar matrix to clusters containing an equal 
-amount of both species. By the use of electron-electron 
-coincidence spectroscopy and of theoretical simulations on 
-prototypical systems we show how the radiationless decay spectrum 
-of Ar inner valence (3s) ionized states connects to the structure 
-of the clusters.
-
-Intermolecular Coulombic Decay initially was predicted from 
-theoretical considerations of the energy levels in singly vs.\  
-doubly ionized, and doubly vs.\ triply ionized, hydrogen bonded 
-clusters.\cite{cederbaum} First experimental work some years 
-later used Ne clusters,\cite{marburger,jahnkenedimer} but quickly 
-was followed by demonstrations of ICD in a diverse range of other 
-systems. Experimental and theoretical progress has been reviewed.
-\cite{hergenhahn_review, averbukh_review, jahnke_review} ICD 
-proceeds by an initial ionization producing an ion in an excited 
-state, followed by a transfer of energy to a neighbouring site, 
-and an electron emission process therefrom. The final state contains 
-two positive charges; one at the original site of ionization, and a second
-one at another atom or molecule.
-
-Soon after, related 
-autoionization processes were discovered that proceed via a 
-charge transfer instead of an energy transfer. 
-These were termed `Electron Transfer Mediated Decay' 
- (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
- which the originally excited site is neutralized by the decay 
-and `exchange ICD' for charge transfer contributions to the 
-normal ICD amplitude.\cite{santrarev,jahnkesat}
-We find that both energy and charge transfer induced 
-autoionization play a role in Ar-Xe, and will detail the 
-relevant processes below. The notion of ICD requires that the 
-electronic orbitals of the two sites can be distinguished, which 
-typically is the case in weakly bonded systems, held together by 
-hydrogen bonds or van-der-Waals bonds. In the case of strong
-(covalent or metallic) bonding, it is impossible to make a
-distinction between ICD and Auger decay.\cite{hergenhahn_review}
-
-Rare gas clusters are suitable prototype systems for studies of
-ICD, as they can readily be produced by supersonic 
-expansion through a cooled nozzle. 
-The size of the clusters can be changed by varying the expansion parameters.
-The formation of heterogeneous rare gas clusters by coexpansion of a gas mixture cannot {\it a priori} be taken for granted, but was experimentally shown for most combinations of two rare gases, when suitable mixing ratios and expansion parameters are used (see references throughout this article).
-
-First experiments on ICD in heterogeneous systems used Ne-Ar 
-clusters.\cite{barthnear} Those were followed by studies of 
-ICD-like inner-shell decays in aqueous solution.\cite{aziz,pokapanich,pokapanich2011}
-Pioneering work also showed the 
-potential for studies of the interface between a substrate and an 
-adsorbate by ICD.\cite{grieves} More detailed work on Ne-Ar 
-clusters was recently presented by some of the authors \cite{fasshauer2014}
-showing that an analysis of the ICD spectra
-allowed to decide between structural alternatives, for which the
-photoelectron data were indiscriminate.
-For this system, a detailed account of the
-photoelectron spectra with respect to structural features of the 
-mixed clusters is also available.\cite{lundwall}
-
-Several experimental techniques have been used for the study of mixed Ar-Xe clusters, most notably fluorescence spectroscopy, electron diffraction and photoelectron spectroscopy. 
-Early work focussed on the fluorescence of a single Xe atom 
-embedded in an Ar cluster.\cite{lengenprl}
-%Different sites of the dopant atom (on top of a surface, 
-%integrated in an Ar surface, inside the cluster) were 
-%distinguished by three separate bands in the fluorescence yield 
-%recorded as a function of excitation wavelength.\cite{goldberg} 
-Increasing the Xe concentration in the expansion lead to the formation of \ce{Xe2} and larger Xe complexes inside the clusters.\cite{lengen} 
-With increasing Xe content, the formation of Xe-core, Ar-shell systems with a sharp interface between the two species was shown in photoionization experiments.\cite{tchaplyguine,hoener}
-This finding was confirmed by electron diffraction.\cite{Danylchenko,Danylchenko07} 
-Always, the observed Xe content in the clusters is higher than the Xe content in the expanding gas mixture, as Xe can be condensed much easier than Ar.\cite{hoener,Danylchenko07}
-%A complementary study used photoelectron-photoion coincidence of
-%large Ar-Xe clusters, and found that after inner shell (Xe 4d, Ar 2p)
-%photoionization significant charge transfer between both species
-%occurs before the mass spectroscopic final state is reached.\cite{berrah}
-%
-More recently, photoelectron spectra of 
-small Ar-Xe clusters were analyzed, adding to the findings in 
-earlier work.\cite{lindblad} We will discuss this paper in 
-connection with our results below. 
-For completeness, we mention that Ar-Xe complexes can also be produced by passing clusters from a neat Ar expansion through a zone filled with Xe gas (`pick-up').\cite{pietrowski}
-Clusters produced such can structurally be quite different from those produced by coexpansion.\cite{lindbladpccp}
-
-A number of theoretical works on Ar-Xe clusters aimed at the prediction of minimum energy structures. 
-Most recently, these converged to structures which have the Xe atoms mainly in the interior.\cite{marques} 
-Xe was also found to diffuse into the interior of Ar clusters in molecular dynamics simulations after pick-up.\cite{Vach_1999} 
-The electronic energy levels of very small Ar-Xe clusters were calculated in ref \citenum{fasshauer} and the secondary electron spectra were simulated for
-model structures of one argon atom placed on a xenon surface \cite{Fasshauer13}.
-Interestingly, it was found that Ar 3s$^{-1}$ is stable 
-against autoionization in an ArXe dimer, but is destabilized by 
-adding further Xe atoms, or an Ar solvation shell, to the system, thereby allowing
-for combinations of argon and xenon atoms with larger interatomic distances. 
-Again, we will detail these results in conjunction with our 
-current work.
-
-The plan of our paper is as follows: We firstly delineate our experimental and theoretical methods. 
-Calculations were done for a number of model structures which were systematically varied, and are described in the following section.
-After that, we describe and discuss our theoretical results for the autoionization spectra of the model clusters.
-Experimental results are then shown and possible conclusions from comparing them to the calculations are given.
-Details on the experimental technique, and calculated spectra for a wider range of structures are given as Supporting Information.
-
-%\input{experimental}
-
-\section{Experimental}
-%
-\begin{table*}
-\caption{
-The expansion parameters used for cluster production. 
-Here, Xe$_{\rm in}$ is the molar fraction of Xe in the gas mixture before the expansion, $T$ is the nozzle temperature, and $p$ the stagnation pressure. 
-Experiments were performed with $d = 80~\mu$m (first two sections) and $d = 100~\mu$m (bottom section) conical nozzles of 15$^\circ$ half opening angle. 
-We basically have an Ar seeded expansion of Xe gas, as the freezing point of Ar is much lower. 
-$\langle N_{\rm Ar} \rangle$ and $\langle N_{\rm Xe} \rangle$ refer to cluster sizes for a pure Ar, or pure Xe expansion, respectively, at the given conditions, calculated from a scaling law.\protect\cite{hagena1981}
-We expect actual cluster sizes in-between these two limiting values. 
-Inaccuracies in the calculation of $\langle N\rangle$ due to fluctuations of the input parameters are less than 6\,\%. This figure does not include systematic errors of the empirical model.
-}
-\label{tab:cluster}
-
-\begin{tabular}{l c c c c r r}
-%
-\toprule
-  \multicolumn{2}{r}{size label}  &  Xe$_{\rm in}$ (\%)  &  $T$ (K)  &  $p$ (bar) & $\langle N_{\rm Ar} \rangle$ & $\langle N_{\rm Xe} \rangle$ \\
-%
-\midrule
-% Ar, from Marko 
-Ar & (1) & --- &  96.5  & 0.35  & 44  &  --- \\
-% Ar, from Marko 
-Ar & (2) & --- &  96.5  & 0.67  & 200  &  --- \\
-\midrule
-% 1103 676, 679
-ArXe & `S' & 1.2 &  174   & 0.32  & 4  &   74 \\
-% 1103 670
-ArXe & `M' & 1.2 &  174   & 0.49  & 11  &  199 \\
-% 1103 671
-ArXe & `L' & 1.2 &  174   & 0.68  & 23  &  431 \\
-\midrule
-% 1103 663
-ArXe & `S' & 3.0 &  172   & 0.28  & 3  &   57 \\
-% 1103 653
-ArXe & `M' & 3.0 &  172   & 0.51  & 12  &  233 \\
-% 1103 658
-ArXe & `L' & 3.0 &  172   & 0.68  & 24  &  458 \\
-\midrule
-% 1103 630
-ArXe & `S'  & 5.0 &  167  & 0.37  & 7  &  129 \\
-% 1103 640
-ArXe & `M' & 5.0 &  171   & 0.51  & 13  &  240 \\
-% 1103 629
-ArXe & `L'  & 5.0 &  167  & 0.68  & 28  &  537 \\
-\midrule
-% 1004 867 (32 eV)
-ArXe & `XL' & 2.5 &  154  & 2.12  & 995 & 18800\\
-\midrule
-% 0506 382, Keller offset ber?cksichtigt
-Xe &  & 100 & 183.5  & 0.68  & ---  &  615 \\     
-% 1004 868
-%868 & & 2.5 &  158   & 1.50  &  355 &  6090\\
-% 1004 886 (17 eV)
-%886 &  & 2.5 &  161   & 2.41  &  980 & 16770\\
-% 1004 858
-%858 &  & 5.0 &  149   & 2.50  & 1620 & 27700\\
-%
-\bottomrule
-\end{tabular}
-\end{table*}
-%
-%
-The apparatus used for the experiments consists of a supersonic molecular jet with a cooled nozzle, and a magnetic bottle spectrometer, which detects photoelectrons and secondary electrons produced after ionization with synchrotron radiation.\cite{arion}
-% Leave this citation in place to avoid Latex error
-A comprehensive description can be found in ref \citenum{arion}, and here we focus on details specific for the current experiment. 
-Commercialy obtained Ar and Xe gas was filled into 
-separate cylinders up to pressures suitable for producing a certain mixing ratio. The gases were then allowed to mix before the expansion. 
-Expansion parameters are given in Table \ref{tab:cluster}. 
-Similar expansion conditions are further referred by the labels `S'-`XL', as given in the Table.
-
-Prediction of the sizes of clusters from a supersonic expansion mainly rests on empirical scaling laws,\cite{hagena1981} which have been the subject of some discussion.
-Moreover, such scaling laws originally were derived only for pure gas expansions.
-A recent investigation of cluster sizes in a mixed Ar-Kr expansion yielded a revised scaling law, which essentially amounts to the use of a weighted average over the atom-specific parameters of the two gases.\cite{danylchenko2015}
-Although the analogy to our case is not complete, as phase segregation occurs in Ar-Kr to a much lesser extent,\cite{Vach_1999,lundwall_arkr} we expect scaling law cluster sizes between the values calculated for Ar and Xe.
-Recent analyses of photoionization spectra suggest that mean sizes arrived at by scaling laws are smaller than the actual size, at least for rare gas clusters in the range $\langle N\rangle < 1000$.\cite{bergersen,hergenhahnprb,foerstel_arg2_2011}
-For the expansion conditions labelled `S'-`L', we therefore expect that the scaling law estimates are a lower boundary for the actual cluster size.
-
-The expansion chamber for the supersonic jet is separated from the interaction chamber by a non-magnetic, conical skimmer with an opening of 1~mm in diameter (Beam Dynamics). 
-At few cm distance behind the skimmer, the cluster jet was crossed by synchrotron radiation from the BESSY electron storage ring at Helmholtz-Zentrum Berlin. 
-Electrons were detected by a short `magnetic bottle' time-of-flight spectrometer, that has been described earlier.\cite{mucke_review}
-Due to its large collection angle, this instrument is particularly suited for experiments that employ electron-electron coincidence detection.
-Data were recorded in two different beamtimes at the UE112-PGM-1 (small and medium sized clusters, first two sections in Table \ref{tab:cluster}) and at the TGM-4 beamline (large clusters, last section in Table \ref{tab:cluster}).
-Linearly, horizontally polarized radiation was used. 
-The storage ring was operated in single bunch conditions.
-Spectra of pure Ar clusters shown for comparison are from ref \citenum{foerstel_arg2_2011}, and a spectrum of pure Xe clusters was recorded with the set-up described in ref \citenum{hergenhahnprb}.
-
-The entrance aperture and drift tube of the magnetical bottle spectrometer can be independently biased to influence the electron flight times. 
-For the data shown here, slightly positive bias voltages were used (+1.8 V to +2.2 V) in order to have all electrons arriving at the detector within one BESSY single bunch period (800 ns). 
-The detection efficiency was determined as 0.6, with the method outlined in ref \citenum{mucke_review}.
-Data were converted from flight times to kinetic energy by measuring calibration data for atomic photolines of known binding energy.
-The systematical uncertainty of this procedure may lead to a common shift of all experimental kinetic energy data shown in this article of up to 30~meV.
-
-The high detection efficiency of the instrument is a pre-requisite for measuring two-electron emission processes, such as photoelectron emission followed by ICD or ETMD, by using electron-electron coincidence detection.
-This allows to filter the full electron spectrum for contributions arising after emission of an Ar 3s photoelectron.
-ICD/ETMD spectra presented here are based on this method, which has been explained earlier.\cite{mucke_review,Foerstel_phd}
-Technical details and full electron-electron coincidence spectra are given in the Supporting Information.
-
-%\input{theory}
 \section{Theoretical Approach}
@@
 This choice is identical to the one made in ref \citenum{Fasshauer13}.
-
-%\input{structures}
-\section{Cluster Structures}
-
-From the experimental results we can obtain two hints for the cluster
-structure: the minimum size and the xenon content. In the following we will 
-use these to construct representative cluster structures, for which we will 
-simulate the ICD and ETMD spectra. At this point we put in a variety of
-structures, in order to learn about general structure-spectrum relations
-and therefore being able to
-exclude some of them by comparison of
-the ICD and ETMD spectra to the experimental ones.
-
-In our previous study\cite{Fasshauer13} the ArXe clusters were assumed
-to be large, having more than 1500 atoms. The model structures assumed
-an fcc structure and not an icosahedral structure, which is energetically
-favoured for small clusters.
-Most estimated cluster sizes given in Table \ref{tab:cluster} are much smaller.
-We use the estimated number of atoms for a pure Ar expansion as the lower limit for the actual cluster size and start our search for model structures from there.
-%
-%Additionally,
-%the expectation value for the number of xenon atoms relies on a pure
-%xenon gas. Since the xenon content in the mixed gas is much lower, also
-%the number of xenon atoms can be expected to be by far less. We therefore
-%start from the estimated number of atoms in the cluster after expansion
-%of pure argon gas.
-%We therefore rethink the possible cluster structures.
-%Furthermore, the theoretical prediction did not match the experimental results.
-%Since the spectra are strongly depending on the cluster structure as shown in
-%\cite{fasshauer2014}, the underlying structure seems not to fit and hence
-%we rethink the possible cluster structures.
-%
-For the smaller clusters measured,
-these expectation values range from \unit[3--21]{Ar atoms}. 
-The cluster sizes for expansion of a mixed gas are unknown, but
-for xenon as the second component a larger size is expected compared to a
-pure argon expansion, due to the higher polarizability
-and hence larger cohesive energy of xenon. All clusters
-contributing to the coincidence spectrum
-contain at least one xenon atom, as otherwise decay by ICD or ETMD is energetically not allowed.
-
-In a gas expansion a range of clusters sizes with different structures is produced. 
-However, for small rare gas clusters consisting of less than approximately \unit[1000]{atoms} so-called \emph{islands of stability} were found.\cite{haberland}  
-In mass spectra, clusters with mass numbers corresponding to icosahedral shapes had an abundance that was (slightly) enhanced over other sizes. 
-We therefore started from icosahedral structures and constructed mixed cluster structures by substitution of individual atoms with one or the other kind (Ar or Xe), or added individual atoms close to the desired position within a given structure.
-After that, the cluster structures were optimized using the unified force
-field implemented in the 
-Avogadro programme (version 1.1.0) \cite{Avogadro,Hanwell12} to give local
-minimum structures.
-All cluster structures are listed in Table \ref{table:theo_gammas}.
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{cluster_2_overview.pdf}
- \caption{Cluster structures composed of 13 argon atoms and two additional xenon
-          atoms on different surfaces of the argon icosahedron, varying in Xe-Xe distance:
-          (a) closest possible, (b) middle, (c) furthest away. They refer to
-          numbers 9--11 in Table \ref{table:theo_gammas}.}
- \label{figure:cluster_2_overview}
-\end{figure}
-%
-\begin{figure}[h]
- \centering
- \includegraphics[width=8.5cm]{cluster_3_overview.pdf}
- \caption{Cluster structures derived from a 55 atom icosahedral structure:
-          (a) one xenon atom on the surface, (b) six xenon atoms inside a 55 atoms cluster,
-          grouped on one side, (c) six xenon atoms distributed randomly
-          in a 55 atoms cluster. They refer to numbers 12, 18 and 19
-          in Table \ref{table:theo_gammas}.}
- \label{figure:cluster_3_overview}
-\end{figure}
-
-As discussed in the introduction, the small clusters will likely
-deviate from a core-shell structure with a xenon core surrounded
-by argon shells, as observed for large clusters.\cite{tchaplyguinearxe,Vach_1999} We therefore start from
-argon clusters of 13 or 55 atoms, and modify them in one of the following
-ways:
-%
-\begin{itemize}
- \item add one xenon atom on top of a surface / edge / vertex of
-       the argon core, with an example shown in
-       Figure \ref{figure:cluster_3_overview}a
-       (one additional xenon atom
-       on top of a surface of a \unit[55]{atom} argon core)
-       (Table \ref{table:theo_gammas}, \#6--8, \#12--14),
- \item substitute one argon atom in a surface / edge / vertex position
-       (Table \ref{table:theo_gammas}, \#15--16),
- \item substitute one or two argon atoms in the core of the argon cluster
-       by xenon atom(s) for the simulation of the core-shell structures
-       (Table \ref{table:theo_gammas}, \#1--3),
- \item add two xenon atoms on top of surfaces of a 13 atoms argon core
-       in different relative positions (see Figure
-       \ref{figure:cluster_2_overview}),
-       in order to achieve a xenon content in the cluster close to the
-       measured one (see below)
-       (Table \ref{table:theo_gammas}, \#9--11),
- \item substitute six argon atoms of a 55 atoms argon cluster by xenon
-       atoms either grouping them or distributing them througout the cluster
-       (see Figure \ref{figure:cluster_3_overview}b and c) in order to
-       achieve a xenon content in the cluster close to the measured one
-       (Table \ref{table:theo_gammas}, \#18--19).
-\end{itemize}
-
-These structures were then optimized using force field methods.
-%
-Furthermore, for comparison with the largest measured ArXe clusters, we constructed also larger core-shell structures (Table \ref{table:theo_gammas}, \#4--5).
-
-%\input{theo_results}
-\section{Theoretical Results
-\label{sec:th_results}}
-%
-%
-\begin{table}[H]
-\small
-\centering
-\caption{Structural and calculated properties of some model clusters.
-The cluster structures are characterized by the number of Ar and Xe atoms,
-and are arranged in three groups according to gross structural properties. 
-The first group contains Xe core-Ar shell systems of various
-size and relative Xe content.
-In the second group, model structures for small clusters are displayed,
-in which 1-2 Xe atoms are added at systematically varied locations
-to an icosahedric Ar clusters consisting of one or two full shells,
-or in which 1-6 Ar atoms of such cluster were replaced by Xe atoms.
-The last group contains data for calculated minimal energy structures
-of mixed ArXe clusters.\protect\cite{marques}
-The cluster structures are classified into core-shell structures (cs),
-structures with segregated xenon atoms (in) and completely mixed
-structures.
-The columns `ICD' and `ETMD' are the respective partial decay widths
-in \unit[$10^{-4}$]{eV}, and `\% ICD' gives the percentage of ICD in
-the total decay width.
-See text for details.
-\label{table:theo_gammas}
-}
-\begin{tabular}{rrrrcccccrrr}
-\toprule
-\# & \# Xe & \# Ar & Xe$_{\rm cl}$\% & str. cl. & pos. & rel. pos. & ICD   &  ETMD & \% ICD & Fig.\\ %$\Gamma_{\rm ICD,ETMD}$\\
-\midrule
- 1 &     1 &    12 &  7.7  & cs    &         &          & 0.000 & 0.000 &  -- &\\ %    0.0            \\     ArXe\_2\_1atom      
- 2 &     1 &    54 &  1.8  & cs    &         &          & 0.000 & 0.000 &  -- & \ref{figure:xe_3_in}\\ %    0.0            \\     ArXe\_3\_1atom      
- 3 &     2 &    53 &  3.6  & cs    &         &          & 0.033 & 0.167 &  16.7& \ref{figure:xe_3_in}\\ %2.006$\cdot 10^{-5}$ \\ ArXe\_3\_2atom      
- 4 &  1415 &   642 & 68.8  & cs    &         &          & 7.039 & 2.573 &  73.2& supp.\\ %9.612$\cdot 10^{-4}$ \\ ArXe\_8\_1layer     
- 5 &   561 &  3310 & 14.5  & cs    &         &          &       &       &  85  & \ref{figure:xe_6_lay5}\\ % c6l5
-
-\midrule
- 6 &     1 &    13 &  7.1  & cs    & surface &          & 0.792 & 0.000 & 100.0& \ref{figure:surf}\\ %7.922$\cdot 10^{-5}$ \\ XeAr\_2\_surface    
- 7 &     1 &    13 &  7.1  & cs    & edge    &          & 0.013 & 0.000 & 100.0&\\ %1.320$\cdot 10^{-6}$ \\ XeAr\_2\_edge       
- 8 &     1 &    13 &  7.1  & cs    & vertex  &          & 0.050 & 0.000 & 100.0&\\ %5.013$\cdot 10^{-6}$ \\ XeAr\_2\_vertex     
- 9 &     2 &    13 & 13.3  & cs    &         & closest  & 0.101 & 0.151 &  40.1& \ref{figure:2tops}\\ %2.523$\cdot 10^{-5}$ \\ XeAr\_2\_2top       
-10 &     2 &    13 & 13.3  & cs    &         & middle   & 0.159 & 0.008 &  95.4& \ref{figure:2tops}\\ %1.665$\cdot 10^{-5}$ \\ XeAr\_2\_2midtop    
-11 &     2 &    13 & 13.3  & cs    &         & furthest & 0.159 & 0.002 &  98.9& \ref{figure:2tops}\\ %1.605$\cdot 10^{-5}$ \\ XeAr\_2\_2endtop    
-12 &     1 &    55 &  1.8  & cs    & surface &          & 0.064 & 0.000 & 100.0& \ref{figure:surf}\\ %6.371$\cdot 10^{-6}$ \\ XeAr\_3\_surface    
-13 &     1 &    55 &  1.8  & cs    & edge    &          & 0.048 & 0.000 & 100.0&\\ %4.791$\cdot 10^{-6}$ \\ XeAr\_3\_edge       
-14 &     1 &    55 &  1.8  & cs    & vertex  &          & 0.027 & 0.000 & 100.0&\\ %2.701$\cdot 10^{-6}$ \\ XeAr\_3\_vertex     
-15 &     1 &    54 &  1.8  & in    & edge    &          & 0.077 & 0.000 & 100.0&\\ %7.708$\cdot 10^{-6}$ \\ XeAr\_3\_edge\_in   
-16 &     1 &    54 &  1.8  & in    & vertex  &          & 0.053 & 0.000 & 100.0&\\ %5.258$\cdot 10^{-6}$ \\ XeAr\_3\_vertex\_in 
-17 &     2 &    53 &  3.6  & in    &         &          & 0.117 & 0.055 &  68.1&\\ %1.711$\cdot 10^{-5}$ \\ XeAr\_3\_2in        
-18 &     6 &    49 & 10.9  & in    &         &          & 0.375 & 0.405 &  48.1& \ref{figure:ar_3_6in}\\ %7.796$\cdot 10^{-5}$ \\ XeAr\_3\_6in        
-19 &     6 &    49 & 10.9  & mixed &         &          & 0.292 & 0.674 &  30.3& \ref{figure:ar_3_6in}\\ %9.660$\cdot 10^{-5}$ \\ XeAr\_3\_6\_scat    
-                                                                                                 \midrule
-20 &     2 &    36 &  5.3  & cs    &         &          & 0.117 & 0.151 &  43.6& supp.\\                        % Ar$_{36}$Xe$_{2}$   
-21 &     4 &    34 & 10.5  & mixed &         &          & 0.248 & 0.587 &  29.7& supp.\\                        % Ar$_{34}$Xe$_{4}$   
-22 &     5 &    33 & 13.2  & mixed &         &          & 0.335 & 0.844 &  28.4& supp.\\                        % Ar$_{33}$Xe$_{5}$   
-23 &    13 &    25 & 34.2  & mixed &         &          & 0.828 & 5.414 &  13.3& supp.\\                        % Ar$_{25}$Xe$_{13}$  
-24 &    24 &    14 & 63.2  & mixed &         &          & 1.488 &16.718 &   8.2& supp.\\                        % Ar$_{14}$Xe$_{24}$  
-25 &    25 &    13 & 65.8  & in    &         &          & 1.432 & 4.995 &  22.3& supp.\\                        % Ar$_{13}$Xe$_{25}$  
-26 &    35 &     3 & 92.1  & in    &         &          & 2.017 & 7.051 &  22.2& supp.\\                        % Ar$_{3}$Xe$_{35}$   
-\bottomrule
-\end{tabular}
-\end{table}
-%
-The geometrical properties as well as the total ICD and ETMD decay widths
-of the investigated structures are shown in Table \ref{table:theo_gammas}.
-It is important to remember that the first ICD channel opens at a
-channel opening distance of \unit[7.58]{\AA}. In the smallest
-clusters with only one argon layer around each
-xenon atom, the Ar-Xe pair distances are below that value, therefore 
-no ICD can take place. Also, by definition, two Xe atoms are
-required for ETMD(3), hence it cannot occur in clusters with only one xenon atom.
-%Because secondary electrons are observed in the experimental spectra
-%we exclude all structures without any signal from our further
-%discussions.
-%
-\begin{figure}[H]
- \centering
- \includegraphics[width=8.0cm]{surf.pdf}\\
- \includegraphics[width=8.0cm]{R_comp.pdf}
- \caption{
- %
- Top panel: Simulated electron emission spectra of an Ar 3s vacancy in 
-          argon clusters
-          consisting of 13 and 55 atoms, with an additional xenon atom residing
-          on top of one of the argon surfaces.
-          Bottom panel: Distribution of Ar-Xe distances $d$ in the studied ArXe
-          clusters. The ICD channels to final states involving Xe 5p$_{3/2}^{-1}$ and 
-          5p$_{1/2}^{-1}$ vacancies open at \unit[7.58]{\AA} and
-          \unit[36.00]{\AA}, resp.; the former distance is marked by a vertical dotted line. 
-          Only pairs at longer interatomic
-          distances contribute to the electron emission spectra.
-          Larger Ar-Xe distances, as found in the larger cluster,
-          correspond to features at a higher kinetic energy of
-          the ICD electron (top panel).}
- \label{figure:surf}
-\end{figure}
-
-%In the investigated structures several different aspects have to be
-%taken into account which we will discuss separately if possible
-%on selected structures.
-
-We will now discuss features of several structures, using selected examples.
-First we consider clusters having an argon core of 13 and 55 atoms plus a single xenon
-atom on one of the surfaces (see Figure \ref{figure:cluster_3_overview}a
-for the structure of clusters with the 55 atoms core).
-Secondary electron spectra simulated for these systems are shown in Figure \ref{figure:surf}, top panel.
-%two different argon core sizes one consisting
-%of 13 and one consisting of 55 atoms with one xenon atom on one of
-%the surfaces (see Figure \ref{figure:cluster_3_overview} Panel a)
-%for the 55 atom core). The simulated secondary electron spectra are
-%shown in Figure \ref{figure:surf} Panel 1.
-
-Because the structures contain only one xenon atom, ETMD(3) is not possible, only ICD is expected. 
-%Both spectra show several smaller peaks which
-%are convoluted into one single peak with a maximum at
-%approximately \unit[0.2]{eV}. 
-%In comparison to the 13 argon atoms core
-%spectrum t
-The spectrum pertaining to the clusters with larger (55 atoms) Ar core shows
-signals at higher energies of the secondary electron. These features
-can be explained by investigating the Ar-Xe distance distributions
-in the clusters, shown
-in the bottom panel of Figure \ref{figure:surf}. 
-Every different value of the atom pair distance
-results in a different energy of the secondary electron and only pairs
-with a distance of larger than the channel opening distance
-(dashed gray line) will contribute
-to the spectrum. 
-In our model, there is a one-to-one correspondence between interatomic distance $d$ and kinetic energy of the ICD electron.
-The larger the interatomic distance, the higher is the
-kinetic energy of the secondary electron for a given channel.
-%Since the cluster with an Ar core of 55 atoms is larger, and therefore
-%contains Ar-Xe pairs with larger distances, its spectrum 
-Therefore, the spectrum of the cluster with a 55 atoms core extends to higher energies.
-%energies as well.
-This relation between ICD energy and cluster size holds true for all cluster structures.
-%This explains why the ICD spectrum for larger clusters extends to higher energies, and holds for all cluster structures.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{2tops.pdf}
- \caption{Simulated electron emission spectra of an Ar 3s vacancy in 
-          argon clusters consisting of 13
-          argon atoms with two additional xenon atoms on top of two different
-          argon surfaces. ICD and ETMD spectra are shown for three
-          different relative positions of the two xenon atoms. If 
-          the xenon atoms are close to each other, an ETMD process is
-          clearly visible. In the other two cases the spectra are dominated by
-          the ICD spectrum.}
- \label{figure:2tops}
-\end{figure}
-%
-For clusters with more than one xenon atom, also ETMD(3) is possible.
-Depending on the positions of the xenon atoms relative to each other and to the Ar core, the spectra are expected to be different.
-As an example, we discuss clusters with a core of 13 argon atoms and two xenon atoms on different surfaces. 
-Their xenon content is \unit[13.3]{\%} and thus close to the experimental one of \unit[10-12]{\%} for the lowest xenon admixture.
-The cluster structures were illustrated in Figure \ref{figure:cluster_2_overview}, simulated spectra are shown in Figure \ref{figure:2tops}.
-In all three cases, both ICD and ETMD(3) are energetically allowed. The ICD
-spectra do not change qualitatively by adding the second xenon.
-%either identical or at least very similar to the ones for
-%cluster with a single  consisting of one
-%convoluted peak at approximately \unit[0.2]{eV}. 
-However, the ETMD(3) spectra
-are very sensitive to the relative position of the two xenon atoms.
-Two aspects have to be taken into account: an energy shift of the peaks due
-to different charge distances in the final state (i.e. the interatomic Xe-Xe
-distance) and the decrease of the decay width with $R^{-6}$, $R$ being the distance
-between the electron transfer unit and the xenon atom ionized in the final state.
-The larger the distance between the xenon atoms, the higher are the energies
-of the secondary electrons and the smaller are the decay widths. 
-Therefore, a
-significant contribution from ETMD(3) compared to ICD is only
-seen if the two xenon atoms reside on two adjacent
-surfaces. 
-%{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
-The three energetically separated peaks in the ETMD(3) spectrum pertain to different combinations of the Xe 5p$_j^{-1}$ vacancy states, which have a substantial fine-structure splitting (see Table \ref{tab:valence}).
-%\ref{sec:exp_results}).
-%
-%The threefold peak structure of the ETMD(3) peak does in contrast to
-%the ICD spectrum not stem from different triple structures but from the
-%four different decay channels for one triple structure.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{ar_3_6in.pdf}
- \caption{Same as Figure \protect\ref{figure:2tops}, for clusters consisting of
-          55 atoms, 6 out of which are xenon atoms. These are either grouped
-          on one side of the cluster (label `group') or evenly distributed
-          in the cluster interior (label `scattered').}
- \label{figure:ar_3_6in}
-\end{figure}
-%
-For the 55 atoms clusters, a xenon content of \unit[10--12]{\%}
-corresponds to six xenon atoms out of a total of 55 atoms. These can form a connected 
-group in one part of the cluster or can be evenly distributed,
-as shown in Figures \ref{figure:cluster_3_overview}b and \ref{figure:cluster_3_overview}c. The
-ICD and ETMD(3) spectra for these structures are shown in Figure \ref{figure:ar_3_6in}.
-
-For both cases the overall ICD spectra are very similar, and show a maximum at a kinetic energy of approximately \unit[0.3]{eV}. 
-In case of grouped xenon atoms, the ICD spectrum extends to slightly higher energies, corresponding to ArXe pairs at slightly larger spatial distances.
-A more significant difference is observed in the ETMD(3) spectra. 
-The interatomic xenon distance is shorter in clusters, in which the xenon atoms form a connected group.
-Hence, the triple structure of the ETMD(3) spectrum is seen at lower kinetic energies. 
-Additionally, the probability for an electron
-transfer from a xenon to an argon atom decreases exponentially with the
-interatomic distance. Therefore, only those xenon atoms which have direct
-argon atom neighbours have a significant contribution to the
-total decay width, and the total ETMD(3) decay width is lower for the structure with
-grouped xenon atoms than for
-the structure with evenly distributed xenon atoms (see Table \ref{table:theo_gammas}).
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{xe_3_in.pdf}
- \caption{Same as Figure \protect\ref{figure:2tops}, for argon clusters with
-          one or two xenon atoms in the core of the cluster (55 atoms total). 
-          All ICD and ETMD channels are closed, if the cluster contains only 
-          a single xenon atom. For clusters with two xenon atoms
-          in the core, the first ICD channel is open for some pairs,
-          and additionally ETMD is possible for multiple triples. Due to a
-          different distance distribution compared to the clusters with an argon
-          core (Figure \protect\ref{figure:2tops}), 
-          the ICD peak is shifted to higher kinetic energies.}
- \label{figure:xe_3_in}
-\end{figure}
-%
-For comparison with the previous assumptions of a xenon core surrounded
-by argon atoms we investigated clusters of 13 and 55 atoms with one or two
-xenon atoms in the core. Some of the corresponding
-spectra are shown in Figure \ref{figure:xe_3_in}.
-
-%For the clusters with only one xenon atom in the core and the ionization
-%energies used for the simulation of the secondary electron energies
-%all ICD channels are closed. Since the cluster contains only one xenon atom,
-%an ETMD(3) is not possible. Hence there is no signal to be expected at all.
-For a core consisting of two xenon atoms both an ICD and an ETMD(3) spectrum
-can be seen. Compared to the cluster structures involving an argon core, the ICD peak is
-shifted to higher ICD electron energies. 
-Additionally, the ICD and ETMD(3) spectra overlap.
-For ETMD(3), only three of the four different decay channels are
-energetically allowed.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{c6l5.pdf}
- \caption{Same as Figure \protect\ref{figure:2tops},
-          for a large cluster consisting
-          of a xenon core of 561 atoms surrounded by five complete layers of
-          argon atoms (Xe content: 14.5\,\%) for both an icosahedral and
-          cuboctahedral basic structure.
-          The ICD and ETMD peak overlap such that the ETMD peak
-          is unlikely to be visible.}
- \label{figure:xe_6_lay5}
-\end{figure}
-%
-In the first experiments very large argon-xenon clusters of 
-$\approx 4380$ atoms with a xenon content of \unit[19]{\%}
-were measured,\cite{Mucke_phd}
-which we in one example approximate by a cluster consisting of 561 xenon
-atoms surrounded
-by five layers of argon atoms (3871 atoms in total). In order to take the
-better stabilization of charges in larger clusters into account, the
-ionization energies of the XL clusters (see Table \ref{tab:valence})
-were used.
-The spectra are shown in 
-Figure \ref{figure:xe_6_lay5}.
-
-Compared to the small clusters with a xenon core in Figure \ref{figure:xe_3_in}
-the ICD peak is broadened and shifted to higher ICD electron energies which is
-expected due to the larger interatomic Ar-Xe distances in the large cluster and
-the better stabilization of charges, which is relevant mostly for the final state, but also the initial state.
-The ETMD(3) peak is shifted to slightly higher energies as well. This allows opening of the
-fourth decay channel, pertaining to Xe 5p$_{1/2}^{-1}$ Ar 3p$_{1/2}^{-1}$ final states.
-
-We also note that the percentage of decay via ICD is practically
-independent of the Xe content for large clusters with a Xe core, Ar shell structure.
-This can be expected, as both decay processes are most pronounced for the
-atoms in the interface region of the xenon core and the argon shell.
-The ETMD(3), depending on the electron transfer from one xenon atom to the
-initially ionized argon atom, and hence on the corresponding orbital overlap,
-is purely an interface effect that involves the argon atoms with direct xenon
-neighbours, and the two xenon layers closest to the argon shell.
-The ICD has a stronger long range character, due to which the description
-of decays with partners of at least twice the smallest channel opening
-distance is necessary for clusters. However, the bigger the clusters are,
-the more homogeneous does the interface region become for clusters of
-different sizes. This manifests itself in the distribution of relevant
-Ar-Xe pair distances (compare Figure \ref{figure:surf}, lower panel).
-As a consequence, the ICD spectra of two large clusters of different size
-hardly differ.
-
-\clearpage
-
-%\input{exp_results}
-\section{Experimental Results}
-\label{sec:exp_results}
-%
-%
-\begin{table}
-\caption{Properties of the outer valence spectra of mixed ArXe clusters. 
-Spectra of pure Ar and Xe clusters are included for reference. 
-All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV). 
-Binding energies $\EB$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit. 
-The average Xe content of the cluster ensemble, Xe$_{\rm cl}$, was determined from the areas of the respective photolines, corrected by their atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}.
-Uncertainties are estimated as $\pm$3\,\% for the Xe content and 0.05~eV for the binding energies. 
-The row labelled `(th.)' gives the binding energies used in the simulations of this paper, and the last row their atomic counterparts. 
-Values for Ar 3p in the last row refer to the fine structure states.
-\label{tab:valence}}
-\begin{tabular}{ l c c c c c c c c}
-%
-\toprule
- \multicolumn{2}{r}{size} &  Xe$_{\rm in}$& $\EB$ (eV)& $w$ (eV)& \multicolumn{2}{c}{$\EB$ (eV)}  & $w$ (eV) &  Xe$_{\rm cl}$ \\
-%
- \multicolumn{2}{r}{(label)}&  (\%) & Ar 3p & Ar 3p & Xe 5p$_{1/2}$ &  Xe 5p$_{3/2}$ & Xe 5p$_{3/2}$  &  (\%) \\
-\midrule
-% Ar, from Marko
- Ar & (1) &&  15.3  &  1.1 & & & &  \\
-% Ar, from Marko 
- Ar & (2) &&  15.1  &  1.3 & & & &  \\
-%
-%  columns in the following: energies c.g. 51-plt-oval, widths Marko Diss., Xe content Marko Diss
-% 1103 676, 679
- ArXe & S &1.2 & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
-% 1103 670
- ArXe & M &1.2 & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
-% 1103 671
- ArXe & L &1.2 & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
-% 1103 663
- ArXe & S &3.0 & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
-% 1103 640
- ArXe & M &5.0 & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
-% 0506 
- Xe &  & & & & 12.76 & 11.19 & 1.18 & 100\\
-%
-\midrule
-%
-%  1004  886  (UHe, c.g. + roi values)
- ArXe & XL &2.5 & 15.15 & 1.3 & 12.59 & 11.01 & 1.24 & 19\\
-%
-\midrule
-% Date: Wed, 20 Jan 2016 11:27:39, From: Elke Fa?hauer <elke.fasshauer@uit.no>
- Ar, Xe & (th.) && 15.3 && 13.0 & 11.5 &&\\
-%
- \multicolumn{2}{l}{(atomic)\cite{velchev,sansonetti}} && 15.76|15.94 && 13.43 & 12.13 &&\\
-%
-\bottomrule
-\end{tabular}
-\end{table}
-
-\subsection{Outer valence spectra}
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_oval_1.pdf}
- \caption{
-Outer valence photoelectron spectra of mixed Ar-Xe clusters, in comparison to the pure species. 
-(a) shows the outer valence region of homogeneous Ar and Xe clusters, respectively (see text for details). 
-The two lower panels show spectra of the mixed species with different mean size. 
-Sharp lines marked `m' (for `monomer') result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states. 
-Labels in (b) and (c) give the Xe content in the expanding gas mixture (Xe$_{\rm in}$), which is lower than the Xe content observed in the heterogeneous clusters (Xe$_{\rm cl}$). 
-The photon energy was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
-%{\color{red}{Die Stabilisierung der Xe-bulk Atome ist in den gemischten Cluster
-% höher als in den gemischten Clustern. Das ist ungewöhnlich. Habt ihr hier
-% verschiedene CLustergrößen?}}
-}
- \label{figure:oval1}
-\end{figure}
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_oval_2.pdf}
- \caption{
-Outer valence photoelectron spectra of mixed Ar-Xe clusters from gas mixtures with different Xe concentration. 
-For better visibility, a scaling factor is applied to the Xe part of the spectrum in panel (a).
-See Figure \ref{figure:oval1} and text for details.
-}
- \label{figure:oval2}
-\end{figure}
-
-Figure \ref{figure:oval1} shows the outer valence spectra of small and large ArXe clusters, compared to clusters of the pure gases. 
-Qualitatively similar spectra have been published without detailed discussion in ref \citenum{lindblad}.
-Differences are seen in particular for the Ar component. 
-In pure Ar clusters, outer valence photoionization leads to a broad band, caused both by spin-orbit coupling and crystal field splitting. 
-The relative importance of these two mechanisms remains under debate.\cite{hergenhahnprb,rolles,foerstel_arg1_2010} 
-For larger clusters (e.g.
-$\langle N\rangle = 190$, black trace), the maximum at low binding energies becomes more pronounced, and is identified with emission from the cluster interior.\cite{hergenhahnprb,rolles}
-At the particular photon energy selected here, atop of this band a sharp feature is also visible (in Figure \ref{figure:oval1} at a kinetic energy of about 1.8 eV).
-For larger clusters (above $\langle N\rangle \approx 100$), over a range of photon energies of about 3 eV, its appararent binding energy changes in a way which is reminiscent to photoemission of crystalline bulk matter (`dispersion').\cite{foerstel_arg1_2010,foerstel_arg2_2011}
-
-Ar 3p spectra of the smaller mixed clusters (Figure \ref{figure:oval1}c, Figure \ref{figure:oval2}) show neither of these traits.
-Rather, the Ar band is symmetric, less wide than in the pure clusters and at a higher binding energy.
-Even for very large clusters (Figure \ref{figure:oval1}b) the asymmetry of the 3p band and the `dispersing feature' do not appear.
-We characterize the spectral shape by giving a single value for the Ar 3p binding energy, and the FWHM of the feature.
-Values for different expansion parameters, and for both Ar and Xe valence lines, are collected in Table\ \ref{tab:valence}.
-
-We find experimentally that clusters we have produced have a Xe content Xe$_{\rm cl}$ between 10\,\% and 50\,\%.
-A slight decrease of the binding energy with cluster size is seen for all outer valence lines, and is attributed to a larger final state polarization energy in larger clusters.
-
-For further interpretation of the shape of the Ar peaks we refer to photoemission spectra of condensed Ar monolayers, measured in several settings.\cite{jacobi,jacobi2}
-Spectra were reported for physisorption of Ar on two different metal single crystal substrates, and for Ar atop of a Xe spacer layer adsorbed on the metal.
-While the binding energy depends on the substrate, the spectral shape is very similar in all cases. 
-Most spectra were recorded for emission along the surface normal, and show a double peak split by about 0.5 eV, leading to a structure with $w$ about 1 eV.
-Although the splitting is larger than the gas phase fine structure split of 0.18 eV, the pertaining states have been assigned to Ar 3p$_{1/2}$ and 3p$_{3/2}$.
-A crystal field splitting of the 3p$_{3/2}$ state has been assumed to be also present, but with a smaller value of 0.1-0.2 eV, approx.\cite{jacobi2} 
-The spectrum clearly changes when going to an emission angle of 40$^\circ$ with respect to the surface normal (Figure 2 in ref \citenum{jacobi2}).
-The higher binding energy peak significantly loses in intensity, and the spectrum is now dominated by a single peak comprising both crystal field split substates of Ar 3p$_{3/2}$, with a FWHM ($w$) of only 0.4 eV.
-As our measured spectrum is comprised of contributions recorded under all emission angles with respect to the cluster surface, grazing emission will be the rule.
-We therefore believe that the arguments given above make it plausible that only a single peak is observed in all our spectra.
-
-Emission from the Xe 5p state shows a much larger fine structure splitting then from the Ar 3p state; it dominates the spectrum even in clusters (where other broadening mechanisms are also present).
-The shift of the cluster bands with respect to the monomer lines in the largest mixed clusters we have probed (Figure \ref{figure:oval1}b) are similar to the ones in the pure Xe spectrum, the scaling law size of which is at somewhat more than five filled shells.
-This indicates an approximate upper limit for the size of the Xe core in our mixed clusters, as their binding energy shift might be somewhat higher than the one in pure clusters, due to polarization of covering Ar layers.
-Xe cluster features in the spectra of mixed clusters appear less asymmetric than the pure Xe spectrum, and also less asymmetric as some the ArXe spectra shown in ref \citenum{lindblad}.
-This might be caused by the difference in photon energy ($h\nu = 90$ eV in ref \citenum{lindblad} and for the pure Xe spectrum, $h\nu = 32$ eV for the mixed ArXe spectra in this work).
-% For the mixed clusters, the Xe band broadens and shifts towards lower binding energy for larger size clusters.
-%For pure Xe clusters, an asymmetry observed in the Xe 5p$_{3/2}$ part has no counterpart in the respective spectra from the mixed clusters.
-%This might be caused by the difference in photon energy, as can be seen from a comparison to literature spectra (ArXe at $h\nu = 90$ eV in ref \citenum{lindblad}, Xe at $h\nu = 20$ eV in ref \citenum{rolles}).
-%For the largest clusters, the nominal size yielded from the jet parameters applied to a pure Xe expansion would correspond to clusters in which bulk atoms far outweigh those on the surface.
-%At least for the 5p$_{1/2}$ photoelectron line, this would be seen as a clear asymmetry towards the low binding energy side, which is not observed in our spectra.
-
-In Figure \ref{figure:oval2}, we compare the outer valence spectra of clusters with similar expansion conditions, but different composition of the gas mixture.
-A Xe-rich mixture obviously leads to clusters with more intense Xe photolines, but besides that the main change consists in a narrowing of the Ar band.
-A comparison with the Ar monomer features (clipped in the Figure) also shows an increased degree of condensation for the Ar gas in the expansion.
-
-For the smallest clusters we have produced, a possible model is provided by calculated minimum energy structures of Ar$_N$Xe$_{38-N}$ (Figure 7 in ref \citenum{marques}).
-We there see that for a Xe content of less than 60\,\%, core-shell systems are {\it not} formed, and although the Xe atoms tend to connect, the degree of Ar-Xe mixing is large.
-While for low Xe content (approx. 10\,\%), some Ar atoms have only Ar nearest neighbours, for larger Xe content all Ar atoms seem to see both Ar and Xe nearest neighbours.
-We believe this leads to the Ar 3p narrowing pointed out above.
-For Figure \ref{figure:oval2}, possibly, some clusters of our ensemble already are in the core-shell regime, which would lead to an even lower 3p width.
-
-For the largest clusters we have produced (Figure \ref{figure:oval1}b), the low binding energy of the Xe lines and the broadening of the Ar feature without appearance of the `bulk Ar'-maximum, supports formation of a Xe core covered by at least two layers of Ar.
-If the scaling law size for a pure Ar expansion is taken as the lower limit for the cluster size, from the observed Xe content we arrive at clusters composed of a Xe core with four layers, covered by three layers of Ar (see Supporting Information).
-
-Finally, comparing Figure \ref{figure:oval2} to Figure \ref{figure:oval1} reveals that much larger changes in the valence emission spectra occur by changes in size than by changes of the (relative) Xe content.
-This finding is supported by the spectra shown in ref \citenum{lindblad}.
-%
-%
-\subsection{Inner valence spectra}
-%
-We now focus on the Ar inner valence (3s) vacancy states. 
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.8cm]{figure_ival.pdf}
- \caption{
-Photon excited electron spectra of mixed Ar-Xe clusters in the inner valence region.
-Symbols show the Ar 3s photoline from clusters (`cl') and uncondensed Ar monomers (`m'), atop of a background resulting from inelastic intracluster scattering of outer valence photoelectrons (`excitonic satellites').\protect\cite{hergenhahn2002}
-The photon energy was $h\nu = 32$ eV.
-Panel (a) shows all electrons accumulated.
-For the same conditions, in panel (b) we only show electrons that were detected in coincidence with a secondary electron of lower kinetic energy.
-The black solid trace in (a), and red solid trace in (b) result from a least squares fit to the cluster part of the spectrum. 
-The red solid trace in (a) is the fit shown in (b), divided by the detection efficiency of the spectrometer of 0.6.
-Panels (c) and (d) show the same type of data for smaller clusters with a lower Xe content.
-See text for details.
-\label{figure:ival}
-}
-\end{figure}
-
-Figure\ \ref{figure:ival} shows the Ar part of the inner valence spectrum for representative ArXe clusters. 
-The total photoelectron signal looks similar to literature spectra for pure Ar clusters.\cite{feifel,zhang} 
-A low energy tail seen for the Ar 3s monomer line results from the transmission properties of the electron spectrometer, together with the strongly positive angular distribution parameter of this line.\cite{zhang,kruit}
-The Ar 3s cluster line shows no splitting into bulk and surface components, different to the literature on pure clusters but in agreement with our discussion of the outer valence spectra. 
-The binding energy of the cluster line has values between 28.85 and 28.70 eV for all cluster ensembles with size label S-L, and 28.67 eV for the largest clusters measured. 
-A small, but systematic decrease of the binding energy is observed when the cluster size is increased. 
-The value assumed in the simulations is 28.7 eV.
-
-If we produce a spectrum only from those electrons recorded as part of a two-electron coincidence (electron pair with kinetic energies ($e_1,e_2$)) the apparent intensity drops (compare panel b to a, and d to c in Figure \ref{figure:ival}).
-This can partly be attributed to the finite detection efficiency of the spectrometer. 
-Moreover, the monomer part of the Ar 3s signal completely disappears, as 3s photoionization of an uncondensed Ar atom in the gas jet cannot lead to emission of a second electron. 
-Further features of these diagrams and the least squares fits shown in the Figure are discussed below.
-%
-%
-\subsection{ICD/ETMD spectra}
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_icd_12.pdf}
- \caption{
-Energy spectrum of all coincident secondary (ICD or ETMD) electrons of kinetic energy $e_2$ pertaining to primary electrons of kinetic energy $e_1$ in the Ar 3s binding energy region. 
-Spectra were recorded with a photon energy of $h\nu = 32$~eV. 
-Black error bars show the data points for the smallest clusters measured (`S'), two larger clusters sizes are shown by the red and blue traces. 
-Error bars for the latter are smaller than the ones shown and have been omitted.
-For better comparison, all spectra are shown area-normalized. 
-}
- \label{figure:icd_12}
-\end{figure}
-%
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_icd_l.pdf}
- \caption{
-Energy spectrum of all coincident secondary (ICD or ETMD) electrons, kinetic energy $e_2$, for clusters of the same size, but from gas mixtures with different Xe concentration.
-See Figure \protect\ref{figure:icd_12} for details.
-}
- \label{figure:icd_l}
-\end{figure}
-%
-In Figure \ref{figure:icd_12}, we show the spectra of ICD/ETMD electrons pertaining to emission of an Ar 3s cluster photoelectron. 
-Due to their low kinetic energy, without use of a coincidence method they could hardly be separated from the background of inelastically scattered photoelectrons.\cite{mucke}
-This and the following Figure constitute the central experimental result of the article.
-Spectra recorded at $h\nu = 34$ eV as a cross-check quantitatively agree to those shown here.
-This underpins our assignment of this intensity to an autoionization process.
-Further details on the data acquisition and analysis methodology, as well as the 34~eV spectra, are given in the Supporting Information.
-
-Spectra for the three different cluster sizes in Figure \ref{figure:icd_12} are significantly different: Spectra for the larger clusters acquire more intensity in the 1-1.5 eV region and have less intensity for energies below 0.5 eV.
-In contrast to that, the ICD/ETMD spectrum hardly varies when the composition of the expanding gas mixture, and with that the relative Xe content of the clusters, is changed (Figure \ref{figure:icd_l}).
-The full set of ICD/ETMD spectra is shown as Supporting Information.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_eff.pdf}
- \caption{
-Efficiency of the decay of Ar 3s ionized states in ArXe clusters by emission of a secondary electron via ICD or ETMD.
-Values are arranged by Xe content of the initial gas mixture (`+' symbols: 1.2\,\%, asterisk: 3\,\%, triangle: 5\,\%).
-Symbol sizes indicate the photon energy (large symbols: 32 eV, small: 34 eV), and color indicates the cluster size (black symbols: S, red: M, blue: L).
-See text for details.
-}
- \label{figure:eff}
-\end{figure}
-%
-We now discuss which fraction of Ar 3s vacancy states relaxes via ICD or ETMD.
-A method to derive this information has been established by some of us.\cite{foerstel_2013}
-Briefly, we correct the intensity of the Ar 3s photoline in the coincident spectra by the detector efficiency, and divide it by the total (coincident and non-coincident) Ar 3s intensity.
-The result gives the branching ratio of decay via ICD/ETMD vs. the sum of all channels, including those not involving electron emission.
-(If all Ar 3s vacancies decay by emission of another electron, the coincident and non-coincident count rate differ only by the probability for the spectrometer to actually detect the secondary electron.
-This figure has been determined as 0.6 for this data set, in the same way as discussed earlier.\cite{mucke_review})
-To arrive at quantitative results, we have performed least squares fits of the non-coincident and coincident $e_1$ spectra.
-The fits assumed one or two Gaussian peaks, resp., atop of a background modelled by two more Gaussian curves with very large widths.
-The peak pertaining to the Ar 3s cluster photoline, with the background added, is shown by the black solid trace in Figure \ref{figure:ival}a and red solid trace in Figure \ref{figure:ival}b.
-Moreover, the line labelled `c.fit/det.' shows the fit to the coincident events, corrected by the detection efficiency, and plotted atop of the non-coincident intensity. 
-This virtually agrees with the fit to the total spectrum in Figure \ref{figure:ival}a, but not in \ref{figure:ival}c. 
-The corresponding figure for the ICD/ETMD efficiency comes out as one for \ref{figure:ival}a, and significantly smaller than one for \ref{figure:ival}c.
-Figure \ref{figure:eff} shows all results of this analysis.
-The error in the autoionization efficiency shown is mainly determined by uncertainties in the peak/background separation.
-%(Our choice for the background shape is shown in Figure \ref{figure:ival}.)
-For the gas mixture with a Xe$_{\rm in}$ of 1.2\,\%, we therefore show results from fits using two different choices of the background shape in Figure \ref{figure:eff}.
-Statistical errors are much smaller than the differences between the pairs of values arrived at such.
-
-We found an Ar 3s autoionization efficiency which, for clusters with the lowest Xe content (Xe$_{\rm cl}$ approx.
-10-12\,\%), is smaller than unity, and further decreases with decreasing cluster size.
-For larger Xe$_{\rm cl}$, the values are compatible with unity, within the accuracy of our experiment.
-
-%\input{theo_discussion}
-\section{Discussion
-\label{sec:discussion}}
-%
-%We have discussed the experimental spectra in Section \ref{sec:exp_results} and
-%the expected features of spectra for different cluster types in
-%Section \ref{sec:th_results}. In this section we combine the experimental and theoretical
-%results in order to determine the structure of the noble gas clusters.
-%
-%The simulated secondary electron spectra for the xenon core structures
-%(see Figure \ref{figure:xe_3_in})
-%show an ICD peak at higher energies than those structures with added xenon
-%atoms on the surface. This does not fit to the experimentally determined
-%spectra and hence we consider an argon core to be more probable for the
-%small measured clusters.
-%
-%The experimental spectra in Figure \ref{}
-%show a broadening of the secondary electron peak with increasing
-%pressure (?) and hence cluster size just as can be expected from
-%the theoretically simulated spectra in Figure \ref{figure:surf}.
-%
-%From the theoretical simulations of larger small clusters
-%having the same xenon content as experimentally observed a clearly
-%visible ETMD peak is to be expected as shown in Figure \ref{figure:ar_3_6in}.
-%However, the experimental spectra do not show a signal in the energy
-%region of \unit[1.5--6.5]{eV}. From this we conclude that the clusters
-%measured were smaller than 55 atoms containing only very few xenon atoms.
-%Additionally, if the cluster contains more than one xenon atom, they are
-%not expected to be close because of an otherwise visible ETMD peak
-%(compare Figure \ref{figure:2tops}).
-%
-%The large clusters with a large xenon content can be expected to have
-%a xenon core being surrounded by argon layers and hence, both ICD and
-%ETMD should be visible in the spectrum. Unfortunately, the ICD and ETMD
-%peaks overlap such that the two processes can not be distiguished.
-%
-We now would like to interpret our experimental findings in view of the simulated results described in Section `Theoretical Results'.
-Figure \ref{figure:eff} shows that for Ar 3s$^{-1}$ states autoionization by either ICD or ETMD is the only mode of relaxation, except for the clusters with the smallest Xe content.
-We consider this a remarkable result, because ICD of these states is only possible with a Xe atom in the second coordination shell of the decaying Ar vacancy (or shells even further apart), which significantly slows down the ICD process.
-Also decay rates for ETMD were found to be small in early studies of this effect.\cite{zobeley}
-Nevertheless, even in this situation the non-local autoionization channels foreclose radiative decay.
-
-% lowest kinetic energy is the first point of energy raster for t-E code of 52-proc-spec
-Structurally, all experimental ICD/ETMD spectra have a maximum at or near the lowest kinetic energy that could be measured (50~meV), and decrease in intensity to less than half for kinetic energies already below one eV.
-Qualitatively, this shape fits to the ICD contributions in the autoionization spectra discussed in the `Theory' section, but not to the ones from ETMD. 
-The calculated ETMD spectra have a typical three-fold structure with peaks between 3.5-5~eV, 1.5-2.5~eV and around 0 eV kinetic energy. 
-The former two features seem not to be present in the experimental spectra. 
-Due to restrictions in the detector electronics, electron pairs with very similar kinetic energy cannot be detected. 
-The highest kinetic energy for an autoionization electron that can be detected in coincidence with a photoelectron of $\sim3.5$~eV ($h\nu = 32$~eV) is around 2.5~eV.
-Very weak intensity is observed at this energy, and also at higher $e_2$ energies that can be probed at $h\nu = 34$~eV (Supporting Information).
-
-As a cross-check for our theoretical methods we have calculated the radiationless decay spectrum of Ar 3s$^{-1}$ in ArKr, which may arise {\it only} from ETMD(3),\cite{foerstel} and arrived at qualitative agreement with the experimental data.\cite{arkr}
-
-The size-dependent trend within the experimental data is in qualitative agreement to the change in the calculated spectral shape for ICD in systems of increased size (compare Figure~\ref{figure:2tops} to \ref{figure:xe_3_in} and \ref{figure:xe_6_lay5}.)
-
-We are therefore lead to the conclusion that the autoionization spectra we incur are dominated by ICD to non-nearest neighbour atoms, while the intensity of the ETMD channel is low. 
-We would like to recall the factors that lead to a propensity for decay via one or the other mechanism, which have been discussed in the `Theoretical Results'-section.
-For ETMD to occur with a measurable rate, two Xe atoms have to be present in the vincinity of the decaying Ar atom (Figure \ref{figure:2tops}).
-Should that be the case for a large part of the Ar atoms in some cluster structure, ETMD can even dominate over ICD (Figure \ref{figure:ar_3_6in} and Supporting Information).
-Model structures shown in Figures \ref{figure:2tops} and \ref{figure:ar_3_6in} have a Xe content similar to the lowest one probed in our experiment ($\sim$11\,\%).
-For a higher Xe content, ETMD will always dominate the spectra if the two species are given the chance to mix, as e.g.
-in the calculated minimum energy structures of $N=38$ ArXe clusters (Supporting Info).
-On the other hand, in core-shell systems decay via ETMD is probable only for Ar atoms in the interface layer, as this mechanism requires some wavefunction overlap between Ar and one of the Xe atoms involved.
-For the core-shell systems we have investigated, the likelihood of decay via ETMD stays below 25\,\% even for a Xe content above 50\,\% (Table \ref{table:theo_gammas}).
-
-In summary, the two structural motifs that can best be reconciled with our experimental data are
-\begin{enumerate}
-	\item small clusters containing only few Xe atoms that are spread out to distant positions on the cluster surface, and
-	\item systems with a compact Xe core and Ar outer layers.
-\end{enumerate}
-These structures are compatible with the findings of Lindblad {\it et al.}\ from core level photoelectron spectroscopy, who proposed the former structure for the smallest clusters in their study, and the latter for larger ones.\cite{lindblad}
-As even in these two cases intensity for decay via ETMD would not vanish completely, we have to leave it open though whether other mechanisms are present, which further suppress ETMD vs. ICD.
-
-While in early work on ICD it has almost been a paradigm that the decay involves two {\it neighbouring} atoms or molecules,\cite{hergenhahn_review} more recently significant intensity for non-nearest neighbour ICD has been found also in other systems.
-One example is Ne-Ar after Ne 2s ionization, where decay to Ar in the second coordination shell is clearly visible despite the fact that in this system decay involving nearest neighbours is energetically allowed.\cite{fasshauer2014}
-A further theoretical delineation of the respective factors has recently been presented by one of us.\cite{fasshauernjp}
-
-%\input{summary}
-\section{Summary}
-%
-We have presented comprehensive experimental and theoretical data for the
-autoionization of inner valence ionized states in ArXe clusters.
-Both ICD and ETMD are allowed for most cases we considered.
-Because of energetical reasons ICD requires a separation of the final state
-vacancies of \unit[7.58]{\AA} or more, which is about two times the typical
-Ar-Xe distance.
-We found that autoionization has an efficiency of 0.8 to 1.0 within the
-experimental accuracy, that is it dominates over other modes of relaxation.
-By comparing our measured spectra to calculations, we identified `long range'
-ICD as the most important decay mode and were able to determine the most
-probable structural motifs to be a xenon core surrounded by several argon layers
-for large clusters and argon clusters with with very few xenon atoms spread out
-over the surface.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The "Acknowledgement" section can be given in all manuscript
-%% classes.  This should be given within the "acknowledgement"
-%% environment, which will make the correct section or running title.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{acknowledgements}
-\begin{acknowledgement}
-%
-We thank HZB for the allocation of synchrotron radiation beamtime, and the
-Deutsche Forschungsgemeinschaft for funding via the Forschergruppe 1789.
-E. F. gratefully acknowledges the Research
-Council of Norway through a Centre of Excellence Grant (Grant No.\ 179568/V30)
-for funding.
-%
-\end{acknowledgement}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The same is true for Supporting Information, which should use the
-%% suppinfo environment.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{suppinfo}
-
-%This will usually read something like: ``Experimental procedures and
-%characterization data for all new compounds. The class will
-%automatically add a sentence pointing to the information on-line:
-
-%\end{suppinfo}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The appropriate \bibliography command should be placed here.
-%% Notice that the class file automatically sets \bibliographystyle
-%% and also names the section correctly.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliography{arxe}
-
-\end{document}

### 2016-08-02 letters/reply_referee.tex
add reply to referee letter

\documentclass[DIN,pagenumber=false,parskip=half,fromalign=left,fromphone=true,fromemail=true,fromurl=false,fromlogo=false,fromrule=false]{scrlttr2}
\usepackage[utf8]{inputenc}
\usepackage{ngerman}
\usepackage[english]{babel}
\usepackage{units}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage[right]{eurosym}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{braket}
\usepackage{graphicx}
%\RequirePackage{graphicx}

\setkomavar{fromname}{Dr. Elke Faßhauer}
\setkomavar{fromaddress}{Department of Chemistry\\University of Troms\o --- The Artic University of Norway\\9037 Tromsø\\Norway}
\setkomavar{fromphone}{+47 40382485}
\setkomavar{fromemail}{elke.fasshauer@uit.no}
\setkomavar{subject}{Revision of Out Article jp-2016-06665e}
\setkomavar{signature}{Dr. Elke Faßhauer (corresponding author)}

\begin{document}
\begin{letter}{To the Editor}

	\opening{Dear Editor,}

Our paper has been reviewed by two of your Referees,
who recommended it for the publication in the
New Journal of Physics subject to minor amendments.
We are thankful for the comments made by the Referees and
respond to them below. Additionally, we took the opportunity to
{\color{blue}{correct some typos or whatever.}}

\textbf{Referee \#1} raised the following points:

\begin{enumerate}
 \item \emph{In general, I find the manuscript clearly written but unnecessary long. Some details and discussions can be avoided without weakening the presentation. Here are some examples:}
  \begin{enumerate}
   \item \emph{ICD is explained twice in the introduction (top of page 3 and
         3rd paragraph of page 3)}\\
   \item \emph{the sentence: The notion of ICD requires that the electronic orbitals … can be distinguished... make a distinction between ICD and Auger decay. does not bring important informations. Furthermore, using only a one-particle picture to define ICD may be misleading. For example, in molecular clusters ICD can be clearly identified after deep ionization (typically for binding energy above 20 eV) of one molecule. However, owing to the strong electronic correlation in this binding energy range the states cannot be described as ionization from a single orbital.}\\
   \item \emph{Page 9: the sentence “These atoms do not necessarily need to form bonds...” just rephrases what is already explained earlier in the manuscript on ICD.}
   \item \emph{Page 10: the definition of open and close channel is repeated. Explanations in page 9 and figure 1 are enough.}
   \item \emph{Page :
         the section “Cluster Structures” can be moved to Supporting information since only Table 2 is important to understand the results. Furthermore, it seems to me that the paragraph on previous study of the authors on large clusters does provide relevant informations on the reported results.}
   \item \emph{Page:
         the section Outer valence spectra is very detailed and the reader may lose the main point of this section which is, as far as I understood, to evaluate experimentally the percentage of Xe in the clusters. All extra details can be avoided. Just to help the readers, this section could be renamed to highlight the goal of the section like for example “Xe content”.}
   \item \emph{Page:
         I think the section Inner valence spectra can be skipped without losing any relevant informations.}
  \end{enumerate}

  \item \emph{Page 8:
        the authors write that “the intensities of the peaks are proportional to the probability decay as well as the decay width”. However, the probability and the width are simply related : Prob =  Width*time/hbar.}\\
        We included the relation between the decay probability and the decay
        width. However, the important information of this sentence is that
        the decay widths can be used to describe the intensities of the
        different peaks. Therefore, its proportionality is important. The
        sentence now reads:\\
        The latter is proportional to the
probability of the decay {\color{blue}{$P=\frac{\Gamma t}{\hbar}$}}
as well as the theoretically determinable
decay width $\Gamma=\frac{\hbar}{\tau}$,
which is inversely proportional to the lifetime $\tau$ of the decay process.

  \item \emph{Page 11:
        Eqs 6 and 7 the sums run over ALL pairs and ALL triples. In that case there should not be $N_{ICD,i}$ and $N_{ETMD,j}$ in the sums; otherwise those pairs and triples are counted several times.}\\
        It now reads:\\
        These are given by the sum over the decay widths of all 
        {\color{blue}{geometrically different}} pairs $i$ for the
        ICD and all {\color{blue}{geometrically different}} triples $j$
        for the ETMD(3),
        respectively, and over all channels $\beta$:

  \item \emph{Page 12:
        some symbols are not defined: $\Phi_{in}$, $\chi_\beta$, $H_f$
        for example.
        Since this part of theory has already been published, it can be shorten
        leaving just Eqs. 9 and 10.
}

  \item \emph{Page 12:
        ionization cross-sections, radiative lifetimes,... are not EXPERIMENTAL properties of atoms, they are intrinsic properties of atoms that can be experimentally measured.}

  \item \emph{As far as I understand Figs 4-8 report Widths with respect to Electron energy and are thus not strictly speaking electron emission spectra. The authors should really compute the spectra. Furthermore, the lines which I guess are some convolution of the bars are not defined. And more importantly, how these “spectra” were normalized is not clear: in the cluster with 55 Ar atoms the central and inner layer of atoms can undergo ICD. A more intense band compared to 13 atoms is therefore expected. More explanations are needed.}

  \item \emph{Page 18:
        it is stated that the decay width decreases like R-6 but in page 20 it decreases exponentially.
}

  \item \emph{Page 29:
        the efficiency of ICD is found below unity for clusters having few Xe atoms. I guess this is because in these clusters ICD and ETMD are closed for some Argon atoms which are anyway ionized. Maybe a statistical model may explain it. The theory could also help since it should be easy to determine the efficiency for all clusters considered in this study.}

\end{enumerate}

\textbf{Referee \#2} raised the following points:

\begin{enumerate}
 \item \emph{ETMD(3) should be explained in the introduction by a sentence or two to aid the reader (at the moment, it is first explained in the theory section).
}
 \item \emph{The authors mention that the ‘nuclear dynamics may play an important role’ but that they have been neglected in the calculations. While I understand that it is not feasible in such large systems the authors should at least briefly discuss the possible effect of nuclear dynamics e.g. peak shifts, broadening, ICD vs. ETMD, etc. }

 \item \emph{The spin-orbit splitting of the Ar 3p$^{-1}$ state is briefly mentioned in Table 3 in the experimental section but it also stated that the a single value of the binding energy of Ar 3p equal to 15.3 eV is used for all of the simulations. The authors should explain the motivation for this choice in the theory section.}

 \item \emph{Page 13:
       The authors should justify the use of the ‘unified force field’ method for the calculation f the cluster structure (p13).}

 \item \emph{Page 12:
       On page 12 last line there is to Tables II and III. I have not been able to locate these. The reference should be clarified.}

 \item \emph{Page 20,21:
       it is not clear what structure of the larger clusters with 3871 atoms is used in the simulation. The authors mention icosahedral and cuboctahedral but no further details are given, e.g. Ar-Xe distance, Ar-Ar distance, etc.}

 \item \emph{In fig. 9(a) it is specified in the text that  Ar <N> =190 for the black trace but as far as I can tell no value is given for the other spectrum on the same graph.}

 \item \emph{It is not clear what the dotted lines in Figure 10 are?}

 \item \emph{The colour schemes of some of the figures lead to confusion when printed in grayscale. Some effort could be made to resolve this.}

\end{enumerate}

I took the opportunity to shorten the title in order to not highlight only
one out of several aspects. It now reads:\\
      Non-nearest Neighbour ICD in 
      Clusters

        \closing{Sincerely yours,}
	\end{letter}

\end{document}

### 2016-08-03 letters/reply_referee.tex
easy changes for reply

@@
         Since this part of theory has already been published, it can be shorten
-        leaving just Eqs. 9 and 10.
-}
+        leaving just Eqs. 9 and 10.}\\
+        This part of the theory has indeed been published already. However,
+        the general formula for the decay width of electronic decay processes
+        serves as the best starting point for the explanation since it is
+        known by a wider community. For the same reason, equation 11 should
+        be shown, as it connects the earlier formulation and the new more
+        abstract formulation in equation 10. We therefore rephrased the
+        paragraph to read:\\
+        {\color{blue}{
+        \begin{equation}
+         \Gamma_{\beta}(E_{\rm res}) = 2\pi \left|
+                                   \braket{\Phi_{\rm in}| \hat{V} |\chi_{\beta}}
+                                   \right|^2,
+        \end{equation}
+%
+where $\ket{\Phi_{\rm in}}$ and $\ket{\chi_{\beta}}$ are the initial and final
+state, respectively and $\hat{V}$ is the interaction operator between these
+two, can be approximated by its asymptotic behaviour.
+For the ICD the approximation reads:}}
+%
+\begin{equation}
+ \Gamma_{{\rm ICD},i,\beta} = (2J_{\rm in}+1)\, \frac{3c^4}{8\pi}\,
+                        \sum\limits_{M_{in}'}
+                        \left| \left(
+                        \begin{array}{ccc}
+                        J_A'  & 1        & J_A\\
+                        -M_A' & M_A'-M_A & M_A
+                        \end{array}\right) \right|^2
+                        \frac{\sigma^{(X_E)}(\omega_{vp,\beta})}
+                        {R_i^6 \, \omega_{vp,\beta}^4 \tau_{in,\beta}},
+\end{equation}                                                 
+%
+where $J_A$, $J_A'$ and $M_A$, $M_A'$ denote the total angular momentum of the
+initially ionized atom (which is the same as the electron donor atom) in the 
+initial and final state, respectively,
+{\color{blue}{which otherwise depends on
+intrinsic atomic properties
+which can be determined experimentally, like the ionization
+cross sections
+$\sigma^{(X_E)}(\omega_{vp,\beta})$, radiative lifetimes of the initially
+ionized state $\tau_{in,\beta}$ and the excess energy transferred to the
+emitting atom (the energy of the virtual photon) $\omega_{vp,\beta}$.
+
+For the ETMD(3) the approximation reads}}
+%
+\begin{align}                                                  
+ \Gamma_{{\rm ETMD},j,\beta} =& \frac{c}{\pi} \sum\limits_{m,M_{in,D'}}      
+                        \frac{\Theta_{m,k}(\alpha_j) \sigma^{(X_E)}(\omega_{vp,\beta})
+                              \left| <\tilde{D}_{m,j,\beta}(M_{in,D'})>\right|^2}
+                         {R_j^6 \omega_{vp,\beta}}\\           
+               =& \frac{c}{\pi R_j^6}                          
+               \sum\limits_{M_{in,D'}}                         
+               \left( \left| <\tilde{D}_{x,j,\beta} (M_{in,D'}) > \right|^2  
+                 (2+ \sin^2\alpha_j)                           
+               + \left| <\tilde{D}_{z,j,\beta} (M_{in,D'}) > \right|^2       
+                 (1+\cos^2\alpha_j) \right) \nonumber \\       
+           & \times\, \frac{c\sigma^{(X_E)}(\omega_{vp,\beta})}{\omega_{vp,\beta}}
+\end{align}                                                    
+%                                                              
+{\color{blue}{
+where $\tilde{D}_{m,j,\beta}$ are calculated transition dipole moments and}}
+$\Theta_{m}(\alpha_j)$ is a function depending on the angle $\alpha_j$       
+of the triple and the direction of the dipole                  
+transition moment $m$ ...
 
   \item \emph{Page 12:
-        ionization cross-sections, radiative lifetimes,... are not EXPERIMENTAL properties of atoms, they are intrinsic properties of atoms that can be experimentally measured.}
+        ionization cross-sections, radiative lifetimes,... are not EXPERIMENTAL properties of atoms, they are intrinsic properties of atoms that can be experimentally measured.}\\
+        Agreed. The sentence now reads:\\
+        ... on {\color{blue}{intrinsic atomic properties
+        which can be determined experimentally}}, like the ionization
+        cross sections
+        $\sigma^{(X_E)}(\omega_{vp,\beta})$, radiative lifetimes of the initially
+        ionized state $\tau_{in,\beta}$ ...
 
@@
   \item \emph{Page 18:
-        it is stated that the decay width decreases like R-6 but in page 20 it decreases exponentially.
-}
+        it is stated that the decay width decreases like R-6 but in page 20 it decreases exponentially.}\\
+        The reason is that it discusses different interatomic distances being
+        the energy transfer distance $R$ ($R^{-6}$) and the electron
+        transfer distance $Q$ ($e^{-Q}$) which can both be found in previous and
+        coming papers about ETMD(3) (J. Chem. Phys. \textbf{138}, 014305 (2013).
+        and Fasshauer \emph{et al.} Mol. Phys. (2016), submitted.):
+\begin{center}
+ \includegraphics[width=6cm]{../pics/coord_systems.pdf}
+\end{center}
+        Both on page 18 and 20, these distances are very clearly characterized
+        in terms involved atom types or groups and which process is ongoing.
+        To further clarify the matter, the sentences on page 18 now read:\\
+        Two aspects have to be taken into account: an energy shift of the peaks
+        due to different charge distances {\color{blue}{$d$}} in the
+        final state (i.e. the interatomic Xe-Xe
+        distance) and the decrease of the decay width with $R^{-6}$,
+        $R$ being the distance between the electron transfer unit and the xenon
+        atom ionized in the final state.
+        The larger the distance between the xenon atoms, the higher are the
+        energies of the secondary electrons{\color{blue}{. For the case of xenon
+        atoms on argon surfaces this at the same time means a larger distance
+        between the Ar-Xe pair involved in the electron transfer and the
+        electron emitting xenon atom. Hence, the decay widths are smaller.}}
+        Therefore, a
+        significant contribution from ETMD(3) compared to ICD is only
+        seen if the two xenon atoms reside on two adjacent
+        surfaces.
 
@@
        The authors should justify the use of the ‘unified force field’ method for the calculation f the cluster structure (p13).}
+       We added a sentence to justify our choice:\\
+       After that, the cluster structures were optimized using the unified
+       force field implemented in the Avogadro programme
+       (version 1.1.0)$^{51,52}$ to give local minimum structures.
+       {\color{blue}{ The method
+       was chosen due to its low computational cost, the possibility to find
+       the next local minimum structure based on the chosen starting point
+       and the necessary effort to produce reliable results with density
+       functional theory (DFT) for v. d. Waals interactions since we in
+       this work discuss structural trends and not absolute structures.}}
 
  \item \emph{Page 12:
-       On page 12 last line there is to Tables II and III. I have not been able to locate these. The reference should be clarified.}
+       On page 12 last line there is to Tables II and III. I have not been able to locate these. The reference should be clarified.}\\
+       The sentence has been changed to:\\
+       In this work we evaluate the secondary energies and decay widths with
+       the programme HARDRoC$^{20,49}$ using the experimental ionization energies
+       of Table 3 and data from the literature given in Tables II and III
+       {\color{blue}{of Ref. 34.}}\\
+       The following sentence was removed.
 
@@
 The authors mention icosahedral and cuboctahedral but no further details are given, e.g.
-Ar-Xe distance, Ar-Ar distance, etc.}
+Ar-Xe distance, Ar-Ar distance, etc.}\\
+       The details were added to the Cluster Structures section. The last
+       sentences now read:\\
+       Furthermore, for comparison with the largest measured ArXe clusters,
+       we constructed also larger core-shell structures (Table 2, \#4 – 5).
+       {\color{blue}{These were idealized icosahedral and cuboctahedral
+       structures based on the v. d. Waals radii of argon and xenon
+       $r_{Ar} =$\unit[1.88]{\AA}$^{54}$
+       and $r_{Xe} =$\unit[2.16]{\AA}$^{55}$.}}
 

### 2016-08-03 structures.tex
easy changes for reply

@@
 Avogadro programme (version 1.1.0) \cite{Avogadro,Hanwell12} to give local
-minimum structures.
+minimum structures. The method was chosen due to its low computational cost,
+the possibility to find the next local minimum structure based on the chosen
+starting point and the necessary effort to produce reliable results
+with density functional theory (DFT) for
+v. d. Waals interactions since we in this work discuss structural trends and
+not absolute structures.
 All cluster structures are listed in Table \ref{table:theo_gammas}.
@@
 Furthermore, for comparison with the largest measured ArXe clusters, we constructed also larger core-shell structures (Table \ref{table:theo_gammas}, \#4--5).
+These were idealized icosahedral and cuboctahedral structures based on the
+v. d. Waals radii of argon and xenon $r_{Ar}=$\unit[1.88]{\AA} \cite{Herman88}
+and $r_{Xe}=$\unit[2.16]{\AA} \cite{Freeman74}.

### 2016-08-03 theo_results.tex
add changes from Melanie
easy changes for reply

@@
 Two aspects have to be taken into account: an energy shift of the peaks due
-to different charge distances in the final state (i.e. the interatomic Xe-Xe
+to different charge distances $d$ in the final state (i.e. the interatomic Xe-Xe
 distance) and the decrease of the decay width with $R^{-6}$, $R$ being the distance
@@
 The larger the distance between the xenon atoms, the higher are the energies
-of the secondary electrons and the smaller are the decay widths. 
+of the secondary electrons. For the case of xenon atoms on argon surfaces
+this at the same time means a larger distance between the Ar-Xe pair involved in
+the electron transfer and the electron emitting xenon atom. Hence, the
+decay widths are smaller. 
 Therefore, a
@@
           cuboctahedral basic structure.
-          The ICD and ETMD peak overlap such, that the peak
-          structure might not be visible.}
+          The ICD and ETMD peak overlap such that the ETMD peak
+          is unlikely to be visible.}
  \label{figure:xe_6_lay5}

### 2016-08-03 theory.tex
easy changes for reply

@@
 and the intensities of the peaks. The latter is proportional to the
-probability of the decay as well as the theoretically determinable
+probability of the decay $P=\frac{\Gamma t}{\hbar}$
+as well as the theoretically determinable
 decay width $\Gamma=\frac{\hbar}{\tau}$,
@@
 
-%We are interested in describing the electron emission spectra of excited states in clusters, that where measured by the electron-electron coincidence method in our experiments. 
-%In our theoretical description, these will be composed of multiple transitions, each characterized by a kinetic energy $E_{\rm sec}$ of the secondary electrons, and the intensity of the peak.
-%The latter is proportional to the probability of the decay, represented here by the decay width $\Gamma_\beta = \hbar/\tau_\beta$, where $\tau_\beta$ is the lifetime due to the respective transition.
-%The total decay width $\Gamma$ is the sum of all partial $\Gamma_\beta$.
-%In case of noble gas clusters with a given geometrical structure, three aspects have to be taken into account:
-%different decay mechanisms, the contribution of different cluster sites to the respective decay, and the existence of different decay channels within each decay mechanism.
-%At the current stage of development we have to neglect the nuclear dynamics, which
-
 This means, for the evaluation of the decay width we are dealing with a sum over three different indices: 
@@
 In the following, this approach will be called model of pairs and triples.
-
-%Decomposing every system into pairs and triples of atoms is a very useful
-%first order approximation to both the investigation of energies and
-%decay widths of a larger system. Pairs and triples are combinations of
-%two and three atoms, respectively.
 
@@
 
-These are given by the sum over the decay widths of all pairs $i$ for the
-ICD and all triples $j$ for the ETMD(3), respectively, and over all channels $\beta$:
+These are given by the sum over the decay widths of all 
+geometrically different pairs $i$ for the
+ICD and all geometrically different triples $j$ for the ETMD(3),
+respectively, and over all channels $\beta$:
 %
@@
  \Gamma_{\beta}(E_{\rm res}) = 2\pi \left|
-                           \braket{\Phi_{\rm in}| H_f |\chi_{\beta}}
+                           \braket{\Phi_{\rm in}| \hat{V} |\chi_{\beta}}
                            \right|^2,
@@
 %
-can be approximated by its asymptotic behaviour
+where $\ket{\Phi_{\rm in}}$ and $\ket{\chi_{\beta}}$ are the initial and final
+state, respectively and $\hat{V}$ is the interaction operator between these
+two, can be approximated by its asymptotic behaviour.
+For the ICD the approximation reads:
 %
@@
 initially ionized atom (which is the same as the electron donor atom) in the
-initial and final state, respectively,
-and
+initial and final state, respectively, which otherwise depends on
+intrinsic atomic properties
+which can be determined experimentally, like the ionization
+cross sections
+$\sigma^{(X_E)}(\omega_{vp,\beta})$, radiative lifetimes of the initially
+ionized state $\tau_{in,\beta}$ and the excess energy transferred to the
+emitting atom (the energy of the virtual photon) $\omega_{vp,\beta}$.
+
+For the ETMD(3) the approximation reads
 %
@@
 %
-depending on 
-experimental properties
-of atoms, like the ionization cross sections
-$\sigma^{(X_E)}(\omega_{vp,\beta})$, radiative lifetimes of the initially
-ionized state $\tau_{in,\beta}$ and the excess energy transferred to the
-emitting atom (the energy of the virtual photon) $\omega_{vp,\beta}$
-and calculated dipole transition moments $\tilde{D}_{m,j,\beta}$, only.
-Here, $\Theta_{m}(\alpha_j)$ is a function depending on the angle $\alpha_j$
+where $\tilde{D}_{m,j,\beta}$ are calculated transition dipole moments and
+$\Theta_{m}(\alpha_j)$ is a function depending on the angle $\alpha_j$
 of the triple and the direction of the dipole
@@
 experimental ionization energies of Table \ref{tab:valence}
-and data from the literature given in Tables II and III.
-This choice is identical to the one made in ref \citenum{Fasshauer13}.
+and data from the literature given in Tables II and III of
+Ref. \citenum{Fasshauer13}.

### 2016-08-05 letters/reply_referee.tex
first changes

@@
          3rd paragraph of page 3)}\\
+
+				We have deleted the explanation of ICD in the 3rd pargraph of page 3.
+
    \item \emph{the sentence: The notion of ICD requires that the electronic orbitals … can be distinguished...
@@
 However, owing to the strong electronic correlation in this binding energy range the states cannot be described as ionization from a single orbital.}\\
+
+				The referee is correct, the statement does not bring new information.
+We have therefore deleted this section from the manuscript.
+That is also in accordance to the referees notion that the manuscript is too long.
+
    \item \emph{Page 9: the sentence “These atoms do not necessarily need to form bonds...” just rephrases what is already explained earlier in the manuscript on ICD.}
@@
 However, the probability and the width are simply related : Prob =  Width*time/hbar.}\\
+
         We included the relation between the decay probability and the decay

### 2016-08-05 intro.tex
first changes

@@
 systems. Experimental and theoretical progress has been reviewed.
-\cite{hergenhahn_review, averbukh_review, jahnke_review} ICD 
-proceeds by an initial ionization producing an ion in an excited 
-state, followed by a transfer of energy to a neighbouring site, 
-and an electron emission process therefrom. The final state contains 
-two positive charges; one at the original site of ionization, and a second
-one at another atom or molecule.
+\cite{hergenhahn_review, averbukh_review, jahnke_review}
 
@@
 autoionization play a role in Ar-Xe, and will detail the 
-relevant processes below. The notion of ICD requires that the 
-electronic orbitals of the two sites can be distinguished, which 
-typically is the case in weakly bonded systems, held together by 
-hydrogen bonds or van-der-Waals bonds. In the case of strong
-(covalent or metallic) bonding, it is impossible to make a
-distinction between ICD and Auger decay.\cite{hergenhahn_review}
+relevant processes below.
 

### 2016-08-05 letters/reply_referee.tex
point 1e included...

@@
 Just to help the readers, this section could be renamed to highlight the goal of the section like for example “Xe content”.}
+
+				The referee is correct if one reads the article from a theoreticians point of view.
+However, the outer valence spectra of our clusters were not reported in this detail earlier nor were they ever discussed.
+We therefore think that this section holds very valuable information for the experimentalist which we do not want to hide in the supplementary section.
+To accommodate the referees suggestion we have included two sentences in the beginning of the section, summarizing the points that are most important for the theory part of the article: \color{blue}{This section describes and discusses the outer valence spectra of the mixed Ar-Xe clusters.
+The main information we obtain from these spectra within the context of our theoretical considerations are the relative Xe contents in the mixed cluster.}
+
    \item \emph{Page:

### 2016-08-05 letters/reply_referee.tex
most theory related erferee comments

--- 2016-08-03 letters/reply_referee.tex
@@
 However, owing to the strong electronic correlation in this binding energy range the states cannot be described as ionization from a single orbital.}\\
-   \item \emph{Page 9: the sentence “These atoms do not necessarily need to form bonds...” just rephrases what is already explained earlier in the manuscript on ICD.}
-   \item \emph{Page 10: the definition of open and close channel is repeated. Explanations in page 9 and figure 1 are enough.}
-   \item \emph{Page :
+   \item \emph{Page 9: the sentence “These atoms do not necessarily need to form bonds...” just rephrases what is already explained earlier in the manuscript on ICD.}\vspace{0.3cm}\\
+         The comment skips the important part of the argumentation, which is
+         that the units/atoms do not need to be close. The comment about the
+         bonding situation was made intentionally to clarify the difference
+         between pairs and triples on the one hand and dimers and trimers on
+         the other hand. We therefore do not change the sentence.
+
+   \item \emph{Page 10: the definition of open and close channel is repeated. Explanations in page 9 and figure 1 are enough.}\vspace{0.3cm}\\
+         The explanation on page 10 belongs to the explanation on page 9, which
+         would not be understandable without half of the text. While the
+         text formulates the general concept, the figure illustrates this concept
+         on an example which is this manuscript's system under investigation.
+         Since also the caption of the figure should be understandable without
+         reading the text, we do not shorten the manuscript at this point.
+
+   \item \emph{Page 13:
          the section “Cluster Structures” can be moved to Supporting information since only Table 2 is important to understand the results.
-Furthermore, it seems to me that the paragraph on previous study of the authors on large clusters does provide relevant informations on the reported results.}
+Furthermore, it seems to me that the paragraph on previous study of the authors on large clusters does provide relevant informations on the reported results.}\vspace{0.3cm}\\
+         We object to move the pictures showing
+         some classes of systems under investigation,
+         which is far less the all systems, to the
+         supplementary information. Additionally, the paragraph the reviewer
+         refers to are two paragraphs. Since the section only consists of
+         four paragraphs in total, the first one explains the general
+         procedure of the manuscript and the fourth explains the pictures of
+         the classes, there is nothing left to reasonably be moved to the
+         Supplementary Information. We therefore don't change the manuscript
+         in this point.
+
    \item \emph{Page:
@@
 A more intense band compared to 13 atoms is therefore expected.
-More explanations are needed.}
+More explanations are needed.}\vspace{0.3cm}\\
+        The first part of the reviewer's comment is confusing. We have clearly
+        explained the direct proportionality between the decay width and
+        the probability of the decay for a given initial and a given final state,
+        which is also related to a specific kinetic energy of the emitted
+        electron. This gives a stick spectrum within the limitations
+        of the model as explained in the theory section. The convoluted stick
+        spectrum then gives the estimated spectrum
+        (for details see the adjustments made for
+        comment to reviewer \# 2 point 2).\\
+        In terms of the normalization we agree with the reviewer that this part
+        was not explicitly described and we therefore added the following
+        paragraph to the theory section:\\
+        {\color{blue}{The decay width for the total system is in the end
+        normalized to the decay width
+        per initially ionized atom since we are interested in the events
+        after one ionization which could be located at any of the atoms of
+        the corresponding atom
+        type. We thereby yield an averaged decay width for the cluster structure.
+        This step allows the comparison of the total average decay widths
+        between cluster structures of different size and composition.}}
+        \vspace{0.3cm}\\
+        This means, that in the 13 and 55 atoms argon clusters with one
+        additional xenon atom
+        located on one of its surfaces, there are 13 or 55 potentially
+        initially ionized atoms. Inspecting Figure 4, lower panel, it is
+        evident, that the number of pairs for which all decay channels are
+        closed is similar for the 14 and the 56 atom cluster. However,
+        the distribution of pairs with open decay channels is significantly
+        different. The 14 atom cluster has only a few more pairs which are
+        characterized by comparably small distances. Therefore, each of these
+        pairs will have a significant decay width. In case of the 56 atoms
+        cluster there are many pairs with open channels characterized by many
+        different distances and especially much larger distances than in the
+        14 atoms cluster. Therefore, the average decay width is smaller in the
+        56 atoms cluster than in the 14 atoms cluster.
+        The reviewers intuition would be correct if the atom types of argon
+        and xenon atoms were interchanged.
 

### 2016-08-05 intro.tex
most theory related erferee comments

@@
 systems. Experimental and theoretical progress has been reviewed.
-\cite{hergenhahn_review, averbukh_review, jahnke_review}
+\cite{hergenhahn_review, averbukh_review, jahnke_review} ICD 
+proceeds by an initial ionization producing an ion in an excited 
+state, followed by a transfer of energy to a neighbouring site, 
+and an electron emission process therefrom. The final state contains 
+two positive charges; one at the original site of ionization, and a second
+one at another atom or molecule.
 
 Soon after, related 
-autoionization processes were discovered that proceed via a 
+autoionization processes were discovered that are governed by a
 charge transfer instead of an energy transfer. 
@@
 normal ICD amplitude.\cite{santrarev,jahnkesat}
+
 We find that both energy and charge transfer induced 
 autoionization play a role in Ar-Xe, and will detail the 
-relevant processes below.
+relevant processes below. The notion of ICD requires that the 
+electronic orbitals of the two sites can be distinguished, which 
+typically is the case in weakly bonded systems, held together by 
+hydrogen bonds or van-der-Waals bonds. In the case of strong
+(covalent or metallic) bonding, it is impossible to make a
+distinction between ICD and Auger decay.\cite{hergenhahn_review}
 

### 2016-08-05 theory.tex
most theory related erferee comments

@@
 
+The decay width for the total system is in the end normalized to the decay width
+per initially ionized atom since we are interested in the events after one
+ionization which could be located at any of the atoms of the corresponding atom
+type. We thereby yield an averaged decay width for the cluster structure.
+This step allows the comparison of the total average decay widths
+between cluster structures of different size and composition.
+
 In this work we evaluate the secondary energies and decay widths with

### 2016-08-05 letters/reply_referee.tex
ref1.8

--- 2016-08-05 letters/reply_referee.tex
@@
 \usepackage[utf8]{inputenc}
-\usepackage{ngerman}
+%\usepackage{ngerman}
 \usepackage[english]{babel}
@@
 Just to help the readers, this section could be renamed to highlight the goal of the section like for example “Xe content”.}
+
+				The referee is correct if one reads the article from a theoreticians point of view.
+However, the outer valence spectra of our clusters were not reported in this detail earlier nor were they ever discussed.
+We therefore think that this section holds very valuable information for the experimentalist which we do not want to hide in the supplementary section.
+To accommodate the referees suggestion we have included two sentences in the beginning of the section, summarizing the points that are most important for the theory part of the article: {\color{blue}This section describes and discusses the outer valence spectra of the mixed Ar-Xe clusters.
+The main information we obtain from these spectra within the context of our theoretical considerations are the relative Xe contents in the mixed clusters.}
+
    \item \emph{Page:
          I think the section Inner valence spectra can be skipped without losing any relevant informations.}
+
+				Here we disagree with the referee.
+The presentation and discussion of the inner valence spectra is very relevant because they form the basis for our theoretical considerations.
+Additionally, they provide further direct insight into the structure of our clusters.
+An experimentally interested reader would surely miss the information provided here.
+
   \end{enumerate}
@@
 
+				This is a good point from the referee.
+We have included a short discussion of the possible explanations of this effect at the respective place: {\color{blue}{In clusters with a low Xe content we can assume that there are Ar atoms that have distances to the next Xe atom that are too large for autoionization to occur.
+This is especially the case if we have very large clusters that show segregation of Ar and Xe atoms.
+If we decrease the cluster size, this effect should play a minor role because large distances are not available here.
+However, with decreasing cluster size, the number of homogeneous clusters in the cluster beam increases.
+In fact, at small cluster sizes, the size distribution has its maximum at the monomer.
+This increasing number of homogeneous Ar clusters still show Ar 3s intensity but do not contribute to recorded coincidences because they cannot autoionize.
+}
+
 \end{enumerate}

### 2016-08-05 exp_results.tex
point 1e included...
ref1.8

@@
 \subsection{Outer valence spectra}
+%
+This section describes and discusses the outer valence spectra of the mixed Ar-Xe clusters.
+The main information we obtain from these spectra within the context of our theoretical considerations are the relative Xe contents in the mixed clusters (see Table\ \ref{tab:valence}).
 %
@@
 
-We found an Ar 3s autoionization efficiency which, for clusters with the lowest Xe content (Xe$_{\rm cl}$ approx.
-10-12\,\%), is smaller than unity, and further decreases with decreasing cluster size.
+We found an Ar 3s autoionization efficiency which, for clusters with the lowest Xe content (Xe$_{\rm cl}$ approx. 10-12\,\%), is smaller than unity, and further decreases with decreasing cluster size.
+
+In clusters with a low Xe content we can assume that there are Ar atoms that have distances to the next Xe atom that are too large for autoionization to occur.
+This is especially the case if we have very large clusters that show segregation of Ar and Xe atoms.
+If we decrease the cluster size, this effect should play a minor role because large distances are not available here.
+However, with decreasing cluster size, the number of homogeneous clusters in the cluster beam increases.
+In fact, at small cluster sizes, the size distribution has its maximum at the monomer.
+This increasing number of homogeneous Ar clusters still show Ar 3s intensity but do not contribute to recorded coincidences because they cannot autoionize.
 For larger Xe$_{\rm cl}$, the values are compatible with unity, within the accuracy of our experiment.

### 2016-08-05 letters/reply_referee.tex

--- 2016-08-05 letters/reply_referee.tex
@@
 However, owing to the strong electronic correlation in this binding energy range the states cannot be described as ionization from a single orbital.}\\
+				The referee is correct, the statement does not bring new information.
+We have therefore deleted this section from the manuscript.
+That is also in accordance to the referees notion that the manuscript is too long.
    \item \emph{Page 9: the sentence “These atoms do not necessarily need to form bonds...” just rephrases what is already explained earlier in the manuscript on ICD.}\vspace{0.3cm}\\

### 2016-08-05 letters/reply_referee.tex

@@
 We therefore think that this section holds very valuable information for the experimentalist which we do not want to hide in the supplementary section.
-To accommodate the referees suggestion we have included two sentences in the beginning of the section, summarizing the points that are most important for the theory part of the article: \color{blue}{This section describes and discusses the outer valence spectra of the mixed Ar-Xe clusters.
-The main information we obtain from these spectra within the context of our theoretical considerations are the relative Xe contents in the mixed cluster.}
+To accommodate the referees suggestion we have included two sentences in the beginning of the section, summarizing the points that are most important for the theory part of the article: {\color{blue}This section describes and discusses the outer valence spectra of the mixed Ar-Xe clusters.
+The main information we obtain from these spectra within the context of our theoretical considerations are the relative Xe contents in the mixed clusters.}
 
@@
          I think the section Inner valence spectra can be skipped without losing any relevant informations.}
+
+				Here we disagree with the referee.
+The presentation and discussion of the inner valence spectra is very relevant because they form the basis for our theoretical considerations.
+Additionally, they provide further direct insight into the structure of our clusters.
+An experimentally interested reader would surely miss the information provided here.
+
   \end{enumerate}

### 2016-08-05 letters/reply_referee.tex
not so nice merge

@@
 \usepackage[utf8]{inputenc}
-%\usepackage{ngerman}
+\usepackage{ngerman}
 \usepackage[english]{babel}
@@
 We therefore think that this section holds very valuable information for the experimentalist which we do not want to hide in the supplementary section.
-To accommodate the referees suggestion we have included two sentences in the beginning of the section, summarizing the points that are most important for the theory part of the article: {\color{blue}This section describes and discusses the outer valence spectra of the mixed Ar-Xe clusters.
-The main information we obtain from these spectra within the context of our theoretical considerations are the relative Xe contents in the mixed clusters.}
+To accommodate the referees suggestion we have included two sentences in the beginning of the section, summarizing the points that are most important for the theory part of the article: \color{blue}{This section describes and discusses the outer valence spectra of the mixed Ar-Xe clusters.
+The main information we obtain from these spectra within the context of our theoretical considerations are the relative Xe contents in the mixed cluster.}
 
    \item \emph{Page:
-         I think the section Inner valence spectra can be skipped without losing any relevant informations.}
-
+         I think the section Inner valence spectra can be skipped without losing any relevant informations.}\vspace{0.3cm}\\
          Here we disagree with the referee.
@@
 Maybe a statistical model may explain it.
-The theory could also help since it should be easy to determine the efficiency for all clusters considered in this study.}
-
+The theory could also help since it should be easy to determine the efficiency for all clusters considered in this study.}\vspace{0.3cm}\\
         This is a good point from the referee.
@@
 This increasing number of homogeneous Ar clusters still show Ar 3s intensity but do not contribute to recorded coincidences because they cannot autoionize.
-}
+}}
 

### 2016-08-05 letters/reply_referee.tex
ref2

--- 2016-08-05 letters/reply_referee.tex
@@
 However, owing to the strong electronic correlation in this binding energy range the states cannot be described as ionization from a single orbital.}\\
+
 				The referee is correct, the statement does not bring new information.
@@
 That is also in accordance to the referees notion that the manuscript is too long.
-   \item \emph{Page 9: the sentence “These atoms do not necessarily need to form bonds...” just rephrases what is already explained earlier in the manuscript on ICD.}\vspace{0.3cm}\\
-         The comment skips the important part of the argumentation, which is
-         that the units/atoms do not need to be close. The comment about the
-         bonding situation was made intentionally to clarify the difference
-         between pairs and triples on the one hand and dimers and trimers on
-         the other hand. We therefore do not change the sentence.
 
-   \item \emph{Page 10: the definition of open and close channel is repeated. Explanations in page 9 and figure 1 are enough.}\vspace{0.3cm}\\
-         The explanation on page 10 belongs to the explanation on page 9, which
-         would not be understandable without half of the text. While the
-         text formulates the general concept, the figure illustrates this concept
-         on an example which is this manuscript's system under investigation.
-         Since also the caption of the figure should be understandable without
-         reading the text, we do not shorten the manuscript at this point.
-
-   \item \emph{Page 13:
+   \item \emph{Page 9: the sentence “These atoms do not necessarily need to form bonds...” just rephrases what is already explained earlier in the manuscript on ICD.}
+   \item \emph{Page 10: the definition of open and close channel is repeated. Explanations in page 9 and figure 1 are enough.}
+   \item \emph{Page :
          the section “Cluster Structures” can be moved to Supporting information since only Table 2 is important to understand the results.
-Furthermore, it seems to me that the paragraph on previous study of the authors on large clusters does provide relevant informations on the reported results.}\vspace{0.3cm}\\
-         We object to move the pictures showing
-         some classes of systems under investigation,
-         which is far less the all systems, to the
-         supplementary information. Additionally, the paragraph the reviewer
-         refers to are two paragraphs. Since the section only consists of
-         four paragraphs in total, the first one explains the general
-         procedure of the manuscript and the fourth explains the pictures of
-         the classes, there is nothing left to reasonably be moved to the
-         Supplementary Information. We therefore don't change the manuscript
-         in this point.
-
+Furthermore, it seems to me that the paragraph on previous study of the authors on large clusters does provide relevant informations on the reported results.}
    \item \emph{Page:
@@
 A more intense band compared to 13 atoms is therefore expected.
-More explanations are needed.}\vspace{0.3cm}\\
-        The first part of the reviewer's comment is confusing. We have clearly
-        explained the direct proportionality between the decay width and
-        the probability of the decay for a given initial and a given final state,
-        which is also related to a specific kinetic energy of the emitted
-        electron. This gives a stick spectrum within the limitations
-        of the model as explained in the theory section. The convoluted stick
-        spectrum then gives the estimated spectrum
-        (for details see the adjustments made for
-        comment to reviewer \# 2 point 2).\\
-        In terms of the normalization we agree with the reviewer that this part
-        was not explicitly described and we therefore added the following
-        paragraph to the theory section:\\
-        {\color{blue}{The decay width for the total system is in the end
-        normalized to the decay width
-        per initially ionized atom since we are interested in the events
-        after one ionization which could be located at any of the atoms of
-        the corresponding atom
-        type. We thereby yield an averaged decay width for the cluster structure.
-        This step allows the comparison of the total average decay widths
-        between cluster structures of different size and composition.}}
-        \vspace{0.3cm}\\
-        This means, that in the 13 and 55 atoms argon clusters with one
-        additional xenon atom
-        located on one of its surfaces, there are 13 or 55 potentially
-        initially ionized atoms. Inspecting Figure 4, lower panel, it is
-        evident, that the number of pairs for which all decay channels are
-        closed is similar for the 14 and the 56 atom cluster. However,
-        the distribution of pairs with open decay channels is significantly
-        different. The 14 atom cluster has only a few more pairs which are
-        characterized by comparably small distances. Therefore, each of these
-        pairs will have a significant decay width. In case of the 56 atoms
-        cluster there are many pairs with open channels characterized by many
-        different distances and especially much larger distances than in the
-        14 atoms cluster. Therefore, the average decay width is smaller in the
-        56 atoms cluster than in the 14 atoms cluster.
-        The reviewers intuition would be correct if the atom types of argon
-        and xenon atoms were interchanged.
+More explanations are needed.}
 
@@
 
+The reason is that the clusters do not show spin-orbit splitting as opposed to the monomer.
+To make this more clear we have included a sentence in the "outer valence" section: {\color{blue}{ A distinction between the Ar 3p $_{1/2}$ and the Ar 3p $_{3/2}$ derived cluster bands can therefore not be made.}}
+
  \item \emph{Page 13:
@@
 
+	We have clarified the information in the figure caption and additionally refer to the respective table.
+
  \item \emph{It is not clear what the dotted lines in Figure 10 are?}
+
+ We have clarified the information in the figure caption by including the sentence: {\color{blue}{The dotted line shows the unscaled spectrum in this region.}}
 

### 2016-08-05 theo_results.tex

@@
 
+All these results neglect the effect of nuclear dynamics, which might
+affect the spectra. Possible reasons are distance dependend channel closings
+and openings,
+a different distribution of interatomic distances due to vibrations
+and their different impact on
+the ICD and the ETMD(3). E.g., for the ICD in the neon dimer, the treatment of
+nuclear dynamics increases the decay width by approximately a factor 2
+\cite{Schnorr15}.
+However, the atomic displacement can be expected to be by far less severe
+in clusters than in dimers or trimers. Additionally, 
+the elongation of one interatomic distance in a cluster
+automatically results in
+the shortening of a different interatomic distance, which will reduce
+the overall effect. Therefore, there will be a broader spectrum charges in the
+final state $d$ resulting in a broadening of the peak. This was taken into
+account by folding the stick spectrum with Gaussians with a width of
+\unit[300]{meV} and \unit[600]{meV} for the ICD and ETMD(3), respectively.
+While the width of the ICD peaks was estimated from the potential energy
+surface of the ArXe dimer, the situation is more complex in case of the ETMD(3)
+with three degrees of freedom involved. It was therefore guessed to be twice the
+width of the ICD peak.
+
+The channel closing due to shortening of the interatomic distance is not
+relevant for the ETMD(3) process in the ArXe clusters, treated in this work,
+because this would require unnaturally short interatomic distances.
+However, for the ICD it might result in a lower number of pairs with open
+decay channels and hence decrease the decay width. Since the folded peaks
+are constituted from several pairs of different distances, it would result
+in a slight peak shift to higher energies of the combined peak at lowest energy.
+
 \clearpage

### 2016-08-05 exp_results.tex

@@
 Outer valence photoelectron spectra of mixed Ar-Xe clusters, in comparison to the pure species. 
-(a) shows the outer valence region of homogeneous Ar and Xe clusters, respectively (see text for details). 
+(a) shows the outer valence region of homogeneous Ar(1) (red) Ar(2) (black) and Xe clusters, respectively (see text and Table\ \ref{tab:cluster} for details). 
 The two lower panels show spectra of the mixed species with different mean size. 
@@
 Outer valence photoelectron spectra of mixed Ar-Xe clusters from gas mixtures with different Xe concentration. 
-For better visibility, a scaling factor is applied to the Xe part of the spectrum in panel (a).
+For better visibility, a scaling factor is applied to the Xe part of the spectrum in panel (a). The dotted line shows the unscaled spectrum in this region.
 See Figure \ref{figure:oval1} and text for details.
@@
 In pure Ar clusters, outer valence photoionization leads to a broad band, caused both by spin-orbit coupling and crystal field splitting.
+A distinction between the Ar 3p $_{1/2}$ and the Ar 3p $_{3/2}$ derived cluster bands can therefore not be made.
 The relative importance of these two mechanisms remains under debate.\cite{hergenhahnprb,rolles,foerstel_arg1_2010}

### 2016-08-05 onefolder/intro.tex
2.1

@@
 Soon after, related 
-autoionization processes were discovered that proceed via a 
-charge transfer instead of an energy transfer. 
+autoionization processes were discovered 
+in which the initial vacancy is filled by an electron from a neighbouring
+unit.
 These were termed `Electron Transfer Mediated Decay' 
- (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
- which the originally excited site is neutralized by the decay 
-and `exchange ICD' for charge transfer contributions to the 
-normal ICD amplitude.\cite{santrarev,jahnkesat}
+ (ETMD),\cite{zobeley,mueller,sakai,foerstel}
+If the excess is transferred to a third unit, which is subsequently ionized,
+the process is called ETMD(3), if the electron donor is ionized once more
+the process is called ETMD(2) and if the excess energy is used to ionize the
+initially ionized unit the process is called
+`exchange ICD' \cite{santrarev,jahnkesat}.
+ for transitions in 
 We find that both energy and charge transfer induced 

### 2016-08-05 letters/reply_referee.tex
last points

@@
  \item \emph{ETMD(3) should be explained in the introduction by a sentence or two to aid the reader (at the moment, it is first explained in the theory section).
-}
+}\vspace{0.3cm}\\
+       It was indeed explained already but in wording specific to
+       experimentalists. We therefore changed the last paragraph on page 3 to:\\
+       Soon after, related autoionization processes were discovered
+       {\color{blue}{in which the initial vacancy is filled by an electron from a neighbouring unit. These were termed `Electron Transfer Mediated Decay'
+(ETMD)$^{9–12}$.
+If the excess energy is transferred to a third unit which is subsequently ionized, the process is called ETMD(3), if the electron donor is ionized once more the process is called ETMD(2) and if the excess energy is used to ionize the initially ionized unit the process is called `exchange ICD'$^{13,14}.$}}
+
  \item \emph{The authors mention that the ‘nuclear dynamics may play an important role’ but that they have been neglected in the calculations.
@@
 ETMD, etc.
-}
+}\vspace{0.3cm}\\
+       We added two paragraphs at the end of the theoretical results section
+       discussing the possible effects of nuclear dynamics:\\
+       {\color{blue}{All these results neglect the effect of nuclear dynamics, which might affect the spectra.
+Possible reasons are distance dependend channel closings and openings, a different distribu- tion of interatomic distances due to vibrations and their different impact on the ICD and the ETMD(3).
+E.g., for the ICD in the neon dimer, the treatment of nuclear dynamics increases the decay width by approximately a factor 2.$^{57}$ However, the atomic displacement can be expected to be by far less severe in clusters than in dimers or trimers.
+Additionally, the
+elongation of one interatomic distance in a cluster automatically results in the shortening of a different interatomic distance, which will reduce the overall effect.
+Therefore, there will be a broader spectrum charges in the final state d resulting in a broadening of the peak.
+This was taken into account by folding the stick spectrum with Gaussians with a width of 300 meV and 600meV for the ICD and ETMD(3), respectively.
+While the width of the ICD peaks was estimated from the potential energy surface of the ArXe dimer, the situation is more complex in case of the ETMD(3) with three degrees of freedom involved.
+It was therefore guessed to be twice the width of the ICD peak.
+The channel closing due to shortening of the interatomic distance is not relevant for the ETMD(3) process in the ArXe clusters, treated in this work, because this would require unnaturally short interatomic distances.
+However, for the ICD it might result in a lower number of pairs with open decay channels and hence decrease the decay width.
+Since the folded peaks are constituted from several pairs of different distances, it would result in a slight peak shift to higher energies of the combined peak at lowest energy.
+For a more detailed discussion of nculear dynamics for the ICD in dimers vs.
+in clusters see Ref 58.}}
 

### 2016-08-05 intro.tex
last points

@@
 Soon after, related 
-autoionization processes were discovered that are governed by a
-charge transfer instead of an energy transfer. 
+autoionization processes were discovered
+in which the initial vacancy is filled by an electron from a neighbouring unit.
 These were termed `Electron Transfer Mediated Decay' 
- (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
- which the originally excited site is neutralized by the decay 
-and `exchange ICD' for charge transfer contributions to the 
-normal ICD amplitude.\cite{santrarev,jahnkesat}
+ (ETMD),\cite{zobeley,mueller,sakai,foerstel}.
+If the excess energy is transferred to a third unit which is subsequently
+ionized, the process is called ETMD(3), if the electron donor is ionized once
+more the process is called ETMD(2) and if the excess energy is used to
+ionize the initially ionized unit the process is called
+`exchange ICD'. \cite{santrarev,jahnkesat}
 

### 2016-08-05 letters/reply_referee.tex
remove last nonnearest comment
correct smaller errors

@@
 We are thankful for the comments made by the Referees and
-respond to them below. Additionally, we took the opportunity to
-{\color{blue}{correct some typos or whatever.}}
+respond to them below.
 
@@
 
-				We have deleted the explanation of ICD in the 3rd pargraph of page 3.
+				We have deleted the explanation of ICD in the 3rd paragraph of page 3.
 
@@
 We therefore think that this section holds very valuable information for the experimentalist which we do not want to hide in the supplementary section.
-To accommodate the referees suggestion we have included two sentences in the beginning of the section, summarizing the points that are most important for the theory part of the article: \color{blue}{This section describes and discusses the outer valence spectra of the mixed Ar-Xe clusters.
-The main information we obtain from these spectra within the context of our theoretical considerations are the relative Xe contents in the mixed cluster.}
+To accommodate the referees suggestion we have included two sentences in the beginning of the section, summarizing the points that are most important for the theory part of the article: {\color{blue}{This section describes and discusses the outer valence spectra of the mixed Ar-Xe clusters.
+The main information we obtain from these spectra within the context of our theoretical considerations are
+the single ionization potentials and
+the relative Xe contents in the mixed cluster.}}
 
@@
 
- \item \emph{In fig. 9(a) it is specified in the text that  Ar <N> =190 for the black trace but as far as I can tell no value is given for the other spectrum on the same graph.}
+ \item \emph{In fig. 9(a) it is specified in the text that  Ar $<N>$ =190 for the black trace but as far as I can tell no value is given for the other spectrum on the same graph.}
 
@@
 
- \item \emph{The colour schemes of some of the figures lead to confusion when printed in grayscale. Some effort could be made to resolve this.}
+ \item \emph{The colour schemes of some of the figures lead to confusion when printed in grayscale. Some effort could be made to resolve this.}\vspace{0.3cm}\\
+       The reviewer does not specify which figures are affected by this.
+       We therefore assume a reference to figures 4-8. In these, the
+       information density is very high, especially within the stick spectrum.
+       Due to this, overlapping dotted or dashed lines would not be
+       decipherable and only confuse the reader not only on a grayscale print
+       but also a coloured print. Since the majority of scientific journals
+       at least have the pdf version available as well, we therefore leave
+       the colour choice, which was made to allow readability by
+       colour blind people as well.
 
 \end{enumerate}
-
-I took the opportunity to shorten the title in order to not highlight only
-one out of several aspects. It now reads:\\
-      Non-nearest Neighbour ICD in 
-      Clusters
 

### 2016-08-05 exp_results.tex
correct smaller errors

@@
 %
-This section describes and discusses the outer valence spectra of the mixed Ar-Xe clusters.
-The main information we obtain from these spectra within the context of our theoretical considerations are the relative Xe contents in the mixed clusters (see Table\ \ref{tab:valence}).
+This section describes and discusses the outer valence spectra of the mixed
+Ar-Xe clusters. The main information we obtain from these spectra within
+the context of our theoretical considerations are the single ionization
+potentials and the relative Xe
+contents in the mixed clusters (see Table\ \ref{tab:valence}). 
 %

### 2016-08-05 letters/reply_referee.tex
format

@@
 We are thankful for the comments made by the Referees and
-respond to them below.
+respond to them below. We additionally reply on two of the additional
+format requests made by Ms. Maja Vujovic.
 
@@
 
+We also applied almost all requested changes to the format of the manuscript.
+Request number 4 (remove unpublished results from References) asks for
+published and sonn-to-be published material. Since the manuscript in
+questions was submitted a month ago and was an invited contribution
+for special issue to be published in October at the latest.
+We expect this manuscript
+will become published then. We also interpret this timeframe as soon
+and therefore leave the Reference in the list.
+
+For point 6 see Reviewer 2 point 5.
+
         \closing{Sincerely yours,}

### 2016-08-05 theo_results.tex
last points
format

@@
 in the clusters, shown
-in the bottom panel of Figure \ref{figure:surf}. 
+in the lower panel of Figure \ref{figure:surf}. 
 Every different value of the atom pair distance
@@
 in a slight peak shift to higher energies of the combined peak at lowest energy.
+For a more detailed discussion of nculear dynamics for the ICD in dimers vs.
+in clusters see Ref. \citenum{fasshauernjp}
 

### 2016-08-08 letters/reply_referee.tex
ref 1 last point edits...

@@
         This is a good point from the referee.
-We have included a short discussion of the possible explanations of this effect at the respective place: {\color{blue}{In clusters with a low Xe content we can assume that there are Ar atoms that have distances to the next Xe atom that are too large for autoionization to occur.
-This is especially the case if we have very large clusters that show segregation of Ar and Xe atoms.
-If we decrease the cluster size, this effect should play a minor role because large distances are not available here.
-However, with decreasing cluster size, the number of homogeneous clusters in the cluster beam increases.
-In fact, at small cluster sizes, the size distribution has its maximum at the monomer.
-This increasing number of homogeneous Ar clusters still show Ar 3s intensity but do not contribute to recorded coincidences because they cannot autoionize.
+We have included a short discussion of the possible explanations of this effect at the respective place: {\color{blue}{Two main reasons can be identified that cause a decrease in autoionization efficiency.
+First, is the distance between the initially ionized Ar atom to the decay partner too large, then the excited Ar ion can decay via fluorescence before it can autoionize.
+And second, if there is no decay partner available at a sufficiently large distance, then a decay is energetically not possible.
+In both cases, a small Xe content would lead to a decrease in autoionization efficiency.
+The first case should not occur in small clusters while the second should strongly increase with decreasing cluster size.
 }}

### 2016-08-08 letters/reply_referee.tex
corrections elkes part

@@
 For example, in molecular clusters ICD can be clearly identified after deep ionization (typically for binding energy above 20 eV) of one molecule.
-However, owing to the strong electronic correlation in this binding energy range the states cannot be described as ionization from a single orbital.}\\
+However, owing to the strong electronic correlation in this binding energy range the states cannot be described as ionization from a single orbital.}\\\vspace{0.3cm}\\
 				The referee is correct, the statement does not bring new information.
@@
 That is also in accordance to the referees notion that the manuscript is too long.
+
 	\item \emph{Page 9: the sentence “These atoms do not necessarily need to form bonds...” just rephrases what is already explained earlier in the manuscript on ICD.}\vspace{0.3cm}\\
@@
 Furthermore, it seems to me that the paragraph on previous study of the authors on large clusters does provide relevant informations on the reported results.}\vspace{0.3cm}\\
-         We object to move the pictures showing
-         some classes of systems under investigation,
-         which is far less the all systems, to the
-         supplementary information. Additionally, the paragraph the reviewer
-         refers to are two paragraphs. Since the section only consists of
-         four paragraphs in total, the first one explains the general
-         procedure of the manuscript and the fourth explains the pictures of
-         the classes, there is nothing left to reasonably be moved to the
-         Supplementary Information. We therefore don't change the manuscript
-         in this point.
+
+     The whole section consists of only four paragraphs in total and is rather short.
+The cluster structures are crucial for understanding the underlying theory and results.
+It is a very descriptive part of the manuscript and helps the reader to assess the different structures and classes under discussion.
+We therefore think that it will not improve the MS if the whole section is moved to the supplementary information.
+(note that a large part of this section is already there).
 
@@
 All extra details can be avoided.
-Just to help the readers, this section could be renamed to highlight the goal of the section like for example “Xe content”.}
-
+Just to help the readers, this section could be renamed to highlight the goal of the section like for example “Xe content”.}\vspace{0.3cm}\\
 				The referee is correct if one reads the article from a theoreticians point of view.
@@
        {\color{blue}{All these results neglect the effect of nuclear dynamics, which might affect the spectra.
-Possible reasons are distance dependend channel closings and openings, a different distribu- tion of interatomic distances due to vibrations and their different impact on the ICD and the ETMD(3).
-E.g., for the ICD in the neon dimer, the treatment of nuclear dynamics increases the decay width by approximately a factor 2.$^{57}$ However, the atomic displacement can be expected to be by far less severe in clusters than in dimers or trimers.
+Possible reasons are distance dependent channel closings and openings, a different distribution of interatomic distances due to vibrations and their different impact on the ICD and the ETMD(3).
+E.g., for the ICD in the neon dimer, the treatment of nuclear dynamics increases the decay width by approximately a factor 2.$^{57}$ However, the atomic displacement can be expected to be far less severe in clusters than in dimers or trimers.
 Additionally, the
@@
 Therefore, there will be a broader spectrum charges in the final state d resulting in a broadening of the peak.
-This was taken into account by folding the stick spectrum with Gaussians with a width of 300 meV and 600meV for the ICD and ETMD(3), respectively.
+This was taken into account by folding the stick spectrum with Gaussians with a width of 300 meV and 600 meV for the ICD and ETMD(3), respectively.
 While the width of the ICD peaks was estimated from the potential energy surface of the ArXe dimer, the situation is more complex in case of the ETMD(3) with three degrees of freedom involved.
@@
 Since the folded peaks are constituted from several pairs of different distances, it would result in a slight peak shift to higher energies of the combined peak at lowest energy.
-For a more detailed discussion of nculear dynamics for the ICD in dimers vs.
+For a more detailed discussion of nuclear dynamics for the ICD in dimers vs.
 in clusters see Ref 58.}}

### 2016-08-12 exp_results.tex

@@
 
-We found an Ar 3s autoionization efficiency which, for clusters with the lowest Xe content (Xe$_{\rm cl}$ approx. 10-12\,\%), is smaller than unity, and further decreases with decreasing cluster size.
-
-In clusters with a low Xe content we can assume that there are Ar atoms that have distances to the next Xe atom that are too large for autoionization to occur.
-This is especially the case if we have very large clusters that show segregation of Ar and Xe atoms.
-If we decrease the cluster size, this effect should play a minor role because large distances are not available here.
-However, with decreasing cluster size, the number of homogeneous clusters in the cluster beam increases.
-In fact, at small cluster sizes, the size distribution has its maximum at the monomer.
-This increasing number of homogeneous Ar clusters still show Ar 3s intensity but do not contribute to recorded coincidences because they cannot autoionize.
+We found an Ar 3s autoionization efficiency which, for clusters with the lowest Xe content (Xe$_{\rm cl}$ approx.
+10-12\,\%), is smaller than unity, and further decreases with decreasing cluster size.
+Two main reasons can be identified that cause this decrease in autoionization efficiency.
+First, is the distance between the initially ionized Ar atom to the decay partner too large, then the excited Ar ion can decay via fluorescence before it can autoionize.
+And second, if there is no decay partner available at a sufficiently large distance, then a decay is energetically not possible.
+In both cases, a small Xe content would lead to a decrease in autoionization efficiency.
+The first case should not occur in small clusters while the second should strongly increase with decreasing cluster size.
 For larger Xe$_{\rm cl}$, the values are compatible with unity, within the accuracy of our experiment.

### 2016-08-12 theo_results.tex

@@
 All these results neglect the effect of nuclear dynamics, which might
-affect the spectra. Possible reasons are distance dependend channel closings
+affect the spectra. Possible reasons are distance dependent channel closings
 and openings,
@@
 \cite{Schnorr15}.
-However, the atomic displacement can be expected to be by far less severe
+However, the atomic displacement can be expected to be far less severe
 in clusters than in dimers or trimers. Additionally, 
@@
 in a slight peak shift to higher energies of the combined peak at lowest energy.
-For a more detailed discussion of nculear dynamics for the ICD in dimers vs.
+For a more detailed discussion of nuclear dynamics for the ICD in dimers vs.
 in clusters see Ref. \citenum{fasshauernjp}

### 2016-08-12 letters/reply_referee.tex
correct one sentence

@@
 Furthermore, it seems to me that the paragraph on previous study of the authors on large clusters does provide relevant informations on the reported results.}\vspace{0.3cm}\\
-
      The whole section consists of only four paragraphs in total and is rather short.
@@
 elongation of one interatomic distance in a cluster automatically results in the shortening of a different interatomic distance, which will reduce the overall effect.
-Therefore, there will be a broader spectrum charges in the final state d resulting in a broadening of the peak.
-This was taken into account by folding the stick spectrum with Gaussians with a width of 300 meV and 600 meV for the ICD and ETMD(3), respectively.
+Therefore, there will be a broader spectrum of final state charge
+distances $d$ resulting in a broadening of the peak. This was taken into
+account by folding the stick spectrum with Gaussians with a width of 300 meV and 600 meV for the ICD and ETMD(3), respectively.
 While the width of the ICD peaks was estimated from the potential energy surface of the ArXe dimer, the situation is more complex in case of the ETMD(3) with three degrees of freedom involved.
 It was therefore guessed to be twice the width of the ICD peak.
+
 The channel closing due to shortening of the interatomic distance is not relevant for the ETMD(3) process in the ArXe clusters, treated in this work, because this would require unnaturally short interatomic distances.

### 2016-08-14 exp_results.tex
kleine sprachliche Änderungen

@@
 
-We found an Ar 3s autoionization efficiency which, for clusters with the lowest Xe content (Xe$_{\rm cl}$ approx.
-10-12\,\%), is smaller than unity, and further decreases with decreasing cluster size.
-Two main reasons can be identified that cause this decrease in autoionization efficiency.
-First, is the distance between the initially ionized Ar atom to the decay partner too large, then the excited Ar ion can decay via fluorescence before it can autoionize.
-And second, if there is no decay partner available at a sufficiently large distance, then a decay is energetically not possible.
-In both cases, a small Xe content would lead to a decrease in autoionization efficiency.
-The first case should not occur in small clusters while the second should strongly increase with decreasing cluster size.
-For larger Xe$_{\rm cl}$, the values are compatible with unity, within the accuracy of our experiment.
+We found an Ar 3s autoionization efficiency which is compatible with unity, within the accuracy of our experiment, for all clusters except those with the lowest Xe content (Xe$_{\rm cl}$ approx.
+10-12\,\%).
+For the latter, also a decrease of the efficiency with decreasing cluster size is seen. 
+Two main reasons can be identified that may cause a decrease in autoionization efficiency. 
+Firstly, in small clusters with a low Xe content, for some Ar atoms no Xe partners allowing either ICD or ETMD might be available.
+A simple example are clusters containing just a single Xe atom.
+This mechanism would gain in importance for cluster ensembles with small $\langle N\rangle$.
+Secondly, if only Xe partners at very large distances are available, ICD might be outpaced by other decay processes, most importantly fluorescence.

### 2016-08-14 experimental.tex
kleine sprachliche Änderungen

@@
 We basically have an Ar seeded expansion of Xe gas, as the freezing point of Ar is much lower. 
-$\langle N_{\rm Ar} \rangle$ and $\langle N_{\rm Xe} \rangle$ refer to cluster sizes for a pure Ar, or pure Xe expansion, resp., at the given conditions, calculated from a scaling law.\protect\cite{hagena1981}
+$\langle N_{\rm Ar} \rangle$ and $\langle N_{\rm Xe} \rangle$ refer to cluster sizes for a pure Ar, or pure Xe expansion, respectively, at the given conditions, calculated from a scaling law.\protect\cite{Hagena1992}
 We expect actual cluster sizes in-between these two limiting values. 
@@
 % Leave this citation in place to avoid Latex error
-A comprehensive description can be found in Ref. \citenum{arion}, and here we focus on details specific for the current experiment. Commercial Ar and Xe gas was used. 
-Separate containers for the two gases were filled up to pressures suitable for producing a certain mixing ratio. The gases were then allowed to mix before the expansion. 
+A comprehensive description can be found in ref \citenum{arion}, and here we focus on details specific for the current experiment. 
+Commercialy obtained Ar and Xe gas was filled into 
+separate cylinders up to pressures suitable for producing a certain mixing ratio. The gases were then allowed to mix before the expansion. 
 Expansion parameters are given in Table \ref{tab:cluster}. 
-Similar expansion conditions are further referred by labels `S'-`XL', as given shown in the Table.grep
+Similar expansion conditions are further referred by the labels `S'-`XL', as given in the Table.
 
-Prediction of the sizes of clusters from a supersonic expansion mainly rests on empirical scaling laws,\cite{hagena1981} which have been the subject of some discussion.
+Prediction of the sizes of clusters from a supersonic expansion mainly rests on empirical scaling laws,\cite{Hagena1992} which have been the subject of some discussion.
 Moreover, such scaling laws originally were derived only for pure gas expansions.

### 2016-08-15 letters/reply_referee.tex

@@
         This is a good point from the referee.
-We have included a short discussion of the possible explanations of this effect at the respective place: {\color{blue}{Two main reasons can be identified that cause a decrease in autoionization efficiency.
-First, is the distance between the initially ionized Ar atom to the decay partner too large, then the excited Ar ion can decay via fluorescence before it can autoionize.
-And second, if there is no decay partner available at a sufficiently large distance, then a decay is energetically not possible.
-In both cases, a small Xe content would lead to a decrease in autoionization efficiency.
-The first case should not occur in small clusters while the second should strongly increase with decreasing cluster size.
+We have included a short discussion of the possible explanations of this effect at the respective place: {\color{blue}{We found an Ar 3s autoionization efficiency which is compatible with unity, within the accuracy of our experiment, for all clusters except those with the lowest Xe content (Xe$_{\rm cl}$ approx.
+10-12\,\%).
+For the latter, also a decrease of the efficiency with decreasing cluster size is seen. 
+Two main reasons can be identified that may cause a decrease in autoionization efficiency. 
+Firstly, in small clusters with a low Xe content, for some Ar atoms no Xe partners allowing either ICD or ETMD might be available.
+A simple example are clusters containing just a single Xe atom.
+This mechanism would gain in importance for cluster ensembles with small $\langle N\rangle$.
+Secondly, if only Xe partners at very large distances are available, ICD might be outpaced by other decay processes, most importantly fluorescence.
 }}
@@
 
-The channel closing due to shortening of the interatomic distance is not relevant for the ETMD(3) process in the ArXe clusters, treated in this work, because this would require unnaturally short interatomic distances.
-However, for the ICD it might result in a lower number of pairs with open decay channels and hence decrease the decay width.
-Since the folded peaks are constituted from several pairs of different distances, it would result in a slight peak shift to higher energies of the combined peak at lowest energy.
+The channel closing due to shortening of the interatomic distance is not
+relevant for the ETMD(3) process in the ArXe clusters treated in this work,
+because this would require unnaturally short interatomic distances.
+However, for the ICD it might result in a lower number of pairs with open
+decay channels and hence a decrease of the decay width. 
+Since the peaks in the convoluted spectrum 
+contain contributions from several atom pairs at different distances, 
+this would result
+in a small peak shift to higher energies of the combined peak at lowest energy.
 For a more detailed discussion of nuclear dynamics for the ICD in dimers vs.
-in clusters see Ref 58.}}
+clusters see Ref. 58.
+}}
 
@@
        and the necessary effort to produce reliable results with density
-       functional theory (DFT) for v. d. Waals interactions since we in
-       this work discuss structural trends and not absolute structures.}}
+       functional theory (DFT) for v. d. Waals interactions since in
+       this work we discuss structural trends and not absolute structures.}}
 

### 2016-08-15 theo_results.tex
correct one sentence

@@
 the shortening of a different interatomic distance, which will reduce
-the overall effect. Therefore, there will be a broader spectrum charges in the
-final state $d$ resulting in a broadening of the peak. This was taken into
+the overall effect. Therefore, there will be a broader spectrum  of final
+state charge distances
+$d$ resulting in a broadening of the peak. This was taken into
 account by folding the stick spectrum with Gaussians with a width of
@@
 The channel closing due to shortening of the interatomic distance is not
-relevant for the ETMD(3) process in the ArXe clusters, treated in this work,
+relevant for the ETMD(3) process in the ArXe clusters treated in this work,
 because this would require unnaturally short interatomic distances.
 However, for the ICD it might result in a lower number of pairs with open
-decay channels and hence decrease the decay width. Since the folded peaks
-are constituted from several pairs of different distances, it would result
-in a slight peak shift to higher energies of the combined peak at lowest energy.
+decay channels and hence a decrease of the decay width. 
+Since the peaks in the convoluted spectrum 
+contain contributions from several atom pairs at different distances, 
+this would result
+in a small peak shift to higher energies of the combined peak at lowest energy.
 For a more detailed discussion of nuclear dynamics for the ICD in dimers vs.
-in clusters see Ref. \citenum{fasshauernjp}
+clusters see Ref. \citenum{fasshauernjp}
 

### 2016-08-15 resubmit/master.tex
resubmitted version

--- 2016-07-04 onefolder/master.tex
@@
 
-\pgfplotsset{compat=1.10}
+\pgfplotsset{compat=1.8}
 
@@
 \email{uwe.hergenhahn@iom-leipzig.de}
+\phone{+49 (0)341 235 3286}
 \author{Elke Fasshauer}
-\affiliation[UIT]{Centre for Theoretical and Computational Chemistry,
+\affiliation[UiT]{Centre for Theoretical and Computational Chemistry,
 Department of Chemistry, University of Troms\o
@@
 \email{elke.fasshauer@uit.no}
-%\phone{+123 (0)123 4445556}
+\phone{+47 776 23103}
 %\fax{+123 (0)123 4445557}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Long-range Interatomic Coulombic Decay in ArXe clusters: Experiment and Theory}
+\title{Long-Range Interatomic Coulombic Decay in ArXe Clusters: Experiment and Theory}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{abstract}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{intro}
 \section{Introduction}
@@
 systems. Experimental and theoretical progress has been reviewed.
-\cite{hergenhahn_review, averbukh_review, jahnke_review} ICD 
-proceeds by an initial ionization producing an ion in an excited 
-state, followed by a transfer of energy to a neighbouring site, 
-and an electron emission process therefrom. The final state contains 
-two positive charges; one at the original site of ionization, and a second
-one at another atom or molecule.
+\cite{hergenhahn_review, averbukh_review, jahnke_review}
 
 Soon after, related 
-autoionization processes were discovered that proceed via a 
-charge transfer instead of an energy transfer. 
+autoionization processes were discovered
+in which the initial vacancy is filled by an electron from a neighbouring unit.
 These were termed `Electron Transfer Mediated Decay' 
- (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
- which the originally excited site is neutralized by the decay 
-and `exchange ICD' for charge transfer contributions to the 
-normal ICD amplitude.\cite{santrarev,jahnkesat}
+ (ETMD),\cite{zobeley,mueller,sakai,foerstel}.
+If the excess energy is transferred to a third unit which is subsequently
+ionized, the process is called ETMD(3), if the electron donor is ionized once
+more the process is called ETMD(2) and if the excess energy is used to
+ionize the initially ionized unit the process is called
+`exchange ICD'. \cite{santrarev,jahnkesat}
+
 We find that both energy and charge transfer induced 
 autoionization play a role in Ar-Xe, and will detail the 
-relevant processes below. The notion of ICD requires that the 
-electronic orbitals of the two sites can be distinguished, which 
-typically is the case in weakly bonded systems, held together by 
-hydrogen bonds or van-der-Waals bonds. In the case of strong
-(covalent or metallic) bonding, it is impossible to make a
-distinction between ICD and Auger decay.\cite{hergenhahn_review}
+relevant processes below.
 
@@
 
-%\input{experimental}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 We basically have an Ar seeded expansion of Xe gas, as the freezing point of Ar is much lower. 
-$\langle N_{\rm Ar} \rangle$ and $\langle N_{\rm Xe} \rangle$ refer to cluster sizes for a pure Ar, or pure Xe expansion, respectively, at the given conditions, calculated from a scaling law.\protect\cite{hagena1981}
+$\langle N_{\rm Ar} \rangle$ and $\langle N_{\rm Xe} \rangle$ refer to cluster sizes for a pure Ar, or pure Xe expansion, respectively, at the given conditions, calculated from a scaling law.\protect\cite{Hagena1992}
 We expect actual cluster sizes in-between these two limiting values. 
@@
 
-Prediction of the sizes of clusters from a supersonic expansion mainly rests on empirical scaling laws,\cite{hagena1981} which have been the subject of some discussion.
+Prediction of the sizes of clusters from a supersonic expansion mainly rests on empirical scaling laws,\cite{Hagena1992} which have been the subject of some discussion.
 Moreover, such scaling laws originally were derived only for pure gas expansions.
@@
 
-%\input{theory}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Theoretical Approach}
@@
 experimental ionization energies of Table \ref{tab:valence}
-and data from the literature given in Tables II and III.
-This choice is identical to the one made in ref \citenum{Fasshauer13}.
-
-%\input{structures}
+and data from the literature given in Tables II and III of
+Ref.\ \citenum{Fasshauer13}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Cluster Structures}
@@
 Avogadro programme (version 1.1.0) \cite{Avogadro,Hanwell12} to give local
-minimum structures.
+minimum structures. The method was chosen due to its low computational cost,
+the possibility to find the next local minimum structure based on the chosen
+starting point and the necessary effort to produce reliable results
+with density functional theory (DFT) for
+v. d. Waals interactions since in this work we discuss structural trends and
+not absolute structures.
 All cluster structures are listed in Table \ref{table:theo_gammas}.
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{cluster_2_overview.pdf}
- \caption{Cluster structures composed of 13 argon atoms and two additional xenon
-          atoms on different surfaces of the argon icosahedron, varying in Xe-Xe distance:
-          (a) closest possible, (b) middle, (c) furthest away. They refer to
-          numbers 9--11 in Table \ref{table:theo_gammas}.}
- \label{figure:cluster_2_overview}
-\end{figure}
 %
@@
  \label{figure:cluster_3_overview}
+\end{figure}
+%
+\begin{figure}[ht]
+ \centering
+ \includegraphics[width=8.5cm]{cluster_2_overview.pdf}
+ \caption{Cluster structures composed of 13 argon atoms and two additional xenon
+          atoms on different surfaces of the argon icosahedron, varying in Xe-Xe distance:
+          (a) closest possible, (b) middle, (c) furthest away. They refer to
+          numbers 9--11 in Table \ref{table:theo_gammas}.}
+ \label{figure:cluster_2_overview}
 \end{figure}
@@
 Furthermore, for comparison with the largest measured ArXe clusters, we constructed also larger core-shell structures (Table \ref{table:theo_gammas}, \#4--5).
-
-%\input{theo_results}
+These were idealized icosahedral and cuboctahedral structures based on the
+v. d. Waals radii of argon and xenon $r_{Ar}=$\unit[1.88]{\AA} \cite{Herman88}
+and $r_{Xe}=$\unit[2.16]{\AA} \cite{Freeman74}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Theoretical Results
@@
 
+All these results neglect the effect of nuclear dynamics, which might
+affect the spectra. Possible reasons are distance dependent channel closings
+and openings,
+a different distribution of interatomic distances due to vibrations
+and their different impact on
+the ICD and the ETMD(3). E.g., for the ICD in the neon dimer, the treatment of
+nuclear dynamics increases the decay width by approximately a factor 2
+\cite{Schnorr15}.
+However, the atomic displacement can be expected to be far less severe
+in clusters than in dimers or trimers. Additionally, 
+the elongation of one interatomic distance in a cluster
+automatically results in
+the shortening of a different interatomic distance, which will reduce
+the overall effect. Therefore, there will be a broader spectrum  of final
+state charge distances
+$d$ resulting in a broadening of the peak. This was taken into
+account by folding the stick spectrum with Gaussians with a width of
+\unit[300]{meV} and \unit[600]{meV} for the ICD and ETMD(3), respectively.
+While the width of the ICD peaks was estimated from the potential energy
+surface of the ArXe dimer, the situation is more complex in case of the ETMD(3)
+with three degrees of freedom involved. It was therefore guessed to be twice the
+width of the ICD peak.
+
+The channel closing due to shortening of the interatomic distance is not
+relevant for the ETMD(3) process in the ArXe clusters treated in this work,
+because this would require unnaturally short interatomic distances.
+However, for the ICD it might result in a lower number of pairs with open
+decay channels and hence a decrease of the decay width. 
+Since the peaks in the convoluted spectrum 
+contain contributions from several atom pairs at different distances, 
+this would result
+in a small peak shift to higher energies of the combined peak at lowest energy.
+For a more detailed discussion of nuclear dynamics for the ICD in dimers vs.
+clusters see Ref. \citenum{fasshauernjp}.
+
 \clearpage
-
-%\input{exp_results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Experimental Results}
@@
 %
+This section describes and discusses the outer valence spectra of the mixed
+Ar-Xe clusters. The main information we obtain from these spectra within
+the context of our theoretical considerations are the single ionization
+potentials and the relative Xe
+contents in the mixed clusters (see Table\ \ref{tab:valence}). 
+%
 \begin{figure}[ht]
@@
 
-We found an Ar 3s autoionization efficiency which, for clusters with the lowest Xe content (Xe$_{\rm cl}$ approx.
-10-12\,\%), is smaller than unity, and further decreases with decreasing cluster size.
-For larger Xe$_{\rm cl}$, the values are compatible with unity, within the accuracy of our experiment.
-
-%\input{theo_discussion}
+We found an Ar 3s autoionization efficiency which is compatible with unity, within the accuracy of our experiment, for all clusters except those with the lowest Xe content (Xe$_{\rm cl}$ approx.
+10-12\,\%).
+For the latter, also a decrease of the efficiency with decreasing cluster size is seen. 
+Two main reasons can be identified that may cause a decrease in autoionization efficiency. 
+Firstly, in small clusters with a low Xe content, for some Ar atoms no Xe partners allowing either ICD or ETMD might be available.
+A simple example are clusters containing just a single Xe atom.
+This mechanism would gain in importance for cluster ensembles with small $\langle N\rangle$.
+Secondly, if only Xe partners at very large distances are available, ICD might be outpaced by other decay processes, most importantly fluorescence.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Discussion
@@
 
-%\input{summary}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Summary}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% The same is true for Supporting Information, which should use the
+%% suppinfo environment.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{suppinfo}
+
+Detailed experimental approach and results and Theoretical Spectra
+for structures 20 -- 26.
+
+\end{suppinfo}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %% The "Acknowledgement" section can be given in all manuscript
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{acknowledgements}
 \begin{acknowledgement}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The same is true for Supporting Information, which should use the
-%% suppinfo environment.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{suppinfo}
-
-%This will usually read something like: ``Experimental procedures and
-%characterization data for all new compounds. The class will
-%automatically add a sentence pointing to the information on-line:
-
-%\end{suppinfo}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %% The appropriate \bibliography command should be placed here.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliography{arxe}
+%\bibliography{arxe}
+
+\providecommand{\latin}[1]{#1}
+\providecommand*\mcitethebibliography{\thebibliography}
+\csname @ifundefined\endcsname{endmcitethebibliography}
+  {\let\endmcitethebibliography\endthebibliography}{}
+\begin{mcitethebibliography}{73}
+\providecommand*\natexlab[1]{#1}
+\providecommand*\mciteSetBstSublistMode[1]{}
+\providecommand*\mciteSetBstMaxWidthForm[2]{}
+\providecommand*\mciteBstWouldAddEndPuncttrue
+  {\def\EndOfBibitem{\unskip.}}
+\providecommand*\mciteBstWouldAddEndPunctfalse
+  {\let\EndOfBibitem\relax}
+\providecommand*\mciteSetBstMidEndSepPunct[3]{}
+\providecommand*\mciteSetBstSublistLabelBeginEnd[3]{}
+\providecommand*\EndOfBibitem{}
+\mciteSetBstSublistMode{f}
+\mciteSetBstMaxWidthForm{subitem}{(\alph{mcitesubitemcount})}
+\mciteSetBstSublistLabelBeginEnd
+  {\mcitemaxwidthsubitemform\space}
+  {\relax}
+  {\relax}
+
+\bibitem[jpc(2015)]{jpcc}
+Special issue: Current Trends in Clusters and Nanoparticles. \emph{J. Phys.
+  Chem. C} \textbf{2015}, \emph{119}, (issue 20)\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Cederbaum \latin{et~al.}(1997)Cederbaum, Zobeley, and
+  Tarantelli]{cederbaum}
+Cederbaum,~L.~S.; Zobeley,~J.; Tarantelli,~F. Giant Intermolecular Decay and
+  Fragmentation of Clusters. \emph{Phys. Rev. Lett.} \textbf{1997}, \emph{79},
+  4778--4781\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Slav\'{i}\v{c}ek \latin{et~al.}(2014)Slav\'{i}\v{c}ek, Winter,
+  Cederbaum, and Kryzhevoi]{slavicek}
+Slav\'{i}\v{c}ek,~P.; Winter,~B.; Cederbaum,~L.~S.; Kryzhevoi,~N.~V.
+  Proton-Transfer Mediated Enhancement of Nonlocal Electronic Relaxation
+  Processes in X-ray Irradiated Liquid Water. \emph{JACS} \textbf{2014},
+  \emph{136}, 18170--18176\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Marburger \latin{et~al.}(2003)Marburger, Kugeler, Hergenhahn, and
+  M\"oller]{marburger}
+Marburger,~S.; Kugeler,~O.; Hergenhahn,~U.; M\"oller,~T. Experimental evidence
+  for Interatomic Coulombic Decay in Ne clusters. \emph{Phys. Rev. Lett.}
+  \textbf{2003}, \emph{90}, 203401\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Jahnke \latin{et~al.}(2004)Jahnke, Czasch, Sch\"offler, Sch\"ossler,
+  Knapp, K\"asz, Titze, Wimmer, Kreidi, Grisenti, Staudte, Jagutzki,
+  Hergenhahn, Schmidt-B\"ocking, and D\"orner]{jahnkenedimer}
+Jahnke,~T.; Czasch,~A.; Sch\"offler,~M.~S.; Sch\"ossler,~S.; Knapp,~A.;
+  K\"asz,~M.; Titze,~J.; Wimmer,~C.; Kreidi,~K.; Grisenti,~R.~E. \latin{et~al.}
+   Experimental Observation of Interatomic Coulombic Decay in Neon Dimers.
+  \emph{Phys. Rev. Lett.} \textbf{2004}, \emph{93}, 163401\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Hergenhahn(2011)]{hergenhahn_review}
+Hergenhahn,~U. Interatomic and intermolecular coulombic decay: The early years.
+  \emph{J. Electron Spectrosc. Relat. Phenom.} \textbf{2011}, \emph{184},
+  78\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Averbukh \latin{et~al.}(2011)Averbukh, Demekhin, Kolorenc, Scheit,
+  Stoychev, Kuleff, Chiang, Gokhberg, Kopelke, Sisourat, and
+  Cederbaum]{averbukh_review}
+Averbukh,~V.; Demekhin,~P.; Kolorenc,~P.; Scheit,~S.; Stoychev,~S.~D.;
+  Kuleff,~A.~I.; Chiang,~Y.-C.; Gokhberg,~K.; Kopelke,~S.; Sisourat,~N.
+  \latin{et~al.}  Interatomic electronic decay processes in singly and multiply
+  ionized clusters. \emph{J. Electron Spectrosc. Relat. Phenom.} \textbf{2011},
+  \emph{183}, 36\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Jahnke(2015)]{jahnke_review}
+Jahnke,~T. Interatomic and intermolecular Coulombic decay: the coming of age
+  story. \emph{J. Phys. B} \textbf{2015}, \emph{48}, 082001\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Zobeley \latin{et~al.}(2001)Zobeley, Santra, and Cederbaum]{zobeley}
+Zobeley,~J.; Santra,~R.; Cederbaum,~L.~S. Electronic decay in weakly bound
+  heteroclusters: Energy transfer versus electron transfer. \emph{J. Chem.
+  Phys.} \textbf{2001}, \emph{115}, 5076--5088\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[M\"uller and Cederbaum(2005)M\"uller, and Cederbaum]{mueller}
+M\"uller,~I.~B.; Cederbaum,~L.~S. Electronic decay following ionization of
+  aqueous Li$^+$ microsolvation clusters. \emph{J. Chem. Phys.} \textbf{2005},
+  \emph{122}, 094305\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Sakai \latin{et~al.}(2011)Sakai, Stoychev, Ouchi, Higuchi,
+  Sch\"offler, Mazza, Fukuzawa, Nagaya, Yao, Tamenori, Kuleff, Saito, and
+  Ueda]{sakai}
+Sakai,~K.; Stoychev,~S.; Ouchi,~T.; Higuchi,~I.; Sch\"offler,~M.; Mazza,~T.;
+  Fukuzawa,~H.; Nagaya,~K.; Yao,~M.; Tamenori,~Y. \latin{et~al.}
+  Electron-Transfer-Mediated Decay and Interatomic Coulombic Decay from the
+  Triply Ionized States in Argon Dimers. \emph{Phys. Rev. Lett.} \textbf{2011},
+  \emph{106}, 33401\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[F\"orstel \latin{et~al.}(2011)F\"orstel, Mucke, Arion, Bradshaw, and
+  Hergenhahn]{foerstel}
+F\"orstel,~M.; Mucke,~M.; Arion,~T.; Bradshaw,~A.~M.; Hergenhahn,~U.
+  Autoionization Mediated by Electron Transfer. \emph{Phys. Rev. Lett.}
+  \textbf{2011}, \emph{106}, 033402\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Santra and Cederbaum(2002)Santra, and Cederbaum]{santrarev}
+Santra,~R.; Cederbaum,~L.~S. Non-Hermitian electronic theory and applications
+  to clusters. \emph{Phys. Rep.} \textbf{2002}, \emph{368}, 1--117\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Jahnke \latin{et~al.}(2007)Jahnke, Czasch, Sch\"offler, Sch\"ossler,
+  K\"asz, Titze, Kreidi, Grisenti, Staudte, Jagutzki, Schmidt, Weber,
+  Schmidt-B\"ocking, Ueda, and D\"orner]{jahnkesat}
+Jahnke,~T.; Czasch,~A.; Sch\"offler,~M.; Sch\"ossler,~S.; K\"asz,~M.;
+  Titze,~J.; Kreidi,~K.; Grisenti,~R.~E.; Staudte,~A.; Jagutzki,~O.
+  \latin{et~al.}  Experimental Separation of Virtual Photon Exchange and
+  Electron Transfer in Interatomic Coulombic Decay of Neon Dimers. \emph{Phys.
+  Rev. Lett.} \textbf{2007}, \emph{99}, 153401\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Barth \latin{et~al.}(2006)Barth, Marburger, Joshi, Ulrich, Kugeler,
+  and Hergenhahn]{barthnear}
+Barth,~S.; Marburger,~S.~P.; Joshi,~S.; Ulrich,~V.; Kugeler,~O.; Hergenhahn,~U.
+  Interface Identification by Non-Local Autoionization Transitions. \emph{Phys.
+  Chem. Chem. Phys.} \textbf{2006}, \emph{8}, 3218--3222\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Aziz \latin{et~al.}(2008)Aziz, Ottosson, Faubel, Hertel, and
+  Winter]{aziz}
+Aziz,~E.~F.; Ottosson,~N.; Faubel,~M.; Hertel,~I.~V.; Winter,~B. Interaction
+  Between Liquid Water and Hydroxide Revealed by Core-Hole Deexcitation.
+  \emph{Nature} \textbf{2008}, \emph{455}, 89--91\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Pokapanich \latin{et~al.}(2009)Pokapanich, Bergersen, Bradeanu,
+  Marinho, Lindblad, Legendre, Rosso, Svensson, Bj\"orneholm, Tchaplyguine,
+  \"Ohrwall, Kryzhevoi, and Cederbaum]{pokapanich}
+Pokapanich,~W.; Bergersen,~H.; Bradeanu,~I.~L.; Marinho,~R. R.~T.;
+  Lindblad,~A.; Legendre,~S.; Rosso,~A.; Svensson,~S.; Bj\"orneholm,~O.;
+  Tchaplyguine,~M. \latin{et~al.}  Auger Electron Spectroscopy as a Probe of
+  the Solution of Aqueous Ions. \emph{J. Am. Chem. Soc.} \textbf{2009},
+  \emph{131}, 7264--7271\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Pokapanich \latin{et~al.}(2012)Pokapanich, Ottosson, Svensson,
+  \"Ohrwall, Winter, and Bj\"orneholm]{pokapanich2011}
+Pokapanich,~W.; Ottosson,~N.; Svensson,~S.; \"Ohrwall,~G.; Winter,~B.;
+  Bj\"orneholm,~O. Bond Breaking, Electron Pushing, and Proton Pulling: Active
+  and Passive Roles in the Interaction between Aqueous Ions and Water as
+  Manifested in the O 1s Auger Decay. \emph{J. Phys. Chem. B} \textbf{2012},
+  \emph{116}, 3--8\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Grieves and Orlando(2011)Grieves, and Orlando]{grieves}
+Grieves,~G.~A.; Orlando,~T.~M. Intermolecular Coulomb Decay at Weakly Coupled
+  Heterogeneous Interfaces. \emph{Phys. Rev. Lett.} \textbf{2011}, \emph{107},
+  016104\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Fasshauer \latin{et~al.}(2014)Fasshauer, F\"orstel, Pallmann,
+  Pernpointner, and Hergenhahn]{fasshauer2014}
+Fasshauer,~E.; F\"orstel,~M.; Pallmann,~S.; Pernpointner,~M.; Hergenhahn,~U.
+  Using ICD for Structural Analysis of Clusters: A Case Study on NeAr Clusters.
+  \emph{New J. Phys.} \textbf{2014}, \emph{16}, 103026\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Lundwall \latin{et~al.}(2007)Lundwall, Pokapanich, Bergersen,
+  Lindblad, Rander, \"Ohrwall, Tchaplyguine, Barth, Hergenhahn, Svensson, and
+  Bj\"orneholm]{lundwall}
+Lundwall,~M.; Pokapanich,~W.; Bergersen,~H.; Lindblad,~A.; Rander,~T.;
+  \"Ohrwall,~G.; Tchaplyguine,~M.; Barth,~S.; Hergenhahn,~U.; Svensson,~S.
+  \latin{et~al.}  Self-Assembled Heterogeneous Argon/Neon Core-Shell Clusters
+  Studied by Photoelectron Spectroscopy. \emph{J. Chem. Phys.} \textbf{2007},
+  \emph{126}, 214706 -- 214708\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Lengen \latin{et~al.}(1992)Lengen, Joppien, M\"uller, W\"ormer, and
+  M\"oller]{lengenprl}
+Lengen,~M.; Joppien,~M.; M\"uller,~R.; W\"ormer,~J.; M\"oller,~T. Site-specific
+  excitation and decay processes in XeAr$_{N}$ clusters. \emph{Phys. Rev.
+  Lett.} \textbf{1992}, \emph{68}, 2362\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Lengen \latin{et~al.}(1994)Lengen, Joppien, von Pietrowski, and
+  M\"oller]{lengen}
+Lengen,~M.; Joppien,~M.; von Pietrowski,~R.; M\"oller,~T. Assignment of
+  Impurity States in Xenon-Doped Argon Clusters. \emph{Chem. Phys. Lett.}
+  \textbf{1994}, \emph{229}, 362 -- 369\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Tchaplyguine \latin{et~al.}(2004)Tchaplyguine, Marinho, Gisselbrecht,
+  Schulz, Martensson, Sorensen, Naves~de Brito, Feifel, \"Ohrwall, Lundwall,
+  and et~al.]{tchaplyguine}
+Tchaplyguine,~M.; Marinho,~R.~R.; Gisselbrecht,~M.; Schulz,~J.; Martensson,~N.;
+  Sorensen,~S.~L.; Naves~de Brito,~A.; Feifel,~R.; \"Ohrwall,~G.; Lundwall,~M.
+  \latin{et~al.}  The Size of Neutral Free Clusters as Manifested in the
+  Relative Bulk-to-Surface Intensity in Core Level Photoelectron Spectroscopy.
+  \emph{J. Chem. Phys.} \textbf{2004}, \emph{120}, 345 -- 356\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Hoener \latin{et~al.}(2008)Hoener, Bostedt, Thomas, Landt, Eremina,
+  Wabnitz, Laarmann, Treusch, Castro, and M\"oller]{hoener}
+Hoener,~M.; Bostedt,~C.; Thomas,~H.; Landt,~L.; Eremina,~E.; Wabnitz,~H.;
+  Laarmann,~T.; Treusch,~R.; Castro,~A. R. B.~d.; M\"oller,~T. Charge
+  Recombination in Soft X-Ray Laser Produced Nanoplasmas. \emph{J. Phys. B}
+  \textbf{2008}, \emph{41}, 181001\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Danylchenko \latin{et~al.}(2006)Danylchenko, Doronin, Kovalenko, and
+  Samovarov]{Danylchenko}
+Danylchenko,~O.; Doronin,~Y.; Kovalenko,~S.; Samovarov,~V. Phase Separation
+  into Pure Components in Mixed Ar-Xe Clusters. \emph{JETP Lett.}
+  \textbf{2006}, \emph{84}, 324 -- 328\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Danylchenko \latin{et~al.}(2007)Danylchenko, Doronin, Kovalenko,
+  Libin, Samovarov, and Vakula]{Danylchenko07}
+Danylchenko,~O.~G.; Doronin,~Y.~S.; Kovalenko,~S.~I.; Libin,~M.~Y.;
+  Samovarov,~V.~N.; Vakula,~V.~L. Luminescence Evidence for Bulk and Surface
+  Excitons in Free Xenon Clusters. \emph{Phys. Rev. A} \textbf{2007},
+  \emph{76}, 043202\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Lindblad \latin{et~al.}(2011)Lindblad, Rander, Bradeanu, \"Ohrwall,
+  Bj\"orneholm, Mucke, Ulrich, Lischke, and Hergenhahn]{lindblad}
+Lindblad,~A.; Rander,~T.; Bradeanu,~I.; \"Ohrwall,~G.; Bj\"orneholm,~O.;
+  Mucke,~M.; Ulrich,~V.; Lischke,~T.; Hergenhahn,~U. Chemical Shifts of Small
+  Heterogeneous Ar/Xe Clusters. \emph{Phys. Rev. B} \textbf{2011}, \emph{83},
+  125414\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[von Pietrowski \latin{et~al.}(2006)von Pietrowski, von Haeften,
+  Laarmann, M\"oller, Museur, and Kanaev]{pietrowski}
+von Pietrowski,~R.; von Haeften,~K.; Laarmann,~T.; M\"oller,~T.; Museur,~L.;
+  Kanaev,~A.~V. Electronic and Geometric Structure of Doped Rare-Gas Clusters:
+  Surface, site and size effects studied with luminescence spectroscopy.
+  \emph{Eur. Phys. J. D} \textbf{2006}, \emph{38}, 323--336, and references
+  therein\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Lindblad \latin{et~al.}(2006)Lindblad, Bergersen, Rander, Lundwall,
+  \"Ohrwall, Tchaplyguine, Svensson, and Bj\"orneholm]{lindbladpccp}
+Lindblad,~A.; Bergersen,~H.; Rander,~T.; Lundwall,~M.; \"Ohrwall,~G.;
+  Tchaplyguine,~M.; Svensson,~S.; Bj\"orneholm,~O. The Far from Equilibrium
+  Structure of Argon Clusters Doped with Krypton or Xenon. \emph{Phys. Chem.
+  Chem. Phys.} \textbf{2006}, \emph{8}, 1899--1905\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Marques and Pereira(2013)Marques, and Pereira]{marques}
+Marques,~J. M.~C.; Pereira,~F.~B. A Detailed Investigation on the Global
+  Minimum Structures of Mixed Rare-Gas Clusters: Geometry, Energetics, and Site
+  Occupancy. \emph{J. Comput. Chem.} \textbf{2013}, \emph{34}, 505--517\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Vach(1999)]{Vach_1999}
+Vach,~H. Impurity Dynamics in Binary van der Waals Clusters Created by Pick-Up.
+  \emph{J. Chem. Phys.} \textbf{1999}, \emph{111}, 3536 -- 3547\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Fasshauer \latin{et~al.}(2010)Fasshauer, Kryzhevoi, and
+  Pernpointner]{fasshauer}
+Fasshauer,~E.; Kryzhevoi,~N.~V.; Pernpointner,~M. Possible Electronic Decay
+  Channels in the Ionization Spectra of Small Clusters Composed of Ar and Xe: A
+  Four-Component Relativistic Treatment. \emph{J. Chem. Phys.} \textbf{2010},
+  \emph{133}, 014303\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Fasshauer \latin{et~al.}(2013)Fasshauer, Pernpointner, and
+  Gokhberg]{Fasshauer13}
+Fasshauer,~E.; Pernpointner,~M.; Gokhberg,~K. Interatomic Decay of
+  Inner-Valence Ionized States in ArXe Clusters: Relativistic Approach.
+  \emph{J. Chem. Phys.} \textbf{2013}, \emph{138}, 014305\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Hagena(1992)]{Hagena1992}
+Hagena,~O.~F. {Cluster Ion Sources}. \emph{Rev. Sci. Instrum.} \textbf{1992},
+  \emph{63}, 2374--2379\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Arion \latin{et~al.}(2011)Arion, Mucke, F\"orstel, Bradshaw, and
+  Hergenhahn]{arion}
+Arion,~T.; Mucke,~M.; F\"orstel,~M.; Bradshaw,~A.~M.; Hergenhahn,~U.
+  Interatomic Coulombic Decay in Mixed NeKr Clusters. \emph{J. Chem. Phys.}
+  \textbf{2011}, \emph{134}, 074306\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Danylchenko \latin{et~al.}(2015)Danylchenko, Kovalenko, Konotop, and
+  Samovarov]{danylchenko2015}
+Danylchenko,~O.~G.; Kovalenko,~S.~I.; Konotop,~O.~P.; Samovarov,~V.~N.
+  Diagnostics of Composition and Size of Clusters Formed in Supersonic Jets of
+  ArKr Gas Mixtures. \emph{Low Temp. Phys.} \textbf{2015}, \emph{41},
+  637--644\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Lundwall \latin{et~al.}(2004)Lundwall, Tchaplyguine, \"Ohrwall,
+  Feifel, Lindblad, Lindgren, S\"orensen, Svensson, and
+  Bj\"orneholm]{lundwall_arkr}
+Lundwall,~M.; Tchaplyguine,~M.; \"Ohrwall,~G.; Feifel,~R.; Lindblad,~A.;
+  Lindgren,~A.; S\"orensen,~S.; Svensson,~S.; Bj\"orneholm,~O. Radial Surface
+  Segregation in Free Heterogeneous Argon/Krypton Clusters. \emph{Chem. Phys.
+  Lett.} \textbf{2004}, \emph{392}, 433--438\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Bergersen \latin{et~al.}(2006)Bergersen, Abu-Samha, Harnes,
+  Bj\"orneholm, Svensson, S{\ae}thre, and B{\o}rve]{bergersen}
+Bergersen,~H.; Abu-Samha,~M.; Harnes,~J.; Bj\"orneholm,~O.; Svensson,~S.;
+  S{\ae}thre,~L.~J.; B{\o}rve,~K.~J. Size of Neutral Argon Clusters from
+  Core-Level Photoelectron Spectroscopy. \emph{Phys. Chem. Chem. Phys.}
+  \textbf{2006}, \emph{8}, 1891--1898\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Hergenhahn \latin{et~al.}(2009)Hergenhahn, Barth, Ulrich, Mucke,
+  Joshi, Lischke, Lindblad, Rander, \"Ohrwall, and Bj\"orneholm]{hergenhahnprb}
+Hergenhahn,~U.; Barth,~S.; Ulrich,~V.; Mucke,~M.; Joshi,~S.; Lischke,~T.;
+  Lindblad,~A.; Rander,~T.; \"Ohrwall,~G.; Bj\"orneholm,~O. 3p Valence
+  Photoelectron Spectrum of Ar Clusters. \emph{Phys. Rev. B} \textbf{2009},
+  \emph{79}, 155448\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[F\"orstel \latin{et~al.}(2011)F\"orstel, Mucke, Arion, Lischke, Barth,
+  Ulrich, \"Ohrwall, Bj\"orneholm, Hergenhahn, and
+  Bradshaw]{foerstel_arg2_2011}
+F\"orstel,~M.; Mucke,~M.; Arion,~T.; Lischke,~T.; Barth,~S.; Ulrich,~V.;
+  \"Ohrwall,~G.; Bj\"orneholm,~O.; Hergenhahn,~U.; Bradshaw,~A.~M. Energy Band
+  Dispersion in Photoemission Spectra of Argon Clusters. \emph{J. Electron
+  Spectrosc. Relat. Phenom.} \textbf{2011}, \emph{184}, 107 -- 112, Advances in
+  Vacuum Ultraviolet and X-ray Physics, The 37th International Conference on
+  Vacuum Ultraviolet and X-ray Physics (VUVX2010)\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Mucke \latin{et~al.}(2012)Mucke, F\"orstel, Lischke, Arion, Bradshaw,
+  and Hergenhahn]{mucke_review}
+Mucke,~M.; F\"orstel,~M.; Lischke,~T.; Arion,~T.; Bradshaw,~A.~M.;
+  Hergenhahn,~U. Performance of a Short `Magnetic Bottle' Electron
+  Spectrometer. \emph{Rev. Sci. Instrum.} \textbf{2012}, \emph{83},
+  063106\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[F\"orstel(2012)]{Foerstel_phd}
+F\"orstel,~M. Investigation of Non-Local Autoionization Processes in Rare Gas
+  Clusters. Ph.D.\ thesis, Technical University Berlin, 2012;
+  http://opus.kobv.de/tuberlin/volltexte/2012/3656/\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Fasshauer(2014)]{Fasshauer_thesis}
+Fasshauer,~E. Investigation of Relativistic Effects in Electronic Decay
+  Processes in Small and Large Noble Gas Clusters by Ab Initio and New
+  Simulation Approaches. Ph.D.\ thesis, University of Heidelberg, 2014\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Wentzel(1927)]{Wentzel27}
+Wentzel,~G. {\"U}ber Strahlungslose Quantenspr{\"u}nge. \emph{Z. Physik}
+  \textbf{1927}, \emph{43}, 524 -- 530\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Feshbach(1958)]{Feshbach58}
+Feshbach,~H. Unified Theory of Nuclear Reactions. \emph{Ann. Phys.}
+  \textbf{1958}, \emph{5}, 357 -- 390\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Feshbach(1962)]{Feshbach62}
+Feshbach,~H. A Unified Theory of Nuclear Reactions. II. \emph{Ann. Phys.}
+  \textbf{1962}, \emph{19}, 287 -- 313\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Fano(1961)]{Fano61}
+Fano,~U. Effects of Configuration Interaction on Intensities and Phase Shifts.
+  \emph{Phys. Rev.} \textbf{1961}, \emph{124}, 1866--1878\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[HAR()]{HARDRoC}
+{HARDRoC}, Hunting Asymptotic Relativistic Decay Rates of Clusters (2013),
+  written by E.~Fasshauer (see
+  http://www.pci.uni-heidelberg.de/tc/usr/elke/hardroc/html/main.html)\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Haberland(1994)]{haberland}
+Haberland,~H. \emph{Clusters of Atoms and Molecules Theory, Experiment, and
+  Clusters of Atoms}; Springer Series in Chemical Physics; Springer Berlin
+  Heidelberg: Berlin, Heidelberg, 1994; p 422\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Avo()]{Avogadro}
+Avogadro: An Open-Source Molecular Builder and Visualization Tool. Version
+  1.1.0. http://avogadro.openmolecules.net\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Hanwell \latin{et~al.}(2012)Hanwell, Curtis, Lonie, Vandermeersch,
+  Zurek, and Hutchison]{Hanwell12}
+Hanwell,~M.~D.; Curtis,~D.~E.; Lonie,~D.~C.; Vandermeersch,~T.; Zurek,~E.;
+  Hutchison,~G.~R. Avogadro: An Advanced Semantic Chemical Editor,
+  Visualization, and Analysis Platform. \emph{J. Cheminformatics}
+  \textbf{2012}, \emph{4}, 17\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Tchaplyguine \latin{et~al.}(2004)Tchaplyguine, Lundwall, Gisselbrecht,
+  \"Ohrwall, Feifel, Sorensen, Svensson, Martensson, and
+  Bj\"orneholm]{tchaplyguinearxe}
+Tchaplyguine,~M.; Lundwall,~M.; Gisselbrecht,~M.; \"Ohrwall,~G.; Feifel,~R.;
+  Sorensen,~S.; Svensson,~S.; Martensson,~N.; Bj\"orneholm,~O. Variable Surface
+  Composition and Radial Interface Formation in Self-Assembled Free, Mixed
+  Ar/Xe Clusters. \emph{Phys. Rev. A} \textbf{2004}, \emph{69}, 031201(R)\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Herman \latin{et~al.}(1988)Herman, LaRocque, and Stoicheff]{Herman88}
+Herman,~P.~R.; LaRocque,~P.~E.; Stoicheff,~B.~P. Vacuum Ultraviolet Laser
+  Spectroscopy. V. Rovibronic Spectra of Ar$_2$ and Constants of the Ground and
+  Excited States. \emph{J. Chem. Phys.} \textbf{1988}, \emph{89}, 4535 --
+  4549\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Freeman \latin{et~al.}(1974)Freeman, Yoshino, and Tanaka]{Freeman74}
+Freeman,~D.~E.; Yoshino,~K.; Tanaka,~Y. Vacuum Ultraviolet Absorption Spectrum
+  of the van der Waals Molecule Xe$_2$. I. Ground State Vibrational Structure,
+  Potential Well Depth, and Shape. \emph{J. Chem. Phys.} \textbf{1974},
+  \emph{61}, 4880 -- 4889\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Mucke(2011)]{Mucke_phd}
+Mucke,~M. Employing Electron-Electron Coincidence Techniques to Investigate the
+  Autoionisation of Clusters. Ph.D.\ thesis, Technical University Berlin, 2011;
+  http://opus.kobv.de/tuberlin/volltexte/2011/3073/\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Schnorr \latin{et~al.}(2015)Schnorr, Senftleben, Schmid, Augustin,
+  Kurka, Rudenko, Foucar, Broska, Meyer, Anielski, Anielski, Boll, Rolles,
+  K{\"u}bel, Kling, Jiang, Mondal, Tachibana, Ueda, Marchenko, Simon, Brenner,
+  Treusch, Scheit, Averbukh, Ullrich, Pfeifer, Schr{\"o}ter, and
+  Moshammer]{Schnorr15}
+Schnorr,~K.; Senftleben,~A.; Schmid,~G.; Augustin,~S.; Kurka,~M.; Rudenko,~A.;
+  Foucar,~L.; Broska,~A.; Meyer,~K.; Anielski,~D. \latin{et~al.}
+  {Time-Resolved Study of ICD in Ne Dimers Using FEL Radiation}. \emph{J.
+  Electron Spectrosc. Relat. Phenom.} \textbf{2015}, \emph{204}, 245\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Fasshauer(2016)]{fasshauernjp}
+Fasshauer,~E. Non-Nearest Neighbour ICD in Clusters. \emph{New J. Phys.}
+  \textbf{2016}, \emph{18}, 043028\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Samson and Stolte(2002)Samson, and Stolte]{samson2002}
+Samson,~J. A.~R.; Stolte,~W.~C. Precision Measurements of the Total
+  Photoionization Cross-Sections of He, Ne, Ar, Kr, and Xe. \emph{J. Electron
+  Spectrosc. Relat. Phenom.} \textbf{2002}, \emph{123}, 265 -- 276\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Velchev \latin{et~al.}(1999)Velchev, Hogervorst, and Ubachs]{velchev}
+Velchev,~I.; Hogervorst,~W.; Ubachs,~W. Precision VUV Spectroscopy of Ar I at
+  105 nm. \emph{J. Phys. B} \textbf{1999}, \emph{32}, L511\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Sansonetti and Martin(2005)Sansonetti, and Martin]{sansonetti}
+Sansonetti,~J.~E.; Martin,~W.~C. Handbook of Basic Atomic Spectroscopic Data.
+  \emph{J. Phys. Chem. Ref. Data} \textbf{2005}, \emph{34}, 1559--2259\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Rolles \latin{et~al.}(2009)Rolles, Zhang, Pesic, Bozek, and
+  Berrah]{rolles}
+Rolles,~D.; Zhang,~H.; Pesic,~Z.~D.; Bozek,~J.~D.; Berrah,~N. Emergence of
+  Valence Band Structure in Rare-Gas Clusters. \emph{Chem. Phys. Lett.}
+  \textbf{2009}, \emph{468}, 148--152\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[F\"orstel \latin{et~al.}(2010)F\"orstel, Mucke, Arion, Lischke, Barth,
+  Ulrich, \"Ohrwall, Bj\"orneholm, Hergenhahn, and
+  Bradshaw]{foerstel_arg1_2010}
+F\"orstel,~M.; Mucke,~M.; Arion,~T.; Lischke,~T.; Barth,~S.; Ulrich,~V.;
+  \"Ohrwall,~G.; Bj\"orneholm,~O.; Hergenhahn,~U.; Bradshaw,~A.~M. Observation
+  of Electronic Energy Bands in Argon Clusters. \emph{Phys. Rev. B}
+  \textbf{2010}, \emph{82}, 125450\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Jacobi and Rotermund(1982)Jacobi, and Rotermund]{jacobi}
+Jacobi,~K.; Rotermund,~H. UV Photoemission from Physisorbed Atoms and
+  Molecules: Electronic Binding Energies of Valence Levels in Mono- and
+  Multilayers. \emph{Surf. Sci.} \textbf{1982}, \emph{116}, 435 -- 455\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Jacobi(1988)]{jacobi2}
+Jacobi,~K. Photoemission from Ar, Kr, and Xe on Pb(111). \emph{Phys. Rev. B}
+  \textbf{1988}, \emph{38}, 5869 -- 5877\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Hergenhahn \latin{et~al.}(2002)Hergenhahn, Kolmakov, Riedler,
+  de~Castro, L\"ofken, and M\"oller]{hergenhahn2002}
+Hergenhahn,~U.; Kolmakov,~A.; Riedler,~M.; de~Castro,~A. R.~B.; L\"ofken,~O.;
+  M\"oller,~T. Observation of excitonic satellites in the photoelectron spectra
+  of Ne and Ar clusters. \emph{Chem. Phys. Lett.} \textbf{2002}, \emph{351},
+  235--241\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Feifel \latin{et~al.}(2004)Feifel, Tchaplyguine, \"Ohrwall, Salonen,
+  Lundwall, Marinho, Gisselbrecht, Sorensen, Naves~de Brito, Karlsson,
+  M\r{a}rtensson, Svensson, and Bj\"orneholm]{feifel}
+Feifel,~R.; Tchaplyguine,~M.; \"Ohrwall,~G.; Salonen,~M.; Lundwall,~M.;
+  Marinho,~R. R.~T.; Gisselbrecht,~M.; Sorensen,~S.~L.; Naves~de Brito,~A.;
+  Karlsson,~L. \latin{et~al.}  From Localised to Delocalised Electronic States
+  in Free Ar, Kr and Xe Clusters. \emph{Eur. Phys. J. D} \textbf{2004},
+  \emph{30}, 343 -- 351\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Zhang \latin{et~al.}(2008)Zhang, Rolles, Pesic, Bozek, and
+  Berrah]{zhang}
+Zhang,~H.; Rolles,~D.; Pesic,~Z.~D.; Bozek,~J.~D.; Berrah,~N. Angular
+  Distributions of Inner-Shell Photoelectrons from Rare-Gas Clusters.
+  \emph{Phys. Rev. A} \textbf{2008}, \emph{78}, 063201\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Kruit and Read(1983)Kruit, and Read]{kruit}
+Kruit,~P.; Read,~F.~H. Magnetic Field Paralleliser for 2$\pi$
+  Electron-Spectrometer and Electron-Image Magnifier. \emph{J. Phys. E}
+  \textbf{1983}, \emph{16}, 313--324\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Mucke \latin{et~al.}(2010)Mucke, Braune, Barth, F\"orstel, Lischke,
+  Ulrich, Arion, Becker, Bradshaw, and Hergenhahn]{mucke}
+Mucke,~M.; Braune,~M.; Barth,~S.; F\"orstel,~M.; Lischke,~T.; Ulrich,~V.;
+  Arion,~T.; Becker,~U.; Bradshaw,~A.; Hergenhahn,~U. A Hitherto Unrecognized
+  Source of Low-Energy Electrons in Water. \emph{Nat. Phys.} \textbf{2010},
+  \emph{6}, 143--146\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[F\"orstel \latin{et~al.}(2013)F\"orstel, Arion, and
+  Hergenhahn]{foerstel_2013}
+F\"orstel,~M.; Arion,~T.; Hergenhahn,~U. Measuring the Efficiency of
+  Interatomic Coulombic Decay in Ne Clusters. \emph{J. Electron Spectros.
+  Relat. Phenomena} \textbf{2013}, \emph{191}, 16 -- 19\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\bibitem[Fasshauer \latin{et~al.}()Fasshauer, F\"orstel, Mucke, Arion, Lischke,
+  and Hergenhahn]{arkr}
+Fasshauer,~E.; F\"orstel,~M.; Mucke,~M.; Arion,~T.; Lischke,~T.; Hergenhahn,~U.
+  to be published\relax
+\mciteBstWouldAddEndPuncttrue
+\mciteSetBstMidEndSepPunct{\mcitedefaultmidpunct}
+{\mcitedefaultendpunct}{\mcitedefaultseppunct}\relax
+\EndOfBibitem
+\end{mcitethebibliography}
 

### 2019-03-22 onefolder_2/exp_results.tex
submitted files

--- 2016-07-04 onefolder/master.tex
@@
-	
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% This is a (brief) model paper using the achemso class
-%% The document class accepts keyval options, which should include
-%% the target journal and optionally the manuscript type.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\documentclass[journal=jpccck,manuscript=article,layout=twocolumn]{achemso}
-\documentclass[journal=jpccck,manuscript=article]{achemso}
-
-% UHe stuff
-\def\EB{E_{\rm b}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Place any additional packages needed here.  Only include packages
-%% which are essential, to avoid problems later. Do NOT use any
-%% packages which require e-TeX (for example etoolbox): the e-TeX
-%% extensions are not currently available on the ACS conversion
-%% servers.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage[english]{babel}
-\usepackage{braket}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath,amsfonts,amssymb}
-\usepackage{dsfont}
-\usepackage{booktabs}
-\usepackage{units}
-\usepackage{xcolor}
-\usepackage{multirow}
-\usepackage{tikz,pgfplots}
-\usepackage{float} %force figure position
-
-\usetikzlibrary{patterns,shadows,trees,calc}
-\usepgfplotslibrary{units}
-
-\pgfplotsset{compat=1.10}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% If issues arise when submitting your manuscript, you may want to
-%% un-comment the next line.  This provides information on the
-%% version of every file you have used.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%\listfiles
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Place any additional macros here. Please use \newcommand* where
-%% possible, and avoid layout-changing macros (which are not used
-%% when typesetting).
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newcommand*\mycommand[1]{\texttt{\emph{#1}}}
-% Define some colours
-\definecolor{diplom1}{rgb}{0.0 0.4 1.0}
-\definecolor{diplom2}{rgb}{0.0 0.0 0.6}
-\definecolor{diplom3}{RGB}{153,0,0} %unirot
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Meta-data block
-%% ---------------
-%% Each author should be given as a separate \author command.
-%%
-%% Corresponding authors should have an e-mail given after the author
-%% name as an \email command. Phone and fax numbers can be given
-%% using \phone and \fax, respectively; this information is optional.
-%%
-%% The affiliation of authors is given after the authors; each
-%% \affiliation command applies to all preceding authors not already
-%% assigned an affiliation.
-%%
-%% The affiliation takes an option argument for the short name.  This
-%% will typically be something like "University of Somewhere".
-%%
-%% The \altaffiliation macro should be used for new address, etc.
-%% On the other hand, \alsoaffiliation is used on a per author basis
-%% when authors are associated with multiple institutions.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author{Marko F\"orstel}
-\altaffiliation{Now at: Institut für Optik und Atomare Physik, Technische Universit\"at Berlin, Hardenbergstr. 36, 10623 Berlin, Germany}
-\author{Melanie Mucke}
-\altaffiliation{Now at: Department of Physics and Astronomy, Uppsala University, Box 516, 75120 Uppsala, Sweden}
-\author{Tiberiu Arion}
-\altaffiliation{Now at: Center for Free-Electron Laser Science/DESY, Notkestr. 85, D-22607 Hamburg, Germany}
-\author{Toralf Lischke}
-\affiliation[IPP]{Max-Planck-Institute for Plasma Physics, Boltzmannstr. 2, D-85748 Garching, Germany}
-\author{Markus Pernpointner}
-\affiliation[University of Heidelberg]{Theoretical Chemistry, University of Heidelberg,
-              Im Neuenheimer Feld 229, D-69120 Heidelberg, Germany}
-\author{Uwe Hergenhahn}
-\affiliation[IOM]{Leibniz Institute of Surface Modification, Permoserstr. 15, D-04318 Leipzig, Germany}
-\alsoaffiliation[IPP HGW]{Max-Planck-Institute for Plasma Physics, Wendelsteinstr. 1, D-14791 Greifswald, Germany}
-\email{uwe.hergenhahn@iom-leipzig.de}
-\author{Elke Fasshauer}
-\affiliation[UIT]{Centre for Theoretical and Computational Chemistry,
-Department of Chemistry, University of Troms\o
--- The Arctic University of Norway, N-9037 Troms\o, Norway}
-\email{elke.fasshauer@uit.no}
-%\phone{+123 (0)123 4445556}
-%\fax{+123 (0)123 4445557}
-%\alsoaffiliation[Second University]
-%{Department of Chemistry, Second University, Nearby Town}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The document title should be given as usual. Some journals require
-%% a running title from the author: this should be supplied as an
-%% optional argument to \title.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Long-range Interatomic Coulombic Decay in ArXe clusters: Experiment and Theory}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Some journals require a list of abbreviations or keywords to be
-%% supplied. These should be set up here, and will be printed after
-%% the title and author information, if needed.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\abbreviations{IR,NMR,UV}
-%\keywords{American Chemical Society, \LaTeX}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The manuscript does not need to include \maketitle, which is
-%% executed automatically.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The "tocentry" environment can be used to create an entry for the
-%% graphical table of contents. It is given here as some journals
-%% require that it is printed as part of the abstract page. It will
-%% be automatically moved as appropriate.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{tocentry}
-
-\begin{center}
- \includegraphics[height=3.5cm]{front1.pdf}
-\end{center}
-
-%Some journals require a graphical entry for the Table of Contents.
-%This should be laid out ``print ready'' so that the sizing of the
-%text is correct.
-%
-%Inside the \texttt{tocentry} environment, the font used is Helvetica
-%8\,pt, as required by \emph{Journal of the American Chemical
-%Society}.
-%
-%The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
-%permitted for  \emph{Journal of the American Chemical Society}
-%graphical table of content entries. The box will not resize if the
-%content is too big: instead it will overflow the edge of the box.
-%
-%This box and the associated title will always be printed on a
-%separate page at the end of the document.
-
-\end{tocentry}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The abstract environment will automatically gobble the contents
-%% if an abstract is not used by the target journal.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{abstract}
-
-\begin{abstract}
-We report about autoionization channels of Ar inner valence ionized states in mixed ArXe clusters and compare
-our experimental data obtained by electron-electron coincidence spectroscopy
-to our theoretical simulations for representative cluster structures.
-The combined experimental and theoretical data show that the autoionization of Ar 3s$^{-1}$ in ArXe is dominated by Interatomic Coulombic Decay (ICD) to Xe atoms in the second and higher coordination shells of the originally excited atom.
-Clusters with a range of sizes, compositions and structures were probed. 
-The Xe content in the clusters was varied between 10\,\% and 53\,\%. 
-Besides ICD, also Electron Transfer Mediated Decay (ETMD(3)) was found important in many of the calculated spectra, but is seen with less intensity in the experimental spectra. 
-From the calculations, we identify structural motifs which minimize the ETMD vs.
-the ICD rate and suggest that these are preferentially realized in our experiment, in which clusters are formed by supersonic expansion of an Ar-Xe mixture.
-Suggested cluster structures either feature a clear segregation between Ar and Xe fractions, e.g. Xe core, Ar shell systems, or contain a few Xe atoms singled out in surface sites on an Ar cluster.
-These structures differ significantly from the majority of calculated minimum energy structures for ArXe systems of 38 atoms, which might show that the latter, annealed structures are not realized in our experiment.
-We show experimentally that the relaxation of Ar inner valence states by ICD and ETMD together has an efficiency of unity, within the experimental accuracy, for all clusters except those with the lowest Xe content.
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Start the main part of the manuscript here.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{intro}
-\section{Introduction}
-%
-Electron spectroscopy can make important contributions to the 
-research on composition and structure of free nanoparticles.\cite{
-jpcc} Besides photoionization, free electrons emerging from 
-nanoparticles can also be produced by the relaxation of 
-electronically excited states. One such process, which is of 
-particular relevance in weakly bonded systems, is the 
-Interatomic or Intermolecular Coulombic Decay (ICD).\cite{
-cederbaum} In ICD, an electronic excitation decays by energy 
-transfer to one of its neighboring atoms or molecules, thus 
-releasing a free electron from the latter site. ICD is an 
-important relaxation channel e.g. for inner-valence holes in 
-atoms, and also for core level vacancies e.g. in \ce{H2O}
-, where it competes with Auger decay.\cite{slavicek}
-
-By definition, ICD is particularly sensitive to the chemical 
-environment of the atom or molecule in which the primary 
-excitation has taken place. We suggest that this property of ICD 
-decay spectra can be used to derive information on a nanoparticle 
-or a solvation system. 
-The term excitation is used here in a broader sense---in the
-systems we consider in this work, ICD occurs from an excited, singly 
-charged Ar state created by photoionization.
-In other systems, ICD was also observed from neutral excited
-states and states with more than one vacancy.
-
-We report here about studies 
-in which we produced heterogeneous clusters of the noble gases Ar 
-and Xe with different sizes, and compositions ranging from a few 
-Xe dopant atoms in an Ar matrix to clusters containing an equal 
-amount of both species. By the use of electron-electron 
-coincidence spectroscopy and of theoretical simulations on 
-prototypical systems we show how the radiationless decay spectrum 
-of Ar inner valence (3s) ionized states connects to the structure 
-of the clusters.
-
-Intermolecular Coulombic Decay initially was predicted from 
-theoretical considerations of the energy levels in singly vs.\  
-doubly ionized, and doubly vs.\ triply ionized, hydrogen bonded 
-clusters.\cite{cederbaum} First experimental work some years 
-later used Ne clusters,\cite{marburger,jahnkenedimer} but quickly 
-was followed by demonstrations of ICD in a diverse range of other 
-systems. Experimental and theoretical progress has been reviewed.
-\cite{hergenhahn_review, averbukh_review, jahnke_review} ICD 
-proceeds by an initial ionization producing an ion in an excited 
-state, followed by a transfer of energy to a neighbouring site, 
-and an electron emission process therefrom. The final state contains 
-two positive charges; one at the original site of ionization, and a second
-one at another atom or molecule.
-
-Soon after, related 
-autoionization processes were discovered that proceed via a 
-charge transfer instead of an energy transfer. 
-These were termed `Electron Transfer Mediated Decay' 
- (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
- which the originally excited site is neutralized by the decay 
-and `exchange ICD' for charge transfer contributions to the 
-normal ICD amplitude.\cite{santrarev,jahnkesat}
-We find that both energy and charge transfer induced 
-autoionization play a role in Ar-Xe, and will detail the 
-relevant processes below. The notion of ICD requires that the 
-electronic orbitals of the two sites can be distinguished, which 
-typically is the case in weakly bonded systems, held together by 
-hydrogen bonds or van-der-Waals bonds. In the case of strong
-(covalent or metallic) bonding, it is impossible to make a
-distinction between ICD and Auger decay.\cite{hergenhahn_review}
-
-Rare gas clusters are suitable prototype systems for studies of
-ICD, as they can readily be produced by supersonic 
-expansion through a cooled nozzle. 
-The size of the clusters can be changed by varying the expansion parameters.
-The formation of heterogeneous rare gas clusters by coexpansion of a gas mixture cannot {\it a priori} be taken for granted, but was experimentally shown for most combinations of two rare gases, when suitable mixing ratios and expansion parameters are used (see references throughout this article).
-
-First experiments on ICD in heterogeneous systems used Ne-Ar 
-clusters.\cite{barthnear} Those were followed by studies of 
-ICD-like inner-shell decays in aqueous solution.\cite{aziz,pokapanich,pokapanich2011}
-Pioneering work also showed the 
-potential for studies of the interface between a substrate and an 
-adsorbate by ICD.\cite{grieves} More detailed work on Ne-Ar 
-clusters was recently presented by some of the authors \cite{fasshauer2014}
-showing that an analysis of the ICD spectra
-allowed to decide between structural alternatives, for which the
-photoelectron data were indiscriminate.
-For this system, a detailed account of the
-photoelectron spectra with respect to structural features of the 
-mixed clusters is also available.\cite{lundwall}
-
-Several experimental techniques have been used for the study of mixed Ar-Xe clusters, most notably fluorescence spectroscopy, electron diffraction and photoelectron spectroscopy. 
-Early work focussed on the fluorescence of a single Xe atom 
-embedded in an Ar cluster.\cite{lengenprl}
-%Different sites of the dopant atom (on top of a surface, 
-%integrated in an Ar surface, inside the cluster) were 
-%distinguished by three separate bands in the fluorescence yield 
-%recorded as a function of excitation wavelength.\cite{goldberg} 
-Increasing the Xe concentration in the expansion lead to the formation of \ce{Xe2} and larger Xe complexes inside the clusters.\cite{lengen} 
-With increasing Xe content, the formation of Xe-core, Ar-shell systems with a sharp interface between the two species was shown in photoionization experiments.\cite{tchaplyguine,hoener}
-This finding was confirmed by electron diffraction.\cite{Danylchenko,Danylchenko07} 
-Always, the observed Xe content in the clusters is higher than the Xe content in the expanding gas mixture, as Xe can be condensed much easier than Ar.\cite{hoener,Danylchenko07}
-%A complementary study used photoelectron-photoion coincidence of
-%large Ar-Xe clusters, and found that after inner shell (Xe 4d, Ar 2p)
-%photoionization significant charge transfer between both species
-%occurs before the mass spectroscopic final state is reached.\cite{berrah}
-%
-More recently, photoelectron spectra of 
-small Ar-Xe clusters were analyzed, adding to the findings in 
-earlier work.\cite{lindblad} We will discuss this paper in 
-connection with our results below. 
-For completeness, we mention that Ar-Xe complexes can also be produced by passing clusters from a neat Ar expansion through a zone filled with Xe gas (`pick-up').\cite{pietrowski}
-Clusters produced such can structurally be quite different from those produced by coexpansion.\cite{lindbladpccp}
-
-A number of theoretical works on Ar-Xe clusters aimed at the prediction of minimum energy structures. 
-Most recently, these converged to structures which have the Xe atoms mainly in the interior.\cite{marques} 
-Xe was also found to diffuse into the interior of Ar clusters in molecular dynamics simulations after pick-up.\cite{Vach_1999} 
-The electronic energy levels of very small Ar-Xe clusters were calculated in ref \citenum{fasshauer} and the secondary electron spectra were simulated for
-model structures of one argon atom placed on a xenon surface \cite{Fasshauer13}.
-Interestingly, it was found that Ar 3s$^{-1}$ is stable 
-against autoionization in an ArXe dimer, but is destabilized by 
-adding further Xe atoms, or an Ar solvation shell, to the system, thereby allowing
-for combinations of argon and xenon atoms with larger interatomic distances. 
-Again, we will detail these results in conjunction with our 
-current work.
-
-The plan of our paper is as follows: We firstly delineate our experimental and theoretical methods. 
-Calculations were done for a number of model structures which were systematically varied, and are described in the following section.
-After that, we describe and discuss our theoretical results for the autoionization spectra of the model clusters.
-Experimental results are then shown and possible conclusions from comparing them to the calculations are given.
-Details on the experimental technique, and calculated spectra for a wider range of structures are given as Supporting Information.
-
-%\input{experimental}
-
-\section{Experimental}
-%
-\begin{table*}
-\caption{
-The expansion parameters used for cluster production. 
-Here, Xe$_{\rm in}$ is the molar fraction of Xe in the gas mixture before the expansion, $T$ is the nozzle temperature, and $p$ the stagnation pressure. 
-Experiments were performed with $d = 80~\mu$m (first two sections) and $d = 100~\mu$m (bottom section) conical nozzles of 15$^\circ$ half opening angle. 
-We basically have an Ar seeded expansion of Xe gas, as the freezing point of Ar is much lower. 
-$\langle N_{\rm Ar} \rangle$ and $\langle N_{\rm Xe} \rangle$ refer to cluster sizes for a pure Ar, or pure Xe expansion, respectively, at the given conditions, calculated from a scaling law.\protect\cite{hagena1981}
-We expect actual cluster sizes in-between these two limiting values. 
-Inaccuracies in the calculation of $\langle N\rangle$ due to fluctuations of the input parameters are less than 6\,\%. This figure does not include systematic errors of the empirical model.
-}
-\label{tab:cluster}
-
-\begin{tabular}{l c c c c r r}
-%
-\toprule
-  \multicolumn{2}{r}{size label}  &  Xe$_{\rm in}$ (\%)  &  $T$ (K)  &  $p$ (bar) & $\langle N_{\rm Ar} \rangle$ & $\langle N_{\rm Xe} \rangle$ \\
-%
-\midrule
-% Ar, from Marko 
-Ar & (1) & --- &  96.5  & 0.35  & 44  &  --- \\
-% Ar, from Marko 
-Ar & (2) & --- &  96.5  & 0.67  & 200  &  --- \\
-\midrule
-% 1103 676, 679
-ArXe & `S' & 1.2 &  174   & 0.32  & 4  &   74 \\
-% 1103 670
-ArXe & `M' & 1.2 &  174   & 0.49  & 11  &  199 \\
-% 1103 671
-ArXe & `L' & 1.2 &  174   & 0.68  & 23  &  431 \\
-\midrule
-% 1103 663
-ArXe & `S' & 3.0 &  172   & 0.28  & 3  &   57 \\
-% 1103 653
-ArXe & `M' & 3.0 &  172   & 0.51  & 12  &  233 \\
-% 1103 658
-ArXe & `L' & 3.0 &  172   & 0.68  & 24  &  458 \\
-\midrule
-% 1103 630
-ArXe & `S'  & 5.0 &  167  & 0.37  & 7  &  129 \\
-% 1103 640
-ArXe & `M' & 5.0 &  171   & 0.51  & 13  &  240 \\
-% 1103 629
-ArXe & `L'  & 5.0 &  167  & 0.68  & 28  &  537 \\
-\midrule
-% 1004 867 (32 eV)
-ArXe & `XL' & 2.5 &  154  & 2.12  & 995 & 18800\\
-\midrule
-% 0506 382, Keller offset ber?cksichtigt
-Xe &  & 100 & 183.5  & 0.68  & ---  &  615 \\     
-% 1004 868
-%868 & & 2.5 &  158   & 1.50  &  355 &  6090\\
-% 1004 886 (17 eV)
-%886 &  & 2.5 &  161   & 2.41  &  980 & 16770\\
-% 1004 858
-%858 &  & 5.0 &  149   & 2.50  & 1620 & 27700\\
-%
-\bottomrule
-\end{tabular}
-\end{table*}
-%
-%
-The apparatus used for the experiments consists of a supersonic molecular jet with a cooled nozzle, and a magnetic bottle spectrometer, which detects photoelectrons and secondary electrons produced after ionization with synchrotron radiation.\cite{arion}
-% Leave this citation in place to avoid Latex error
-A comprehensive description can be found in ref \citenum{arion}, and here we focus on details specific for the current experiment. 
-Commercialy obtained Ar and Xe gas was filled into 
-separate cylinders up to pressures suitable for producing a certain mixing ratio. The gases were then allowed to mix before the expansion. 
-Expansion parameters are given in Table \ref{tab:cluster}. 
-Similar expansion conditions are further referred by the labels `S'-`XL', as given in the Table.
-
-Prediction of the sizes of clusters from a supersonic expansion mainly rests on empirical scaling laws,\cite{hagena1981} which have been the subject of some discussion.
-Moreover, such scaling laws originally were derived only for pure gas expansions.
-A recent investigation of cluster sizes in a mixed Ar-Kr expansion yielded a revised scaling law, which essentially amounts to the use of a weighted average over the atom-specific parameters of the two gases.\cite{danylchenko2015}
-Although the analogy to our case is not complete, as phase segregation occurs in Ar-Kr to a much lesser extent,\cite{Vach_1999,lundwall_arkr} we expect scaling law cluster sizes between the values calculated for Ar and Xe.
-Recent analyses of photoionization spectra suggest that mean sizes arrived at by scaling laws are smaller than the actual size, at least for rare gas clusters in the range $\langle N\rangle < 1000$.\cite{bergersen,hergenhahnprb,foerstel_arg2_2011}
-For the expansion conditions labelled `S'-`L', we therefore expect that the scaling law estimates are a lower boundary for the actual cluster size.
-
-The expansion chamber for the supersonic jet is separated from the interaction chamber by a non-magnetic, conical skimmer with an opening of 1~mm in diameter (Beam Dynamics). 
-At few cm distance behind the skimmer, the cluster jet was crossed by synchrotron radiation from the BESSY electron storage ring at Helmholtz-Zentrum Berlin. 
-Electrons were detected by a short `magnetic bottle' time-of-flight spectrometer, that has been described earlier.\cite{mucke_review}
-Due to its large collection angle, this instrument is particularly suited for experiments that employ electron-electron coincidence detection.
-Data were recorded in two different beamtimes at the UE112-PGM-1 (small and medium sized clusters, first two sections in Table \ref{tab:cluster}) and at the TGM-4 beamline (large clusters, last section in Table \ref{tab:cluster}).
-Linearly, horizontally polarized radiation was used. 
-The storage ring was operated in single bunch conditions.
-Spectra of pure Ar clusters shown for comparison are from ref \citenum{foerstel_arg2_2011}, and a spectrum of pure Xe clusters was recorded with the set-up described in ref \citenum{hergenhahnprb}.
-
-The entrance aperture and drift tube of the magnetical bottle spectrometer can be independently biased to influence the electron flight times. 
-For the data shown here, slightly positive bias voltages were used (+1.8 V to +2.2 V) in order to have all electrons arriving at the detector within one BESSY single bunch period (800 ns). 
-The detection efficiency was determined as 0.6, with the method outlined in ref \citenum{mucke_review}.
-Data were converted from flight times to kinetic energy by measuring calibration data for atomic photolines of known binding energy.
-The systematical uncertainty of this procedure may lead to a common shift of all experimental kinetic energy data shown in this article of up to 30~meV.
-
-The high detection efficiency of the instrument is a pre-requisite for measuring two-electron emission processes, such as photoelectron emission followed by ICD or ETMD, by using electron-electron coincidence detection.
-This allows to filter the full electron spectrum for contributions arising after emission of an Ar 3s photoelectron.
-ICD/ETMD spectra presented here are based on this method, which has been explained earlier.\cite{mucke_review,Foerstel_phd}
-Technical details and full electron-electron coincidence spectra are given in the Supporting Information.
-
-%\input{theory}
-\section{Theoretical Approach}
-%
-Experimental coincidence spectra are given by the multitude of
-kinetic energies $E_{\rm sec}$ of the secondary electron
-and the intensities of the peaks. The latter is proportional to the
-probability of the decay as well as the theoretically determinable
-decay width $\Gamma=\frac{\hbar}{\tau}$,
-which is inversely proportional to the lifetime $\tau$ of the decay process.
-The manifold of the
-secondary energies and decay widths will therefore compose the electron-electron
-coincidence spectrum.
-In case of noble gas clusters
-with given geometrical structures three aspects have to be taken into account:
-different decay mechanisms, the possibility to decay with multiple
-interaction partners and different decay channels $\beta$ within
-each decay mechanism.
-At the current stage of development we need to neglect the nuclear dynamics which
-additionally might play an important role.
-
-%We are interested in describing the electron emission spectra of excited states in clusters, that where measured by the electron-electron coincidence method in our experiments. 
-%In our theoretical description, these will be composed of multiple transitions, each characterized by a kinetic energy $E_{\rm sec}$ of the secondary electrons, and the intensity of the peak.
-%The latter is proportional to the probability of the decay, represented here by the decay width $\Gamma_\beta = \hbar/\tau_\beta$, where $\tau_\beta$ is the lifetime due to the respective transition.
-%The total decay width $\Gamma$ is the sum of all partial $\Gamma_\beta$.
-%In case of noble gas clusters with a given geometrical structure, three aspects have to be taken into account:
-%different decay mechanisms, the contribution of different cluster sites to the respective decay, and the existence of different decay channels within each decay mechanism.
-%At the current stage of development we have to neglect the nuclear dynamics, which
-
-This means, for the evaluation of the decay width we are dealing with a sum over three different indices: 
-For a given structure it is most convenient to
-start with a decomposition of the system into interaction partners of
-the different relevant decay mechanisms, i.e. pairs (combination of two atoms regardless
-of their internuclear distance) for the ICD and triples (combinations of three atoms)
-for the ETMD(3).
-These atoms do not necessarily need to form bonds between each other or
-even be close, but they are characterized according to fixed internal
-coordinates. 
-Each pair and each triple leads to a decay spectrum that can be described by the energy of the secondary electron and the decay width, which is in first order of approximation independent of other atoms present in the cluster.
-In the following, this approach will be called model of pairs and triples.
-
-%Decomposing every system into pairs and triples of atoms is a very useful
-%first order approximation to both the investigation of energies and
-%decay widths of a larger system. Pairs and triples are combinations of
-%two and three atoms, respectively.
-
-In order to determine, whether a channel $\beta$ for a given geometry and decay
-mechanism is open, i.e., whether it is in accordance with energy conservation,
-knowledge of the energies of the initial and the final states, $E_{\rm in}$ and $E_{\rm fin}$, of
-the corresponding processes is necessary.
-If the channel
-is open, the excess energy is carried away by the emitted electron
-in form of its kinetic energy $E_{\rm sec}$. These energies in the model
-of pairs and triples can be approximated by
-
-\begin{align}
- E_{\rm in}        &= SIP(X_{\rm in}) \label{equation:E_in}\\
- E_{\rm fin}^\beta &= SIP(X_{D}^\beta) + SIP(X_{E}^\beta) + \frac 1d
-           \label{equation:E_fin}\\
- E_{\rm sec}^\beta &= E_{\rm in}^\beta - E_{\rm fin}^\beta \label{equation:E_sec}
-\end{align}
-where $X_{\rm in}$ denotes the initially ionized atom and
-$X_{D}$ and $X_{E}$ describe the electron donating atom and electron
-emitting atom, respectively.
-$\beta$ denotes the decay channel characterized by the quantum numbers of the ionized atoms in the pairs and triples, $SIP(X^\beta)$ the single ionization potential of vacancy $\beta$ in atom $X$ and $d$ the interatomic distance between the atoms $X_{D}$ and $X_{E}$.
-Atomic units are used.
-The initially ionized atom $X_{\rm in}$ can
-coincide with one or both of
-the final state atoms
-$X_{D}$ and $X_{E}$.
-The distribution of the vacancies over the different
-atoms determines the kind of electronic decay process at hand. Hence, in an
-Auger process all three atoms coincide, for an ICD process $X_{\rm in}$
-coincides with $X_{D}$, for an ETMD(2) process $X_D$ and $X_E$ coincide
-and for an ETMD(3) process
-all ionized states are located on different atoms.
-
-\begin{figure}[h]
- \centering
- \includegraphics[width=\columnwidth]{channel_open_ICD.pdf}
- \caption{Illustration of channel opening: Initial (Ar3s$^{-1}$)
-          and final state (Ar3p$^{-1}$Xe5p$_{3/2}^{-1}$ and
-          Ar3p$^{-1}$Xe5p$_{1/2}^{-1}$) energies
-          for ICD in ArXe pairs as a function of 
-          internuclear distance, using eq. (\ref{equation:E_fin})
-          and the experimental ionization
-          potentials given
-          in Table \ref{tab:valence}. When the final state energy is lower
-          than the initial state energy the corresponding channel
-          is open. We call the distance at which the energies are equal
-          the `channel opening distance'. If the curves do not cross, the
-          corresponding channel is closed.}
- \label{figure:channel_open_ICD}
-\end{figure}
-
-The electron emitted by autoionization has the kinetic energy $E_{\rm sec}$. 
-If the calculated value of $E_{\rm sec}$ is negative,
-the final state energy is higher than the initial state energy and the        
-process is energetically not accessible. Hence, the corresponding channel     
-is closed, as shown in Figure \ref{figure:channel_open_ICD} for the
-Ar3p$^{-1}$Xe5p$_{1/2}^{-1}$ final state. Related to
-the opening of each channel is an internuclear distance which we will call 
-\emph{channel opening distance} in the following.
-
-This {\latin ad hoc} approach allows to easily correct for energetic shifts of ionization potentials as observed in larger clusters by adding experimentally or theoretically determined energy shifts $\Delta E(X_{I}^{\beta})$ for a given vacancy $I={\rm in},D,E$ and channel $\beta$.
-This yields the working expression for the kinetic energy of the secondary electron:
-
-\begin{equation}
- E_{\rm sec}^\beta = SIP(X_{\rm in}) + \Delta E (X_{\rm in})
-               - SIP(X_{D}^\beta) - \Delta E (X_{D}^\beta)
-               - SIP(X_{E}^\beta) - \Delta E (X_{E}^\beta)
-               - \frac 1d .
-\end{equation}
-
-The total decay width $\Gamma$ is given by the sum over the decay widths
-of all decay mechanisms. In case of the ArXe clusters we only consider
-ICD and ETMD(3), because the ETMD(2) pathway is energetically not accessible:
-
-\begin{equation}
- \Gamma = \Gamma_{\rm ICD} + \Gamma_{\rm ETMD} .
-\end{equation}
-
-These are given by the sum over the decay widths of all pairs $i$ for the
-ICD and all triples $j$ for the ETMD(3), respectively, and over all channels $\beta$:
-%
-\begin{align}
- \Gamma_{\rm ICD}  &= \sum\limits_{i,\beta} N_{{\rm ICD},i}  \, \Gamma_{{\rm ICD},i,\beta},\\
- \Gamma_{\rm ETMD} &= \sum\limits_{j,\beta} N_{{\rm ETMD},j} \, \Gamma_{{\rm ETMD},j,\beta}.
-\end{align}
-Here, $N_{{\rm ICD},i}$ and $N_{{\rm ETMD},j}$ denote the number of geometrically
-equal pairs and triples in a given cluster structure. The total number of pairs
-reads
-$N_{{\rm ICD}} = N_{\rm in} \cdot N_{D/E} = N_{\rm Ar} \cdot N_{\rm Xe}
- = \sum\limits_i N_{{\rm ICD},i}$ and the number of triples is
-$N_{{\rm ETMD}} = N_{\rm in} \cdot N_{D/E} (N_{D/E} - 1) = N_{\rm Ar} \cdot N_{\rm Xe} (N_{\rm Xe} - 1)
- = \sum\limits_j N_{{\rm ETMD},j}$.
-The numbers of geometrically equivalent pairs $N_{{\rm ICD},i}$ and triples $N_{{\rm ETMD},j}$
-strongly depend on the structure of the cluster. From these relationships
-it can be seen that a higher xenon content in the cluster statistically
-favours ETMD(3) over ICD.
-
-In previous work \cite{Fasshauer13,Fasshauer_thesis} we have shown that
-the decay width for a single pair or triple for a distinct channel $\beta$
-following Wentzel \cite{Wentzel27}, Feshbach\cite{Feshbach58,Feshbach62}
-and Fano,\cite{Fano61}
-%
-\begin{equation}
- \Gamma_{\beta}(E_{\rm res}) = 2\pi \left|
-                           \braket{\Phi_{\rm in}| H_f |\chi_{\beta}}
-                           \right|^2,
-\end{equation}
-%
-can be approximated by its asymptotic behaviour
-%
-\begin{equation}
- \Gamma_{{\rm ICD},i,\beta} = (2J_{\rm in}+1)\, \frac{3c^4}{8\pi}\,
-                        \sum\limits_{M_{in}'}
-                        \left| \left(
-                        \begin{array}{ccc}
-                        J_A'  & 1        & J_A\\
-                        -M_A' & M_A'-M_A & M_A
-                        \end{array}\right) \right|^2
-                        \frac{\sigma^{(X_E)}(\omega_{vp,\beta})}
-                        {R_i^6 \, \omega_{vp,\beta}^4 \tau_{in,\beta}},
-\end{equation}
-%
-where $J_A$, $J_A'$ and $M_A$, $M_A'$ denote the total angular momentum of the
-initially ionized atom (which is the same as the electron donor atom) in the
-initial and final state, respectively,
-and
-%
-\begin{align}
- \Gamma_{{\rm ETMD},j,\beta} =& \frac{c}{\pi} \sum\limits_{m,M_{in,D'}}
-                        \frac{\Theta_{m,k}(\alpha_j) \sigma^{(X_E)}(\omega_{vp,\beta})
-                              \left| <\tilde{D}_{m,j,\beta}(M_{in,D'})>\right|^2}
-                         {R_j^6 \omega_{vp,\beta}}\\
-               =& \frac{c}{\pi R_j^6}
-               \sum\limits_{M_{in,D'}}
-               \left( \left| <\tilde{D}_{x,j,\beta} (M_{in,D'}) > \right|^2
-                 (2+ \sin^2\alpha_j)
-               + \left| <\tilde{D}_{z,j,\beta} (M_{in,D'}) > \right|^2
-                 (1+\cos^2\alpha_j) \right) \nonumber \\
-           & \times\, \frac{c\sigma^{(X_E)}(\omega_{vp,\beta})}{\omega_{vp,\beta}}
-\end{align}
-%
-depending on 
-experimental properties
-of atoms, like the ionization cross sections
-$\sigma^{(X_E)}(\omega_{vp,\beta})$, radiative lifetimes of the initially
-ionized state $\tau_{in,\beta}$ and the excess energy transferred to the
-emitting atom (the energy of the virtual photon) $\omega_{vp,\beta}$
-and calculated dipole transition moments $\tilde{D}_{m,j,\beta}$, only.
-Here, $\Theta_{m}(\alpha_j)$ is a function depending on the angle $\alpha_j$
-of the triple and the direction of the dipole
-transition moment $m$
-(compare ref \citenum{Fasshauer13}).
-
-In this work we evaluate the secondary energies and decay widths with
-the programme HARDRoC\cite{HARDRoC,fasshauer2014} using the
-experimental ionization energies of Table \ref{tab:valence}
-and data from the literature given in Tables II and III.
-This choice is identical to the one made in ref \citenum{Fasshauer13}.
-
-%\input{structures}
-\section{Cluster Structures}
-
-From the experimental results we can obtain two hints for the cluster
-structure: the minimum size and the xenon content. In the following we will 
-use these to construct representative cluster structures, for which we will 
-simulate the ICD and ETMD spectra. At this point we put in a variety of
-structures, in order to learn about general structure-spectrum relations
-and therefore being able to
-exclude some of them by comparison of
-the ICD and ETMD spectra to the experimental ones.
-
-In our previous study\cite{Fasshauer13} the ArXe clusters were assumed
-to be large, having more than 1500 atoms. The model structures assumed
-an fcc structure and not an icosahedral structure, which is energetically
-favoured for small clusters.
-Most estimated cluster sizes given in Table \ref{tab:cluster} are much smaller.
-We use the estimated number of atoms for a pure Ar expansion as the lower limit for the actual cluster size and start our search for model structures from there.
-%
-%Additionally,
-%the expectation value for the number of xenon atoms relies on a pure
-%xenon gas. Since the xenon content in the mixed gas is much lower, also
-%the number of xenon atoms can be expected to be by far less. We therefore
-%start from the estimated number of atoms in the cluster after expansion
-%of pure argon gas.
-%We therefore rethink the possible cluster structures.
-%Furthermore, the theoretical prediction did not match the experimental results.
-%Since the spectra are strongly depending on the cluster structure as shown in
-%\cite{fasshauer2014}, the underlying structure seems not to fit and hence
-%we rethink the possible cluster structures.
-%
-For the smaller clusters measured,
-these expectation values range from \unit[3--21]{Ar atoms}. 
-The cluster sizes for expansion of a mixed gas are unknown, but
-for xenon as the second component a larger size is expected compared to a
-pure argon expansion, due to the higher polarizability
-and hence larger cohesive energy of xenon. All clusters
-contributing to the coincidence spectrum
-contain at least one xenon atom, as otherwise decay by ICD or ETMD is energetically not allowed.
-
-In a gas expansion a range of clusters sizes with different structures is produced. 
-However, for small rare gas clusters consisting of less than approximately \unit[1000]{atoms} so-called \emph{islands of stability} were found.\cite{haberland}  
-In mass spectra, clusters with mass numbers corresponding to icosahedral shapes had an abundance that was (slightly) enhanced over other sizes. 
-We therefore started from icosahedral structures and constructed mixed cluster structures by substitution of individual atoms with one or the other kind (Ar or Xe), or added individual atoms close to the desired position within a given structure.
-After that, the cluster structures were optimized using the unified force
-field implemented in the 
-Avogadro programme (version 1.1.0) \cite{Avogadro,Hanwell12} to give local
-minimum structures.
-All cluster structures are listed in Table \ref{table:theo_gammas}.
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{cluster_2_overview.pdf}
- \caption{Cluster structures composed of 13 argon atoms and two additional xenon
-          atoms on different surfaces of the argon icosahedron, varying in Xe-Xe distance:
-          (a) closest possible, (b) middle, (c) furthest away. They refer to
-          numbers 9--11 in Table \ref{table:theo_gammas}.}
- \label{figure:cluster_2_overview}
-\end{figure}
-%
-\begin{figure}[h]
- \centering
- \includegraphics[width=8.5cm]{cluster_3_overview.pdf}
- \caption{Cluster structures derived from a 55 atom icosahedral structure:
-          (a) one xenon atom on the surface, (b) six xenon atoms inside a 55 atoms cluster,
-          grouped on one side, (c) six xenon atoms distributed randomly
-          in a 55 atoms cluster. They refer to numbers 12, 18 and 19
-          in Table \ref{table:theo_gammas}.}
- \label{figure:cluster_3_overview}
-\end{figure}
-
-As discussed in the introduction, the small clusters will likely
-deviate from a core-shell structure with a xenon core surrounded
-by argon shells, as observed for large clusters.\cite{tchaplyguinearxe,Vach_1999} We therefore start from
-argon clusters of 13 or 55 atoms, and modify them in one of the following
-ways:
-%
-\begin{itemize}
- \item add one xenon atom on top of a surface / edge / vertex of
-       the argon core, with an example shown in
-       Figure \ref{figure:cluster_3_overview}a
-       (one additional xenon atom
-       on top of a surface of a \unit[55]{atom} argon core)
-       (Table \ref{table:theo_gammas}, \#6--8, \#12--14),
- \item substitute one argon atom in a surface / edge / vertex position
-       (Table \ref{table:theo_gammas}, \#15--16),
- \item substitute one or two argon atoms in the core of the argon cluster
-       by xenon atom(s) for the simulation of the core-shell structures
-       (Table \ref{table:theo_gammas}, \#1--3),
- \item add two xenon atoms on top of surfaces of a 13 atoms argon core
-       in different relative positions (see Figure
-       \ref{figure:cluster_2_overview}),
-       in order to achieve a xenon content in the cluster close to the
-       measured one (see below)
-       (Table \ref{table:theo_gammas}, \#9--11),
- \item substitute six argon atoms of a 55 atoms argon cluster by xenon
-       atoms either grouping them or distributing them througout the cluster
-       (see Figure \ref{figure:cluster_3_overview}b and c) in order to
-       achieve a xenon content in the cluster close to the measured one
-       (Table \ref{table:theo_gammas}, \#18--19).
-\end{itemize}
-
-These structures were then optimized using force field methods.
-%
-Furthermore, for comparison with the largest measured ArXe clusters, we constructed also larger core-shell structures (Table \ref{table:theo_gammas}, \#4--5).
-
-%\input{theo_results}
-\section{Theoretical Results
-\label{sec:th_results}}
-%
-%
-\begin{table}[H]
-\small
-\centering
-\caption{Structural and calculated properties of some model clusters.
-The cluster structures are characterized by the number of Ar and Xe atoms,
-and are arranged in three groups according to gross structural properties. 
-The first group contains Xe core-Ar shell systems of various
-size and relative Xe content.
-In the second group, model structures for small clusters are displayed,
-in which 1-2 Xe atoms are added at systematically varied locations
-to an icosahedric Ar clusters consisting of one or two full shells,
-or in which 1-6 Ar atoms of such cluster were replaced by Xe atoms.
-The last group contains data for calculated minimal energy structures
-of mixed ArXe clusters.\protect\cite{marques}
-The cluster structures are classified into core-shell structures (cs),
-structures with segregated xenon atoms (in) and completely mixed
-structures.
-The columns `ICD' and `ETMD' are the respective partial decay widths
-in \unit[$10^{-4}$]{eV}, and `\% ICD' gives the percentage of ICD in
-the total decay width.
-See text for details.
-\label{table:theo_gammas}
-}
-\begin{tabular}{rrrrcccccrrr}
-\toprule
-\# & \# Xe & \# Ar & Xe$_{\rm cl}$\% & str. cl. & pos. & rel. pos. & ICD   &  ETMD & \% ICD & Fig.\\ %$\Gamma_{\rm ICD,ETMD}$\\
-\midrule
- 1 &     1 &    12 &  7.7  & cs    &         &          & 0.000 & 0.000 &  -- &\\ %    0.0            \\     ArXe\_2\_1atom      
- 2 &     1 &    54 &  1.8  & cs    &         &          & 0.000 & 0.000 &  -- & \ref{figure:xe_3_in}\\ %    0.0            \\     ArXe\_3\_1atom      
- 3 &     2 &    53 &  3.6  & cs    &         &          & 0.033 & 0.167 &  16.7& \ref{figure:xe_3_in}\\ %2.006$\cdot 10^{-5}$ \\ ArXe\_3\_2atom      
- 4 &  1415 &   642 & 68.8  & cs    &         &          & 7.039 & 2.573 &  73.2& supp.\\ %9.612$\cdot 10^{-4}$ \\ ArXe\_8\_1layer     
- 5 &   561 &  3310 & 14.5  & cs    &         &          &       &       &  85  & \ref{figure:xe_6_lay5}\\ % c6l5
-
-\midrule
- 6 &     1 &    13 &  7.1  & cs    & surface &          & 0.792 & 0.000 & 100.0& \ref{figure:surf}\\ %7.922$\cdot 10^{-5}$ \\ XeAr\_2\_surface    
- 7 &     1 &    13 &  7.1  & cs    & edge    &          & 0.013 & 0.000 & 100.0&\\ %1.320$\cdot 10^{-6}$ \\ XeAr\_2\_edge       
- 8 &     1 &    13 &  7.1  & cs    & vertex  &          & 0.050 & 0.000 & 100.0&\\ %5.013$\cdot 10^{-6}$ \\ XeAr\_2\_vertex     
- 9 &     2 &    13 & 13.3  & cs    &         & closest  & 0.101 & 0.151 &  40.1& \ref{figure:2tops}\\ %2.523$\cdot 10^{-5}$ \\ XeAr\_2\_2top       
-10 &     2 &    13 & 13.3  & cs    &         & middle   & 0.159 & 0.008 &  95.4& \ref{figure:2tops}\\ %1.665$\cdot 10^{-5}$ \\ XeAr\_2\_2midtop    
-11 &     2 &    13 & 13.3  & cs    &         & furthest & 0.159 & 0.002 &  98.9& \ref{figure:2tops}\\ %1.605$\cdot 10^{-5}$ \\ XeAr\_2\_2endtop    
-12 &     1 &    55 &  1.8  & cs    & surface &          & 0.064 & 0.000 & 100.0& \ref{figure:surf}\\ %6.371$\cdot 10^{-6}$ \\ XeAr\_3\_surface    
-13 &     1 &    55 &  1.8  & cs    & edge    &          & 0.048 & 0.000 & 100.0&\\ %4.791$\cdot 10^{-6}$ \\ XeAr\_3\_edge       
-14 &     1 &    55 &  1.8  & cs    & vertex  &          & 0.027 & 0.000 & 100.0&\\ %2.701$\cdot 10^{-6}$ \\ XeAr\_3\_vertex     
-15 &     1 &    54 &  1.8  & in    & edge    &          & 0.077 & 0.000 & 100.0&\\ %7.708$\cdot 10^{-6}$ \\ XeAr\_3\_edge\_in   
-16 &     1 &    54 &  1.8  & in    & vertex  &          & 0.053 & 0.000 & 100.0&\\ %5.258$\cdot 10^{-6}$ \\ XeAr\_3\_vertex\_in 
-17 &     2 &    53 &  3.6  & in    &         &          & 0.117 & 0.055 &  68.1&\\ %1.711$\cdot 10^{-5}$ \\ XeAr\_3\_2in        
-18 &     6 &    49 & 10.9  & in    &         &          & 0.375 & 0.405 &  48.1& \ref{figure:ar_3_6in}\\ %7.796$\cdot 10^{-5}$ \\ XeAr\_3\_6in        
-19 &     6 &    49 & 10.9  & mixed &         &          & 0.292 & 0.674 &  30.3& \ref{figure:ar_3_6in}\\ %9.660$\cdot 10^{-5}$ \\ XeAr\_3\_6\_scat    
-                                                                                                 \midrule
-20 &     2 &    36 &  5.3  & cs    &         &          & 0.117 & 0.151 &  43.6& supp.\\                        % Ar$_{36}$Xe$_{2}$   
-21 &     4 &    34 & 10.5  & mixed &         &          & 0.248 & 0.587 &  29.7& supp.\\                        % Ar$_{34}$Xe$_{4}$   
-22 &     5 &    33 & 13.2  & mixed &         &          & 0.335 & 0.844 &  28.4& supp.\\                        % Ar$_{33}$Xe$_{5}$   
-23 &    13 &    25 & 34.2  & mixed &         &          & 0.828 & 5.414 &  13.3& supp.\\                        % Ar$_{25}$Xe$_{13}$  
-24 &    24 &    14 & 63.2  & mixed &         &          & 1.488 &16.718 &   8.2& supp.\\                        % Ar$_{14}$Xe$_{24}$  
-25 &    25 &    13 & 65.8  & in    &         &          & 1.432 & 4.995 &  22.3& supp.\\                        % Ar$_{13}$Xe$_{25}$  
-26 &    35 &     3 & 92.1  & in    &         &          & 2.017 & 7.051 &  22.2& supp.\\                        % Ar$_{3}$Xe$_{35}$   
-\bottomrule
-\end{tabular}
-\end{table}
-%
-The geometrical properties as well as the total ICD and ETMD decay widths
-of the investigated structures are shown in Table \ref{table:theo_gammas}.
-It is important to remember that the first ICD channel opens at a
-channel opening distance of \unit[7.58]{\AA}. In the smallest
-clusters with only one argon layer around each
-xenon atom, the Ar-Xe pair distances are below that value, therefore 
-no ICD can take place. Also, by definition, two Xe atoms are
-required for ETMD(3), hence it cannot occur in clusters with only one xenon atom.
-%Because secondary electrons are observed in the experimental spectra
-%we exclude all structures without any signal from our further
-%discussions.
-%
-\begin{figure}[H]
- \centering
- \includegraphics[width=8.0cm]{surf.pdf}\\
- \includegraphics[width=8.0cm]{R_comp.pdf}
- \caption{
- %
- Top panel: Simulated electron emission spectra of an Ar 3s vacancy in 
-          argon clusters
-          consisting of 13 and 55 atoms, with an additional xenon atom residing
-          on top of one of the argon surfaces.
-          Bottom panel: Distribution of Ar-Xe distances $d$ in the studied ArXe
-          clusters. The ICD channels to final states involving Xe 5p$_{3/2}^{-1}$ and 
-          5p$_{1/2}^{-1}$ vacancies open at \unit[7.58]{\AA} and
-          \unit[36.00]{\AA}, resp.; the former distance is marked by a vertical dotted line. 
-          Only pairs at longer interatomic
-          distances contribute to the electron emission spectra.
-          Larger Ar-Xe distances, as found in the larger cluster,
-          correspond to features at a higher kinetic energy of
-          the ICD electron (top panel).}
- \label{figure:surf}
-\end{figure}
-
-%In the investigated structures several different aspects have to be
-%taken into account which we will discuss separately if possible
-%on selected structures.
-
-We will now discuss features of several structures, using selected examples.
-First we consider clusters having an argon core of 13 and 55 atoms plus a single xenon
-atom on one of the surfaces (see Figure \ref{figure:cluster_3_overview}a
-for the structure of clusters with the 55 atoms core).
-Secondary electron spectra simulated for these systems are shown in Figure \ref{figure:surf}, top panel.
-%two different argon core sizes one consisting
-%of 13 and one consisting of 55 atoms with one xenon atom on one of
-%the surfaces (see Figure \ref{figure:cluster_3_overview} Panel a)
-%for the 55 atom core). The simulated secondary electron spectra are
-%shown in Figure \ref{figure:surf} Panel 1.
-
-Because the structures contain only one xenon atom, ETMD(3) is not possible, only ICD is expected. 
-%Both spectra show several smaller peaks which
-%are convoluted into one single peak with a maximum at
-%approximately \unit[0.2]{eV}. 
-%In comparison to the 13 argon atoms core
-%spectrum t
-The spectrum pertaining to the clusters with larger (55 atoms) Ar core shows
-signals at higher energies of the secondary electron. These features
-can be explained by investigating the Ar-Xe distance distributions
-in the clusters, shown
-in the bottom panel of Figure \ref{figure:surf}. 
-Every different value of the atom pair distance
-results in a different energy of the secondary electron and only pairs
-with a distance of larger than the channel opening distance
-(dashed gray line) will contribute
-to the spectrum. 
-In our model, there is a one-to-one correspondence between interatomic distance $d$ and kinetic energy of the ICD electron.
-The larger the interatomic distance, the higher is the
-kinetic energy of the secondary electron for a given channel.
-%Since the cluster with an Ar core of 55 atoms is larger, and therefore
-%contains Ar-Xe pairs with larger distances, its spectrum 
-Therefore, the spectrum of the cluster with a 55 atoms core extends to higher energies.
-%energies as well.
-This relation between ICD energy and cluster size holds true for all cluster structures.
-%This explains why the ICD spectrum for larger clusters extends to higher energies, and holds for all cluster structures.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{2tops.pdf}
- \caption{Simulated electron emission spectra of an Ar 3s vacancy in 
-          argon clusters consisting of 13
-          argon atoms with two additional xenon atoms on top of two different
-          argon surfaces. ICD and ETMD spectra are shown for three
-          different relative positions of the two xenon atoms. If 
-          the xenon atoms are close to each other, an ETMD process is
-          clearly visible. In the other two cases the spectra are dominated by
-          the ICD spectrum.}
- \label{figure:2tops}
-\end{figure}
-%
-For clusters with more than one xenon atom, also ETMD(3) is possible.
-Depending on the positions of the xenon atoms relative to each other and to the Ar core, the spectra are expected to be different.
-As an example, we discuss clusters with a core of 13 argon atoms and two xenon atoms on different surfaces. 
-Their xenon content is \unit[13.3]{\%} and thus close to the experimental one of \unit[10-12]{\%} for the lowest xenon admixture.
-The cluster structures were illustrated in Figure \ref{figure:cluster_2_overview}, simulated spectra are shown in Figure \ref{figure:2tops}.
-In all three cases, both ICD and ETMD(3) are energetically allowed. The ICD
-spectra do not change qualitatively by adding the second xenon.
-%either identical or at least very similar to the ones for
-%cluster with a single  consisting of one
-%convoluted peak at approximately \unit[0.2]{eV}. 
-However, the ETMD(3) spectra
-are very sensitive to the relative position of the two xenon atoms.
-Two aspects have to be taken into account: an energy shift of the peaks due
-to different charge distances in the final state (i.e. the interatomic Xe-Xe
-distance) and the decrease of the decay width with $R^{-6}$, $R$ being the distance
-between the electron transfer unit and the xenon atom ionized in the final state.
-The larger the distance between the xenon atoms, the higher are the energies
-of the secondary electrons and the smaller are the decay widths. 
-Therefore, a
-significant contribution from ETMD(3) compared to ICD is only
-seen if the two xenon atoms reside on two adjacent
-surfaces. 
-%{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
-The three energetically separated peaks in the ETMD(3) spectrum pertain to different combinations of the Xe 5p$_j^{-1}$ vacancy states, which have a substantial fine-structure splitting (see Table \ref{tab:valence}).
-%\ref{sec:exp_results}).
-%
-%The threefold peak structure of the ETMD(3) peak does in contrast to
-%the ICD spectrum not stem from different triple structures but from the
-%four different decay channels for one triple structure.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{ar_3_6in.pdf}
- \caption{Same as Figure \protect\ref{figure:2tops}, for clusters consisting of
-          55 atoms, 6 out of which are xenon atoms. These are either grouped
-          on one side of the cluster (label `group') or evenly distributed
-          in the cluster interior (label `scattered').}
- \label{figure:ar_3_6in}
-\end{figure}
-%
-For the 55 atoms clusters, a xenon content of \unit[10--12]{\%}
-corresponds to six xenon atoms out of a total of 55 atoms. These can form a connected 
-group in one part of the cluster or can be evenly distributed,
-as shown in Figures \ref{figure:cluster_3_overview}b and \ref{figure:cluster_3_overview}c. The
-ICD and ETMD(3) spectra for these structures are shown in Figure \ref{figure:ar_3_6in}.
-
-For both cases the overall ICD spectra are very similar, and show a maximum at a kinetic energy of approximately \unit[0.3]{eV}. 
-In case of grouped xenon atoms, the ICD spectrum extends to slightly higher energies, corresponding to ArXe pairs at slightly larger spatial distances.
-A more significant difference is observed in the ETMD(3) spectra. 
-The interatomic xenon distance is shorter in clusters, in which the xenon atoms form a connected group.
-Hence, the triple structure of the ETMD(3) spectrum is seen at lower kinetic energies. 
-Additionally, the probability for an electron
-transfer from a xenon to an argon atom decreases exponentially with the
-interatomic distance. Therefore, only those xenon atoms which have direct
-argon atom neighbours have a significant contribution to the
-total decay width, and the total ETMD(3) decay width is lower for the structure with
-grouped xenon atoms than for
-the structure with evenly distributed xenon atoms (see Table \ref{table:theo_gammas}).
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{xe_3_in.pdf}
- \caption{Same as Figure \protect\ref{figure:2tops}, for argon clusters with
-          one or two xenon atoms in the core of the cluster (55 atoms total). 
-          All ICD and ETMD channels are closed, if the cluster contains only 
-          a single xenon atom. For clusters with two xenon atoms
-          in the core, the first ICD channel is open for some pairs,
-          and additionally ETMD is possible for multiple triples. Due to a
-          different distance distribution compared to the clusters with an argon
-          core (Figure \protect\ref{figure:2tops}), 
-          the ICD peak is shifted to higher kinetic energies.}
- \label{figure:xe_3_in}
-\end{figure}
-%
-For comparison with the previous assumptions of a xenon core surrounded
-by argon atoms we investigated clusters of 13 and 55 atoms with one or two
-xenon atoms in the core. Some of the corresponding
-spectra are shown in Figure \ref{figure:xe_3_in}.
-
-%For the clusters with only one xenon atom in the core and the ionization
-%energies used for the simulation of the secondary electron energies
-%all ICD channels are closed. Since the cluster contains only one xenon atom,
-%an ETMD(3) is not possible. Hence there is no signal to be expected at all.
-For a core consisting of two xenon atoms both an ICD and an ETMD(3) spectrum
-can be seen. Compared to the cluster structures involving an argon core, the ICD peak is
-shifted to higher ICD electron energies. 
-Additionally, the ICD and ETMD(3) spectra overlap.
-For ETMD(3), only three of the four different decay channels are
-energetically allowed.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{c6l5.pdf}
- \caption{Same as Figure \protect\ref{figure:2tops},
-          for a large cluster consisting
-          of a xenon core of 561 atoms surrounded by five complete layers of
-          argon atoms (Xe content: 14.5\,\%) for both an icosahedral and
-          cuboctahedral basic structure.
-          The ICD and ETMD peak overlap such that the ETMD peak
-          is unlikely to be visible.}
- \label{figure:xe_6_lay5}
-\end{figure}
-%
-In the first experiments very large argon-xenon clusters of 
-$\approx 4380$ atoms with a xenon content of \unit[19]{\%}
-were measured,\cite{Mucke_phd}
-which we in one example approximate by a cluster consisting of 561 xenon
-atoms surrounded
-by five layers of argon atoms (3871 atoms in total). In order to take the
-better stabilization of charges in larger clusters into account, the
-ionization energies of the XL clusters (see Table \ref{tab:valence})
-were used.
-The spectra are shown in 
-Figure \ref{figure:xe_6_lay5}.
-
-Compared to the small clusters with a xenon core in Figure \ref{figure:xe_3_in}
-the ICD peak is broadened and shifted to higher ICD electron energies which is
-expected due to the larger interatomic Ar-Xe distances in the large cluster and
-the better stabilization of charges, which is relevant mostly for the final state, but also the initial state.
-The ETMD(3) peak is shifted to slightly higher energies as well. This allows opening of the
-fourth decay channel, pertaining to Xe 5p$_{1/2}^{-1}$ Ar 3p$_{1/2}^{-1}$ final states.
-
-We also note that the percentage of decay via ICD is practically
-independent of the Xe content for large clusters with a Xe core, Ar shell structure.
-This can be expected, as both decay processes are most pronounced for the
-atoms in the interface region of the xenon core and the argon shell.
-The ETMD(3), depending on the electron transfer from one xenon atom to the
-initially ionized argon atom, and hence on the corresponding orbital overlap,
-is purely an interface effect that involves the argon atoms with direct xenon
-neighbours, and the two xenon layers closest to the argon shell.
-The ICD has a stronger long range character, due to which the description
-of decays with partners of at least twice the smallest channel opening
-distance is necessary for clusters. However, the bigger the clusters are,
-the more homogeneous does the interface region become for clusters of
-different sizes. This manifests itself in the distribution of relevant
-Ar-Xe pair distances (compare Figure \ref{figure:surf}, lower panel).
-As a consequence, the ICD spectra of two large clusters of different size
-hardly differ.
-
-\clearpage
-
-%\input{exp_results}
 \section{Experimental Results}
@@
 For larger Xe$_{\rm cl}$, the values are compatible with unity, within the accuracy of our experiment.
-
-%\input{theo_discussion}
-\section{Discussion
-\label{sec:discussion}}
-%
-%We have discussed the experimental spectra in Section \ref{sec:exp_results} and
-%the expected features of spectra for different cluster types in
-%Section \ref{sec:th_results}. In this section we combine the experimental and theoretical
-%results in order to determine the structure of the noble gas clusters.
-%
-%The simulated secondary electron spectra for the xenon core structures
-%(see Figure \ref{figure:xe_3_in})
-%show an ICD peak at higher energies than those structures with added xenon
-%atoms on the surface. This does not fit to the experimentally determined
-%spectra and hence we consider an argon core to be more probable for the
-%small measured clusters.
-%
-%The experimental spectra in Figure \ref{}
-%show a broadening of the secondary electron peak with increasing
-%pressure (?) and hence cluster size just as can be expected from
-%the theoretically simulated spectra in Figure \ref{figure:surf}.
-%
-%From the theoretical simulations of larger small clusters
-%having the same xenon content as experimentally observed a clearly
-%visible ETMD peak is to be expected as shown in Figure \ref{figure:ar_3_6in}.
-%However, the experimental spectra do not show a signal in the energy
-%region of \unit[1.5--6.5]{eV}. From this we conclude that the clusters
-%measured were smaller than 55 atoms containing only very few xenon atoms.
-%Additionally, if the cluster contains more than one xenon atom, they are
-%not expected to be close because of an otherwise visible ETMD peak
-%(compare Figure \ref{figure:2tops}).
-%
-%The large clusters with a large xenon content can be expected to have
-%a xenon core being surrounded by argon layers and hence, both ICD and
-%ETMD should be visible in the spectrum. Unfortunately, the ICD and ETMD
-%peaks overlap such that the two processes can not be distiguished.
-%
-We now would like to interpret our experimental findings in view of the simulated results described in Section `Theoretical Results'.
-Figure \ref{figure:eff} shows that for Ar 3s$^{-1}$ states autoionization by either ICD or ETMD is the only mode of relaxation, except for the clusters with the smallest Xe content.
-We consider this a remarkable result, because ICD of these states is only possible with a Xe atom in the second coordination shell of the decaying Ar vacancy (or shells even further apart), which significantly slows down the ICD process.
-Also decay rates for ETMD were found to be small in early studies of this effect.\cite{zobeley}
-Nevertheless, even in this situation the non-local autoionization channels foreclose radiative decay.
-
-% lowest kinetic energy is the first point of energy raster for t-E code of 52-proc-spec
-Structurally, all experimental ICD/ETMD spectra have a maximum at or near the lowest kinetic energy that could be measured (50~meV), and decrease in intensity to less than half for kinetic energies already below one eV.
-Qualitatively, this shape fits to the ICD contributions in the autoionization spectra discussed in the `Theory' section, but not to the ones from ETMD. 
-The calculated ETMD spectra have a typical three-fold structure with peaks between 3.5-5~eV, 1.5-2.5~eV and around 0 eV kinetic energy. 
-The former two features seem not to be present in the experimental spectra. 
-Due to restrictions in the detector electronics, electron pairs with very similar kinetic energy cannot be detected. 
-The highest kinetic energy for an autoionization electron that can be detected in coincidence with a photoelectron of $\sim3.5$~eV ($h\nu = 32$~eV) is around 2.5~eV.
-Very weak intensity is observed at this energy, and also at higher $e_2$ energies that can be probed at $h\nu = 34$~eV (Supporting Information).
-
-As a cross-check for our theoretical methods we have calculated the radiationless decay spectrum of Ar 3s$^{-1}$ in ArKr, which may arise {\it only} from ETMD(3),\cite{foerstel} and arrived at qualitative agreement with the experimental data.\cite{arkr}
-
-The size-dependent trend within the experimental data is in qualitative agreement to the change in the calculated spectral shape for ICD in systems of increased size (compare Figure~\ref{figure:2tops} to \ref{figure:xe_3_in} and \ref{figure:xe_6_lay5}.)
-
-We are therefore lead to the conclusion that the autoionization spectra we incur are dominated by ICD to non-nearest neighbour atoms, while the intensity of the ETMD channel is low. 
-We would like to recall the factors that lead to a propensity for decay via one or the other mechanism, which have been discussed in the `Theoretical Results'-section.
-For ETMD to occur with a measurable rate, two Xe atoms have to be present in the vincinity of the decaying Ar atom (Figure \ref{figure:2tops}).
-Should that be the case for a large part of the Ar atoms in some cluster structure, ETMD can even dominate over ICD (Figure \ref{figure:ar_3_6in} and Supporting Information).
-Model structures shown in Figures \ref{figure:2tops} and \ref{figure:ar_3_6in} have a Xe content similar to the lowest one probed in our experiment ($\sim$11\,\%).
-For a higher Xe content, ETMD will always dominate the spectra if the two species are given the chance to mix, as e.g.
-in the calculated minimum energy structures of $N=38$ ArXe clusters (Supporting Info).
-On the other hand, in core-shell systems decay via ETMD is probable only for Ar atoms in the interface layer, as this mechanism requires some wavefunction overlap between Ar and one of the Xe atoms involved.
-For the core-shell systems we have investigated, the likelihood of decay via ETMD stays below 25\,\% even for a Xe content above 50\,\% (Table \ref{table:theo_gammas}).
-
-In summary, the two structural motifs that can best be reconciled with our experimental data are
-\begin{enumerate}
-	\item small clusters containing only few Xe atoms that are spread out to distant positions on the cluster surface, and
-	\item systems with a compact Xe core and Ar outer layers.
-\end{enumerate}
-These structures are compatible with the findings of Lindblad {\it et al.}\ from core level photoelectron spectroscopy, who proposed the former structure for the smallest clusters in their study, and the latter for larger ones.\cite{lindblad}
-As even in these two cases intensity for decay via ETMD would not vanish completely, we have to leave it open though whether other mechanisms are present, which further suppress ETMD vs. ICD.
-
-While in early work on ICD it has almost been a paradigm that the decay involves two {\it neighbouring} atoms or molecules,\cite{hergenhahn_review} more recently significant intensity for non-nearest neighbour ICD has been found also in other systems.
-One example is Ne-Ar after Ne 2s ionization, where decay to Ar in the second coordination shell is clearly visible despite the fact that in this system decay involving nearest neighbours is energetically allowed.\cite{fasshauer2014}
-A further theoretical delineation of the respective factors has recently been presented by one of us.\cite{fasshauernjp}
-
-%\input{summary}
-\section{Summary}
-%
-We have presented comprehensive experimental and theoretical data for the
-autoionization of inner valence ionized states in ArXe clusters.
-Both ICD and ETMD are allowed for most cases we considered.
-Because of energetical reasons ICD requires a separation of the final state
-vacancies of \unit[7.58]{\AA} or more, which is about two times the typical
-Ar-Xe distance.
-We found that autoionization has an efficiency of 0.8 to 1.0 within the
-experimental accuracy, that is it dominates over other modes of relaxation.
-By comparing our measured spectra to calculations, we identified `long range'
-ICD as the most important decay mode and were able to determine the most
-probable structural motifs to be a xenon core surrounded by several argon layers
-for large clusters and argon clusters with with very few xenon atoms spread out
-over the surface.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The "Acknowledgement" section can be given in all manuscript
-%% classes.  This should be given within the "acknowledgement"
-%% environment, which will make the correct section or running title.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{acknowledgements}
-\begin{acknowledgement}
-%
-We thank HZB for the allocation of synchrotron radiation beamtime, and the
-Deutsche Forschungsgemeinschaft for funding via the Forschergruppe 1789.
-E. F. gratefully acknowledges the Research
-Council of Norway through a Centre of Excellence Grant (Grant No.\ 179568/V30)
-for funding.
-%
-\end{acknowledgement}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The same is true for Supporting Information, which should use the
-%% suppinfo environment.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{suppinfo}
-
-%This will usually read something like: ``Experimental procedures and
-%characterization data for all new compounds. The class will
-%automatically add a sentence pointing to the information on-line:
-
-%\end{suppinfo}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The appropriate \bibliography command should be placed here.
-%% Notice that the class file automatically sets \bibliographystyle
-%% and also names the section correctly.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliography{arxe}
-
-\end{document}

### 2019-03-22 onefolder_2/structures.tex
submitted files

--- 2016-07-04 onefolder/master.tex
@@
-	
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% This is a (brief) model paper using the achemso class
-%% The document class accepts keyval options, which should include
-%% the target journal and optionally the manuscript type.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\documentclass[journal=jpccck,manuscript=article,layout=twocolumn]{achemso}
-\documentclass[journal=jpccck,manuscript=article]{achemso}
-
-% UHe stuff
-\def\EB{E_{\rm b}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Place any additional packages needed here.  Only include packages
-%% which are essential, to avoid problems later. Do NOT use any
-%% packages which require e-TeX (for example etoolbox): the e-TeX
-%% extensions are not currently available on the ACS conversion
-%% servers.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage[english]{babel}
-\usepackage{braket}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath,amsfonts,amssymb}
-\usepackage{dsfont}
-\usepackage{booktabs}
-\usepackage{units}
-\usepackage{xcolor}
-\usepackage{multirow}
-\usepackage{tikz,pgfplots}
-\usepackage{float} %force figure position
-
-\usetikzlibrary{patterns,shadows,trees,calc}
-\usepgfplotslibrary{units}
-
-\pgfplotsset{compat=1.10}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% If issues arise when submitting your manuscript, you may want to
-%% un-comment the next line.  This provides information on the
-%% version of every file you have used.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%\listfiles
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Place any additional macros here. Please use \newcommand* where
-%% possible, and avoid layout-changing macros (which are not used
-%% when typesetting).
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newcommand*\mycommand[1]{\texttt{\emph{#1}}}
-% Define some colours
-\definecolor{diplom1}{rgb}{0.0 0.4 1.0}
-\definecolor{diplom2}{rgb}{0.0 0.0 0.6}
-\definecolor{diplom3}{RGB}{153,0,0} %unirot
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Meta-data block
-%% ---------------
-%% Each author should be given as a separate \author command.
-%%
-%% Corresponding authors should have an e-mail given after the author
-%% name as an \email command. Phone and fax numbers can be given
-%% using \phone and \fax, respectively; this information is optional.
-%%
-%% The affiliation of authors is given after the authors; each
-%% \affiliation command applies to all preceding authors not already
-%% assigned an affiliation.
-%%
-%% The affiliation takes an option argument for the short name.  This
-%% will typically be something like "University of Somewhere".
-%%
-%% The \altaffiliation macro should be used for new address, etc.
-%% On the other hand, \alsoaffiliation is used on a per author basis
-%% when authors are associated with multiple institutions.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author{Marko F\"orstel}
-\altaffiliation{Now at: Institut für Optik und Atomare Physik, Technische Universit\"at Berlin, Hardenbergstr. 36, 10623 Berlin, Germany}
-\author{Melanie Mucke}
-\altaffiliation{Now at: Department of Physics and Astronomy, Uppsala University, Box 516, 75120 Uppsala, Sweden}
-\author{Tiberiu Arion}
-\altaffiliation{Now at: Center for Free-Electron Laser Science/DESY, Notkestr. 85, D-22607 Hamburg, Germany}
-\author{Toralf Lischke}
-\affiliation[IPP]{Max-Planck-Institute for Plasma Physics, Boltzmannstr. 2, D-85748 Garching, Germany}
-\author{Markus Pernpointner}
-\affiliation[University of Heidelberg]{Theoretical Chemistry, University of Heidelberg,
-              Im Neuenheimer Feld 229, D-69120 Heidelberg, Germany}
-\author{Uwe Hergenhahn}
-\affiliation[IOM]{Leibniz Institute of Surface Modification, Permoserstr. 15, D-04318 Leipzig, Germany}
-\alsoaffiliation[IPP HGW]{Max-Planck-Institute for Plasma Physics, Wendelsteinstr. 1, D-14791 Greifswald, Germany}
-\email{uwe.hergenhahn@iom-leipzig.de}
-\author{Elke Fasshauer}
-\affiliation[UIT]{Centre for Theoretical and Computational Chemistry,
-Department of Chemistry, University of Troms\o
--- The Arctic University of Norway, N-9037 Troms\o, Norway}
-\email{elke.fasshauer@uit.no}
-%\phone{+123 (0)123 4445556}
-%\fax{+123 (0)123 4445557}
-%\alsoaffiliation[Second University]
-%{Department of Chemistry, Second University, Nearby Town}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The document title should be given as usual. Some journals require
-%% a running title from the author: this should be supplied as an
-%% optional argument to \title.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Long-range Interatomic Coulombic Decay in ArXe clusters: Experiment and Theory}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Some journals require a list of abbreviations or keywords to be
-%% supplied. These should be set up here, and will be printed after
-%% the title and author information, if needed.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\abbreviations{IR,NMR,UV}
-%\keywords{American Chemical Society, \LaTeX}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The manuscript does not need to include \maketitle, which is
-%% executed automatically.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The "tocentry" environment can be used to create an entry for the
-%% graphical table of contents. It is given here as some journals
-%% require that it is printed as part of the abstract page. It will
-%% be automatically moved as appropriate.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{tocentry}
-
-\begin{center}
- \includegraphics[height=3.5cm]{front1.pdf}
-\end{center}
-
-%Some journals require a graphical entry for the Table of Contents.
-%This should be laid out ``print ready'' so that the sizing of the
-%text is correct.
-%
-%Inside the \texttt{tocentry} environment, the font used is Helvetica
-%8\,pt, as required by \emph{Journal of the American Chemical
-%Society}.
-%
-%The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
-%permitted for  \emph{Journal of the American Chemical Society}
-%graphical table of content entries. The box will not resize if the
-%content is too big: instead it will overflow the edge of the box.
-%
-%This box and the associated title will always be printed on a
-%separate page at the end of the document.
-
-\end{tocentry}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The abstract environment will automatically gobble the contents
-%% if an abstract is not used by the target journal.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{abstract}
-
-\begin{abstract}
-We report about autoionization channels of Ar inner valence ionized states in mixed ArXe clusters and compare
-our experimental data obtained by electron-electron coincidence spectroscopy
-to our theoretical simulations for representative cluster structures.
-The combined experimental and theoretical data show that the autoionization of Ar 3s$^{-1}$ in ArXe is dominated by Interatomic Coulombic Decay (ICD) to Xe atoms in the second and higher coordination shells of the originally excited atom.
-Clusters with a range of sizes, compositions and structures were probed. 
-The Xe content in the clusters was varied between 10\,\% and 53\,\%. 
-Besides ICD, also Electron Transfer Mediated Decay (ETMD(3)) was found important in many of the calculated spectra, but is seen with less intensity in the experimental spectra. 
-From the calculations, we identify structural motifs which minimize the ETMD vs.
-the ICD rate and suggest that these are preferentially realized in our experiment, in which clusters are formed by supersonic expansion of an Ar-Xe mixture.
-Suggested cluster structures either feature a clear segregation between Ar and Xe fractions, e.g. Xe core, Ar shell systems, or contain a few Xe atoms singled out in surface sites on an Ar cluster.
-These structures differ significantly from the majority of calculated minimum energy structures for ArXe systems of 38 atoms, which might show that the latter, annealed structures are not realized in our experiment.
-We show experimentally that the relaxation of Ar inner valence states by ICD and ETMD together has an efficiency of unity, within the experimental accuracy, for all clusters except those with the lowest Xe content.
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Start the main part of the manuscript here.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{intro}
-\section{Introduction}
-%
-Electron spectroscopy can make important contributions to the 
-research on composition and structure of free nanoparticles.\cite{
-jpcc} Besides photoionization, free electrons emerging from 
-nanoparticles can also be produced by the relaxation of 
-electronically excited states. One such process, which is of 
-particular relevance in weakly bonded systems, is the 
-Interatomic or Intermolecular Coulombic Decay (ICD).\cite{
-cederbaum} In ICD, an electronic excitation decays by energy 
-transfer to one of its neighboring atoms or molecules, thus 
-releasing a free electron from the latter site. ICD is an 
-important relaxation channel e.g. for inner-valence holes in 
-atoms, and also for core level vacancies e.g. in \ce{H2O}
-, where it competes with Auger decay.\cite{slavicek}
-
-By definition, ICD is particularly sensitive to the chemical 
-environment of the atom or molecule in which the primary 
-excitation has taken place. We suggest that this property of ICD 
-decay spectra can be used to derive information on a nanoparticle 
-or a solvation system. 
-The term excitation is used here in a broader sense---in the
-systems we consider in this work, ICD occurs from an excited, singly 
-charged Ar state created by photoionization.
-In other systems, ICD was also observed from neutral excited
-states and states with more than one vacancy.
-
-We report here about studies 
-in which we produced heterogeneous clusters of the noble gases Ar 
-and Xe with different sizes, and compositions ranging from a few 
-Xe dopant atoms in an Ar matrix to clusters containing an equal 
-amount of both species. By the use of electron-electron 
-coincidence spectroscopy and of theoretical simulations on 
-prototypical systems we show how the radiationless decay spectrum 
-of Ar inner valence (3s) ionized states connects to the structure 
-of the clusters.
-
-Intermolecular Coulombic Decay initially was predicted from 
-theoretical considerations of the energy levels in singly vs.\  
-doubly ionized, and doubly vs.\ triply ionized, hydrogen bonded 
-clusters.\cite{cederbaum} First experimental work some years 
-later used Ne clusters,\cite{marburger,jahnkenedimer} but quickly 
-was followed by demonstrations of ICD in a diverse range of other 
-systems. Experimental and theoretical progress has been reviewed.
-\cite{hergenhahn_review, averbukh_review, jahnke_review} ICD 
-proceeds by an initial ionization producing an ion in an excited 
-state, followed by a transfer of energy to a neighbouring site, 
-and an electron emission process therefrom. The final state contains 
-two positive charges; one at the original site of ionization, and a second
-one at another atom or molecule.
-
-Soon after, related 
-autoionization processes were discovered that proceed via a 
-charge transfer instead of an energy transfer. 
-These were termed `Electron Transfer Mediated Decay' 
- (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
- which the originally excited site is neutralized by the decay 
-and `exchange ICD' for charge transfer contributions to the 
-normal ICD amplitude.\cite{santrarev,jahnkesat}
-We find that both energy and charge transfer induced 
-autoionization play a role in Ar-Xe, and will detail the 
-relevant processes below. The notion of ICD requires that the 
-electronic orbitals of the two sites can be distinguished, which 
-typically is the case in weakly bonded systems, held together by 
-hydrogen bonds or van-der-Waals bonds. In the case of strong
-(covalent or metallic) bonding, it is impossible to make a
-distinction between ICD and Auger decay.\cite{hergenhahn_review}
-
-Rare gas clusters are suitable prototype systems for studies of
-ICD, as they can readily be produced by supersonic 
-expansion through a cooled nozzle. 
-The size of the clusters can be changed by varying the expansion parameters.
-The formation of heterogeneous rare gas clusters by coexpansion of a gas mixture cannot {\it a priori} be taken for granted, but was experimentally shown for most combinations of two rare gases, when suitable mixing ratios and expansion parameters are used (see references throughout this article).
-
-First experiments on ICD in heterogeneous systems used Ne-Ar 
-clusters.\cite{barthnear} Those were followed by studies of 
-ICD-like inner-shell decays in aqueous solution.\cite{aziz,pokapanich,pokapanich2011}
-Pioneering work also showed the 
-potential for studies of the interface between a substrate and an 
-adsorbate by ICD.\cite{grieves} More detailed work on Ne-Ar 
-clusters was recently presented by some of the authors \cite{fasshauer2014}
-showing that an analysis of the ICD spectra
-allowed to decide between structural alternatives, for which the
-photoelectron data were indiscriminate.
-For this system, a detailed account of the
-photoelectron spectra with respect to structural features of the 
-mixed clusters is also available.\cite{lundwall}
-
-Several experimental techniques have been used for the study of mixed Ar-Xe clusters, most notably fluorescence spectroscopy, electron diffraction and photoelectron spectroscopy. 
-Early work focussed on the fluorescence of a single Xe atom 
-embedded in an Ar cluster.\cite{lengenprl}
-%Different sites of the dopant atom (on top of a surface, 
-%integrated in an Ar surface, inside the cluster) were 
-%distinguished by three separate bands in the fluorescence yield 
-%recorded as a function of excitation wavelength.\cite{goldberg} 
-Increasing the Xe concentration in the expansion lead to the formation of \ce{Xe2} and larger Xe complexes inside the clusters.\cite{lengen} 
-With increasing Xe content, the formation of Xe-core, Ar-shell systems with a sharp interface between the two species was shown in photoionization experiments.\cite{tchaplyguine,hoener}
-This finding was confirmed by electron diffraction.\cite{Danylchenko,Danylchenko07} 
-Always, the observed Xe content in the clusters is higher than the Xe content in the expanding gas mixture, as Xe can be condensed much easier than Ar.\cite{hoener,Danylchenko07}
-%A complementary study used photoelectron-photoion coincidence of
-%large Ar-Xe clusters, and found that after inner shell (Xe 4d, Ar 2p)
-%photoionization significant charge transfer between both species
-%occurs before the mass spectroscopic final state is reached.\cite{berrah}
-%
-More recently, photoelectron spectra of 
-small Ar-Xe clusters were analyzed, adding to the findings in 
-earlier work.\cite{lindblad} We will discuss this paper in 
-connection with our results below. 
-For completeness, we mention that Ar-Xe complexes can also be produced by passing clusters from a neat Ar expansion through a zone filled with Xe gas (`pick-up').\cite{pietrowski}
-Clusters produced such can structurally be quite different from those produced by coexpansion.\cite{lindbladpccp}
-
-A number of theoretical works on Ar-Xe clusters aimed at the prediction of minimum energy structures. 
-Most recently, these converged to structures which have the Xe atoms mainly in the interior.\cite{marques} 
-Xe was also found to diffuse into the interior of Ar clusters in molecular dynamics simulations after pick-up.\cite{Vach_1999} 
-The electronic energy levels of very small Ar-Xe clusters were calculated in ref \citenum{fasshauer} and the secondary electron spectra were simulated for
-model structures of one argon atom placed on a xenon surface \cite{Fasshauer13}.
-Interestingly, it was found that Ar 3s$^{-1}$ is stable 
-against autoionization in an ArXe dimer, but is destabilized by 
-adding further Xe atoms, or an Ar solvation shell, to the system, thereby allowing
-for combinations of argon and xenon atoms with larger interatomic distances. 
-Again, we will detail these results in conjunction with our 
-current work.
-
-The plan of our paper is as follows: We firstly delineate our experimental and theoretical methods. 
-Calculations were done for a number of model structures which were systematically varied, and are described in the following section.
-After that, we describe and discuss our theoretical results for the autoionization spectra of the model clusters.
-Experimental results are then shown and possible conclusions from comparing them to the calculations are given.
-Details on the experimental technique, and calculated spectra for a wider range of structures are given as Supporting Information.
-
-%\input{experimental}
-
-\section{Experimental}
-%
-\begin{table*}
-\caption{
-The expansion parameters used for cluster production. 
-Here, Xe$_{\rm in}$ is the molar fraction of Xe in the gas mixture before the expansion, $T$ is the nozzle temperature, and $p$ the stagnation pressure. 
-Experiments were performed with $d = 80~\mu$m (first two sections) and $d = 100~\mu$m (bottom section) conical nozzles of 15$^\circ$ half opening angle. 
-We basically have an Ar seeded expansion of Xe gas, as the freezing point of Ar is much lower. 
-$\langle N_{\rm Ar} \rangle$ and $\langle N_{\rm Xe} \rangle$ refer to cluster sizes for a pure Ar, or pure Xe expansion, respectively, at the given conditions, calculated from a scaling law.\protect\cite{hagena1981}
-We expect actual cluster sizes in-between these two limiting values. 
-Inaccuracies in the calculation of $\langle N\rangle$ due to fluctuations of the input parameters are less than 6\,\%. This figure does not include systematic errors of the empirical model.
-}
-\label{tab:cluster}
-
-\begin{tabular}{l c c c c r r}
-%
-\toprule
-  \multicolumn{2}{r}{size label}  &  Xe$_{\rm in}$ (\%)  &  $T$ (K)  &  $p$ (bar) & $\langle N_{\rm Ar} \rangle$ & $\langle N_{\rm Xe} \rangle$ \\
-%
-\midrule
-% Ar, from Marko 
-Ar & (1) & --- &  96.5  & 0.35  & 44  &  --- \\
-% Ar, from Marko 
-Ar & (2) & --- &  96.5  & 0.67  & 200  &  --- \\
-\midrule
-% 1103 676, 679
-ArXe & `S' & 1.2 &  174   & 0.32  & 4  &   74 \\
-% 1103 670
-ArXe & `M' & 1.2 &  174   & 0.49  & 11  &  199 \\
-% 1103 671
-ArXe & `L' & 1.2 &  174   & 0.68  & 23  &  431 \\
-\midrule
-% 1103 663
-ArXe & `S' & 3.0 &  172   & 0.28  & 3  &   57 \\
-% 1103 653
-ArXe & `M' & 3.0 &  172   & 0.51  & 12  &  233 \\
-% 1103 658
-ArXe & `L' & 3.0 &  172   & 0.68  & 24  &  458 \\
-\midrule
-% 1103 630
-ArXe & `S'  & 5.0 &  167  & 0.37  & 7  &  129 \\
-% 1103 640
-ArXe & `M' & 5.0 &  171   & 0.51  & 13  &  240 \\
-% 1103 629
-ArXe & `L'  & 5.0 &  167  & 0.68  & 28  &  537 \\
-\midrule
-% 1004 867 (32 eV)
-ArXe & `XL' & 2.5 &  154  & 2.12  & 995 & 18800\\
-\midrule
-% 0506 382, Keller offset ber?cksichtigt
-Xe &  & 100 & 183.5  & 0.68  & ---  &  615 \\     
-% 1004 868
-%868 & & 2.5 &  158   & 1.50  &  355 &  6090\\
-% 1004 886 (17 eV)
-%886 &  & 2.5 &  161   & 2.41  &  980 & 16770\\
-% 1004 858
-%858 &  & 5.0 &  149   & 2.50  & 1620 & 27700\\
-%
-\bottomrule
-\end{tabular}
-\end{table*}
-%
-%
-The apparatus used for the experiments consists of a supersonic molecular jet with a cooled nozzle, and a magnetic bottle spectrometer, which detects photoelectrons and secondary electrons produced after ionization with synchrotron radiation.\cite{arion}
-% Leave this citation in place to avoid Latex error
-A comprehensive description can be found in ref \citenum{arion}, and here we focus on details specific for the current experiment. 
-Commercialy obtained Ar and Xe gas was filled into 
-separate cylinders up to pressures suitable for producing a certain mixing ratio. The gases were then allowed to mix before the expansion. 
-Expansion parameters are given in Table \ref{tab:cluster}. 
-Similar expansion conditions are further referred by the labels `S'-`XL', as given in the Table.
-
-Prediction of the sizes of clusters from a supersonic expansion mainly rests on empirical scaling laws,\cite{hagena1981} which have been the subject of some discussion.
-Moreover, such scaling laws originally were derived only for pure gas expansions.
-A recent investigation of cluster sizes in a mixed Ar-Kr expansion yielded a revised scaling law, which essentially amounts to the use of a weighted average over the atom-specific parameters of the two gases.\cite{danylchenko2015}
-Although the analogy to our case is not complete, as phase segregation occurs in Ar-Kr to a much lesser extent,\cite{Vach_1999,lundwall_arkr} we expect scaling law cluster sizes between the values calculated for Ar and Xe.
-Recent analyses of photoionization spectra suggest that mean sizes arrived at by scaling laws are smaller than the actual size, at least for rare gas clusters in the range $\langle N\rangle < 1000$.\cite{bergersen,hergenhahnprb,foerstel_arg2_2011}
-For the expansion conditions labelled `S'-`L', we therefore expect that the scaling law estimates are a lower boundary for the actual cluster size.
-
-The expansion chamber for the supersonic jet is separated from the interaction chamber by a non-magnetic, conical skimmer with an opening of 1~mm in diameter (Beam Dynamics). 
-At few cm distance behind the skimmer, the cluster jet was crossed by synchrotron radiation from the BESSY electron storage ring at Helmholtz-Zentrum Berlin. 
-Electrons were detected by a short `magnetic bottle' time-of-flight spectrometer, that has been described earlier.\cite{mucke_review}
-Due to its large collection angle, this instrument is particularly suited for experiments that employ electron-electron coincidence detection.
-Data were recorded in two different beamtimes at the UE112-PGM-1 (small and medium sized clusters, first two sections in Table \ref{tab:cluster}) and at the TGM-4 beamline (large clusters, last section in Table \ref{tab:cluster}).
-Linearly, horizontally polarized radiation was used. 
-The storage ring was operated in single bunch conditions.
-Spectra of pure Ar clusters shown for comparison are from ref \citenum{foerstel_arg2_2011}, and a spectrum of pure Xe clusters was recorded with the set-up described in ref \citenum{hergenhahnprb}.
-
-The entrance aperture and drift tube of the magnetical bottle spectrometer can be independently biased to influence the electron flight times. 
-For the data shown here, slightly positive bias voltages were used (+1.8 V to +2.2 V) in order to have all electrons arriving at the detector within one BESSY single bunch period (800 ns). 
-The detection efficiency was determined as 0.6, with the method outlined in ref \citenum{mucke_review}.
-Data were converted from flight times to kinetic energy by measuring calibration data for atomic photolines of known binding energy.
-The systematical uncertainty of this procedure may lead to a common shift of all experimental kinetic energy data shown in this article of up to 30~meV.
-
-The high detection efficiency of the instrument is a pre-requisite for measuring two-electron emission processes, such as photoelectron emission followed by ICD or ETMD, by using electron-electron coincidence detection.
-This allows to filter the full electron spectrum for contributions arising after emission of an Ar 3s photoelectron.
-ICD/ETMD spectra presented here are based on this method, which has been explained earlier.\cite{mucke_review,Foerstel_phd}
-Technical details and full electron-electron coincidence spectra are given in the Supporting Information.
-
-%\input{theory}
-\section{Theoretical Approach}
-%
-Experimental coincidence spectra are given by the multitude of
-kinetic energies $E_{\rm sec}$ of the secondary electron
-and the intensities of the peaks. The latter is proportional to the
-probability of the decay as well as the theoretically determinable
-decay width $\Gamma=\frac{\hbar}{\tau}$,
-which is inversely proportional to the lifetime $\tau$ of the decay process.
-The manifold of the
-secondary energies and decay widths will therefore compose the electron-electron
-coincidence spectrum.
-In case of noble gas clusters
-with given geometrical structures three aspects have to be taken into account:
-different decay mechanisms, the possibility to decay with multiple
-interaction partners and different decay channels $\beta$ within
-each decay mechanism.
-At the current stage of development we need to neglect the nuclear dynamics which
-additionally might play an important role.
-
-%We are interested in describing the electron emission spectra of excited states in clusters, that where measured by the electron-electron coincidence method in our experiments. 
-%In our theoretical description, these will be composed of multiple transitions, each characterized by a kinetic energy $E_{\rm sec}$ of the secondary electrons, and the intensity of the peak.
-%The latter is proportional to the probability of the decay, represented here by the decay width $\Gamma_\beta = \hbar/\tau_\beta$, where $\tau_\beta$ is the lifetime due to the respective transition.
-%The total decay width $\Gamma$ is the sum of all partial $\Gamma_\beta$.
-%In case of noble gas clusters with a given geometrical structure, three aspects have to be taken into account:
-%different decay mechanisms, the contribution of different cluster sites to the respective decay, and the existence of different decay channels within each decay mechanism.
-%At the current stage of development we have to neglect the nuclear dynamics, which
-
-This means, for the evaluation of the decay width we are dealing with a sum over three different indices: 
-For a given structure it is most convenient to
-start with a decomposition of the system into interaction partners of
-the different relevant decay mechanisms, i.e. pairs (combination of two atoms regardless
-of their internuclear distance) for the ICD and triples (combinations of three atoms)
-for the ETMD(3).
-These atoms do not necessarily need to form bonds between each other or
-even be close, but they are characterized according to fixed internal
-coordinates. 
-Each pair and each triple leads to a decay spectrum that can be described by the energy of the secondary electron and the decay width, which is in first order of approximation independent of other atoms present in the cluster.
-In the following, this approach will be called model of pairs and triples.
-
-%Decomposing every system into pairs and triples of atoms is a very useful
-%first order approximation to both the investigation of energies and
-%decay widths of a larger system. Pairs and triples are combinations of
-%two and three atoms, respectively.
-
-In order to determine, whether a channel $\beta$ for a given geometry and decay
-mechanism is open, i.e., whether it is in accordance with energy conservation,
-knowledge of the energies of the initial and the final states, $E_{\rm in}$ and $E_{\rm fin}$, of
-the corresponding processes is necessary.
-If the channel
-is open, the excess energy is carried away by the emitted electron
-in form of its kinetic energy $E_{\rm sec}$. These energies in the model
-of pairs and triples can be approximated by
-
-\begin{align}
- E_{\rm in}        &= SIP(X_{\rm in}) \label{equation:E_in}\\
- E_{\rm fin}^\beta &= SIP(X_{D}^\beta) + SIP(X_{E}^\beta) + \frac 1d
-           \label{equation:E_fin}\\
- E_{\rm sec}^\beta &= E_{\rm in}^\beta - E_{\rm fin}^\beta \label{equation:E_sec}
-\end{align}
-where $X_{\rm in}$ denotes the initially ionized atom and
-$X_{D}$ and $X_{E}$ describe the electron donating atom and electron
-emitting atom, respectively.
-$\beta$ denotes the decay channel characterized by the quantum numbers of the ionized atoms in the pairs and triples, $SIP(X^\beta)$ the single ionization potential of vacancy $\beta$ in atom $X$ and $d$ the interatomic distance between the atoms $X_{D}$ and $X_{E}$.
-Atomic units are used.
-The initially ionized atom $X_{\rm in}$ can
-coincide with one or both of
-the final state atoms
-$X_{D}$ and $X_{E}$.
-The distribution of the vacancies over the different
-atoms determines the kind of electronic decay process at hand. Hence, in an
-Auger process all three atoms coincide, for an ICD process $X_{\rm in}$
-coincides with $X_{D}$, for an ETMD(2) process $X_D$ and $X_E$ coincide
-and for an ETMD(3) process
-all ionized states are located on different atoms.
-
-\begin{figure}[h]
- \centering
- \includegraphics[width=\columnwidth]{channel_open_ICD.pdf}
- \caption{Illustration of channel opening: Initial (Ar3s$^{-1}$)
-          and final state (Ar3p$^{-1}$Xe5p$_{3/2}^{-1}$ and
-          Ar3p$^{-1}$Xe5p$_{1/2}^{-1}$) energies
-          for ICD in ArXe pairs as a function of 
-          internuclear distance, using eq. (\ref{equation:E_fin})
-          and the experimental ionization
-          potentials given
-          in Table \ref{tab:valence}. When the final state energy is lower
-          than the initial state energy the corresponding channel
-          is open. We call the distance at which the energies are equal
-          the `channel opening distance'. If the curves do not cross, the
-          corresponding channel is closed.}
- \label{figure:channel_open_ICD}
-\end{figure}
-
-The electron emitted by autoionization has the kinetic energy $E_{\rm sec}$. 
-If the calculated value of $E_{\rm sec}$ is negative,
-the final state energy is higher than the initial state energy and the        
-process is energetically not accessible. Hence, the corresponding channel     
-is closed, as shown in Figure \ref{figure:channel_open_ICD} for the
-Ar3p$^{-1}$Xe5p$_{1/2}^{-1}$ final state. Related to
-the opening of each channel is an internuclear distance which we will call 
-\emph{channel opening distance} in the following.
-
-This {\latin ad hoc} approach allows to easily correct for energetic shifts of ionization potentials as observed in larger clusters by adding experimentally or theoretically determined energy shifts $\Delta E(X_{I}^{\beta})$ for a given vacancy $I={\rm in},D,E$ and channel $\beta$.
-This yields the working expression for the kinetic energy of the secondary electron:
-
-\begin{equation}
- E_{\rm sec}^\beta = SIP(X_{\rm in}) + \Delta E (X_{\rm in})
-               - SIP(X_{D}^\beta) - \Delta E (X_{D}^\beta)
-               - SIP(X_{E}^\beta) - \Delta E (X_{E}^\beta)
-               - \frac 1d .
-\end{equation}
-
-The total decay width $\Gamma$ is given by the sum over the decay widths
-of all decay mechanisms. In case of the ArXe clusters we only consider
-ICD and ETMD(3), because the ETMD(2) pathway is energetically not accessible:
-
-\begin{equation}
- \Gamma = \Gamma_{\rm ICD} + \Gamma_{\rm ETMD} .
-\end{equation}
-
-These are given by the sum over the decay widths of all pairs $i$ for the
-ICD and all triples $j$ for the ETMD(3), respectively, and over all channels $\beta$:
-%
-\begin{align}
- \Gamma_{\rm ICD}  &= \sum\limits_{i,\beta} N_{{\rm ICD},i}  \, \Gamma_{{\rm ICD},i,\beta},\\
- \Gamma_{\rm ETMD} &= \sum\limits_{j,\beta} N_{{\rm ETMD},j} \, \Gamma_{{\rm ETMD},j,\beta}.
-\end{align}
-Here, $N_{{\rm ICD},i}$ and $N_{{\rm ETMD},j}$ denote the number of geometrically
-equal pairs and triples in a given cluster structure. The total number of pairs
-reads
-$N_{{\rm ICD}} = N_{\rm in} \cdot N_{D/E} = N_{\rm Ar} \cdot N_{\rm Xe}
- = \sum\limits_i N_{{\rm ICD},i}$ and the number of triples is
-$N_{{\rm ETMD}} = N_{\rm in} \cdot N_{D/E} (N_{D/E} - 1) = N_{\rm Ar} \cdot N_{\rm Xe} (N_{\rm Xe} - 1)
- = \sum\limits_j N_{{\rm ETMD},j}$.
-The numbers of geometrically equivalent pairs $N_{{\rm ICD},i}$ and triples $N_{{\rm ETMD},j}$
-strongly depend on the structure of the cluster. From these relationships
-it can be seen that a higher xenon content in the cluster statistically
-favours ETMD(3) over ICD.
-
-In previous work \cite{Fasshauer13,Fasshauer_thesis} we have shown that
-the decay width for a single pair or triple for a distinct channel $\beta$
-following Wentzel \cite{Wentzel27}, Feshbach\cite{Feshbach58,Feshbach62}
-and Fano,\cite{Fano61}
-%
-\begin{equation}
- \Gamma_{\beta}(E_{\rm res}) = 2\pi \left|
-                           \braket{\Phi_{\rm in}| H_f |\chi_{\beta}}
-                           \right|^2,
-\end{equation}
-%
-can be approximated by its asymptotic behaviour
-%
-\begin{equation}
- \Gamma_{{\rm ICD},i,\beta} = (2J_{\rm in}+1)\, \frac{3c^4}{8\pi}\,
-                        \sum\limits_{M_{in}'}
-                        \left| \left(
-                        \begin{array}{ccc}
-                        J_A'  & 1        & J_A\\
-                        -M_A' & M_A'-M_A & M_A
-                        \end{array}\right) \right|^2
-                        \frac{\sigma^{(X_E)}(\omega_{vp,\beta})}
-                        {R_i^6 \, \omega_{vp,\beta}^4 \tau_{in,\beta}},
-\end{equation}
-%
-where $J_A$, $J_A'$ and $M_A$, $M_A'$ denote the total angular momentum of the
-initially ionized atom (which is the same as the electron donor atom) in the
-initial and final state, respectively,
-and
-%
-\begin{align}
- \Gamma_{{\rm ETMD},j,\beta} =& \frac{c}{\pi} \sum\limits_{m,M_{in,D'}}
-                        \frac{\Theta_{m,k}(\alpha_j) \sigma^{(X_E)}(\omega_{vp,\beta})
-                              \left| <\tilde{D}_{m,j,\beta}(M_{in,D'})>\right|^2}
-                         {R_j^6 \omega_{vp,\beta}}\\
-               =& \frac{c}{\pi R_j^6}
-               \sum\limits_{M_{in,D'}}
-               \left( \left| <\tilde{D}_{x,j,\beta} (M_{in,D'}) > \right|^2
-                 (2+ \sin^2\alpha_j)
-               + \left| <\tilde{D}_{z,j,\beta} (M_{in,D'}) > \right|^2
-                 (1+\cos^2\alpha_j) \right) \nonumber \\
-           & \times\, \frac{c\sigma^{(X_E)}(\omega_{vp,\beta})}{\omega_{vp,\beta}}
-\end{align}
-%
-depending on 
-experimental properties
-of atoms, like the ionization cross sections
-$\sigma^{(X_E)}(\omega_{vp,\beta})$, radiative lifetimes of the initially
-ionized state $\tau_{in,\beta}$ and the excess energy transferred to the
-emitting atom (the energy of the virtual photon) $\omega_{vp,\beta}$
-and calculated dipole transition moments $\tilde{D}_{m,j,\beta}$, only.
-Here, $\Theta_{m}(\alpha_j)$ is a function depending on the angle $\alpha_j$
-of the triple and the direction of the dipole
-transition moment $m$
-(compare ref \citenum{Fasshauer13}).
-
-In this work we evaluate the secondary energies and decay widths with
-the programme HARDRoC\cite{HARDRoC,fasshauer2014} using the
-experimental ionization energies of Table \ref{tab:valence}
-and data from the literature given in Tables II and III.
-This choice is identical to the one made in ref \citenum{Fasshauer13}.
-
-%\input{structures}
 \section{Cluster Structures}
@@
 Furthermore, for comparison with the largest measured ArXe clusters, we constructed also larger core-shell structures (Table \ref{table:theo_gammas}, \#4--5).
-
-%\input{theo_results}
-\section{Theoretical Results
-\label{sec:th_results}}
-%
-%
-\begin{table}[H]
-\small
-\centering
-\caption{Structural and calculated properties of some model clusters.
-The cluster structures are characterized by the number of Ar and Xe atoms,
-and are arranged in three groups according to gross structural properties. 
-The first group contains Xe core-Ar shell systems of various
-size and relative Xe content.
-In the second group, model structures for small clusters are displayed,
-in which 1-2 Xe atoms are added at systematically varied locations
-to an icosahedric Ar clusters consisting of one or two full shells,
-or in which 1-6 Ar atoms of such cluster were replaced by Xe atoms.
-The last group contains data for calculated minimal energy structures
-of mixed ArXe clusters.\protect\cite{marques}
-The cluster structures are classified into core-shell structures (cs),
-structures with segregated xenon atoms (in) and completely mixed
-structures.
-The columns `ICD' and `ETMD' are the respective partial decay widths
-in \unit[$10^{-4}$]{eV}, and `\% ICD' gives the percentage of ICD in
-the total decay width.
-See text for details.
-\label{table:theo_gammas}
-}
-\begin{tabular}{rrrrcccccrrr}
-\toprule
-\# & \# Xe & \# Ar & Xe$_{\rm cl}$\% & str. cl. & pos. & rel. pos. & ICD   &  ETMD & \% ICD & Fig.\\ %$\Gamma_{\rm ICD,ETMD}$\\
-\midrule
- 1 &     1 &    12 &  7.7  & cs    &         &          & 0.000 & 0.000 &  -- &\\ %    0.0            \\     ArXe\_2\_1atom      
- 2 &     1 &    54 &  1.8  & cs    &         &          & 0.000 & 0.000 &  -- & \ref{figure:xe_3_in}\\ %    0.0            \\     ArXe\_3\_1atom      
- 3 &     2 &    53 &  3.6  & cs    &         &          & 0.033 & 0.167 &  16.7& \ref{figure:xe_3_in}\\ %2.006$\cdot 10^{-5}$ \\ ArXe\_3\_2atom      
- 4 &  1415 &   642 & 68.8  & cs    &         &          & 7.039 & 2.573 &  73.2& supp.\\ %9.612$\cdot 10^{-4}$ \\ ArXe\_8\_1layer     
- 5 &   561 &  3310 & 14.5  & cs    &         &          &       &       &  85  & \ref{figure:xe_6_lay5}\\ % c6l5
-
-\midrule
- 6 &     1 &    13 &  7.1  & cs    & surface &          & 0.792 & 0.000 & 100.0& \ref{figure:surf}\\ %7.922$\cdot 10^{-5}$ \\ XeAr\_2\_surface    
- 7 &     1 &    13 &  7.1  & cs    & edge    &          & 0.013 & 0.000 & 100.0&\\ %1.320$\cdot 10^{-6}$ \\ XeAr\_2\_edge       
- 8 &     1 &    13 &  7.1  & cs    & vertex  &          & 0.050 & 0.000 & 100.0&\\ %5.013$\cdot 10^{-6}$ \\ XeAr\_2\_vertex     
- 9 &     2 &    13 & 13.3  & cs    &         & closest  & 0.101 & 0.151 &  40.1& \ref{figure:2tops}\\ %2.523$\cdot 10^{-5}$ \\ XeAr\_2\_2top       
-10 &     2 &    13 & 13.3  & cs    &         & middle   & 0.159 & 0.008 &  95.4& \ref{figure:2tops}\\ %1.665$\cdot 10^{-5}$ \\ XeAr\_2\_2midtop    
-11 &     2 &    13 & 13.3  & cs    &         & furthest & 0.159 & 0.002 &  98.9& \ref{figure:2tops}\\ %1.605$\cdot 10^{-5}$ \\ XeAr\_2\_2endtop    
-12 &     1 &    55 &  1.8  & cs    & surface &          & 0.064 & 0.000 & 100.0& \ref{figure:surf}\\ %6.371$\cdot 10^{-6}$ \\ XeAr\_3\_surface    
-13 &     1 &    55 &  1.8  & cs    & edge    &          & 0.048 & 0.000 & 100.0&\\ %4.791$\cdot 10^{-6}$ \\ XeAr\_3\_edge       
-14 &     1 &    55 &  1.8  & cs    & vertex  &          & 0.027 & 0.000 & 100.0&\\ %2.701$\cdot 10^{-6}$ \\ XeAr\_3\_vertex     
-15 &     1 &    54 &  1.8  & in    & edge    &          & 0.077 & 0.000 & 100.0&\\ %7.708$\cdot 10^{-6}$ \\ XeAr\_3\_edge\_in   
-16 &     1 &    54 &  1.8  & in    & vertex  &          & 0.053 & 0.000 & 100.0&\\ %5.258$\cdot 10^{-6}$ \\ XeAr\_3\_vertex\_in 
-17 &     2 &    53 &  3.6  & in    &         &          & 0.117 & 0.055 &  68.1&\\ %1.711$\cdot 10^{-5}$ \\ XeAr\_3\_2in        
-18 &     6 &    49 & 10.9  & in    &         &          & 0.375 & 0.405 &  48.1& \ref{figure:ar_3_6in}\\ %7.796$\cdot 10^{-5}$ \\ XeAr\_3\_6in        
-19 &     6 &    49 & 10.9  & mixed &         &          & 0.292 & 0.674 &  30.3& \ref{figure:ar_3_6in}\\ %9.660$\cdot 10^{-5}$ \\ XeAr\_3\_6\_scat    
-                                                                                                 \midrule
-20 &     2 &    36 &  5.3  & cs    &         &          & 0.117 & 0.151 &  43.6& supp.\\                        % Ar$_{36}$Xe$_{2}$   
-21 &     4 &    34 & 10.5  & mixed &         &          & 0.248 & 0.587 &  29.7& supp.\\                        % Ar$_{34}$Xe$_{4}$   
-22 &     5 &    33 & 13.2  & mixed &         &          & 0.335 & 0.844 &  28.4& supp.\\                        % Ar$_{33}$Xe$_{5}$   
-23 &    13 &    25 & 34.2  & mixed &         &          & 0.828 & 5.414 &  13.3& supp.\\                        % Ar$_{25}$Xe$_{13}$  
-24 &    24 &    14 & 63.2  & mixed &         &          & 1.488 &16.718 &   8.2& supp.\\                        % Ar$_{14}$Xe$_{24}$  
-25 &    25 &    13 & 65.8  & in    &         &          & 1.432 & 4.995 &  22.3& supp.\\                        % Ar$_{13}$Xe$_{25}$  
-26 &    35 &     3 & 92.1  & in    &         &          & 2.017 & 7.051 &  22.2& supp.\\                        % Ar$_{3}$Xe$_{35}$   
-\bottomrule
-\end{tabular}
-\end{table}
-%
-The geometrical properties as well as the total ICD and ETMD decay widths
-of the investigated structures are shown in Table \ref{table:theo_gammas}.
-It is important to remember that the first ICD channel opens at a
-channel opening distance of \unit[7.58]{\AA}. In the smallest
-clusters with only one argon layer around each
-xenon atom, the Ar-Xe pair distances are below that value, therefore 
-no ICD can take place. Also, by definition, two Xe atoms are
-required for ETMD(3), hence it cannot occur in clusters with only one xenon atom.
-%Because secondary electrons are observed in the experimental spectra
-%we exclude all structures without any signal from our further
-%discussions.
-%
-\begin{figure}[H]
- \centering
- \includegraphics[width=8.0cm]{surf.pdf}\\
- \includegraphics[width=8.0cm]{R_comp.pdf}
- \caption{
- %
- Top panel: Simulated electron emission spectra of an Ar 3s vacancy in 
-          argon clusters
-          consisting of 13 and 55 atoms, with an additional xenon atom residing
-          on top of one of the argon surfaces.
-          Bottom panel: Distribution of Ar-Xe distances $d$ in the studied ArXe
-          clusters. The ICD channels to final states involving Xe 5p$_{3/2}^{-1}$ and 
-          5p$_{1/2}^{-1}$ vacancies open at \unit[7.58]{\AA} and
-          \unit[36.00]{\AA}, resp.; the former distance is marked by a vertical dotted line. 
-          Only pairs at longer interatomic
-          distances contribute to the electron emission spectra.
-          Larger Ar-Xe distances, as found in the larger cluster,
-          correspond to features at a higher kinetic energy of
-          the ICD electron (top panel).}
- \label{figure:surf}
-\end{figure}
-
-%In the investigated structures several different aspects have to be
-%taken into account which we will discuss separately if possible
-%on selected structures.
-
-We will now discuss features of several structures, using selected examples.
-First we consider clusters having an argon core of 13 and 55 atoms plus a single xenon
-atom on one of the surfaces (see Figure \ref{figure:cluster_3_overview}a
-for the structure of clusters with the 55 atoms core).
-Secondary electron spectra simulated for these systems are shown in Figure \ref{figure:surf}, top panel.
-%two different argon core sizes one consisting
-%of 13 and one consisting of 55 atoms with one xenon atom on one of
-%the surfaces (see Figure \ref{figure:cluster_3_overview} Panel a)
-%for the 55 atom core). The simulated secondary electron spectra are
-%shown in Figure \ref{figure:surf} Panel 1.
-
-Because the structures contain only one xenon atom, ETMD(3) is not possible, only ICD is expected. 
-%Both spectra show several smaller peaks which
-%are convoluted into one single peak with a maximum at
-%approximately \unit[0.2]{eV}. 
-%In comparison to the 13 argon atoms core
-%spectrum t
-The spectrum pertaining to the clusters with larger (55 atoms) Ar core shows
-signals at higher energies of the secondary electron. These features
-can be explained by investigating the Ar-Xe distance distributions
-in the clusters, shown
-in the bottom panel of Figure \ref{figure:surf}. 
-Every different value of the atom pair distance
-results in a different energy of the secondary electron and only pairs
-with a distance of larger than the channel opening distance
-(dashed gray line) will contribute
-to the spectrum. 
-In our model, there is a one-to-one correspondence between interatomic distance $d$ and kinetic energy of the ICD electron.
-The larger the interatomic distance, the higher is the
-kinetic energy of the secondary electron for a given channel.
-%Since the cluster with an Ar core of 55 atoms is larger, and therefore
-%contains Ar-Xe pairs with larger distances, its spectrum 
-Therefore, the spectrum of the cluster with a 55 atoms core extends to higher energies.
-%energies as well.
-This relation between ICD energy and cluster size holds true for all cluster structures.
-%This explains why the ICD spectrum for larger clusters extends to higher energies, and holds for all cluster structures.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{2tops.pdf}
- \caption{Simulated electron emission spectra of an Ar 3s vacancy in 
-          argon clusters consisting of 13
-          argon atoms with two additional xenon atoms on top of two different
-          argon surfaces. ICD and ETMD spectra are shown for three
-          different relative positions of the two xenon atoms. If 
-          the xenon atoms are close to each other, an ETMD process is
-          clearly visible. In the other two cases the spectra are dominated by
-          the ICD spectrum.}
- \label{figure:2tops}
-\end{figure}
-%
-For clusters with more than one xenon atom, also ETMD(3) is possible.
-Depending on the positions of the xenon atoms relative to each other and to the Ar core, the spectra are expected to be different.
-As an example, we discuss clusters with a core of 13 argon atoms and two xenon atoms on different surfaces. 
-Their xenon content is \unit[13.3]{\%} and thus close to the experimental one of \unit[10-12]{\%} for the lowest xenon admixture.
-The cluster structures were illustrated in Figure \ref{figure:cluster_2_overview}, simulated spectra are shown in Figure \ref{figure:2tops}.
-In all three cases, both ICD and ETMD(3) are energetically allowed. The ICD
-spectra do not change qualitatively by adding the second xenon.
-%either identical or at least very similar to the ones for
-%cluster with a single  consisting of one
-%convoluted peak at approximately \unit[0.2]{eV}. 
-However, the ETMD(3) spectra
-are very sensitive to the relative position of the two xenon atoms.
-Two aspects have to be taken into account: an energy shift of the peaks due
-to different charge distances in the final state (i.e. the interatomic Xe-Xe
-distance) and the decrease of the decay width with $R^{-6}$, $R$ being the distance
-between the electron transfer unit and the xenon atom ionized in the final state.
-The larger the distance between the xenon atoms, the higher are the energies
-of the secondary electrons and the smaller are the decay widths. 
-Therefore, a
-significant contribution from ETMD(3) compared to ICD is only
-seen if the two xenon atoms reside on two adjacent
-surfaces. 
-%{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
-The three energetically separated peaks in the ETMD(3) spectrum pertain to different combinations of the Xe 5p$_j^{-1}$ vacancy states, which have a substantial fine-structure splitting (see Table \ref{tab:valence}).
-%\ref{sec:exp_results}).
-%
-%The threefold peak structure of the ETMD(3) peak does in contrast to
-%the ICD spectrum not stem from different triple structures but from the
-%four different decay channels for one triple structure.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{ar_3_6in.pdf}
- \caption{Same as Figure \protect\ref{figure:2tops}, for clusters consisting of
-          55 atoms, 6 out of which are xenon atoms. These are either grouped
-          on one side of the cluster (label `group') or evenly distributed
-          in the cluster interior (label `scattered').}
- \label{figure:ar_3_6in}
-\end{figure}
-%
-For the 55 atoms clusters, a xenon content of \unit[10--12]{\%}
-corresponds to six xenon atoms out of a total of 55 atoms. These can form a connected 
-group in one part of the cluster or can be evenly distributed,
-as shown in Figures \ref{figure:cluster_3_overview}b and \ref{figure:cluster_3_overview}c. The
-ICD and ETMD(3) spectra for these structures are shown in Figure \ref{figure:ar_3_6in}.
-
-For both cases the overall ICD spectra are very similar, and show a maximum at a kinetic energy of approximately \unit[0.3]{eV}. 
-In case of grouped xenon atoms, the ICD spectrum extends to slightly higher energies, corresponding to ArXe pairs at slightly larger spatial distances.
-A more significant difference is observed in the ETMD(3) spectra. 
-The interatomic xenon distance is shorter in clusters, in which the xenon atoms form a connected group.
-Hence, the triple structure of the ETMD(3) spectrum is seen at lower kinetic energies. 
-Additionally, the probability for an electron
-transfer from a xenon to an argon atom decreases exponentially with the
-interatomic distance. Therefore, only those xenon atoms which have direct
-argon atom neighbours have a significant contribution to the
-total decay width, and the total ETMD(3) decay width is lower for the structure with
-grouped xenon atoms than for
-the structure with evenly distributed xenon atoms (see Table \ref{table:theo_gammas}).
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{xe_3_in.pdf}
- \caption{Same as Figure \protect\ref{figure:2tops}, for argon clusters with
-          one or two xenon atoms in the core of the cluster (55 atoms total). 
-          All ICD and ETMD channels are closed, if the cluster contains only 
-          a single xenon atom. For clusters with two xenon atoms
-          in the core, the first ICD channel is open for some pairs,
-          and additionally ETMD is possible for multiple triples. Due to a
-          different distance distribution compared to the clusters with an argon
-          core (Figure \protect\ref{figure:2tops}), 
-          the ICD peak is shifted to higher kinetic energies.}
- \label{figure:xe_3_in}
-\end{figure}
-%
-For comparison with the previous assumptions of a xenon core surrounded
-by argon atoms we investigated clusters of 13 and 55 atoms with one or two
-xenon atoms in the core. Some of the corresponding
-spectra are shown in Figure \ref{figure:xe_3_in}.
-
-%For the clusters with only one xenon atom in the core and the ionization
-%energies used for the simulation of the secondary electron energies
-%all ICD channels are closed. Since the cluster contains only one xenon atom,
-%an ETMD(3) is not possible. Hence there is no signal to be expected at all.
-For a core consisting of two xenon atoms both an ICD and an ETMD(3) spectrum
-can be seen. Compared to the cluster structures involving an argon core, the ICD peak is
-shifted to higher ICD electron energies. 
-Additionally, the ICD and ETMD(3) spectra overlap.
-For ETMD(3), only three of the four different decay channels are
-energetically allowed.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{c6l5.pdf}
- \caption{Same as Figure \protect\ref{figure:2tops},
-          for a large cluster consisting
-          of a xenon core of 561 atoms surrounded by five complete layers of
-          argon atoms (Xe content: 14.5\,\%) for both an icosahedral and
-          cuboctahedral basic structure.
-          The ICD and ETMD peak overlap such that the ETMD peak
-          is unlikely to be visible.}
- \label{figure:xe_6_lay5}
-\end{figure}
-%
-In the first experiments very large argon-xenon clusters of 
-$\approx 4380$ atoms with a xenon content of \unit[19]{\%}
-were measured,\cite{Mucke_phd}
-which we in one example approximate by a cluster consisting of 561 xenon
-atoms surrounded
-by five layers of argon atoms (3871 atoms in total). In order to take the
-better stabilization of charges in larger clusters into account, the
-ionization energies of the XL clusters (see Table \ref{tab:valence})
-were used.
-The spectra are shown in 
-Figure \ref{figure:xe_6_lay5}.
-
-Compared to the small clusters with a xenon core in Figure \ref{figure:xe_3_in}
-the ICD peak is broadened and shifted to higher ICD electron energies which is
-expected due to the larger interatomic Ar-Xe distances in the large cluster and
-the better stabilization of charges, which is relevant mostly for the final state, but also the initial state.
-The ETMD(3) peak is shifted to slightly higher energies as well. This allows opening of the
-fourth decay channel, pertaining to Xe 5p$_{1/2}^{-1}$ Ar 3p$_{1/2}^{-1}$ final states.
-
-We also note that the percentage of decay via ICD is practically
-independent of the Xe content for large clusters with a Xe core, Ar shell structure.
-This can be expected, as both decay processes are most pronounced for the
-atoms in the interface region of the xenon core and the argon shell.
-The ETMD(3), depending on the electron transfer from one xenon atom to the
-initially ionized argon atom, and hence on the corresponding orbital overlap,
-is purely an interface effect that involves the argon atoms with direct xenon
-neighbours, and the two xenon layers closest to the argon shell.
-The ICD has a stronger long range character, due to which the description
-of decays with partners of at least twice the smallest channel opening
-distance is necessary for clusters. However, the bigger the clusters are,
-the more homogeneous does the interface region become for clusters of
-different sizes. This manifests itself in the distribution of relevant
-Ar-Xe pair distances (compare Figure \ref{figure:surf}, lower panel).
-As a consequence, the ICD spectra of two large clusters of different size
-hardly differ.
-
-\clearpage
-
-%\input{exp_results}
-\section{Experimental Results}
-\label{sec:exp_results}
-%
-%
-\begin{table}
-\caption{Properties of the outer valence spectra of mixed ArXe clusters. 
-Spectra of pure Ar and Xe clusters are included for reference. 
-All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV). 
-Binding energies $\EB$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit. 
-The average Xe content of the cluster ensemble, Xe$_{\rm cl}$, was determined from the areas of the respective photolines, corrected by their atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}.
-Uncertainties are estimated as $\pm$3\,\% for the Xe content and 0.05~eV for the binding energies. 
-The row labelled `(th.)' gives the binding energies used in the simulations of this paper, and the last row their atomic counterparts. 
-Values for Ar 3p in the last row refer to the fine structure states.
-\label{tab:valence}}
-\begin{tabular}{ l c c c c c c c c}
-%
-\toprule
- \multicolumn{2}{r}{size} &  Xe$_{\rm in}$& $\EB$ (eV)& $w$ (eV)& \multicolumn{2}{c}{$\EB$ (eV)}  & $w$ (eV) &  Xe$_{\rm cl}$ \\
-%
- \multicolumn{2}{r}{(label)}&  (\%) & Ar 3p & Ar 3p & Xe 5p$_{1/2}$ &  Xe 5p$_{3/2}$ & Xe 5p$_{3/2}$  &  (\%) \\
-\midrule
-% Ar, from Marko
- Ar & (1) &&  15.3  &  1.1 & & & &  \\
-% Ar, from Marko 
- Ar & (2) &&  15.1  &  1.3 & & & &  \\
-%
-%  columns in the following: energies c.g. 51-plt-oval, widths Marko Diss., Xe content Marko Diss
-% 1103 676, 679
- ArXe & S &1.2 & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
-% 1103 670
- ArXe & M &1.2 & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
-% 1103 671
- ArXe & L &1.2 & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
-% 1103 663
- ArXe & S &3.0 & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
-% 1103 640
- ArXe & M &5.0 & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
-% 0506 
- Xe &  & & & & 12.76 & 11.19 & 1.18 & 100\\
-%
-\midrule
-%
-%  1004  886  (UHe, c.g. + roi values)
- ArXe & XL &2.5 & 15.15 & 1.3 & 12.59 & 11.01 & 1.24 & 19\\
-%
-\midrule
-% Date: Wed, 20 Jan 2016 11:27:39, From: Elke Fa?hauer <elke.fasshauer@uit.no>
- Ar, Xe & (th.) && 15.3 && 13.0 & 11.5 &&\\
-%
- \multicolumn{2}{l}{(atomic)\cite{velchev,sansonetti}} && 15.76|15.94 && 13.43 & 12.13 &&\\
-%
-\bottomrule
-\end{tabular}
-\end{table}
-
-\subsection{Outer valence spectra}
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_oval_1.pdf}
- \caption{
-Outer valence photoelectron spectra of mixed Ar-Xe clusters, in comparison to the pure species. 
-(a) shows the outer valence region of homogeneous Ar and Xe clusters, respectively (see text for details). 
-The two lower panels show spectra of the mixed species with different mean size. 
-Sharp lines marked `m' (for `monomer') result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states. 
-Labels in (b) and (c) give the Xe content in the expanding gas mixture (Xe$_{\rm in}$), which is lower than the Xe content observed in the heterogeneous clusters (Xe$_{\rm cl}$). 
-The photon energy was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
-%{\color{red}{Die Stabilisierung der Xe-bulk Atome ist in den gemischten Cluster
-% höher als in den gemischten Clustern. Das ist ungewöhnlich. Habt ihr hier
-% verschiedene CLustergrößen?}}
-}
- \label{figure:oval1}
-\end{figure}
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_oval_2.pdf}
- \caption{
-Outer valence photoelectron spectra of mixed Ar-Xe clusters from gas mixtures with different Xe concentration. 
-For better visibility, a scaling factor is applied to the Xe part of the spectrum in panel (a).
-See Figure \ref{figure:oval1} and text for details.
-}
- \label{figure:oval2}
-\end{figure}
-
-Figure \ref{figure:oval1} shows the outer valence spectra of small and large ArXe clusters, compared to clusters of the pure gases. 
-Qualitatively similar spectra have been published without detailed discussion in ref \citenum{lindblad}.
-Differences are seen in particular for the Ar component. 
-In pure Ar clusters, outer valence photoionization leads to a broad band, caused both by spin-orbit coupling and crystal field splitting. 
-The relative importance of these two mechanisms remains under debate.\cite{hergenhahnprb,rolles,foerstel_arg1_2010} 
-For larger clusters (e.g.
-$\langle N\rangle = 190$, black trace), the maximum at low binding energies becomes more pronounced, and is identified with emission from the cluster interior.\cite{hergenhahnprb,rolles}
-At the particular photon energy selected here, atop of this band a sharp feature is also visible (in Figure \ref{figure:oval1} at a kinetic energy of about 1.8 eV).
-For larger clusters (above $\langle N\rangle \approx 100$), over a range of photon energies of about 3 eV, its appararent binding energy changes in a way which is reminiscent to photoemission of crystalline bulk matter (`dispersion').\cite{foerstel_arg1_2010,foerstel_arg2_2011}
-
-Ar 3p spectra of the smaller mixed clusters (Figure \ref{figure:oval1}c, Figure \ref{figure:oval2}) show neither of these traits.
-Rather, the Ar band is symmetric, less wide than in the pure clusters and at a higher binding energy.
-Even for very large clusters (Figure \ref{figure:oval1}b) the asymmetry of the 3p band and the `dispersing feature' do not appear.
-We characterize the spectral shape by giving a single value for the Ar 3p binding energy, and the FWHM of the feature.
-Values for different expansion parameters, and for both Ar and Xe valence lines, are collected in Table\ \ref{tab:valence}.
-
-We find experimentally that clusters we have produced have a Xe content Xe$_{\rm cl}$ between 10\,\% and 50\,\%.
-A slight decrease of the binding energy with cluster size is seen for all outer valence lines, and is attributed to a larger final state polarization energy in larger clusters.
-
-For further interpretation of the shape of the Ar peaks we refer to photoemission spectra of condensed Ar monolayers, measured in several settings.\cite{jacobi,jacobi2}
-Spectra were reported for physisorption of Ar on two different metal single crystal substrates, and for Ar atop of a Xe spacer layer adsorbed on the metal.
-While the binding energy depends on the substrate, the spectral shape is very similar in all cases. 
-Most spectra were recorded for emission along the surface normal, and show a double peak split by about 0.5 eV, leading to a structure with $w$ about 1 eV.
-Although the splitting is larger than the gas phase fine structure split of 0.18 eV, the pertaining states have been assigned to Ar 3p$_{1/2}$ and 3p$_{3/2}$.
-A crystal field splitting of the 3p$_{3/2}$ state has been assumed to be also present, but with a smaller value of 0.1-0.2 eV, approx.\cite{jacobi2} 
-The spectrum clearly changes when going to an emission angle of 40$^\circ$ with respect to the surface normal (Figure 2 in ref \citenum{jacobi2}).
-The higher binding energy peak significantly loses in intensity, and the spectrum is now dominated by a single peak comprising both crystal field split substates of Ar 3p$_{3/2}$, with a FWHM ($w$) of only 0.4 eV.
-As our measured spectrum is comprised of contributions recorded under all emission angles with respect to the cluster surface, grazing emission will be the rule.
-We therefore believe that the arguments given above make it plausible that only a single peak is observed in all our spectra.
-
-Emission from the Xe 5p state shows a much larger fine structure splitting then from the Ar 3p state; it dominates the spectrum even in clusters (where other broadening mechanisms are also present).
-The shift of the cluster bands with respect to the monomer lines in the largest mixed clusters we have probed (Figure \ref{figure:oval1}b) are similar to the ones in the pure Xe spectrum, the scaling law size of which is at somewhat more than five filled shells.
-This indicates an approximate upper limit for the size of the Xe core in our mixed clusters, as their binding energy shift might be somewhat higher than the one in pure clusters, due to polarization of covering Ar layers.
-Xe cluster features in the spectra of mixed clusters appear less asymmetric than the pure Xe spectrum, and also less asymmetric as some the ArXe spectra shown in ref \citenum{lindblad}.
-This might be caused by the difference in photon energy ($h\nu = 90$ eV in ref \citenum{lindblad} and for the pure Xe spectrum, $h\nu = 32$ eV for the mixed ArXe spectra in this work).
-% For the mixed clusters, the Xe band broadens and shifts towards lower binding energy for larger size clusters.
-%For pure Xe clusters, an asymmetry observed in the Xe 5p$_{3/2}$ part has no counterpart in the respective spectra from the mixed clusters.
-%This might be caused by the difference in photon energy, as can be seen from a comparison to literature spectra (ArXe at $h\nu = 90$ eV in ref \citenum{lindblad}, Xe at $h\nu = 20$ eV in ref \citenum{rolles}).
-%For the largest clusters, the nominal size yielded from the jet parameters applied to a pure Xe expansion would correspond to clusters in which bulk atoms far outweigh those on the surface.
-%At least for the 5p$_{1/2}$ photoelectron line, this would be seen as a clear asymmetry towards the low binding energy side, which is not observed in our spectra.
-
-In Figure \ref{figure:oval2}, we compare the outer valence spectra of clusters with similar expansion conditions, but different composition of the gas mixture.
-A Xe-rich mixture obviously leads to clusters with more intense Xe photolines, but besides that the main change consists in a narrowing of the Ar band.
-A comparison with the Ar monomer features (clipped in the Figure) also shows an increased degree of condensation for the Ar gas in the expansion.
-
-For the smallest clusters we have produced, a possible model is provided by calculated minimum energy structures of Ar$_N$Xe$_{38-N}$ (Figure 7 in ref \citenum{marques}).
-We there see that for a Xe content of less than 60\,\%, core-shell systems are {\it not} formed, and although the Xe atoms tend to connect, the degree of Ar-Xe mixing is large.
-While for low Xe content (approx. 10\,\%), some Ar atoms have only Ar nearest neighbours, for larger Xe content all Ar atoms seem to see both Ar and Xe nearest neighbours.
-We believe this leads to the Ar 3p narrowing pointed out above.
-For Figure \ref{figure:oval2}, possibly, some clusters of our ensemble already are in the core-shell regime, which would lead to an even lower 3p width.
-
-For the largest clusters we have produced (Figure \ref{figure:oval1}b), the low binding energy of the Xe lines and the broadening of the Ar feature without appearance of the `bulk Ar'-maximum, supports formation of a Xe core covered by at least two layers of Ar.
-If the scaling law size for a pure Ar expansion is taken as the lower limit for the cluster size, from the observed Xe content we arrive at clusters composed of a Xe core with four layers, covered by three layers of Ar (see Supporting Information).
-
-Finally, comparing Figure \ref{figure:oval2} to Figure \ref{figure:oval1} reveals that much larger changes in the valence emission spectra occur by changes in size than by changes of the (relative) Xe content.
-This finding is supported by the spectra shown in ref \citenum{lindblad}.
-%
-%
-\subsection{Inner valence spectra}
-%
-We now focus on the Ar inner valence (3s) vacancy states. 
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.8cm]{figure_ival.pdf}
- \caption{
-Photon excited electron spectra of mixed Ar-Xe clusters in the inner valence region.
-Symbols show the Ar 3s photoline from clusters (`cl') and uncondensed Ar monomers (`m'), atop of a background resulting from inelastic intracluster scattering of outer valence photoelectrons (`excitonic satellites').\protect\cite{hergenhahn2002}
-The photon energy was $h\nu = 32$ eV.
-Panel (a) shows all electrons accumulated.
-For the same conditions, in panel (b) we only show electrons that were detected in coincidence with a secondary electron of lower kinetic energy.
-The black solid trace in (a), and red solid trace in (b) result from a least squares fit to the cluster part of the spectrum. 
-The red solid trace in (a) is the fit shown in (b), divided by the detection efficiency of the spectrometer of 0.6.
-Panels (c) and (d) show the same type of data for smaller clusters with a lower Xe content.
-See text for details.
-\label{figure:ival}
-}
-\end{figure}
-
-Figure\ \ref{figure:ival} shows the Ar part of the inner valence spectrum for representative ArXe clusters. 
-The total photoelectron signal looks similar to literature spectra for pure Ar clusters.\cite{feifel,zhang} 
-A low energy tail seen for the Ar 3s monomer line results from the transmission properties of the electron spectrometer, together with the strongly positive angular distribution parameter of this line.\cite{zhang,kruit}
-The Ar 3s cluster line shows no splitting into bulk and surface components, different to the literature on pure clusters but in agreement with our discussion of the outer valence spectra. 
-The binding energy of the cluster line has values between 28.85 and 28.70 eV for all cluster ensembles with size label S-L, and 28.67 eV for the largest clusters measured. 
-A small, but systematic decrease of the binding energy is observed when the cluster size is increased. 
-The value assumed in the simulations is 28.7 eV.
-
-If we produce a spectrum only from those electrons recorded as part of a two-electron coincidence (electron pair with kinetic energies ($e_1,e_2$)) the apparent intensity drops (compare panel b to a, and d to c in Figure \ref{figure:ival}).
-This can partly be attributed to the finite detection efficiency of the spectrometer. 
-Moreover, the monomer part of the Ar 3s signal completely disappears, as 3s photoionization of an uncondensed Ar atom in the gas jet cannot lead to emission of a second electron. 
-Further features of these diagrams and the least squares fits shown in the Figure are discussed below.
-%
-%
-\subsection{ICD/ETMD spectra}
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_icd_12.pdf}
- \caption{
-Energy spectrum of all coincident secondary (ICD or ETMD) electrons of kinetic energy $e_2$ pertaining to primary electrons of kinetic energy $e_1$ in the Ar 3s binding energy region. 
-Spectra were recorded with a photon energy of $h\nu = 32$~eV. 
-Black error bars show the data points for the smallest clusters measured (`S'), two larger clusters sizes are shown by the red and blue traces. 
-Error bars for the latter are smaller than the ones shown and have been omitted.
-For better comparison, all spectra are shown area-normalized. 
-}
- \label{figure:icd_12}
-\end{figure}
-%
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_icd_l.pdf}
- \caption{
-Energy spectrum of all coincident secondary (ICD or ETMD) electrons, kinetic energy $e_2$, for clusters of the same size, but from gas mixtures with different Xe concentration.
-See Figure \protect\ref{figure:icd_12} for details.
-}
- \label{figure:icd_l}
-\end{figure}
-%
-In Figure \ref{figure:icd_12}, we show the spectra of ICD/ETMD electrons pertaining to emission of an Ar 3s cluster photoelectron. 
-Due to their low kinetic energy, without use of a coincidence method they could hardly be separated from the background of inelastically scattered photoelectrons.\cite{mucke}
-This and the following Figure constitute the central experimental result of the article.
-Spectra recorded at $h\nu = 34$ eV as a cross-check quantitatively agree to those shown here.
-This underpins our assignment of this intensity to an autoionization process.
-Further details on the data acquisition and analysis methodology, as well as the 34~eV spectra, are given in the Supporting Information.
-
-Spectra for the three different cluster sizes in Figure \ref{figure:icd_12} are significantly different: Spectra for the larger clusters acquire more intensity in the 1-1.5 eV region and have less intensity for energies below 0.5 eV.
-In contrast to that, the ICD/ETMD spectrum hardly varies when the composition of the expanding gas mixture, and with that the relative Xe content of the clusters, is changed (Figure \ref{figure:icd_l}).
-The full set of ICD/ETMD spectra is shown as Supporting Information.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_eff.pdf}
- \caption{
-Efficiency of the decay of Ar 3s ionized states in ArXe clusters by emission of a secondary electron via ICD or ETMD.
-Values are arranged by Xe content of the initial gas mixture (`+' symbols: 1.2\,\%, asterisk: 3\,\%, triangle: 5\,\%).
-Symbol sizes indicate the photon energy (large symbols: 32 eV, small: 34 eV), and color indicates the cluster size (black symbols: S, red: M, blue: L).
-See text for details.
-}
- \label{figure:eff}
-\end{figure}
-%
-We now discuss which fraction of Ar 3s vacancy states relaxes via ICD or ETMD.
-A method to derive this information has been established by some of us.\cite{foerstel_2013}
-Briefly, we correct the intensity of the Ar 3s photoline in the coincident spectra by the detector efficiency, and divide it by the total (coincident and non-coincident) Ar 3s intensity.
-The result gives the branching ratio of decay via ICD/ETMD vs. the sum of all channels, including those not involving electron emission.
-(If all Ar 3s vacancies decay by emission of another electron, the coincident and non-coincident count rate differ only by the probability for the spectrometer to actually detect the secondary electron.
-This figure has been determined as 0.6 for this data set, in the same way as discussed earlier.\cite{mucke_review})
-To arrive at quantitative results, we have performed least squares fits of the non-coincident and coincident $e_1$ spectra.
-The fits assumed one or two Gaussian peaks, resp., atop of a background modelled by two more Gaussian curves with very large widths.
-The peak pertaining to the Ar 3s cluster photoline, with the background added, is shown by the black solid trace in Figure \ref{figure:ival}a and red solid trace in Figure \ref{figure:ival}b.
-Moreover, the line labelled `c.fit/det.' shows the fit to the coincident events, corrected by the detection efficiency, and plotted atop of the non-coincident intensity. 
-This virtually agrees with the fit to the total spectrum in Figure \ref{figure:ival}a, but not in \ref{figure:ival}c. 
-The corresponding figure for the ICD/ETMD efficiency comes out as one for \ref{figure:ival}a, and significantly smaller than one for \ref{figure:ival}c.
-Figure \ref{figure:eff} shows all results of this analysis.
-The error in the autoionization efficiency shown is mainly determined by uncertainties in the peak/background separation.
-%(Our choice for the background shape is shown in Figure \ref{figure:ival}.)
-For the gas mixture with a Xe$_{\rm in}$ of 1.2\,\%, we therefore show results from fits using two different choices of the background shape in Figure \ref{figure:eff}.
-Statistical errors are much smaller than the differences between the pairs of values arrived at such.
-
-We found an Ar 3s autoionization efficiency which, for clusters with the lowest Xe content (Xe$_{\rm cl}$ approx.
-10-12\,\%), is smaller than unity, and further decreases with decreasing cluster size.
-For larger Xe$_{\rm cl}$, the values are compatible with unity, within the accuracy of our experiment.
-
-%\input{theo_discussion}
-\section{Discussion
-\label{sec:discussion}}
-%
-%We have discussed the experimental spectra in Section \ref{sec:exp_results} and
-%the expected features of spectra for different cluster types in
-%Section \ref{sec:th_results}. In this section we combine the experimental and theoretical
-%results in order to determine the structure of the noble gas clusters.
-%
-%The simulated secondary electron spectra for the xenon core structures
-%(see Figure \ref{figure:xe_3_in})
-%show an ICD peak at higher energies than those structures with added xenon
-%atoms on the surface. This does not fit to the experimentally determined
-%spectra and hence we consider an argon core to be more probable for the
-%small measured clusters.
-%
-%The experimental spectra in Figure \ref{}
-%show a broadening of the secondary electron peak with increasing
-%pressure (?) and hence cluster size just as can be expected from
-%the theoretically simulated spectra in Figure \ref{figure:surf}.
-%
-%From the theoretical simulations of larger small clusters
-%having the same xenon content as experimentally observed a clearly
-%visible ETMD peak is to be expected as shown in Figure \ref{figure:ar_3_6in}.
-%However, the experimental spectra do not show a signal in the energy
-%region of \unit[1.5--6.5]{eV}. From this we conclude that the clusters
-%measured were smaller than 55 atoms containing only very few xenon atoms.
-%Additionally, if the cluster contains more than one xenon atom, they are
-%not expected to be close because of an otherwise visible ETMD peak
-%(compare Figure \ref{figure:2tops}).
-%
-%The large clusters with a large xenon content can be expected to have
-%a xenon core being surrounded by argon layers and hence, both ICD and
-%ETMD should be visible in the spectrum. Unfortunately, the ICD and ETMD
-%peaks overlap such that the two processes can not be distiguished.
-%
-We now would like to interpret our experimental findings in view of the simulated results described in Section `Theoretical Results'.
-Figure \ref{figure:eff} shows that for Ar 3s$^{-1}$ states autoionization by either ICD or ETMD is the only mode of relaxation, except for the clusters with the smallest Xe content.
-We consider this a remarkable result, because ICD of these states is only possible with a Xe atom in the second coordination shell of the decaying Ar vacancy (or shells even further apart), which significantly slows down the ICD process.
-Also decay rates for ETMD were found to be small in early studies of this effect.\cite{zobeley}
-Nevertheless, even in this situation the non-local autoionization channels foreclose radiative decay.
-
-% lowest kinetic energy is the first point of energy raster for t-E code of 52-proc-spec
-Structurally, all experimental ICD/ETMD spectra have a maximum at or near the lowest kinetic energy that could be measured (50~meV), and decrease in intensity to less than half for kinetic energies already below one eV.
-Qualitatively, this shape fits to the ICD contributions in the autoionization spectra discussed in the `Theory' section, but not to the ones from ETMD. 
-The calculated ETMD spectra have a typical three-fold structure with peaks between 3.5-5~eV, 1.5-2.5~eV and around 0 eV kinetic energy. 
-The former two features seem not to be present in the experimental spectra. 
-Due to restrictions in the detector electronics, electron pairs with very similar kinetic energy cannot be detected. 
-The highest kinetic energy for an autoionization electron that can be detected in coincidence with a photoelectron of $\sim3.5$~eV ($h\nu = 32$~eV) is around 2.5~eV.
-Very weak intensity is observed at this energy, and also at higher $e_2$ energies that can be probed at $h\nu = 34$~eV (Supporting Information).
-
-As a cross-check for our theoretical methods we have calculated the radiationless decay spectrum of Ar 3s$^{-1}$ in ArKr, which may arise {\it only} from ETMD(3),\cite{foerstel} and arrived at qualitative agreement with the experimental data.\cite{arkr}
-
-The size-dependent trend within the experimental data is in qualitative agreement to the change in the calculated spectral shape for ICD in systems of increased size (compare Figure~\ref{figure:2tops} to \ref{figure:xe_3_in} and \ref{figure:xe_6_lay5}.)
-
-We are therefore lead to the conclusion that the autoionization spectra we incur are dominated by ICD to non-nearest neighbour atoms, while the intensity of the ETMD channel is low. 
-We would like to recall the factors that lead to a propensity for decay via one or the other mechanism, which have been discussed in the `Theoretical Results'-section.
-For ETMD to occur with a measurable rate, two Xe atoms have to be present in the vincinity of the decaying Ar atom (Figure \ref{figure:2tops}).
-Should that be the case for a large part of the Ar atoms in some cluster structure, ETMD can even dominate over ICD (Figure \ref{figure:ar_3_6in} and Supporting Information).
-Model structures shown in Figures \ref{figure:2tops} and \ref{figure:ar_3_6in} have a Xe content similar to the lowest one probed in our experiment ($\sim$11\,\%).
-For a higher Xe content, ETMD will always dominate the spectra if the two species are given the chance to mix, as e.g.
-in the calculated minimum energy structures of $N=38$ ArXe clusters (Supporting Info).
-On the other hand, in core-shell systems decay via ETMD is probable only for Ar atoms in the interface layer, as this mechanism requires some wavefunction overlap between Ar and one of the Xe atoms involved.
-For the core-shell systems we have investigated, the likelihood of decay via ETMD stays below 25\,\% even for a Xe content above 50\,\% (Table \ref{table:theo_gammas}).
-
-In summary, the two structural motifs that can best be reconciled with our experimental data are
-\begin{enumerate}
-	\item small clusters containing only few Xe atoms that are spread out to distant positions on the cluster surface, and
-	\item systems with a compact Xe core and Ar outer layers.
-\end{enumerate}
-These structures are compatible with the findings of Lindblad {\it et al.}\ from core level photoelectron spectroscopy, who proposed the former structure for the smallest clusters in their study, and the latter for larger ones.\cite{lindblad}
-As even in these two cases intensity for decay via ETMD would not vanish completely, we have to leave it open though whether other mechanisms are present, which further suppress ETMD vs. ICD.
-
-While in early work on ICD it has almost been a paradigm that the decay involves two {\it neighbouring} atoms or molecules,\cite{hergenhahn_review} more recently significant intensity for non-nearest neighbour ICD has been found also in other systems.
-One example is Ne-Ar after Ne 2s ionization, where decay to Ar in the second coordination shell is clearly visible despite the fact that in this system decay involving nearest neighbours is energetically allowed.\cite{fasshauer2014}
-A further theoretical delineation of the respective factors has recently been presented by one of us.\cite{fasshauernjp}
-
-%\input{summary}
-\section{Summary}
-%
-We have presented comprehensive experimental and theoretical data for the
-autoionization of inner valence ionized states in ArXe clusters.
-Both ICD and ETMD are allowed for most cases we considered.
-Because of energetical reasons ICD requires a separation of the final state
-vacancies of \unit[7.58]{\AA} or more, which is about two times the typical
-Ar-Xe distance.
-We found that autoionization has an efficiency of 0.8 to 1.0 within the
-experimental accuracy, that is it dominates over other modes of relaxation.
-By comparing our measured spectra to calculations, we identified `long range'
-ICD as the most important decay mode and were able to determine the most
-probable structural motifs to be a xenon core surrounded by several argon layers
-for large clusters and argon clusters with with very few xenon atoms spread out
-over the surface.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The "Acknowledgement" section can be given in all manuscript
-%% classes.  This should be given within the "acknowledgement"
-%% environment, which will make the correct section or running title.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{acknowledgements}
-\begin{acknowledgement}
-%
-We thank HZB for the allocation of synchrotron radiation beamtime, and the
-Deutsche Forschungsgemeinschaft for funding via the Forschergruppe 1789.
-E. F. gratefully acknowledges the Research
-Council of Norway through a Centre of Excellence Grant (Grant No.\ 179568/V30)
-for funding.
-%
-\end{acknowledgement}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The same is true for Supporting Information, which should use the
-%% suppinfo environment.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{suppinfo}
-
-%This will usually read something like: ``Experimental procedures and
-%characterization data for all new compounds. The class will
-%automatically add a sentence pointing to the information on-line:
-
-%\end{suppinfo}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The appropriate \bibliography command should be placed here.
-%% Notice that the class file automatically sets \bibliographystyle
-%% and also names the section correctly.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliography{arxe}
-
-\end{document}

### 2019-03-22 resubmit_2/summary.tex
submitted files

--- 2016-07-04 onefolder/master.tex
@@
-	
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% This is a (brief) model paper using the achemso class
-%% The document class accepts keyval options, which should include
-%% the target journal and optionally the manuscript type.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\documentclass[journal=jpccck,manuscript=article,layout=twocolumn]{achemso}
-\documentclass[journal=jpccck,manuscript=article]{achemso}
-
-% UHe stuff
-\def\EB{E_{\rm b}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Place any additional packages needed here.  Only include packages
-%% which are essential, to avoid problems later. Do NOT use any
-%% packages which require e-TeX (for example etoolbox): the e-TeX
-%% extensions are not currently available on the ACS conversion
-%% servers.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage[english]{babel}
-\usepackage{braket}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath,amsfonts,amssymb}
-\usepackage{dsfont}
-\usepackage{booktabs}
-\usepackage{units}
-\usepackage{xcolor}
-\usepackage{multirow}
-\usepackage{tikz,pgfplots}
-\usepackage{float} %force figure position
-
-\usetikzlibrary{patterns,shadows,trees,calc}
-\usepgfplotslibrary{units}
-
-\pgfplotsset{compat=1.10}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% If issues arise when submitting your manuscript, you may want to
-%% un-comment the next line.  This provides information on the
-%% version of every file you have used.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%\listfiles
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Place any additional macros here. Please use \newcommand* where
-%% possible, and avoid layout-changing macros (which are not used
-%% when typesetting).
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newcommand*\mycommand[1]{\texttt{\emph{#1}}}
-% Define some colours
-\definecolor{diplom1}{rgb}{0.0 0.4 1.0}
-\definecolor{diplom2}{rgb}{0.0 0.0 0.6}
-\definecolor{diplom3}{RGB}{153,0,0} %unirot
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Meta-data block
-%% ---------------
-%% Each author should be given as a separate \author command.
-%%
-%% Corresponding authors should have an e-mail given after the author
-%% name as an \email command. Phone and fax numbers can be given
-%% using \phone and \fax, respectively; this information is optional.
-%%
-%% The affiliation of authors is given after the authors; each
-%% \affiliation command applies to all preceding authors not already
-%% assigned an affiliation.
-%%
-%% The affiliation takes an option argument for the short name.  This
-%% will typically be something like "University of Somewhere".
-%%
-%% The \altaffiliation macro should be used for new address, etc.
-%% On the other hand, \alsoaffiliation is used on a per author basis
-%% when authors are associated with multiple institutions.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author{Marko F\"orstel}
-\altaffiliation{Now at: Institut für Optik und Atomare Physik, Technische Universit\"at Berlin, Hardenbergstr. 36, 10623 Berlin, Germany}
-\author{Melanie Mucke}
-\altaffiliation{Now at: Department of Physics and Astronomy, Uppsala University, Box 516, 75120 Uppsala, Sweden}
-\author{Tiberiu Arion}
-\altaffiliation{Now at: Center for Free-Electron Laser Science/DESY, Notkestr. 85, D-22607 Hamburg, Germany}
-\author{Toralf Lischke}
-\affiliation[IPP]{Max-Planck-Institute for Plasma Physics, Boltzmannstr. 2, D-85748 Garching, Germany}
-\author{Markus Pernpointner}
-\affiliation[University of Heidelberg]{Theoretical Chemistry, University of Heidelberg,
-              Im Neuenheimer Feld 229, D-69120 Heidelberg, Germany}
-\author{Uwe Hergenhahn}
-\affiliation[IOM]{Leibniz Institute of Surface Modification, Permoserstr. 15, D-04318 Leipzig, Germany}
-\alsoaffiliation[IPP HGW]{Max-Planck-Institute for Plasma Physics, Wendelsteinstr. 1, D-14791 Greifswald, Germany}
-\email{uwe.hergenhahn@iom-leipzig.de}
-\author{Elke Fasshauer}
-\affiliation[UIT]{Centre for Theoretical and Computational Chemistry,
-Department of Chemistry, University of Troms\o
--- The Arctic University of Norway, N-9037 Troms\o, Norway}
-\email{elke.fasshauer@uit.no}
-%\phone{+123 (0)123 4445556}
-%\fax{+123 (0)123 4445557}
-%\alsoaffiliation[Second University]
-%{Department of Chemistry, Second University, Nearby Town}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The document title should be given as usual. Some journals require
-%% a running title from the author: this should be supplied as an
-%% optional argument to \title.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Long-range Interatomic Coulombic Decay in ArXe clusters: Experiment and Theory}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Some journals require a list of abbreviations or keywords to be
-%% supplied. These should be set up here, and will be printed after
-%% the title and author information, if needed.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\abbreviations{IR,NMR,UV}
-%\keywords{American Chemical Society, \LaTeX}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The manuscript does not need to include \maketitle, which is
-%% executed automatically.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The "tocentry" environment can be used to create an entry for the
-%% graphical table of contents. It is given here as some journals
-%% require that it is printed as part of the abstract page. It will
-%% be automatically moved as appropriate.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{tocentry}
-
-\begin{center}
- \includegraphics[height=3.5cm]{front1.pdf}
-\end{center}
-
-%Some journals require a graphical entry for the Table of Contents.
-%This should be laid out ``print ready'' so that the sizing of the
-%text is correct.
-%
-%Inside the \texttt{tocentry} environment, the font used is Helvetica
-%8\,pt, as required by \emph{Journal of the American Chemical
-%Society}.
-%
-%The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
-%permitted for  \emph{Journal of the American Chemical Society}
-%graphical table of content entries. The box will not resize if the
-%content is too big: instead it will overflow the edge of the box.
-%
-%This box and the associated title will always be printed on a
-%separate page at the end of the document.
-
-\end{tocentry}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The abstract environment will automatically gobble the contents
-%% if an abstract is not used by the target journal.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{abstract}
-
-\begin{abstract}
-We report about autoionization channels of Ar inner valence ionized states in mixed ArXe clusters and compare
-our experimental data obtained by electron-electron coincidence spectroscopy
-to our theoretical simulations for representative cluster structures.
-The combined experimental and theoretical data show that the autoionization of Ar 3s$^{-1}$ in ArXe is dominated by Interatomic Coulombic Decay (ICD) to Xe atoms in the second and higher coordination shells of the originally excited atom.
-Clusters with a range of sizes, compositions and structures were probed. 
-The Xe content in the clusters was varied between 10\,\% and 53\,\%. 
-Besides ICD, also Electron Transfer Mediated Decay (ETMD(3)) was found important in many of the calculated spectra, but is seen with less intensity in the experimental spectra. 
-From the calculations, we identify structural motifs which minimize the ETMD vs.
-the ICD rate and suggest that these are preferentially realized in our experiment, in which clusters are formed by supersonic expansion of an Ar-Xe mixture.
-Suggested cluster structures either feature a clear segregation between Ar and Xe fractions, e.g. Xe core, Ar shell systems, or contain a few Xe atoms singled out in surface sites on an Ar cluster.
-These structures differ significantly from the majority of calculated minimum energy structures for ArXe systems of 38 atoms, which might show that the latter, annealed structures are not realized in our experiment.
-We show experimentally that the relaxation of Ar inner valence states by ICD and ETMD together has an efficiency of unity, within the experimental accuracy, for all clusters except those with the lowest Xe content.
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Start the main part of the manuscript here.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{intro}
-\section{Introduction}
-%
-Electron spectroscopy can make important contributions to the 
-research on composition and structure of free nanoparticles.\cite{
-jpcc} Besides photoionization, free electrons emerging from 
-nanoparticles can also be produced by the relaxation of 
-electronically excited states. One such process, which is of 
-particular relevance in weakly bonded systems, is the 
-Interatomic or Intermolecular Coulombic Decay (ICD).\cite{
-cederbaum} In ICD, an electronic excitation decays by energy 
-transfer to one of its neighboring atoms or molecules, thus 
-releasing a free electron from the latter site. ICD is an 
-important relaxation channel e.g. for inner-valence holes in 
-atoms, and also for core level vacancies e.g. in \ce{H2O}
-, where it competes with Auger decay.\cite{slavicek}
-
-By definition, ICD is particularly sensitive to the chemical 
-environment of the atom or molecule in which the primary 
-excitation has taken place. We suggest that this property of ICD 
-decay spectra can be used to derive information on a nanoparticle 
-or a solvation system. 
-The term excitation is used here in a broader sense---in the
-systems we consider in this work, ICD occurs from an excited, singly 
-charged Ar state created by photoionization.
-In other systems, ICD was also observed from neutral excited
-states and states with more than one vacancy.
-
-We report here about studies 
-in which we produced heterogeneous clusters of the noble gases Ar 
-and Xe with different sizes, and compositions ranging from a few 
-Xe dopant atoms in an Ar matrix to clusters containing an equal 
-amount of both species. By the use of electron-electron 
-coincidence spectroscopy and of theoretical simulations on 
-prototypical systems we show how the radiationless decay spectrum 
-of Ar inner valence (3s) ionized states connects to the structure 
-of the clusters.
-
-Intermolecular Coulombic Decay initially was predicted from 
-theoretical considerations of the energy levels in singly vs.\  
-doubly ionized, and doubly vs.\ triply ionized, hydrogen bonded 
-clusters.\cite{cederbaum} First experimental work some years 
-later used Ne clusters,\cite{marburger,jahnkenedimer} but quickly 
-was followed by demonstrations of ICD in a diverse range of other 
-systems. Experimental and theoretical progress has been reviewed.
-\cite{hergenhahn_review, averbukh_review, jahnke_review} ICD 
-proceeds by an initial ionization producing an ion in an excited 
-state, followed by a transfer of energy to a neighbouring site, 
-and an electron emission process therefrom. The final state contains 
-two positive charges; one at the original site of ionization, and a second
-one at another atom or molecule.
-
-Soon after, related 
-autoionization processes were discovered that proceed via a 
-charge transfer instead of an energy transfer. 
-These were termed `Electron Transfer Mediated Decay' 
- (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
- which the originally excited site is neutralized by the decay 
-and `exchange ICD' for charge transfer contributions to the 
-normal ICD amplitude.\cite{santrarev,jahnkesat}
-We find that both energy and charge transfer induced 
-autoionization play a role in Ar-Xe, and will detail the 
-relevant processes below. The notion of ICD requires that the 
-electronic orbitals of the two sites can be distinguished, which 
-typically is the case in weakly bonded systems, held together by 
-hydrogen bonds or van-der-Waals bonds. In the case of strong
-(covalent or metallic) bonding, it is impossible to make a
-distinction between ICD and Auger decay.\cite{hergenhahn_review}
-
-Rare gas clusters are suitable prototype systems for studies of
-ICD, as they can readily be produced by supersonic 
-expansion through a cooled nozzle. 
-The size of the clusters can be changed by varying the expansion parameters.
-The formation of heterogeneous rare gas clusters by coexpansion of a gas mixture cannot {\it a priori} be taken for granted, but was experimentally shown for most combinations of two rare gases, when suitable mixing ratios and expansion parameters are used (see references throughout this article).
-
-First experiments on ICD in heterogeneous systems used Ne-Ar 
-clusters.\cite{barthnear} Those were followed by studies of 
-ICD-like inner-shell decays in aqueous solution.\cite{aziz,pokapanich,pokapanich2011}
-Pioneering work also showed the 
-potential for studies of the interface between a substrate and an 
-adsorbate by ICD.\cite{grieves} More detailed work on Ne-Ar 
-clusters was recently presented by some of the authors \cite{fasshauer2014}
-showing that an analysis of the ICD spectra
-allowed to decide between structural alternatives, for which the
-photoelectron data were indiscriminate.
-For this system, a detailed account of the
-photoelectron spectra with respect to structural features of the 
-mixed clusters is also available.\cite{lundwall}
-
-Several experimental techniques have been used for the study of mixed Ar-Xe clusters, most notably fluorescence spectroscopy, electron diffraction and photoelectron spectroscopy. 
-Early work focussed on the fluorescence of a single Xe atom 
-embedded in an Ar cluster.\cite{lengenprl}
-%Different sites of the dopant atom (on top of a surface, 
-%integrated in an Ar surface, inside the cluster) were 
-%distinguished by three separate bands in the fluorescence yield 
-%recorded as a function of excitation wavelength.\cite{goldberg} 
-Increasing the Xe concentration in the expansion lead to the formation of \ce{Xe2} and larger Xe complexes inside the clusters.\cite{lengen} 
-With increasing Xe content, the formation of Xe-core, Ar-shell systems with a sharp interface between the two species was shown in photoionization experiments.\cite{tchaplyguine,hoener}
-This finding was confirmed by electron diffraction.\cite{Danylchenko,Danylchenko07} 
-Always, the observed Xe content in the clusters is higher than the Xe content in the expanding gas mixture, as Xe can be condensed much easier than Ar.\cite{hoener,Danylchenko07}
-%A complementary study used photoelectron-photoion coincidence of
-%large Ar-Xe clusters, and found that after inner shell (Xe 4d, Ar 2p)
-%photoionization significant charge transfer between both species
-%occurs before the mass spectroscopic final state is reached.\cite{berrah}
-%
-More recently, photoelectron spectra of 
-small Ar-Xe clusters were analyzed, adding to the findings in 
-earlier work.\cite{lindblad} We will discuss this paper in 
-connection with our results below. 
-For completeness, we mention that Ar-Xe complexes can also be produced by passing clusters from a neat Ar expansion through a zone filled with Xe gas (`pick-up').\cite{pietrowski}
-Clusters produced such can structurally be quite different from those produced by coexpansion.\cite{lindbladpccp}
-
-A number of theoretical works on Ar-Xe clusters aimed at the prediction of minimum energy structures. 
-Most recently, these converged to structures which have the Xe atoms mainly in the interior.\cite{marques} 
-Xe was also found to diffuse into the interior of Ar clusters in molecular dynamics simulations after pick-up.\cite{Vach_1999} 
-The electronic energy levels of very small Ar-Xe clusters were calculated in ref \citenum{fasshauer} and the secondary electron spectra were simulated for
-model structures of one argon atom placed on a xenon surface \cite{Fasshauer13}.
-Interestingly, it was found that Ar 3s$^{-1}$ is stable 
-against autoionization in an ArXe dimer, but is destabilized by 
-adding further Xe atoms, or an Ar solvation shell, to the system, thereby allowing
-for combinations of argon and xenon atoms with larger interatomic distances. 
-Again, we will detail these results in conjunction with our 
-current work.
-
-The plan of our paper is as follows: We firstly delineate our experimental and theoretical methods. 
-Calculations were done for a number of model structures which were systematically varied, and are described in the following section.
-After that, we describe and discuss our theoretical results for the autoionization spectra of the model clusters.
-Experimental results are then shown and possible conclusions from comparing them to the calculations are given.
-Details on the experimental technique, and calculated spectra for a wider range of structures are given as Supporting Information.
-
-%\input{experimental}
-
-\section{Experimental}
-%
-\begin{table*}
-\caption{
-The expansion parameters used for cluster production. 
-Here, Xe$_{\rm in}$ is the molar fraction of Xe in the gas mixture before the expansion, $T$ is the nozzle temperature, and $p$ the stagnation pressure. 
-Experiments were performed with $d = 80~\mu$m (first two sections) and $d = 100~\mu$m (bottom section) conical nozzles of 15$^\circ$ half opening angle. 
-We basically have an Ar seeded expansion of Xe gas, as the freezing point of Ar is much lower. 
-$\langle N_{\rm Ar} \rangle$ and $\langle N_{\rm Xe} \rangle$ refer to cluster sizes for a pure Ar, or pure Xe expansion, respectively, at the given conditions, calculated from a scaling law.\protect\cite{hagena1981}
-We expect actual cluster sizes in-between these two limiting values. 
-Inaccuracies in the calculation of $\langle N\rangle$ due to fluctuations of the input parameters are less than 6\,\%. This figure does not include systematic errors of the empirical model.
-}
-\label{tab:cluster}
-
-\begin{tabular}{l c c c c r r}
-%
-\toprule
-  \multicolumn{2}{r}{size label}  &  Xe$_{\rm in}$ (\%)  &  $T$ (K)  &  $p$ (bar) & $\langle N_{\rm Ar} \rangle$ & $\langle N_{\rm Xe} \rangle$ \\
-%
-\midrule
-% Ar, from Marko 
-Ar & (1) & --- &  96.5  & 0.35  & 44  &  --- \\
-% Ar, from Marko 
-Ar & (2) & --- &  96.5  & 0.67  & 200  &  --- \\
-\midrule
-% 1103 676, 679
-ArXe & `S' & 1.2 &  174   & 0.32  & 4  &   74 \\
-% 1103 670
-ArXe & `M' & 1.2 &  174   & 0.49  & 11  &  199 \\
-% 1103 671
-ArXe & `L' & 1.2 &  174   & 0.68  & 23  &  431 \\
-\midrule
-% 1103 663
-ArXe & `S' & 3.0 &  172   & 0.28  & 3  &   57 \\
-% 1103 653
-ArXe & `M' & 3.0 &  172   & 0.51  & 12  &  233 \\
-% 1103 658
-ArXe & `L' & 3.0 &  172   & 0.68  & 24  &  458 \\
-\midrule
-% 1103 630
-ArXe & `S'  & 5.0 &  167  & 0.37  & 7  &  129 \\
-% 1103 640
-ArXe & `M' & 5.0 &  171   & 0.51  & 13  &  240 \\
-% 1103 629
-ArXe & `L'  & 5.0 &  167  & 0.68  & 28  &  537 \\
-\midrule
-% 1004 867 (32 eV)
-ArXe & `XL' & 2.5 &  154  & 2.12  & 995 & 18800\\
-\midrule
-% 0506 382, Keller offset ber?cksichtigt
-Xe &  & 100 & 183.5  & 0.68  & ---  &  615 \\     
-% 1004 868
-%868 & & 2.5 &  158   & 1.50  &  355 &  6090\\
-% 1004 886 (17 eV)
-%886 &  & 2.5 &  161   & 2.41  &  980 & 16770\\
-% 1004 858
-%858 &  & 5.0 &  149   & 2.50  & 1620 & 27700\\
-%
-\bottomrule
-\end{tabular}
-\end{table*}
-%
-%
-The apparatus used for the experiments consists of a supersonic molecular jet with a cooled nozzle, and a magnetic bottle spectrometer, which detects photoelectrons and secondary electrons produced after ionization with synchrotron radiation.\cite{arion}
-% Leave this citation in place to avoid Latex error
-A comprehensive description can be found in ref \citenum{arion}, and here we focus on details specific for the current experiment. 
-Commercialy obtained Ar and Xe gas was filled into 
-separate cylinders up to pressures suitable for producing a certain mixing ratio. The gases were then allowed to mix before the expansion. 
-Expansion parameters are given in Table \ref{tab:cluster}. 
-Similar expansion conditions are further referred by the labels `S'-`XL', as given in the Table.
-
-Prediction of the sizes of clusters from a supersonic expansion mainly rests on empirical scaling laws,\cite{hagena1981} which have been the subject of some discussion.
-Moreover, such scaling laws originally were derived only for pure gas expansions.
-A recent investigation of cluster sizes in a mixed Ar-Kr expansion yielded a revised scaling law, which essentially amounts to the use of a weighted average over the atom-specific parameters of the two gases.\cite{danylchenko2015}
-Although the analogy to our case is not complete, as phase segregation occurs in Ar-Kr to a much lesser extent,\cite{Vach_1999,lundwall_arkr} we expect scaling law cluster sizes between the values calculated for Ar and Xe.
-Recent analyses of photoionization spectra suggest that mean sizes arrived at by scaling laws are smaller than the actual size, at least for rare gas clusters in the range $\langle N\rangle < 1000$.\cite{bergersen,hergenhahnprb,foerstel_arg2_2011}
-For the expansion conditions labelled `S'-`L', we therefore expect that the scaling law estimates are a lower boundary for the actual cluster size.
-
-The expansion chamber for the supersonic jet is separated from the interaction chamber by a non-magnetic, conical skimmer with an opening of 1~mm in diameter (Beam Dynamics). 
-At few cm distance behind the skimmer, the cluster jet was crossed by synchrotron radiation from the BESSY electron storage ring at Helmholtz-Zentrum Berlin. 
-Electrons were detected by a short `magnetic bottle' time-of-flight spectrometer, that has been described earlier.\cite{mucke_review}
-Due to its large collection angle, this instrument is particularly suited for experiments that employ electron-electron coincidence detection.
-Data were recorded in two different beamtimes at the UE112-PGM-1 (small and medium sized clusters, first two sections in Table \ref{tab:cluster}) and at the TGM-4 beamline (large clusters, last section in Table \ref{tab:cluster}).
-Linearly, horizontally polarized radiation was used. 
-The storage ring was operated in single bunch conditions.
-Spectra of pure Ar clusters shown for comparison are from ref \citenum{foerstel_arg2_2011}, and a spectrum of pure Xe clusters was recorded with the set-up described in ref \citenum{hergenhahnprb}.
-
-The entrance aperture and drift tube of the magnetical bottle spectrometer can be independently biased to influence the electron flight times. 
-For the data shown here, slightly positive bias voltages were used (+1.8 V to +2.2 V) in order to have all electrons arriving at the detector within one BESSY single bunch period (800 ns). 
-The detection efficiency was determined as 0.6, with the method outlined in ref \citenum{mucke_review}.
-Data were converted from flight times to kinetic energy by measuring calibration data for atomic photolines of known binding energy.
-The systematical uncertainty of this procedure may lead to a common shift of all experimental kinetic energy data shown in this article of up to 30~meV.
-
-The high detection efficiency of the instrument is a pre-requisite for measuring two-electron emission processes, such as photoelectron emission followed by ICD or ETMD, by using electron-electron coincidence detection.
-This allows to filter the full electron spectrum for contributions arising after emission of an Ar 3s photoelectron.
-ICD/ETMD spectra presented here are based on this method, which has been explained earlier.\cite{mucke_review,Foerstel_phd}
-Technical details and full electron-electron coincidence spectra are given in the Supporting Information.
-
-%\input{theory}
-\section{Theoretical Approach}
-%
-Experimental coincidence spectra are given by the multitude of
-kinetic energies $E_{\rm sec}$ of the secondary electron
-and the intensities of the peaks. The latter is proportional to the
-probability of the decay as well as the theoretically determinable
-decay width $\Gamma=\frac{\hbar}{\tau}$,
-which is inversely proportional to the lifetime $\tau$ of the decay process.
-The manifold of the
-secondary energies and decay widths will therefore compose the electron-electron
-coincidence spectrum.
-In case of noble gas clusters
-with given geometrical structures three aspects have to be taken into account:
-different decay mechanisms, the possibility to decay with multiple
-interaction partners and different decay channels $\beta$ within
-each decay mechanism.
-At the current stage of development we need to neglect the nuclear dynamics which
-additionally might play an important role.
-
-%We are interested in describing the electron emission spectra of excited states in clusters, that where measured by the electron-electron coincidence method in our experiments. 
-%In our theoretical description, these will be composed of multiple transitions, each characterized by a kinetic energy $E_{\rm sec}$ of the secondary electrons, and the intensity of the peak.
-%The latter is proportional to the probability of the decay, represented here by the decay width $\Gamma_\beta = \hbar/\tau_\beta$, where $\tau_\beta$ is the lifetime due to the respective transition.
-%The total decay width $\Gamma$ is the sum of all partial $\Gamma_\beta$.
-%In case of noble gas clusters with a given geometrical structure, three aspects have to be taken into account:
-%different decay mechanisms, the contribution of different cluster sites to the respective decay, and the existence of different decay channels within each decay mechanism.
-%At the current stage of development we have to neglect the nuclear dynamics, which
-
-This means, for the evaluation of the decay width we are dealing with a sum over three different indices: 
-For a given structure it is most convenient to
-start with a decomposition of the system into interaction partners of
-the different relevant decay mechanisms, i.e. pairs (combination of two atoms regardless
-of their internuclear distance) for the ICD and triples (combinations of three atoms)
-for the ETMD(3).
-These atoms do not necessarily need to form bonds between each other or
-even be close, but they are characterized according to fixed internal
-coordinates. 
-Each pair and each triple leads to a decay spectrum that can be described by the energy of the secondary electron and the decay width, which is in first order of approximation independent of other atoms present in the cluster.
-In the following, this approach will be called model of pairs and triples.
-
-%Decomposing every system into pairs and triples of atoms is a very useful
-%first order approximation to both the investigation of energies and
-%decay widths of a larger system. Pairs and triples are combinations of
-%two and three atoms, respectively.
-
-In order to determine, whether a channel $\beta$ for a given geometry and decay
-mechanism is open, i.e., whether it is in accordance with energy conservation,
-knowledge of the energies of the initial and the final states, $E_{\rm in}$ and $E_{\rm fin}$, of
-the corresponding processes is necessary.
-If the channel
-is open, the excess energy is carried away by the emitted electron
-in form of its kinetic energy $E_{\rm sec}$. These energies in the model
-of pairs and triples can be approximated by
-
-\begin{align}
- E_{\rm in}        &= SIP(X_{\rm in}) \label{equation:E_in}\\
- E_{\rm fin}^\beta &= SIP(X_{D}^\beta) + SIP(X_{E}^\beta) + \frac 1d
-           \label{equation:E_fin}\\
- E_{\rm sec}^\beta &= E_{\rm in}^\beta - E_{\rm fin}^\beta \label{equation:E_sec}
-\end{align}
-where $X_{\rm in}$ denotes the initially ionized atom and
-$X_{D}$ and $X_{E}$ describe the electron donating atom and electron
-emitting atom, respectively.
-$\beta$ denotes the decay channel characterized by the quantum numbers of the ionized atoms in the pairs and triples, $SIP(X^\beta)$ the single ionization potential of vacancy $\beta$ in atom $X$ and $d$ the interatomic distance between the atoms $X_{D}$ and $X_{E}$.
-Atomic units are used.
-The initially ionized atom $X_{\rm in}$ can
-coincide with one or both of
-the final state atoms
-$X_{D}$ and $X_{E}$.
-The distribution of the vacancies over the different
-atoms determines the kind of electronic decay process at hand. Hence, in an
-Auger process all three atoms coincide, for an ICD process $X_{\rm in}$
-coincides with $X_{D}$, for an ETMD(2) process $X_D$ and $X_E$ coincide
-and for an ETMD(3) process
-all ionized states are located on different atoms.
-
-\begin{figure}[h]
- \centering
- \includegraphics[width=\columnwidth]{channel_open_ICD.pdf}
- \caption{Illustration of channel opening: Initial (Ar3s$^{-1}$)
-          and final state (Ar3p$^{-1}$Xe5p$_{3/2}^{-1}$ and
-          Ar3p$^{-1}$Xe5p$_{1/2}^{-1}$) energies
-          for ICD in ArXe pairs as a function of 
-          internuclear distance, using eq. (\ref{equation:E_fin})
-          and the experimental ionization
-          potentials given
-          in Table \ref{tab:valence}. When the final state energy is lower
-          than the initial state energy the corresponding channel
-          is open. We call the distance at which the energies are equal
-          the `channel opening distance'. If the curves do not cross, the
-          corresponding channel is closed.}
- \label{figure:channel_open_ICD}
-\end{figure}
-
-The electron emitted by autoionization has the kinetic energy $E_{\rm sec}$. 
-If the calculated value of $E_{\rm sec}$ is negative,
-the final state energy is higher than the initial state energy and the        
-process is energetically not accessible. Hence, the corresponding channel     
-is closed, as shown in Figure \ref{figure:channel_open_ICD} for the
-Ar3p$^{-1}$Xe5p$_{1/2}^{-1}$ final state. Related to
-the opening of each channel is an internuclear distance which we will call 
-\emph{channel opening distance} in the following.
-
-This {\latin ad hoc} approach allows to easily correct for energetic shifts of ionization potentials as observed in larger clusters by adding experimentally or theoretically determined energy shifts $\Delta E(X_{I}^{\beta})$ for a given vacancy $I={\rm in},D,E$ and channel $\beta$.
-This yields the working expression for the kinetic energy of the secondary electron:
-
-\begin{equation}
- E_{\rm sec}^\beta = SIP(X_{\rm in}) + \Delta E (X_{\rm in})
-               - SIP(X_{D}^\beta) - \Delta E (X_{D}^\beta)
-               - SIP(X_{E}^\beta) - \Delta E (X_{E}^\beta)
-               - \frac 1d .
-\end{equation}
-
-The total decay width $\Gamma$ is given by the sum over the decay widths
-of all decay mechanisms. In case of the ArXe clusters we only consider
-ICD and ETMD(3), because the ETMD(2) pathway is energetically not accessible:
-
-\begin{equation}
- \Gamma = \Gamma_{\rm ICD} + \Gamma_{\rm ETMD} .
-\end{equation}
-
-These are given by the sum over the decay widths of all pairs $i$ for the
-ICD and all triples $j$ for the ETMD(3), respectively, and over all channels $\beta$:
-%
-\begin{align}
- \Gamma_{\rm ICD}  &= \sum\limits_{i,\beta} N_{{\rm ICD},i}  \, \Gamma_{{\rm ICD},i,\beta},\\
- \Gamma_{\rm ETMD} &= \sum\limits_{j,\beta} N_{{\rm ETMD},j} \, \Gamma_{{\rm ETMD},j,\beta}.
-\end{align}
-Here, $N_{{\rm ICD},i}$ and $N_{{\rm ETMD},j}$ denote the number of geometrically
-equal pairs and triples in a given cluster structure. The total number of pairs
-reads
-$N_{{\rm ICD}} = N_{\rm in} \cdot N_{D/E} = N_{\rm Ar} \cdot N_{\rm Xe}
- = \sum\limits_i N_{{\rm ICD},i}$ and the number of triples is
-$N_{{\rm ETMD}} = N_{\rm in} \cdot N_{D/E} (N_{D/E} - 1) = N_{\rm Ar} \cdot N_{\rm Xe} (N_{\rm Xe} - 1)
- = \sum\limits_j N_{{\rm ETMD},j}$.
-The numbers of geometrically equivalent pairs $N_{{\rm ICD},i}$ and triples $N_{{\rm ETMD},j}$
-strongly depend on the structure of the cluster. From these relationships
-it can be seen that a higher xenon content in the cluster statistically
-favours ETMD(3) over ICD.
-
-In previous work \cite{Fasshauer13,Fasshauer_thesis} we have shown that
-the decay width for a single pair or triple for a distinct channel $\beta$
-following Wentzel \cite{Wentzel27}, Feshbach\cite{Feshbach58,Feshbach62}
-and Fano,\cite{Fano61}
-%
-\begin{equation}
- \Gamma_{\beta}(E_{\rm res}) = 2\pi \left|
-                           \braket{\Phi_{\rm in}| H_f |\chi_{\beta}}
-                           \right|^2,
-\end{equation}
-%
-can be approximated by its asymptotic behaviour
-%
-\begin{equation}
- \Gamma_{{\rm ICD},i,\beta} = (2J_{\rm in}+1)\, \frac{3c^4}{8\pi}\,
-                        \sum\limits_{M_{in}'}
-                        \left| \left(
-                        \begin{array}{ccc}
-                        J_A'  & 1        & J_A\\
-                        -M_A' & M_A'-M_A & M_A
-                        \end{array}\right) \right|^2
-                        \frac{\sigma^{(X_E)}(\omega_{vp,\beta})}
-                        {R_i^6 \, \omega_{vp,\beta}^4 \tau_{in,\beta}},
-\end{equation}
-%
-where $J_A$, $J_A'$ and $M_A$, $M_A'$ denote the total angular momentum of the
-initially ionized atom (which is the same as the electron donor atom) in the
-initial and final state, respectively,
-and
-%
-\begin{align}
- \Gamma_{{\rm ETMD},j,\beta} =& \frac{c}{\pi} \sum\limits_{m,M_{in,D'}}
-                        \frac{\Theta_{m,k}(\alpha_j) \sigma^{(X_E)}(\omega_{vp,\beta})
-                              \left| <\tilde{D}_{m,j,\beta}(M_{in,D'})>\right|^2}
-                         {R_j^6 \omega_{vp,\beta}}\\
-               =& \frac{c}{\pi R_j^6}
-               \sum\limits_{M_{in,D'}}
-               \left( \left| <\tilde{D}_{x,j,\beta} (M_{in,D'}) > \right|^2
-                 (2+ \sin^2\alpha_j)
-               + \left| <\tilde{D}_{z,j,\beta} (M_{in,D'}) > \right|^2
-                 (1+\cos^2\alpha_j) \right) \nonumber \\
-           & \times\, \frac{c\sigma^{(X_E)}(\omega_{vp,\beta})}{\omega_{vp,\beta}}
-\end{align}
-%
-depending on 
-experimental properties
-of atoms, like the ionization cross sections
-$\sigma^{(X_E)}(\omega_{vp,\beta})$, radiative lifetimes of the initially
-ionized state $\tau_{in,\beta}$ and the excess energy transferred to the
-emitting atom (the energy of the virtual photon) $\omega_{vp,\beta}$
-and calculated dipole transition moments $\tilde{D}_{m,j,\beta}$, only.
-Here, $\Theta_{m}(\alpha_j)$ is a function depending on the angle $\alpha_j$
-of the triple and the direction of the dipole
-transition moment $m$
-(compare ref \citenum{Fasshauer13}).
-
-In this work we evaluate the secondary energies and decay widths with
-the programme HARDRoC\cite{HARDRoC,fasshauer2014} using the
-experimental ionization energies of Table \ref{tab:valence}
-and data from the literature given in Tables II and III.
-This choice is identical to the one made in ref \citenum{Fasshauer13}.
-
-%\input{structures}
-\section{Cluster Structures}
-
-From the experimental results we can obtain two hints for the cluster
-structure: the minimum size and the xenon content. In the following we will 
-use these to construct representative cluster structures, for which we will 
-simulate the ICD and ETMD spectra. At this point we put in a variety of
-structures, in order to learn about general structure-spectrum relations
-and therefore being able to
-exclude some of them by comparison of
-the ICD and ETMD spectra to the experimental ones.
-
-In our previous study\cite{Fasshauer13} the ArXe clusters were assumed
-to be large, having more than 1500 atoms. The model structures assumed
-an fcc structure and not an icosahedral structure, which is energetically
-favoured for small clusters.
-Most estimated cluster sizes given in Table \ref{tab:cluster} are much smaller.
-We use the estimated number of atoms for a pure Ar expansion as the lower limit for the actual cluster size and start our search for model structures from there.
-%
-%Additionally,
-%the expectation value for the number of xenon atoms relies on a pure
-%xenon gas. Since the xenon content in the mixed gas is much lower, also
-%the number of xenon atoms can be expected to be by far less. We therefore
-%start from the estimated number of atoms in the cluster after expansion
-%of pure argon gas.
-%We therefore rethink the possible cluster structures.
-%Furthermore, the theoretical prediction did not match the experimental results.
-%Since the spectra are strongly depending on the cluster structure as shown in
-%\cite{fasshauer2014}, the underlying structure seems not to fit and hence
-%we rethink the possible cluster structures.
-%
-For the smaller clusters measured,
-these expectation values range from \unit[3--21]{Ar atoms}. 
-The cluster sizes for expansion of a mixed gas are unknown, but
-for xenon as the second component a larger size is expected compared to a
-pure argon expansion, due to the higher polarizability
-and hence larger cohesive energy of xenon. All clusters
-contributing to the coincidence spectrum
-contain at least one xenon atom, as otherwise decay by ICD or ETMD is energetically not allowed.
-
-In a gas expansion a range of clusters sizes with different structures is produced. 
-However, for small rare gas clusters consisting of less than approximately \unit[1000]{atoms} so-called \emph{islands of stability} were found.\cite{haberland}  
-In mass spectra, clusters with mass numbers corresponding to icosahedral shapes had an abundance that was (slightly) enhanced over other sizes. 
-We therefore started from icosahedral structures and constructed mixed cluster structures by substitution of individual atoms with one or the other kind (Ar or Xe), or added individual atoms close to the desired position within a given structure.
-After that, the cluster structures were optimized using the unified force
-field implemented in the 
-Avogadro programme (version 1.1.0) \cite{Avogadro,Hanwell12} to give local
-minimum structures.
-All cluster structures are listed in Table \ref{table:theo_gammas}.
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{cluster_2_overview.pdf}
- \caption{Cluster structures composed of 13 argon atoms and two additional xenon
-          atoms on different surfaces of the argon icosahedron, varying in Xe-Xe distance:
-          (a) closest possible, (b) middle, (c) furthest away. They refer to
-          numbers 9--11 in Table \ref{table:theo_gammas}.}
- \label{figure:cluster_2_overview}
-\end{figure}
-%
-\begin{figure}[h]
- \centering
- \includegraphics[width=8.5cm]{cluster_3_overview.pdf}
- \caption{Cluster structures derived from a 55 atom icosahedral structure:
-          (a) one xenon atom on the surface, (b) six xenon atoms inside a 55 atoms cluster,
-          grouped on one side, (c) six xenon atoms distributed randomly
-          in a 55 atoms cluster. They refer to numbers 12, 18 and 19
-          in Table \ref{table:theo_gammas}.}
- \label{figure:cluster_3_overview}
-\end{figure}
-
-As discussed in the introduction, the small clusters will likely
-deviate from a core-shell structure with a xenon core surrounded
-by argon shells, as observed for large clusters.\cite{tchaplyguinearxe,Vach_1999} We therefore start from
-argon clusters of 13 or 55 atoms, and modify them in one of the following
-ways:
-%
-\begin{itemize}
- \item add one xenon atom on top of a surface / edge / vertex of
-       the argon core, with an example shown in
-       Figure \ref{figure:cluster_3_overview}a
-       (one additional xenon atom
-       on top of a surface of a \unit[55]{atom} argon core)
-       (Table \ref{table:theo_gammas}, \#6--8, \#12--14),
- \item substitute one argon atom in a surface / edge / vertex position
-       (Table \ref{table:theo_gammas}, \#15--16),
- \item substitute one or two argon atoms in the core of the argon cluster
-       by xenon atom(s) for the simulation of the core-shell structures
-       (Table \ref{table:theo_gammas}, \#1--3),
- \item add two xenon atoms on top of surfaces of a 13 atoms argon core
-       in different relative positions (see Figure
-       \ref{figure:cluster_2_overview}),
-       in order to achieve a xenon content in the cluster close to the
-       measured one (see below)
-       (Table \ref{table:theo_gammas}, \#9--11),
- \item substitute six argon atoms of a 55 atoms argon cluster by xenon
-       atoms either grouping them or distributing them througout the cluster
-       (see Figure \ref{figure:cluster_3_overview}b and c) in order to
-       achieve a xenon content in the cluster close to the measured one
-       (Table \ref{table:theo_gammas}, \#18--19).
-\end{itemize}
-
-These structures were then optimized using force field methods.
-%
-Furthermore, for comparison with the largest measured ArXe clusters, we constructed also larger core-shell structures (Table \ref{table:theo_gammas}, \#4--5).
-
-%\input{theo_results}
-\section{Theoretical Results
-\label{sec:th_results}}
-%
-%
-\begin{table}[H]
-\small
-\centering
-\caption{Structural and calculated properties of some model clusters.
-The cluster structures are characterized by the number of Ar and Xe atoms,
-and are arranged in three groups according to gross structural properties. 
-The first group contains Xe core-Ar shell systems of various
-size and relative Xe content.
-In the second group, model structures for small clusters are displayed,
-in which 1-2 Xe atoms are added at systematically varied locations
-to an icosahedric Ar clusters consisting of one or two full shells,
-or in which 1-6 Ar atoms of such cluster were replaced by Xe atoms.
-The last group contains data for calculated minimal energy structures
-of mixed ArXe clusters.\protect\cite{marques}
-The cluster structures are classified into core-shell structures (cs),
-structures with segregated xenon atoms (in) and completely mixed
-structures.
-The columns `ICD' and `ETMD' are the respective partial decay widths
-in \unit[$10^{-4}$]{eV}, and `\% ICD' gives the percentage of ICD in
-the total decay width.
-See text for details.
-\label{table:theo_gammas}
-}
-\begin{tabular}{rrrrcccccrrr}
-\toprule
-\# & \# Xe & \# Ar & Xe$_{\rm cl}$\% & str. cl. & pos. & rel. pos. & ICD   &  ETMD & \% ICD & Fig.\\ %$\Gamma_{\rm ICD,ETMD}$\\
-\midrule
- 1 &     1 &    12 &  7.7  & cs    &         &          & 0.000 & 0.000 &  -- &\\ %    0.0            \\     ArXe\_2\_1atom      
- 2 &     1 &    54 &  1.8  & cs    &         &          & 0.000 & 0.000 &  -- & \ref{figure:xe_3_in}\\ %    0.0            \\     ArXe\_3\_1atom      
- 3 &     2 &    53 &  3.6  & cs    &         &          & 0.033 & 0.167 &  16.7& \ref{figure:xe_3_in}\\ %2.006$\cdot 10^{-5}$ \\ ArXe\_3\_2atom      
- 4 &  1415 &   642 & 68.8  & cs    &         &          & 7.039 & 2.573 &  73.2& supp.\\ %9.612$\cdot 10^{-4}$ \\ ArXe\_8\_1layer     
- 5 &   561 &  3310 & 14.5  & cs    &         &          &       &       &  85  & \ref{figure:xe_6_lay5}\\ % c6l5
-
-\midrule
- 6 &     1 &    13 &  7.1  & cs    & surface &          & 0.792 & 0.000 & 100.0& \ref{figure:surf}\\ %7.922$\cdot 10^{-5}$ \\ XeAr\_2\_surface    
- 7 &     1 &    13 &  7.1  & cs    & edge    &          & 0.013 & 0.000 & 100.0&\\ %1.320$\cdot 10^{-6}$ \\ XeAr\_2\_edge       
- 8 &     1 &    13 &  7.1  & cs    & vertex  &          & 0.050 & 0.000 & 100.0&\\ %5.013$\cdot 10^{-6}$ \\ XeAr\_2\_vertex     
- 9 &     2 &    13 & 13.3  & cs    &         & closest  & 0.101 & 0.151 &  40.1& \ref{figure:2tops}\\ %2.523$\cdot 10^{-5}$ \\ XeAr\_2\_2top       
-10 &     2 &    13 & 13.3  & cs    &         & middle   & 0.159 & 0.008 &  95.4& \ref{figure:2tops}\\ %1.665$\cdot 10^{-5}$ \\ XeAr\_2\_2midtop    
-11 &     2 &    13 & 13.3  & cs    &         & furthest & 0.159 & 0.002 &  98.9& \ref{figure:2tops}\\ %1.605$\cdot 10^{-5}$ \\ XeAr\_2\_2endtop    
-12 &     1 &    55 &  1.8  & cs    & surface &          & 0.064 & 0.000 & 100.0& \ref{figure:surf}\\ %6.371$\cdot 10^{-6}$ \\ XeAr\_3\_surface    
-13 &     1 &    55 &  1.8  & cs    & edge    &          & 0.048 & 0.000 & 100.0&\\ %4.791$\cdot 10^{-6}$ \\ XeAr\_3\_edge       
-14 &     1 &    55 &  1.8  & cs    & vertex  &          & 0.027 & 0.000 & 100.0&\\ %2.701$\cdot 10^{-6}$ \\ XeAr\_3\_vertex     
-15 &     1 &    54 &  1.8  & in    & edge    &          & 0.077 & 0.000 & 100.0&\\ %7.708$\cdot 10^{-6}$ \\ XeAr\_3\_edge\_in   
-16 &     1 &    54 &  1.8  & in    & vertex  &          & 0.053 & 0.000 & 100.0&\\ %5.258$\cdot 10^{-6}$ \\ XeAr\_3\_vertex\_in 
-17 &     2 &    53 &  3.6  & in    &         &          & 0.117 & 0.055 &  68.1&\\ %1.711$\cdot 10^{-5}$ \\ XeAr\_3\_2in        
-18 &     6 &    49 & 10.9  & in    &         &          & 0.375 & 0.405 &  48.1& \ref{figure:ar_3_6in}\\ %7.796$\cdot 10^{-5}$ \\ XeAr\_3\_6in        
-19 &     6 &    49 & 10.9  & mixed &         &          & 0.292 & 0.674 &  30.3& \ref{figure:ar_3_6in}\\ %9.660$\cdot 10^{-5}$ \\ XeAr\_3\_6\_scat    
-                                                                                                 \midrule
-20 &     2 &    36 &  5.3  & cs    &         &          & 0.117 & 0.151 &  43.6& supp.\\                        % Ar$_{36}$Xe$_{2}$   
-21 &     4 &    34 & 10.5  & mixed &         &          & 0.248 & 0.587 &  29.7& supp.\\                        % Ar$_{34}$Xe$_{4}$   
-22 &     5 &    33 & 13.2  & mixed &         &          & 0.335 & 0.844 &  28.4& supp.\\                        % Ar$_{33}$Xe$_{5}$   
-23 &    13 &    25 & 34.2  & mixed &         &          & 0.828 & 5.414 &  13.3& supp.\\                        % Ar$_{25}$Xe$_{13}$  
-24 &    24 &    14 & 63.2  & mixed &         &          & 1.488 &16.718 &   8.2& supp.\\                        % Ar$_{14}$Xe$_{24}$  
-25 &    25 &    13 & 65.8  & in    &         &          & 1.432 & 4.995 &  22.3& supp.\\                        % Ar$_{13}$Xe$_{25}$  
-26 &    35 &     3 & 92.1  & in    &         &          & 2.017 & 7.051 &  22.2& supp.\\                        % Ar$_{3}$Xe$_{35}$   
-\bottomrule
-\end{tabular}
-\end{table}
-%
-The geometrical properties as well as the total ICD and ETMD decay widths
-of the investigated structures are shown in Table \ref{table:theo_gammas}.
-It is important to remember that the first ICD channel opens at a
-channel opening distance of \unit[7.58]{\AA}. In the smallest
-clusters with only one argon layer around each
-xenon atom, the Ar-Xe pair distances are below that value, therefore 
-no ICD can take place. Also, by definition, two Xe atoms are
-required for ETMD(3), hence it cannot occur in clusters with only one xenon atom.
-%Because secondary electrons are observed in the experimental spectra
-%we exclude all structures without any signal from our further
-%discussions.
-%
-\begin{figure}[H]
- \centering
- \includegraphics[width=8.0cm]{surf.pdf}\\
- \includegraphics[width=8.0cm]{R_comp.pdf}
- \caption{
- %
- Top panel: Simulated electron emission spectra of an Ar 3s vacancy in 
-          argon clusters
-          consisting of 13 and 55 atoms, with an additional xenon atom residing
-          on top of one of the argon surfaces.
-          Bottom panel: Distribution of Ar-Xe distances $d$ in the studied ArXe
-          clusters. The ICD channels to final states involving Xe 5p$_{3/2}^{-1}$ and 
-          5p$_{1/2}^{-1}$ vacancies open at \unit[7.58]{\AA} and
-          \unit[36.00]{\AA}, resp.; the former distance is marked by a vertical dotted line. 
-          Only pairs at longer interatomic
-          distances contribute to the electron emission spectra.
-          Larger Ar-Xe distances, as found in the larger cluster,
-          correspond to features at a higher kinetic energy of
-          the ICD electron (top panel).}
- \label{figure:surf}
-\end{figure}
-
-%In the investigated structures several different aspects have to be
-%taken into account which we will discuss separately if possible
-%on selected structures.
-
-We will now discuss features of several structures, using selected examples.
-First we consider clusters having an argon core of 13 and 55 atoms plus a single xenon
-atom on one of the surfaces (see Figure \ref{figure:cluster_3_overview}a
-for the structure of clusters with the 55 atoms core).
-Secondary electron spectra simulated for these systems are shown in Figure \ref{figure:surf}, top panel.
-%two different argon core sizes one consisting
-%of 13 and one consisting of 55 atoms with one xenon atom on one of
-%the surfaces (see Figure \ref{figure:cluster_3_overview} Panel a)
-%for the 55 atom core). The simulated secondary electron spectra are
-%shown in Figure \ref{figure:surf} Panel 1.
-
-Because the structures contain only one xenon atom, ETMD(3) is not possible, only ICD is expected. 
-%Both spectra show several smaller peaks which
-%are convoluted into one single peak with a maximum at
-%approximately \unit[0.2]{eV}. 
-%In comparison to the 13 argon atoms core
-%spectrum t
-The spectrum pertaining to the clusters with larger (55 atoms) Ar core shows
-signals at higher energies of the secondary electron. These features
-can be explained by investigating the Ar-Xe distance distributions
-in the clusters, shown
-in the bottom panel of Figure \ref{figure:surf}. 
-Every different value of the atom pair distance
-results in a different energy of the secondary electron and only pairs
-with a distance of larger than the channel opening distance
-(dashed gray line) will contribute
-to the spectrum. 
-In our model, there is a one-to-one correspondence between interatomic distance $d$ and kinetic energy of the ICD electron.
-The larger the interatomic distance, the higher is the
-kinetic energy of the secondary electron for a given channel.
-%Since the cluster with an Ar core of 55 atoms is larger, and therefore
-%contains Ar-Xe pairs with larger distances, its spectrum 
-Therefore, the spectrum of the cluster with a 55 atoms core extends to higher energies.
-%energies as well.
-This relation between ICD energy and cluster size holds true for all cluster structures.
-%This explains why the ICD spectrum for larger clusters extends to higher energies, and holds for all cluster structures.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{2tops.pdf}
- \caption{Simulated electron emission spectra of an Ar 3s vacancy in 
-          argon clusters consisting of 13
-          argon atoms with two additional xenon atoms on top of two different
-          argon surfaces. ICD and ETMD spectra are shown for three
-          different relative positions of the two xenon atoms. If 
-          the xenon atoms are close to each other, an ETMD process is
-          clearly visible. In the other two cases the spectra are dominated by
-          the ICD spectrum.}
- \label{figure:2tops}
-\end{figure}
-%
-For clusters with more than one xenon atom, also ETMD(3) is possible.
-Depending on the positions of the xenon atoms relative to each other and to the Ar core, the spectra are expected to be different.
-As an example, we discuss clusters with a core of 13 argon atoms and two xenon atoms on different surfaces. 
-Their xenon content is \unit[13.3]{\%} and thus close to the experimental one of \unit[10-12]{\%} for the lowest xenon admixture.
-The cluster structures were illustrated in Figure \ref{figure:cluster_2_overview}, simulated spectra are shown in Figure \ref{figure:2tops}.
-In all three cases, both ICD and ETMD(3) are energetically allowed. The ICD
-spectra do not change qualitatively by adding the second xenon.
-%either identical or at least very similar to the ones for
-%cluster with a single  consisting of one
-%convoluted peak at approximately \unit[0.2]{eV}. 
-However, the ETMD(3) spectra
-are very sensitive to the relative position of the two xenon atoms.
-Two aspects have to be taken into account: an energy shift of the peaks due
-to different charge distances in the final state (i.e. the interatomic Xe-Xe
-distance) and the decrease of the decay width with $R^{-6}$, $R$ being the distance
-between the electron transfer unit and the xenon atom ionized in the final state.
-The larger the distance between the xenon atoms, the higher are the energies
-of the secondary electrons and the smaller are the decay widths. 
-Therefore, a
-significant contribution from ETMD(3) compared to ICD is only
-seen if the two xenon atoms reside on two adjacent
-surfaces. 
-%{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
-The three energetically separated peaks in the ETMD(3) spectrum pertain to different combinations of the Xe 5p$_j^{-1}$ vacancy states, which have a substantial fine-structure splitting (see Table \ref{tab:valence}).
-%\ref{sec:exp_results}).
-%
-%The threefold peak structure of the ETMD(3) peak does in contrast to
-%the ICD spectrum not stem from different triple structures but from the
-%four different decay channels for one triple structure.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{ar_3_6in.pdf}
- \caption{Same as Figure \protect\ref{figure:2tops}, for clusters consisting of
-          55 atoms, 6 out of which are xenon atoms. These are either grouped
-          on one side of the cluster (label `group') or evenly distributed
-          in the cluster interior (label `scattered').}
- \label{figure:ar_3_6in}
-\end{figure}
-%
-For the 55 atoms clusters, a xenon content of \unit[10--12]{\%}
-corresponds to six xenon atoms out of a total of 55 atoms. These can form a connected 
-group in one part of the cluster or can be evenly distributed,
-as shown in Figures \ref{figure:cluster_3_overview}b and \ref{figure:cluster_3_overview}c. The
-ICD and ETMD(3) spectra for these structures are shown in Figure \ref{figure:ar_3_6in}.
-
-For both cases the overall ICD spectra are very similar, and show a maximum at a kinetic energy of approximately \unit[0.3]{eV}. 
-In case of grouped xenon atoms, the ICD spectrum extends to slightly higher energies, corresponding to ArXe pairs at slightly larger spatial distances.
-A more significant difference is observed in the ETMD(3) spectra. 
-The interatomic xenon distance is shorter in clusters, in which the xenon atoms form a connected group.
-Hence, the triple structure of the ETMD(3) spectrum is seen at lower kinetic energies. 
-Additionally, the probability for an electron
-transfer from a xenon to an argon atom decreases exponentially with the
-interatomic distance. Therefore, only those xenon atoms which have direct
-argon atom neighbours have a significant contribution to the
-total decay width, and the total ETMD(3) decay width is lower for the structure with
-grouped xenon atoms than for
-the structure with evenly distributed xenon atoms (see Table \ref{table:theo_gammas}).
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{xe_3_in.pdf}
- \caption{Same as Figure \protect\ref{figure:2tops}, for argon clusters with
-          one or two xenon atoms in the core of the cluster (55 atoms total). 
-          All ICD and ETMD channels are closed, if the cluster contains only 
-          a single xenon atom. For clusters with two xenon atoms
-          in the core, the first ICD channel is open for some pairs,
-          and additionally ETMD is possible for multiple triples. Due to a
-          different distance distribution compared to the clusters with an argon
-          core (Figure \protect\ref{figure:2tops}), 
-          the ICD peak is shifted to higher kinetic energies.}
- \label{figure:xe_3_in}
-\end{figure}
-%
-For comparison with the previous assumptions of a xenon core surrounded
-by argon atoms we investigated clusters of 13 and 55 atoms with one or two
-xenon atoms in the core. Some of the corresponding
-spectra are shown in Figure \ref{figure:xe_3_in}.
-
-%For the clusters with only one xenon atom in the core and the ionization
-%energies used for the simulation of the secondary electron energies
-%all ICD channels are closed. Since the cluster contains only one xenon atom,
-%an ETMD(3) is not possible. Hence there is no signal to be expected at all.
-For a core consisting of two xenon atoms both an ICD and an ETMD(3) spectrum
-can be seen. Compared to the cluster structures involving an argon core, the ICD peak is
-shifted to higher ICD electron energies. 
-Additionally, the ICD and ETMD(3) spectra overlap.
-For ETMD(3), only three of the four different decay channels are
-energetically allowed.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{c6l5.pdf}
- \caption{Same as Figure \protect\ref{figure:2tops},
-          for a large cluster consisting
-          of a xenon core of 561 atoms surrounded by five complete layers of
-          argon atoms (Xe content: 14.5\,\%) for both an icosahedral and
-          cuboctahedral basic structure.
-          The ICD and ETMD peak overlap such that the ETMD peak
-          is unlikely to be visible.}
- \label{figure:xe_6_lay5}
-\end{figure}
-%
-In the first experiments very large argon-xenon clusters of 
-$\approx 4380$ atoms with a xenon content of \unit[19]{\%}
-were measured,\cite{Mucke_phd}
-which we in one example approximate by a cluster consisting of 561 xenon
-atoms surrounded
-by five layers of argon atoms (3871 atoms in total). In order to take the
-better stabilization of charges in larger clusters into account, the
-ionization energies of the XL clusters (see Table \ref{tab:valence})
-were used.
-The spectra are shown in 
-Figure \ref{figure:xe_6_lay5}.
-
-Compared to the small clusters with a xenon core in Figure \ref{figure:xe_3_in}
-the ICD peak is broadened and shifted to higher ICD electron energies which is
-expected due to the larger interatomic Ar-Xe distances in the large cluster and
-the better stabilization of charges, which is relevant mostly for the final state, but also the initial state.
-The ETMD(3) peak is shifted to slightly higher energies as well. This allows opening of the
-fourth decay channel, pertaining to Xe 5p$_{1/2}^{-1}$ Ar 3p$_{1/2}^{-1}$ final states.
-
-We also note that the percentage of decay via ICD is practically
-independent of the Xe content for large clusters with a Xe core, Ar shell structure.
-This can be expected, as both decay processes are most pronounced for the
-atoms in the interface region of the xenon core and the argon shell.
-The ETMD(3), depending on the electron transfer from one xenon atom to the
-initially ionized argon atom, and hence on the corresponding orbital overlap,
-is purely an interface effect that involves the argon atoms with direct xenon
-neighbours, and the two xenon layers closest to the argon shell.
-The ICD has a stronger long range character, due to which the description
-of decays with partners of at least twice the smallest channel opening
-distance is necessary for clusters. However, the bigger the clusters are,
-the more homogeneous does the interface region become for clusters of
-different sizes. This manifests itself in the distribution of relevant
-Ar-Xe pair distances (compare Figure \ref{figure:surf}, lower panel).
-As a consequence, the ICD spectra of two large clusters of different size
-hardly differ.
-
-\clearpage
-
-%\input{exp_results}
-\section{Experimental Results}
-\label{sec:exp_results}
-%
-%
-\begin{table}
-\caption{Properties of the outer valence spectra of mixed ArXe clusters. 
-Spectra of pure Ar and Xe clusters are included for reference. 
-All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV). 
-Binding energies $\EB$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit. 
-The average Xe content of the cluster ensemble, Xe$_{\rm cl}$, was determined from the areas of the respective photolines, corrected by their atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}.
-Uncertainties are estimated as $\pm$3\,\% for the Xe content and 0.05~eV for the binding energies. 
-The row labelled `(th.)' gives the binding energies used in the simulations of this paper, and the last row their atomic counterparts. 
-Values for Ar 3p in the last row refer to the fine structure states.
-\label{tab:valence}}
-\begin{tabular}{ l c c c c c c c c}
-%
-\toprule
- \multicolumn{2}{r}{size} &  Xe$_{\rm in}$& $\EB$ (eV)& $w$ (eV)& \multicolumn{2}{c}{$\EB$ (eV)}  & $w$ (eV) &  Xe$_{\rm cl}$ \\
-%
- \multicolumn{2}{r}{(label)}&  (\%) & Ar 3p & Ar 3p & Xe 5p$_{1/2}$ &  Xe 5p$_{3/2}$ & Xe 5p$_{3/2}$  &  (\%) \\
-\midrule
-% Ar, from Marko
- Ar & (1) &&  15.3  &  1.1 & & & &  \\
-% Ar, from Marko 
- Ar & (2) &&  15.1  &  1.3 & & & &  \\
-%
-%  columns in the following: energies c.g. 51-plt-oval, widths Marko Diss., Xe content Marko Diss
-% 1103 676, 679
- ArXe & S &1.2 & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
-% 1103 670
- ArXe & M &1.2 & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
-% 1103 671
- ArXe & L &1.2 & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
-% 1103 663
- ArXe & S &3.0 & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
-% 1103 640
- ArXe & M &5.0 & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
-% 0506 
- Xe &  & & & & 12.76 & 11.19 & 1.18 & 100\\
-%
-\midrule
-%
-%  1004  886  (UHe, c.g. + roi values)
- ArXe & XL &2.5 & 15.15 & 1.3 & 12.59 & 11.01 & 1.24 & 19\\
-%
-\midrule
-% Date: Wed, 20 Jan 2016 11:27:39, From: Elke Fa?hauer <elke.fasshauer@uit.no>
- Ar, Xe & (th.) && 15.3 && 13.0 & 11.5 &&\\
-%
- \multicolumn{2}{l}{(atomic)\cite{velchev,sansonetti}} && 15.76|15.94 && 13.43 & 12.13 &&\\
-%
-\bottomrule
-\end{tabular}
-\end{table}
-
-\subsection{Outer valence spectra}
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_oval_1.pdf}
- \caption{
-Outer valence photoelectron spectra of mixed Ar-Xe clusters, in comparison to the pure species. 
-(a) shows the outer valence region of homogeneous Ar and Xe clusters, respectively (see text for details). 
-The two lower panels show spectra of the mixed species with different mean size. 
-Sharp lines marked `m' (for `monomer') result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states. 
-Labels in (b) and (c) give the Xe content in the expanding gas mixture (Xe$_{\rm in}$), which is lower than the Xe content observed in the heterogeneous clusters (Xe$_{\rm cl}$). 
-The photon energy was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
-%{\color{red}{Die Stabilisierung der Xe-bulk Atome ist in den gemischten Cluster
-% höher als in den gemischten Clustern. Das ist ungewöhnlich. Habt ihr hier
-% verschiedene CLustergrößen?}}
-}
- \label{figure:oval1}
-\end{figure}
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_oval_2.pdf}
- \caption{
-Outer valence photoelectron spectra of mixed Ar-Xe clusters from gas mixtures with different Xe concentration. 
-For better visibility, a scaling factor is applied to the Xe part of the spectrum in panel (a).
-See Figure \ref{figure:oval1} and text for details.
-}
- \label{figure:oval2}
-\end{figure}
-
-Figure \ref{figure:oval1} shows the outer valence spectra of small and large ArXe clusters, compared to clusters of the pure gases. 
-Qualitatively similar spectra have been published without detailed discussion in ref \citenum{lindblad}.
-Differences are seen in particular for the Ar component. 
-In pure Ar clusters, outer valence photoionization leads to a broad band, caused both by spin-orbit coupling and crystal field splitting. 
-The relative importance of these two mechanisms remains under debate.\cite{hergenhahnprb,rolles,foerstel_arg1_2010} 
-For larger clusters (e.g.
-$\langle N\rangle = 190$, black trace), the maximum at low binding energies becomes more pronounced, and is identified with emission from the cluster interior.\cite{hergenhahnprb,rolles}
-At the particular photon energy selected here, atop of this band a sharp feature is also visible (in Figure \ref{figure:oval1} at a kinetic energy of about 1.8 eV).
-For larger clusters (above $\langle N\rangle \approx 100$), over a range of photon energies of about 3 eV, its appararent binding energy changes in a way which is reminiscent to photoemission of crystalline bulk matter (`dispersion').\cite{foerstel_arg1_2010,foerstel_arg2_2011}
-
-Ar 3p spectra of the smaller mixed clusters (Figure \ref{figure:oval1}c, Figure \ref{figure:oval2}) show neither of these traits.
-Rather, the Ar band is symmetric, less wide than in the pure clusters and at a higher binding energy.
-Even for very large clusters (Figure \ref{figure:oval1}b) the asymmetry of the 3p band and the `dispersing feature' do not appear.
-We characterize the spectral shape by giving a single value for the Ar 3p binding energy, and the FWHM of the feature.
-Values for different expansion parameters, and for both Ar and Xe valence lines, are collected in Table\ \ref{tab:valence}.
-
-We find experimentally that clusters we have produced have a Xe content Xe$_{\rm cl}$ between 10\,\% and 50\,\%.
-A slight decrease of the binding energy with cluster size is seen for all outer valence lines, and is attributed to a larger final state polarization energy in larger clusters.
-
-For further interpretation of the shape of the Ar peaks we refer to photoemission spectra of condensed Ar monolayers, measured in several settings.\cite{jacobi,jacobi2}
-Spectra were reported for physisorption of Ar on two different metal single crystal substrates, and for Ar atop of a Xe spacer layer adsorbed on the metal.
-While the binding energy depends on the substrate, the spectral shape is very similar in all cases. 
-Most spectra were recorded for emission along the surface normal, and show a double peak split by about 0.5 eV, leading to a structure with $w$ about 1 eV.
-Although the splitting is larger than the gas phase fine structure split of 0.18 eV, the pertaining states have been assigned to Ar 3p$_{1/2}$ and 3p$_{3/2}$.
-A crystal field splitting of the 3p$_{3/2}$ state has been assumed to be also present, but with a smaller value of 0.1-0.2 eV, approx.\cite{jacobi2} 
-The spectrum clearly changes when going to an emission angle of 40$^\circ$ with respect to the surface normal (Figure 2 in ref \citenum{jacobi2}).
-The higher binding energy peak significantly loses in intensity, and the spectrum is now dominated by a single peak comprising both crystal field split substates of Ar 3p$_{3/2}$, with a FWHM ($w$) of only 0.4 eV.
-As our measured spectrum is comprised of contributions recorded under all emission angles with respect to the cluster surface, grazing emission will be the rule.
-We therefore believe that the arguments given above make it plausible that only a single peak is observed in all our spectra.
-
-Emission from the Xe 5p state shows a much larger fine structure splitting then from the Ar 3p state; it dominates the spectrum even in clusters (where other broadening mechanisms are also present).
-The shift of the cluster bands with respect to the monomer lines in the largest mixed clusters we have probed (Figure \ref{figure:oval1}b) are similar to the ones in the pure Xe spectrum, the scaling law size of which is at somewhat more than five filled shells.
-This indicates an approximate upper limit for the size of the Xe core in our mixed clusters, as their binding energy shift might be somewhat higher than the one in pure clusters, due to polarization of covering Ar layers.
-Xe cluster features in the spectra of mixed clusters appear less asymmetric than the pure Xe spectrum, and also less asymmetric as some the ArXe spectra shown in ref \citenum{lindblad}.
-This might be caused by the difference in photon energy ($h\nu = 90$ eV in ref \citenum{lindblad} and for the pure Xe spectrum, $h\nu = 32$ eV for the mixed ArXe spectra in this work).
-% For the mixed clusters, the Xe band broadens and shifts towards lower binding energy for larger size clusters.
-%For pure Xe clusters, an asymmetry observed in the Xe 5p$_{3/2}$ part has no counterpart in the respective spectra from the mixed clusters.
-%This might be caused by the difference in photon energy, as can be seen from a comparison to literature spectra (ArXe at $h\nu = 90$ eV in ref \citenum{lindblad}, Xe at $h\nu = 20$ eV in ref \citenum{rolles}).
-%For the largest clusters, the nominal size yielded from the jet parameters applied to a pure Xe expansion would correspond to clusters in which bulk atoms far outweigh those on the surface.
-%At least for the 5p$_{1/2}$ photoelectron line, this would be seen as a clear asymmetry towards the low binding energy side, which is not observed in our spectra.
-
-In Figure \ref{figure:oval2}, we compare the outer valence spectra of clusters with similar expansion conditions, but different composition of the gas mixture.
-A Xe-rich mixture obviously leads to clusters with more intense Xe photolines, but besides that the main change consists in a narrowing of the Ar band.
-A comparison with the Ar monomer features (clipped in the Figure) also shows an increased degree of condensation for the Ar gas in the expansion.
-
-For the smallest clusters we have produced, a possible model is provided by calculated minimum energy structures of Ar$_N$Xe$_{38-N}$ (Figure 7 in ref \citenum{marques}).
-We there see that for a Xe content of less than 60\,\%, core-shell systems are {\it not} formed, and although the Xe atoms tend to connect, the degree of Ar-Xe mixing is large.
-While for low Xe content (approx. 10\,\%), some Ar atoms have only Ar nearest neighbours, for larger Xe content all Ar atoms seem to see both Ar and Xe nearest neighbours.
-We believe this leads to the Ar 3p narrowing pointed out above.
-For Figure \ref{figure:oval2}, possibly, some clusters of our ensemble already are in the core-shell regime, which would lead to an even lower 3p width.
-
-For the largest clusters we have produced (Figure \ref{figure:oval1}b), the low binding energy of the Xe lines and the broadening of the Ar feature without appearance of the `bulk Ar'-maximum, supports formation of a Xe core covered by at least two layers of Ar.
-If the scaling law size for a pure Ar expansion is taken as the lower limit for the cluster size, from the observed Xe content we arrive at clusters composed of a Xe core with four layers, covered by three layers of Ar (see Supporting Information).
-
-Finally, comparing Figure \ref{figure:oval2} to Figure \ref{figure:oval1} reveals that much larger changes in the valence emission spectra occur by changes in size than by changes of the (relative) Xe content.
-This finding is supported by the spectra shown in ref \citenum{lindblad}.
-%
-%
-\subsection{Inner valence spectra}
-%
-We now focus on the Ar inner valence (3s) vacancy states. 
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.8cm]{figure_ival.pdf}
- \caption{
-Photon excited electron spectra of mixed Ar-Xe clusters in the inner valence region.
-Symbols show the Ar 3s photoline from clusters (`cl') and uncondensed Ar monomers (`m'), atop of a background resulting from inelastic intracluster scattering of outer valence photoelectrons (`excitonic satellites').\protect\cite{hergenhahn2002}
-The photon energy was $h\nu = 32$ eV.
-Panel (a) shows all electrons accumulated.
-For the same conditions, in panel (b) we only show electrons that were detected in coincidence with a secondary electron of lower kinetic energy.
-The black solid trace in (a), and red solid trace in (b) result from a least squares fit to the cluster part of the spectrum. 
-The red solid trace in (a) is the fit shown in (b), divided by the detection efficiency of the spectrometer of 0.6.
-Panels (c) and (d) show the same type of data for smaller clusters with a lower Xe content.
-See text for details.
-\label{figure:ival}
-}
-\end{figure}
-
-Figure\ \ref{figure:ival} shows the Ar part of the inner valence spectrum for representative ArXe clusters. 
-The total photoelectron signal looks similar to literature spectra for pure Ar clusters.\cite{feifel,zhang} 
-A low energy tail seen for the Ar 3s monomer line results from the transmission properties of the electron spectrometer, together with the strongly positive angular distribution parameter of this line.\cite{zhang,kruit}
-The Ar 3s cluster line shows no splitting into bulk and surface components, different to the literature on pure clusters but in agreement with our discussion of the outer valence spectra. 
-The binding energy of the cluster line has values between 28.85 and 28.70 eV for all cluster ensembles with size label S-L, and 28.67 eV for the largest clusters measured. 
-A small, but systematic decrease of the binding energy is observed when the cluster size is increased. 
-The value assumed in the simulations is 28.7 eV.
-
-If we produce a spectrum only from those electrons recorded as part of a two-electron coincidence (electron pair with kinetic energies ($e_1,e_2$)) the apparent intensity drops (compare panel b to a, and d to c in Figure \ref{figure:ival}).
-This can partly be attributed to the finite detection efficiency of the spectrometer. 
-Moreover, the monomer part of the Ar 3s signal completely disappears, as 3s photoionization of an uncondensed Ar atom in the gas jet cannot lead to emission of a second electron. 
-Further features of these diagrams and the least squares fits shown in the Figure are discussed below.
-%
-%
-\subsection{ICD/ETMD spectra}
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_icd_12.pdf}
- \caption{
-Energy spectrum of all coincident secondary (ICD or ETMD) electrons of kinetic energy $e_2$ pertaining to primary electrons of kinetic energy $e_1$ in the Ar 3s binding energy region. 
-Spectra were recorded with a photon energy of $h\nu = 32$~eV. 
-Black error bars show the data points for the smallest clusters measured (`S'), two larger clusters sizes are shown by the red and blue traces. 
-Error bars for the latter are smaller than the ones shown and have been omitted.
-For better comparison, all spectra are shown area-normalized. 
-}
- \label{figure:icd_12}
-\end{figure}
-%
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_icd_l.pdf}
- \caption{
-Energy spectrum of all coincident secondary (ICD or ETMD) electrons, kinetic energy $e_2$, for clusters of the same size, but from gas mixtures with different Xe concentration.
-See Figure \protect\ref{figure:icd_12} for details.
-}
- \label{figure:icd_l}
-\end{figure}
-%
-In Figure \ref{figure:icd_12}, we show the spectra of ICD/ETMD electrons pertaining to emission of an Ar 3s cluster photoelectron. 
-Due to their low kinetic energy, without use of a coincidence method they could hardly be separated from the background of inelastically scattered photoelectrons.\cite{mucke}
-This and the following Figure constitute the central experimental result of the article.
-Spectra recorded at $h\nu = 34$ eV as a cross-check quantitatively agree to those shown here.
-This underpins our assignment of this intensity to an autoionization process.
-Further details on the data acquisition and analysis methodology, as well as the 34~eV spectra, are given in the Supporting Information.
-
-Spectra for the three different cluster sizes in Figure \ref{figure:icd_12} are significantly different: Spectra for the larger clusters acquire more intensity in the 1-1.5 eV region and have less intensity for energies below 0.5 eV.
-In contrast to that, the ICD/ETMD spectrum hardly varies when the composition of the expanding gas mixture, and with that the relative Xe content of the clusters, is changed (Figure \ref{figure:icd_l}).
-The full set of ICD/ETMD spectra is shown as Supporting Information.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_eff.pdf}
- \caption{
-Efficiency of the decay of Ar 3s ionized states in ArXe clusters by emission of a secondary electron via ICD or ETMD.
-Values are arranged by Xe content of the initial gas mixture (`+' symbols: 1.2\,\%, asterisk: 3\,\%, triangle: 5\,\%).
-Symbol sizes indicate the photon energy (large symbols: 32 eV, small: 34 eV), and color indicates the cluster size (black symbols: S, red: M, blue: L).
-See text for details.
-}
- \label{figure:eff}
-\end{figure}
-%
-We now discuss which fraction of Ar 3s vacancy states relaxes via ICD or ETMD.
-A method to derive this information has been established by some of us.\cite{foerstel_2013}
-Briefly, we correct the intensity of the Ar 3s photoline in the coincident spectra by the detector efficiency, and divide it by the total (coincident and non-coincident) Ar 3s intensity.
-The result gives the branching ratio of decay via ICD/ETMD vs. the sum of all channels, including those not involving electron emission.
-(If all Ar 3s vacancies decay by emission of another electron, the coincident and non-coincident count rate differ only by the probability for the spectrometer to actually detect the secondary electron.
-This figure has been determined as 0.6 for this data set, in the same way as discussed earlier.\cite{mucke_review})
-To arrive at quantitative results, we have performed least squares fits of the non-coincident and coincident $e_1$ spectra.
-The fits assumed one or two Gaussian peaks, resp., atop of a background modelled by two more Gaussian curves with very large widths.
-The peak pertaining to the Ar 3s cluster photoline, with the background added, is shown by the black solid trace in Figure \ref{figure:ival}a and red solid trace in Figure \ref{figure:ival}b.
-Moreover, the line labelled `c.fit/det.' shows the fit to the coincident events, corrected by the detection efficiency, and plotted atop of the non-coincident intensity. 
-This virtually agrees with the fit to the total spectrum in Figure \ref{figure:ival}a, but not in \ref{figure:ival}c. 
-The corresponding figure for the ICD/ETMD efficiency comes out as one for \ref{figure:ival}a, and significantly smaller than one for \ref{figure:ival}c.
-Figure \ref{figure:eff} shows all results of this analysis.
-The error in the autoionization efficiency shown is mainly determined by uncertainties in the peak/background separation.
-%(Our choice for the background shape is shown in Figure \ref{figure:ival}.)
-For the gas mixture with a Xe$_{\rm in}$ of 1.2\,\%, we therefore show results from fits using two different choices of the background shape in Figure \ref{figure:eff}.
-Statistical errors are much smaller than the differences between the pairs of values arrived at such.
-
-We found an Ar 3s autoionization efficiency which, for clusters with the lowest Xe content (Xe$_{\rm cl}$ approx.
-10-12\,\%), is smaller than unity, and further decreases with decreasing cluster size.
-For larger Xe$_{\rm cl}$, the values are compatible with unity, within the accuracy of our experiment.
-
-%\input{theo_discussion}
-\section{Discussion
-\label{sec:discussion}}
-%
-%We have discussed the experimental spectra in Section \ref{sec:exp_results} and
-%the expected features of spectra for different cluster types in
-%Section \ref{sec:th_results}. In this section we combine the experimental and theoretical
-%results in order to determine the structure of the noble gas clusters.
-%
-%The simulated secondary electron spectra for the xenon core structures
-%(see Figure \ref{figure:xe_3_in})
-%show an ICD peak at higher energies than those structures with added xenon
-%atoms on the surface. This does not fit to the experimentally determined
-%spectra and hence we consider an argon core to be more probable for the
-%small measured clusters.
-%
-%The experimental spectra in Figure \ref{}
-%show a broadening of the secondary electron peak with increasing
-%pressure (?) and hence cluster size just as can be expected from
-%the theoretically simulated spectra in Figure \ref{figure:surf}.
-%
-%From the theoretical simulations of larger small clusters
-%having the same xenon content as experimentally observed a clearly
-%visible ETMD peak is to be expected as shown in Figure \ref{figure:ar_3_6in}.
-%However, the experimental spectra do not show a signal in the energy
-%region of \unit[1.5--6.5]{eV}. From this we conclude that the clusters
-%measured were smaller than 55 atoms containing only very few xenon atoms.
-%Additionally, if the cluster contains more than one xenon atom, they are
-%not expected to be close because of an otherwise visible ETMD peak
-%(compare Figure \ref{figure:2tops}).
-%
-%The large clusters with a large xenon content can be expected to have
-%a xenon core being surrounded by argon layers and hence, both ICD and
-%ETMD should be visible in the spectrum. Unfortunately, the ICD and ETMD
-%peaks overlap such that the two processes can not be distiguished.
-%
-We now would like to interpret our experimental findings in view of the simulated results described in Section `Theoretical Results'.
-Figure \ref{figure:eff} shows that for Ar 3s$^{-1}$ states autoionization by either ICD or ETMD is the only mode of relaxation, except for the clusters with the smallest Xe content.
-We consider this a remarkable result, because ICD of these states is only possible with a Xe atom in the second coordination shell of the decaying Ar vacancy (or shells even further apart), which significantly slows down the ICD process.
-Also decay rates for ETMD were found to be small in early studies of this effect.\cite{zobeley}
-Nevertheless, even in this situation the non-local autoionization channels foreclose radiative decay.
-
-% lowest kinetic energy is the first point of energy raster for t-E code of 52-proc-spec
-Structurally, all experimental ICD/ETMD spectra have a maximum at or near the lowest kinetic energy that could be measured (50~meV), and decrease in intensity to less than half for kinetic energies already below one eV.
-Qualitatively, this shape fits to the ICD contributions in the autoionization spectra discussed in the `Theory' section, but not to the ones from ETMD. 
-The calculated ETMD spectra have a typical three-fold structure with peaks between 3.5-5~eV, 1.5-2.5~eV and around 0 eV kinetic energy. 
-The former two features seem not to be present in the experimental spectra. 
-Due to restrictions in the detector electronics, electron pairs with very similar kinetic energy cannot be detected. 
-The highest kinetic energy for an autoionization electron that can be detected in coincidence with a photoelectron of $\sim3.5$~eV ($h\nu = 32$~eV) is around 2.5~eV.
-Very weak intensity is observed at this energy, and also at higher $e_2$ energies that can be probed at $h\nu = 34$~eV (Supporting Information).
-
-As a cross-check for our theoretical methods we have calculated the radiationless decay spectrum of Ar 3s$^{-1}$ in ArKr, which may arise {\it only} from ETMD(3),\cite{foerstel} and arrived at qualitative agreement with the experimental data.\cite{arkr}
-
-The size-dependent trend within the experimental data is in qualitative agreement to the change in the calculated spectral shape for ICD in systems of increased size (compare Figure~\ref{figure:2tops} to \ref{figure:xe_3_in} and \ref{figure:xe_6_lay5}.)
-
-We are therefore lead to the conclusion that the autoionization spectra we incur are dominated by ICD to non-nearest neighbour atoms, while the intensity of the ETMD channel is low. 
-We would like to recall the factors that lead to a propensity for decay via one or the other mechanism, which have been discussed in the `Theoretical Results'-section.
-For ETMD to occur with a measurable rate, two Xe atoms have to be present in the vincinity of the decaying Ar atom (Figure \ref{figure:2tops}).
-Should that be the case for a large part of the Ar atoms in some cluster structure, ETMD can even dominate over ICD (Figure \ref{figure:ar_3_6in} and Supporting Information).
-Model structures shown in Figures \ref{figure:2tops} and \ref{figure:ar_3_6in} have a Xe content similar to the lowest one probed in our experiment ($\sim$11\,\%).
-For a higher Xe content, ETMD will always dominate the spectra if the two species are given the chance to mix, as e.g.
-in the calculated minimum energy structures of $N=38$ ArXe clusters (Supporting Info).
-On the other hand, in core-shell systems decay via ETMD is probable only for Ar atoms in the interface layer, as this mechanism requires some wavefunction overlap between Ar and one of the Xe atoms involved.
-For the core-shell systems we have investigated, the likelihood of decay via ETMD stays below 25\,\% even for a Xe content above 50\,\% (Table \ref{table:theo_gammas}).
-
-In summary, the two structural motifs that can best be reconciled with our experimental data are
-\begin{enumerate}
-	\item small clusters containing only few Xe atoms that are spread out to distant positions on the cluster surface, and
-	\item systems with a compact Xe core and Ar outer layers.
-\end{enumerate}
-These structures are compatible with the findings of Lindblad {\it et al.}\ from core level photoelectron spectroscopy, who proposed the former structure for the smallest clusters in their study, and the latter for larger ones.\cite{lindblad}
-As even in these two cases intensity for decay via ETMD would not vanish completely, we have to leave it open though whether other mechanisms are present, which further suppress ETMD vs. ICD.
-
-While in early work on ICD it has almost been a paradigm that the decay involves two {\it neighbouring} atoms or molecules,\cite{hergenhahn_review} more recently significant intensity for non-nearest neighbour ICD has been found also in other systems.
-One example is Ne-Ar after Ne 2s ionization, where decay to Ar in the second coordination shell is clearly visible despite the fact that in this system decay involving nearest neighbours is energetically allowed.\cite{fasshauer2014}
-A further theoretical delineation of the respective factors has recently been presented by one of us.\cite{fasshauernjp}
-
-%\input{summary}
 \section{Summary}
@@
 over the surface.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The "Acknowledgement" section can be given in all manuscript
-%% classes.  This should be given within the "acknowledgement"
-%% environment, which will make the correct section or running title.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{acknowledgements}
-\begin{acknowledgement}
-%
-We thank HZB for the allocation of synchrotron radiation beamtime, and the
-Deutsche Forschungsgemeinschaft for funding via the Forschergruppe 1789.
-E. F. gratefully acknowledges the Research
-Council of Norway through a Centre of Excellence Grant (Grant No.\ 179568/V30)
-for funding.
-%
-\end{acknowledgement}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The same is true for Supporting Information, which should use the
-%% suppinfo environment.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{suppinfo}
-
-%This will usually read something like: ``Experimental procedures and
-%characterization data for all new compounds. The class will
-%automatically add a sentence pointing to the information on-line:
-
-%\end{suppinfo}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The appropriate \bibliography command should be placed here.
-%% Notice that the class file automatically sets \bibliographystyle
-%% and also names the section correctly.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliography{arxe}
-
-\end{document}

### 2019-03-22 resubmit_2/suppl.tex
submitted files

--- 2016-06-05 suppl.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author{Elke Fasshauer}
-\affiliation[UIT]{Centre for Theoretical and Computational Chemistry,
-Department of Chemistry, University of Troms\o
--- The Arctic University of Norway, N-9037 Troms\o, Norway}
 \author{Marko F\"orstel}
@@
 \affiliation[IPP]{Max-Planck-Institute for Plasma Physics, Boltzmannstr. 2, 85748 Garching, Germany}
+\author{Markus Pernpointner}
+\affiliation[University of Heidelberg]{Theoretical Chemistry, University of Heidelberg,
+              Im Neuenheimer Feld 229, D-69120 Heidelberg, Germany}
 \author{Uwe Hergenhahn}
@@
 \alsoaffiliation[IPP HGW]{Max-Planck-Institute for Plasma Physics, Wendelsteinstr. 1, 14791 Greifswald, Germany}
+\author{Elke Fasshauer}
+\affiliation[UIT]{Centre for Theoretical and Computational Chemistry,
+Department of Chemistry, University of Troms\o
+-- The Arctic University of Norway, N-9037 Troms\o, Norway}
 
@@
 \title[ArXe]
-  {Long-range Interatomic Coulombic Decay in ArXe clusters: Experiment and Theory}
+  {Long-Range Interatomic Coulombic Decay in ArXe Clusters: Experiment and Theory}
 
@@
 \input{supp_theo_specs}
+\clearpage
 

### 2019-03-22 resubmit_2/theo_discussion.tex
submitted files

--- 2016-07-04 onefolder/master.tex
@@
-	
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% This is a (brief) model paper using the achemso class
-%% The document class accepts keyval options, which should include
-%% the target journal and optionally the manuscript type.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\documentclass[journal=jpccck,manuscript=article,layout=twocolumn]{achemso}
-\documentclass[journal=jpccck,manuscript=article]{achemso}
-
-% UHe stuff
-\def\EB{E_{\rm b}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Place any additional packages needed here.  Only include packages
-%% which are essential, to avoid problems later. Do NOT use any
-%% packages which require e-TeX (for example etoolbox): the e-TeX
-%% extensions are not currently available on the ACS conversion
-%% servers.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage[english]{babel}
-\usepackage{braket}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath,amsfonts,amssymb}
-\usepackage{dsfont}
-\usepackage{booktabs}
-\usepackage{units}
-\usepackage{xcolor}
-\usepackage{multirow}
-\usepackage{tikz,pgfplots}
-\usepackage{float} %force figure position
-
-\usetikzlibrary{patterns,shadows,trees,calc}
-\usepgfplotslibrary{units}
-
-\pgfplotsset{compat=1.10}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% If issues arise when submitting your manuscript, you may want to
-%% un-comment the next line.  This provides information on the
-%% version of every file you have used.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%\listfiles
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Place any additional macros here. Please use \newcommand* where
-%% possible, and avoid layout-changing macros (which are not used
-%% when typesetting).
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newcommand*\mycommand[1]{\texttt{\emph{#1}}}
-% Define some colours
-\definecolor{diplom1}{rgb}{0.0 0.4 1.0}
-\definecolor{diplom2}{rgb}{0.0 0.0 0.6}
-\definecolor{diplom3}{RGB}{153,0,0} %unirot
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Meta-data block
-%% ---------------
-%% Each author should be given as a separate \author command.
-%%
-%% Corresponding authors should have an e-mail given after the author
-%% name as an \email command. Phone and fax numbers can be given
-%% using \phone and \fax, respectively; this information is optional.
-%%
-%% The affiliation of authors is given after the authors; each
-%% \affiliation command applies to all preceding authors not already
-%% assigned an affiliation.
-%%
-%% The affiliation takes an option argument for the short name.  This
-%% will typically be something like "University of Somewhere".
-%%
-%% The \altaffiliation macro should be used for new address, etc.
-%% On the other hand, \alsoaffiliation is used on a per author basis
-%% when authors are associated with multiple institutions.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author{Marko F\"orstel}
-\altaffiliation{Now at: Institut für Optik und Atomare Physik, Technische Universit\"at Berlin, Hardenbergstr. 36, 10623 Berlin, Germany}
-\author{Melanie Mucke}
-\altaffiliation{Now at: Department of Physics and Astronomy, Uppsala University, Box 516, 75120 Uppsala, Sweden}
-\author{Tiberiu Arion}
-\altaffiliation{Now at: Center for Free-Electron Laser Science/DESY, Notkestr. 85, D-22607 Hamburg, Germany}
-\author{Toralf Lischke}
-\affiliation[IPP]{Max-Planck-Institute for Plasma Physics, Boltzmannstr. 2, D-85748 Garching, Germany}
-\author{Markus Pernpointner}
-\affiliation[University of Heidelberg]{Theoretical Chemistry, University of Heidelberg,
-              Im Neuenheimer Feld 229, D-69120 Heidelberg, Germany}
-\author{Uwe Hergenhahn}
-\affiliation[IOM]{Leibniz Institute of Surface Modification, Permoserstr. 15, D-04318 Leipzig, Germany}
-\alsoaffiliation[IPP HGW]{Max-Planck-Institute for Plasma Physics, Wendelsteinstr. 1, D-14791 Greifswald, Germany}
-\email{uwe.hergenhahn@iom-leipzig.de}
-\author{Elke Fasshauer}
-\affiliation[UIT]{Centre for Theoretical and Computational Chemistry,
-Department of Chemistry, University of Troms\o
--- The Arctic University of Norway, N-9037 Troms\o, Norway}
-\email{elke.fasshauer@uit.no}
-%\phone{+123 (0)123 4445556}
-%\fax{+123 (0)123 4445557}
-%\alsoaffiliation[Second University]
-%{Department of Chemistry, Second University, Nearby Town}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The document title should be given as usual. Some journals require
-%% a running title from the author: this should be supplied as an
-%% optional argument to \title.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Long-range Interatomic Coulombic Decay in ArXe clusters: Experiment and Theory}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Some journals require a list of abbreviations or keywords to be
-%% supplied. These should be set up here, and will be printed after
-%% the title and author information, if needed.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\abbreviations{IR,NMR,UV}
-%\keywords{American Chemical Society, \LaTeX}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The manuscript does not need to include \maketitle, which is
-%% executed automatically.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The "tocentry" environment can be used to create an entry for the
-%% graphical table of contents. It is given here as some journals
-%% require that it is printed as part of the abstract page. It will
-%% be automatically moved as appropriate.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{tocentry}
-
-\begin{center}
- \includegraphics[height=3.5cm]{front1.pdf}
-\end{center}
-
-%Some journals require a graphical entry for the Table of Contents.
-%This should be laid out ``print ready'' so that the sizing of the
-%text is correct.
-%
-%Inside the \texttt{tocentry} environment, the font used is Helvetica
-%8\,pt, as required by \emph{Journal of the American Chemical
-%Society}.
-%
-%The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
-%permitted for  \emph{Journal of the American Chemical Society}
-%graphical table of content entries. The box will not resize if the
-%content is too big: instead it will overflow the edge of the box.
-%
-%This box and the associated title will always be printed on a
-%separate page at the end of the document.
-
-\end{tocentry}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The abstract environment will automatically gobble the contents
-%% if an abstract is not used by the target journal.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{abstract}
-
-\begin{abstract}
-We report about autoionization channels of Ar inner valence ionized states in mixed ArXe clusters and compare
-our experimental data obtained by electron-electron coincidence spectroscopy
-to our theoretical simulations for representative cluster structures.
-The combined experimental and theoretical data show that the autoionization of Ar 3s$^{-1}$ in ArXe is dominated by Interatomic Coulombic Decay (ICD) to Xe atoms in the second and higher coordination shells of the originally excited atom.
-Clusters with a range of sizes, compositions and structures were probed. 
-The Xe content in the clusters was varied between 10\,\% and 53\,\%. 
-Besides ICD, also Electron Transfer Mediated Decay (ETMD(3)) was found important in many of the calculated spectra, but is seen with less intensity in the experimental spectra. 
-From the calculations, we identify structural motifs which minimize the ETMD vs.
-the ICD rate and suggest that these are preferentially realized in our experiment, in which clusters are formed by supersonic expansion of an Ar-Xe mixture.
-Suggested cluster structures either feature a clear segregation between Ar and Xe fractions, e.g. Xe core, Ar shell systems, or contain a few Xe atoms singled out in surface sites on an Ar cluster.
-These structures differ significantly from the majority of calculated minimum energy structures for ArXe systems of 38 atoms, which might show that the latter, annealed structures are not realized in our experiment.
-We show experimentally that the relaxation of Ar inner valence states by ICD and ETMD together has an efficiency of unity, within the experimental accuracy, for all clusters except those with the lowest Xe content.
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Start the main part of the manuscript here.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{intro}
-\section{Introduction}
-%
-Electron spectroscopy can make important contributions to the 
-research on composition and structure of free nanoparticles.\cite{
-jpcc} Besides photoionization, free electrons emerging from 
-nanoparticles can also be produced by the relaxation of 
-electronically excited states. One such process, which is of 
-particular relevance in weakly bonded systems, is the 
-Interatomic or Intermolecular Coulombic Decay (ICD).\cite{
-cederbaum} In ICD, an electronic excitation decays by energy 
-transfer to one of its neighboring atoms or molecules, thus 
-releasing a free electron from the latter site. ICD is an 
-important relaxation channel e.g. for inner-valence holes in 
-atoms, and also for core level vacancies e.g. in \ce{H2O}
-, where it competes with Auger decay.\cite{slavicek}
-
-By definition, ICD is particularly sensitive to the chemical 
-environment of the atom or molecule in which the primary 
-excitation has taken place. We suggest that this property of ICD 
-decay spectra can be used to derive information on a nanoparticle 
-or a solvation system. 
-The term excitation is used here in a broader sense---in the
-systems we consider in this work, ICD occurs from an excited, singly 
-charged Ar state created by photoionization.
-In other systems, ICD was also observed from neutral excited
-states and states with more than one vacancy.
-
-We report here about studies 
-in which we produced heterogeneous clusters of the noble gases Ar 
-and Xe with different sizes, and compositions ranging from a few 
-Xe dopant atoms in an Ar matrix to clusters containing an equal 
-amount of both species. By the use of electron-electron 
-coincidence spectroscopy and of theoretical simulations on 
-prototypical systems we show how the radiationless decay spectrum 
-of Ar inner valence (3s) ionized states connects to the structure 
-of the clusters.
-
-Intermolecular Coulombic Decay initially was predicted from 
-theoretical considerations of the energy levels in singly vs.\  
-doubly ionized, and doubly vs.\ triply ionized, hydrogen bonded 
-clusters.\cite{cederbaum} First experimental work some years 
-later used Ne clusters,\cite{marburger,jahnkenedimer} but quickly 
-was followed by demonstrations of ICD in a diverse range of other 
-systems. Experimental and theoretical progress has been reviewed.
-\cite{hergenhahn_review, averbukh_review, jahnke_review} ICD 
-proceeds by an initial ionization producing an ion in an excited 
-state, followed by a transfer of energy to a neighbouring site, 
-and an electron emission process therefrom. The final state contains 
-two positive charges; one at the original site of ionization, and a second
-one at another atom or molecule.
-
-Soon after, related 
-autoionization processes were discovered that proceed via a 
-charge transfer instead of an energy transfer. 
-These were termed `Electron Transfer Mediated Decay' 
- (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
- which the originally excited site is neutralized by the decay 
-and `exchange ICD' for charge transfer contributions to the 
-normal ICD amplitude.\cite{santrarev,jahnkesat}
-We find that both energy and charge transfer induced 
-autoionization play a role in Ar-Xe, and will detail the 
-relevant processes below. The notion of ICD requires that the 
-electronic orbitals of the two sites can be distinguished, which 
-typically is the case in weakly bonded systems, held together by 
-hydrogen bonds or van-der-Waals bonds. In the case of strong
-(covalent or metallic) bonding, it is impossible to make a
-distinction between ICD and Auger decay.\cite{hergenhahn_review}
-
-Rare gas clusters are suitable prototype systems for studies of
-ICD, as they can readily be produced by supersonic 
-expansion through a cooled nozzle. 
-The size of the clusters can be changed by varying the expansion parameters.
-The formation of heterogeneous rare gas clusters by coexpansion of a gas mixture cannot {\it a priori} be taken for granted, but was experimentally shown for most combinations of two rare gases, when suitable mixing ratios and expansion parameters are used (see references throughout this article).
-
-First experiments on ICD in heterogeneous systems used Ne-Ar 
-clusters.\cite{barthnear} Those were followed by studies of 
-ICD-like inner-shell decays in aqueous solution.\cite{aziz,pokapanich,pokapanich2011}
-Pioneering work also showed the 
-potential for studies of the interface between a substrate and an 
-adsorbate by ICD.\cite{grieves} More detailed work on Ne-Ar 
-clusters was recently presented by some of the authors \cite{fasshauer2014}
-showing that an analysis of the ICD spectra
-allowed to decide between structural alternatives, for which the
-photoelectron data were indiscriminate.
-For this system, a detailed account of the
-photoelectron spectra with respect to structural features of the 
-mixed clusters is also available.\cite{lundwall}
-
-Several experimental techniques have been used for the study of mixed Ar-Xe clusters, most notably fluorescence spectroscopy, electron diffraction and photoelectron spectroscopy. 
-Early work focussed on the fluorescence of a single Xe atom 
-embedded in an Ar cluster.\cite{lengenprl}
-%Different sites of the dopant atom (on top of a surface, 
-%integrated in an Ar surface, inside the cluster) were 
-%distinguished by three separate bands in the fluorescence yield 
-%recorded as a function of excitation wavelength.\cite{goldberg} 
-Increasing the Xe concentration in the expansion lead to the formation of \ce{Xe2} and larger Xe complexes inside the clusters.\cite{lengen} 
-With increasing Xe content, the formation of Xe-core, Ar-shell systems with a sharp interface between the two species was shown in photoionization experiments.\cite{tchaplyguine,hoener}
-This finding was confirmed by electron diffraction.\cite{Danylchenko,Danylchenko07} 
-Always, the observed Xe content in the clusters is higher than the Xe content in the expanding gas mixture, as Xe can be condensed much easier than Ar.\cite{hoener,Danylchenko07}
-%A complementary study used photoelectron-photoion coincidence of
-%large Ar-Xe clusters, and found that after inner shell (Xe 4d, Ar 2p)
-%photoionization significant charge transfer between both species
-%occurs before the mass spectroscopic final state is reached.\cite{berrah}
-%
-More recently, photoelectron spectra of 
-small Ar-Xe clusters were analyzed, adding to the findings in 
-earlier work.\cite{lindblad} We will discuss this paper in 
-connection with our results below. 
-For completeness, we mention that Ar-Xe complexes can also be produced by passing clusters from a neat Ar expansion through a zone filled with Xe gas (`pick-up').\cite{pietrowski}
-Clusters produced such can structurally be quite different from those produced by coexpansion.\cite{lindbladpccp}
-
-A number of theoretical works on Ar-Xe clusters aimed at the prediction of minimum energy structures. 
-Most recently, these converged to structures which have the Xe atoms mainly in the interior.\cite{marques} 
-Xe was also found to diffuse into the interior of Ar clusters in molecular dynamics simulations after pick-up.\cite{Vach_1999} 
-The electronic energy levels of very small Ar-Xe clusters were calculated in ref \citenum{fasshauer} and the secondary electron spectra were simulated for
-model structures of one argon atom placed on a xenon surface \cite{Fasshauer13}.
-Interestingly, it was found that Ar 3s$^{-1}$ is stable 
-against autoionization in an ArXe dimer, but is destabilized by 
-adding further Xe atoms, or an Ar solvation shell, to the system, thereby allowing
-for combinations of argon and xenon atoms with larger interatomic distances. 
-Again, we will detail these results in conjunction with our 
-current work.
-
-The plan of our paper is as follows: We firstly delineate our experimental and theoretical methods. 
-Calculations were done for a number of model structures which were systematically varied, and are described in the following section.
-After that, we describe and discuss our theoretical results for the autoionization spectra of the model clusters.
-Experimental results are then shown and possible conclusions from comparing them to the calculations are given.
-Details on the experimental technique, and calculated spectra for a wider range of structures are given as Supporting Information.
-
-%\input{experimental}
-
-\section{Experimental}
-%
-\begin{table*}
-\caption{
-The expansion parameters used for cluster production. 
-Here, Xe$_{\rm in}$ is the molar fraction of Xe in the gas mixture before the expansion, $T$ is the nozzle temperature, and $p$ the stagnation pressure. 
-Experiments were performed with $d = 80~\mu$m (first two sections) and $d = 100~\mu$m (bottom section) conical nozzles of 15$^\circ$ half opening angle. 
-We basically have an Ar seeded expansion of Xe gas, as the freezing point of Ar is much lower. 
-$\langle N_{\rm Ar} \rangle$ and $\langle N_{\rm Xe} \rangle$ refer to cluster sizes for a pure Ar, or pure Xe expansion, respectively, at the given conditions, calculated from a scaling law.\protect\cite{hagena1981}
-We expect actual cluster sizes in-between these two limiting values. 
-Inaccuracies in the calculation of $\langle N\rangle$ due to fluctuations of the input parameters are less than 6\,\%. This figure does not include systematic errors of the empirical model.
-}
-\label{tab:cluster}
-
-\begin{tabular}{l c c c c r r}
-%
-\toprule
-  \multicolumn{2}{r}{size label}  &  Xe$_{\rm in}$ (\%)  &  $T$ (K)  &  $p$ (bar) & $\langle N_{\rm Ar} \rangle$ & $\langle N_{\rm Xe} \rangle$ \\
-%
-\midrule
-% Ar, from Marko 
-Ar & (1) & --- &  96.5  & 0.35  & 44  &  --- \\
-% Ar, from Marko 
-Ar & (2) & --- &  96.5  & 0.67  & 200  &  --- \\
-\midrule
-% 1103 676, 679
-ArXe & `S' & 1.2 &  174   & 0.32  & 4  &   74 \\
-% 1103 670
-ArXe & `M' & 1.2 &  174   & 0.49  & 11  &  199 \\
-% 1103 671
-ArXe & `L' & 1.2 &  174   & 0.68  & 23  &  431 \\
-\midrule
-% 1103 663
-ArXe & `S' & 3.0 &  172   & 0.28  & 3  &   57 \\
-% 1103 653
-ArXe & `M' & 3.0 &  172   & 0.51  & 12  &  233 \\
-% 1103 658
-ArXe & `L' & 3.0 &  172   & 0.68  & 24  &  458 \\
-\midrule
-% 1103 630
-ArXe & `S'  & 5.0 &  167  & 0.37  & 7  &  129 \\
-% 1103 640
-ArXe & `M' & 5.0 &  171   & 0.51  & 13  &  240 \\
-% 1103 629
-ArXe & `L'  & 5.0 &  167  & 0.68  & 28  &  537 \\
-\midrule
-% 1004 867 (32 eV)
-ArXe & `XL' & 2.5 &  154  & 2.12  & 995 & 18800\\
-\midrule
-% 0506 382, Keller offset ber?cksichtigt
-Xe &  & 100 & 183.5  & 0.68  & ---  &  615 \\     
-% 1004 868
-%868 & & 2.5 &  158   & 1.50  &  355 &  6090\\
-% 1004 886 (17 eV)
-%886 &  & 2.5 &  161   & 2.41  &  980 & 16770\\
-% 1004 858
-%858 &  & 5.0 &  149   & 2.50  & 1620 & 27700\\
-%
-\bottomrule
-\end{tabular}
-\end{table*}
-%
-%
-The apparatus used for the experiments consists of a supersonic molecular jet with a cooled nozzle, and a magnetic bottle spectrometer, which detects photoelectrons and secondary electrons produced after ionization with synchrotron radiation.\cite{arion}
-% Leave this citation in place to avoid Latex error
-A comprehensive description can be found in ref \citenum{arion}, and here we focus on details specific for the current experiment. 
-Commercialy obtained Ar and Xe gas was filled into 
-separate cylinders up to pressures suitable for producing a certain mixing ratio. The gases were then allowed to mix before the expansion. 
-Expansion parameters are given in Table \ref{tab:cluster}. 
-Similar expansion conditions are further referred by the labels `S'-`XL', as given in the Table.
-
-Prediction of the sizes of clusters from a supersonic expansion mainly rests on empirical scaling laws,\cite{hagena1981} which have been the subject of some discussion.
-Moreover, such scaling laws originally were derived only for pure gas expansions.
-A recent investigation of cluster sizes in a mixed Ar-Kr expansion yielded a revised scaling law, which essentially amounts to the use of a weighted average over the atom-specific parameters of the two gases.\cite{danylchenko2015}
-Although the analogy to our case is not complete, as phase segregation occurs in Ar-Kr to a much lesser extent,\cite{Vach_1999,lundwall_arkr} we expect scaling law cluster sizes between the values calculated for Ar and Xe.
-Recent analyses of photoionization spectra suggest that mean sizes arrived at by scaling laws are smaller than the actual size, at least for rare gas clusters in the range $\langle N\rangle < 1000$.\cite{bergersen,hergenhahnprb,foerstel_arg2_2011}
-For the expansion conditions labelled `S'-`L', we therefore expect that the scaling law estimates are a lower boundary for the actual cluster size.
-
-The expansion chamber for the supersonic jet is separated from the interaction chamber by a non-magnetic, conical skimmer with an opening of 1~mm in diameter (Beam Dynamics). 
-At few cm distance behind the skimmer, the cluster jet was crossed by synchrotron radiation from the BESSY electron storage ring at Helmholtz-Zentrum Berlin. 
-Electrons were detected by a short `magnetic bottle' time-of-flight spectrometer, that has been described earlier.\cite{mucke_review}
-Due to its large collection angle, this instrument is particularly suited for experiments that employ electron-electron coincidence detection.
-Data were recorded in two different beamtimes at the UE112-PGM-1 (small and medium sized clusters, first two sections in Table \ref{tab:cluster}) and at the TGM-4 beamline (large clusters, last section in Table \ref{tab:cluster}).
-Linearly, horizontally polarized radiation was used. 
-The storage ring was operated in single bunch conditions.
-Spectra of pure Ar clusters shown for comparison are from ref \citenum{foerstel_arg2_2011}, and a spectrum of pure Xe clusters was recorded with the set-up described in ref \citenum{hergenhahnprb}.
-
-The entrance aperture and drift tube of the magnetical bottle spectrometer can be independently biased to influence the electron flight times. 
-For the data shown here, slightly positive bias voltages were used (+1.8 V to +2.2 V) in order to have all electrons arriving at the detector within one BESSY single bunch period (800 ns). 
-The detection efficiency was determined as 0.6, with the method outlined in ref \citenum{mucke_review}.
-Data were converted from flight times to kinetic energy by measuring calibration data for atomic photolines of known binding energy.
-The systematical uncertainty of this procedure may lead to a common shift of all experimental kinetic energy data shown in this article of up to 30~meV.
-
-The high detection efficiency of the instrument is a pre-requisite for measuring two-electron emission processes, such as photoelectron emission followed by ICD or ETMD, by using electron-electron coincidence detection.
-This allows to filter the full electron spectrum for contributions arising after emission of an Ar 3s photoelectron.
-ICD/ETMD spectra presented here are based on this method, which has been explained earlier.\cite{mucke_review,Foerstel_phd}
-Technical details and full electron-electron coincidence spectra are given in the Supporting Information.
-
-%\input{theory}
-\section{Theoretical Approach}
-%
-Experimental coincidence spectra are given by the multitude of
-kinetic energies $E_{\rm sec}$ of the secondary electron
-and the intensities of the peaks. The latter is proportional to the
-probability of the decay as well as the theoretically determinable
-decay width $\Gamma=\frac{\hbar}{\tau}$,
-which is inversely proportional to the lifetime $\tau$ of the decay process.
-The manifold of the
-secondary energies and decay widths will therefore compose the electron-electron
-coincidence spectrum.
-In case of noble gas clusters
-with given geometrical structures three aspects have to be taken into account:
-different decay mechanisms, the possibility to decay with multiple
-interaction partners and different decay channels $\beta$ within
-each decay mechanism.
-At the current stage of development we need to neglect the nuclear dynamics which
-additionally might play an important role.
-
-%We are interested in describing the electron emission spectra of excited states in clusters, that where measured by the electron-electron coincidence method in our experiments. 
-%In our theoretical description, these will be composed of multiple transitions, each characterized by a kinetic energy $E_{\rm sec}$ of the secondary electrons, and the intensity of the peak.
-%The latter is proportional to the probability of the decay, represented here by the decay width $\Gamma_\beta = \hbar/\tau_\beta$, where $\tau_\beta$ is the lifetime due to the respective transition.
-%The total decay width $\Gamma$ is the sum of all partial $\Gamma_\beta$.
-%In case of noble gas clusters with a given geometrical structure, three aspects have to be taken into account:
-%different decay mechanisms, the contribution of different cluster sites to the respective decay, and the existence of different decay channels within each decay mechanism.
-%At the current stage of development we have to neglect the nuclear dynamics, which
-
-This means, for the evaluation of the decay width we are dealing with a sum over three different indices: 
-For a given structure it is most convenient to
-start with a decomposition of the system into interaction partners of
-the different relevant decay mechanisms, i.e. pairs (combination of two atoms regardless
-of their internuclear distance) for the ICD and triples (combinations of three atoms)
-for the ETMD(3).
-These atoms do not necessarily need to form bonds between each other or
-even be close, but they are characterized according to fixed internal
-coordinates. 
-Each pair and each triple leads to a decay spectrum that can be described by the energy of the secondary electron and the decay width, which is in first order of approximation independent of other atoms present in the cluster.
-In the following, this approach will be called model of pairs and triples.
-
-%Decomposing every system into pairs and triples of atoms is a very useful
-%first order approximation to both the investigation of energies and
-%decay widths of a larger system. Pairs and triples are combinations of
-%two and three atoms, respectively.
-
-In order to determine, whether a channel $\beta$ for a given geometry and decay
-mechanism is open, i.e., whether it is in accordance with energy conservation,
-knowledge of the energies of the initial and the final states, $E_{\rm in}$ and $E_{\rm fin}$, of
-the corresponding processes is necessary.
-If the channel
-is open, the excess energy is carried away by the emitted electron
-in form of its kinetic energy $E_{\rm sec}$. These energies in the model
-of pairs and triples can be approximated by
-
-\begin{align}
- E_{\rm in}        &= SIP(X_{\rm in}) \label{equation:E_in}\\
- E_{\rm fin}^\beta &= SIP(X_{D}^\beta) + SIP(X_{E}^\beta) + \frac 1d
-           \label{equation:E_fin}\\
- E_{\rm sec}^\beta &= E_{\rm in}^\beta - E_{\rm fin}^\beta \label{equation:E_sec}
-\end{align}
-where $X_{\rm in}$ denotes the initially ionized atom and
-$X_{D}$ and $X_{E}$ describe the electron donating atom and electron
-emitting atom, respectively.
-$\beta$ denotes the decay channel characterized by the quantum numbers of the ionized atoms in the pairs and triples, $SIP(X^\beta)$ the single ionization potential of vacancy $\beta$ in atom $X$ and $d$ the interatomic distance between the atoms $X_{D}$ and $X_{E}$.
-Atomic units are used.
-The initially ionized atom $X_{\rm in}$ can
-coincide with one or both of
-the final state atoms
-$X_{D}$ and $X_{E}$.
-The distribution of the vacancies over the different
-atoms determines the kind of electronic decay process at hand. Hence, in an
-Auger process all three atoms coincide, for an ICD process $X_{\rm in}$
-coincides with $X_{D}$, for an ETMD(2) process $X_D$ and $X_E$ coincide
-and for an ETMD(3) process
-all ionized states are located on different atoms.
-
-\begin{figure}[h]
- \centering
- \includegraphics[width=\columnwidth]{channel_open_ICD.pdf}
- \caption{Illustration of channel opening: Initial (Ar3s$^{-1}$)
-          and final state (Ar3p$^{-1}$Xe5p$_{3/2}^{-1}$ and
-          Ar3p$^{-1}$Xe5p$_{1/2}^{-1}$) energies
-          for ICD in ArXe pairs as a function of 
-          internuclear distance, using eq. (\ref{equation:E_fin})
-          and the experimental ionization
-          potentials given
-          in Table \ref{tab:valence}. When the final state energy is lower
-          than the initial state energy the corresponding channel
-          is open. We call the distance at which the energies are equal
-          the `channel opening distance'. If the curves do not cross, the
-          corresponding channel is closed.}
- \label{figure:channel_open_ICD}
-\end{figure}
-
-The electron emitted by autoionization has the kinetic energy $E_{\rm sec}$. 
-If the calculated value of $E_{\rm sec}$ is negative,
-the final state energy is higher than the initial state energy and the        
-process is energetically not accessible. Hence, the corresponding channel     
-is closed, as shown in Figure \ref{figure:channel_open_ICD} for the
-Ar3p$^{-1}$Xe5p$_{1/2}^{-1}$ final state. Related to
-the opening of each channel is an internuclear distance which we will call 
-\emph{channel opening distance} in the following.
-
-This {\latin ad hoc} approach allows to easily correct for energetic shifts of ionization potentials as observed in larger clusters by adding experimentally or theoretically determined energy shifts $\Delta E(X_{I}^{\beta})$ for a given vacancy $I={\rm in},D,E$ and channel $\beta$.
-This yields the working expression for the kinetic energy of the secondary electron:
-
-\begin{equation}
- E_{\rm sec}^\beta = SIP(X_{\rm in}) + \Delta E (X_{\rm in})
-               - SIP(X_{D}^\beta) - \Delta E (X_{D}^\beta)
-               - SIP(X_{E}^\beta) - \Delta E (X_{E}^\beta)
-               - \frac 1d .
-\end{equation}
-
-The total decay width $\Gamma$ is given by the sum over the decay widths
-of all decay mechanisms. In case of the ArXe clusters we only consider
-ICD and ETMD(3), because the ETMD(2) pathway is energetically not accessible:
-
-\begin{equation}
- \Gamma = \Gamma_{\rm ICD} + \Gamma_{\rm ETMD} .
-\end{equation}
-
-These are given by the sum over the decay widths of all pairs $i$ for the
-ICD and all triples $j$ for the ETMD(3), respectively, and over all channels $\beta$:
-%
-\begin{align}
- \Gamma_{\rm ICD}  &= \sum\limits_{i,\beta} N_{{\rm ICD},i}  \, \Gamma_{{\rm ICD},i,\beta},\\
- \Gamma_{\rm ETMD} &= \sum\limits_{j,\beta} N_{{\rm ETMD},j} \, \Gamma_{{\rm ETMD},j,\beta}.
-\end{align}
-Here, $N_{{\rm ICD},i}$ and $N_{{\rm ETMD},j}$ denote the number of geometrically
-equal pairs and triples in a given cluster structure. The total number of pairs
-reads
-$N_{{\rm ICD}} = N_{\rm in} \cdot N_{D/E} = N_{\rm Ar} \cdot N_{\rm Xe}
- = \sum\limits_i N_{{\rm ICD},i}$ and the number of triples is
-$N_{{\rm ETMD}} = N_{\rm in} \cdot N_{D/E} (N_{D/E} - 1) = N_{\rm Ar} \cdot N_{\rm Xe} (N_{\rm Xe} - 1)
- = \sum\limits_j N_{{\rm ETMD},j}$.
-The numbers of geometrically equivalent pairs $N_{{\rm ICD},i}$ and triples $N_{{\rm ETMD},j}$
-strongly depend on the structure of the cluster. From these relationships
-it can be seen that a higher xenon content in the cluster statistically
-favours ETMD(3) over ICD.
-
-In previous work \cite{Fasshauer13,Fasshauer_thesis} we have shown that
-the decay width for a single pair or triple for a distinct channel $\beta$
-following Wentzel \cite{Wentzel27}, Feshbach\cite{Feshbach58,Feshbach62}
-and Fano,\cite{Fano61}
-%
-\begin{equation}
- \Gamma_{\beta}(E_{\rm res}) = 2\pi \left|
-                           \braket{\Phi_{\rm in}| H_f |\chi_{\beta}}
-                           \right|^2,
-\end{equation}
-%
-can be approximated by its asymptotic behaviour
-%
-\begin{equation}
- \Gamma_{{\rm ICD},i,\beta} = (2J_{\rm in}+1)\, \frac{3c^4}{8\pi}\,
-                        \sum\limits_{M_{in}'}
-                        \left| \left(
-                        \begin{array}{ccc}
-                        J_A'  & 1        & J_A\\
-                        -M_A' & M_A'-M_A & M_A
-                        \end{array}\right) \right|^2
-                        \frac{\sigma^{(X_E)}(\omega_{vp,\beta})}
-                        {R_i^6 \, \omega_{vp,\beta}^4 \tau_{in,\beta}},
-\end{equation}
-%
-where $J_A$, $J_A'$ and $M_A$, $M_A'$ denote the total angular momentum of the
-initially ionized atom (which is the same as the electron donor atom) in the
-initial and final state, respectively,
-and
-%
-\begin{align}
- \Gamma_{{\rm ETMD},j,\beta} =& \frac{c}{\pi} \sum\limits_{m,M_{in,D'}}
-                        \frac{\Theta_{m,k}(\alpha_j) \sigma^{(X_E)}(\omega_{vp,\beta})
-                              \left| <\tilde{D}_{m,j,\beta}(M_{in,D'})>\right|^2}
-                         {R_j^6 \omega_{vp,\beta}}\\
-               =& \frac{c}{\pi R_j^6}
-               \sum\limits_{M_{in,D'}}
-               \left( \left| <\tilde{D}_{x,j,\beta} (M_{in,D'}) > \right|^2
-                 (2+ \sin^2\alpha_j)
-               + \left| <\tilde{D}_{z,j,\beta} (M_{in,D'}) > \right|^2
-                 (1+\cos^2\alpha_j) \right) \nonumber \\
-           & \times\, \frac{c\sigma^{(X_E)}(\omega_{vp,\beta})}{\omega_{vp,\beta}}
-\end{align}
-%
-depending on 
-experimental properties
-of atoms, like the ionization cross sections
-$\sigma^{(X_E)}(\omega_{vp,\beta})$, radiative lifetimes of the initially
-ionized state $\tau_{in,\beta}$ and the excess energy transferred to the
-emitting atom (the energy of the virtual photon) $\omega_{vp,\beta}$
-and calculated dipole transition moments $\tilde{D}_{m,j,\beta}$, only.
-Here, $\Theta_{m}(\alpha_j)$ is a function depending on the angle $\alpha_j$
-of the triple and the direction of the dipole
-transition moment $m$
-(compare ref \citenum{Fasshauer13}).
-
-In this work we evaluate the secondary energies and decay widths with
-the programme HARDRoC\cite{HARDRoC,fasshauer2014} using the
-experimental ionization energies of Table \ref{tab:valence}
-and data from the literature given in Tables II and III.
-This choice is identical to the one made in ref \citenum{Fasshauer13}.
-
-%\input{structures}
-\section{Cluster Structures}
-
-From the experimental results we can obtain two hints for the cluster
-structure: the minimum size and the xenon content. In the following we will 
-use these to construct representative cluster structures, for which we will 
-simulate the ICD and ETMD spectra. At this point we put in a variety of
-structures, in order to learn about general structure-spectrum relations
-and therefore being able to
-exclude some of them by comparison of
-the ICD and ETMD spectra to the experimental ones.
-
-In our previous study\cite{Fasshauer13} the ArXe clusters were assumed
-to be large, having more than 1500 atoms. The model structures assumed
-an fcc structure and not an icosahedral structure, which is energetically
-favoured for small clusters.
-Most estimated cluster sizes given in Table \ref{tab:cluster} are much smaller.
-We use the estimated number of atoms for a pure Ar expansion as the lower limit for the actual cluster size and start our search for model structures from there.
-%
-%Additionally,
-%the expectation value for the number of xenon atoms relies on a pure
-%xenon gas. Since the xenon content in the mixed gas is much lower, also
-%the number of xenon atoms can be expected to be by far less. We therefore
-%start from the estimated number of atoms in the cluster after expansion
-%of pure argon gas.
-%We therefore rethink the possible cluster structures.
-%Furthermore, the theoretical prediction did not match the experimental results.
-%Since the spectra are strongly depending on the cluster structure as shown in
-%\cite{fasshauer2014}, the underlying structure seems not to fit and hence
-%we rethink the possible cluster structures.
-%
-For the smaller clusters measured,
-these expectation values range from \unit[3--21]{Ar atoms}. 
-The cluster sizes for expansion of a mixed gas are unknown, but
-for xenon as the second component a larger size is expected compared to a
-pure argon expansion, due to the higher polarizability
-and hence larger cohesive energy of xenon. All clusters
-contributing to the coincidence spectrum
-contain at least one xenon atom, as otherwise decay by ICD or ETMD is energetically not allowed.
-
-In a gas expansion a range of clusters sizes with different structures is produced. 
-However, for small rare gas clusters consisting of less than approximately \unit[1000]{atoms} so-called \emph{islands of stability} were found.\cite{haberland}  
-In mass spectra, clusters with mass numbers corresponding to icosahedral shapes had an abundance that was (slightly) enhanced over other sizes. 
-We therefore started from icosahedral structures and constructed mixed cluster structures by substitution of individual atoms with one or the other kind (Ar or Xe), or added individual atoms close to the desired position within a given structure.
-After that, the cluster structures were optimized using the unified force
-field implemented in the 
-Avogadro programme (version 1.1.0) \cite{Avogadro,Hanwell12} to give local
-minimum structures.
-All cluster structures are listed in Table \ref{table:theo_gammas}.
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{cluster_2_overview.pdf}
- \caption{Cluster structures composed of 13 argon atoms and two additional xenon
-          atoms on different surfaces of the argon icosahedron, varying in Xe-Xe distance:
-          (a) closest possible, (b) middle, (c) furthest away. They refer to
-          numbers 9--11 in Table \ref{table:theo_gammas}.}
- \label{figure:cluster_2_overview}
-\end{figure}
-%
-\begin{figure}[h]
- \centering
- \includegraphics[width=8.5cm]{cluster_3_overview.pdf}
- \caption{Cluster structures derived from a 55 atom icosahedral structure:
-          (a) one xenon atom on the surface, (b) six xenon atoms inside a 55 atoms cluster,
-          grouped on one side, (c) six xenon atoms distributed randomly
-          in a 55 atoms cluster. They refer to numbers 12, 18 and 19
-          in Table \ref{table:theo_gammas}.}
- \label{figure:cluster_3_overview}
-\end{figure}
-
-As discussed in the introduction, the small clusters will likely
-deviate from a core-shell structure with a xenon core surrounded
-by argon shells, as observed for large clusters.\cite{tchaplyguinearxe,Vach_1999} We therefore start from
-argon clusters of 13 or 55 atoms, and modify them in one of the following
-ways:
-%
-\begin{itemize}
- \item add one xenon atom on top of a surface / edge / vertex of
-       the argon core, with an example shown in
-       Figure \ref{figure:cluster_3_overview}a
-       (one additional xenon atom
-       on top of a surface of a \unit[55]{atom} argon core)
-       (Table \ref{table:theo_gammas}, \#6--8, \#12--14),
- \item substitute one argon atom in a surface / edge / vertex position
-       (Table \ref{table:theo_gammas}, \#15--16),
- \item substitute one or two argon atoms in the core of the argon cluster
-       by xenon atom(s) for the simulation of the core-shell structures
-       (Table \ref{table:theo_gammas}, \#1--3),
- \item add two xenon atoms on top of surfaces of a 13 atoms argon core
-       in different relative positions (see Figure
-       \ref{figure:cluster_2_overview}),
-       in order to achieve a xenon content in the cluster close to the
-       measured one (see below)
-       (Table \ref{table:theo_gammas}, \#9--11),
- \item substitute six argon atoms of a 55 atoms argon cluster by xenon
-       atoms either grouping them or distributing them througout the cluster
-       (see Figure \ref{figure:cluster_3_overview}b and c) in order to
-       achieve a xenon content in the cluster close to the measured one
-       (Table \ref{table:theo_gammas}, \#18--19).
-\end{itemize}
-
-These structures were then optimized using force field methods.
-%
-Furthermore, for comparison with the largest measured ArXe clusters, we constructed also larger core-shell structures (Table \ref{table:theo_gammas}, \#4--5).
-
-%\input{theo_results}
-\section{Theoretical Results
-\label{sec:th_results}}
-%
-%
-\begin{table}[H]
-\small
-\centering
-\caption{Structural and calculated properties of some model clusters.
-The cluster structures are characterized by the number of Ar and Xe atoms,
-and are arranged in three groups according to gross structural properties. 
-The first group contains Xe core-Ar shell systems of various
-size and relative Xe content.
-In the second group, model structures for small clusters are displayed,
-in which 1-2 Xe atoms are added at systematically varied locations
-to an icosahedric Ar clusters consisting of one or two full shells,
-or in which 1-6 Ar atoms of such cluster were replaced by Xe atoms.
-The last group contains data for calculated minimal energy structures
-of mixed ArXe clusters.\protect\cite{marques}
-The cluster structures are classified into core-shell structures (cs),
-structures with segregated xenon atoms (in) and completely mixed
-structures.
-The columns `ICD' and `ETMD' are the respective partial decay widths
-in \unit[$10^{-4}$]{eV}, and `\% ICD' gives the percentage of ICD in
-the total decay width.
-See text for details.
-\label{table:theo_gammas}
-}
-\begin{tabular}{rrrrcccccrrr}
-\toprule
-\# & \# Xe & \# Ar & Xe$_{\rm cl}$\% & str. cl. & pos. & rel. pos. & ICD   &  ETMD & \% ICD & Fig.\\ %$\Gamma_{\rm ICD,ETMD}$\\
-\midrule
- 1 &     1 &    12 &  7.7  & cs    &         &          & 0.000 & 0.000 &  -- &\\ %    0.0            \\     ArXe\_2\_1atom      
- 2 &     1 &    54 &  1.8  & cs    &         &          & 0.000 & 0.000 &  -- & \ref{figure:xe_3_in}\\ %    0.0            \\     ArXe\_3\_1atom      
- 3 &     2 &    53 &  3.6  & cs    &         &          & 0.033 & 0.167 &  16.7& \ref{figure:xe_3_in}\\ %2.006$\cdot 10^{-5}$ \\ ArXe\_3\_2atom      
- 4 &  1415 &   642 & 68.8  & cs    &         &          & 7.039 & 2.573 &  73.2& supp.\\ %9.612$\cdot 10^{-4}$ \\ ArXe\_8\_1layer     
- 5 &   561 &  3310 & 14.5  & cs    &         &          &       &       &  85  & \ref{figure:xe_6_lay5}\\ % c6l5
-
-\midrule
- 6 &     1 &    13 &  7.1  & cs    & surface &          & 0.792 & 0.000 & 100.0& \ref{figure:surf}\\ %7.922$\cdot 10^{-5}$ \\ XeAr\_2\_surface    
- 7 &     1 &    13 &  7.1  & cs    & edge    &          & 0.013 & 0.000 & 100.0&\\ %1.320$\cdot 10^{-6}$ \\ XeAr\_2\_edge       
- 8 &     1 &    13 &  7.1  & cs    & vertex  &          & 0.050 & 0.000 & 100.0&\\ %5.013$\cdot 10^{-6}$ \\ XeAr\_2\_vertex     
- 9 &     2 &    13 & 13.3  & cs    &         & closest  & 0.101 & 0.151 &  40.1& \ref{figure:2tops}\\ %2.523$\cdot 10^{-5}$ \\ XeAr\_2\_2top       
-10 &     2 &    13 & 13.3  & cs    &         & middle   & 0.159 & 0.008 &  95.4& \ref{figure:2tops}\\ %1.665$\cdot 10^{-5}$ \\ XeAr\_2\_2midtop    
-11 &     2 &    13 & 13.3  & cs    &         & furthest & 0.159 & 0.002 &  98.9& \ref{figure:2tops}\\ %1.605$\cdot 10^{-5}$ \\ XeAr\_2\_2endtop    
-12 &     1 &    55 &  1.8  & cs    & surface &          & 0.064 & 0.000 & 100.0& \ref{figure:surf}\\ %6.371$\cdot 10^{-6}$ \\ XeAr\_3\_surface    
-13 &     1 &    55 &  1.8  & cs    & edge    &          & 0.048 & 0.000 & 100.0&\\ %4.791$\cdot 10^{-6}$ \\ XeAr\_3\_edge       
-14 &     1 &    55 &  1.8  & cs    & vertex  &          & 0.027 & 0.000 & 100.0&\\ %2.701$\cdot 10^{-6}$ \\ XeAr\_3\_vertex     
-15 &     1 &    54 &  1.8  & in    & edge    &          & 0.077 & 0.000 & 100.0&\\ %7.708$\cdot 10^{-6}$ \\ XeAr\_3\_edge\_in   
-16 &     1 &    54 &  1.8  & in    & vertex  &          & 0.053 & 0.000 & 100.0&\\ %5.258$\cdot 10^{-6}$ \\ XeAr\_3\_vertex\_in 
-17 &     2 &    53 &  3.6  & in    &         &          & 0.117 & 0.055 &  68.1&\\ %1.711$\cdot 10^{-5}$ \\ XeAr\_3\_2in        
-18 &     6 &    49 & 10.9  & in    &         &          & 0.375 & 0.405 &  48.1& \ref{figure:ar_3_6in}\\ %7.796$\cdot 10^{-5}$ \\ XeAr\_3\_6in        
-19 &     6 &    49 & 10.9  & mixed &         &          & 0.292 & 0.674 &  30.3& \ref{figure:ar_3_6in}\\ %9.660$\cdot 10^{-5}$ \\ XeAr\_3\_6\_scat    
-                                                                                                 \midrule
-20 &     2 &    36 &  5.3  & cs    &         &          & 0.117 & 0.151 &  43.6& supp.\\                        % Ar$_{36}$Xe$_{2}$   
-21 &     4 &    34 & 10.5  & mixed &         &          & 0.248 & 0.587 &  29.7& supp.\\                        % Ar$_{34}$Xe$_{4}$   
-22 &     5 &    33 & 13.2  & mixed &         &          & 0.335 & 0.844 &  28.4& supp.\\                        % Ar$_{33}$Xe$_{5}$   
-23 &    13 &    25 & 34.2  & mixed &         &          & 0.828 & 5.414 &  13.3& supp.\\                        % Ar$_{25}$Xe$_{13}$  
-24 &    24 &    14 & 63.2  & mixed &         &          & 1.488 &16.718 &   8.2& supp.\\                        % Ar$_{14}$Xe$_{24}$  
-25 &    25 &    13 & 65.8  & in    &         &          & 1.432 & 4.995 &  22.3& supp.\\                        % Ar$_{13}$Xe$_{25}$  
-26 &    35 &     3 & 92.1  & in    &         &          & 2.017 & 7.051 &  22.2& supp.\\                        % Ar$_{3}$Xe$_{35}$   
-\bottomrule
-\end{tabular}
-\end{table}
-%
-The geometrical properties as well as the total ICD and ETMD decay widths
-of the investigated structures are shown in Table \ref{table:theo_gammas}.
-It is important to remember that the first ICD channel opens at a
-channel opening distance of \unit[7.58]{\AA}. In the smallest
-clusters with only one argon layer around each
-xenon atom, the Ar-Xe pair distances are below that value, therefore 
-no ICD can take place. Also, by definition, two Xe atoms are
-required for ETMD(3), hence it cannot occur in clusters with only one xenon atom.
-%Because secondary electrons are observed in the experimental spectra
-%we exclude all structures without any signal from our further
-%discussions.
-%
-\begin{figure}[H]
- \centering
- \includegraphics[width=8.0cm]{surf.pdf}\\
- \includegraphics[width=8.0cm]{R_comp.pdf}
- \caption{
- %
- Top panel: Simulated electron emission spectra of an Ar 3s vacancy in 
-          argon clusters
-          consisting of 13 and 55 atoms, with an additional xenon atom residing
-          on top of one of the argon surfaces.
-          Bottom panel: Distribution of Ar-Xe distances $d$ in the studied ArXe
-          clusters. The ICD channels to final states involving Xe 5p$_{3/2}^{-1}$ and 
-          5p$_{1/2}^{-1}$ vacancies open at \unit[7.58]{\AA} and
-          \unit[36.00]{\AA}, resp.; the former distance is marked by a vertical dotted line. 
-          Only pairs at longer interatomic
-          distances contribute to the electron emission spectra.
-          Larger Ar-Xe distances, as found in the larger cluster,
-          correspond to features at a higher kinetic energy of
-          the ICD electron (top panel).}
- \label{figure:surf}
-\end{figure}
-
-%In the investigated structures several different aspects have to be
-%taken into account which we will discuss separately if possible
-%on selected structures.
-
-We will now discuss features of several structures, using selected examples.
-First we consider clusters having an argon core of 13 and 55 atoms plus a single xenon
-atom on one of the surfaces (see Figure \ref{figure:cluster_3_overview}a
-for the structure of clusters with the 55 atoms core).
-Secondary electron spectra simulated for these systems are shown in Figure \ref{figure:surf}, top panel.
-%two different argon core sizes one consisting
-%of 13 and one consisting of 55 atoms with one xenon atom on one of
-%the surfaces (see Figure \ref{figure:cluster_3_overview} Panel a)
-%for the 55 atom core). The simulated secondary electron spectra are
-%shown in Figure \ref{figure:surf} Panel 1.
-
-Because the structures contain only one xenon atom, ETMD(3) is not possible, only ICD is expected. 
-%Both spectra show several smaller peaks which
-%are convoluted into one single peak with a maximum at
-%approximately \unit[0.2]{eV}. 
-%In comparison to the 13 argon atoms core
-%spectrum t
-The spectrum pertaining to the clusters with larger (55 atoms) Ar core shows
-signals at higher energies of the secondary electron. These features
-can be explained by investigating the Ar-Xe distance distributions
-in the clusters, shown
-in the bottom panel of Figure \ref{figure:surf}. 
-Every different value of the atom pair distance
-results in a different energy of the secondary electron and only pairs
-with a distance of larger than the channel opening distance
-(dashed gray line) will contribute
-to the spectrum. 
-In our model, there is a one-to-one correspondence between interatomic distance $d$ and kinetic energy of the ICD electron.
-The larger the interatomic distance, the higher is the
-kinetic energy of the secondary electron for a given channel.
-%Since the cluster with an Ar core of 55 atoms is larger, and therefore
-%contains Ar-Xe pairs with larger distances, its spectrum 
-Therefore, the spectrum of the cluster with a 55 atoms core extends to higher energies.
-%energies as well.
-This relation between ICD energy and cluster size holds true for all cluster structures.
-%This explains why the ICD spectrum for larger clusters extends to higher energies, and holds for all cluster structures.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{2tops.pdf}
- \caption{Simulated electron emission spectra of an Ar 3s vacancy in 
-          argon clusters consisting of 13
-          argon atoms with two additional xenon atoms on top of two different
-          argon surfaces. ICD and ETMD spectra are shown for three
-          different relative positions of the two xenon atoms. If 
-          the xenon atoms are close to each other, an ETMD process is
-          clearly visible. In the other two cases the spectra are dominated by
-          the ICD spectrum.}
- \label{figure:2tops}
-\end{figure}
-%
-For clusters with more than one xenon atom, also ETMD(3) is possible.
-Depending on the positions of the xenon atoms relative to each other and to the Ar core, the spectra are expected to be different.
-As an example, we discuss clusters with a core of 13 argon atoms and two xenon atoms on different surfaces. 
-Their xenon content is \unit[13.3]{\%} and thus close to the experimental one of \unit[10-12]{\%} for the lowest xenon admixture.
-The cluster structures were illustrated in Figure \ref{figure:cluster_2_overview}, simulated spectra are shown in Figure \ref{figure:2tops}.
-In all three cases, both ICD and ETMD(3) are energetically allowed. The ICD
-spectra do not change qualitatively by adding the second xenon.
-%either identical or at least very similar to the ones for
-%cluster with a single  consisting of one
-%convoluted peak at approximately \unit[0.2]{eV}. 
-However, the ETMD(3) spectra
-are very sensitive to the relative position of the two xenon atoms.
-Two aspects have to be taken into account: an energy shift of the peaks due
-to different charge distances in the final state (i.e. the interatomic Xe-Xe
-distance) and the decrease of the decay width with $R^{-6}$, $R$ being the distance
-between the electron transfer unit and the xenon atom ionized in the final state.
-The larger the distance between the xenon atoms, the higher are the energies
-of the secondary electrons and the smaller are the decay widths. 
-Therefore, a
-significant contribution from ETMD(3) compared to ICD is only
-seen if the two xenon atoms reside on two adjacent
-surfaces. 
-%{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
-The three energetically separated peaks in the ETMD(3) spectrum pertain to different combinations of the Xe 5p$_j^{-1}$ vacancy states, which have a substantial fine-structure splitting (see Table \ref{tab:valence}).
-%\ref{sec:exp_results}).
-%
-%The threefold peak structure of the ETMD(3) peak does in contrast to
-%the ICD spectrum not stem from different triple structures but from the
-%four different decay channels for one triple structure.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{ar_3_6in.pdf}
- \caption{Same as Figure \protect\ref{figure:2tops}, for clusters consisting of
-          55 atoms, 6 out of which are xenon atoms. These are either grouped
-          on one side of the cluster (label `group') or evenly distributed
-          in the cluster interior (label `scattered').}
- \label{figure:ar_3_6in}
-\end{figure}
-%
-For the 55 atoms clusters, a xenon content of \unit[10--12]{\%}
-corresponds to six xenon atoms out of a total of 55 atoms. These can form a connected 
-group in one part of the cluster or can be evenly distributed,
-as shown in Figures \ref{figure:cluster_3_overview}b and \ref{figure:cluster_3_overview}c. The
-ICD and ETMD(3) spectra for these structures are shown in Figure \ref{figure:ar_3_6in}.
-
-For both cases the overall ICD spectra are very similar, and show a maximum at a kinetic energy of approximately \unit[0.3]{eV}. 
-In case of grouped xenon atoms, the ICD spectrum extends to slightly higher energies, corresponding to ArXe pairs at slightly larger spatial distances.
-A more significant difference is observed in the ETMD(3) spectra. 
-The interatomic xenon distance is shorter in clusters, in which the xenon atoms form a connected group.
-Hence, the triple structure of the ETMD(3) spectrum is seen at lower kinetic energies. 
-Additionally, the probability for an electron
-transfer from a xenon to an argon atom decreases exponentially with the
-interatomic distance. Therefore, only those xenon atoms which have direct
-argon atom neighbours have a significant contribution to the
-total decay width, and the total ETMD(3) decay width is lower for the structure with
-grouped xenon atoms than for
-the structure with evenly distributed xenon atoms (see Table \ref{table:theo_gammas}).
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{xe_3_in.pdf}
- \caption{Same as Figure \protect\ref{figure:2tops}, for argon clusters with
-          one or two xenon atoms in the core of the cluster (55 atoms total). 
-          All ICD and ETMD channels are closed, if the cluster contains only 
-          a single xenon atom. For clusters with two xenon atoms
-          in the core, the first ICD channel is open for some pairs,
-          and additionally ETMD is possible for multiple triples. Due to a
-          different distance distribution compared to the clusters with an argon
-          core (Figure \protect\ref{figure:2tops}), 
-          the ICD peak is shifted to higher kinetic energies.}
- \label{figure:xe_3_in}
-\end{figure}
-%
-For comparison with the previous assumptions of a xenon core surrounded
-by argon atoms we investigated clusters of 13 and 55 atoms with one or two
-xenon atoms in the core. Some of the corresponding
-spectra are shown in Figure \ref{figure:xe_3_in}.
-
-%For the clusters with only one xenon atom in the core and the ionization
-%energies used for the simulation of the secondary electron energies
-%all ICD channels are closed. Since the cluster contains only one xenon atom,
-%an ETMD(3) is not possible. Hence there is no signal to be expected at all.
-For a core consisting of two xenon atoms both an ICD and an ETMD(3) spectrum
-can be seen. Compared to the cluster structures involving an argon core, the ICD peak is
-shifted to higher ICD electron energies. 
-Additionally, the ICD and ETMD(3) spectra overlap.
-For ETMD(3), only three of the four different decay channels are
-energetically allowed.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{c6l5.pdf}
- \caption{Same as Figure \protect\ref{figure:2tops},
-          for a large cluster consisting
-          of a xenon core of 561 atoms surrounded by five complete layers of
-          argon atoms (Xe content: 14.5\,\%) for both an icosahedral and
-          cuboctahedral basic structure.
-          The ICD and ETMD peak overlap such that the ETMD peak
-          is unlikely to be visible.}
- \label{figure:xe_6_lay5}
-\end{figure}
-%
-In the first experiments very large argon-xenon clusters of 
-$\approx 4380$ atoms with a xenon content of \unit[19]{\%}
-were measured,\cite{Mucke_phd}
-which we in one example approximate by a cluster consisting of 561 xenon
-atoms surrounded
-by five layers of argon atoms (3871 atoms in total). In order to take the
-better stabilization of charges in larger clusters into account, the
-ionization energies of the XL clusters (see Table \ref{tab:valence})
-were used.
-The spectra are shown in 
-Figure \ref{figure:xe_6_lay5}.
-
-Compared to the small clusters with a xenon core in Figure \ref{figure:xe_3_in}
-the ICD peak is broadened and shifted to higher ICD electron energies which is
-expected due to the larger interatomic Ar-Xe distances in the large cluster and
-the better stabilization of charges, which is relevant mostly for the final state, but also the initial state.
-The ETMD(3) peak is shifted to slightly higher energies as well. This allows opening of the
-fourth decay channel, pertaining to Xe 5p$_{1/2}^{-1}$ Ar 3p$_{1/2}^{-1}$ final states.
-
-We also note that the percentage of decay via ICD is practically
-independent of the Xe content for large clusters with a Xe core, Ar shell structure.
-This can be expected, as both decay processes are most pronounced for the
-atoms in the interface region of the xenon core and the argon shell.
-The ETMD(3), depending on the electron transfer from one xenon atom to the
-initially ionized argon atom, and hence on the corresponding orbital overlap,
-is purely an interface effect that involves the argon atoms with direct xenon
-neighbours, and the two xenon layers closest to the argon shell.
-The ICD has a stronger long range character, due to which the description
-of decays with partners of at least twice the smallest channel opening
-distance is necessary for clusters. However, the bigger the clusters are,
-the more homogeneous does the interface region become for clusters of
-different sizes. This manifests itself in the distribution of relevant
-Ar-Xe pair distances (compare Figure \ref{figure:surf}, lower panel).
-As a consequence, the ICD spectra of two large clusters of different size
-hardly differ.
-
-\clearpage
-
-%\input{exp_results}
-\section{Experimental Results}
-\label{sec:exp_results}
-%
-%
-\begin{table}
-\caption{Properties of the outer valence spectra of mixed ArXe clusters. 
-Spectra of pure Ar and Xe clusters are included for reference. 
-All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV). 
-Binding energies $\EB$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit. 
-The average Xe content of the cluster ensemble, Xe$_{\rm cl}$, was determined from the areas of the respective photolines, corrected by their atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}.
-Uncertainties are estimated as $\pm$3\,\% for the Xe content and 0.05~eV for the binding energies. 
-The row labelled `(th.)' gives the binding energies used in the simulations of this paper, and the last row their atomic counterparts. 
-Values for Ar 3p in the last row refer to the fine structure states.
-\label{tab:valence}}
-\begin{tabular}{ l c c c c c c c c}
-%
-\toprule
- \multicolumn{2}{r}{size} &  Xe$_{\rm in}$& $\EB$ (eV)& $w$ (eV)& \multicolumn{2}{c}{$\EB$ (eV)}  & $w$ (eV) &  Xe$_{\rm cl}$ \\
-%
- \multicolumn{2}{r}{(label)}&  (\%) & Ar 3p & Ar 3p & Xe 5p$_{1/2}$ &  Xe 5p$_{3/2}$ & Xe 5p$_{3/2}$  &  (\%) \\
-\midrule
-% Ar, from Marko
- Ar & (1) &&  15.3  &  1.1 & & & &  \\
-% Ar, from Marko 
- Ar & (2) &&  15.1  &  1.3 & & & &  \\
-%
-%  columns in the following: energies c.g. 51-plt-oval, widths Marko Diss., Xe content Marko Diss
-% 1103 676, 679
- ArXe & S &1.2 & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
-% 1103 670
- ArXe & M &1.2 & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
-% 1103 671
- ArXe & L &1.2 & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
-% 1103 663
- ArXe & S &3.0 & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
-% 1103 640
- ArXe & M &5.0 & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
-% 0506 
- Xe &  & & & & 12.76 & 11.19 & 1.18 & 100\\
-%
-\midrule
-%
-%  1004  886  (UHe, c.g. + roi values)
- ArXe & XL &2.5 & 15.15 & 1.3 & 12.59 & 11.01 & 1.24 & 19\\
-%
-\midrule
-% Date: Wed, 20 Jan 2016 11:27:39, From: Elke Fa?hauer <elke.fasshauer@uit.no>
- Ar, Xe & (th.) && 15.3 && 13.0 & 11.5 &&\\
-%
- \multicolumn{2}{l}{(atomic)\cite{velchev,sansonetti}} && 15.76|15.94 && 13.43 & 12.13 &&\\
-%
-\bottomrule
-\end{tabular}
-\end{table}
-
-\subsection{Outer valence spectra}
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_oval_1.pdf}
- \caption{
-Outer valence photoelectron spectra of mixed Ar-Xe clusters, in comparison to the pure species. 
-(a) shows the outer valence region of homogeneous Ar and Xe clusters, respectively (see text for details). 
-The two lower panels show spectra of the mixed species with different mean size. 
-Sharp lines marked `m' (for `monomer') result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states. 
-Labels in (b) and (c) give the Xe content in the expanding gas mixture (Xe$_{\rm in}$), which is lower than the Xe content observed in the heterogeneous clusters (Xe$_{\rm cl}$). 
-The photon energy was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
-%{\color{red}{Die Stabilisierung der Xe-bulk Atome ist in den gemischten Cluster
-% höher als in den gemischten Clustern. Das ist ungewöhnlich. Habt ihr hier
-% verschiedene CLustergrößen?}}
-}
- \label{figure:oval1}
-\end{figure}
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_oval_2.pdf}
- \caption{
-Outer valence photoelectron spectra of mixed Ar-Xe clusters from gas mixtures with different Xe concentration. 
-For better visibility, a scaling factor is applied to the Xe part of the spectrum in panel (a).
-See Figure \ref{figure:oval1} and text for details.
-}
- \label{figure:oval2}
-\end{figure}
-
-Figure \ref{figure:oval1} shows the outer valence spectra of small and large ArXe clusters, compared to clusters of the pure gases. 
-Qualitatively similar spectra have been published without detailed discussion in ref \citenum{lindblad}.
-Differences are seen in particular for the Ar component. 
-In pure Ar clusters, outer valence photoionization leads to a broad band, caused both by spin-orbit coupling and crystal field splitting. 
-The relative importance of these two mechanisms remains under debate.\cite{hergenhahnprb,rolles,foerstel_arg1_2010} 
-For larger clusters (e.g.
-$\langle N\rangle = 190$, black trace), the maximum at low binding energies becomes more pronounced, and is identified with emission from the cluster interior.\cite{hergenhahnprb,rolles}
-At the particular photon energy selected here, atop of this band a sharp feature is also visible (in Figure \ref{figure:oval1} at a kinetic energy of about 1.8 eV).
-For larger clusters (above $\langle N\rangle \approx 100$), over a range of photon energies of about 3 eV, its appararent binding energy changes in a way which is reminiscent to photoemission of crystalline bulk matter (`dispersion').\cite{foerstel_arg1_2010,foerstel_arg2_2011}
-
-Ar 3p spectra of the smaller mixed clusters (Figure \ref{figure:oval1}c, Figure \ref{figure:oval2}) show neither of these traits.
-Rather, the Ar band is symmetric, less wide than in the pure clusters and at a higher binding energy.
-Even for very large clusters (Figure \ref{figure:oval1}b) the asymmetry of the 3p band and the `dispersing feature' do not appear.
-We characterize the spectral shape by giving a single value for the Ar 3p binding energy, and the FWHM of the feature.
-Values for different expansion parameters, and for both Ar and Xe valence lines, are collected in Table\ \ref{tab:valence}.
-
-We find experimentally that clusters we have produced have a Xe content Xe$_{\rm cl}$ between 10\,\% and 50\,\%.
-A slight decrease of the binding energy with cluster size is seen for all outer valence lines, and is attributed to a larger final state polarization energy in larger clusters.
-
-For further interpretation of the shape of the Ar peaks we refer to photoemission spectra of condensed Ar monolayers, measured in several settings.\cite{jacobi,jacobi2}
-Spectra were reported for physisorption of Ar on two different metal single crystal substrates, and for Ar atop of a Xe spacer layer adsorbed on the metal.
-While the binding energy depends on the substrate, the spectral shape is very similar in all cases. 
-Most spectra were recorded for emission along the surface normal, and show a double peak split by about 0.5 eV, leading to a structure with $w$ about 1 eV.
-Although the splitting is larger than the gas phase fine structure split of 0.18 eV, the pertaining states have been assigned to Ar 3p$_{1/2}$ and 3p$_{3/2}$.
-A crystal field splitting of the 3p$_{3/2}$ state has been assumed to be also present, but with a smaller value of 0.1-0.2 eV, approx.\cite{jacobi2} 
-The spectrum clearly changes when going to an emission angle of 40$^\circ$ with respect to the surface normal (Figure 2 in ref \citenum{jacobi2}).
-The higher binding energy peak significantly loses in intensity, and the spectrum is now dominated by a single peak comprising both crystal field split substates of Ar 3p$_{3/2}$, with a FWHM ($w$) of only 0.4 eV.
-As our measured spectrum is comprised of contributions recorded under all emission angles with respect to the cluster surface, grazing emission will be the rule.
-We therefore believe that the arguments given above make it plausible that only a single peak is observed in all our spectra.
-
-Emission from the Xe 5p state shows a much larger fine structure splitting then from the Ar 3p state; it dominates the spectrum even in clusters (where other broadening mechanisms are also present).
-The shift of the cluster bands with respect to the monomer lines in the largest mixed clusters we have probed (Figure \ref{figure:oval1}b) are similar to the ones in the pure Xe spectrum, the scaling law size of which is at somewhat more than five filled shells.
-This indicates an approximate upper limit for the size of the Xe core in our mixed clusters, as their binding energy shift might be somewhat higher than the one in pure clusters, due to polarization of covering Ar layers.
-Xe cluster features in the spectra of mixed clusters appear less asymmetric than the pure Xe spectrum, and also less asymmetric as some the ArXe spectra shown in ref \citenum{lindblad}.
-This might be caused by the difference in photon energy ($h\nu = 90$ eV in ref \citenum{lindblad} and for the pure Xe spectrum, $h\nu = 32$ eV for the mixed ArXe spectra in this work).
-% For the mixed clusters, the Xe band broadens and shifts towards lower binding energy for larger size clusters.
-%For pure Xe clusters, an asymmetry observed in the Xe 5p$_{3/2}$ part has no counterpart in the respective spectra from the mixed clusters.
-%This might be caused by the difference in photon energy, as can be seen from a comparison to literature spectra (ArXe at $h\nu = 90$ eV in ref \citenum{lindblad}, Xe at $h\nu = 20$ eV in ref \citenum{rolles}).
-%For the largest clusters, the nominal size yielded from the jet parameters applied to a pure Xe expansion would correspond to clusters in which bulk atoms far outweigh those on the surface.
-%At least for the 5p$_{1/2}$ photoelectron line, this would be seen as a clear asymmetry towards the low binding energy side, which is not observed in our spectra.
-
-In Figure \ref{figure:oval2}, we compare the outer valence spectra of clusters with similar expansion conditions, but different composition of the gas mixture.
-A Xe-rich mixture obviously leads to clusters with more intense Xe photolines, but besides that the main change consists in a narrowing of the Ar band.
-A comparison with the Ar monomer features (clipped in the Figure) also shows an increased degree of condensation for the Ar gas in the expansion.
-
-For the smallest clusters we have produced, a possible model is provided by calculated minimum energy structures of Ar$_N$Xe$_{38-N}$ (Figure 7 in ref \citenum{marques}).
-We there see that for a Xe content of less than 60\,\%, core-shell systems are {\it not} formed, and although the Xe atoms tend to connect, the degree of Ar-Xe mixing is large.
-While for low Xe content (approx. 10\,\%), some Ar atoms have only Ar nearest neighbours, for larger Xe content all Ar atoms seem to see both Ar and Xe nearest neighbours.
-We believe this leads to the Ar 3p narrowing pointed out above.
-For Figure \ref{figure:oval2}, possibly, some clusters of our ensemble already are in the core-shell regime, which would lead to an even lower 3p width.
-
-For the largest clusters we have produced (Figure \ref{figure:oval1}b), the low binding energy of the Xe lines and the broadening of the Ar feature without appearance of the `bulk Ar'-maximum, supports formation of a Xe core covered by at least two layers of Ar.
-If the scaling law size for a pure Ar expansion is taken as the lower limit for the cluster size, from the observed Xe content we arrive at clusters composed of a Xe core with four layers, covered by three layers of Ar (see Supporting Information).
-
-Finally, comparing Figure \ref{figure:oval2} to Figure \ref{figure:oval1} reveals that much larger changes in the valence emission spectra occur by changes in size than by changes of the (relative) Xe content.
-This finding is supported by the spectra shown in ref \citenum{lindblad}.
-%
-%
-\subsection{Inner valence spectra}
-%
-We now focus on the Ar inner valence (3s) vacancy states. 
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.8cm]{figure_ival.pdf}
- \caption{
-Photon excited electron spectra of mixed Ar-Xe clusters in the inner valence region.
-Symbols show the Ar 3s photoline from clusters (`cl') and uncondensed Ar monomers (`m'), atop of a background resulting from inelastic intracluster scattering of outer valence photoelectrons (`excitonic satellites').\protect\cite{hergenhahn2002}
-The photon energy was $h\nu = 32$ eV.
-Panel (a) shows all electrons accumulated.
-For the same conditions, in panel (b) we only show electrons that were detected in coincidence with a secondary electron of lower kinetic energy.
-The black solid trace in (a), and red solid trace in (b) result from a least squares fit to the cluster part of the spectrum. 
-The red solid trace in (a) is the fit shown in (b), divided by the detection efficiency of the spectrometer of 0.6.
-Panels (c) and (d) show the same type of data for smaller clusters with a lower Xe content.
-See text for details.
-\label{figure:ival}
-}
-\end{figure}
-
-Figure\ \ref{figure:ival} shows the Ar part of the inner valence spectrum for representative ArXe clusters. 
-The total photoelectron signal looks similar to literature spectra for pure Ar clusters.\cite{feifel,zhang} 
-A low energy tail seen for the Ar 3s monomer line results from the transmission properties of the electron spectrometer, together with the strongly positive angular distribution parameter of this line.\cite{zhang,kruit}
-The Ar 3s cluster line shows no splitting into bulk and surface components, different to the literature on pure clusters but in agreement with our discussion of the outer valence spectra. 
-The binding energy of the cluster line has values between 28.85 and 28.70 eV for all cluster ensembles with size label S-L, and 28.67 eV for the largest clusters measured. 
-A small, but systematic decrease of the binding energy is observed when the cluster size is increased. 
-The value assumed in the simulations is 28.7 eV.
-
-If we produce a spectrum only from those electrons recorded as part of a two-electron coincidence (electron pair with kinetic energies ($e_1,e_2$)) the apparent intensity drops (compare panel b to a, and d to c in Figure \ref{figure:ival}).
-This can partly be attributed to the finite detection efficiency of the spectrometer. 
-Moreover, the monomer part of the Ar 3s signal completely disappears, as 3s photoionization of an uncondensed Ar atom in the gas jet cannot lead to emission of a second electron. 
-Further features of these diagrams and the least squares fits shown in the Figure are discussed below.
-%
-%
-\subsection{ICD/ETMD spectra}
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_icd_12.pdf}
- \caption{
-Energy spectrum of all coincident secondary (ICD or ETMD) electrons of kinetic energy $e_2$ pertaining to primary electrons of kinetic energy $e_1$ in the Ar 3s binding energy region. 
-Spectra were recorded with a photon energy of $h\nu = 32$~eV. 
-Black error bars show the data points for the smallest clusters measured (`S'), two larger clusters sizes are shown by the red and blue traces. 
-Error bars for the latter are smaller than the ones shown and have been omitted.
-For better comparison, all spectra are shown area-normalized. 
-}
- \label{figure:icd_12}
-\end{figure}
-%
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_icd_l.pdf}
- \caption{
-Energy spectrum of all coincident secondary (ICD or ETMD) electrons, kinetic energy $e_2$, for clusters of the same size, but from gas mixtures with different Xe concentration.
-See Figure \protect\ref{figure:icd_12} for details.
-}
- \label{figure:icd_l}
-\end{figure}
-%
-In Figure \ref{figure:icd_12}, we show the spectra of ICD/ETMD electrons pertaining to emission of an Ar 3s cluster photoelectron. 
-Due to their low kinetic energy, without use of a coincidence method they could hardly be separated from the background of inelastically scattered photoelectrons.\cite{mucke}
-This and the following Figure constitute the central experimental result of the article.
-Spectra recorded at $h\nu = 34$ eV as a cross-check quantitatively agree to those shown here.
-This underpins our assignment of this intensity to an autoionization process.
-Further details on the data acquisition and analysis methodology, as well as the 34~eV spectra, are given in the Supporting Information.
-
-Spectra for the three different cluster sizes in Figure \ref{figure:icd_12} are significantly different: Spectra for the larger clusters acquire more intensity in the 1-1.5 eV region and have less intensity for energies below 0.5 eV.
-In contrast to that, the ICD/ETMD spectrum hardly varies when the composition of the expanding gas mixture, and with that the relative Xe content of the clusters, is changed (Figure \ref{figure:icd_l}).
-The full set of ICD/ETMD spectra is shown as Supporting Information.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_eff.pdf}
- \caption{
-Efficiency of the decay of Ar 3s ionized states in ArXe clusters by emission of a secondary electron via ICD or ETMD.
-Values are arranged by Xe content of the initial gas mixture (`+' symbols: 1.2\,\%, asterisk: 3\,\%, triangle: 5\,\%).
-Symbol sizes indicate the photon energy (large symbols: 32 eV, small: 34 eV), and color indicates the cluster size (black symbols: S, red: M, blue: L).
-See text for details.
-}
- \label{figure:eff}
-\end{figure}
-%
-We now discuss which fraction of Ar 3s vacancy states relaxes via ICD or ETMD.
-A method to derive this information has been established by some of us.\cite{foerstel_2013}
-Briefly, we correct the intensity of the Ar 3s photoline in the coincident spectra by the detector efficiency, and divide it by the total (coincident and non-coincident) Ar 3s intensity.
-The result gives the branching ratio of decay via ICD/ETMD vs. the sum of all channels, including those not involving electron emission.
-(If all Ar 3s vacancies decay by emission of another electron, the coincident and non-coincident count rate differ only by the probability for the spectrometer to actually detect the secondary electron.
-This figure has been determined as 0.6 for this data set, in the same way as discussed earlier.\cite{mucke_review})
-To arrive at quantitative results, we have performed least squares fits of the non-coincident and coincident $e_1$ spectra.
-The fits assumed one or two Gaussian peaks, resp., atop of a background modelled by two more Gaussian curves with very large widths.
-The peak pertaining to the Ar 3s cluster photoline, with the background added, is shown by the black solid trace in Figure \ref{figure:ival}a and red solid trace in Figure \ref{figure:ival}b.
-Moreover, the line labelled `c.fit/det.' shows the fit to the coincident events, corrected by the detection efficiency, and plotted atop of the non-coincident intensity. 
-This virtually agrees with the fit to the total spectrum in Figure \ref{figure:ival}a, but not in \ref{figure:ival}c. 
-The corresponding figure for the ICD/ETMD efficiency comes out as one for \ref{figure:ival}a, and significantly smaller than one for \ref{figure:ival}c.
-Figure \ref{figure:eff} shows all results of this analysis.
-The error in the autoionization efficiency shown is mainly determined by uncertainties in the peak/background separation.
-%(Our choice for the background shape is shown in Figure \ref{figure:ival}.)
-For the gas mixture with a Xe$_{\rm in}$ of 1.2\,\%, we therefore show results from fits using two different choices of the background shape in Figure \ref{figure:eff}.
-Statistical errors are much smaller than the differences between the pairs of values arrived at such.
-
-We found an Ar 3s autoionization efficiency which, for clusters with the lowest Xe content (Xe$_{\rm cl}$ approx.
-10-12\,\%), is smaller than unity, and further decreases with decreasing cluster size.
-For larger Xe$_{\rm cl}$, the values are compatible with unity, within the accuracy of our experiment.
-
-%\input{theo_discussion}
 \section{Discussion
@@
 A further theoretical delineation of the respective factors has recently been presented by one of us.\cite{fasshauernjp}
-
-%\input{summary}
-\section{Summary}
-%
-We have presented comprehensive experimental and theoretical data for the
-autoionization of inner valence ionized states in ArXe clusters.
-Both ICD and ETMD are allowed for most cases we considered.
-Because of energetical reasons ICD requires a separation of the final state
-vacancies of \unit[7.58]{\AA} or more, which is about two times the typical
-Ar-Xe distance.
-We found that autoionization has an efficiency of 0.8 to 1.0 within the
-experimental accuracy, that is it dominates over other modes of relaxation.
-By comparing our measured spectra to calculations, we identified `long range'
-ICD as the most important decay mode and were able to determine the most
-probable structural motifs to be a xenon core surrounded by several argon layers
-for large clusters and argon clusters with with very few xenon atoms spread out
-over the surface.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The "Acknowledgement" section can be given in all manuscript
-%% classes.  This should be given within the "acknowledgement"
-%% environment, which will make the correct section or running title.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{acknowledgements}
-\begin{acknowledgement}
-%
-We thank HZB for the allocation of synchrotron radiation beamtime, and the
-Deutsche Forschungsgemeinschaft for funding via the Forschergruppe 1789.
-E. F. gratefully acknowledges the Research
-Council of Norway through a Centre of Excellence Grant (Grant No.\ 179568/V30)
-for funding.
-%
-\end{acknowledgement}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The same is true for Supporting Information, which should use the
-%% suppinfo environment.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{suppinfo}
-
-%This will usually read something like: ``Experimental procedures and
-%characterization data for all new compounds. The class will
-%automatically add a sentence pointing to the information on-line:
-
-%\end{suppinfo}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The appropriate \bibliography command should be placed here.
-%% Notice that the class file automatically sets \bibliographystyle
-%% and also names the section correctly.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliography{arxe}
-
-\end{document}

### 2019-03-22 resubmit_2/theory.tex
submitted files

--- 2016-07-04 onefolder/master.tex
@@
  \centering
- \includegraphics[width=\columnwidth]{channel_open_ICD.pdf}
+ \includegraphics[width=\columnwidth]{pics/channel_open_ICD.pdf}
  \caption{Illustration of channel opening: Initial (Ar3s$^{-1}$)
@@
 experimental ionization energies of Table \ref{tab:valence}
-and data from the literature given in Tables II and III.
-This choice is identical to the one made in ref \citenum{Fasshauer13}.
-
-%\input{structures}
-\section{Cluster Structures}
-
-From the experimental results we can obtain two hints for the cluster
-structure: the minimum size and the xenon content. In the following we will 
-use these to construct representative cluster structures, for which we will 
-simulate the ICD and ETMD spectra. At this point we put in a variety of
-structures, in order to learn about general structure-spectrum relations
-and therefore being able to
-exclude some of them by comparison of
-the ICD and ETMD spectra to the experimental ones.
-
-In our previous study\cite{Fasshauer13} the ArXe clusters were assumed
-to be large, having more than 1500 atoms. The model structures assumed
-an fcc structure and not an icosahedral structure, which is energetically
-favoured for small clusters.
-Most estimated cluster sizes given in Table \ref{tab:cluster} are much smaller.
-We use the estimated number of atoms for a pure Ar expansion as the lower limit for the actual cluster size and start our search for model structures from there.
-%
-%Additionally,
-%the expectation value for the number of xenon atoms relies on a pure
-%xenon gas. Since the xenon content in the mixed gas is much lower, also
-%the number of xenon atoms can be expected to be by far less. We therefore
-%start from the estimated number of atoms in the cluster after expansion
-%of pure argon gas.
-%We therefore rethink the possible cluster structures.
-%Furthermore, the theoretical prediction did not match the experimental results.
-%Since the spectra are strongly depending on the cluster structure as shown in
-%\cite{fasshauer2014}, the underlying structure seems not to fit and hence
-%we rethink the possible cluster structures.
-%
-For the smaller clusters measured,
-these expectation values range from \unit[3--21]{Ar atoms}. 
-The cluster sizes for expansion of a mixed gas are unknown, but
-for xenon as the second component a larger size is expected compared to a
-pure argon expansion, due to the higher polarizability
-and hence larger cohesive energy of xenon. All clusters
-contributing to the coincidence spectrum
-contain at least one xenon atom, as otherwise decay by ICD or ETMD is energetically not allowed.
-
-In a gas expansion a range of clusters sizes with different structures is produced. 
-However, for small rare gas clusters consisting of less than approximately \unit[1000]{atoms} so-called \emph{islands of stability} were found.\cite{haberland}  
-In mass spectra, clusters with mass numbers corresponding to icosahedral shapes had an abundance that was (slightly) enhanced over other sizes. 
-We therefore started from icosahedral structures and constructed mixed cluster structures by substitution of individual atoms with one or the other kind (Ar or Xe), or added individual atoms close to the desired position within a given structure.
-After that, the cluster structures were optimized using the unified force
-field implemented in the 
-Avogadro programme (version 1.1.0) \cite{Avogadro,Hanwell12} to give local
-minimum structures.
-All cluster structures are listed in Table \ref{table:theo_gammas}.
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{cluster_2_overview.pdf}
- \caption{Cluster structures composed of 13 argon atoms and two additional xenon
-          atoms on different surfaces of the argon icosahedron, varying in Xe-Xe distance:
-          (a) closest possible, (b) middle, (c) furthest away. They refer to
-          numbers 9--11 in Table \ref{table:theo_gammas}.}
- \label{figure:cluster_2_overview}
-\end{figure}
-%
-\begin{figure}[h]
- \centering
- \includegraphics[width=8.5cm]{cluster_3_overview.pdf}
- \caption{Cluster structures derived from a 55 atom icosahedral structure:
-          (a) one xenon atom on the surface, (b) six xenon atoms inside a 55 atoms cluster,
-          grouped on one side, (c) six xenon atoms distributed randomly
-          in a 55 atoms cluster. They refer to numbers 12, 18 and 19
-          in Table \ref{table:theo_gammas}.}
- \label{figure:cluster_3_overview}
-\end{figure}
-
-As discussed in the introduction, the small clusters will likely
-deviate from a core-shell structure with a xenon core surrounded
-by argon shells, as observed for large clusters.\cite{tchaplyguinearxe,Vach_1999} We therefore start from
-argon clusters of 13 or 55 atoms, and modify them in one of the following
-ways:
-%
-\begin{itemize}
- \item add one xenon atom on top of a surface / edge / vertex of
-       the argon core, with an example shown in
-       Figure \ref{figure:cluster_3_overview}a
-       (one additional xenon atom
-       on top of a surface of a \unit[55]{atom} argon core)
-       (Table \ref{table:theo_gammas}, \#6--8, \#12--14),
- \item substitute one argon atom in a surface / edge / vertex position
-       (Table \ref{table:theo_gammas}, \#15--16),
- \item substitute one or two argon atoms in the core of the argon cluster
-       by xenon atom(s) for the simulation of the core-shell structures
-       (Table \ref{table:theo_gammas}, \#1--3),
- \item add two xenon atoms on top of surfaces of a 13 atoms argon core
-       in different relative positions (see Figure
-       \ref{figure:cluster_2_overview}),
-       in order to achieve a xenon content in the cluster close to the
-       measured one (see below)
-       (Table \ref{table:theo_gammas}, \#9--11),
- \item substitute six argon atoms of a 55 atoms argon cluster by xenon
-       atoms either grouping them or distributing them througout the cluster
-       (see Figure \ref{figure:cluster_3_overview}b and c) in order to
-       achieve a xenon content in the cluster close to the measured one
-       (Table \ref{table:theo_gammas}, \#18--19).
-\end{itemize}
-
-These structures were then optimized using force field methods.
-%
-Furthermore, for comparison with the largest measured ArXe clusters, we constructed also larger core-shell structures (Table \ref{table:theo_gammas}, \#4--5).
-
-%\input{theo_results}
-\section{Theoretical Results
-\label{sec:th_results}}
-%
-%
-\begin{table}[H]
-\small
-\centering
-\caption{Structural and calculated properties of some model clusters.
-The cluster structures are characterized by the number of Ar and Xe atoms,
-and are arranged in three groups according to gross structural properties. 
-The first group contains Xe core-Ar shell systems of various
-size and relative Xe content.
-In the second group, model structures for small clusters are displayed,
-in which 1-2 Xe atoms are added at systematically varied locations
-to an icosahedric Ar clusters consisting of one or two full shells,
-or in which 1-6 Ar atoms of such cluster were replaced by Xe atoms.
-The last group contains data for calculated minimal energy structures
-of mixed ArXe clusters.\protect\cite{marques}
-The cluster structures are classified into core-shell structures (cs),
-structures with segregated xenon atoms (in) and completely mixed
-structures.
-The columns `ICD' and `ETMD' are the respective partial decay widths
-in \unit[$10^{-4}$]{eV}, and `\% ICD' gives the percentage of ICD in
-the total decay width.
-See text for details.
-\label{table:theo_gammas}
-}
-\begin{tabular}{rrrrcccccrrr}
-\toprule
-\# & \# Xe & \# Ar & Xe$_{\rm cl}$\% & str. cl. & pos. & rel. pos. & ICD   &  ETMD & \% ICD & Fig.\\ %$\Gamma_{\rm ICD,ETMD}$\\
-\midrule
- 1 &     1 &    12 &  7.7  & cs    &         &          & 0.000 & 0.000 &  -- &\\ %    0.0            \\     ArXe\_2\_1atom      
- 2 &     1 &    54 &  1.8  & cs    &         &          & 0.000 & 0.000 &  -- & \ref{figure:xe_3_in}\\ %    0.0            \\     ArXe\_3\_1atom      
- 3 &     2 &    53 &  3.6  & cs    &         &          & 0.033 & 0.167 &  16.7& \ref{figure:xe_3_in}\\ %2.006$\cdot 10^{-5}$ \\ ArXe\_3\_2atom      
- 4 &  1415 &   642 & 68.8  & cs    &         &          & 7.039 & 2.573 &  73.2& supp.\\ %9.612$\cdot 10^{-4}$ \\ ArXe\_8\_1layer     
- 5 &   561 &  3310 & 14.5  & cs    &         &          &       &       &  85  & \ref{figure:xe_6_lay5}\\ % c6l5
-
-\midrule
- 6 &     1 &    13 &  7.1  & cs    & surface &          & 0.792 & 0.000 & 100.0& \ref{figure:surf}\\ %7.922$\cdot 10^{-5}$ \\ XeAr\_2\_surface    
- 7 &     1 &    13 &  7.1  & cs    & edge    &          & 0.013 & 0.000 & 100.0&\\ %1.320$\cdot 10^{-6}$ \\ XeAr\_2\_edge       
- 8 &     1 &    13 &  7.1  & cs    & vertex  &          & 0.050 & 0.000 & 100.0&\\ %5.013$\cdot 10^{-6}$ \\ XeAr\_2\_vertex     
- 9 &     2 &    13 & 13.3  & cs    &         & closest  & 0.101 & 0.151 &  40.1& \ref{figure:2tops}\\ %2.523$\cdot 10^{-5}$ \\ XeAr\_2\_2top       
-10 &     2 &    13 & 13.3  & cs    &         & middle   & 0.159 & 0.008 &  95.4& \ref{figure:2tops}\\ %1.665$\cdot 10^{-5}$ \\ XeAr\_2\_2midtop    
-11 &     2 &    13 & 13.3  & cs    &         & furthest & 0.159 & 0.002 &  98.9& \ref{figure:2tops}\\ %1.605$\cdot 10^{-5}$ \\ XeAr\_2\_2endtop    
-12 &     1 &    55 &  1.8  & cs    & surface &          & 0.064 & 0.000 & 100.0& \ref{figure:surf}\\ %6.371$\cdot 10^{-6}$ \\ XeAr\_3\_surface    
-13 &     1 &    55 &  1.8  & cs    & edge    &          & 0.048 & 0.000 & 100.0&\\ %4.791$\cdot 10^{-6}$ \\ XeAr\_3\_edge       
-14 &     1 &    55 &  1.8  & cs    & vertex  &          & 0.027 & 0.000 & 100.0&\\ %2.701$\cdot 10^{-6}$ \\ XeAr\_3\_vertex     
-15 &     1 &    54 &  1.8  & in    & edge    &          & 0.077 & 0.000 & 100.0&\\ %7.708$\cdot 10^{-6}$ \\ XeAr\_3\_edge\_in   
-16 &     1 &    54 &  1.8  & in    & vertex  &          & 0.053 & 0.000 & 100.0&\\ %5.258$\cdot 10^{-6}$ \\ XeAr\_3\_vertex\_in 
-17 &     2 &    53 &  3.6  & in    &         &          & 0.117 & 0.055 &  68.1&\\ %1.711$\cdot 10^{-5}$ \\ XeAr\_3\_2in        
-18 &     6 &    49 & 10.9  & in    &         &          & 0.375 & 0.405 &  48.1& \ref{figure:ar_3_6in}\\ %7.796$\cdot 10^{-5}$ \\ XeAr\_3\_6in        
-19 &     6 &    49 & 10.9  & mixed &         &          & 0.292 & 0.674 &  30.3& \ref{figure:ar_3_6in}\\ %9.660$\cdot 10^{-5}$ \\ XeAr\_3\_6\_scat    
-                                                                                                 \midrule
-20 &     2 &    36 &  5.3  & cs    &         &          & 0.117 & 0.151 &  43.6& supp.\\                        % Ar$_{36}$Xe$_{2}$   
-21 &     4 &    34 & 10.5  & mixed &         &          & 0.248 & 0.587 &  29.7& supp.\\                        % Ar$_{34}$Xe$_{4}$   
-22 &     5 &    33 & 13.2  & mixed &         &          & 0.335 & 0.844 &  28.4& supp.\\                        % Ar$_{33}$Xe$_{5}$   
-23 &    13 &    25 & 34.2  & mixed &         &          & 0.828 & 5.414 &  13.3& supp.\\                        % Ar$_{25}$Xe$_{13}$  
-24 &    24 &    14 & 63.2  & mixed &         &          & 1.488 &16.718 &   8.2& supp.\\                        % Ar$_{14}$Xe$_{24}$  
-25 &    25 &    13 & 65.8  & in    &         &          & 1.432 & 4.995 &  22.3& supp.\\                        % Ar$_{13}$Xe$_{25}$  
-26 &    35 &     3 & 92.1  & in    &         &          & 2.017 & 7.051 &  22.2& supp.\\                        % Ar$_{3}$Xe$_{35}$   
-\bottomrule
-\end{tabular}
-\end{table}
-%
-The geometrical properties as well as the total ICD and ETMD decay widths
-of the investigated structures are shown in Table \ref{table:theo_gammas}.
-It is important to remember that the first ICD channel opens at a
-channel opening distance of \unit[7.58]{\AA}. In the smallest
-clusters with only one argon layer around each
-xenon atom, the Ar-Xe pair distances are below that value, therefore 
-no ICD can take place. Also, by definition, two Xe atoms are
-required for ETMD(3), hence it cannot occur in clusters with only one xenon atom.
-%Because secondary electrons are observed in the experimental spectra
-%we exclude all structures without any signal from our further
-%discussions.
-%
-\begin{figure}[H]
- \centering
- \includegraphics[width=8.0cm]{surf.pdf}\\
- \includegraphics[width=8.0cm]{R_comp.pdf}
- \caption{
- %
- Top panel: Simulated electron emission spectra of an Ar 3s vacancy in 
-          argon clusters
-          consisting of 13 and 55 atoms, with an additional xenon atom residing
-          on top of one of the argon surfaces.
-          Bottom panel: Distribution of Ar-Xe distances $d$ in the studied ArXe
-          clusters. The ICD channels to final states involving Xe 5p$_{3/2}^{-1}$ and 
-          5p$_{1/2}^{-1}$ vacancies open at \unit[7.58]{\AA} and
-          \unit[36.00]{\AA}, resp.; the former distance is marked by a vertical dotted line. 
-          Only pairs at longer interatomic
-          distances contribute to the electron emission spectra.
-          Larger Ar-Xe distances, as found in the larger cluster,
-          correspond to features at a higher kinetic energy of
-          the ICD electron (top panel).}
- \label{figure:surf}
-\end{figure}
-
-%In the investigated structures several different aspects have to be
-%taken into account which we will discuss separately if possible
-%on selected structures.
-
-We will now discuss features of several structures, using selected examples.
-First we consider clusters having an argon core of 13 and 55 atoms plus a single xenon
-atom on one of the surfaces (see Figure \ref{figure:cluster_3_overview}a
-for the structure of clusters with the 55 atoms core).
-Secondary electron spectra simulated for these systems are shown in Figure \ref{figure:surf}, top panel.
-%two different argon core sizes one consisting
-%of 13 and one consisting of 55 atoms with one xenon atom on one of
-%the surfaces (see Figure \ref{figure:cluster_3_overview} Panel a)
-%for the 55 atom core). The simulated secondary electron spectra are
-%shown in Figure \ref{figure:surf} Panel 1.
-
-Because the structures contain only one xenon atom, ETMD(3) is not possible, only ICD is expected. 
-%Both spectra show several smaller peaks which
-%are convoluted into one single peak with a maximum at
-%approximately \unit[0.2]{eV}. 
-%In comparison to the 13 argon atoms core
-%spectrum t
-The spectrum pertaining to the clusters with larger (55 atoms) Ar core shows
-signals at higher energies of the secondary electron. These features
-can be explained by investigating the Ar-Xe distance distributions
-in the clusters, shown
-in the bottom panel of Figure \ref{figure:surf}. 
-Every different value of the atom pair distance
-results in a different energy of the secondary electron and only pairs
-with a distance of larger than the channel opening distance
-(dashed gray line) will contribute
-to the spectrum. 
-In our model, there is a one-to-one correspondence between interatomic distance $d$ and kinetic energy of the ICD electron.
-The larger the interatomic distance, the higher is the
-kinetic energy of the secondary electron for a given channel.
-%Since the cluster with an Ar core of 55 atoms is larger, and therefore
-%contains Ar-Xe pairs with larger distances, its spectrum 
-Therefore, the spectrum of the cluster with a 55 atoms core extends to higher energies.
-%energies as well.
-This relation between ICD energy and cluster size holds true for all cluster structures.
-%This explains why the ICD spectrum for larger clusters extends to higher energies, and holds for all cluster structures.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{2tops.pdf}
- \caption{Simulated electron emission spectra of an Ar 3s vacancy in 
-          argon clusters consisting of 13
-          argon atoms with two additional xenon atoms on top of two different
-          argon surfaces. ICD and ETMD spectra are shown for three
-          different relative positions of the two xenon atoms. If 
-          the xenon atoms are close to each other, an ETMD process is
-          clearly visible. In the other two cases the spectra are dominated by
-          the ICD spectrum.}
- \label{figure:2tops}
-\end{figure}
-%
-For clusters with more than one xenon atom, also ETMD(3) is possible.
-Depending on the positions of the xenon atoms relative to each other and to the Ar core, the spectra are expected to be different.
-As an example, we discuss clusters with a core of 13 argon atoms and two xenon atoms on different surfaces. 
-Their xenon content is \unit[13.3]{\%} and thus close to the experimental one of \unit[10-12]{\%} for the lowest xenon admixture.
-The cluster structures were illustrated in Figure \ref{figure:cluster_2_overview}, simulated spectra are shown in Figure \ref{figure:2tops}.
-In all three cases, both ICD and ETMD(3) are energetically allowed. The ICD
-spectra do not change qualitatively by adding the second xenon.
-%either identical or at least very similar to the ones for
-%cluster with a single  consisting of one
-%convoluted peak at approximately \unit[0.2]{eV}. 
-However, the ETMD(3) spectra
-are very sensitive to the relative position of the two xenon atoms.
-Two aspects have to be taken into account: an energy shift of the peaks due
-to different charge distances in the final state (i.e. the interatomic Xe-Xe
-distance) and the decrease of the decay width with $R^{-6}$, $R$ being the distance
-between the electron transfer unit and the xenon atom ionized in the final state.
-The larger the distance between the xenon atoms, the higher are the energies
-of the secondary electrons and the smaller are the decay widths. 
-Therefore, a
-significant contribution from ETMD(3) compared to ICD is only
-seen if the two xenon atoms reside on two adjacent
-surfaces. 
-%{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
-The three energetically separated peaks in the ETMD(3) spectrum pertain to different combinations of the Xe 5p$_j^{-1}$ vacancy states, which have a substantial fine-structure splitting (see Table \ref{tab:valence}).
-%\ref{sec:exp_results}).
-%
-%The threefold peak structure of the ETMD(3) peak does in contrast to
-%the ICD spectrum not stem from different triple structures but from the
-%four different decay channels for one triple structure.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{ar_3_6in.pdf}
- \caption{Same as Figure \protect\ref{figure:2tops}, for clusters consisting of
-          55 atoms, 6 out of which are xenon atoms. These are either grouped
-          on one side of the cluster (label `group') or evenly distributed
-          in the cluster interior (label `scattered').}
- \label{figure:ar_3_6in}
-\end{figure}
-%
-For the 55 atoms clusters, a xenon content of \unit[10--12]{\%}
-corresponds to six xenon atoms out of a total of 55 atoms. These can form a connected 
-group in one part of the cluster or can be evenly distributed,
-as shown in Figures \ref{figure:cluster_3_overview}b and \ref{figure:cluster_3_overview}c. The
-ICD and ETMD(3) spectra for these structures are shown in Figure \ref{figure:ar_3_6in}.
-
-For both cases the overall ICD spectra are very similar, and show a maximum at a kinetic energy of approximately \unit[0.3]{eV}. 
-In case of grouped xenon atoms, the ICD spectrum extends to slightly higher energies, corresponding to ArXe pairs at slightly larger spatial distances.
-A more significant difference is observed in the ETMD(3) spectra. 
-The interatomic xenon distance is shorter in clusters, in which the xenon atoms form a connected group.
-Hence, the triple structure of the ETMD(3) spectrum is seen at lower kinetic energies. 
-Additionally, the probability for an electron
-transfer from a xenon to an argon atom decreases exponentially with the
-interatomic distance. Therefore, only those xenon atoms which have direct
-argon atom neighbours have a significant contribution to the
-total decay width, and the total ETMD(3) decay width is lower for the structure with
-grouped xenon atoms than for
-the structure with evenly distributed xenon atoms (see Table \ref{table:theo_gammas}).
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{xe_3_in.pdf}
- \caption{Same as Figure \protect\ref{figure:2tops}, for argon clusters with
-          one or two xenon atoms in the core of the cluster (55 atoms total). 
-          All ICD and ETMD channels are closed, if the cluster contains only 
-          a single xenon atom. For clusters with two xenon atoms
-          in the core, the first ICD channel is open for some pairs,
-          and additionally ETMD is possible for multiple triples. Due to a
-          different distance distribution compared to the clusters with an argon
-          core (Figure \protect\ref{figure:2tops}), 
-          the ICD peak is shifted to higher kinetic energies.}
- \label{figure:xe_3_in}
-\end{figure}
-%
-For comparison with the previous assumptions of a xenon core surrounded
-by argon atoms we investigated clusters of 13 and 55 atoms with one or two
-xenon atoms in the core. Some of the corresponding
-spectra are shown in Figure \ref{figure:xe_3_in}.
-
-%For the clusters with only one xenon atom in the core and the ionization
-%energies used for the simulation of the secondary electron energies
-%all ICD channels are closed. Since the cluster contains only one xenon atom,
-%an ETMD(3) is not possible. Hence there is no signal to be expected at all.
-For a core consisting of two xenon atoms both an ICD and an ETMD(3) spectrum
-can be seen. Compared to the cluster structures involving an argon core, the ICD peak is
-shifted to higher ICD electron energies. 
-Additionally, the ICD and ETMD(3) spectra overlap.
-For ETMD(3), only three of the four different decay channels are
-energetically allowed.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{c6l5.pdf}
- \caption{Same as Figure \protect\ref{figure:2tops},
-          for a large cluster consisting
-          of a xenon core of 561 atoms surrounded by five complete layers of
-          argon atoms (Xe content: 14.5\,\%) for both an icosahedral and
-          cuboctahedral basic structure.
-          The ICD and ETMD peak overlap such that the ETMD peak
-          is unlikely to be visible.}
- \label{figure:xe_6_lay5}
-\end{figure}
-%
-In the first experiments very large argon-xenon clusters of 
-$\approx 4380$ atoms with a xenon content of \unit[19]{\%}
-were measured,\cite{Mucke_phd}
-which we in one example approximate by a cluster consisting of 561 xenon
-atoms surrounded
-by five layers of argon atoms (3871 atoms in total). In order to take the
-better stabilization of charges in larger clusters into account, the
-ionization energies of the XL clusters (see Table \ref{tab:valence})
-were used.
-The spectra are shown in 
-Figure \ref{figure:xe_6_lay5}.
-
-Compared to the small clusters with a xenon core in Figure \ref{figure:xe_3_in}
-the ICD peak is broadened and shifted to higher ICD electron energies which is
-expected due to the larger interatomic Ar-Xe distances in the large cluster and
-the better stabilization of charges, which is relevant mostly for the final state, but also the initial state.
-The ETMD(3) peak is shifted to slightly higher energies as well. This allows opening of the
-fourth decay channel, pertaining to Xe 5p$_{1/2}^{-1}$ Ar 3p$_{1/2}^{-1}$ final states.
-
-We also note that the percentage of decay via ICD is practically
-independent of the Xe content for large clusters with a Xe core, Ar shell structure.
-This can be expected, as both decay processes are most pronounced for the
-atoms in the interface region of the xenon core and the argon shell.
-The ETMD(3), depending on the electron transfer from one xenon atom to the
-initially ionized argon atom, and hence on the corresponding orbital overlap,
-is purely an interface effect that involves the argon atoms with direct xenon
-neighbours, and the two xenon layers closest to the argon shell.
-The ICD has a stronger long range character, due to which the description
-of decays with partners of at least twice the smallest channel opening
-distance is necessary for clusters. However, the bigger the clusters are,
-the more homogeneous does the interface region become for clusters of
-different sizes. This manifests itself in the distribution of relevant
-Ar-Xe pair distances (compare Figure \ref{figure:surf}, lower panel).
-As a consequence, the ICD spectra of two large clusters of different size
-hardly differ.
-
-\clearpage
-
-%\input{exp_results}
-\section{Experimental Results}
-\label{sec:exp_results}
-%
-%
-\begin{table}
-\caption{Properties of the outer valence spectra of mixed ArXe clusters. 
-Spectra of pure Ar and Xe clusters are included for reference. 
-All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV). 
-Binding energies $\EB$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit. 
-The average Xe content of the cluster ensemble, Xe$_{\rm cl}$, was determined from the areas of the respective photolines, corrected by their atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}.
-Uncertainties are estimated as $\pm$3\,\% for the Xe content and 0.05~eV for the binding energies. 
-The row labelled `(th.)' gives the binding energies used in the simulations of this paper, and the last row their atomic counterparts. 
-Values for Ar 3p in the last row refer to the fine structure states.
-\label{tab:valence}}
-\begin{tabular}{ l c c c c c c c c}
-%
-\toprule
- \multicolumn{2}{r}{size} &  Xe$_{\rm in}$& $\EB$ (eV)& $w$ (eV)& \multicolumn{2}{c}{$\EB$ (eV)}  & $w$ (eV) &  Xe$_{\rm cl}$ \\
-%
- \multicolumn{2}{r}{(label)}&  (\%) & Ar 3p & Ar 3p & Xe 5p$_{1/2}$ &  Xe 5p$_{3/2}$ & Xe 5p$_{3/2}$  &  (\%) \\
-\midrule
-% Ar, from Marko
- Ar & (1) &&  15.3  &  1.1 & & & &  \\
-% Ar, from Marko 
- Ar & (2) &&  15.1  &  1.3 & & & &  \\
-%
-%  columns in the following: energies c.g. 51-plt-oval, widths Marko Diss., Xe content Marko Diss
-% 1103 676, 679
- ArXe & S &1.2 & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
-% 1103 670
- ArXe & M &1.2 & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
-% 1103 671
- ArXe & L &1.2 & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
-% 1103 663
- ArXe & S &3.0 & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
-% 1103 640
- ArXe & M &5.0 & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
-% 0506 
- Xe &  & & & & 12.76 & 11.19 & 1.18 & 100\\
-%
-\midrule
-%
-%  1004  886  (UHe, c.g. + roi values)
- ArXe & XL &2.5 & 15.15 & 1.3 & 12.59 & 11.01 & 1.24 & 19\\
-%
-\midrule
-% Date: Wed, 20 Jan 2016 11:27:39, From: Elke Fa?hauer <elke.fasshauer@uit.no>
- Ar, Xe & (th.) && 15.3 && 13.0 & 11.5 &&\\
-%
- \multicolumn{2}{l}{(atomic)\cite{velchev,sansonetti}} && 15.76|15.94 && 13.43 & 12.13 &&\\
-%
-\bottomrule
-\end{tabular}
-\end{table}
-
-\subsection{Outer valence spectra}
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_oval_1.pdf}
- \caption{
-Outer valence photoelectron spectra of mixed Ar-Xe clusters, in comparison to the pure species. 
-(a) shows the outer valence region of homogeneous Ar and Xe clusters, respectively (see text for details). 
-The two lower panels show spectra of the mixed species with different mean size. 
-Sharp lines marked `m' (for `monomer') result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states. 
-Labels in (b) and (c) give the Xe content in the expanding gas mixture (Xe$_{\rm in}$), which is lower than the Xe content observed in the heterogeneous clusters (Xe$_{\rm cl}$). 
-The photon energy was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
-%{\color{red}{Die Stabilisierung der Xe-bulk Atome ist in den gemischten Cluster
-% höher als in den gemischten Clustern. Das ist ungewöhnlich. Habt ihr hier
-% verschiedene CLustergrößen?}}
-}
- \label{figure:oval1}
-\end{figure}
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_oval_2.pdf}
- \caption{
-Outer valence photoelectron spectra of mixed Ar-Xe clusters from gas mixtures with different Xe concentration. 
-For better visibility, a scaling factor is applied to the Xe part of the spectrum in panel (a).
-See Figure \ref{figure:oval1} and text for details.
-}
- \label{figure:oval2}
-\end{figure}
-
-Figure \ref{figure:oval1} shows the outer valence spectra of small and large ArXe clusters, compared to clusters of the pure gases. 
-Qualitatively similar spectra have been published without detailed discussion in ref \citenum{lindblad}.
-Differences are seen in particular for the Ar component. 
-In pure Ar clusters, outer valence photoionization leads to a broad band, caused both by spin-orbit coupling and crystal field splitting. 
-The relative importance of these two mechanisms remains under debate.\cite{hergenhahnprb,rolles,foerstel_arg1_2010} 
-For larger clusters (e.g.
-$\langle N\rangle = 190$, black trace), the maximum at low binding energies becomes more pronounced, and is identified with emission from the cluster interior.\cite{hergenhahnprb,rolles}
-At the particular photon energy selected here, atop of this band a sharp feature is also visible (in Figure \ref{figure:oval1} at a kinetic energy of about 1.8 eV).
-For larger clusters (above $\langle N\rangle \approx 100$), over a range of photon energies of about 3 eV, its appararent binding energy changes in a way which is reminiscent to photoemission of crystalline bulk matter (`dispersion').\cite{foerstel_arg1_2010,foerstel_arg2_2011}
-
-Ar 3p spectra of the smaller mixed clusters (Figure \ref{figure:oval1}c, Figure \ref{figure:oval2}) show neither of these traits.
-Rather, the Ar band is symmetric, less wide than in the pure clusters and at a higher binding energy.
-Even for very large clusters (Figure \ref{figure:oval1}b) the asymmetry of the 3p band and the `dispersing feature' do not appear.
-We characterize the spectral shape by giving a single value for the Ar 3p binding energy, and the FWHM of the feature.
-Values for different expansion parameters, and for both Ar and Xe valence lines, are collected in Table\ \ref{tab:valence}.
-
-We find experimentally that clusters we have produced have a Xe content Xe$_{\rm cl}$ between 10\,\% and 50\,\%.
-A slight decrease of the binding energy with cluster size is seen for all outer valence lines, and is attributed to a larger final state polarization energy in larger clusters.
-
-For further interpretation of the shape of the Ar peaks we refer to photoemission spectra of condensed Ar monolayers, measured in several settings.\cite{jacobi,jacobi2}
-Spectra were reported for physisorption of Ar on two different metal single crystal substrates, and for Ar atop of a Xe spacer layer adsorbed on the metal.
-While the binding energy depends on the substrate, the spectral shape is very similar in all cases. 
-Most spectra were recorded for emission along the surface normal, and show a double peak split by about 0.5 eV, leading to a structure with $w$ about 1 eV.
-Although the splitting is larger than the gas phase fine structure split of 0.18 eV, the pertaining states have been assigned to Ar 3p$_{1/2}$ and 3p$_{3/2}$.
-A crystal field splitting of the 3p$_{3/2}$ state has been assumed to be also present, but with a smaller value of 0.1-0.2 eV, approx.\cite{jacobi2} 
-The spectrum clearly changes when going to an emission angle of 40$^\circ$ with respect to the surface normal (Figure 2 in ref \citenum{jacobi2}).
-The higher binding energy peak significantly loses in intensity, and the spectrum is now dominated by a single peak comprising both crystal field split substates of Ar 3p$_{3/2}$, with a FWHM ($w$) of only 0.4 eV.
-As our measured spectrum is comprised of contributions recorded under all emission angles with respect to the cluster surface, grazing emission will be the rule.
-We therefore believe that the arguments given above make it plausible that only a single peak is observed in all our spectra.
-
-Emission from the Xe 5p state shows a much larger fine structure splitting then from the Ar 3p state; it dominates the spectrum even in clusters (where other broadening mechanisms are also present).
-The shift of the cluster bands with respect to the monomer lines in the largest mixed clusters we have probed (Figure \ref{figure:oval1}b) are similar to the ones in the pure Xe spectrum, the scaling law size of which is at somewhat more than five filled shells.
-This indicates an approximate upper limit for the size of the Xe core in our mixed clusters, as their binding energy shift might be somewhat higher than the one in pure clusters, due to polarization of covering Ar layers.
-Xe cluster features in the spectra of mixed clusters appear less asymmetric than the pure Xe spectrum, and also less asymmetric as some the ArXe spectra shown in ref \citenum{lindblad}.
-This might be caused by the difference in photon energy ($h\nu = 90$ eV in ref \citenum{lindblad} and for the pure Xe spectrum, $h\nu = 32$ eV for the mixed ArXe spectra in this work).
-% For the mixed clusters, the Xe band broadens and shifts towards lower binding energy for larger size clusters.
-%For pure Xe clusters, an asymmetry observed in the Xe 5p$_{3/2}$ part has no counterpart in the respective spectra from the mixed clusters.
-%This might be caused by the difference in photon energy, as can be seen from a comparison to literature spectra (ArXe at $h\nu = 90$ eV in ref \citenum{lindblad}, Xe at $h\nu = 20$ eV in ref \citenum{rolles}).
-%For the largest clusters, the nominal size yielded from the jet parameters applied to a pure Xe expansion would correspond to clusters in which bulk atoms far outweigh those on the surface.
-%At least for the 5p$_{1/2}$ photoelectron line, this would be seen as a clear asymmetry towards the low binding energy side, which is not observed in our spectra.
-
-In Figure \ref{figure:oval2}, we compare the outer valence spectra of clusters with similar expansion conditions, but different composition of the gas mixture.
-A Xe-rich mixture obviously leads to clusters with more intense Xe photolines, but besides that the main change consists in a narrowing of the Ar band.
-A comparison with the Ar monomer features (clipped in the Figure) also shows an increased degree of condensation for the Ar gas in the expansion.
-
-For the smallest clusters we have produced, a possible model is provided by calculated minimum energy structures of Ar$_N$Xe$_{38-N}$ (Figure 7 in ref \citenum{marques}).
-We there see that for a Xe content of less than 60\,\%, core-shell systems are {\it not} formed, and although the Xe atoms tend to connect, the degree of Ar-Xe mixing is large.
-While for low Xe content (approx. 10\,\%), some Ar atoms have only Ar nearest neighbours, for larger Xe content all Ar atoms seem to see both Ar and Xe nearest neighbours.
-We believe this leads to the Ar 3p narrowing pointed out above.
-For Figure \ref{figure:oval2}, possibly, some clusters of our ensemble already are in the core-shell regime, which would lead to an even lower 3p width.
-
-For the largest clusters we have produced (Figure \ref{figure:oval1}b), the low binding energy of the Xe lines and the broadening of the Ar feature without appearance of the `bulk Ar'-maximum, supports formation of a Xe core covered by at least two layers of Ar.
-If the scaling law size for a pure Ar expansion is taken as the lower limit for the cluster size, from the observed Xe content we arrive at clusters composed of a Xe core with four layers, covered by three layers of Ar (see Supporting Information).
-
-Finally, comparing Figure \ref{figure:oval2} to Figure \ref{figure:oval1} reveals that much larger changes in the valence emission spectra occur by changes in size than by changes of the (relative) Xe content.
-This finding is supported by the spectra shown in ref \citenum{lindblad}.
-%
-%
-\subsection{Inner valence spectra}
-%
-We now focus on the Ar inner valence (3s) vacancy states. 
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.8cm]{figure_ival.pdf}
- \caption{
-Photon excited electron spectra of mixed Ar-Xe clusters in the inner valence region.
-Symbols show the Ar 3s photoline from clusters (`cl') and uncondensed Ar monomers (`m'), atop of a background resulting from inelastic intracluster scattering of outer valence photoelectrons (`excitonic satellites').\protect\cite{hergenhahn2002}
-The photon energy was $h\nu = 32$ eV.
-Panel (a) shows all electrons accumulated.
-For the same conditions, in panel (b) we only show electrons that were detected in coincidence with a secondary electron of lower kinetic energy.
-The black solid trace in (a), and red solid trace in (b) result from a least squares fit to the cluster part of the spectrum. 
-The red solid trace in (a) is the fit shown in (b), divided by the detection efficiency of the spectrometer of 0.6.
-Panels (c) and (d) show the same type of data for smaller clusters with a lower Xe content.
-See text for details.
-\label{figure:ival}
-}
-\end{figure}
-
-Figure\ \ref{figure:ival} shows the Ar part of the inner valence spectrum for representative ArXe clusters. 
-The total photoelectron signal looks similar to literature spectra for pure Ar clusters.\cite{feifel,zhang} 
-A low energy tail seen for the Ar 3s monomer line results from the transmission properties of the electron spectrometer, together with the strongly positive angular distribution parameter of this line.\cite{zhang,kruit}
-The Ar 3s cluster line shows no splitting into bulk and surface components, different to the literature on pure clusters but in agreement with our discussion of the outer valence spectra. 
-The binding energy of the cluster line has values between 28.85 and 28.70 eV for all cluster ensembles with size label S-L, and 28.67 eV for the largest clusters measured. 
-A small, but systematic decrease of the binding energy is observed when the cluster size is increased. 
-The value assumed in the simulations is 28.7 eV.
-
-If we produce a spectrum only from those electrons recorded as part of a two-electron coincidence (electron pair with kinetic energies ($e_1,e_2$)) the apparent intensity drops (compare panel b to a, and d to c in Figure \ref{figure:ival}).
-This can partly be attributed to the finite detection efficiency of the spectrometer. 
-Moreover, the monomer part of the Ar 3s signal completely disappears, as 3s photoionization of an uncondensed Ar atom in the gas jet cannot lead to emission of a second electron. 
-Further features of these diagrams and the least squares fits shown in the Figure are discussed below.
-%
-%
-\subsection{ICD/ETMD spectra}
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_icd_12.pdf}
- \caption{
-Energy spectrum of all coincident secondary (ICD or ETMD) electrons of kinetic energy $e_2$ pertaining to primary electrons of kinetic energy $e_1$ in the Ar 3s binding energy region. 
-Spectra were recorded with a photon energy of $h\nu = 32$~eV. 
-Black error bars show the data points for the smallest clusters measured (`S'), two larger clusters sizes are shown by the red and blue traces. 
-Error bars for the latter are smaller than the ones shown and have been omitted.
-For better comparison, all spectra are shown area-normalized. 
-}
- \label{figure:icd_12}
-\end{figure}
-%
-%
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_icd_l.pdf}
- \caption{
-Energy spectrum of all coincident secondary (ICD or ETMD) electrons, kinetic energy $e_2$, for clusters of the same size, but from gas mixtures with different Xe concentration.
-See Figure \protect\ref{figure:icd_12} for details.
-}
- \label{figure:icd_l}
-\end{figure}
-%
-In Figure \ref{figure:icd_12}, we show the spectra of ICD/ETMD electrons pertaining to emission of an Ar 3s cluster photoelectron. 
-Due to their low kinetic energy, without use of a coincidence method they could hardly be separated from the background of inelastically scattered photoelectrons.\cite{mucke}
-This and the following Figure constitute the central experimental result of the article.
-Spectra recorded at $h\nu = 34$ eV as a cross-check quantitatively agree to those shown here.
-This underpins our assignment of this intensity to an autoionization process.
-Further details on the data acquisition and analysis methodology, as well as the 34~eV spectra, are given in the Supporting Information.
-
-Spectra for the three different cluster sizes in Figure \ref{figure:icd_12} are significantly different: Spectra for the larger clusters acquire more intensity in the 1-1.5 eV region and have less intensity for energies below 0.5 eV.
-In contrast to that, the ICD/ETMD spectrum hardly varies when the composition of the expanding gas mixture, and with that the relative Xe content of the clusters, is changed (Figure \ref{figure:icd_l}).
-The full set of ICD/ETMD spectra is shown as Supporting Information.
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=8.5cm]{figure_eff.pdf}
- \caption{
-Efficiency of the decay of Ar 3s ionized states in ArXe clusters by emission of a secondary electron via ICD or ETMD.
-Values are arranged by Xe content of the initial gas mixture (`+' symbols: 1.2\,\%, asterisk: 3\,\%, triangle: 5\,\%).
-Symbol sizes indicate the photon energy (large symbols: 32 eV, small: 34 eV), and color indicates the cluster size (black symbols: S, red: M, blue: L).
-See text for details.
-}
- \label{figure:eff}
-\end{figure}
-%
-We now discuss which fraction of Ar 3s vacancy states relaxes via ICD or ETMD.
-A method to derive this information has been established by some of us.\cite{foerstel_2013}
-Briefly, we correct the intensity of the Ar 3s photoline in the coincident spectra by the detector efficiency, and divide it by the total (coincident and non-coincident) Ar 3s intensity.
-The result gives the branching ratio of decay via ICD/ETMD vs. the sum of all channels, including those not involving electron emission.
-(If all Ar 3s vacancies decay by emission of another electron, the coincident and non-coincident count rate differ only by the probability for the spectrometer to actually detect the secondary electron.
-This figure has been determined as 0.6 for this data set, in the same way as discussed earlier.\cite{mucke_review})
-To arrive at quantitative results, we have performed least squares fits of the non-coincident and coincident $e_1$ spectra.
-The fits assumed one or two Gaussian peaks, resp., atop of a background modelled by two more Gaussian curves with very large widths.
-The peak pertaining to the Ar 3s cluster photoline, with the background added, is shown by the black solid trace in Figure \ref{figure:ival}a and red solid trace in Figure \ref{figure:ival}b.
-Moreover, the line labelled `c.fit/det.' shows the fit to the coincident events, corrected by the detection efficiency, and plotted atop of the non-coincident intensity. 
-This virtually agrees with the fit to the total spectrum in Figure \ref{figure:ival}a, but not in \ref{figure:ival}c. 
-The corresponding figure for the ICD/ETMD efficiency comes out as one for \ref{figure:ival}a, and significantly smaller than one for \ref{figure:ival}c.
-Figure \ref{figure:eff} shows all results of this analysis.
-The error in the autoionization efficiency shown is mainly determined by uncertainties in the peak/background separation.
-%(Our choice for the background shape is shown in Figure \ref{figure:ival}.)
-For the gas mixture with a Xe$_{\rm in}$ of 1.2\,\%, we therefore show results from fits using two different choices of the background shape in Figure \ref{figure:eff}.
-Statistical errors are much smaller than the differences between the pairs of values arrived at such.
-
-We found an Ar 3s autoionization efficiency which, for clusters with the lowest Xe content (Xe$_{\rm cl}$ approx.
-10-12\,\%), is smaller than unity, and further decreases with decreasing cluster size.
-For larger Xe$_{\rm cl}$, the values are compatible with unity, within the accuracy of our experiment.
-
-%\input{theo_discussion}
-\section{Discussion
-\label{sec:discussion}}
-%
-%We have discussed the experimental spectra in Section \ref{sec:exp_results} and
-%the expected features of spectra for different cluster types in
-%Section \ref{sec:th_results}. In this section we combine the experimental and theoretical
-%results in order to determine the structure of the noble gas clusters.
-%
-%The simulated secondary electron spectra for the xenon core structures
-%(see Figure \ref{figure:xe_3_in})
-%show an ICD peak at higher energies than those structures with added xenon
-%atoms on the surface. This does not fit to the experimentally determined
-%spectra and hence we consider an argon core to be more probable for the
-%small measured clusters.
-%
-%The experimental spectra in Figure \ref{}
-%show a broadening of the secondary electron peak with increasing
-%pressure (?) and hence cluster size just as can be expected from
-%the theoretically simulated spectra in Figure \ref{figure:surf}.
-%
-%From the theoretical simulations of larger small clusters
-%having the same xenon content as experimentally observed a clearly
-%visible ETMD peak is to be expected as shown in Figure \ref{figure:ar_3_6in}.
-%However, the experimental spectra do not show a signal in the energy
-%region of \unit[1.5--6.5]{eV}. From this we conclude that the clusters
-%measured were smaller than 55 atoms containing only very few xenon atoms.
-%Additionally, if the cluster contains more than one xenon atom, they are
-%not expected to be close because of an otherwise visible ETMD peak
-%(compare Figure \ref{figure:2tops}).
-%
-%The large clusters with a large xenon content can be expected to have
-%a xenon core being surrounded by argon layers and hence, both ICD and
-%ETMD should be visible in the spectrum. Unfortunately, the ICD and ETMD
-%peaks overlap such that the two processes can not be distiguished.
-%
-We now would like to interpret our experimental findings in view of the simulated results described in Section `Theoretical Results'.
-Figure \ref{figure:eff} shows that for Ar 3s$^{-1}$ states autoionization by either ICD or ETMD is the only mode of relaxation, except for the clusters with the smallest Xe content.
-We consider this a remarkable result, because ICD of these states is only possible with a Xe atom in the second coordination shell of the decaying Ar vacancy (or shells even further apart), which significantly slows down the ICD process.
-Also decay rates for ETMD were found to be small in early studies of this effect.\cite{zobeley}
-Nevertheless, even in this situation the non-local autoionization channels foreclose radiative decay.
-
-% lowest kinetic energy is the first point of energy raster for t-E code of 52-proc-spec
-Structurally, all experimental ICD/ETMD spectra have a maximum at or near the lowest kinetic energy that could be measured (50~meV), and decrease in intensity to less than half for kinetic energies already below one eV.
-Qualitatively, this shape fits to the ICD contributions in the autoionization spectra discussed in the `Theory' section, but not to the ones from ETMD. 
-The calculated ETMD spectra have a typical three-fold structure with peaks between 3.5-5~eV, 1.5-2.5~eV and around 0 eV kinetic energy. 
-The former two features seem not to be present in the experimental spectra. 
-Due to restrictions in the detector electronics, electron pairs with very similar kinetic energy cannot be detected. 
-The highest kinetic energy for an autoionization electron that can be detected in coincidence with a photoelectron of $\sim3.5$~eV ($h\nu = 32$~eV) is around 2.5~eV.
-Very weak intensity is observed at this energy, and also at higher $e_2$ energies that can be probed at $h\nu = 34$~eV (Supporting Information).
-
-As a cross-check for our theoretical methods we have calculated the radiationless decay spectrum of Ar 3s$^{-1}$ in ArKr, which may arise {\it only} from ETMD(3),\cite{foerstel} and arrived at qualitative agreement with the experimental data.\cite{arkr}
-
-The size-dependent trend within the experimental data is in qualitative agreement to the change in the calculated spectral shape for ICD in systems of increased size (compare Figure~\ref{figure:2tops} to \ref{figure:xe_3_in} and \ref{figure:xe_6_lay5}.)
-
-We are therefore lead to the conclusion that the autoionization spectra we incur are dominated by ICD to non-nearest neighbour atoms, while the intensity of the ETMD channel is low. 
-We would like to recall the factors that lead to a propensity for decay via one or the other mechanism, which have been discussed in the `Theoretical Results'-section.
-For ETMD to occur with a measurable rate, two Xe atoms have to be present in the vincinity of the decaying Ar atom (Figure \ref{figure:2tops}).
-Should that be the case for a large part of the Ar atoms in some cluster structure, ETMD can even dominate over ICD (Figure \ref{figure:ar_3_6in} and Supporting Information).
-Model structures shown in Figures \ref{figure:2tops} and \ref{figure:ar_3_6in} have a Xe content similar to the lowest one probed in our experiment ($\sim$11\,\%).
-For a higher Xe content, ETMD will always dominate the spectra if the two species are given the chance to mix, as e.g.
-in the calculated minimum energy structures of $N=38$ ArXe clusters (Supporting Info).
-On the other hand, in core-shell systems decay via ETMD is probable only for Ar atoms in the interface layer, as this mechanism requires some wavefunction overlap between Ar and one of the Xe atoms involved.
-For the core-shell systems we have investigated, the likelihood of decay via ETMD stays below 25\,\% even for a Xe content above 50\,\% (Table \ref{table:theo_gammas}).
-
-In summary, the two structural motifs that can best be reconciled with our experimental data are
-\begin{enumerate}
-	\item small clusters containing only few Xe atoms that are spread out to distant positions on the cluster surface, and
-	\item systems with a compact Xe core and Ar outer layers.
-\end{enumerate}
-These structures are compatible with the findings of Lindblad {\it et al.}\ from core level photoelectron spectroscopy, who proposed the former structure for the smallest clusters in their study, and the latter for larger ones.\cite{lindblad}
-As even in these two cases intensity for decay via ETMD would not vanish completely, we have to leave it open though whether other mechanisms are present, which further suppress ETMD vs. ICD.
-
-While in early work on ICD it has almost been a paradigm that the decay involves two {\it neighbouring} atoms or molecules,\cite{hergenhahn_review} more recently significant intensity for non-nearest neighbour ICD has been found also in other systems.
-One example is Ne-Ar after Ne 2s ionization, where decay to Ar in the second coordination shell is clearly visible despite the fact that in this system decay involving nearest neighbours is energetically allowed.\cite{fasshauer2014}
-A further theoretical delineation of the respective factors has recently been presented by one of us.\cite{fasshauernjp}
-
-%\input{summary}
-\section{Summary}
-%
-We have presented comprehensive experimental and theoretical data for the
-autoionization of inner valence ionized states in ArXe clusters.
-Both ICD and ETMD are allowed for most cases we considered.
-Because of energetical reasons ICD requires a separation of the final state
-vacancies of \unit[7.58]{\AA} or more, which is about two times the typical
-Ar-Xe distance.
-We found that autoionization has an efficiency of 0.8 to 1.0 within the
-experimental accuracy, that is it dominates over other modes of relaxation.
-By comparing our measured spectra to calculations, we identified `long range'
-ICD as the most important decay mode and were able to determine the most
-probable structural motifs to be a xenon core surrounded by several argon layers
-for large clusters and argon clusters with with very few xenon atoms spread out
-over the surface.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The "Acknowledgement" section can be given in all manuscript
-%% classes.  This should be given within the "acknowledgement"
-%% environment, which will make the correct section or running title.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{acknowledgements}
-\begin{acknowledgement}
-%
-We thank HZB for the allocation of synchrotron radiation beamtime, and the
-Deutsche Forschungsgemeinschaft for funding via the Forschergruppe 1789.
-E. F. gratefully acknowledges the Research
-Council of Norway through a Centre of Excellence Grant (Grant No.\ 179568/V30)
-for funding.
-%
-\end{acknowledgement}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The same is true for Supporting Information, which should use the
-%% suppinfo environment.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{suppinfo}
-
-%This will usually read something like: ``Experimental procedures and
-%characterization data for all new compounds. The class will
-%automatically add a sentence pointing to the information on-line:
-
-%\end{suppinfo}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The appropriate \bibliography command should be placed here.
-%% Notice that the class file automatically sets \bibliographystyle
-%% and also names the section correctly.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliography{arxe}
-
-\end{document}
+and data from the literature given in Tables II and III of
+Ref.\ \citenum{Fasshauer13}.

### 2019-03-22 resubmit_2/replace.py

@@ -1,0 +1,39 @@
+#! /opt/local/bin/python
+
+# IMPORT
+import os
+import sys
+import shutil
+import string
+import glob
+import math
+
+ls = os.listdir('.')
+ls.sort()
+
+count = 0
+
+rootdir = os.getcwd()
+#outfile = open('','w')
+
+for filename in glob.glob("master.tex"):
+#for filename in glob.glob("schale08.tex"):
+   print filename
+   infile = open(filename, 'r')
+   outfile = open('tmpfile', 'w')
+
+   
+#   replacements = {'includegraphics[scale=0.5]':'input', '/compl':'/schale', '/incompl':'/in-shell', '_':'-core', '.ps':'', 'caps':'cap'}
+   replacements = {'pics/':''}
+
+   for line in infile:
+      if 'FloatBarrier' not in line:
+          for src, target in replacements.iteritems():
+              line = line.replace(src, target)
+          outfile.write(line)
+
+   infile.close()
+   outfile.close()
+
+   shutil.copyfile('tmpfile',filename)
+   os.remove('tmpfile')
